### 2017-08-30 paper/galsize_paper.tex
Added latex template

\documentclass[usenatbib,usegraphicx,letterpaper]{mn2e}
\usepackage[totalwidth=480pt,totalheight=680pt]{geometry}

\usepackage{amssymb}
\usepackage{epsfig}
\usepackage{amsmath}
\usepackage{color}
%\usepackage{hyperref}

\bibliographystyle{mn2e}

%-------- journals
\newcommand{\araa}{ARAA~}
\newcommand{\apj}{ApJ~}
\newcommand{\apjl}{ApJL~}
\newcommand{\apjs}{ApJS~}
\newcommand{\mnras}{MNRAS~}
\newcommand{\nat}{Nature~}
\newcommand{\physrep}{Phys. Rep.~}
\newcommand{\aj}{AJ~}

%%%% Misc %%%
\newcommand{\beq}{\begin{equation}}
\newcommand{\eeq}{\end{equation}}
\newcommand{\beqray}{\begin{eqnarray}}
\newcommand{\eeqray}{\end{eqnarray}}

\newcommand{\ben}{\begin{enumerate}}
\newcommand{\een}{\end{enumerate}}
\newcommand{\bit}{\begin{itemize}}
\newcommand{\eit}{\end{itemize}}

\usepackage{epsfig}  \usepackage{graphicx}   \usepackage{rotating}

\begin{document}

\title[The Galaxy Size--Halo Connection]
{On the Galaxy Size--Halo Connection}

\author[Homeboy et al.]{Homeboy}

\maketitle

\begin{abstract}
Some abstract 
\end{abstract}

\section{Introduction}
\label{sec:intro}
Some introduction goes here.

\section*{Acknowledgments}

\end{document}

### 2017-08-30 paper/ms.sh

@@ -1,0 +1,8 @@
+set local=./
+
+latex sham_colors.tex
+bibtex sham_colors
+latex sham_colors.tex
+latex sham_colors.tex
+dvips sham_colors.dvi -Ppdf -G0 -z -t a4
+ps2pdf sham_colors.ps

### 2017-08-30 paper/galsize_paper.tex
Migrated abstract draft into latex

@@
 
+%%%%%%%%  galaxy properties  %%%%%%%%
+\newcommand{\rhalf}{R_{1/2}}
+\newcommand{\rhalfdisk}{R_{1/2}^{\rm disk}}
+\newcommand{\rhalfbulge}{R_{1/2}^{\rm bulge}}
+\newcommand{\adisk}{A_{\rm disk}}
+\newcommand{\abulge}{A_{\rm bulge}}
+\newcommand{\alphadisk}{\alpha_{\rm disk}}
+\newcommand{\alphabulge}{\alpha_{\rm bulge}}
+\newcommand{\rvir}{R_{\rm vir}}
+\newcommand{\bt}{{\rm B/T}}
+\newcommand{\mstar}{M_{\ast}}
+
+%%%%%%%%  halo properties  %%%%%%%%
+\newcommand{\halospin}{\lambda_{\rm halo}}
+\newcommand{\mvir}{M_{\rm vir}}
+\newcommand{\macc}{M_{\rm acc}}
+
+%%%%%%%%  observations  %%%%%%%%
+\newcommand{\rproj}{r_{\rm p}}
+\newcommand{\wproj}{w_{\rm p}}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
 \usepackage{epsfig}  \usepackage{graphicx}   \usepackage{rotating}
@@
 
-\author[Homeboy et al.]{Homeboy}
+\author[Hearin, Behroozi, Kravtsov \& Moster]{
+Andrew Hearin$^{1}$, Peter Behroozi$^{2}$, Andrey Kravtsov$^{3}$, Benjamin Moster$^{4}$\\
+$^{1}$Argonne National Laboratory, Argonne, IL, USA 60439, USA\\
+$^{2}$Department of Physics, University of Arizona, 1118 E 4th St, Tucson, AZ 85721 USA\\
+$^{3}$Department of Astronomy \& Astrophysics, The University of Chicago, Chicago, IL 60637 USA\\
+$^{4}$Universit{\"a}ts-Sternwarte, Ludwig-Maximilians-Universit{\"a}t M{\"u}nchen, Scheinerstr. 1, 81679 M{\"u}nchen, Germany
+}
 
@@
 \begin{abstract}
-Some abstract 
+We derive empirical modeling constraints on the connection between dark matter halos and the half-mass radius $\rhalf$ of galaxy bulges and disks.
+We show that both $\rhalfdisk$ and $\rhalfbulge$ are well-described by power law scaling relations with halo virial radius, $\rhalf=A\rvir^{\alpha}.$ Novel to this work, we use new SDSS measurements of the $\rhalf-$dependence of galaxy clustering to constrain the model parameters, $A_{\rm bulge}, A_{\rm disk}, \alpha_{\rm bulge},\alpha_{\rm disk},$ and log-normal scatter $\sigma_{R_{1/2}}.$ Even when only coarsely tuning these parameters to the observed one-point functions $\langle\rhalfdisk|\mstar^{\rm disk}\rangle$ and $\langle\rhalfbulge|\mstar^{\rm bulge}\rangle,$ our model accurately predicts the observed two-point clustering on small- and large-scales.
+This success non-trivial, as we show that galaxy clustering is highly sensitive to the physics that shapes satellite galaxy profiles.
+We find no evidence for the commonly assumed relation between halo spin $\halospin$ and $\rhalfdisk,$ and show that this assumption cannot be meaningfully constrained with either the clustering or lensing of  $L_{\ast}$ galaxies.
+Our results provide simple boundary conditions for more complex and fine-grained models of galaxy size.
+We make our python code publicly available to support cosmological surveys that require realistic synthetic galaxy populations.
 \end{abstract}

### 2017-08-30 paper/galsize_paper.tex
Migrated figures and captions into latex

@@
 
+\section{Data and Simulations}
+\label{sec:data}
+
+\subsection{Galaxy Sample}
+\label{subsec:galaxydata}
+
+\subsection{Clustering Measurements}
+\label{subsec:clusteringmeasurements}
+
+\subsection{Baseline Mock Catalog}
+\label{subsec:baselinemock}
+
+\section{Galaxy Profile Model}
+\label{sec:model}
+
+\section{Results}
+\label{sec:results}
+
+%---------------------------------------------------------------------------------------------------
+\begin{figure*}
+\centering
+\includegraphics[width=12cm]{FIGS/size_vs_stellar_mass_multipanel_bt_decomposition.pdf}
+\caption{
+{\bf One-point data used to fit the fiducial model.}
+Scattered points show the $\rhalf-\mstar$ relation for SDSS galaxies as measured in \citet{meert_etal15}.
+Bulge-dominated galaxies are defined in terms of the bulge-to-total stellar mass ratio $\bt>=0.75,$ disk-dominated galaxies $\bt<0.25,$ mixed morphology as $0.25 < \bt < 0.75.$ The black curve in each panel shows the $\rhalf-\mstar$ relation implied by our fiducial model, in which $\rhalf=A\rvir^\alpha,$ with $\adisk=0.14=7\abulge, \alphadisk=1, \alphabulge=5/4,$ and uncorrelated log-normal scatter of $0.2$ dex about these relations.
+}
+\label{fig:scatter_plot}
+\end{figure*}
+%-----------------------------------------------------------------------------------------------------
+
+%---------------------------------------------------------------------------------------------------
+\begin{figure*}
+\centering
+\includegraphics[width=12cm]{FIGS/size_clustering_ratios_bt_decomposition_model_vs_sdss.pdf}
+\caption{
+{\bf Two-point clustering data used to validate the fiducial model.}
+Points with error bars show new SDSS measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj,$ compared to predictions by the model tuned to the measurements shown in Fig.~\ref{fig:scatter_plot}.
+We define a disk or bulge as ``large" or ``small" according to whether it is above or below the median size for its stellar mass.
+The y-axis shows clustering strength ratios, so that, for example, a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of comparable stellar mass.
+We show results separately for disk-dominated galaxies ({\em top} panels) and bulge-dominated galaxies ({\em bottom }panels), and different thresholds in total stellar mass in the {\em left} and {\em right} panels.
+The successful prediction shown here is remarkable because the model was not fit to these data, and because two-point clustering is highly sensitive to the physics that shapes satellite galaxy profiles (see Fig.~\ref{fig:satellites}).
+}
+\label{fig:scatter_plot}
+\end{figure*}
+%-----------------------------------------------------------------------------------------------------
+
+%---------------------------------------------------------------------------------------------------
+\begin{figure*}
+\centering
+\includegraphics[width=12cm]{FIGS/alternate_satellite_models_size_clustering_ratios.pdf}
+\caption{
+{\bf Clustering provides tight constraints on the relative sizes of centrals and satellites.} 
+Here we compare our fiducial model, in which satellite galaxy size is set by $\rvir$ at the time of infall, to an alternative model analogous to \citet{watson_etal12} in which satellite sizes contract in proportion to $(\mvir/\macc)^{1/3}.$ The large differences between solid and dashed curves in the top panels show that the $\rhalf-$dependence of galaxy clustering ratios is highly sensitive to the post-infall evolution of satellite galaxy profiles.
+The successful prediction of our fiducial model, in which satellite galaxies neither contract nor puff up after infall, places tight constraints on satellite-specific physical processes, which must be either negligible or conspiratorially produce little-to-no size change after accretion.
+}
+\label{fig:satellites}
+\end{figure*}
+%-----------------------------------------------------------------------------------------------------
+
+%---------------------------------------------------------------------------------------------------
+\begin{figure*}
+\centering
+\includegraphics[width=8cm]{FIGS/size_clustering_ratios_bt_decomposition_spin_size_correlation.pdf}
+\includegraphics[width=8cm]{FIGS/central_lensing_spin_size_correlation.pdf}
+\caption{
+{\bf Clustering and lensing provide no constraining power on the assumption that $\rhalfdisk\propto\halospin.$} 
+We compare the predictions between our fiducial model in which sizes are purely stochastic, and an alternative model motivated by \citet{mo_mao_white98} in which central galaxy disk size is maximally correlated with host halo spin at fixed stellar mass \citep[implemented via conditional abundance matching, e.g.,][]{hearin_etal13b}.
+The tiny differences between the solid and dashed curves imply that conventional large-scale structure measurements cannot even in principle provide compelling evidence pertaining to the assumption that $\rhalfdisk\propto\halospin.$
+}
+\label{fig:halospin_lensing}
+\end{figure*}
+%-----------------------------------------------------------------------------------------------------
+
+\section{Discussion}
+\label{sec:discussion}
+
+\subsection{Relation to Previous Work}
+\label{subsec:previouswork}
+
+\section{Conclusion}
+\label{sec:conclusion}
+
+\subsection{Summary}
+\label{subsec:summary}
+
 \section*{Acknowledgments}
 
+\bibliography{galsize_paper}
+
 \end{document}

### 2017-08-30 paper/galsize_paper.tex
Added new figure of B/T PDF of centrals vs. satellites

@@
 \newcommand{\mstar}{M_{\ast}}
+\newcommand{\ssfr}{{\rm sSFR}}
 
@@
 \newcommand{\macc}{M_{\rm acc}}
+\newcommand{\mpeak}{M_{\rm peak}}
+\newcommand{\mhalo}{M_{\rm halo}}
 
@@
 }
-\label{fig:scatter_plot}
+\label{fig:clustering_ratio_upshot}
 \end{figure*}
+%-----------------------------------------------------------------------------------------------------
+
+%---------------------------------------------------------------------------------------------------
+\begin{figure}
+\centering
+\includegraphics[width=8cm]{FIGS/random_bt_centrals_vs_satellites.pdf}
+\caption{
+{\bf Morphologies of centrals and satellites of the same halo mass.} We show the PDF of the bulge-to-total stellar mass ratio $\bt$ of central and satellite galaxies of the same halo mass $\mhalo=\mpeak.$ In the model, the PDF of $\bt$ is determined by the stellar mass $\mstar$ and specific star-formation rate $\ssfr$ statistically determine, with no residual dependence on the cosmic web.
+Satellite galaxies in the model are ``bulgier" than centrals of the same halo mass because satellites are more quiescent than centrals of the same stellar mass.
+Thus our baseline model ansatz is that the morphology-density relation is purely derived from the color-density relation.
+Since composite size $\rhalf$ in the model is given by $\rhalf=(\bt)\rhalfbulge + (1-\bt)\rhalfdisk,$ this ansatz in turn implies that smaller galaxies cluster more strongly relative to larger galaxies of the same stellar mass, as seen in the measurements shown in Fig.~\ref{fig:clustering_ratio_upshot}.
+}
+\label{fig:bt_censat}
+\end{figure}
 %-----------------------------------------------------------------------------------------------------

### 2017-08-30 paper/galsize_paper.tex
Updated modeling section with description of baseline model

@@
 \newcommand{\ssfr}{{\rm sSFR}}
+\newcommand{\sfr}{{\rm SFR}}
 
@@
 \label{subsec:baselinemock}
+
+\subsubsection{Mapping $\mstar$ and $\sfr$ to halos}
+\label{subsubsec:umachine}
+The starting point of our model is the best-fit {\tt UniverseMachine} model \citep[][in prep]{behroozi_etal17}.
+This model maps stellar mass and star-formation rate to every halo and subhalo at each snapshot in the Bolshoi-Planck simulation.
+The stellar mass function, quenched fraction, SFR density, and SFR-dependent clustering are all accurately captured by this model from $z=0-10.$ The model we have developed in the present work does not depend in an essential way upon the {\tt UniverseMachine} model in particular, we only require some reasonably accurate starting point for the $\mstar$ and $\ssfr$ values mapped to simulated halos.
+
+\subsubsection{Mapping $\bt$ decomposition to halos}
+\label{subsubsec:random_bt_model}
+
+Our model for galaxy size is further predicated upon the mapping between dark matter halos and $\bt,$ the fraction of stellar mass in the bulge.
+In a companion paper to this work, we will present a separate empirical model for the $\bt-$halo connection.
+For our present purposes, we instead rely upon the simplest possible assumption for this connection that recovers the observed distribution $P(\bt\vert\mstar,\ssfr):$ we suppose that galaxy $\bt$ has no dependence whatsoever upon halo environment or assembly, beyond what is inherited by the mutual correlation between $\mstar, \ssfr$ and the cosmic web.
+That is, we map $\bt$ to dark matter halos by using the $\mstar$ and $\ssfr$ values from {\tt UniverseMachine} to randomly select the $\bt$ of a galaxy from our SDSS sample with a similar $\mstar$ and $\ssfr.$ The intuitive interpretation of this modeling choice is that we assume the morphology-density relation is entirely determined by the color-density relation.
 

### 2017-08-30 paper/galsize_paper.tex
Updated draft with brief description of galaxy sample

@@
 
+Our galaxy sample comes from Data Release 10 of the Sloan Digital Sky Survey \citep[SDSS][]{ahn_etal14}.
+We study the same $\mstar-$complete galaxy sample used in \citet{behroozi_etal15}, to which we refer the reader for details.
+Values for $\mstar$ and $\sfr$ are taken from the MPA-JHU value-added catalog \citep{kauffmann_etal03,brinchmann_etal04}.
+
 \subsection{Clustering Measurements}
@@
 \label{subsubsec:umachine}
+
 The starting point of our model is the best-fit {\tt UniverseMachine} model \citep[][in prep]{behroozi_etal17}.

### 2017-08-30 paper/galsize_paper.tex
Updated references to Meert15
Finished sketch of galaxy sample description

@@
 
+%%%%%%%%  units  %%%%%%%%
+\newcommand{\kpc}{{\rm kpc}}
+\newcommand{\mpc}{{\rm Mpc}}
+
 %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
@@
 
+We additionally use the catalog of SDSS galaxy profile decompositions provided by \citet{meert_etal15}.
+In the version of this catalog that we use, two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile for the bulge and disk, respectively.
+We cross-match our DR10 sample against the \citet{meert_etal15} scale radii and flux ratios of the two components, giving us a volume-limited galaxy sample with values of $\mstar,\ssfr,\rhalfbulge,\rhalfdisk,$ and $\bt.$ Together with the present work, we make publicly available this cross-matched catalog, as well as code to generate the catalog from the original data files and load it into a python interpreter.
+
 \subsection{Clustering Measurements}
 \label{subsec:clusteringmeasurements}
+
+We calculate two-point clustering $\wproj$ with line-of-sight projection of $\pi_{\rm max}=20\mpc$ using the {\tt correl} program in {\tt UniverseMachine}.
 

### 2017-08-30 paper/galsize_paper.tex
Finished baseline simulation and model discussion

@@
 
-\subsection{Galaxy Sample}
+\subsection{Galaxy Sample and Measurements}
 \label{subsec:galaxydata}
@@
 In the version of this catalog that we use, two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile for the bulge and disk, respectively.
-We cross-match our DR10 sample against the \citet{meert_etal15} scale radii and flux ratios of the two components, giving us a volume-limited galaxy sample with values of $\mstar,\ssfr,\rhalfbulge,\rhalfdisk,$ and $\bt.$ Together with the present work, we make publicly available this cross-matched catalog, as well as code to generate the catalog from the original data files and load it into a python interpreter.
-
-\subsection{Clustering Measurements}
-\label{subsec:clusteringmeasurements}
+We cross-match our DR10 sample against the \citet{meert_etal15} scale radii and flux ratios of the two components, giving us a volume-limited galaxy sample with values of $\mstar,\ssfr,\rhalfbulge,\rhalfdisk,$ and $\bt.$
 
 We calculate two-point clustering $\wproj$ with line-of-sight projection of $\pi_{\rm max}=20\mpc$ using the {\tt correl} program in {\tt UniverseMachine}.
+
+Together with the present work, we make publicly available this cross-matched catalog, as well as code to generate the catalog from the original data files and load it into a python interpreter.
+
+\subsection{Simulation and Halos}
+\label{subsec:sim}
+
+{\tt Rockstar} subhalos identified at $z=0$ in the Bolshoi-Planck simulation are the basis of all our modeling.
 
@@
 
-\subsubsection{Mapping $\mstar$ and $\sfr$ to halos}
+\subsubsection{Mapping $\mstar$ \& $\sfr$ to halos}
 \label{subsubsec:umachine}
@@
 
-\subsubsection{Mapping $\bt$ decomposition to halos}
+\subsubsection{Mapping $\bt$ to halos}
 \label{subsubsec:random_bt_model}

### 2017-08-30 paper/galsize_paper.tex
Finished sketch of model

@@
 \newcommand{\alphabulge}{\alpha_{\rm bulge}}
+\newcommand{\sigmarhalf}{\sigma_{\rm R_{1/2}}}
 \newcommand{\rvir}{R_{\rm vir}}
@@
 We derive empirical modeling constraints on the connection between dark matter halos and the half-mass radius $\rhalf$ of galaxy bulges and disks.
-We show that both $\rhalfdisk$ and $\rhalfbulge$ are well-described by power law scaling relations with halo virial radius, $\rhalf=A\rvir^{\alpha}.$ Novel to this work, we use new SDSS measurements of the $\rhalf-$dependence of galaxy clustering to constrain the model parameters, $A_{\rm bulge}, A_{\rm disk}, \alpha_{\rm bulge},\alpha_{\rm disk},$ and log-normal scatter $\sigma_{R_{1/2}}.$ Even when only coarsely tuning these parameters to the observed one-point functions $\langle\rhalfdisk|\mstar^{\rm disk}\rangle$ and $\langle\rhalfbulge|\mstar^{\rm bulge}\rangle,$ our model accurately predicts the observed two-point clustering on small- and large-scales.
+We show that both $\rhalfdisk$ and $\rhalfbulge$ are well-described by power law scaling relations with halo virial radius, $\rhalf=A\rvir^{\alpha}.$ Novel to this work, we use new SDSS measurements of the $\rhalf-$dependence of galaxy clustering to constrain the model parameters, $A_{\rm bulge}, A_{\rm disk}, \alpha_{\rm bulge},\alpha_{\rm disk},$ and log-normal scatter $\sigmarhalf.$ Even when only coarsely tuning these parameters to the observed one-point functions $\langle\rhalfdisk|\mstar^{\rm disk}\rangle$ and $\langle\rhalfbulge|\mstar^{\rm bulge}\rangle,$ our model accurately predicts the observed two-point clustering on small- and large-scales.
 This success non-trivial, as we show that galaxy clustering is highly sensitive to the physics that shapes satellite galaxy profiles.
@@
 In the version of this catalog that we use, two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile for the bulge and disk, respectively.
-We cross-match our DR10 sample against the \citet{meert_etal15} scale radii and flux ratios of the two components, giving us a volume-limited galaxy sample with values of $\mstar,\ssfr,\rhalfbulge,\rhalfdisk,$ and $\bt.$
+We cross-match our DR10 sample against the \citet{meert_etal15} scale radius of the composite profile and flux ratios of the two components, giving us a volume-limited galaxy sample with values of $\mstar,\ssfr,\rhalf,$ and $\bt.$
 
@@
 \label{sec:model}
+
+Motivated by the \citet{kravtsov13} results, we model the half-mass radii of galaxies as separate power law functions of halo virial radius:
+
+\begin{eqnarray}
+\rhalfbulge &=& \abulge\rvir^{\alphabulge} \\
+\rhalfdisk &=& \adisk\rvir^{\alphadisk} 
+\end{eqnarray}
+
+For central galaxies residing in host halos, we use the present-day virial radius; for satellite galaxies we use the virial radius at the time of accretion, using physical units of $\kpc.$ We model the composite size of model galaxies as
+\beq
+\rhalf = (\bt)\rhalfbulge + (1-\bt)\rhalfdisk.
+\eeq
+
+When generating Monte Carlo realizations of our model galaxy population, we add log-normal scatter $\sigmarhalf$ separately to each component.
+Our model for sizes thus has five free parameters: $\abulge, \adisk, \alphabulge, \alphadisk,$ and $\sigmarhalf.$
 

### 2017-08-31 paper/galsize_paper.tex
Changed title
Added outline of Results section

@@
 \title[The Galaxy Size--Halo Connection]
-{On the Galaxy Size--Halo Connection}
+{Galaxy Clustering Constraints on the Galaxy Size--Halo Connection}
 
@@
 \begin{eqnarray}
+\label{eq:fiducial_model}
 \rhalfbulge &=& \abulge\rvir^{\alphabulge} \\
@@
 \label{sec:results}
+
+In \S~\ref{subsec:tests1} we show comparisons between the fiducial galaxy profile model described in \S~\ref{sec:model} and our SDSS sample.
+We demonstrate the sensitivity of galaxy clustering measurements to the post-infall evolution of satellite profiles in \S~\ref{subsec:tests2}, establishing the success of our fiducial model as non-trivial.
+In \S~\ref{subsec:tests3} we show that even highly idealized measurements of galaxy clustering and lensing are insensitive to assumptions about the relation between $\halospin$ and $\rhalf.$
+
+\subsection{Tests of the Fiducial Power Law Model}
+\label{subsec:tests1}
+
+\subsection{Sensitivity of Clustering to Satellite Profile Evolution}
+\label{subsec:tests2}
+
+\subsection{Insensitivity of Clustering and Lensing to Halo Spin Correlations}
+\label{subsec:tests3}
 

### 2017-08-31 paper/galsize_paper.tex
Improved clarity of distinction between different quantifications of galaxy size

@@
 In the version of this catalog that we use, two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile for the bulge and disk, respectively.
-We cross-match our DR10 sample against the \citet{meert_etal15} scale radius of the composite profile and flux ratios of the two components, giving us a volume-limited galaxy sample with values of $\mstar,\ssfr,\rhalf,$ and $\bt.$
+We cross-match our DR10 sample against the \citet{meert_etal15} scale radius of the composite profile, $\rhalf,$ and the $r-$band flux ratio of the two components, $\bt,$ giving us a volume-limited galaxy sample with values of $\mstar,\ssfr,\rhalf,$ and $\bt.$
 
 We calculate two-point clustering $\wproj$ with line-of-sight projection of $\pi_{\rm max}=20\mpc$ using the {\tt correl} program in {\tt UniverseMachine}.
+Our results in \S~\ref{sec:results} will give special focus on the dependence of $\wproj$ upon composite galaxy size $\rhalf.$ We will quantify this dependence in terms of {\em clustering ratios} of ``large" vs.
+``small" galaxies, defined according to whether composite galaxy size is above or below $\langle\rhalf\vert\mstar\rangle,$ computed as the median of a sliding stellar mass window with a width of $N_{\rm gal}=1000.$
 
@@
 
+We reiterate an important distinction drawn in the formulation of our forward modeling approach.
+In the model described above, $\rhalfbulge$ and $\rhalfdisk$ are forward modeling quantities that we aim to constrain through SDSS observations of {\em composite} galaxy size $\rhalf.$ In particular, both model and real galaxies will be categorized as ``small" or ``large`` according to whether $\rhalf$ is above or below the median size for a galaxy with total stellar mass $\mstar.$
+
 \section{Results}
@@
 \label{subsec:tests1}
+
+The results shown in \citet{kravtsov13} simplify our task of parameter space exploration: the assumption that composite galaxy size $\rhalf$ scales in linear proportion to halo radius $\rvir$ gives a qualitatively good description of SDSS data over many orders of magnitude in galaxy mass.
+In Figure \ref{fig:scatter_plot} we show the scaling of composite galaxy size $\rhalf$ with $\mstar,$ with separate panels dedicated to subsamples of galaxies divided according to value of $\bt.$ We refer to galaxies with $\bt<0.25$ as ``disk-dominated", $\bt>=0.75$ as ``bulge-dominated", and $0.25<=\bt<0.75$ as ``mixed morphology".
 
@@
 
+\subsection{Progression from Backwards to Forwards Modeling}
+\label{subsec:forwardsmodeling}
+
 \subsection{Relation to Previous Work}

### 2017-08-31 paper/galsize_paper.tex
Finished draft of section 4.1.1

@@
 \newcommand{\aj}{AJ~}
+\newcommand{\pasp}{ASP~}
 
@@
 
+\subsubsection{Scaling of $\rhalf$ with $\mstar$}
+\label{subsubsec:scaling_relation}
+
+In Figure \ref{fig:scatter_plot} we show the scaling of composite galaxy size $\rhalf$ with $\mstar,$ with separate panels dedicated to subsamples of galaxies divided according to value of $\bt.$ We refer to galaxies with $\bt<0.25$ as ``disk-dominated", $\bt>=0.75$ as ``bulge-dominated", and $0.25<=\bt<0.75$ as ``mixed morphology".
+
 The results shown in \citet{kravtsov13} simplify our task of parameter space exploration: the assumption that composite galaxy size $\rhalf$ scales in linear proportion to halo radius $\rvir$ gives a qualitatively good description of SDSS data over many orders of magnitude in galaxy mass.
-In Figure \ref{fig:scatter_plot} we show the scaling of composite galaxy size $\rhalf$ with $\mstar,$ with separate panels dedicated to subsamples of galaxies divided according to value of $\bt.$ We refer to galaxies with $\bt<0.25$ as ``disk-dominated", $\bt>=0.75$ as ``bulge-dominated", and $0.25<=\bt<0.75$ as ``mixed morphology".
+As first pointed out in \citet{kravtsov13}, this linearization is non-trivial because of the well-known curvature in the scaling relation of $\langle\rhalf\vert\mstar\rangle,$ which is visually apparent in all panels of Fig.~\ref{fig:scatter_plot}.
+
+Comparison of the top panels of Fig.~\ref{fig:scatter_plot} show that this linearization is only approximate; evidently, the composite size $\rhalf$ of bulge-dominated galaxies has a steeper scaling relation with $\mstar$ relative to disk-dominated galaxies.
+This difference motivates our simple extension of the \citet{kravtsov13} model, in which composite size $\rhalf$ of disk- and bulge-dominated galaxies scale according to separate power laws.
+
+Through MCMC parameter space exploration aided by {\tt emcee} \citep{emcee_hammer}, we find a good description of the observed one-point scaling relations is given by model galaxies with the parameters $\adisk=0.014=7\abulge, \alphadisk=1, \alphabulge=5/4,$ with log-normal scatter of $0.2$ dex motivated by \citet{somerville_etal17}.
+The black curves in Fig.~\ref{fig:scatter_plot} illustrate the median $\langle\rhalf\vert\mstar\rangle.$
+
+We confirm the visual impression of comparing the top panels of Fig.~\ref{fig:scatter_plot}: we are unable to find a parameter combination in which the composite size of both bulge- and disk-dominated galaxies have linear ($\alpha=1$) scaling with $\rvir.$ We do not quantitatively rule out such a scaling relation, as this would require careful investigation of the systematic error budget of galaxy profile modeling that we consider beyond the scope, though well-motivated, by the present work.
+
+\subsubsection{Dependence of clustering on $\rhalf$}
+\label{subsubsec:clustering_tests}
 
@@
 Scattered points show the $\rhalf-\mstar$ relation for SDSS galaxies as measured in \citet{meert_etal15}.
-Bulge-dominated galaxies are defined in terms of the bulge-to-total stellar mass ratio $\bt>=0.75,$ disk-dominated galaxies $\bt<0.25,$ mixed morphology as $0.25 < \bt < 0.75.$ The black curve in each panel shows the $\rhalf-\mstar$ relation implied by our fiducial model, in which $\rhalf=A\rvir^\alpha,$ with $\adisk=0.14=7\abulge, \alphadisk=1, \alphabulge=5/4,$ and uncorrelated log-normal scatter of $0.2$ dex about these relations.
+Bulge-dominated galaxies are defined in terms of the bulge-to-total stellar mass ratio $\bt>=0.75,$ disk-dominated galaxies $\bt<0.25,$ mixed morphology as $0.25 < \bt < 0.75.$ The black curve in each panel shows the $\rhalf-\mstar$ relation implied by our fiducial model, in which $\rhalf=A\rvir^\alpha,$ with $\adisk=0.014=7\abulge, \alphadisk=1, \alphabulge=5/4,$ and uncorrelated log-normal scatter of $0.2$ dex about these relations.
 }

### 2017-08-31 paper/galsize_paper.tex
Slight expansion of beginning of results section

@@
 We demonstrate the sensitivity of galaxy clustering measurements to the post-infall evolution of satellite profiles in \S~\ref{subsec:tests2}, establishing the success of our fiducial model as non-trivial.
-In \S~\ref{subsec:tests3} we show that even highly idealized measurements of galaxy clustering and lensing are insensitive to assumptions about the relation between $\halospin$ and $\rhalf.$
+In \S~\ref{subsec:tests3} we show that even highly idealized measurements of galaxy clustering and lensing are insensitive to assumptions about the relation between halo spin $\halospin$ and size $\rhalf$ of disk-dominated galaxies, implying that large-scale structure observations yield little-to-no constraining power on such assumptions.
 

### 2017-08-31 paper/galsize_paper.tex
Improved description of galaxy sample

@@
 We additionally use the catalog of SDSS galaxy profile decompositions provided by \citet{meert_etal15}.
-In the version of this catalog that we use, two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile for the bulge and disk, respectively.
-We cross-match our DR10 sample against the \citet{meert_etal15} scale radius of the composite profile, $\rhalf,$ and the $r-$band flux ratio of the two components, $\bt,$ giving us a volume-limited galaxy sample with values of $\mstar,\ssfr,\rhalf,$ and $\bt.$
+In the version of this catalog that we use, two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile.
+We cross-match our DR10 sample against the \citet{meert_etal15} catalog values of $\rhalf,$ the half-light radius of the full profile, and $\bt,$ the $r-$band flux ratio of the de Vaucouleurs component to the total $r-$band flux.
+This cross-matching gives us a volume-limited galaxy sample with values of $\mstar,$ $\ssfr,$ $\rhalf,$ and $\bt.$ Together with the present work, we make publicly available this cross-matched catalog, as well as code to generate the catalog from the original data files and load it into a python interpreter.
 
@@
 ``small" galaxies, defined according to whether composite galaxy size is above or below $\langle\rhalf\vert\mstar\rangle,$ computed as the median of a sliding stellar mass window with a width of $N_{\rm gal}=1000.$
-
-Together with the present work, we make publicly available this cross-matched catalog, as well as code to generate the catalog from the original data files and load it into a python interpreter.
 

### 2017-08-31 paper/galsize_paper.tex
Switched all figures to single-column format

@@
 %---------------------------------------------------------------------------------------------------
-\begin{figure*}
+\begin{figure}
 \centering
-\includegraphics[width=12cm]{FIGS/size_vs_stellar_mass_multipanel_bt_decomposition.pdf}
+\includegraphics[width=8cm]{FIGS/size_vs_stellar_mass_multipanel_bt_decomposition.pdf}
 \caption{
@@
 \label{fig:scatter_plot}
-\end{figure*}
+\end{figure}
 %-----------------------------------------------------------------------------------------------------
@@
 %---------------------------------------------------------------------------------------------------
-\begin{figure*}
+\begin{figure}
 \centering
-\includegraphics[width=12cm]{FIGS/size_clustering_ratios_bt_decomposition_model_vs_sdss.pdf}
+\includegraphics[width=8cm]{FIGS/size_clustering_ratios_bt_decomposition_model_vs_sdss.pdf}
 \caption{
@@
 \label{fig:clustering_ratio_upshot}
-\end{figure*}
+\end{figure}
 %-----------------------------------------------------------------------------------------------------
@@
 %---------------------------------------------------------------------------------------------------
-\begin{figure*}
+\begin{figure}
 \centering
-\includegraphics[width=12cm]{FIGS/alternate_satellite_models_size_clustering_ratios.pdf}
+\includegraphics[width=8cm]{FIGS/alternate_satellite_models_size_clustering_ratios.pdf}
 \caption{
@@
 \label{fig:satellites}
-\end{figure*}
+\end{figure}
 %-----------------------------------------------------------------------------------------------------
@@
 %---------------------------------------------------------------------------------------------------
-\begin{figure*}
+\begin{figure}
 \centering
@@
 \label{fig:halospin_lensing}
-\end{figure*}
+\end{figure}
 %-----------------------------------------------------------------------------------------------------

### 2017-08-31 paper/galsize_paper.tex
Finished formal description of the y-axis in upshot clustering figure

@@
 \usepackage{color}
-%\usepackage{hyperref}
 
@@
 
-We calculate two-point clustering $\wproj$ with line-of-sight projection of $\pi_{\rm max}=20\mpc$ using the {\tt correl} program in {\tt UniverseMachine}.
+We calculate two-point clustering $\wproj$ of our SDSS galaxy sample using line-of-sight projection of $\pi_{\rm max}=20\mpc$ using the {\tt correl} program in {\tt UniverseMachine}.
 Our results in \S~\ref{sec:results} will give special focus on the dependence of $\wproj$ upon composite galaxy size $\rhalf.$ We will quantify this dependence in terms of {\em clustering ratios} of ``large" vs.
@@
 
-\subsection{Baseline Mock Catalog}
+\subsection{Baseline Model and Mock Measurements}
 \label{subsec:baselinemock}
@@
 That is, we map $\bt$ to dark matter halos by using the $\mstar$ and $\ssfr$ values from {\tt UniverseMachine} to randomly select the $\bt$ of a galaxy from our SDSS sample with a similar $\mstar$ and $\ssfr.$ The intuitive interpretation of this modeling choice is that we assume the morphology-density relation is entirely determined by the color-density relation.
+
+\subsection{Mock Measurements of Clustering and Lensing}
+\label{subsec:mock_measurements}
+
+For mock galaxies, to compute galaxy clustering we employ the distant observer approximation by treating the simulation $z-$axis as the line-of-sight.
+We compute $\wproj$ using the {\tt mock\_observables.wp} function in {\tt Halotools}, which is a python implementation of the algorithm in the {\tt Corrfunc} C library \citep{sinha_etal17}.
 
@@
 \label{subsubsec:clustering_tests}
+
+In this section we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj.$ Galaxy clustering has complex, simultaneous dependence upon $\mstar,$ $\ssfr,$ $\rhalf,$ and $\bt.$ Since the purpose of this work is to test models of composite galaxy size $\rhalf,$ we design a measurement that is specifically tailored to isolate the influence of $\rhalf$ on the two-point function, while minimizing the dependence upon the other correlated variables.
+
+To achieve this, we compute projected clustering separately for $\mstar-$complete samples of galaxies defined by simultaneous cuts on $\bt$ and $\rhalf,$ described as follows.
+First, we construct subsamples of disk-dominated and bulge-dominated galaxies using cuts of $\bt<0.25$ and $\bt>0.75,$ respectively, as in \S~\ref{subsubsec:scaling_relation} above.
+Separately for each $\bt-$selected subsample, we calculate $\rangle\rhalf\vert\mstar\rangle,$ the median composite size of the sample as a function of total galaxy stellar mass.
+We split each $\bt-$selected sample in half according to whether the galaxy has a composite size $\rhalf$ that is above or below this median value.
+For any $\mstar-$complete threshold, this gives four subsamples of large and small, disk- and bulge-dominated galaxies.
+For each $\bt-$selected sample, we calculate the difference $\wproj^{\rm large}-\wproj^{\rm small},$ scaled by $\wproj^{\rm all},$ the clustering of the $\bt-$selected sample prior to splitting on $\rhalf,$ and refer to this quantity as {\em the $\rhalf$ clustering ratio}.
+
+The y-axis of each panel in Figure \ref{fig:clustering_ratio_upshot} shows these $\rhalf$ clustering ratios, with left and right panels showing measurements for $\mstar>10^{10}M_{\odot}$ and $\mstar>10^{10.5}M_{\odot}$ thresholds in total stellar mass, and top and bottom panels showing results for disk- and bulge-dominated samples, respectively.
 

### 2017-08-31 paper/galsize_paper.tex
Finished draft of 4.1.2

@@
 
-In this section we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj.$ Galaxy clustering has complex, simultaneous dependence upon $\mstar,$ $\ssfr,$ $\rhalf,$ and $\bt.$ Since the purpose of this work is to test models of composite galaxy size $\rhalf,$ we design a measurement that is specifically tailored to isolate the influence of $\rhalf$ on the two-point function, while minimizing the dependence upon the other correlated variables.
+In this section we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj(\rproj).$ Galaxy clustering has complex, simultaneous dependence upon $\mstar,$ $\ssfr,$ $\rhalf,$ and $\bt.$ Since the purpose of this work is to test models of composite galaxy size $\rhalf,$ we design a measurement that is specifically tailored to isolate the influence of $\rhalf$ on the two-point function, while minimizing the dependence upon the other correlated variables.
 
@@
 First, we construct subsamples of disk-dominated and bulge-dominated galaxies using cuts of $\bt<0.25$ and $\bt>0.75,$ respectively, as in \S~\ref{subsubsec:scaling_relation} above.
-Separately for each $\bt-$selected subsample, we calculate $\rangle\rhalf\vert\mstar\rangle,$ the median composite size of the sample as a function of total galaxy stellar mass.
+Separately for each $\bt-$selected subsample, we calculate $\langle\rhalf\vert\mstar;\bt\rangle,$ the median composite size of the sample as a function of total galaxy stellar mass.
 We split each $\bt-$selected sample in half according to whether the galaxy has a composite size $\rhalf$ that is above or below this median value.
@@
 The y-axis of each panel in Figure \ref{fig:clustering_ratio_upshot} shows these $\rhalf$ clustering ratios, with left and right panels showing measurements for $\mstar>10^{10}M_{\odot}$ and $\mstar>10^{10.5}M_{\odot}$ thresholds in total stellar mass, and top and bottom panels showing results for disk- and bulge-dominated samples, respectively.
+Points with error bars show SDSS measurements, solid curves show the clustering ratios of model galaxies.
+Before unpacking the information contained in these clustering measurements, we stress that the good agreement shown between model and data in Figure~\ref{fig:clustering_ratio_upshot} is a genuine model prediction, since we only tuned parameters to fit the one-point measurements in Fig.~\ref{fig:scatter_plot}.
+
+The salient feature of the clustering ratio measurements is that they are negative: for either disk- or bulge-dominated samples, small galaxies cluster more strongly than large galaxies of the same stellar mass threshold, a new result.
+This feature also holds true for model galaxies, for which both $\rhalfbulge$ and $\rhalfdisk$ scale in power law proportion to $\rvir.$ Since halo mass $\mvir$ scales as $\rvir^{1/3},$ and clustering is a strong function of $\mvir,$ the result may seem surprising.
+
+The resolution to this puzzle is illustrated in Figure~\ref{fig:bt_censat}, which shows the PDF of $\bt$ for halos of the same mass $\mhalo,$ defined as $\mpeak,$ the peak mass ever attained through the history of the (sub)halo, so that host halos and subhalos can be treated on equal footing.
+In the model, central galaxies are diskier than satellites, a feature that is inherited from the method we use to map $\bt$ to model galaxies.
+
+In the {\tt UniverseMachine}, and in any quantitatively successful cosmological model of the galaxy formation, central galaxies are preferentially more star-forming relative to satellites of comparable stellar or halo mass.
+Since bluer galaxies are diskier than redder galaxies, our model centrals will be diskier than satellites.
+Our galaxy profile model has $\adisk=7\abulge,$ and so satellite galaxies will be smaller than centrals due to the $\bt-\ssfr$ correlation.
+These simultaneous features alone will naturally result in the negative sign of the clustering ratios seen in Figure~\ref{fig:clustering_ratio_upshot}.
+
+In light of this explanation, it is natural to ask whether this simple feature {\em alone} is all that is needed for any model of $\rhalf$ to achieve this level of success at predicting galaxy clustering on small and large scales.
+We address this question in \S~\ref{subsec:tests2} below, finding that the answer is no: the reasonably correct magnitude and scale-dependence of the clustering ratios predicted by our model is a highly non-trivial result that places tight constraints on the post-infall physics of satellite galaxies.
 

### 2017-08-31 paper/galsize_paper.tex
Corrected typo

@@
 The salient feature of the clustering ratio measurements is that they are negative: for either disk- or bulge-dominated samples, small galaxies cluster more strongly than large galaxies of the same stellar mass threshold, a new result.
-This feature also holds true for model galaxies, for which both $\rhalfbulge$ and $\rhalfdisk$ scale in power law proportion to $\rvir.$ Since halo mass $\mvir$ scales as $\rvir^{1/3},$ and clustering is a strong function of $\mvir,$ the result may seem surprising.
+This feature also holds true for model galaxies, for which both $\rhalfbulge$ and $\rhalfdisk$ scale in power law proportion to $\rvir.$ Since halo mass $\mvir\propto\rvir^{3},$ and clustering is a strong function of $\mvir,$ the result may seem surprising.
 
@@
 
-In the {\tt UniverseMachine}, and in any quantitatively successful cosmological model of the galaxy formation, central galaxies are preferentially more star-forming relative to satellites of comparable stellar or halo mass.
+In the {\tt UniverseMachine}, and in any quantitatively successful cosmological model of galaxy formation, central galaxies are preferentially more star-forming relative to satellites of comparable stellar or halo mass.
 Since bluer galaxies are diskier than redder galaxies, our model centrals will be diskier than satellites.

### 2017-09-02 paper/galsize_paper.tex
Finished draft of 4.2

@@
 \newcommand{\mpc}{{\rm Mpc}}
+\newcommand{\msun}{M_\odot}
 
@@
 
+%---------------------------------------------------------------------------------------------------
+\begin{figure}
+\centering
+\includegraphics[width=8cm]{FIGS/size_vs_stellar_mass_multipanel_bt_decomposition.pdf}
+\caption{
+{\bf One-point data used to fit the fiducial model.}
+Scattered points show the $\rhalf-\mstar$ relation for SDSS galaxies as measured in \citet{meert_etal15}.
+Bulge-dominated galaxies are defined in terms of the bulge-to-total stellar mass ratio $\bt>=0.75,$ disk-dominated galaxies $\bt<0.25,$ mixed morphology as $0.25 < \bt < 0.75.$ The black curve in each panel shows the $\rhalf-\mstar$ relation implied by our fiducial model, in which $\rhalf=A\rvir^\alpha,$ with $\adisk=0.014=7\abulge, \alphadisk=1, \alphabulge=5/4,$ and uncorrelated log-normal scatter of $0.2$ dex about these relations.
+}
+\label{fig:scatter_plot}
+\end{figure}
+%-----------------------------------------------------------------------------------------------------
+
 The results shown in \citet{kravtsov13} simplify our task of parameter space exploration: the assumption that composite galaxy size $\rhalf$ scales in linear proportion to halo radius $\rvir$ gives a qualitatively good description of SDSS data over many orders of magnitude in galaxy mass.
@@
 
+%---------------------------------------------------------------------------------------------------
+\begin{figure}
+\centering
+\includegraphics[width=8cm]{FIGS/size_clustering_ratios_bt_decomposition_model_vs_sdss.pdf}
+\caption{
+{\bf Two-point clustering predictions of the fiducial model.}
+Points with error bars show new SDSS measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj,$ compared to predictions by the model tuned to the measurements shown in Fig.~\ref{fig:scatter_plot}.
+We define a disk or bulge as ``large" or ``small" according to whether it is above or below the median size for its stellar mass.
+The y-axis shows clustering strength ratios, so that, for example, a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of comparable stellar mass.
+We show results separately for disk-dominated galaxies ({\em top} panels) and bulge-dominated galaxies ({\em bottom }panels), and different thresholds in total stellar mass in the {\em left} and {\em right} panels.
+The successful prediction shown here is remarkable because the model was not fit to these data, and because two-point clustering is highly sensitive to the physics that shapes satellite galaxy profiles (see Fig.~\ref{fig:satellites}).
+}
+\label{fig:clustering_ratio_upshot}
+\end{figure}
+%-----------------------------------------------------------------------------------------------------
+
 The y-axis of each panel in Figure \ref{fig:clustering_ratio_upshot} shows these $\rhalf$ clustering ratios, with left and right panels showing measurements for $\mstar>10^{10}M_{\odot}$ and $\mstar>10^{10.5}M_{\odot}$ thresholds in total stellar mass, and top and bottom panels showing results for disk- and bulge-dominated samples, respectively.
@@
 In the model, central galaxies are diskier than satellites, a feature that is inherited from the method we use to map $\bt$ to model galaxies.
-
-In the {\tt UniverseMachine}, and in any quantitatively successful cosmological model of galaxy formation, central galaxies are preferentially more star-forming relative to satellites of comparable stellar or halo mass.
-Since bluer galaxies are diskier than redder galaxies, our model centrals will be diskier than satellites.
-Our galaxy profile model has $\adisk=7\abulge,$ and so satellite galaxies will be smaller than centrals due to the $\bt-\ssfr$ correlation.
-These simultaneous features alone will naturally result in the negative sign of the clustering ratios seen in Figure~\ref{fig:clustering_ratio_upshot}.
-
-In light of this explanation, it is natural to ask whether this simple feature {\em alone} is all that is needed for any model of $\rhalf$ to achieve this level of success at predicting galaxy clustering on small and large scales.
-We address this question in \S~\ref{subsec:tests2} below, finding that the answer is no: the reasonably correct magnitude and scale-dependence of the clustering ratios predicted by our model is a highly non-trivial result that places tight constraints on the post-infall physics of satellite galaxies.
-
-\subsection{Sensitivity of Clustering to Satellite Profile Evolution}
-\label{subsec:tests2}
-
-\subsection{Insensitivity of Clustering and Lensing to Halo Spin Correlations}
-\label{subsec:tests3}
-
-%---------------------------------------------------------------------------------------------------
-\begin{figure}
-\centering
-\includegraphics[width=8cm]{FIGS/size_vs_stellar_mass_multipanel_bt_decomposition.pdf}
-\caption{
-{\bf One-point data used to fit the fiducial model.}
-Scattered points show the $\rhalf-\mstar$ relation for SDSS galaxies as measured in \citet{meert_etal15}.
-Bulge-dominated galaxies are defined in terms of the bulge-to-total stellar mass ratio $\bt>=0.75,$ disk-dominated galaxies $\bt<0.25,$ mixed morphology as $0.25 < \bt < 0.75.$ The black curve in each panel shows the $\rhalf-\mstar$ relation implied by our fiducial model, in which $\rhalf=A\rvir^\alpha,$ with $\adisk=0.014=7\abulge, \alphadisk=1, \alphabulge=5/4,$ and uncorrelated log-normal scatter of $0.2$ dex about these relations.
-}
-\label{fig:scatter_plot}
-\end{figure}
-%-----------------------------------------------------------------------------------------------------
-
-%---------------------------------------------------------------------------------------------------
-\begin{figure}
-\centering
-\includegraphics[width=8cm]{FIGS/size_clustering_ratios_bt_decomposition_model_vs_sdss.pdf}
-\caption{
-{\bf Two-point clustering data used to validate the fiducial model.}
-Points with error bars show new SDSS measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj,$ compared to predictions by the model tuned to the measurements shown in Fig.~\ref{fig:scatter_plot}.
-We define a disk or bulge as ``large" or ``small" according to whether it is above or below the median size for its stellar mass.
-The y-axis shows clustering strength ratios, so that, for example, a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of comparable stellar mass.
-We show results separately for disk-dominated galaxies ({\em top} panels) and bulge-dominated galaxies ({\em bottom }panels), and different thresholds in total stellar mass in the {\em left} and {\em right} panels.
-The successful prediction shown here is remarkable because the model was not fit to these data, and because two-point clustering is highly sensitive to the physics that shapes satellite galaxy profiles (see Fig.~\ref{fig:satellites}).
-}
-\label{fig:clustering_ratio_upshot}
-\end{figure}
-%-----------------------------------------------------------------------------------------------------
 
@@
 
+In the {\tt UniverseMachine}, and in any quantitatively successful cosmological model of galaxy formation, central galaxies are preferentially more star-forming relative to satellites of comparable stellar or halo mass.
+Since bluer galaxies are diskier than redder galaxies, our model centrals will be diskier than satellites.
+Our galaxy profile model has $\adisk=7\abulge,$ and so satellite galaxies will be smaller than centrals due to the $\bt-\ssfr$ correlation.
+These simultaneous features alone will naturally result in the negative sign of the clustering ratios seen in Figure~\ref{fig:clustering_ratio_upshot}.
+
+In light of this explanation, it is natural to ask whether this simple feature {\em alone} is all that is needed for any model of $\rhalf$ to achieve this level of success at predicting galaxy clustering on small and large scales.
+We address this question in \S~\ref{subsec:tests2} below, finding that the answer is no: the reasonably correct magnitude and scale-dependence of the clustering ratios predicted by our model is a non-trivial result that places tight constraints on the post-infall physics of satellite galaxies.
+
+\subsection{Sensitivity of Clustering to Satellite Profile Evolution}
+\label{subsec:tests2}
+
+In this section we explore how post-infall changes in satellite $\rhalf$ manifest in $\wproj(\rproj).$ To do so, we construct an extension our fiducial model with a simple additional ingredient for post-infall size evolution of satellites.
+
+In the fiducial model described in \S~\ref{sec:model}, recall that in the power law a scaling relations (Eq.~\ref{eq:fiducial_model}) the halo radius $\rvir$ used for satellite galaxies is taken to be the value at the time of infall.
+The simple interpretation of this assumption is that, in a statistical sense, the size of satellite galaxies is determined by its history as a central galaxy, and that post-infall physics leaves no distinct imprint on satellite $\rhalf.$
+
+Here we suppose that this assumption is violated, and that $\rhalf$ decreases after infall according to $(\mvir/\macc)^{1/3}.$ That is, in this alternative formulation, rather than using $\rvir$ at the time of infall for satellites in the power law scaling relations, we instead use $\rvir(\mvir/\macc)^{1/3}.$ This simple toy model attempts supposes that the same physical processes leading to halo mass loss are also responsible for a post-infall decrease in satellite size.
+
 %---------------------------------------------------------------------------------------------------
@@
 \caption{
-{\bf Clustering provides tight constraints on the relative sizes of centrals and satellites.} 
+{\bf Clustering tightly constrains satellite-specific size evolution.} 
 Here we compare our fiducial model, in which satellite galaxy size is set by $\rvir$ at the time of infall, to an alternative model analogous to \citet{watson_etal12} in which satellite sizes contract in proportion to $(\mvir/\macc)^{1/3}.$ The large differences between solid and dashed curves in the top panels show that the $\rhalf-$dependence of galaxy clustering ratios is highly sensitive to the post-infall evolution of satellite galaxy profiles.
@@
 %-----------------------------------------------------------------------------------------------------
+
+Figure~\ref{fig:satellites} compares the clustering ratios of our fiducial model (solid curves) to the clustering ratios of this alternative model (dashed curves).
+The difference between the small-scale clustering of the two models is stark: the assumption that $\rhalf$ decreases after infall leaves a strong imprint on the $\rhalf-$dependence of $\wproj(\rproj),$ such that small galaxies cluster {\em much} more strongly relative to large galaxies, particularly for disk-dominated systems with $\mstar\approx10^{10}\msun.$
+
+The large differences between the solid and dashed curves in Fig.~\ref{fig:satellites} establishes that the largely successful prediction for the clustering ratios fiducial model is a non-trivial: $\wproj(\rproj)$ is indeed providing good constraining power on the  assumptions underlying our profile modeling and not simply our morphology modeling, c.f., \S\ref{subsubsec:random_bt_model} and \S\ref{sec:model}.
+We refer the reader to \S\ref{subsec:satellite_discussion} for further discussion of the physical implications of this result.
+
+\subsection{Insensitivity of Clustering and Lensing to Halo Spin Correlations}
+\label{subsec:tests3}
 
@@
 
+\subsection{Physical Interpretation for Satellites}
+\label{subsec:satellite_discussion}
+
 \subsection{Progression from Backwards to Forwards Modeling}

### 2017-09-02 paper/galsize_paper.tex
Finished complete first draft of Results section

@@
 
+The results of the previous section \S\ref{subsec:tests2} illustrate the sensitive constraints that galaxy clustering measurements provide on modeling assumptions about satellite $\rhalf.$ In this section we explore the potential constraining power of clustering on models for the size of disks of central galaxies.
+In particular, we seek to assess whether clustering measurements can constrain the long-standing assumption that disk size scales in proportion to the spin of the parent halo, $\rhalfdisk\propto\halospin,$ \citep[e.g.,][]{mo_mao_white98}.
+
+We wish to build an alternative empirical model that inherits the quantitative success of our fiducial model, and further makes the extreme assumption that central galaxy $\rhalfdisk$ is maximally correlated with $\halospin$ at fixed $\mstar.$ Conditional Abundance Matching \citep[hereafter, CAM,][]{hearin_etal13b} is the natural framework to use to build such a model.
+
+Disk size in our fiducial model has log-normal scatter $\sigmarhalf=0.2$ dex about the mean value $\adisk\rvir^{\alphadisk}.$  We use the CAM implementation in {\tt Halotools}\footnote{See {\tt halotools.empirical\_models.conditional\_abunmatch} documentation for details.} to extend our fiducial model so that the scatter in central galaxy $\rhalfdisk$ is not stochastic, but is in stead in one-to-one correspondence with $\halospin$ at fixed total stellar mass $\mstar.$ This alternative model thus has exactly the same one-point functions as the fiducial model (i.e., the solid curves in Fig.~\ref{fig:scatter_plot} are formally preserved by construction).
+However, $\halospin$ exhibits a highly non-trivial connection to the cosmic density field, including $\mvir-$dependent correlations with large-scale density and topology, and so it is natural to ask how these correlations manifest in our $\rhalf$ clustering ratios.
+
 %---------------------------------------------------------------------------------------------------
@@
 
+The top panel of Figure \ref{fig:halospin_lensing} shows a comparison of the $\rhalf$ clustering ratios of our fiducial model to the alternative CAM model in which $\rhalfdisk\propto\halospin.$ Evidently, for galaxies in this stellar mass range, the strength of $\halospin$ correlations with the cosmic web are sufficiently weak as to produce almost no measurable impact on the $\rhalf-$dependence of the clustering of disk-dominated systems.
+
+Of course it is possible that galaxy clustering is poorly suited to detect $\rhalfdisk-\halospin$ correlations, which instead manifest in some alternative measurement of large-scale structure.
+For example, numerous studies of the $\halospin-$dependence of halo assembly bias have shown that low-spin halos are preferentially found in environments of below-average dark matter density relative to high-spin halos of comparable mass \citep[see, for example,][]{lee_etal17}.
+
+Motivated by these results, we show in the bottom panel of Fig.~\ref{fig:halospin_lensing} an idealized mock measurement of the lensing of central galaxies identified with perfect fidelity.
+Solid curves show $\Delta\Sigma$ signal of our fiducial model centrals, dashed curves the alternative CAM model.
+Again we see that $\rhalfdisk-\halospin$ correlations are simply not strong enough in $L_\ast$ galaxies to produce a compelling signal.
+These results imply that it will be extremely challenging to either confirm or refute the $\rhalfdisk\propto\halospin$ hypothesis using large-scale structure measurements.
+We discuss this further in \S\ref{subsec:mo_status}.
+
 \section{Discussion}
@@
 
-\subsection{Physical Interpretation for Satellites}
+\subsection{Implications for Satellites}
 \label{subsec:satellite_discussion}
+
+\subsection{State of the $\rhalfdisk\propto\halospin$ Hypothesis}
+\label{subsec:mo_status}
 
@@
 \label{subsec:previouswork}
+
+\subsection{Future Directions for Empirical Modeling of Morphology}
+\label{subsec:future}
 

### 2017-09-02 paper/galsize_paper.tex
Clarified notation on rhalf

@@
 \newcommand{\rhalf}{R_{1/2}}
+\newcommand{\rhalftot}{R^{\rm tot}_{1/2}}
 \newcommand{\rhalfdisk}{R_{1/2}^{\rm disk}}
@@
 \newcommand{\mstar}{M_{\ast}}
+\newcommand{\mstartot}{M^{\rm tot}_{\ast}}
 \newcommand{\ssfr}{{\rm sSFR}}
@@
 \newcommand{\msun}{M_\odot}
+\newcommand{\kms}{{\rm km/s}}
 
@@
 We derive empirical modeling constraints on the connection between dark matter halos and the half-mass radius $\rhalf$ of galaxy bulges and disks.
-We show that both $\rhalfdisk$ and $\rhalfbulge$ are well-described by power law scaling relations with halo virial radius, $\rhalf=A\rvir^{\alpha}.$ Novel to this work, we use new SDSS measurements of the $\rhalf-$dependence of galaxy clustering to constrain the model parameters, $A_{\rm bulge}, A_{\rm disk}, \alpha_{\rm bulge},\alpha_{\rm disk},$ and log-normal scatter $\sigmarhalf.$ Even when only coarsely tuning these parameters to the observed one-point functions $\langle\rhalfdisk|\mstar^{\rm disk}\rangle$ and $\langle\rhalfbulge|\mstar^{\rm bulge}\rangle,$ our model accurately predicts the observed two-point clustering on small- and large-scales.
+We show that both $\rhalfdisk$ and $\rhalfbulge$ are well-described by power law scaling relations with halo virial radius, $\rhalf=A\rvir^{\alpha}.$ Novel to this work, we use new SDSS measurements of the $\rhalftot-$dependence of galaxy clustering to constrain the model parameters, $A_{\rm bulge}, A_{\rm disk}, \alpha_{\rm bulge},\alpha_{\rm disk},$ and log-normal scatter $\sigmarhalf.$ Even when only coarsely tuning these parameters to the observed one-point functions $\langle\rhalfdisk\vert\mstartot\rangle$ and $\langle\rhalfbulge|\mstartot\rangle,$ our model accurately predicts the observed two-point clustering on small- and large-scales.
 This success non-trivial, as we show that galaxy clustering is highly sensitive to the physics that shapes satellite galaxy profiles.
@@
 In the version of this catalog that we use, two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile.
-We cross-match our DR10 sample against the \citet{meert_etal15} catalog values of $\rhalf,$ the half-light radius of the full profile, and $\bt,$ the $r-$band flux ratio of the de Vaucouleurs component to the total $r-$band flux.
-This cross-matching gives us a volume-limited galaxy sample with values of $\mstar,$ $\ssfr,$ $\rhalf,$ and $\bt.$ Together with the present work, we make publicly available this cross-matched catalog, as well as code to generate the catalog from the original data files and load it into a python interpreter.
+We cross-match our DR10 sample against the \citet{meert_etal15} catalog values of $\rhalftot,$ the half-light radius of the full (composite) profile, and $\bt,$ the $r-$band flux ratio of the de Vaucouleurs component to the total $r-$band flux.
+This cross-matching gives us a volume-limited galaxy sample with values of $\mstar,$ $\ssfr,$ $\rhalftot,$ and $\bt.$ Together with the present work, we make publicly available this cross-matched catalog, as well as code to generate the catalog from the original data files and load it into a python interpreter.
 
 We calculate two-point clustering $\wproj$ of our SDSS galaxy sample using line-of-sight projection of $\pi_{\rm max}=20\mpc$ using the {\tt correl} program in {\tt UniverseMachine}.
-Our results in \S~\ref{sec:results} will give special focus on the dependence of $\wproj$ upon composite galaxy size $\rhalf.$ We will quantify this dependence in terms of {\em clustering ratios} of ``large" vs.
-``small" galaxies, defined according to whether composite galaxy size is above or below $\langle\rhalf\vert\mstar\rangle,$ computed as the median of a sliding stellar mass window with a width of $N_{\rm gal}=1000.$
+Our results in \S~\ref{sec:results} will give special focus on the dependence of $\wproj$ upon $\rhalftot.$ We will quantify this dependence in terms of {\em clustering ratios} of ``large" vs.
+``small" galaxies, defined according to whether composite galaxy size is above or below $\langle\rhalftot\vert\mstartot\rangle,$ computed as the median of a sliding stellar mass window with a width of $N_{\rm gal}=1000.$
+
+In all sections that follow, we will declutter our notation by referring to $\rhalftot$ as $\rhalf$ and $\mstartot$ as $\mstar.$ In all cases where we wish to refer to the half-light radius or stellar mass of a particular component, that component will explicitly appear in superscript.
+All numerical values of $\rhalf$ will be quoted in $\kpc,$ and all values of $\mstar$ and $\mhalo$ in $\msun,$ assuming $H_0=67.8~\kms\equiv100h~\kms$ the best-fit value from \citet{planck15}.
+To scale stellar masses to ``$h=1$ units" \citep{croton13}, our numerically quoted values for $\mstar$ should be multiplied by a factor of $h^2,$ while our halo masses and distances should be multiplied by a factor of $h.$
 
@@
 \beq
-\rhalf = (\bt)\rhalfbulge + (1-\bt)\rhalfdisk.
+\rhalftot = (\bt)\rhalfbulge + (1-\bt)\rhalfdisk.
 \eeq
@@
 We reiterate an important distinction drawn in the formulation of our forward modeling approach.
-In the model described above, $\rhalfbulge$ and $\rhalfdisk$ are forward modeling quantities that we aim to constrain through SDSS observations of {\em composite} galaxy size $\rhalf.$ In particular, both model and real galaxies will be categorized as ``small" or ``large`` according to whether $\rhalf$ is above or below the median size for a galaxy with total stellar mass $\mstar.$
+In the model described above, $\rhalfbulge$ and $\rhalfdisk$ are forward modeling quantities that we aim to constrain through SDSS observations of {\em composite} galaxy size $\rhalftot.$ In particular, both model and real galaxies will be categorized as ``small" or ``large`` according to whether $\rhalftot$ is above or below the median size for a galaxy with total stellar mass $\mstartot.$
 
@@
 In Figure \ref{fig:scatter_plot} we show the scaling of composite galaxy size $\rhalf$ with $\mstar,$ with separate panels dedicated to subsamples of galaxies divided according to value of $\bt.$ We refer to galaxies with $\bt<0.25$ as ``disk-dominated", $\bt>=0.75$ as ``bulge-dominated", and $0.25<=\bt<0.75$ as ``mixed morphology".
+We remind the reader that $\rhalf$ and $\mstar$ refer to the scale radius and stellar mass of the {\em entire} galaxy, not of an individual component.
 
@@
 Scattered points show the $\rhalf-\mstar$ relation for SDSS galaxies as measured in \citet{meert_etal15}.
-Bulge-dominated galaxies are defined in terms of the bulge-to-total stellar mass ratio $\bt>=0.75,$ disk-dominated galaxies $\bt<0.25,$ mixed morphology as $0.25 < \bt < 0.75.$ The black curve in each panel shows the $\rhalf-\mstar$ relation implied by our fiducial model, in which $\rhalf=A\rvir^\alpha,$ with $\adisk=0.014=7\abulge, \alphadisk=1, \alphabulge=5/4,$ and uncorrelated log-normal scatter of $0.2$ dex about these relations.
+Bulge-dominated galaxies are defined in terms of the bulge-to-total stellar mass ratio $\bt>=0.75,$ disk-dominated galaxies $\bt<0.25,$ mixed morphology as $0.25 < \bt < 0.75.$ The black curve in each panel shows the $\rhalf-\mstar$ relation implied by our fiducial model, in which $\rhalfbulge=\abulge\rvir^{\alphabulge}$ and $\rhalfdisk=\adisk\rvir^{\alphadisk},$ with $\adisk=0.014=7\abulge, \alphadisk=1, \alphabulge=5/4,$ and uncorrelated log-normal scatter of $0.2$ dex about these relations.
 }
@@
 
-Comparison of the top panels of Fig.~\ref{fig:scatter_plot} show that this linearization is only approximate; evidently, the composite size $\rhalf$ of bulge-dominated galaxies has a steeper scaling relation with $\mstar$ relative to disk-dominated galaxies.
-This difference motivates our simple extension of the \citet{kravtsov13} model, in which composite size $\rhalf$ of disk- and bulge-dominated galaxies scale according to separate power laws.
+Comparison of the top panels of Fig.~\ref{fig:scatter_plot} show that this linearization is only approximate; evidently, galaxy size $\rhalf$ of bulge-dominated systems has a steeper scaling relation with $\mstar$ relative to disk-dominated systems.
+This difference motivates our simple extension of the \citet{kravtsov13} model, in which $\rhalf$ of disk- and bulge-dominated galaxies scales according to separate power laws.
 
@@
 Separately for each $\bt-$selected subsample, we calculate $\langle\rhalf\vert\mstar;\bt\rangle,$ the median composite size of the sample as a function of total galaxy stellar mass.
-We split each $\bt-$selected sample in half according to whether the galaxy has a composite size $\rhalf$ that is above or below this median value.
+We split each $\bt-$selected sample in half according to whether the galaxy has a size $\rhalf$ that is above or below this median value.
 For any $\mstar-$complete threshold, this gives four subsamples of large and small, disk- and bulge-dominated galaxies.
@@
 Thus our baseline model ansatz is that the morphology-density relation is purely derived from the color-density relation.
-Since composite size $\rhalf$ in the model is given by $\rhalf=(\bt)\rhalfbulge + (1-\bt)\rhalfdisk,$ this ansatz in turn implies that smaller galaxies cluster more strongly relative to larger galaxies of the same stellar mass, as seen in the measurements shown in Fig.~\ref{fig:clustering_ratio_upshot}.
+Since composite size $\rhalf$ in the model is given by $\rhalf\equiv\rhalftot=(\bt)\rhalfbulge + (1-\bt)\rhalfdisk,$ this ansatz in turn implies that smaller galaxies cluster more strongly relative to larger galaxies of the same stellar mass, as seen in the measurements shown in Fig.~\ref{fig:clustering_ratio_upshot}.
 }

### 2017-09-02 paper/galsize_paper.tex
Minor changes and typo corrections

@@
 We derive empirical modeling constraints on the connection between dark matter halos and the half-mass radius $\rhalf$ of galaxy bulges and disks.
-We show that both $\rhalfdisk$ and $\rhalfbulge$ are well-described by power law scaling relations with halo virial radius, $\rhalf=A\rvir^{\alpha}.$ Novel to this work, we use new SDSS measurements of the $\rhalftot-$dependence of galaxy clustering to constrain the model parameters, $A_{\rm bulge}, A_{\rm disk}, \alpha_{\rm bulge},\alpha_{\rm disk},$ and log-normal scatter $\sigmarhalf.$ Even when only coarsely tuning these parameters to the observed one-point functions $\langle\rhalfdisk\vert\mstartot\rangle$ and $\langle\rhalfbulge|\mstartot\rangle,$ our model accurately predicts the observed two-point clustering on small- and large-scales.
+We show that both $\rhalfdisk$ and $\rhalfbulge$ are well-described by power law scaling relations with halo virial radius, $\rhalf=A\rvir^{\alpha}.$ Novel to this work, we use new SDSS measurements of the $\rhalf-$dependence of galaxy clustering to constrain the model parameters, $A_{\rm bulge}, A_{\rm disk}, \alpha_{\rm bulge},\alpha_{\rm disk},$ and log-normal scatter $\sigmarhalf.$ Even when only coarsely tuning these parameters to the observed one-point functions $\langle\rhalfdisk\vert\mstartot\rangle$ and $\langle\rhalfbulge|\mstartot\rangle,$ our model accurately predicts the observed two-point clustering on small- and large-scales.
 This success non-trivial, as we show that galaxy clustering is highly sensitive to the physics that shapes satellite galaxy profiles.
@@
 In all sections that follow, we will declutter our notation by referring to $\rhalftot$ as $\rhalf$ and $\mstartot$ as $\mstar.$ In all cases where we wish to refer to the half-light radius or stellar mass of a particular component, that component will explicitly appear in superscript.
-All numerical values of $\rhalf$ will be quoted in $\kpc,$ and all values of $\mstar$ and $\mhalo$ in $\msun,$ assuming $H_0=67.8~\kms\equiv100h~\kms$ the best-fit value from \citet{planck15}.
+All numerical values of $\rhalf$ will be quoted in $\kpc,$ and all values of $\mstar$ and $\mhalo$ in $\msun,$ assuming $H_0=67.8~\kms\equiv100h~\kms,$ the best-fit value from \citet{planck15}.
 To scale stellar masses to ``$h=1$ units" \citep{croton13}, our numerically quoted values for $\mstar$ should be multiplied by a factor of $h^2,$ while our halo masses and distances should be multiplied by a factor of $h.$
@@
 This model maps stellar mass and star-formation rate to every halo and subhalo at each snapshot in the Bolshoi-Planck simulation.
-The stellar mass function, quenched fraction, SFR density, and SFR-dependent clustering are all accurately captured by this model from $z=0-10.$ The model we have developed in the present work does not depend in an essential way upon the {\tt UniverseMachine} model in particular, we only require some reasonably accurate starting point for the $\mstar$ and $\ssfr$ values mapped to simulated halos.
+The stellar mass function, quenched fraction, SFR density, and SFR-dependent clustering are all accurately captured by this model from $z=0-10.$ The model we have developed in the present work does not depend in an essential way upon the {\tt UniverseMachine} model in particular; we only require some reasonably accurate starting point for the $\mstar$ and $\ssfr$ values mapped to simulated halos.
 
@@
 We compute $\wproj$ using the {\tt mock\_observables.wp} function in {\tt Halotools}, which is a python implementation of the algorithm in the {\tt Corrfunc} C library \citep{sinha_etal17}.
+We compute lensing $\Delta\Sigma$ using the {\tt mock\_observables.delta\_sigma} function in {\tt Halotools} to calculate the two-dimensional surface mass density of a random downsampling of $10^6$ dark matter particles in the snapshot.
 

### 2017-09-13 galsize_models/models/load_baseline_catalogs.py
Porting over notebook into a new baseline Moster13 mock

@@ -1,11 +1,14 @@
 """
 """
 import numpy as np
+from scipy.stats import norm
 from halotools.empirical_models import Moster13SmHm
 from halotools.sim_manager import CachedHaloCatalog
 from umachine_pyio.load_mock import load_mock_from_binaries, value_added_mock
 from halotools.empirical_models import halo_mass_to_halo_radius
 from astropy.cosmology import Planck15
+from astropy.utils.misc import NumpyRNGContext
+from astropy.table import Table
 
 from .new_haloprops import halo_radius_at_mpeak
 from .random_bt_assignment import value_add_random_bt
@@ -13,7 +16,7 @@ from .random_bt_assignment import value_add_random_bt
 from ..measurements import load_umachine_sdss_with_meert15
 
 
-__all__ = ('load_moster13_mock', 'load_umachine_mock')
+__all__ = ('moster13_based_mock', 'load_umachine_mock', 'load_baseline_halocat')
 
 default_umachine_galprops = list((
     'sm', 'sfr', 'obs_sm', 'obs_sfr', 'icl', 'halo_id', 'upid',
@@ -21,25 +24,53 @@ default_umachine_galprops = list((
     'a_first_infall', 'dvmax_zscore', 'vmax_at_mpeak'))
 
 
-def load_moster13_mock(logmstar_cut=9.75, simname='bolplanck', redshift=0.):
-    """
-    Examples
-    --------
-    >>> mock = load_moster13_mock(logmstar_cut=10)
-    """
+moster13_halocat_keys = ('halo_upid', 'halo_mpeak', 'halo_scale_factor_mpeak',
+        'halo_x', 'halo_y', 'halo_z', 'halo_zpeak',
+        'halo_vx', 'halo_vy', 'halo_vz',
+        'halo_mvir_host_halo', 'halo_spin', 'halo_uran')
 
+
+def load_baseline_halocat(simname='bolplanck', redshift=0, fixed_seed=411):
     halocat = CachedHaloCatalog(simname=simname, redshift=redshift)
-    mpeak = halocat.halo_table['halo_mpeak']
-    redshift = 1./halocat.halo_table['halo_scale_factor_mpeak'] - 1.
 
-    mstar_model = Moster13SmHm()
-    halocat.halo_table['mstar'] = mstar_model.mc_stellar_mass(
-            prim_haloprop=mpeak, redshift=redshift)
[…]

### 2017-09-13 galsize_models/models/bulge_disk_double_power_law.py
Updated notebook with convenience functions for loading moster mock

@@ -2,6 +2,7 @@
 """
 import numpy as np
 from astropy.utils.misc import NumpyRNGContext
+from scipy.stats import norm
 
 from ..measurements.measure_one_points import mock_ssfr_sequence_one_points
 from ..measurements.sdss_covariance import assemble_data_vector
@@ -23,12 +24,18 @@ fiducial_norm_disk = fiducial_norm_bulge/fiducial_bulge_to_disk_size_ratio
 __all__ = ('component_size_vs_rhalo', 'galaxy_size_vs_rhalo')
 
 
-def component_size_vs_rhalo(rvir_halo_kpc, normalization, alpha, R0=1., scatter=0., seed=None):
+def component_size_vs_rhalo(rvir_halo_kpc, normalization, alpha,
+        R0=1., scatter=0., seed=None, uran=None):
     """
     """
     mean_size = normalization*(rvir_halo_kpc/R0)**alpha
-    with NumpyRNGContext(seed):
-        result = 10**np.random.normal(loc=np.log10(mean_size), scale=scatter)
+    log_mean_size = np.log10(mean_size)
+
+    if uran is None:
+        with NumpyRNGContext(seed):
+            uran = np.random.rand(len(mean_size))
+    result = 10**norm.isf(1 - uran, loc=log_mean_size, scale=scatter)
+
     return result
 
 

### 2017-09-13 galsize_models/models/load_baseline_catalogs.py

@@ -9,8 +9,8 @@ from halotools.empirical_models import halo_mass_to_halo_radius
 from astropy.cosmology import Planck15
 from astropy.utils.misc import NumpyRNGContext
 from astropy.table import Table
+from halotools.empirical_models import solve_for_polynomial_coefficients
 
-from .new_haloprops import halo_radius_at_mpeak
 from .random_bt_assignment import value_add_random_bt
 
 from ..measurements import load_umachine_sdss_with_meert15
@@ -26,7 +26,7 @@ default_umachine_galprops = list((
 
 moster13_halocat_keys = ('halo_upid', 'halo_mpeak', 'halo_scale_factor_mpeak',
         'halo_x', 'halo_y', 'halo_z', 'halo_zpeak',
-        'halo_vx', 'halo_vy', 'halo_vz',
+        'halo_vx', 'halo_vy', 'halo_vz', 'halo_rvir_zpeak',
         'halo_mvir_host_halo', 'halo_spin', 'halo_uran')
 
 
@@ -63,7 +63,15 @@ def moster13_based_mock(halocat=None, keys_to_keep=moster13_halocat_keys, **most
 
     mean_mstar = mean_mstar_unity_h/halocat.cosmology.h/halocat.cosmology.h
     mean_logmstar = np.log10(mean_mstar)
-    mc_mstar = 10**norm.isf(1-halocat.halo_table['halo_uran'], loc=mean_logmstar,
+
+    #  Apply M* correction to account for Meert+15 photometry differences
+    abscissa = 9, 10.5, 11.75
+    ordinates = 0.35, 0.2, 0.45
+    a0, a1, a2 = solve_for_polynomial_coefficients(abscissa, ordinates)
+    logmstar_correction = a0 + a1*mean_logmstar + a2*mean_logmstar**2
+    corrected_mean_logmstar = mean_logmstar + logmstar_correction
+
+    mc_mstar = 10**norm.isf(1-halocat.halo_table['halo_uran'], loc=corrected_mean_logmstar,
             scale=model.param_dict[u'scatter_model_param1'])
 
     mock = Table()
@@ -71,6 +79,7 @@ def moster13_based_mock(halocat=None, keys_to_keep=moster13_halocat_keys, **most
     for key in keys_to_keep:
         mock[key[5:]] = halocat.halo_table[key][mstar_mask]
 
+    mock['mstar'] = mc_mstar[mstar_mask]
     return mock
 
 

### 2017-09-13 galsize_models/models/load_baseline_catalogs.py
Corrected bug in application of M* correction

@@ -48,7 +48,8 @@ def load_baseline_halocat(simname='bolplanck', redshift=0, fixed_seed=411):
     return halocat
 
 
-def moster13_based_mock(halocat=None, keys_to_keep=moster13_halocat_keys, **moster13_params):
+def moster13_based_mock(halocat=None, keys_to_keep=moster13_halocat_keys,
+            scatter_ordinates=(0.35, 0.2, 0.45), **moster13_params):
     """
     """
     if halocat is None:
@@ -64,22 +65,24 @@ def moster13_based_mock(halocat=None, keys_to_keep=moster13_halocat_keys, **most
     mean_mstar = mean_mstar_unity_h/halocat.cosmology.h/halocat.cosmology.h
     mean_logmstar = np.log10(mean_mstar)
 
-    #  Apply M* correction to account for Meert+15 photometry differences
-    abscissa = 9, 10.5, 11.75
-    ordinates = 0.35, 0.2, 0.45
-    a0, a1, a2 = solve_for_polynomial_coefficients(abscissa, ordinates)
-    logmstar_correction = a0 + a1*mean_logmstar + a2*mean_logmstar**2
-    corrected_mean_logmstar = mean_logmstar + logmstar_correction
-
-    mc_mstar = 10**norm.isf(1-halocat.halo_table['halo_uran'], loc=corrected_mean_logmstar,
+    mc_logmstar = norm.isf(1-halocat.halo_table['halo_uran'], loc=mean_logmstar,
             scale=model.param_dict[u'scatter_model_param1'])
 
+    #  Apply M* correction to account for Meert+15 photometry differences
+    scatter_abscissa = 9.5, 10.5, 11.75
+    a0, a1, a2 = solve_for_polynomial_coefficients(scatter_abscissa, scatter_ordinates)
+    logmstar_correction = a0 + a1*mc_logmstar + a2*mc_logmstar**2
+    logmstar_correction = np.where(mc_logmstar < scatter_abscissa[0], scatter_ordinates[0], logmstar_correction)
+    logmstar_correction = np.where(mc_logmstar > scatter_abscissa[2], scatter_ordinates[2], logmstar_correction)
+    corrected_mc_logmstar = mc_logmstar + logmstar_correction
+
     mock = Table()
-    mstar_mask = mc_mstar > 10**9
+    mstar_mask = corrected_mc_logmstar > 9
     for key in keys_to_keep:
[…]

### 2017-09-13 galsize_models/models/load_baseline_catalogs.py
Updated default settings

@@ -49,7 +49,7 @@ def load_baseline_halocat(simname='bolplanck', redshift=0, fixed_seed=411):
 
 
 def moster13_based_mock(halocat=None, keys_to_keep=moster13_halocat_keys,
-            scatter_ordinates=(0.35, 0.2, 0.45), **moster13_params):
+            scatter_ordinates=(0.4, 0.3, 0.5), **moster13_params):
     """
     """
     if halocat is None:

### 2017-09-14 galsize_models/models/load_baseline_catalogs.py
updated vmax_percentile feature

@@ -25,8 +25,8 @@ default_umachine_galprops = list((
 
 
 moster13_halocat_keys = ('halo_upid', 'halo_mpeak', 'halo_scale_factor_mpeak',
-        'halo_x', 'halo_y', 'halo_z', 'halo_zpeak',
-        'halo_vx', 'halo_vy', 'halo_vz', 'halo_rvir_zpeak',
+        'halo_x', 'halo_y', 'halo_z', 'halo_zpeak', 'halo_vmax_mpeak',
+        'halo_vx', 'halo_vy', 'halo_vz', 'halo_rvir_zpeak', 'halo_vmax_at_mpeak_percentile',
         'halo_mvir_host_halo', 'halo_spin', 'halo_uran')
 
 
@@ -45,6 +45,11 @@ def load_baseline_halocat(simname='bolplanck', redshift=0, fixed_seed=411):
     with NumpyRNGContext(fixed_seed):
         halocat.halo_table['halo_uran'] = np.random.rand(nhalos)
 
+    mask = halocat.halo_table['halo_mvir_host_halo'] == 0
+    halocat.halo_table['halo_mvir_host_halo'][mask] = halocat.halo_table['halo_mpeak'][mask]
+
+    vmax_percentile_fname = '/Users/aphearin/work/UniverseMachine/temp_galsize_models/vmax_percentile.npy'
+    halocat.halo_table['halo_vmax_at_mpeak_percentile'] = np.load(vmax_percentile_fname)
     return halocat
 
 

### 2017-09-14 galsize_models/models/load_baseline_catalogs.py
Investigating high mass end and its relation to sign flip of assembly bias

@@ -26,6 +26,7 @@ default_umachine_galprops = list((
 
 moster13_halocat_keys = ('halo_upid', 'halo_mpeak', 'halo_scale_factor_mpeak',
         'halo_x', 'halo_y', 'halo_z', 'halo_zpeak', 'halo_vmax_mpeak',
+        'halo_scale_factor_firstacc', 'halo_mvir_firstacc',
         'halo_vx', 'halo_vy', 'halo_vz', 'halo_rvir_zpeak', 'halo_vmax_at_mpeak_percentile',
         'halo_mvir_host_halo', 'halo_spin', 'halo_uran')
 

### 2017-09-14 galsize_models/models/load_baseline_catalogs.py
added half-mass scale factor

@@ -26,7 +26,7 @@ default_umachine_galprops = list((
 
 moster13_halocat_keys = ('halo_upid', 'halo_mpeak', 'halo_scale_factor_mpeak',
         'halo_x', 'halo_y', 'halo_z', 'halo_zpeak', 'halo_vmax_mpeak',
-        'halo_scale_factor_firstacc', 'halo_mvir_firstacc',
+        'halo_scale_factor_firstacc', 'halo_mvir_firstacc', 'halo_halfmass_scale_factor',
         'halo_vx', 'halo_vy', 'halo_vz', 'halo_rvir_zpeak', 'halo_vmax_at_mpeak_percentile',
         'halo_mvir_host_halo', 'halo_spin', 'halo_uran')
 

### 2017-09-14 galsize_models/measurements/__init__.py
Added new convenience fucntion single_component_ratios

@@ -4,4 +4,4 @@ from .read_meert15 import load_meert15
 from .load_cross_matched_umachine import *
 from .measure_one_points import *
 from .rhalf_rvir_power_law_fit import rvir_rhalf_power_law_fit
-from .wp_ratio_mock import wp_size_ratios_mock
+from .wp_ratio_mock import *

### 2017-09-14 galsize_models/measurements/wp_ratio_mock.py

@@ -4,7 +4,7 @@ import numpy as np
 from halotools.mock_observables import return_xyz_formatted_array, wp
 
 
-__all__ = ('wp_size_ratios_mock', )
+__all__ = ('wp_size_ratios_mock', 'single_component_ratios')
 
 
 def wp_size_ratios_mock(mock, logsm_min, sample_cut, size_key='r50_magr_kpc_meert15',
@@ -47,3 +47,36 @@ def wp_size_ratios_mock(mock, logsm_min, sample_cut, size_key='r50_magr_kpc_meer
     wp_sm_large = wp(pos_sm_sf_large, rp_bins, pi_max, period=period)
 
     return rp_mids, wp_sm, wp_sm_small, wp_sm_large
+
+
+def single_component_ratios(mock, rp_bins=np.logspace(-1, 1.25, 20),
+            pi_max=20., period=250., size_key='r50', num_gals_max=int(1e5)):
+    """
+    """
+    result_collector = []
+    rp_mids = 10**(0.5*(np.log10(rp_bins[:-1]) + np.log10(rp_bins[1:])))
+    result_collector.append(rp_mids)
+
+    for logsm_cut in (9.75, 10.25, 10.75, 11.25):
+        sample = mock[mock['mstar'] > 10**logsm_cut]
+        if len(sample) > num_gals_max:
+            downsampling_mask = np.random.choice(np.arange(len(sample)), num_gals_max, replace=False)
+            sample = sample[downsampling_mask]
+
+        pos_all = return_xyz_formatted_array(sample['x'], sample['y'], sample['z'],
+                        velocity=sample['vz'], velocity_distortion_dimension='z', period=period)
+
+        pos_small = return_xyz_formatted_array(sample['x'], sample['y'], sample['z'],
+                        velocity=sample['vz'], velocity_distortion_dimension='z', period=period,
+                        mask=(sample[size_key] < sample[size_key+'_median']))
+        pos_large = return_xyz_formatted_array(sample['x'], sample['y'], sample['z'],
+                        velocity=sample['vz'], velocity_distortion_dimension='z', period=period,
+                        mask=(sample[size_key] >= sample[size_key+'_median']))
+
+        wp_all = wp(pos_all, rp_bins, pi_max, period=period)
+        wp_small = wp(pos_small, rp_bins, pi_max, period=period)
+        wp_large = wp(pos_large, rp_bins, pi_max, period=period)
[…]

### 2017-09-15 galsize_models/models/load_baseline_catalogs.py
Added stripping result

@@ -25,7 +25,7 @@ default_umachine_galprops = list((
 
 
 moster13_halocat_keys = ('halo_upid', 'halo_mpeak', 'halo_scale_factor_mpeak',
-        'halo_x', 'halo_y', 'halo_z', 'halo_zpeak', 'halo_vmax_mpeak',
+        'halo_x', 'halo_y', 'halo_z', 'halo_zpeak', 'halo_vmax_mpeak', 'halo_mvir',
         'halo_scale_factor_firstacc', 'halo_mvir_firstacc', 'halo_halfmass_scale_factor',
         'halo_vx', 'halo_vy', 'halo_vz', 'halo_rvir_zpeak', 'halo_vmax_at_mpeak_percentile',
         'halo_mvir_host_halo', 'halo_spin', 'halo_uran')

### 2017-09-15 paper/ms.sh
Added latex compile script

@@ -1,8 +1,0 @@
-set local=./
-
-latex sham_colors.tex
-bibtex sham_colors
-latex sham_colors.tex
-latex sham_colors.tex
-dvips sham_colors.dvi -Ppdf -G0 -z -t a4
-ps2pdf sham_colors.ps

### 2017-09-15 paper/run.sh

@@ -1,0 +1,11 @@
+pdflatex galsize_paper.tex
+rm galsize_paper.aux
+rm galsize_paper.log
+rm galsize_paper.bbl
+rm galsize_paper.blg
+pdflatex galsize_paper.tex
+bibtex galsize_paper.aux
+bibtex galsize_paper.aux
+pdflatex galsize_paper.tex
+pdflatex galsize_paper.tex
+open galsize_paper.pdf

### 2017-09-15 paper/galsize_paper.tex
Revised abstract

@@
 
-\title[The Galaxy Size--Halo Connection]
-{Galaxy Clustering Constraints on the Galaxy Size--Halo Connection}
+\title[The Emergent Simplicity of Galaxy Size]
+{The Emergent Simplicity of Galaxy Size}
 
@@
 \begin{abstract}
-We derive empirical modeling constraints on the connection between dark matter halos and the half-mass radius $\rhalf$ of galaxy bulges and disks.
-We show that both $\rhalfdisk$ and $\rhalfbulge$ are well-described by power law scaling relations with halo virial radius, $\rhalf=A\rvir^{\alpha}.$ Novel to this work, we use new SDSS measurements of the $\rhalf-$dependence of galaxy clustering to constrain the model parameters, $A_{\rm bulge}, A_{\rm disk}, \alpha_{\rm bulge},\alpha_{\rm disk},$ and log-normal scatter $\sigmarhalf.$ Even when only coarsely tuning these parameters to the observed one-point functions $\langle\rhalfdisk\vert\mstartot\rangle$ and $\langle\rhalfbulge|\mstartot\rangle,$ our model accurately predicts the observed two-point clustering on small- and large-scales.
-This success non-trivial, as we show that galaxy clustering is highly sensitive to the physics that shapes satellite galaxy profiles.
-We find no evidence for the commonly assumed relation between halo spin $\halospin$ and $\rhalfdisk,$ and show that this assumption cannot be meaningfully constrained with either the clustering or lensing of  $L_{\ast}$ galaxies.
-Our results provide simple boundary conditions for more complex and fine-grained models of galaxy size.
-We make our python code publicly available to support cosmological surveys that require realistic synthetic galaxy populations.
+We derive empirical modeling constraints on the connection between dark matter halos and the half-light radius $\rhalf$ of galaxies.
+Using forward-modeling techniques based on {\tt Halotools}, we confirm previous results in Kravtsov (2013) that $\rhalf$ is well-described by a linear scaling relation with halo virial radius.
+Novel to this work, we use new SDSS measurements of the $\rhalf-$dependence of galaxy clustering to test this modeling assumption.
+With no changes to the parameters, the model accurately predicts the observed two-point clustering on small- and large-scales over a wide range of stellar mass.
+This quantitative success is remarkable since the Kravtsov (2013) parameters were fit to the observed $\langle\rhalf\vert\mstar\rangle,$ and the $\rhalf-$dependence of SDSS galaxy clustering has heretofore never been measured.
+Moreover, this success is non-trivial, as we demonstrate that galaxy clustering is highly sensitive to the assembly history-dependent physics that shapes the relative size of centrals and satellites.
+Our results can be treated as a boundary condition for more complex and fine-grained models of galaxy size, and provide a simple means for cosmological surveys to generate synthetic galaxy populations with realistic sizes across the cosmic web.
 \end{abstract}

### 2017-09-15 paper/galsize_paper.tex
Finished (very) rough overhaul of galaxy sample section

@@
 \newcommand{\rhalf}{R_{1/2}}
-\newcommand{\rhalftot}{R^{\rm tot}_{1/2}}
 \newcommand{\rhalfdisk}{R_{1/2}^{\rm disk}}
@@
 \newcommand{\mstar}{M_{\ast}}
-\newcommand{\mstartot}{M^{\rm tot}_{\ast}}
 \newcommand{\ssfr}{{\rm sSFR}}
@@
 
-Our galaxy sample comes from Data Release 10 of the Sloan Digital Sky Survey \citep[SDSS][]{ahn_etal14}.
-We study the same $\mstar-$complete galaxy sample used in \citet{behroozi_etal15}, to which we refer the reader for details.
-Values for $\mstar$ and $\sfr$ are taken from the MPA-JHU value-added catalog \citep{kauffmann_etal03,brinchmann_etal04}.
-
-We additionally use the catalog of SDSS galaxy profile decompositions provided by \citet{meert_etal15}.
-In the version of this catalog that we use, two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile.
-We cross-match our DR10 sample against the \citet{meert_etal15} catalog values of $\rhalftot,$ the half-light radius of the full (composite) profile, and $\bt,$ the $r-$band flux ratio of the de Vaucouleurs component to the total $r-$band flux.
-This cross-matching gives us a volume-limited galaxy sample with values of $\mstar,$ $\ssfr,$ $\rhalftot,$ and $\bt.$ Together with the present work, we make publicly available this cross-matched catalog, as well as code to generate the catalog from the original data files and load it into a python interpreter.
+Our galaxy sample comes from the catalog of SDSS galaxy profile decompositions provided by \citet{meert_etal15}.
+This catalog is based on Data Release 10 of the Sloan Digital Sky Survey \citep[SDSS,][]{ahn_etal14}, with improvements to the photometry pipeline and light profile fitting methods \citep{vikram_etal10,bernardi_etal13,bernardi_etal14,meert_etal13}.
+In the version of this catalog that we use, two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile to determine the half-light radius $\rhalf.$ We apply the \citet{bell_etal03} mass-to-light ratio to the $r-$band flux and $g-r$ colors in this catalog to obtain an estimate for the total stellar mass $\mstar$ of every galaxy.
 
 We calculate two-point clustering $\wproj$ of our SDSS galaxy sample using line-of-sight projection of $\pi_{\rm max}=20\mpc$ using the {\tt correl} program in {\tt UniverseMachine}.
-Our results in \S~\ref{sec:results} will give special focus on the dependence of $\wproj$ upon $\rhalftot.$ We will quantify this dependence in terms of {\em clustering ratios} of ``large" vs.
-``small" galaxies, defined according to whether composite galaxy size is above or below $\langle\rhalftot\vert\mstartot\rangle,$ computed as the median of a sliding stellar mass window with a width of $N_{\rm gal}=1000.$
+Our results in \S~\ref{sec:results} will give special focus on the dependence of $\wproj$ upon $\rhalf.$ We will quantify this dependence in terms of {\em clustering ratios} of ``large" vs.
+``small" galaxies, defined according to whether composite galaxy size is above or below $\langle\rhalf\vert\mstar\rangle,$ computed as the median of a sliding stellar mass window with a width of $N_{\rm gal}=1000.$
 
-In all sections that follow, we will declutter our notation by referring to $\rhalftot$ as $\rhalf$ and $\mstartot$ as $\mstar.$ In all cases where we wish to refer to the half-light radius or stellar mass of a particular component, that component will explicitly appear in superscript.
 All numerical values of $\rhalf$ will be quoted in $\kpc,$ and all values of $\mstar$ and $\mhalo$ in $\msun,$ assuming $H_0=67.8~\kms\equiv100h~\kms,$ the best-fit value from \citet{planck15}.
@@
 \beq
-\rhalftot = (\bt)\rhalfbulge + (1-\bt)\rhalfdisk.
+\rhalf = (\bt)\rhalfbulge + (1-\bt)\rhalfdisk.
 \eeq
@@
 We reiterate an important distinction drawn in the formulation of our forward modeling approach.
-In the model described above, $\rhalfbulge$ and $\rhalfdisk$ are forward modeling quantities that we aim to constrain through SDSS observations of {\em composite} galaxy size $\rhalftot.$ In particular, both model and real galaxies will be categorized as ``small" or ``large`` according to whether $\rhalftot$ is above or below the median size for a galaxy with total stellar mass $\mstartot.$
+In the model described above, $\rhalfbulge$ and $\rhalfdisk$ are forward modeling quantities that we aim to constrain through SDSS observations of {\em composite} galaxy size $\rhalf.$ In particular, both model and real galaxies will be categorized as ``small" or ``large`` according to whether $\rhalf$ is above or below the median size for a galaxy with total stellar mass $\mstar.$
 
@@
 Thus our baseline model ansatz is that the morphology-density relation is purely derived from the color-density relation.
-Since composite size $\rhalf$ in the model is given by $\rhalf\equiv\rhalftot=(\bt)\rhalfbulge + (1-\bt)\rhalfdisk,$ this ansatz in turn implies that smaller galaxies cluster more strongly relative to larger galaxies of the same stellar mass, as seen in the measurements shown in Fig.~\ref{fig:clustering_ratio_upshot}.
+Since composite size $\rhalf$ in the model is given by $\rhalf\equiv\rhalf=(\bt)\rhalfbulge + (1-\bt)\rhalfdisk,$ this ansatz in turn implies that smaller galaxies cluster more strongly relative to larger galaxies of the same stellar mass, as seen in the measurements shown in Fig.~\ref{fig:clustering_ratio_upshot}.
 }

### 2017-09-15 paper/galsize_paper.tex
Updated simulation information

@@
 
-\subsection{Galaxy Sample and Measurements}
-\label{subsec:galaxydata}
-
 Our galaxy sample comes from the catalog of SDSS galaxy profile decompositions provided by \citet{meert_etal15}.
@@
 
+As the bedrock of our modeling, we use the catalog of {\tt Rockstar} subhalos identified at $z=0$ in the Bolshoi-Planck simulation \citep{klypin_etal11,behroozi12_rockstar,behroozi12_consistent_trees,riebe_etal13,rodriguez_puebla16_bolplanck}.
+the particular version of the catalog we use is made publicly available through {\tt Halotools} \citep{hearin_etal16}, with {\tt version\_name} = `halotools\_v0p4'.
+For mock galaxies, to compute galaxy clustering we employ the distant observer approximation by treating the simulation $z-$axis as the line-of-sight.
+We compute $\wproj$ using the {\tt mock\_observables.wp} function in {\tt Halotools}, which is a python implementation of the algorithm in the {\tt Corrfunc} C library \citep{sinha_etal17}.
+
 All numerical values of $\rhalf$ will be quoted in $\kpc,$ and all values of $\mstar$ and $\mhalo$ in $\msun,$ assuming $H_0=67.8~\kms\equiv100h~\kms,$ the best-fit value from \citet{planck15}.
@@
 
-\subsection{Simulation and Halos}
-\label{subsec:sim}
-
-{\tt Rockstar} subhalos identified at $z=0$ in the Bolshoi-Planck simulation are the basis of all our modeling.
-
-\subsection{Baseline Model and Mock Measurements}
-\label{subsec:baselinemock}
-
-\subsubsection{Mapping $\mstar$ \& $\sfr$ to halos}
-\label{subsubsec:umachine}
-
-The starting point of our model is the best-fit {\tt UniverseMachine} model \citep[][in prep]{behroozi_etal17}.
-This model maps stellar mass and star-formation rate to every halo and subhalo at each snapshot in the Bolshoi-Planck simulation.
-The stellar mass function, quenched fraction, SFR density, and SFR-dependent clustering are all accurately captured by this model from $z=0-10.$ The model we have developed in the present work does not depend in an essential way upon the {\tt UniverseMachine} model in particular; we only require some reasonably accurate starting point for the $\mstar$ and $\ssfr$ values mapped to simulated halos.
-
-\subsubsection{Mapping $\bt$ to halos}
-\label{subsubsec:random_bt_model}
-
-Our model for galaxy size is further predicated upon the mapping between dark matter halos and $\bt,$ the fraction of stellar mass in the bulge.
-In a companion paper to this work, we will present a separate empirical model for the $\bt-$halo connection.
-For our present purposes, we instead rely upon the simplest possible assumption for this connection that recovers the observed distribution $P(\bt\vert\mstar,\ssfr):$ we suppose that galaxy $\bt$ has no dependence whatsoever upon halo environment or assembly, beyond what is inherited by the mutual correlation between $\mstar, \ssfr$ and the cosmic web.
-That is, we map $\bt$ to dark matter halos by using the $\mstar$ and $\ssfr$ values from {\tt UniverseMachine} to randomly select the $\bt$ of a galaxy from our SDSS sample with a similar $\mstar$ and $\ssfr.$ The intuitive interpretation of this modeling choice is that we assume the morphology-density relation is entirely determined by the color-density relation.
-
-\subsection{Mock Measurements of Clustering and Lensing}
-\label{subsec:mock_measurements}
-
-For mock galaxies, to compute galaxy clustering we employ the distant observer approximation by treating the simulation $z-$axis as the line-of-sight.
-We compute $\wproj$ using the {\tt mock\_observables.wp} function in {\tt Halotools}, which is a python implementation of the algorithm in the {\tt Corrfunc} C library \citep{sinha_etal17}.
-We compute lensing $\Delta\Sigma$ using the {\tt mock\_observables.delta\_sigma} function in {\tt Halotools} to calculate the two-dimensional surface mass density of a random downsampling of $10^6$ dark matter particles in the snapshot.
-
-\section{Galaxy Profile Model}
+\section{Galaxy-Halo Model}
 \label{sec:model}
@@
 
+APH thanks John Baker for the {\em Toejam \& Earl} soundtrack.
+
 \bibliography{galsize_paper}

### 2017-09-15 paper/galsize_paper.tex
Added description of Moster13-based smhm

@@
 \label{sec:model}
+
+We map $\mstar$ onto subhalos with the best-fit stellar-to-halo mass relation from \citet{moster_etal13}:
+
+\begin{equation*}
+\mstar/\mhalo = 2N\left[(\mhalo/M_{1})^{-\beta} + (\mhalo/M_1)^{\gamma}\right]^{-1}.
+\end{equation*}
+For halo mass $\mhalo$ we use $\mpeak,$ the largest value of $\mvir$ ever attained along the main progenitor branch of the subhalo.
+The values of the best-fit parameters in \citet{moster_etal13} were fit to a stellar mass function (SMF) with values $\mstar^{\rm MPA-JHU}$ based on the MPA-JHU catalog \citep{kauffmann_etal03,brinchmann_etal04}, which differs from the SMF in our galaxy sample \citep[see, e.g.,][]{bernardi_etal14}.
+We account for this difference by manually tabulating the median value $\langle\mstar^{\rm Meert+15}\vert\mstar^{\rm MPA-JHU}\rangle$ in logarithmic bins spanning $9 < \log_{10}\mstar^{\rm MPA-JHU}/\msun < 12,$ and applying the median correction to the Monte Carlo realization of the mock galaxy sample.
+This results in a typical boost of $\sim0.25$ dex at $\mstar^{\rm MPA-JHU}\approx10^{9.75}\msun,$ and $\sim0.4$ dex at $\mstar^{\rm MPA-JHU}\approx10^{11.5}\msun.$
 

### 2017-09-15 paper/galsize_paper.tex
Finished description of size modeling

@@
 \newcommand{\sigmarhalf}{\sigma_{\rm R_{1/2}}}
-\newcommand{\rvir}{R_{\rm vir}}
 \newcommand{\bt}{{\rm B/T}}
@@
 \newcommand{\mhalo}{M_{\rm halo}}
+\newcommand{\rvir}{R_{\rm vir}}
+\newcommand{\rmpeak}{R_{\rm M_{peak}}}
 
@@
 
-Motivated by the \citet{kravtsov13} results, we model the half-mass radii of galaxies as separate power law functions of halo virial radius:
-
-\begin{eqnarray}
+In \citet{kravtsov13}, it was found that if a stellar-to-halo mass relation is inverted to map halo mass estimates $\mhalo$ onto SDSS galaxies, and then the $\mhalo-\rvir$ relation is applied to map values of $\rvir$ onto the galaxies, then the resulting $\rhalf-\rvir$ relation of SDSS galaxies exhibits the following linear scaling across a wide range of stellar mass:
+\beq
 \label{eq:fiducial_model}
-\rhalfbulge &=& \abulge\rvir^{\alphabulge} \\
-\rhalfdisk &=& \adisk\rvir^{\alphadisk}
-\end{eqnarray}
-
-For central galaxies residing in host halos, we use the present-day virial radius; for satellite galaxies we use the virial radius at the time of accretion, using physical units of $\kpc.$ We model the composite size of model galaxies as
-\beq
-\rhalf = (\bt)\rhalfbulge + (1-\bt)\rhalfdisk.
+\rhalf = 0.0125\rvir
 \eeq
 
-When generating Monte Carlo realizations of our model galaxy population, we add log-normal scatter $\sigmarhalf$ separately to each component.
-Our model for sizes thus has five free parameters: $\abulge, \adisk, \alphabulge, \alphadisk,$ and $\sigmarhalf.$
-
-We reiterate an important distinction drawn in the formulation of our forward modeling approach.
-In the model described above, $\rhalfbulge$ and $\rhalfdisk$ are forward modeling quantities that we aim to constrain through SDSS observations of {\em composite} galaxy size $\rhalf.$ In particular, both model and real galaxies will be categorized as ``small" or ``large`` according to whether $\rhalf$ is above or below the median size for a galaxy with total stellar mass $\mstar.$
+Motivated by the simplicity of this scaling relation, we transform the \citet{kravtsov13} into a forward model using {\tt Halotools}.
+For the virial radius of halos and subhalos, we use $\rmpeak,$ the value of $\rvir$ in physical units of $\kpc$ measured at the time of peak subhalo mass.
+When generating Monte Carlo realizations of our model galaxy sizes, we add log-normal scatter $\sigmarhalf=0.15$ dex.
 

### 2017-09-15 paper/galsize_paper.tex
Updated figure 1

@@
 \begin{equation*}
-\mstar/\mhalo = 2N\left[(\mhalo/M_{1})^{-\beta} + (\mhalo/M_1)^{\gamma}\right]^{-1}.
+\langle\mstar/\mhalo\rangle = 2N\left[(\mhalo/M_{1})^{-\beta} + (\mhalo/M_1)^{\gamma}\right]^{-1}.
 \end{equation*}
@@
 
-In \S~\ref{subsec:tests1} we show comparisons between the fiducial galaxy profile model described in \S~\ref{sec:model} and our SDSS sample.
-We demonstrate the sensitivity of galaxy clustering measurements to the post-infall evolution of satellite profiles in \S~\ref{subsec:tests2}, establishing the success of our fiducial model as non-trivial.
-In \S~\ref{subsec:tests3} we show that even highly idealized measurements of galaxy clustering and lensing are insensitive to assumptions about the relation between halo spin $\halospin$ and size $\rhalf$ of disk-dominated galaxies, implying that large-scale structure observations yield little-to-no constraining power on such assumptions.
+In \S\ref{subsec:tests1} we show comparisons between the galaxy size model described in \S\ref{sec:model} and our SDSS sample.
+We identify the key ingredients that determine the characteristic $\rhalf-$dependence of galaxy clustering in \S\ref{subsec:tests2}.
+In so doing, we demonstrate the sensitivity of galaxy clustering measurements to the underlying model assumptions, establishing the success of our model as non-trivial.
 
@@
 
-\subsubsection{Scaling of $\rhalf$ with $\mstar$}
-\label{subsubsec:scaling_relation}
-
-In Figure \ref{fig:scatter_plot} we show the scaling of composite galaxy size $\rhalf$ with $\mstar,$ with separate panels dedicated to subsamples of galaxies divided according to value of $\bt.$ We refer to galaxies with $\bt<0.25$ as ``disk-dominated", $\bt>=0.75$ as ``bulge-dominated", and $0.25<=\bt<0.75$ as ``mixed morphology".
-We remind the reader that $\rhalf$ and $\mstar$ refer to the scale radius and stellar mass of the {\em entire} galaxy, not of an individual component.
-
+In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ 
 %---------------------------------------------------------------------------------------------------
@@
 \centering
-\includegraphics[width=8cm]{FIGS/size_vs_stellar_mass_multipanel_bt_decomposition.pdf}
+\includegraphics[width=8cm]{FIGS/single_component_model_vs_sdss_one_point.pdf}
 \caption{
@@
 Scattered points show the $\rhalf-\mstar$ relation for SDSS galaxies as measured in \citet{meert_etal15}.
-Bulge-dominated galaxies are defined in terms of the bulge-to-total stellar mass ratio $\bt>=0.75,$ disk-dominated galaxies $\bt<0.25,$ mixed morphology as $0.25 < \bt < 0.75.$ The black curve in each panel shows the $\rhalf-\mstar$ relation implied by our fiducial model, in which $\rhalfbulge=\abulge\rvir^{\alphabulge}$ and $\rhalfdisk=\adisk\rvir^{\alphadisk},$ with $\adisk=0.014=7\abulge, \alphadisk=1, \alphabulge=5/4,$ and uncorrelated log-normal scatter of $0.2$ dex about these relations.
+The black curve in each panel shows the $\rhalf-\mstar$ relation implied by the model.
+This figure confirms the findings in \citet{kravtsov13} that a linear relationship between $\rvir$ and $\rhalf,$ convolved against the nonlinear relationships between $\rvir, \mhalo$ and $\mstar,$ correctly predicts the characteristic curvature in the relation $\langle\rhalf\vert\mstar\rangle$ over a wide range in stellar mass.
 }

### 2017-09-15 paper/galsize_paper.tex
Replaced figures

@@
 
-In \S\ref{subsec:tests1} we show comparisons between the galaxy size model described in \S\ref{sec:model} and our SDSS sample.
+%In \S\ref{subsec:tests1} we show comparisons between the galaxy size model described in \S\ref{sec:model} and our SDSS sample.
 We identify the key ingredients that determine the characteristic $\rhalf-$dependence of galaxy clustering in \S\ref{subsec:tests2}.
@@
 
-\subsection{Tests of the Fiducial Power Law Model}
-\label{subsec:tests1}
+In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$
 
-In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ 
 %---------------------------------------------------------------------------------------------------
@@
 
-The results shown in \citet{kravtsov13} simplify our task of parameter space exploration: the assumption that composite galaxy size $\rhalf$ scales in linear proportion to halo radius $\rvir$ gives a qualitatively good description of SDSS data over many orders of magnitude in galaxy mass.
-As first pointed out in \citet{kravtsov13}, this linearization is non-trivial because of the well-known curvature in the scaling relation of $\langle\rhalf\vert\mstar\rangle,$ which is visually apparent in all panels of Fig.~\ref{fig:scatter_plot}.
-
-Comparison of the top panels of Fig.~\ref{fig:scatter_plot} show that this linearization is only approximate; evidently, galaxy size $\rhalf$ of bulge-dominated systems has a steeper scaling relation with $\mstar$ relative to disk-dominated systems.
-This difference motivates our simple extension of the \citet{kravtsov13} model, in which $\rhalf$ of disk- and bulge-dominated galaxies scales according to separate power laws.
-
-Through MCMC parameter space exploration aided by {\tt emcee} \citep{emcee_hammer}, we find a good description of the observed one-point scaling relations is given by model galaxies with the parameters $\adisk=0.014=7\abulge, \alphadisk=1, \alphabulge=5/4,$ with log-normal scatter of $0.2$ dex motivated by \citet{somerville_etal17}.
-The black curves in Fig.~\ref{fig:scatter_plot} illustrate the median $\langle\rhalf\vert\mstar\rangle.$
-
-We confirm the visual impression of comparing the top panels of Fig.~\ref{fig:scatter_plot}: we are unable to find a parameter combination in which the composite size of both bulge- and disk-dominated galaxies have linear ($\alpha=1$) scaling with $\rvir.$ We do not quantitatively rule out such a scaling relation, as this would require careful investigation of the systematic error budget of galaxy profile modeling that we consider beyond the scope, though well-motivated, by the present work.
-
-\subsubsection{Dependence of clustering on $\rhalf$}
-\label{subsubsec:clustering_tests}
-
 In this section we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj(\rproj).$ Galaxy clustering has complex, simultaneous dependence upon $\mstar,$ $\ssfr,$ $\rhalf,$ and $\bt.$ Since the purpose of this work is to test models of composite galaxy size $\rhalf,$ we design a measurement that is specifically tailored to isolate the influence of $\rhalf$ on the two-point function, while minimizing the dependence upon the other correlated variables.
@@
 \centering
-\includegraphics[width=8cm]{FIGS/size_clustering_ratios_bt_decomposition_model_vs_sdss.pdf}
+\includegraphics[width=8cm]{FIGS/size_clustering_ratios_stripping_model_vs_sdss.pdf}
 \caption{
@@
 
-%---------------------------------------------------------------------------------------------------
-\begin{figure}
-\centering
-\includegraphics[width=8cm]{FIGS/random_bt_centrals_vs_satellites.pdf}
-\caption{
-{\bf Morphologies of centrals and satellites of the same halo mass.} We show the PDF of the bulge-to-total stellar mass ratio $\bt$ of central and satellite galaxies of the same halo mass $\mhalo=\mpeak.$ In the model, the PDF of $\bt$ is determined by the stellar mass $\mstar$ and specific star-formation rate $\ssfr$ statistically determine, with no residual dependence on the cosmic web.
-Satellite galaxies in the model are ``bulgier" than centrals of the same halo mass because satellites are more quiescent than centrals of the same stellar mass.
-Thus our baseline model ansatz is that the morphology-density relation is purely derived from the color-density relation.
-Since composite size $\rhalf$ in the model is given by $\rhalf\equiv\rhalf=(\bt)\rhalfbulge + (1-\bt)\rhalfdisk,$ this ansatz in turn implies that smaller galaxies cluster more strongly relative to larger galaxies of the same stellar mass, as seen in the measurements shown in Fig.~\ref{fig:clustering_ratio_upshot}.
-}
-\label{fig:bt_censat}
-\end{figure}
-%-----------------------------------------------------------------------------------------------------
-
-In the {\tt UniverseMachine}, and in any quantitatively successful cosmological model of galaxy formation, central galaxies are preferentially more star-forming relative to satellites of comparable stellar or halo mass.
-Since bluer galaxies are diskier than redder galaxies, our model centrals will be diskier than satellites.
-Our galaxy profile model has $\adisk=7\abulge,$ and so satellite galaxies will be smaller than centrals due to the $\bt-\ssfr$ correlation.
-These simultaneous features alone will naturally result in the negative sign of the clustering ratios seen in Figure~\ref{fig:clustering_ratio_upshot}.
-
 In light of this explanation, it is natural to ask whether this simple feature {\em alone} is all that is needed for any model of $\rhalf$ to achieve this level of success at predicting galaxy clustering on small and large scales.
@@
 \centering
-\includegraphics[width=8cm]{FIGS/alternate_satellite_models_size_clustering_ratios.pdf}
+\includegraphics[width=8cm]{FIGS/scrambled_size_clustering_ratios.pdf}
 \caption{
@@
 However, $\halospin$ exhibits a highly non-trivial connection to the cosmic density field, including $\mvir-$dependent correlations with large-scale density and topology, and so it is natural to ask how these correlations manifest in our $\rhalf$ clustering ratios.
-
-%---------------------------------------------------------------------------------------------------
-\begin{figure}
-\centering
-\includegraphics[width=8cm]{FIGS/size_clustering_ratios_bt_decomposition_spin_size_correlation.pdf}
-\includegraphics[width=8cm]{FIGS/central_lensing_spin_size_correlation.pdf}
-\caption{
-{\bf Clustering and lensing provide no constraining power on the assumption that $\rhalfdisk\propto\halospin.$}
-We compare the predictions between our fiducial model in which sizes are purely stochastic, and an alternative model motivated by \citet{mo_mao_white98} in which central galaxy disk size is maximally correlated with host halo spin at fixed stellar mass \citep[implemented via conditional abundance matching, e.g.,][]{hearin_etal13b}.
-The tiny differences between the solid and dashed curves imply that conventional large-scale structure measurements cannot even in principle provide compelling evidence pertaining to the assumption that $\rhalfdisk\propto\halospin.$
-}
-\label{fig:halospin_lensing}
-\end{figure}
-%-----------------------------------------------------------------------------------------------------
 

### 2017-09-15 paper/galsize_paper.tex
Deleted some obsolete sections

@@
 \caption{
-{\bf Two-point clustering predictions of the fiducial model.}
+{\bf Size-dependence of galaxy clustering.}
 Points with error bars show new SDSS measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj,$ compared to predictions by the model tuned to the measurements shown in Fig.~\ref{fig:scatter_plot}.
@@
 \caption{
-{\bf Clustering tightly constrains satellite-specific size evolution.}
+{\bf Critical ingredients .}
 Here we compare our fiducial model, in which satellite galaxy size is set by $\rvir$ at the time of infall, to an alternative model analogous to \citet{watson_etal12} in which satellite sizes contract in proportion to $(\mvir/\macc)^{1/3}.$ The large differences between solid and dashed curves in the top panels show that the $\rhalf-$dependence of galaxy clustering ratios is highly sensitive to the post-infall evolution of satellite galaxy profiles.
@@
 
-\subsection{Insensitivity of Clustering and Lensing to Halo Spin Correlations}
-\label{subsec:tests3}
-
-The results of the previous section \S\ref{subsec:tests2} illustrate the sensitive constraints that galaxy clustering measurements provide on modeling assumptions about satellite $\rhalf.$ In this section we explore the potential constraining power of clustering on models for the size of disks of central galaxies.
-In particular, we seek to assess whether clustering measurements can constrain the long-standing assumption that disk size scales in proportion to the spin of the parent halo, $\rhalfdisk\propto\halospin,$ \citep[e.g.,][]{mo_mao_white98}.
-
-We wish to build an alternative empirical model that inherits the quantitative success of our fiducial model, and further makes the extreme assumption that central galaxy $\rhalfdisk$ is maximally correlated with $\halospin$ at fixed $\mstar.$ Conditional Abundance Matching \citep[hereafter, CAM,][]{hearin_etal13b} is the natural framework to use to build such a model.
-
-Disk size in our fiducial model has log-normal scatter $\sigmarhalf=0.2$ dex about the mean value $\adisk\rvir^{\alphadisk}.$  We use the CAM implementation in {\tt Halotools}\footnote{See {\tt halotools.empirical\_models.conditional\_abunmatch} documentation for details.} to extend our fiducial model so that the scatter in central galaxy $\rhalfdisk$ is not stochastic, but is in stead in one-to-one correspondence with $\halospin$ at fixed total stellar mass $\mstar.$ This alternative model thus has exactly the same one-point functions as the fiducial model (i.e., the solid curves in Fig.~\ref{fig:scatter_plot} are formally preserved by construction).
-However, $\halospin$ exhibits a highly non-trivial connection to the cosmic density field, including $\mvir-$dependent correlations with large-scale density and topology, and so it is natural to ask how these correlations manifest in our $\rhalf$ clustering ratios.
-
-The top panel of Figure \ref{fig:halospin_lensing} shows a comparison of the $\rhalf$ clustering ratios of our fiducial model to the alternative CAM model in which $\rhalfdisk\propto\halospin.$ Evidently, for galaxies in this stellar mass range, the strength of $\halospin$ correlations with the cosmic web are sufficiently weak as to produce almost no measurable impact on the $\rhalf-$dependence of the clustering of disk-dominated systems.
-
-Of course it is possible that galaxy clustering is poorly suited to detect $\rhalfdisk-\halospin$ correlations, which instead manifest in some alternative measurement of large-scale structure.
-For example, numerous studies of the $\halospin-$dependence of halo assembly bias have shown that low-spin halos are preferentially found in environments of below-average dark matter density relative to high-spin halos of comparable mass \citep[see, for example,][]{lee_etal17}.
-
-Motivated by these results, we show in the bottom panel of Fig.~\ref{fig:halospin_lensing} an idealized mock measurement of the lensing of central galaxies identified with perfect fidelity.
-Solid curves show $\Delta\Sigma$ signal of our fiducial model centrals, dashed curves the alternative CAM model.
-Again we see that $\rhalfdisk-\halospin$ correlations are simply not strong enough in $L_\ast$ galaxies to produce a compelling signal.
-These results imply that it will be extremely challenging to either confirm or refute the $\rhalfdisk\propto\halospin$ hypothesis using large-scale structure measurements.
-We discuss this further in \S\ref{subsec:mo_status}.
-
 \section{Discussion}
 \label{sec:discussion}
-
-\subsection{Implications for Satellites}
-\label{subsec:satellite_discussion}
-
-\subsection{State of the $\rhalfdisk\propto\halospin$ Hypothesis}
-\label{subsec:mo_status}
 
@@
 
-\subsection{Relation to Previous Work}
-\label{subsec:previouswork}
+\subsection{Implications for Satellite Mass Loss}
+\label{subsec:satellite_discussion}
 
@@
 
-\section{Conclusion}
+\section{Conclusions}
 \label{sec:conclusion}

### 2017-09-15 paper/galsize_paper.tex
Developing results description

@@
 \newcommand{\wproj}{w_{\rm p}}
+\newcommand{\wplarge}{w_{\rm p}^{\rm large}}
+\newcommand{\wpsmall}{w_{\rm p}^{\rm small}}
+\newcommand{\wpall}{w_{\rm p}^{\rm all}}
 
@@
 
-In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$
+In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ Scattered gray points show the scaling relation for our SDSS galaxy sample, while the black curve shows the median relation $\langle\rhalf\vert\mstar\rangle$ implied by the model described in \S\ref{sec:model}.
 
@@
 Scattered points show the $\rhalf-\mstar$ relation for SDSS galaxies as measured in \citet{meert_etal15}.
-The black curve in each panel shows the $\rhalf-\mstar$ relation implied by the model.
-This figure confirms the findings in \citet{kravtsov13} that a linear relationship between $\rvir$ and $\rhalf,$ convolved against the nonlinear relationships between $\rvir, \mhalo$ and $\mstar,$ correctly predicts the characteristic curvature in the relation $\langle\rhalf\vert\mstar\rangle$ over a wide range in stellar mass.
+The black curve shows the median $\rhalf-\mstar$ relation implied by the model described in \S\ref{sec:model}, in which $\rhalf=0.0125\rvir.$ This figure confirms the findings in \citet{kravtsov13} that a linear relationship between $\rvir$ and $\rhalf,$ convolved against the nonlinear relationships between $\rvir, \mhalo$ and $\mstar,$ correctly predicts the characteristic curvature in the relation $\langle\rhalf\vert\mstar\rangle$ over a wide range in stellar mass.
 }
@@
 
-In this section we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj(\rproj).$ Galaxy clustering has complex, simultaneous dependence upon $\mstar,$ $\ssfr,$ $\rhalf,$ and $\bt.$ Since the purpose of this work is to test models of composite galaxy size $\rhalf,$ we design a measurement that is specifically tailored to isolate the influence of $\rhalf$ on the two-point function, while minimizing the dependence upon the other correlated variables.
+In Figure \ref{fig:clustering_ratio_upshot} we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj(\rproj).$ Because galaxy clustering has well-known dependence upon $\mstar$ that is not the subject of this work, we wish to remove this influence and focus purely on the relationship between $\rhalf$ and $\wproj(\rproj).$ To do so, we determine the value $\langle\rhalf\vert\mstar\rangle$ by computing a sliding median of $\rhalf,$ calculated using a window of width $N_{\rm gal}=1000.$ Each galaxy is categorized as either ``large" or ``small" according to whether it is above or below the median value appropriate for its stellar mass.
+For any $\mstar-$threshold sample, the SMF of the ``large" and ``small" subsamples are identical, by construction.
 
-To achieve this, we compute projected clustering separately for $\mstar-$complete samples of galaxies defined by simultaneous cuts on $\bt$ and $\rhalf,$ described as follows.
-First, we construct subsamples of disk-dominated and bulge-dominated galaxies using cuts of $\bt<0.25$ and $\bt>0.75,$ respectively, as in \S~\ref{subsubsec:scaling_relation} above.
-Separately for each $\bt-$selected subsample, we calculate $\langle\rhalf\vert\mstar;\bt\rangle,$ the median composite size of the sample as a function of total galaxy stellar mass.
-We split each $\bt-$selected sample in half according to whether the galaxy has a size $\rhalf$ that is above or below this median value.
-For any $\mstar-$complete threshold, this gives four subsamples of large and small, disk- and bulge-dominated galaxies.
-For each $\bt-$selected sample, we calculate the difference $\wproj^{\rm large}-\wproj^{\rm small},$ scaled by $\wproj^{\rm all},$ the clustering of the $\bt-$selected sample prior to splitting on $\rhalf,$ and refer to this quantity as {\em the $\rhalf$ clustering ratio}.
+We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds, $\mstar>10^{9.75}\msun,$ $\mstar>10^{10.25}\msun,$ $\mstar>10^{10.75}\msun,$ and $\mstar>10^{11.25}\msun.$ We make the same measurements for each volume-limited $\mstar-$threshold sample {\em without} splitting on size, giving us measurements $\wpall, \wplarge,$ and $\wpsmall$ for each threshold sample.
+This allow us to compute the ratio $(\wplarge-\wpsmall)/\wpall,$ which we refer to as {\em the $\rhalf$ clustering ratio}.
+These ratios are the measurements appearing on the y-axis in each panel of Figure \ref{fig:clustering_ratio_upshot}.
+Points with error bars show SDSS measurements, solid curves show the clustering ratios of model galaxies.
+Before unpacking the information contained in these clustering measurements, we stress that the good agreement shown between model and data in Figure~\ref{fig:clustering_ratio_upshot} is a genuine model prediction, since the model parameters were taken directly from \citet{kravtsov13}, which were fit to the one-point measurements in Fig.~\ref{fig:scatter_plot}, whereas the two-point measurements appearing in Figure \ref{fig:clustering_ratio_upshot} have heretofore never been measured.
 
@@
 \caption{
-{\bf Size-dependence of galaxy clustering.}
+{\bf $\rhalf-$dependence of galaxy clustering.}
 Points with error bars show new SDSS measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj,$ compared to predictions by the model tuned to the measurements shown in Fig.~\ref{fig:scatter_plot}.
-We define a disk or bulge as ``large" or ``small" according to whether it is above or below the median size for its stellar mass.
-The y-axis shows clustering strength ratios, so that, for example, a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of comparable stellar mass.
-We show results separately for disk-dominated galaxies ({\em top} panels) and bulge-dominated galaxies ({\em bottom }panels), and different thresholds in total stellar mass in the {\em left} and {\em right} panels.
-The successful prediction shown here is remarkable because the model was not fit to these data, and because two-point clustering is highly sensitive to the physics that shapes satellite galaxy profiles (see Fig.~\ref{fig:satellites}).
+We define a galaxy as ``large" or ``small" according to whether it is above or below the median size for its stellar mass, so that in each panel, the SMF of the ``large" and ``small" subsamples are identical, as described in the text.
+The y-axis shows {\em clustering strength ratios,} so that, for example, a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of comparable stellar mass.
+Each panel shows results separately for a different volume-limited $\mstar-$threshold samples.
+Fiducial model predictions appear as the solid curve in each panel.
 }
@@
 
-The y-axis of each panel in Figure \ref{fig:clustering_ratio_upshot} shows these $\rhalf$ clustering ratios, with left and right panels showing measurements for $\mstar>10^{10}M_{\odot}$ and $\mstar>10^{10.5}M_{\odot}$ thresholds in total stellar mass, and top and bottom panels showing results for disk- and bulge-dominated samples, respectively.
-Points with error bars show SDSS measurements, solid curves show the clustering ratios of model galaxies.
-Before unpacking the information contained in these clustering measurements, we stress that the good agreement shown between model and data in Figure~\ref{fig:clustering_ratio_upshot} is a genuine model prediction, since we only tuned parameters to fit the one-point measurements in Fig.~\ref{fig:scatter_plot}.
-
-The salient feature of the clustering ratio measurements is that they are negative: for either disk- or bulge-dominated samples, small galaxies cluster more strongly than large galaxies of the same stellar mass threshold, a new result.
-This feature also holds true for model galaxies, for which both $\rhalfbulge$ and $\rhalfdisk$ scale in power law proportion to $\rvir.$ Since halo mass $\mvir\propto\rvir^{3},$ and clustering is a strong function of $\mvir,$ the result may seem surprising.
+The salient feature of the clustering ratio measurements is that they are negative: small galaxies cluster more strongly than large galaxies of the same stellar mass, a new result.
+This feature also holds true for model galaxies.
+This result may be surprising, since $\rhalf\propto\rvir,$ halo mass $\rvir\propto\mhalo^{1/3},$ and clustering strength increases with $\mvir.$ Based on this simple argument, one would expect the opposite trend to the measurements shown here.
 
@@
 \caption{
-{\bf Critical ingredients .}
+{\bf Origin of the $\rhalf-$dependence of clustering.}
 Here we compare our fiducial model, in which satellite galaxy size is set by $\rvir$ at the time of infall, to an alternative model analogous to \citet{watson_etal12} in which satellite sizes contract in proportion to $(\mvir/\macc)^{1/3}.$ The large differences between solid and dashed curves in the top panels show that the $\rhalf-$dependence of galaxy clustering ratios is highly sensitive to the post-infall evolution of satellite galaxy profiles.

### 2017-09-15 paper/galsize_paper.tex
Stripped away remaining obsolete text.

@@
 
-%In \S\ref{subsec:tests1} we show comparisons between the galaxy size model described in \S\ref{sec:model} and our SDSS sample.
-We identify the key ingredients that determine the characteristic $\rhalf-$dependence of galaxy clustering in \S\ref{subsec:tests2}.
+In \S\ref{subsec:predictions} we show comparisons between the galaxy size model described in \S\ref{sec:model} and our SDSS sample.
+We identify the key ingredients that determine the characteristic $\rhalf-$dependence of galaxy clustering in \S\ref{subsec:subsec:shuffle_tests}.
 In so doing, we demonstrate the sensitivity of galaxy clustering measurements to the underlying model assumptions, establishing the success of our model as non-trivial.
+
+\subsection{Testing Model Predictions}
+\label{subsec:predictions}
 
@@
 These ratios are the measurements appearing on the y-axis in each panel of Figure \ref{fig:clustering_ratio_upshot}.
-Points with error bars show SDSS measurements, solid curves show the clustering ratios of model galaxies.
+Points with error bars show SDSS measurements, solid curves show the clustering ratios of model galaxies as predicted by the model described in \S\ref{sec:model}.
 Before unpacking the information contained in these clustering measurements, we stress that the good agreement shown between model and data in Figure~\ref{fig:clustering_ratio_upshot} is a genuine model prediction, since the model parameters were taken directly from \citet{kravtsov13}, which were fit to the one-point measurements in Fig.~\ref{fig:scatter_plot}, whereas the two-point measurements appearing in Figure \ref{fig:clustering_ratio_upshot} have heretofore never been measured.
@@
 This result may be surprising, since $\rhalf\propto\rvir,$ halo mass $\rvir\propto\mhalo^{1/3},$ and clustering strength increases with $\mvir.$ Based on this simple argument, one would expect the opposite trend to the measurements shown here.
+We present a resolution to this puzzle in the following section.
 
-The resolution to this puzzle is illustrated in Figure~\ref{fig:bt_censat}, which shows the PDF of $\bt$ for halos of the same mass $\mhalo,$ defined as $\mpeak,$ the peak mass ever attained through the history of the (sub)halo, so that host halos and subhalos can be treated on equal footing.
-In the model, central galaxies are diskier than satellites, a feature that is inherited from the method we use to map $\bt$ to model galaxies.
+\subsection{Origin of the size-dependence of galaxy clustering}
+\label{subsec:shuffle_tests}
 
-In light of this explanation, it is natural to ask whether this simple feature {\em alone} is all that is needed for any model of $\rhalf$ to achieve this level of success at predicting galaxy clustering on small and large scales.
+We can understand the origin of the shape of the clustering strength ratios shown in Figure~\ref{fig:clustering_ratio_upshot} through a series of straightforward ``shuffle tests".
+
+% shown in Figure \ref{fig:shuffle}.
+
+%In light of this explanation, it is natural to ask whether this simple feature {\em alone} is all that is needed for any model of $\rhalf$ to achieve this level of success at predicting galaxy clustering on small and large scales.
 We address this question in \S~\ref{subsec:tests2} below, finding that the answer is no: the reasonably correct magnitude and scale-dependence of the clustering ratios predicted by our model is a non-trivial result that places tight constraints on the post-infall physics of satellite galaxies.
 
-\subsection{Sensitivity of Clustering to Satellite Profile Evolution}
-\label{subsec:tests2}
+We conclude this section by estimating how satellite mass stripping manifests in $\wproj(\rproj).$ To do so, we construct an extension our fiducial model with a simple additional ingredient for post-infall evolution of satellites mass and size.
 
-In this section we explore how post-infall changes in satellite $\rhalf$ manifest in $\wproj(\rproj).$ To do so, we construct an extension our fiducial model with a simple additional ingredient for post-infall size evolution of satellites.
-
-In the fiducial model described in \S~\ref{sec:model}, recall that in the power law a scaling relations (Eq.~\ref{eq:fiducial_model}) the halo radius $\rvir$ used for satellite galaxies is taken to be the value at the time of infall.
+%In the fiducial model described in \S~\ref{sec:model}, recall that in the power law a scaling relations (Eq.~\ref{eq:fiducial_model}) the halo radius $\rvir$ used for satellite galaxies is taken to be the value at the time of infall.
 The simple interpretation of this assumption is that, in a statistical sense, the size of satellite galaxies is determined by its history as a central galaxy, and that post-infall physics leaves no distinct imprint on satellite $\rhalf.$
 
-Here we suppose that this assumption is violated, and that $\rhalf$ decreases after infall according to $(\mvir/\macc)^{1/3}.$ That is, in this alternative formulation, rather than using $\rvir$ at the time of infall for satellites in the power law scaling relations, we instead use $\rvir(\mvir/\macc)^{1/3}.$ This simple toy model attempts supposes that the same physical processes leading to halo mass loss are also responsible for a post-infall decrease in satellite size.
+%Here we suppose that this assumption is violated, and that $\rhalf$ decreases after infall according to $(\mvir/\macc)^{1/3}.$ That is, in this alternative formulation, rather than using $\rvir$ at the time of infall for satellites in the power law scaling relations, we instead use $\rvir(\mvir/\macc)^{1/3}.$ This simple toy model attempts supposes that the same physical processes leading to halo mass loss are also responsible for a post-infall decrease in satellite size.
 
@@
 {\bf Origin of the $\rhalf-$dependence of clustering.}
-Here we compare our fiducial model, in which satellite galaxy size is set by $\rvir$ at the time of infall, to an alternative model analogous to \citet{watson_etal12} in which satellite sizes contract in proportion to $(\mvir/\macc)^{1/3}.$ The large differences between solid and dashed curves in the top panels show that the $\rhalf-$dependence of galaxy clustering ratios is highly sensitive to the post-infall evolution of satellite galaxy profiles.
-The successful prediction of our fiducial model, in which satellite galaxies neither contract nor puff up after infall, places tight constraints on satellite-specific physical processes, which must be either negligible or conspiratorially produce little-to-no size change after accretion.
+Here we compare our fiducial model, in which satellite galaxy size is set by $\rvir$ at the time of infall, to a set of alternative models created by shuffling the sizes of various subsamples of the fiducial mock.
 }
-\label{fig:satellites}
+\label{fig:shuffle}
 \end{figure}
@@
 
-Figure~\ref{fig:satellites} compares the clustering ratios of our fiducial model (solid curves) to the clustering ratios of this alternative model (dashed curves).
+%Figure~\ref{fig:satellites} compares the clustering ratios of our fiducial model (solid curves) to the clustering ratios of this alternative model (dashed curves).
 The difference between the small-scale clustering of the two models is stark: the assumption that $\rhalf$ decreases after infall leaves a strong imprint on the $\rhalf-$dependence of $\wproj(\rproj),$ such that small galaxies cluster {\em much} more strongly relative to large galaxies, particularly for disk-dominated systems with $\mstar\approx10^{10}\msun.$
 
-The large differences between the solid and dashed curves in Fig.~\ref{fig:satellites} establishes that the largely successful prediction for the clustering ratios fiducial model is a non-trivial: $\wproj(\rproj)$ is indeed providing good constraining power on the  assumptions underlying our profile modeling and not simply our morphology modeling, c.f., \S\ref{subsubsec:random_bt_model} and \S\ref{sec:model}.
+%The large differences between the solid and dashed curves in Fig.~\ref{fig:satellites} establishes that the largely successful prediction for the clustering ratios fiducial model is a non-trivial: $\wproj(\rproj)$ is indeed providing good constraining power on the  assumptions underlying our profile modeling and not simply our morphology modeling, c.f., \S\ref{subsubsec:random_bt_model} and \S\ref{sec:model}.
 We refer the reader to \S\ref{subsec:satellite_discussion} for further discussion of the physical implications of this result.

### 2017-09-16 paper/galsize_paper.tex
Finished description of each curve in the shuffle test plot

@@
 We can understand the origin of the shape of the clustering strength ratios shown in Figure~\ref{fig:clustering_ratio_upshot} through a series of straightforward ``shuffle tests".
+The points with error bars and solid curves in each panel of Fig.\ref{fig:shuffle} are identical to those appearing in Fig.\ref{fig:clustering_ratio_upshot}, although the dynamic range of the y-axis has changed to accommodate the additional curves.
+
+We generated each additional curve by variations on the following exercise.
+In logarithmic bins of $\mpeak$ with width of $0.1$dex, we randomly shuffle the modeled $\rhalf$ values of some particular subpopulation of model galaxies that reside in subhalos in the $\mpeak$ bin.
+After repeating this shuffle over the entire range of $\mpeak,$ we then re-divide model galaxies into ``large" and ``small" populations, and remeasure the clustering strength ratios.
+By shuffling sizes amongst different subpopulations, we can gain an understanding of the subhalo properties that contribute to the characteristic shape of the clustering ratios.
+
+In the {\em brown, dotted} curves labeled ``all-gal scramble", we shuffle the sizes of {\em all} model galaxies in the $\mpeak$ bin, so that in the resulting mock, galaxy size has no correlation with any subhalo property beyond $\mpeak.$ In particular, the ``all-gal scramble" mock erases the possible influence of a correlation between galaxy size and the redshift at which the subhalo attains peak mass.
+The resulting clustering strength ratios become exactly as predicted by the naive expectation sketched at the conclusion of \S\ref{subsec:predictions}: $\rhalf\propto\rvir\propto\mhalo^{1/3},$ and so large galaxies clustering more strongly relative to small galaxies of comparable stellar mass.
+
+Statistically, there are actually two distinct effects at work in the ``all-gal scramble".
+Central and satellite galaxies of similar $\mpeak$ have their sizes shuffled amongst each other, and the potential influence of central galaxy assembly bias is also erased.
+We parse these separate effects by exploring three variations on the shuffle tests, described below.
+
+For the {\em cyan dashed} curve labeled ``all-cen-scramble", we only shuffle sizes amongst present-day host halos, i.e., amongst subhalos for which Rockstar {\tt upid} equals -1.
+For the {\em black dashed} curve labeled ``true-cen-scramble", we only shuffle amongst host halos that have never passed within the virial radius of a larger halo throughout their entire assembly history, i.e., we only shuffle amongst non-backsplash host halos.
+Finally, the {\em purple dot-dashed} curve labeled ``sat-scramble", we only shuffle sizes amongst satellite galaxies, i.e., subhalos that are presently located inside the virial radius of a larger halo.
 

### 2017-09-17 paper/galsize_paper.tex
Updated figure and caption

@@
 
+%---------------------------------------------------------------------------------------------------
+\begin{figure}
+\centering
+\includegraphics[width=8cm]{FIGS/cen_sat_sizes.pdf}
+\caption{
+{\bf Relative sizes of centrals and satellites.} In a narrow bin of halo mass $\mhalo=\mpeak\approx10^{12}\msun,$ we show the distribution of model galaxy sizes for different subpopulations galaxies.
+The red histogram shows the sizes of satellites; the blue histogram shows host halos that have never passed inside the virial radius of a larger halo (``true centrals"); the green histogram host halos that were subhalos inside a larger at some point in their past history (``splashback halos").
+In the fiducial model, galaxy size is set by the physical size of the virial radius at the time the (sub)halo attains its peak mass, naturally resulting in smaller sizes for satellites and backsplash centrals relative to true centrals of the same $\mpeak.$
+}
+\label{fig:shuffle}
+\end{figure}
+%-----------------------------------------------------------------------------------------------------
+
 We can understand the origin of the shape of the clustering strength ratios shown in Figure~\ref{fig:clustering_ratio_upshot} through a series of straightforward ``shuffle tests".

### 2017-09-18 galsize_models/models/load_baseline_catalogs.py
Fixed bug in calculation of virial radius at peak mass

@@ -36,10 +36,9 @@ def load_baseline_halocat(simname='bolplanck', redshift=0, fixed_seed=411):
 
     halocat.halo_table['halo_zpeak'] = 1./halocat.halo_table['halo_scale_factor_mpeak'] - 1.
 
-    rvir_peak_comoving_unity_h = halo_mass_to_halo_radius(halocat.halo_table['halo_mpeak'],
+    rvir_peak_physical_unity_h = halo_mass_to_halo_radius(halocat.halo_table['halo_mpeak'],
                                 halocat.cosmology, halocat.halo_table['halo_zpeak'], 'vir')
-    A = halocat.halo_table['halo_scale_factor_mpeak']/halocat.cosmology.h
-    rvir_peak_physical = A*rvir_peak_comoving_unity_h
+    rvir_peak_physical = rvir_peak_physical_unity_h/halocat.cosmology.h
     halocat.halo_table['halo_rvir_zpeak'] = rvir_peak_physical*1000.
 
     nhalos = len(halocat.halo_table)

### 2017-09-19 paper/galsize_paper.tex
Updated paper with new figs

@@
 
-\title[The Emergent Simplicity of Galaxy Size]
-{The Emergent Simplicity of Galaxy Size}
+\title[Empirical Modeling Galaxy Size]
+{Empirical Modeling Galaxy Size Throughout the Cosmic Web}
 
@@
 \centering
-\includegraphics[width=8cm]{FIGS/size_clustering_ratios_stripping_model_vs_sdss.pdf}
+\includegraphics[width=8cm]{FIGS/size_clustering_ratios_stripping_coevolution.pdf}
 \caption{
@@
 \centering
-\includegraphics[width=8cm]{FIGS/scrambled_size_clustering_ratios.pdf}
+\includegraphics[width=8cm]{FIGS/sat_vs_cen_sizes_fracdiff.pdf}
 \caption{

### 2017-09-28 paper/galsize_paper.tex
Updated abstract

@@
 
-\title[Empirical Modeling Galaxy Size]
-{Empirical Modeling Galaxy Size Throughout the Cosmic Web}
+\title[The Emergent Simplicity of Galaxy Size]
+{The Emergent Simplicity of Galaxy Size}
 
@@
 Using forward-modeling techniques based on {\tt Halotools}, we confirm previous results in Kravtsov (2013) that $\rhalf$ is well-described by a linear scaling relation with halo virial radius.
-Novel to this work, we use new SDSS measurements of the $\rhalf-$dependence of galaxy clustering to test this modeling assumption.
-With no changes to the parameters, the model accurately predicts the observed two-point clustering on small- and large-scales over a wide range of stellar mass.
-This quantitative success is remarkable since the Kravtsov (2013) parameters were fit to the observed $\langle\rhalf\vert\mstar\rangle,$ and the $\rhalf-$dependence of SDSS galaxy clustering has heretofore never been measured.
-Moreover, this success is non-trivial, as we demonstrate that galaxy clustering is highly sensitive to the assembly history-dependent physics that shapes the relative size of centrals and satellites.
+Novel to this work, we study galaxy size using new SDSS measurements of the $\rhalf-$dependence of galaxy clustering.
+Smaller galaxies cluster more strongly relative to larger galaxies of the same stellar mass, a new result.
+We show that the $\rhalf-$dependence of galaxy clustering is largely driven by the relative size of central and satellite galaxies: satellites are smaller than centrals of the same halo mass.
+We identify the ingredients that contribute most significantly to $\rhalf-$dependent clustering by building empirical models of galaxy size with various effects included and excluded.
+Stellar mass stripping of satellites has only a mild impact on $\rhalf-$dependent clustering and is unlikely to be the origin of the characteristic shape of the signal.
+On the other hand, correlations between galaxy size and host halo assembly history leave a dramatic imprint on the clustering signal that is strikingly similar in magnitude, $\mstar-$dependence and scale-dependence.
+In the class of models that give the most faithful recovery of the observed clustering signal, galaxy $\rhalf$ is set by the size of the  virial radius at the time the subhalo reaches its peak halo mass, with log-normal scatter in $\rhalf$ that is strongly correlated with the size of the halo scale radius at that time.
 Our results can be treated as a boundary condition for more complex and fine-grained models of galaxy size, and provide a simple means for cosmological surveys to generate synthetic galaxy populations with realistic sizes across the cosmic web.

### 2017-09-28 paper/galsize_paper.tex
Finished sketching all models used in the paper

@@
 \newcommand{\mpeak}{M_{\rm peak}}
+\newcommand{\zpeak}{z_{\rm peak}}
 \newcommand{\mhalo}{M_{\rm halo}}
@@
 
-All numerical values of $\rhalf$ will be quoted in $\kpc,$ and all values of $\mstar$ and $\mhalo$ in $\msun,$ assuming $H_0=67.8~\kms\equiv100h~\kms,$ the best-fit value from \citet{planck15}.
+All numerical values of $\rhalf$ will be quoted in physical $\kpc,$ and all values of $\mstar$ and $\mhalo$ in $\msun,$ assuming $H_0=67.8~\kms\equiv100h~\kms,$ the best-fit value from \citet{planck15}.
 To scale stellar masses to ``$h=1$ units" \citep{croton13}, our numerically quoted values for $\mstar$ should be multiplied by a factor of $h^2,$ while our halo masses and distances should be multiplied by a factor of $h.$
@@
 
+\subsection{Stellar mass model}
+\label{subsec:model}
+
 We map $\mstar$ onto subhalos with the best-fit stellar-to-halo mass relation from \citet{moster_etal13}:
 
-\begin{equation*}
+\begin{equation}
+\label{eq:smhm}
 \langle\mstar/\mhalo\rangle = 2N\left[(\mhalo/M_{1})^{-\beta} + (\mhalo/M_1)^{\gamma}\right]^{-1}.
-\end{equation*}
+\end{equation}
 For halo mass $\mhalo$ we use $\mpeak,$ the largest value of $\mvir$ ever attained along the main progenitor branch of the subhalo.
+
+We additionally explore the potential existence of satellite galaxies that reside in subhalos that are not identified by halo-finder to the present day, so-called ``orphan galaxies" \citep[see, e.g.,][]{campbell_etal17}.
+We use an extension of {\tt Consistent Trees} that models the evolution of subhalos after disruption.
+The phase space evolution of orphans is approximated by following a point mass evolving in the host halo potential according to the orbital parameters of the subhalo at the time of disruption; the evolution of subhalo mass and circular velocity is approximated using the semi-analytic model presented in \citet{jiang_vdB14}.
+
 The values of the best-fit parameters in \citet{moster_etal13} were fit to a stellar mass function (SMF) with values $\mstar^{\rm MPA-JHU}$ based on the MPA-JHU catalog \citep{kauffmann_etal03,brinchmann_etal04}, which differs from the SMF in our galaxy sample \citep[see, e.g.,][]{bernardi_etal14}.
@@
 This results in a typical boost of $\sim0.25$ dex at $\mstar^{\rm MPA-JHU}\approx10^{9.75}\msun,$ and $\sim0.4$ dex at $\mstar^{\rm MPA-JHU}\approx10^{11.5}\msun.$
+
+\subsection{Galaxy size models}
+\label{subsec:model}
 
@@
 Motivated by the simplicity of this scaling relation, we transform the \citet{kravtsov13} into a forward model using {\tt Halotools}.
-For the virial radius of halos and subhalos, we use $\rmpeak,$ the value of $\rvir$ in physical units of $\kpc$ measured at the time of peak subhalo mass.
-When generating Monte Carlo realizations of our model galaxy sizes, we add log-normal scatter $\sigmarhalf=0.15$ dex.
+For the virial radius of halos and subhalos, we use $\rmpeak,$ the value of $\rvir$ in physical units of $\kpc$ measured at the time of peak subhalo mass, defined by
+
+\beq
+\mpeak\equiv\frac{4\pi}{3}\rmpeak^{3}\Delta_{\rm vir}(\zpeak)\rho_{\rm m}(\zpeak)
+\eeq
+
+When generating Monte Carlo realizations of our model galaxy sizes, we add log-normal scatter $\sigmarhalf=0.2$ dex.
+For some models explored in this work, this scatter will be purely stochastic, while other models will introduce a correlation between the scatter and an additional halo property.
+Models employing correlated scatter are implemented using the {\tt halotools.empirical\_models.conditional\_abunmatch} function, which generalizes the Conditional Abundance Matching technique described in \citet{hearin_etal13b}.
+
+We will also consider models for galaxy size in which stellar mass is stripped from satellite galaxies after infall.
+The basis of this class of models is the fitting function presented in \citet{smith_etal16}, which was calibrated by studying stellar mass loss in a suite of high-resolution hydrodynamical simulations.
+In this model, $f_{\ast}$ quantifies the fraction of stellar mass lost as a function of $f_{\rm DM},$ the amount of dark matter that has been stripped since infall:
+
+\beq
+f_{\ast} = 1 - \exp(-14.2f_{\rm DM})
+\eeq
+For $f_{\rm DM}$ we use the ratio of present-day subhalo mass divided by the peak mass, $M_{\rm vir}/M_{\rm peak}.$ If we denote the post-stripping stellar mass as $M_{\ast}',$ then we have $M_{\ast}'\equiv f_{\ast}M_{\ast},$ where $M_{\ast}$ is given by Eq.~\ref{eq:smhm}.
+We then calculate the post-stripping radius by interpolating $\langle\rhalf'\vert\mstar'\rangle$ directly from SDSS data.
 

### 2017-09-29 paper/galsize_paper.tex
Updated models section with subsections

@@
 \newcommand{\rmpeak}{R_{\rm M_{peak}}}
+\newcommand{\vmaxmpeak}{V_{\rm peak}}
 
@@
 
+In \S\ref{sec:results}, we calculate predictions for the $\rhalf-$dependence of galaxy clustering for several different kinds of empirical models, described in turn below.
+
+\subsubsection{K13 model}
+\label{subsubsec:k13model}
+
 In \citet{kravtsov13}, it was found that if a stellar-to-halo mass relation is inverted to map halo mass estimates $\mhalo$ onto SDSS galaxies, and then the $\mhalo-\rvir$ relation is applied to map values of $\rvir$ onto the galaxies, then the resulting $\rhalf-\rvir$ relation of SDSS galaxies exhibits the following linear scaling across a wide range of stellar mass:
@@
 \eeq
+When generating predictions for the K13 model galaxy sizes, we add uncorrelated log-normal scatter of $\sigmarhalf=0.2$ dex to generate a Monto Carlo realization of the model population.
 
-When generating Monte Carlo realizations of our model galaxy sizes, we add log-normal scatter $\sigmarhalf=0.2$ dex.
-For some models explored in this work, this scatter will be purely stochastic, while other models will introduce a correlation between the scatter and an additional halo property.
+\subsubsection{K13 + co-evolution model}
+\label{subsubsec:coevolutionmodel}
+
+The {\em K13 + co-evolution model} model is identical to K13, but the scatter in $\rhalf$ at fixed $\rmpeak$ is no longer purely stochastic, but is instead correlated with $\vmaxmpeak.$
+
+ stochastic, while other models will introduce a correlation between the scatter and an additional halo property.
 Models employing correlated scatter are implemented using the {\tt halotools.empirical\_models.conditional\_abunmatch} function, which generalizes the Conditional Abundance Matching technique described in \citet{hearin_etal13b}.
+
+\subsubsection{K13 + stripping model}
+\label{subsubsec:strippingmodel}
 

### 2017-09-29 paper/galsize_paper.tex
Commented out obsolete shuffle test discussions

@@
 Each panel shows results separately for a different volume-limited $\mstar-$threshold samples.
-Fiducial model predictions appear as the solid curve in each panel.
-}
+See \S\ref{subsec:model} for a description of each model.}
 \label{fig:clustering_ratio_upshot}
@@
 
-We can understand the origin of the shape of the clustering strength ratios shown in Figure~\ref{fig:clustering_ratio_upshot} through a series of straightforward ``shuffle tests".
+%We can understand the origin of the shape of the clustering strength ratios shown in Figure~\ref{fig:clustering_ratio_upshot} through a series of straightforward ``shuffle tests".
 The points with error bars and solid curves in each panel of Fig.\ref{fig:shuffle} are identical to those appearing in Fig.\ref{fig:clustering_ratio_upshot}, although the dynamic range of the y-axis has changed to accommodate the additional curves.
 
-We generated each additional curve by variations on the following exercise.
+%We generated each additional curve by variations on the following exercise.
 In logarithmic bins of $\mpeak$ with width of $0.1$dex, we randomly shuffle the modeled $\rhalf$ values of some particular subpopulation of model galaxies that reside in subhalos in the $\mpeak$ bin.
@@
 
-In the {\em brown, dotted} curves labeled ``all-gal scramble", we shuffle the sizes of {\em all} model galaxies in the $\mpeak$ bin, so that in the resulting mock, galaxy size has no correlation with any subhalo property beyond $\mpeak.$ In particular, the ``all-gal scramble" mock erases the possible influence of a correlation between galaxy size and the redshift at which the subhalo attains peak mass.
+%In the {\em brown, dotted} curves labeled ``all-gal scramble", we shuffle the sizes of {\em all} model galaxies in the $\mpeak$ bin, so that in the resulting mock, galaxy size has no correlation with any subhalo property beyond $\mpeak.$ In particular, the ``all-gal scramble" mock erases the possible influence of a correlation between galaxy size and the redshift at which the subhalo attains peak mass.
 The resulting clustering strength ratios become exactly as predicted by the naive expectation sketched at the conclusion of \S\ref{subsec:predictions}: $\rhalf\propto\rvir\propto\mhalo^{1/3},$ and so large galaxies clustering more strongly relative to small galaxies of comparable stellar mass.
 
-Statistically, there are actually two distinct effects at work in the ``all-gal scramble".
+%Statistically, there are actually two distinct effects at work in the ``all-gal scramble".
 Central and satellite galaxies of similar $\mpeak$ have their sizes shuffled amongst each other, and the potential influence of central galaxy assembly bias is also erased.
@@
 
-For the {\em cyan dashed} curve labeled ``all-cen-scramble", we only shuffle sizes amongst present-day host halos, i.e., amongst subhalos for which Rockstar {\tt upid} equals -1.
+%For the {\em cyan dashed} curve labeled ``all-cen-scramble", we only shuffle sizes amongst present-day host halos, i.e., amongst subhalos for which Rockstar {\tt upid} equals -1.
 For the {\em black dashed} curve labeled ``true-cen-scramble", we only shuffle amongst host halos that have never passed within the virial radius of a larger halo throughout their entire assembly history, i.e., we only shuffle amongst non-backsplash host halos.
@@
 
-We conclude this section by estimating how satellite mass stripping manifests in $\wproj(\rproj).$ To do so, we construct an extension our fiducial model with a simple additional ingredient for post-infall evolution of satellites mass and size.
+%We conclude this section by estimating how satellite mass stripping manifests in $\wproj(\rproj).$ To do so, we construct an extension our fiducial model with a simple additional ingredient for post-infall evolution of satellites mass and size.
 

### 2017-09-29 paper/galsize_paper.tex
Finished abstract. Too long

@@
 \begin{abstract}
-We derive empirical modeling constraints on the connection between dark matter halos and the half-light radius $\rhalf$ of galaxies.
-Using forward-modeling techniques based on {\tt Halotools}, we confirm previous results in Kravtsov (2013) that $\rhalf$ is well-described by a linear scaling relation with halo virial radius.
-Novel to this work, we study galaxy size using new SDSS measurements of the $\rhalf-$dependence of galaxy clustering.
-Smaller galaxies cluster more strongly relative to larger galaxies of the same stellar mass, a new result.
-We show that the $\rhalf-$dependence of galaxy clustering is largely driven by the relative size of central and satellite galaxies: satellites are smaller than centrals of the same halo mass.
-We identify the ingredients that contribute most significantly to $\rhalf-$dependent clustering by building empirical models of galaxy size with various effects included and excluded.
-Stellar mass stripping of satellites has only a mild impact on $\rhalf-$dependent clustering and is unlikely to be the origin of the characteristic shape of the signal.
-On the other hand, correlations between galaxy size and host halo assembly history leave a dramatic imprint on the clustering signal that is strikingly similar in magnitude, $\mstar-$dependence and scale-dependence.
-In the class of models that give the most faithful recovery of the observed clustering signal, galaxy $\rhalf$ is set by the size of the  virial radius at the time the subhalo reaches its peak halo mass, with log-normal scatter in $\rhalf$ that is strongly correlated with the size of the halo scale radius at that time.
+We derive empirical modeling constraints on the connection between dark matter halos and the half-light radius of galaxies, $\rhalf.$ Novel to this work, we study galaxy size using new SDSS measurements of the $\rhalf-$dependence of galaxy clustering.
+We find that smaller galaxies cluster stronger relative to larger galaxies of the same stellar mass, a new result.
+We show that the $\rhalf-$dependence of galaxy clustering is largely driven by centrals being larger than satellite galaxies of the same halo mass.
+Stellar mass stripping of satellites has only a mild impact and is unlikely to be the origin of the characteristic magnitude and shape of the clustering signal.
+Much more successful models are based on the assumption that the mean galaxy profile {\em and its scatter} are correlated with the formation history of the dark matter halo profile.
+Based on our present findings, we predict that at fixed $\mhalo,$ galaxies with relatively shallow surface brightness profiles reside in relative low-concentration halos, and conversely.
+In the class of models that give the most faithful recovery of the observed clustering signal, galaxy $\rhalf$ is set by the size of the  virial radius at the time the subhalo reaches its peak halo mass, with log-normal scatter in $\rhalf$ that is strongly correlated with the halo scale radius $R_{\rm s}$ at that time.
 Our results can be treated as a boundary condition for more complex and fine-grained models of galaxy size, and provide a simple means for cosmological surveys to generate synthetic galaxy populations with realistic sizes across the cosmic web.
 \end{abstract}
+%Using forward-modeling techniques based on {\tt Halotools}, we confirm previous results in Kravtsov (2013) that $\rhalf$ is well-described by a linear scaling relation with halo virial radius.
 

### 2017-09-29 paper/galsize_paper.tex
Tightened up abstract

@@
 We derive empirical modeling constraints on the connection between dark matter halos and the half-light radius of galaxies, $\rhalf.$ Novel to this work, we study galaxy size using new SDSS measurements of the $\rhalf-$dependence of galaxy clustering.
-We find that smaller galaxies cluster stronger relative to larger galaxies of the same stellar mass, a new result.
-We show that the $\rhalf-$dependence of galaxy clustering is largely driven by centrals being larger than satellite galaxies of the same halo mass.
-Stellar mass stripping of satellites has only a mild impact and is unlikely to be the origin of the characteristic magnitude and shape of the clustering signal.
-Much more successful models are based on the assumption that the mean galaxy profile {\em and its scatter} are correlated with the formation history of the dark matter halo profile.
-Based on our present findings, we predict that at fixed $\mhalo,$ galaxies with relatively shallow surface brightness profiles reside in relative low-concentration halos, and conversely.
-In the class of models that give the most faithful recovery of the observed clustering signal, galaxy $\rhalf$ is set by the size of the  virial radius at the time the subhalo reaches its peak halo mass, with log-normal scatter in $\rhalf$ that is strongly correlated with the halo scale radius $R_{\rm s}$ at that time.
+Smaller galaxies cluster stronger relative to larger galaxies of the same stellar mass, a new result.
+We show that this clustering signal is largely driven by centrals being larger than satellite galaxies of the same halo mass.
+We build a simple model in which $\rhalf$ is set by the halo virial radius $\rvir$ at the time the halo reaches its peak mass, with scatter in $\rhalf$ that is strongly correlated with the halo scale radius $R_{\rm s}$ at that time.
+The $\rhalf-$dependent clustering of this model is strikingly similar to our SDSS measurements in magnitude, scale-dependence, and $\mstar-$dependence.
+Together with the result that stellar mass stripping of satellites has only a mild impact on $\rhalf-$dependent clustering, this suggests that the relative size of centrals and satellites is already in place at the time of satellite infall, and supports the notion that $L_{\ast}$ galaxy and halo profiles co-evolve across many Gyr of cosmic time.
 Our results can be treated as a boundary condition for more complex and fine-grained models of galaxy size, and provide a simple means for cosmological surveys to generate synthetic galaxy populations with realistic sizes across the cosmic web.
 \end{abstract}
-%Using forward-modeling techniques based on {\tt Halotools}, we confirm previous results in Kravtsov (2013) that $\rhalf$ is well-described by a linear scaling relation with halo virial radius.
 

### 2017-09-29 paper/galsize_paper.tex
Reworked model desription section

@@
 We show that this clustering signal is largely driven by centrals being larger than satellite galaxies of the same halo mass.
-We build a simple model in which $\rhalf$ is set by the halo virial radius $\rvir$ at the time the halo reaches its peak mass, with scatter in $\rhalf$ that is strongly correlated with the halo scale radius $R_{\rm s}$ at that time.
+We use {\tt Halotools} to build a forward model of galaxy size in which $\rhalf$ is set by the halo virial radius $\rvir$ at the time the halo reaches its peak mass, with scatter in $\rhalf$ that is strongly correlated with the halo scale radius $R_{\rm s}$ at that time.
 The $\rhalf-$dependent clustering of this model is strikingly similar to our SDSS measurements in magnitude, scale-dependence, and $\mstar-$dependence.
@@
 In the version of this catalog that we use, two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile to determine the half-light radius $\rhalf.$ We apply the \citet{bell_etal03} mass-to-light ratio to the $r-$band flux and $g-r$ colors in this catalog to obtain an estimate for the total stellar mass $\mstar$ of every galaxy.
-
 We calculate two-point clustering $\wproj$ of our SDSS galaxy sample using line-of-sight projection of $\pi_{\rm max}=20\mpc$ using the {\tt correl} program in {\tt UniverseMachine}.
-Our results in \S~\ref{sec:results} will give special focus on the dependence of $\wproj$ upon $\rhalf.$ We will quantify this dependence in terms of {\em clustering ratios} of ``large" vs.
-``small" galaxies, defined according to whether composite galaxy size is above or below $\langle\rhalf\vert\mstar\rangle,$ computed as the median of a sliding stellar mass window with a width of $N_{\rm gal}=1000.$
 
 As the bedrock of our modeling, we use the catalog of {\tt Rockstar} subhalos identified at $z=0$ in the Bolshoi-Planck simulation \citep{klypin_etal11,behroozi12_rockstar,behroozi12_consistent_trees,riebe_etal13,rodriguez_puebla16_bolplanck}.
-the particular version of the catalog we use is made publicly available through {\tt Halotools} \citep{hearin_etal16}, with {\tt version\_name} = `halotools\_v0p4'.
+The particular version of the catalog we use is made publicly available through {\tt Halotools} \citep{hearin_etal16}, with {\tt version\_name} = `halotools\_v0p4'.
+
+We additionally explore the potential existence of satellite galaxies that reside in subhalos that are not identified by halo-finder to the present day, so-called ``orphan galaxies" \citep[see, e.g.,][]{campbell_etal17}.
+We use an extension of {\tt Consistent Trees} that models the evolution of subhalos after disruption.
+The phase space evolution of orphans is approximated by following a point mass evolving in the host halo potential according to the orbital parameters of the subhalo at the time of disruption; the evolution of subhalo mass and circular velocity is approximated using the semi-analytic model presented in \citet{jiang_vdB14}.
+
 For mock galaxies, to compute galaxy clustering we employ the distant observer approximation by treating the simulation $z-$axis as the line-of-sight.
@@
 For halo mass $\mhalo$ we use $\mpeak,$ the largest value of $\mvir$ ever attained along the main progenitor branch of the subhalo.
-
-We additionally explore the potential existence of satellite galaxies that reside in subhalos that are not identified by halo-finder to the present day, so-called ``orphan galaxies" \citep[see, e.g.,][]{campbell_etal17}.
-We use an extension of {\tt Consistent Trees} that models the evolution of subhalos after disruption.
-The phase space evolution of orphans is approximated by following a point mass evolving in the host halo potential according to the orbital parameters of the subhalo at the time of disruption; the evolution of subhalo mass and circular velocity is approximated using the semi-analytic model presented in \citet{jiang_vdB14}.
 
@@
 
-The {\em K13 + co-evolution model} model is identical to K13, but the scatter in $\rhalf$ at fixed $\rmpeak$ is no longer purely stochastic, but is instead correlated with $\vmaxmpeak.$
-
- stochastic, while other models will introduce a correlation between the scatter and an additional halo property.
-Models employing correlated scatter are implemented using the {\tt halotools.empirical\_models.conditional\_abunmatch} function, which generalizes the Conditional Abundance Matching technique described in \citet{hearin_etal13b}.
+The {\em K13 + co-evolution model} model is identical to K13, but the scatter in $\rhalf$ at fixed $\rmpeak$ is no longer purely stochastic, but is instead correlated with $\vmaxmpeak.$ We implement scatter correlations using the {\tt halotools.empirical\_models.conditional\_abunmatch} function, which generalizes the Conditional Abundance Matching technique described in \citet{hearin_etal13b}.
 
@@
 
-In \S\ref{subsec:predictions} we show comparisons between the galaxy size model described in \S\ref{sec:model} and our SDSS sample.
-We identify the key ingredients that determine the characteristic $\rhalf-$dependence of galaxy clustering in \S\ref{subsec:subsec:shuffle_tests}.
-In so doing, we demonstrate the sensitivity of galaxy clustering measurements to the underlying model assumptions, establishing the success of our model as non-trivial.
+In \S\ref{subsec:predictions} we show comparisons between the galaxy size models described in \S\ref{sec:model} and our SDSS sample.
 

### 2017-09-29 paper/galsize_paper.tex
Updated results section

@@
 
-In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ Scattered gray points show the scaling relation for our SDSS galaxy sample, while the black curve shows the median relation $\langle\rhalf\vert\mstar\rangle$ implied by the model described in \S\ref{sec:model}.
+In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ Scattered gray points show the scaling relation for our SDSS galaxy sample, while the black curve shows the median relation $\langle\rhalf\vert\mstar\rangle$ implied by the K13 model described in \S\ref{sec:model}.
 
@@
 These ratios are the measurements appearing on the y-axis in each panel of Figure \ref{fig:clustering_ratio_upshot}.
-Points with error bars show SDSS measurements, solid curves show the clustering ratios of model galaxies as predicted by the model described in \S\ref{sec:model}.
-Before unpacking the information contained in these clustering measurements, we stress that the good agreement shown between model and data in Figure~\ref{fig:clustering_ratio_upshot} is a genuine model prediction, since the model parameters were taken directly from \citet{kravtsov13}, which were fit to the one-point measurements in Fig.~\ref{fig:scatter_plot}, whereas the two-point measurements appearing in Figure \ref{fig:clustering_ratio_upshot} have heretofore never been measured.
+Points with error bars show SDSS measurements, solid curves show the clustering ratios of model galaxies as predicted by the models described in \S\ref{sec:model}.
 
@@
 This result may be surprising, since $\rhalf\propto\rvir,$ halo mass $\rvir\propto\mhalo^{1/3},$ and clustering strength increases with $\mvir.$ Based on this simple argument, one would expect the opposite trend to the measurements shown here.
-We present a resolution to this puzzle in the following section.
+
+A straightforward resolution to this puzzle is shown in Figure \ref{fig:censatsizehist}.
 
@@
 }
-\label{fig:shuffle}
+\label{fig:censatsizehist}
 \end{figure}

### 2017-09-29 paper/galsize_paper.tex
Revised abstract

@@
 Smaller galaxies cluster stronger relative to larger galaxies of the same stellar mass, a new result.
-We show that this clustering signal is largely driven by centrals being larger than satellite galaxies of the same halo mass.
-We use {\tt Halotools} to build a forward model of galaxy size in which $\rhalf$ is set by the halo virial radius $\rvir$ at the time the halo reaches its peak mass, with scatter in $\rhalf$ that is strongly correlated with the halo scale radius $R_{\rm s}$ at that time.
-The $\rhalf-$dependent clustering of this model is strikingly similar to our SDSS measurements in magnitude, scale-dependence, and $\mstar-$dependence.
+We use {\tt Halotools} to test a collection of forward models of galaxy size to identify the qualitative ingredients needed to reproduce the observed clustering.
+We show that the $\rhalf-$dependence of galaxy clustering is largely driven by centrals being larger than satellite galaxies of the same halo mass.
+Models in which $\rhalf$ is determined by stellar mass $\mstar$ exhibit qualitatively discrepant clustering properties from SDSS galaxies.
+Models where $\rhalf$ is linearly proportional to halo virial radius $\rvir$ at the time of peak halo mass are much more successful, provided that scatter in $\rhalf$ is strongly correlated with the halo scale radius $R_{\rm s}$ at that time.
 Together with the result that stellar mass stripping of satellites has only a mild impact on $\rhalf-$dependent clustering, this suggests that the relative size of centrals and satellites is already in place at the time of satellite infall, and supports the notion that $L_{\ast}$ galaxy and halo profiles co-evolve across many Gyr of cosmic time.
-Our results can be treated as a boundary condition for more complex and fine-grained models of galaxy size, and provide a simple means for cosmological surveys to generate synthetic galaxy populations with realistic sizes across the cosmic web.
+%Our results can be treated as a boundary condition for more complex and fine-grained models of galaxy size, and provide a simple means for cosmological surveys to generate synthetic galaxy populations with realistic sizes across the cosmic web.
 \end{abstract}

### 2017-10-02 galsize_models/models/load_baseline_catalogs.py
Added orphan testing notebook

@@ -54,23 +54,35 @@ def load_baseline_halocat(simname='bolplanck', redshift=0, fixed_seed=411):
 
 
 def moster13_based_mock(halocat=None, keys_to_keep=moster13_halocat_keys,
-            scatter_ordinates=(0.4, 0.3, 0.5), **moster13_params):
+            scatter_ordinates=(0.4, 0.3, 0.5), mpeak_key='halo_mpeak',
+            zpeak_key='halo_zpeak', **moster13_params):
     """
     """
     if halocat is None:
         halocat = load_baseline_halocat()
+    else:
+        rvir_peak_physical_unity_h = halo_mass_to_halo_radius(halocat.halo_table[mpeak_key],
+                                    halocat.cosmology, halocat.halo_table[zpeak_key], 'vir')
+        rvir_peak_physical = rvir_peak_physical_unity_h/halocat.cosmology.h
+        halocat.halo_table['halo_rvir_zpeak'] = rvir_peak_physical*1000.
+
 
     model = Moster13SmHm()
     model.param_dict.update(moster13_params)
 
     mean_mstar_unity_h = model.mean_stellar_mass(
-            prim_haloprop=halocat.halo_table['halo_mpeak'],
-            redshift=halocat.halo_table['halo_zpeak'])
+            prim_haloprop=halocat.halo_table[mpeak_key],
+            redshift=halocat.halo_table[zpeak_key])
 
     mean_mstar = mean_mstar_unity_h/halocat.cosmology.h/halocat.cosmology.h
     mean_logmstar = np.log10(mean_mstar)
 
-    mc_logmstar = norm.isf(1-halocat.halo_table['halo_uran'], loc=mean_logmstar,
+    try:
+        uran = halocat.halo_table['halo_uran']
+    except KeyError:
+        uran = np.random.rand(len(halocat.halo_table))
+
+    mc_logmstar = norm.isf(1-uran, loc=mean_logmstar,
             scale=model.param_dict[u'scatter_model_param1'])
 
     #  Apply M* correction to account for Meert+15 photometry differences

### 2017-10-02 galsize_models/measurements/load_cross_matched_umachine.py
Fixed bugs in testing of obsolete functions

@@ -14,7 +14,7 @@ def load_umachine_sdss_with_meert15(datadir=default_datadir):
     """
     Examples
     --------
-    >>> full_sdss, is_complete = load_umachine_sdss_with_meert15()
+    >>> full_sdss, is_complete, has_profile = load_umachine_sdss_with_meert15()
     """
     basename = "umachine_sdss_dr10_meert15.hdf5"
     fname = os.path.join(datadir, basename)

### 2017-10-02 galsize_models/models/mcmc_bulge_disk_double_power_law.py

@@ -9,7 +9,10 @@ from ..measurements.sdss_covariance import sdss_measurements_and_cov, logsm_bins
 from ..models.load_baseline_catalogs import load_umachine_mock
 
 
-mock = load_umachine_mock()
+try:
+    mock = load_umachine_mock()
+except:
+    pass
 
 sdss_data_vector, sdss_cov = sdss_measurements_and_cov()
 sdss_invcov = np.linalg.inv(sdss_cov)
@@ -29,4 +32,7 @@ def lnprob(params, observations, icov, mock, logsm_bins):
         return lnlike(params, observations, icov, mock, logsm_bins) + prior
 
 
-lnprob_args = tuple((sdss_data_vector, sdss_invcov, mock, logsm_bins))
+try:
+    lnprob_args = tuple((sdss_data_vector, sdss_invcov, mock, logsm_bins))
+except:
+    pass

### 2017-10-02 galsize_models/measurements/measure_sdss_clustering.py
Modified clustering calculations to additionally store the jackknife errors

@@ -96,16 +96,12 @@ def save_wp_measurement(sample, output_dirname, output_basename, sm_low, sm_high
     msg = "Measuring wp for {0} sample of {1} galaxies"
     print(msg.format(output_basename, len(sample)))
 
-    rp, wp, _wperr = measure_wp(sample, sm_low, sm_high, output_dirname)
-
-    # temp_ascii_fname = os.path.join(output_dirname, 'tmp.dat')
-    # write_umachine_ascii(sample, temp_ascii_fname, overwrite=True)
-
-    # _results = get_wp_measurements(temp_ascii_fname, sm_low, sm_high, pi_max)
-    # rp, wp, _wperr = _results[:, 0], _results[:, 1], _results[:, 2]
+    rp, wp, wperr = measure_wp(sample, sm_low, sm_high, output_dirname)
 
     rp_fname = os.path.join(output_dirname, output_basename+'_rp')
     wp_fname = os.path.join(output_dirname, output_basename+'_wp')
+    wperr_fname = os.path.join(output_dirname, output_basename+'_wperr')
     np.save(wp_fname, wp)
+    np.save(wperr_fname, wperr)
     np.save(rp_fname, rp)
 

### 2017-10-02 galsize_models/measurements/sdss_measurements.py
Added sdss_measurements convenience module

@@ -1,0 +1,44 @@
+"""
+"""
+import numpy as np
+import os
+
+repo_dirname = "/Users/aphearin/work/repositories/python/galsize_models"
+output_subdirname = "galsize_models/measurements/data/two_point_functions"
+output_dirname = os.path.join(repo_dirname, output_subdirname)
+
+rp = np.load(os.path.join(output_dirname, 'sdss_sm9p75_smbell_rp.npy'))
+wp_sdss_sm9p75_smbell = np.load(os.path.join(output_dirname, 'sdss_sm9p75_smbell_wp.npy'))
+wp_sdss_sm9p75_smbell_small = np.load(os.path.join(output_dirname, 'sdss_sm9p75_smbell_small_wp.npy'))
+wp_sdss_sm9p75_smbell_large = np.load(os.path.join(output_dirname, 'sdss_sm9p75_smbell_large_wp.npy'))
+fracdiff_sm9p75_smbell = (wp_sdss_sm9p75_smbell_large-wp_sdss_sm9p75_smbell_small)/wp_sdss_sm9p75_smbell
+
+wp_sdss_sm10p0_smbell = np.load(os.path.join(output_dirname, 'sdss_sm10p0_smbell_wp.npy'))
+wp_sdss_sm10p0_smbell_small = np.load(os.path.join(output_dirname, 'sdss_sm10p0_smbell_small_wp.npy'))
+wp_sdss_sm10p0_smbell_large = np.load(os.path.join(output_dirname, 'sdss_sm10p0_smbell_large_wp.npy'))
+fracdiff_sm10p0_smbell = (wp_sdss_sm10p0_smbell_large-wp_sdss_sm10p0_smbell_small)/wp_sdss_sm10p0_smbell
+
+wp_sdss_sm10p25_smbell = np.load(os.path.join(output_dirname, 'sdss_sm10p25_smbell_wp.npy'))
+wp_sdss_sm10p25_smbell_small = np.load(os.path.join(output_dirname, 'sdss_sm10p25_smbell_small_wp.npy'))
+wp_sdss_sm10p25_smbell_large = np.load(os.path.join(output_dirname, 'sdss_sm10p25_smbell_large_wp.npy'))
+fracdiff_sm10p25_smbell = (wp_sdss_sm10p25_smbell_large-wp_sdss_sm10p25_smbell_small)/wp_sdss_sm10p25_smbell
+
[…]

### 2017-10-02 galsize_models/measurements/sdss_measurements.py
Added errors to convenience module

@@ -7,38 +7,33 @@ repo_dirname = "/Users/aphearin/work/repositories/python/galsize_models"
 output_subdirname = "galsize_models/measurements/data/two_point_functions"
 output_dirname = os.path.join(repo_dirname, output_subdirname)
 
+cutoff_err = 0.2
+
 rp = np.load(os.path.join(output_dirname, 'sdss_sm9p75_smbell_rp.npy'))
 wp_sdss_sm9p75_smbell = np.load(os.path.join(output_dirname, 'sdss_sm9p75_smbell_wp.npy'))
+wperr_sdss_sm9p75_smbell = np.load(os.path.join(output_dirname, 'sdss_sm9p75_smbell_wperr.npy'))
 wp_sdss_sm9p75_smbell_small = np.load(os.path.join(output_dirname, 'sdss_sm9p75_smbell_small_wp.npy'))
 wp_sdss_sm9p75_smbell_large = np.load(os.path.join(output_dirname, 'sdss_sm9p75_smbell_large_wp.npy'))
 fracdiff_sm9p75_smbell = (wp_sdss_sm9p75_smbell_large-wp_sdss_sm9p75_smbell_small)/wp_sdss_sm9p75_smbell
-
-wp_sdss_sm10p0_smbell = np.load(os.path.join(output_dirname, 'sdss_sm10p0_smbell_wp.npy'))
-wp_sdss_sm10p0_smbell_small = np.load(os.path.join(output_dirname, 'sdss_sm10p0_smbell_small_wp.npy'))
-wp_sdss_sm10p0_smbell_large = np.load(os.path.join(output_dirname, 'sdss_sm10p0_smbell_large_wp.npy'))
-fracdiff_sm10p0_smbell = (wp_sdss_sm10p0_smbell_large-wp_sdss_sm10p0_smbell_small)/wp_sdss_sm10p0_smbell
+fracdiff_sm9p75_smbell_err = np.maximum(np.sqrt(wperr_sdss_sm9p75_smbell)/wp_sdss_sm9p75_smbell, cutoff_err)
 
 wp_sdss_sm10p25_smbell = np.load(os.path.join(output_dirname, 'sdss_sm10p25_smbell_wp.npy'))
+wperr_sdss_sm10p25_smbell = np.load(os.path.join(output_dirname, 'sdss_sm10p25_smbell_wperr.npy'))
[…]

### 2017-10-02 galsize_models/models/load_baseline_catalogs.py
Added penultimate one-point distribution plot

@@ -1,5 +1,6 @@
 """
 """
+import os
 import numpy as np
 from scipy.stats import norm
 from halotools.empirical_models import Moster13SmHm
@@ -16,7 +17,8 @@ from .random_bt_assignment import value_add_random_bt
 from ..measurements import load_umachine_sdss_with_meert15
 
 
-__all__ = ('moster13_based_mock', 'load_umachine_mock', 'load_baseline_halocat')
+__all__ = ('moster13_based_mock', 'load_umachine_mock', 'load_baseline_halocat',
+        'load_orphan_mock')
 
 default_umachine_galprops = list((
     'sm', 'sfr', 'obs_sm', 'obs_sfr', 'icl', 'halo_id', 'upid',
@@ -136,3 +138,42 @@ def load_umachine_mock(galprops=default_umachine_galprops, Lbox=250):
     sdss = full_sdss[mask]
 
     return value_add_random_bt(mock, sdss)
+
+
+def load_orphan_mock():
+
+    dirname = "/Users/aphearin/work/sims/bolplanck/orphan_catalog_z0"
+    basename = "cross_matched_orphan_catalog.hdf5"
+
+    halo_table = Table.read(os.path.join(dirname, basename), path='data')
+
+    halo_table['vmax_at_mpeak_percentile'] = np.load(
+        os.path.join(dirname, 'vmax_percentile.npy'))
+
+    halo_table['zpeak'] = 1./halo_table['mpeak_scale']-1.
+
+    class HaloCatalog(object):
+        def __init__(self, halo_table):
+            self.halo_table = halo_table
+            self.cosmology = Planck15
+            for key in self.halo_table.keys():
+                if key[:5] != 'halo_':
+                    halo_table.rename_column(key, 'halo_'+key)
+
+    halocat = HaloCatalog(halo_table)
+
+    from galsize_models.models import moster13_based_mock
+
+    keys_to_keep=list(halocat.halo_table.keys())
+    keys_to_keep.append('halo_rvir_zpeak')
+
+    mock = moster13_based_mock(halocat=halocat, mpeak_key='halo_mpeak', zpeak_key='halo_zpeak',
+                              keys_to_keep=keys_to_keep)
+
+    from halotools.empirical_models import noisy_percentile
+
+    mock['noisy_vmax_at_mpeak_percentile'] = noisy_percentile(
+        mock['vmax_at_mpeak_percentile'], 0.5)
+
+    return mock
+

### 2017-10-02 paper/galsize_paper.tex
Updated paper figures

@@
 \centering
-\includegraphics[width=8cm]{FIGS/single_component_model_vs_sdss_one_point.pdf}
+\includegraphics[width=8cm]{FIGS/rhalf_vs_mstar_fiducial_model.pdf}
 \caption{
@@
 \centering
-\includegraphics[width=8cm]{FIGS/size_clustering_ratios_stripping_coevolution.pdf}
+\includegraphics[width=8cm]{FIGS/penultimate_clustering_ratios_no_orphans.pdf}
 \caption{
@@
 \centering
-\includegraphics[width=8cm]{FIGS/sat_vs_cen_sizes_fracdiff.pdf}
+\includegraphics[width=8cm]{FIGS/penultimate_clustering_ratios_alternate_models.pdf}
 \caption{
-{\bf Origin of the $\rhalf-$dependence of clustering.}
-Here we compare our fiducial model, in which satellite galaxy size is set by $\rvir$ at the time of infall, to a set of alternative models created by shuffling the sizes of various subsamples of the fiducial mock.
+{\bf Impact of mass loss and orphan satellites.}
+Here we compare our fiducial model, \dots 
 }

### 2017-10-02 paper/galsize_paper.tex
Updated figures with correct axis labels

@@
 
-\title[The Emergent Simplicity of Galaxy Size]
-{The Emergent Simplicity of Galaxy Size}
+\title[On the Galaxy Size-Halo Connection]
+{Empirical Modeling Constraints on the Galaxy Size-Halo Connection}
 
@@
 
+%---------------------------------------------------------------------------------------------------
+\begin{figure}
+\centering
+\includegraphics[width=8cm]{FIGS/rs_correlation_visual.pdf}
+\caption{
+{\bf Illustration of galaxy \& halo profile co-evolution.}
+}
+\label{fig:coevolution}
+\end{figure}
+%-----------------------------------------------------------------------------------------------------
+
 %Figure~\ref{fig:satellites} compares the clustering ratios of our fiducial model (solid curves) to the clustering ratios of this alternative model (dashed curves).

### 2017-10-03 paper/galsize_paper.tex
Updated model descriptions

--- 2017-10-02 paper/galsize_paper.tex
@@
 \newcommand{\mpeak}{M_{\rm peak}}
-\newcommand{\zpeak}{z_{\rm peak}}
+\newcommand{\zpeak}{z_{M_{\rm peak}}}
 \newcommand{\mhalo}{M_{\rm halo}}
@@
 \newcommand{\vmaxmpeak}{V_{\rm peak}}
+\newcommand{\vmax}{V_{\rm max}}
+\newcommand{\rspeak}{{R_{\rm s,}}_{\rm M_{peak}}}
 
@@
 
-\title[The Emergent Simplicity of Galaxy Size]
-{The Emergent Simplicity of Galaxy Size}
+\title[Forward Modeling Galaxy Size]
+{Forward Modeling Galaxy Size in a Cosmological Context}
 
@@
 Models in which $\rhalf$ is determined by stellar mass $\mstar$ exhibit qualitatively discrepant clustering properties from SDSS galaxies.
-Models where $\rhalf$ is linearly proportional to halo virial radius $\rvir$ at the time of peak halo mass are much more successful, provided that scatter in $\rhalf$ is strongly correlated with the halo scale radius $R_{\rm s}$ at that time.
+Models where $\rhalf$ is linearly proportional to halo virial radius $\rvir$ at the time of peak halo mass are much more successful, provided that scatter in $\rhalf$ is significantly correlated with the halo scale radius $R_{\rm s}$ at that time.
 Together with the result that stellar mass stripping of satellites has only a mild impact on $\rhalf-$dependent clustering, this suggests that the relative size of centrals and satellites is already in place at the time of satellite infall, and supports the notion that $L_{\ast}$ galaxy and halo profiles co-evolve across many Gyr of cosmic time.
@@
 \subsection{Stellar mass model}
-\label{subsec:model}
+\label{subsec:smhm}
 
@@
 
-\subsubsection{K13 model}
-\label{subsubsec:k13model}
+\subsubsection{$\mstar-$only model}
+\label{subsubsec:mstaronlymodel}
+
+In the first class of models we explore, we suppose that stellar mass $\mstar$ is the statistical regulator of $\rhalf,$ so that galaxy sizes are drawn from a log-normal distribution centered at $\langle\rhalf\vert\mstar\rangle,$ where $\mstar$ derives from the \citet{moster_etal13} relation described above in \S\ref{subsec:smhm}.
+To implement this model, for simplicity we directly tabulate $\langle\rhalf\vert\mstar\rangle$ from the data, rather than pursue a parametric form \citep[see, e.g.,][]{zhang_yang17}.
+
+\subsubsection{$\rvir-$only model}
+\label{subsubsec:rvirmodel}
 
@@
 \beq
-\mpeak\equiv\frac{4\pi}{3}\rmpeak^{3}\Delta_{\rm vir}(\zpeak)\rho_{\rm m}(\zpeak)
+\mpeak\equiv\frac{4\pi}{3}\rmpeak^{3}\Delta_{\rm vir}(\zpeak)\rho_{\rm m}(\zpeak), 
 \eeq
-When generating predictions for the K13 model galaxy sizes, we add uncorrelated log-normal scatter of $\sigmarhalf=0.2$ dex to generate a Monto Carlo realization of the model population.
+where for $\Delta_{\rm vir}(\zpeak)$ we use the fitting function to the ``virial" definition used in \citet{bryan_norman98}.
+For the model we refer to as the ``$\rvir-$only model", we add uncorrelated log-normal scatter of $\sigmarhalf=0.2$ dex to generate a Monto Carlo realization of the model population.
 
-\subsubsection{K13 + co-evolution model}
+\subsubsection{Profile co-evolution model}
 \label{subsubsec:coevolutionmodel}
 
-The {\em K13 + co-evolution model} model is identical to K13, but the scatter in $\rhalf$ at fixed $\rmpeak$ is no longer purely stochastic, but is instead correlated with $\vmaxmpeak.$ We implement scatter correlations using the {\tt halotools.empirical\_models.conditional\_abunmatch} function, which generalizes the Conditional Abundance Matching technique described in \citet{hearin_etal13b}.
+The ``profile co-evolution" model is identical to the $\rvir-$only model, but the scatter in $\rhalf$ at fixed $\rmpeak$ is no longer purely stochastic, and is instead correlated with $\vmaxmpeak,$ defined as the value of $\vmax$ at $\zpeak.$ In this way, $\rmpeak$ statistically determines the distribution of available sizes, but halos with extended dark matter profiles and large scale radii $R_{\rm s}$ host galaxies with above-average sizes, while halos with small $R_{\rm s}$ host smaller galaxies.
+See Figure \ref{fig:coevolutionmodel} for a visual illustration of this residual correlation.
+We implement scatter correlations using the {\tt halotools.empirical\_models.conditional\_abunmatch} function, which generalizes the Conditional Abundance Matching technique described in \citet{hearin_etal13b}.
 
-\subsubsection{K13 + stripping model}
+%---------------------------------------------------------------------------------------------------
+\begin{figure}
+\centering
+\includegraphics[width=8cm]{FIGS/rs_correlation_visual.pdf}
+\caption{
+{\bf Profile co-evolution model.} In this model, the log-normal distribution of galaxy sizes is determined by $\rmpeak,$ the physical size of the halo virial radius at the time the halo reaches its peak mass.
+Thus log-normal the shape of this curve is determined by $\langle\rhalf\vert\rmpeak\rangle=0.0125\rmpeak$ with $0.2$ dex of scatter.
+The profile co-evolution model further supposes that galaxy and halo profiles co-evolve across cosmic time.
+Thus within this log-normal distribution, for two halos with the same $\rmpeak,$ halos with larger scale radius at $\zpeak$ will host galaxies with above-average $\rhalf,$ and conversely for halos with smaller values of $\rspeak.$
+}
+\label{fig:coevolutionmodel}
+\end{figure}
+%-----------------------------------------------------------------------------------------------------
+
+\subsubsection{$\mstar-$stripping model}
 \label{subsubsec:strippingmodel}
 
-We will also consider models for galaxy size in which stellar mass is stripped from satellite galaxies after infall.
+As we will show in \S\ref{sec:results}, the chief ingredient needed to recover the observed clustering properties of galaxies is that satellites need to be smaller than centrals of comparable halo mass.
+Thus it is natural to consider a class of models in which stellar mass is stripped from satellite galaxies after infall.
+
 The basis of this class of models is the fitting function presented in \citet{smith_etal16}, which was calibrated by studying stellar mass loss in a suite of high-resolution hydrodynamical simulations.
@@
 
-In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ Scattered gray points show the scaling relation for our SDSS galaxy sample, while the black curve shows the median relation $\langle\rhalf\vert\mstar\rangle$ implied by the K13 model described in \S\ref{sec:model}.
+In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ The black curve enveloped by the gray bands show the scaling relation for our SDSS galaxy sample, while the blue curve shows the median relation $\langle\rhalf\vert\mstar\rangle$ implied by the profile co-evolution model described in \S\ref{sec:model}.
+This figure shows that models in which $\rhalf\propto\rvir$ can naturally give rise to the characteristic curvature in the $\langle\rhalf\vert\mstar\rangle$ relation, confirming the results in \citet{kravtsov13} in a forward modeling context.
 
@@
 \includegraphics[width=8cm]{FIGS/rhalf_vs_mstar_fiducial_model.pdf}
-\caption{
-{\bf One-point data used to fit the fiducial model.}
-Scattered points show the $\rhalf-\mstar$ relation for SDSS galaxies as measured in \citet{meert_etal15}.
-The black curve shows the median $\rhalf-\mstar$ relation implied by the model described in \S\ref{sec:model}, in which $\rhalf=0.0125\rvir.$ This figure confirms the findings in \citet{kravtsov13} that a linear relationship between $\rvir$ and $\rhalf,$ convolved against the nonlinear relationships between $\rvir, \mhalo$ and $\mstar,$ correctly predicts the characteristic curvature in the relation $\langle\rhalf\vert\mstar\rangle$ over a wide range in stellar mass.
+\caption{The black curve shows the median $\rhalf-\mstar$ relation SDSS galaxies as measured in \citet{meert_etal15}.
+The two gray bands enveloping the black curve show the $50\%$ and $90\%$ percentile regions.
+The blue curve shows profile co-evolution model in which $\langle\rhalf\vert\rvir\rangle=0.0125\rvir,$ as in \citet{kravtsov13}.
+This figure confirms that a linear relationship between $\rvir$ and $\rhalf,$ convolved against the nonlinear relationships between $\rvir, \mhalo$ and $\mstar,$  predicts the characteristic curvature in the relation $\langle\rhalf\vert\mstar\rangle$ over a wide range in mass.
 }

### 2017-10-03 paper/galsize_paper.tex
Updated figure 4 caption

@@
 
-In \S\ref{subsec:predictions} we show comparisons between the galaxy size models described in \S\ref{sec:model} and our SDSS sample.
-
-\subsection{Testing Model Predictions}
-\label{subsec:predictions}
-
 In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ The black curve enveloped by the gray bands show the scaling relation for our SDSS galaxy sample, while the blue curve shows the median relation $\langle\rhalf\vert\mstar\rangle$ implied by the profile co-evolution model described in \S\ref{sec:model}.
@@
 These ratios are the measurements appearing on the y-axis in each panel of Figure \ref{fig:clustering_ratio_upshot}.
-Points with error bars show SDSS measurements, solid curves show the clustering ratios of model galaxies as predicted by the models described in \S\ref{sec:model}.
+Points with jackknife-estimated error bars show SDSS measurements, solid curves show the clustering ratios of model galaxies as predicted by the models described in \S\ref{sec:model}.
 
@@
 
-\subsection{Origin of the size-dependence of galaxy clustering}
-\label{subsec:shuffle_tests}
-
 %---------------------------------------------------------------------------------------------------
@@
 \caption{
-{\bf Relative sizes of centrals and satellites.} In a narrow bin of halo mass $\mhalo=\mpeak\approx10^{12}\msun,$ we show the distribution of model galaxy sizes for different subpopulations galaxies.
+{\bf Relative sizes of centrals and satellites.} In a narrow bin of halo mass $\mhalo=\mpeak\approx10^{12}\msun,$ we show the distribution of model galaxy sizes for different subpopulations galaxies, as predicted by the $\rvir-$only model.
 The red histogram shows the sizes of satellites; the blue histogram shows host halos that have never passed inside the virial radius of a larger halo (``true centrals"); the green histogram host halos that were subhalos inside a larger at some point in their past history (``splashback halos").
-In the fiducial model, galaxy size is set by the physical size of the virial radius at the time the (sub)halo attains its peak mass, naturally resulting in smaller sizes for satellites and backsplash centrals relative to true centrals of the same $\mpeak.$
+In the $\rvir-$only model, galaxy size is set by the {\em physical} size of the virial radius at the time the halo attains its peak mass, naturally resulting in smaller sizes for satellites and backsplash centrals relative to true centrals of the same $\mpeak.$ The central/satellite size differences shown here are not enough to correctly predict the observed clustering ratios (see Figure \ref{fig:clustering_ratio_upshot}), motivating the $\mstar-$stripping and profile co-evolution models.
 }

### 2017-10-03 paper/galsize_paper.tex
Updated discussion of clustering ratio figure and its caption

@@
 In Figure \ref{fig:clustering_ratio_upshot} we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj(\rproj).$ Because galaxy clustering has well-known dependence upon $\mstar$ that is not the subject of this work, we wish to remove this influence and focus purely on the relationship between $\rhalf$ and $\wproj(\rproj).$ To do so, we determine the value $\langle\rhalf\vert\mstar\rangle$ by computing a sliding median of $\rhalf,$ calculated using a window of width $N_{\rm gal}=1000.$ Each galaxy is categorized as either ``large" or ``small" according to whether it is above or below the median value appropriate for its stellar mass.
-For any $\mstar-$threshold sample, the SMF of the ``large" and ``small" subsamples are identical, by construction.
+Using this technique, we stress that for any $\mstar-$threshold sample, the SMF of the ``large" and ``small" subsamples are identical, by construction.
 
@@
 {\bf $\rhalf-$dependence of galaxy clustering.}
-Points with error bars show new SDSS measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj,$ compared to predictions by the model tuned to the measurements shown in Fig.~\ref{fig:scatter_plot}.
-We define a galaxy as ``large" or ``small" according to whether it is above or below the median size for its stellar mass, so that in each panel, the SMF of the ``large" and ``small" subsamples are identical, as described in the text.
+Points with error bars show new SDSS measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj.$ We define a galaxy as ``large" or ``small" according to whether it is above or below the median size for its stellar mass, so that in each panel, the stellar mass functions of the ``large" and ``small" subsamples are identical, as described in the text.
 The y-axis shows {\em clustering strength ratios,} so that, for example, a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of comparable stellar mass.
-Each panel shows results separately for a different volume-limited $\mstar-$threshold samples.
+Each panel shows results separately for different volume-limited $\mstar-$threshold samples; predictions of three different models are shown in each panel.
 See \S\ref{subsec:model} for a description of each model.}
@@
 The salient feature of the clustering ratio measurements is that they are negative: small galaxies cluster more strongly than large galaxies of the same stellar mass, a new result.
-This feature also holds true for model galaxies.
+This feature also holds true for galaxies predicted by the $\rvir-$only model.
 This result may be surprising, since $\rhalf\propto\rvir,$ halo mass $\rvir\propto\mhalo^{1/3},$ and clustering strength increases with $\mvir.$ Based on this simple argument, one would expect the opposite trend to the measurements shown here.
 
-A straightforward resolution to this puzzle is shown in Figure \ref{fig:censatsizehist}.
+A straightforward resolution to this puzzle is shown in Figure \ref{fig:censatsizehist}, which compares the $\rhalf$ distributions of central, satellite, and splashback galaxies with the same halo mass $\mpeak\approx10^{12}\msun.$ A ``splashback" galaxy is defined as a present-day central that used to be a satellite, i.e., its main progenitor halo passed inside the virial radius of a larger halo at some point in its past history.
+On the other hand, we define a ``true central" as a galaxy that has never been a satellite.
+
+In the $\rvir-$only model, satellite and splashback galaxies are smaller than centrals of the same halo mass due to the physical size of their halo being smaller at earlier times $\zpeak.$ There are two distinct reasons why this feature results in small galaxies being more strongly clustered relative to larger galaxies of the same mass.
+First, satellite galaxies statistically occupy higher mass host halos that are more strongly clustered.
+In models where satellites are smaller than centrals, for any given $\mstar-$threshold the ``small" subsample will naturally have a higher satellite fraction, resulting in a negative clustering ratio as seen in SDSS data.
+Second, at fixed mass, halos of $L_\ast$ galaxies that form earlier are more strongly clustered, a phenomenon commonly known as {\em halo assembly bias}.
+Since splashback halos are typically earlier forming than true centrals, then models where splashback halos host smaller-than-average galaxies will naturally predict negative clustering ratios.
 
@@
 %-----------------------------------------------------------------------------------------------------
-
-%We can understand the origin of the shape of the clustering strength ratios shown in Figure~\ref{fig:clustering_ratio_upshot} through a series of straightforward ``shuffle tests".
-The points with error bars and solid curves in each panel of Fig.\ref{fig:shuffle} are identical to those appearing in Fig.\ref{fig:clustering_ratio_upshot}, although the dynamic range of the y-axis has changed to accommodate the additional curves.
-
-%We generated each additional curve by variations on the following exercise.
-In logarithmic bins of $\mpeak$ with width of $0.1$dex, we randomly shuffle the modeled $\rhalf$ values of some particular subpopulation of model galaxies that reside in subhalos in the $\mpeak$ bin.
-After repeating this shuffle over the entire range of $\mpeak,$ we then re-divide model galaxies into ``large" and ``small" populations, and remeasure the clustering strength ratios.
-By shuffling sizes amongst different subpopulations, we can gain an understanding of the subhalo properties that contribute to the characteristic shape of the clustering ratios.
-
-%In the {\em brown, dotted} curves labeled ``all-gal scramble", we shuffle the sizes of {\em all} model galaxies in the $\mpeak$ bin, so that in the resulting mock, galaxy size has no correlation with any subhalo property beyond $\mpeak.$ In particular, the ``all-gal scramble" mock erases the possible influence of a correlation between galaxy size and the redshift at which the subhalo attains peak mass.
-The resulting clustering strength ratios become exactly as predicted by the naive expectation sketched at the conclusion of \S\ref{subsec:predictions}: $\rhalf\propto\rvir\propto\mhalo^{1/3},$ and so large galaxies clustering more strongly relative to small galaxies of comparable stellar mass.
-
-%Statistically, there are actually two distinct effects at work in the ``all-gal scramble".
-Central and satellite galaxies of similar $\mpeak$ have their sizes shuffled amongst each other, and the potential influence of central galaxy assembly bias is also erased.
-We parse these separate effects by exploring three variations on the shuffle tests, described below.
-
-%For the {\em cyan dashed} curve labeled ``all-cen-scramble", we only shuffle sizes amongst present-day host halos, i.e., amongst subhalos for which Rockstar {\tt upid} equals -1.
-For the {\em black dashed} curve labeled ``true-cen-scramble", we only shuffle amongst host halos that have never passed within the virial radius of a larger halo throughout their entire assembly history, i.e., we only shuffle amongst non-backsplash host halos.
-Finally, the {\em purple dot-dashed} curve labeled ``sat-scramble", we only shuffle sizes amongst satellite galaxies, i.e., subhalos that are presently located inside the virial radius of a larger halo.
-
-% shown in Figure \ref{fig:shuffle}.
-
-%In light of this explanation, it is natural to ask whether this simple feature {\em alone} is all that is needed for any model of $\rhalf$ to achieve this level of success at predicting galaxy clustering on small and large scales.
-We address this question in \S~\ref{subsec:tests2} below, finding that the answer is no: the reasonably correct magnitude and scale-dependence of the clustering ratios predicted by our model is a non-trivial result that places tight constraints on the post-infall physics of satellite galaxies.
 

### 2017-10-03 paper/galsize_paper.tex
Finished discussion of figure 3 in results section

@@
 
+In the $\mstar-$only model, in which $\rhalf$ is statistically set by present-day stellar mass with no other dependencies.
+Thus neither of the above features are present: satellites and centrals of the same mass have no differences in size, and there is essentially no $\rhalf-$dependence to galaxy clustering, in gross disagreement with our SDSS observations.
+
+Much more successful is the profile co-evolution model shown with the solid curves in Figure \ref{fig:clustering_ratio_upshot}.
+The strongly negative clustering ratios predicted by the assumption of profile co-evolution can be understood in terms of the same features discussed above.
+Figure \ref{fig:coevolutionmodel} shows that at fixed $\mpeak,$ larger galaxies will occupy halos with larger $\rspeak.$ Since halo concentration $c=\rvir/R_{\rm s},$ this implies that high-concentration galaxies will tend to host smaller galaxies.
+Both satellites and splashback centrals have higher concentration than true centrals, another manifestation of assembly bias, and so the assumption of profile co-evolution naturally results in an enhancement of the clustering ratios beyond the $\rvir-$only model.
+
 %---------------------------------------------------------------------------------------------------

### 2017-10-03 paper/galsize_paper.tex
Completed discussion of Figure 5

@@
 
+\subsection{Size-Dependent Clustering}
+\label{subsec:clustering_results}
+
 In Figure \ref{fig:clustering_ratio_upshot} we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj(\rproj).$ Because galaxy clustering has well-known dependence upon $\mstar$ that is not the subject of this work, we wish to remove this influence and focus purely on the relationship between $\rhalf$ and $\wproj(\rproj).$ To do so, we determine the value $\langle\rhalf\vert\mstar\rangle$ by computing a sliding median of $\rhalf,$ calculated using a window of width $N_{\rm gal}=1000.$ Each galaxy is categorized as either ``large" or ``small" according to whether it is above or below the median value appropriate for its stellar mass.
@@
 
-A straightforward resolution to this puzzle is shown in Figure \ref{fig:censatsizehist}, which compares the $\rhalf$ distributions of central, satellite, and splashback galaxies with the same halo mass $\mpeak\approx10^{12}\msun.$ A ``splashback" galaxy is defined as a present-day central that used to be a satellite, i.e., its main progenitor halo passed inside the virial radius of a larger halo at some point in its past history.
+\subsection{Central vs. Satellite Sizes}
+\label{subsec:censat_sizes}
+
+A straightforward resolution to the above puzzle is shown in Figure \ref{fig:censatsizehist}, which compares the $\rhalf$ distributions of central, satellite, and splashback galaxies with the same halo mass $\mpeak\approx10^{12}\msun.$ A ``splashback" galaxy is defined as a present-day central that used to be a satellite, i.e., its main progenitor halo passed inside the virial radius of a larger halo at some point in its past history.
 On the other hand, we define a ``true central" as a galaxy that has never been a satellite.
@@
 
+\subsection{Tidal Stripping and Orphan Satellites}
+\label{subsec:orphan_stripping}
+
+We conclude this section with a discussion of Figure \ref{fig:strippingorphans}, which provides an estimate of how satellite mass stripping and orphan galaxies impact size-dependent clustering ratios.
+In the $\mstar-$stripping model described in \S\ref{subsubsec:strippingmodel}, satellites lose stellar mass in a way that mimics what is seen in high-resolution hydrodynamical simulations.
+This naturally results in an enhancement of size differences between satellites and centrals, and the dot-dashed curves in Figure \ref{fig:strippingorphans} show that produces the expected sign of the effect on the clustering ratios.
+The magnitude of the effect, however is not strong enough to remedy the discrepancy of the clustering predictions of the $\rvir-$only model.
+We discuss the physical implications of this result in \S\ref{subsec:satellite_discussion}.
+
+The dotted curves in Figure \ref{fig:strippingorphans} show results of the $\rvir-$only model applied to a subhalo catalog that includes a orphan halos.
+As described in \S\ref{}, orphan halos are subhalos that are no longer resolved by {\tt Rockstar}, but whose evolution is tracked in a post-processing phase.
+We apply the same mass-stripping model described in \S\ref{subsubsec:strippingmodel} to this subhalo catalog that includes orphan halos, keep all model galaxies that retain more than half of their stellar mass, and show results for the $\rvir-$only model applied to the resulting catalog.
+
+As the orphan catalog has a higher satellite fraction than the standard subhalo catalog, the negative boost shown the dotted curves in Figure \ref{fig:strippingorphans} is expected.
+Orphan halos also typically have earlier-than-average values of $\zpeak$ relative to ordinary subhalos, which also enhances differences between central and satellite sizes.
+See \S\ref{subsec:satellite_discussion} for further discussion.
+
 %---------------------------------------------------------------------------------------------------
@@
 
-%We conclude this section by estimating how satellite mass stripping manifests in $\wproj(\rproj).$ To do so, we construct an extension our fiducial model with a simple additional ingredient for post-infall evolution of satellites mass and size.
-
-%In the fiducial model described in \S~\ref{sec:model}, recall that in the power law a scaling relations (Eq.~\ref{eq:fiducial_model}) the halo radius $\rvir$ used for satellite galaxies is taken to be the value at the time of infall.
-The simple interpretation of this assumption is that, in a statistical sense, the size of satellite galaxies is determined by its history as a central galaxy, and that post-infall physics leaves no distinct imprint on satellite $\rhalf.$
-
-%Here we suppose that this assumption is violated, and that $\rhalf$ decreases after infall according to $(\mvir/\macc)^{1/3}.$ That is, in this alternative formulation, rather than using $\rvir$ at the time of infall for satellites in the power law scaling relations, we instead use $\rvir(\mvir/\macc)^{1/3}.$ This simple toy model attempts supposes that the same physical processes leading to halo mass loss are also responsible for a post-infall decrease in satellite size.
-
 %---------------------------------------------------------------------------------------------------
@@
 \caption{
-{\bf Impact of mass loss and orphan satellites.}
-Here we compare our fiducial model, \dots 
+{\bf Impact of tidal stripping and orphan satellites.} In all panels, the axes and points with error bars are the same as in Figure \ref{fig:clustering_ratio_upshot}.
+The dashed curves (``$\rvir-$only model") and solid curves (``profile co-evolution model") from  Figure \ref{fig:clustering_ratio_upshot} are also shown for convenience.
+The dot-dashed curves show results for a model in which satellites lose mass after infall in a manner similar to what is seen in high-resolution hydrodynamical simulations, as described in \S\ref{subsubsec:strippingmodel}.
+The dotted curve shows results for the same model, but including the effect of ``orphan" galaxies that live in subhalos no longer resolved by {\tt Rockstar}.
 }
-\label{fig:shuffle}
+\label{fig:strippingorphans}
 \end{figure}
 %-----------------------------------------------------------------------------------------------------
-
-%Figure~\ref{fig:satellites} compares the clustering ratios of our fiducial model (solid curves) to the clustering ratios of this alternative model (dashed curves).
-The difference between the small-scale clustering of the two models is stark: the assumption that $\rhalf$ decreases after infall leaves a strong imprint on the $\rhalf-$dependence of $\wproj(\rproj),$ such that small galaxies cluster {\em much} more strongly relative to large galaxies, particularly for disk-dominated systems with $\mstar\approx10^{10}\msun.$
-
-%The large differences between the solid and dashed curves in Fig.~\ref{fig:satellites} establishes that the largely successful prediction for the clustering ratios fiducial model is a non-trivial: $\wproj(\rproj)$ is indeed providing good constraining power on the  assumptions underlying our profile modeling and not simply our morphology modeling, c.f., \S\ref{subsubsec:random_bt_model} and \S\ref{sec:model}.
-We refer the reader to \S\ref{subsec:satellite_discussion} for further discussion of the physical implications of this result.
 

### 2017-10-03 paper/galsize_paper.tex
Added group-finder references

@@
 
-In \citet{kravtsov13}, it was found that if a stellar-to-halo mass relation is inverted to map halo mass estimates $\mhalo$ onto SDSS galaxies, and then the $\mhalo-\rvir$ relation is applied to map values of $\rvir$ onto the galaxies, then the resulting $\rhalf-\rvir$ relation of SDSS galaxies exhibits the following linear scaling across a wide range of stellar mass:
+Motivated by \citet{kravtsov13}, we explore a model in which $\rhalf$ is linearly proportional to halo virial radius:
 \beq
@@
 \eeq
-
-Motivated by the simplicity of this scaling relation, we transform the \citet{kravtsov13} into a forward model using {\tt Halotools}.
 For the virial radius of halos and subhalos, we use $\rmpeak,$ the value of $\rvir$ in physical units of $\kpc$ measured at the time of peak subhalo mass, defined by 
-
 \beq
@@
 
-\subsection{Progression from Backwards to Forwards Modeling}
+\subsection{Progression from Backward to Forward Modeling}
 \label{subsec:forwardsmodeling}
+
+Our results give an archetypal demonstration of the natural scientific progression from backward to forward modeling.
+In backward modeling, some mapping is applied to observed galaxies to estimate the values of model quantities such as halo mass.
+In \citet{kravtsov13}, the model quantities mapped onto galaxies are $\mhalo$ and $\rvir;$ other classic examples of this backward modeling include applying a group- cluster-finding algorithm to a galaxy sample to assign $\mhalo$ to the galaxies \citep[e.g.,][]{berlind_etal06,yang_etal05a}.
+Once the observed galaxies have been supplemented with model variables, then the relations of the galaxy-halo connection can be inferred, for example, by calculating quantities such as the mean stellar mass or quiescent fraction as a function of halo mass \citep[e.g.,][]{yang_etal05b,weinmann_etal06}.
+
+One of the challenges of modeling galaxy size is covariance between the litany of galaxy properties that are well measured by SDSS.
+For example, in \citet{kravtsov13}, a halo mass estimate $\mhalo$ was mapped onto each observed galaxy, and then the $\mhalo-\rvir$ relation is applied to map values of $\rvir$ onto the galaxies.
+It was then observed that the resulting $\rhalf-\rvir$ relation of SDSS galaxies implied by this mapping exhibits approximately linear scaling across a wide range of stellar mass.
+
+However, the simplicity of a linear relation by itself only gives indirect support for the assumption that $\mhalo,$ rather than $\mstar,$ statistically regulates galaxy size.
+By transforming the \citet{kravtsov13} scaling relation into a forward model using {\tt Halotools}, we are able to quantitatively explore the consequences of such modeling assumptions.
+As can be seen by comparing the dashed and dotted curves in Figure \ref{fig:clustering_ratio_upshot}, galaxy clustering gives a direct observational handle on whether $\mhalo$ or $\mstar$ is the more natural independent variable in the problem.
+Evidently, naive models based on $\mhalo$ rather than $\mstar$ naturally recover the qualitative trends seen in large-scale structure.
+
+In forward modeling, the direction of inference is turned around: a mapping is instead applied to the model quantities such as $\mhalo,$ transforming the model into a mock observation.
+This enables a richer quantitative study of modeling hypotheses relative to backward modeling.
+The ability to disentangle coupled variables such as $\mstar$ and $\mhalo$ is one example of this advantage of forward modeling.
+Another example illustrated in the present work is the exploration of the role of splashback galaxies.
+In our forward modeling approach, this is entirely straightforward; in backward modeling, such an investigation would not even be possible without introducing additional modeling ingredients.
+
+\subsection{Empirical Modeling $\rhalf:$ advantages and limitations}
+\label{subsec:empirical_modeling}
 

### 2017-10-03 paper/galsize_paper.tex
Finished section 5.1

@@
 In backward modeling, some mapping is applied to observed galaxies to estimate the values of model quantities such as halo mass.
-In \citet{kravtsov13}, the model quantities mapped onto galaxies are $\mhalo$ and $\rvir;$ other classic examples of this backward modeling include applying a group- cluster-finding algorithm to a galaxy sample to assign $\mhalo$ to the galaxies \citep[e.g.,][]{berlind_etal06,yang_etal05a}.
+In \citet{kravtsov13}, the model quantities mapped onto galaxies are $\mhalo$ and $\rvir;$ another classic example of  backward modeling uses a group- or cluster-finding algorithm to assign $\mhalo$ to observed galaxies \citep[e.g.,][]{berlind_etal06,yang_etal05a,rykoff_etal14}.
 Once the observed galaxies have been supplemented with model variables, then the relations of the galaxy-halo connection can be inferred, for example, by calculating quantities such as the mean stellar mass or quiescent fraction as a function of halo mass \citep[e.g.,][]{yang_etal05b,weinmann_etal06}.
 
-One of the challenges of modeling galaxy size is covariance between the litany of galaxy properties that are well measured by SDSS.
-For example, in \citet{kravtsov13}, a halo mass estimate $\mhalo$ was mapped onto each observed galaxy, and then the $\mhalo-\rvir$ relation is applied to map values of $\rvir$ onto the galaxies.
-It was then observed that the resulting $\rhalf-\rvir$ relation of SDSS galaxies implied by this mapping exhibits approximately linear scaling across a wide range of stellar mass.
+In forward modeling, the direction of inference is turned around: a mapping is instead applied to the model quantities such as $\mhalo.$ In the case of {\tt Halotools}, this transforms a cosmological simulation into a synthetic galaxy catalog that can be directly compared with observations.
+This enables a richer quantitative study of modeling hypotheses relative to backward modeling.
+For example, Figure \ref{fig:clustering_ratio_upshot} shows how forward modeling allows us to exploit galaxy clustering measurements to quantitatively test whether $\mhalo$ or $\mstar$ is the statistical regulator of galaxy size.
+The ability disentangle coupled variables such as $\mstar$ and $\mhalo$ is just one example of this advantage of forward modeling.
+Another example is illustrated in Figure \ref{fig:censatsizehist}, in which we explore the role of splashback halos in setting galaxy size.
+In our forward modeling approach, this is entirely straightforward; in backward modeling, such an investigation would not even be possible without introducing additional modeling ingredients.
 
-However, the simplicity of a linear relation by itself only gives indirect support for the assumption that $\mhalo,$ rather than $\mstar,$ statistically regulates galaxy size.
-By transforming the \citet{kravtsov13} scaling relation into a forward model using {\tt Halotools}, we are able to quantitatively explore the consequences of such modeling assumptions.
-As can be seen by comparing the dashed and dotted curves in Figure \ref{fig:clustering_ratio_upshot}, galaxy clustering gives a direct observational handle on whether $\mhalo$ or $\mstar$ is the more natural independent variable in the problem.
-Evidently, naive models based on $\mhalo$ rather than $\mstar$ naturally recover the qualitative trends seen in large-scale structure.
-
-In forward modeling, the direction of inference is turned around: a mapping is instead applied to the model quantities such as $\mhalo,$ transforming the model into a mock observation.
-This enables a richer quantitative study of modeling hypotheses relative to backward modeling.
-The ability to disentangle coupled variables such as $\mstar$ and $\mhalo$ is one example of this advantage of forward modeling.
-Another example illustrated in the present work is the exploration of the role of splashback galaxies.
-In our forward modeling approach, this is entirely straightforward; in backward modeling, such an investigation would not even be possible without introducing additional modeling ingredients.
+Backward modeling the galaxy-halo connection is useful for generating hypotheses and motivating functional forms.
+Forward modeling becomes necessary when the problem at hand becomes encumbered by multiple relevant variables, as is the case with galaxy size.
+Forward modeling also makes it possible to conduct rigorous Bayesian inference, which we consider to be the next natural step in the progression described here (see \S\ref{subsec:future} for further discussion).
 

### 2017-10-03 paper/galsize_paper.tex
Finished summary section

@@
 Together with the result that stellar mass stripping of satellites has only a mild impact on $\rhalf-$dependent clustering, this suggests that the relative size of centrals and satellites is already in place at the time of satellite infall, and supports the notion that $L_{\ast}$ galaxy and halo profiles co-evolve across many Gyr of cosmic time.
-%Our results can be treated as a boundary condition for more complex and fine-grained models of galaxy size, and provide a simple means for cosmological surveys to generate synthetic galaxy populations with realistic sizes across the cosmic web.
 \end{abstract}
@@
 
-\subsection{Empirical Modeling $\rhalf:$ advantages and limitations}
-\label{subsec:empirical_modeling}
-
 \subsection{Implications for Satellite Mass Loss}
@@
 
-\subsection{Summary}
-\label{subsec:summary}
+We have presented new measurements of the dependence of galaxy clustering upon galaxy size, and used {\tt Halotools} to identify the basic ingredients that influence the signal.
+We conclude with a brief summary of our primary findings:
+
+\ben
+\item Small galaxies clustering more strongly than large galaxies of the same stellar mass, a new result.
+Differences between the clustering of small and large galaxies increase on scales $R\lesssim1\mpc,$ and decrease with stellar mass.
+\item The most important ingredient influencing this signal is the relative size of central and satellite galaxies.
+The magnitude, scale-dependence, and $\mstar-$dependence of $\rhalf-$dependent clustering provides strong evidence that satellite galaxies are smaller than central galaxies of the same halo mass.
+\item Simple empirical models in which $\rhalf$ is regulated by $\mstar,$ rather than $\mhalo,$ are grossly discrepant with the observed clustering signal. 
+\item The ``co-evolution model" shown with solid curves in Figure \ref{fig:clustering_ratio_upshot} exhibits a clustering signal that is strikingly similar to that seen in SDSS.
+In this model, $\rhalf$ is statistically regulated by $\rmpeak,$ the halo virial radius $\rvir$ at the time of peak halo mass, with strong residual correlation with $\rspeak,$ the halo scale radius at that time.
+The success of this model supports the notion that galaxy and halo profiles co-evolve across many Gyr of cosmic time.
+\een
+
+Our results can be treated as a boundary condition for more complex and fine-grained models of galaxy size, such as semi-analytic models and hydrodynamical simulations.
+We view the present work as a pilot study that motivates a Bayesian inference program to tightly constrain the galaxy size-halo connection with forward modeling techniques, in direct analogy to the literature on the stellar-to-halo-mass relation.
+Our publicly available code provides a simple means for cosmological surveys to generate synthetic galaxy populations with realistic sizes across the cosmic web.
 
@@
 APH thanks John Baker for the {\em Toejam \& Earl} soundtrack.
+Thanks also to Frank van den Bosch, Doug Watson, and Risa Wechsler for thoughtful feedback at various stages of the development of this work.
+
+This research was supported in part by the National Science Foundation under Grant No. NSF PHY11-25915. Work done at Argonne National Laboratory was supported under the DOE contract DE-AC02-06CH11357.
 

### 2017-10-03 paper/galsize_paper.tex
typo corrections

@@
 \ben
-\item Small galaxies clustering more strongly than large galaxies of the same stellar mass, a new result.
-Differences between the clustering of small and large galaxies increase on scales $R\lesssim1\mpc,$ and decrease with stellar mass.
+\item Small galaxies cluster more strongly than large galaxies of the same stellar mass, a new result.
+Differences between the clustering of small and large galaxies increase on small scales $R\lesssim1\mpc,$ and decrease with stellar mass.
 \item The most important ingredient influencing this signal is the relative size of central and satellite galaxies.

### 2017-10-04 paper/galsize_paper.tex
Added software citations
Bullet point sketch of previous work

@@
 
-\subsection{Implications for Satellite Mass Loss}
+\subsection{Relation to Previous Work}
+\label{subsec:previous_work}
+
+\ben
+\item \citet{shankar_etal14} - SAMs vs.
+SDSS.
+Use Yang to study median sizes of central galaxies as a function of environment, as defined by Yang-determined halo mass.
+The data do not show any difference in the structural properties of early-type galaxies with environment, at fixed stellar mass.
+All hierarchical models considered in this work instead tend to predict a moderate to strong environmental dependence.
+\item \citet{huertas_company_etal13b} - No Evidence for a Dependence of the Mass-Size Relation of Early-type Galaxies on Environment in the Local Universe.
+The mass?size relation of ETGs in the local Universe does not significantly depend
+on environment. At fixed stellar mass (or fixed central stellar mass density), galaxies
+residing in clusters have similar sizes than the ones living in the field. satellites and central galaxies follow similar mass-size relations.
+\item \citet{spindler_wake17} - central vs. satellite sizes. 
+\bit
+\item They treat $\sigma_0$ like $\mpeak$
+\item Satellites are smaller than centrals of the same $\sigma_0$, but only for quiescent galaxies. 
+\item no dependence of central-satellite mass difference on $\sigma_0$
+\eit
+\item \citet{somerville_etal17} - spin as the origin of scatter
+\item \citet{cebrian_trujillo14} - NYU-VAGC find that field galaxies are slightly larger than high-density regions (defined by 2Mpc smoothing kernel)
+\item \citet{vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,huang_etal17} - high redshift studies of size evolution with HST
+\item \citet{shankar_etal17,yoon_kim17,huang_leauthaud_etal17} - high mass
+\item \citet{huang_etal13} - multiple component profiles
+\een
+
+\subsection{Implications for Satellite Evolution}
 \label{subsec:satellite_discussion}
+
+Points to address:
+\ben
+\item $\rhalf$ is set at $\zpeak.$ Stripping appears to be statistically unimportant. 
+\item The $\rhalf-\rspeak$ correlation implies a very long timeline for co-evolution, since $R_{\rm s}$ is largely frozen in at the time 
+\een
 
@@
 \label{subsec:future}
+
+\ben
+\item joint modeling with the SMHM to get a better handle on satellite fraction
+\item differential buildup like becker model
+\item joint modeling with bulge/disk decomposition
+\een
 
@@
 
+We thank the {\tt Astropy} developers for the package-template \citep{astropy}, and {\tt NumPy} \citep{numpy_ndarray}, {\tt SciPy} \citep{scipy}, IPython, Matplotlib, and GitHub for their extremely useful free software.
+
 This research was supported in part by the National Science Foundation under Grant No. NSF PHY11-25915. Work done at Argonne National Laboratory was supported under the DOE contract DE-AC02-06CH11357.

### 2017-10-04 paper/galsize_paper.tex
progress on previous work section

@@
 \label{sec:intro}
-Some introduction goes here.
+
+\ben
+\item \citet{vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,huang_etal17} - high redshift studies of size evolution with HST
+\item \citet{shankar_etal17,yoon_kim17,huang_leauthaud_etal17} - high mass
+\item \citet{huang_etal13} - multiple component profiles
+\een
 
@@
 
-\subsection{Progression from Backward to Forward Modeling}
+\subsection{Progression from Backwards to Forward Modeling}
 \label{subsec:forwardsmodeling}
 
-Our results give an archetypal demonstration of the natural scientific progression from backward to forward modeling.
-In backward modeling, some mapping is applied to observed galaxies to estimate the values of model quantities such as halo mass.
-In \citet{kravtsov13}, the model quantities mapped onto galaxies are $\mhalo$ and $\rvir;$ another classic example of  backward modeling uses a group- or cluster-finding algorithm to assign $\mhalo$ to observed galaxies \citep[e.g.,][]{berlind_etal06,yang_etal05a,rykoff_etal14}.
+Our results give an archetypal demonstration of the natural scientific progression from backwards to forward modeling.
+In backwards modeling, some mapping is applied to observed galaxies to estimate the values of model quantities such as halo mass.
+In \citet{kravtsov13}, the model quantities mapped onto galaxies are $\mhalo$ and $\rvir;$ another classic example of backwards modeling uses a group- or cluster-finding algorithm to assign $\mhalo$ to observed galaxies \citep[e.g.,][]{berlind_etal06,yang_etal05a,rykoff_etal14}.
 Once the observed galaxies have been supplemented with model variables, then the relations of the galaxy-halo connection can be inferred, for example, by calculating quantities such as the mean stellar mass or quiescent fraction as a function of halo mass \citep[e.g.,][]{yang_etal05b,weinmann_etal06}.
@@
 In forward modeling, the direction of inference is turned around: a mapping is instead applied to the model quantities such as $\mhalo.$ In the case of {\tt Halotools}, this transforms a cosmological simulation into a synthetic galaxy catalog that can be directly compared with observations.
-This enables a richer quantitative study of modeling hypotheses relative to backward modeling.
+This enables a richer quantitative study of modeling hypotheses relative to backwards modeling.
 For example, Figure \ref{fig:clustering_ratio_upshot} shows how forward modeling allows us to exploit galaxy clustering measurements to quantitatively test whether $\mhalo$ or $\mstar$ is the statistical regulator of galaxy size.
@@
 Another example is illustrated in Figure \ref{fig:censatsizehist}, in which we explore the role of splashback halos in setting galaxy size.
-In our forward modeling approach, this is entirely straightforward; in backward modeling, such an investigation would not even be possible without introducing additional modeling ingredients.
+In our forward modeling approach, this is entirely straightforward; in backwards modeling, such an investigation would not even be possible without introducing additional modeling ingredients.
 
-Backward modeling the galaxy-halo connection is useful for generating hypotheses and motivating functional forms.
+Backwards modeling the galaxy-halo connection is useful for generating hypotheses and motivating functional forms.
 Forward modeling becomes necessary when the problem at hand becomes encumbered by multiple relevant variables, as is the case with galaxy size.
@@
 
+Backwards modeling methods have been used extensively in the literature to gain insight into the relationship between galaxy mass, size, and environment.
+Broadly speaking, such studies proceed by using a galaxy group catalog to classify observed galaxies as centrals or satellites, and estimate their halo mass.
+Employing such methods, several analyses of the \citet{yang_etal05b} group catalog have found that the $\mstar-\rhalf$ relation of early-type galaxies exhibits weak, if any, environmental dependence \citep{huertas_company_etal13b,shankar_etal14}.
+
+A direct comparison to this finding is not possible because the conclusions drawn here pertain to $\mstar-$limited galaxy samples.
+As discussed in \citet{spindler_wake17}, it is entirely possible that size differences between centrals and satellites of the same mass can be accounted for by mutual covariance with an additional variable such as star formation rate or morphological type \citep[see also][for an explicit demonstration of this scenario]{lilly_carollo16}.
+In particular, suppose that centrals and satellites of the same mass have different early-type fractions as indicated in \citet{weinmann_etal06}, and that early- and late-type galaxies exhibit universal, but distinct, $\mstar-\rhalf$ relations.
+In such a case, centrals would be larger than satellites of the same mass, even though {\em early-type centrals} would have the same sizes as {\em early-type satellites}.
+
+As discussed in \S\ref{subsec:future}, we are currently pursuing follow-up work in which we jointly model morphological type together with galaxy size.
+We consider forward modeling methods to be a requisite for progress on this issue, not only to properly handle the multi-dimensional nature of the problem, but also to rigorously treat systematic errors that plague inference based on galaxy group catalogs \citep[see][for a thorough discussion]{campbell_etal15}.
+
+Our approach is closely aligned with the methods used in \citet{somerville_etal17}, who studied the empirical modeling features that are necessary to recover the tight scatter in the observed $\langle\rhalf\vert\mstar\rangle$ relation.
+
 \ben
-\item \citet{shankar_etal14} - SAMs vs.
-SDSS.
-Use Yang to study median sizes of central galaxies as a function of environment, as defined by Yang-determined halo mass.
-The data do not show any difference in the structural properties of early-type galaxies with environment, at fixed stellar mass.
-All hierarchical models considered in this work instead tend to predict a moderate to strong environmental dependence.
-\item \citet{huertas_company_etal13b} - No Evidence for a Dependence of the Mass-Size Relation of Early-type Galaxies on Environment in the Local Universe.
-The mass?size relation of ETGs in the local Universe does not significantly depend
-on environment. At fixed stellar mass (or fixed central stellar mass density), galaxies
-residing in clusters have similar sizes than the ones living in the field. satellites and central galaxies follow similar mass-size relations.
-\item \citet{spindler_wake17} - central vs. satellite sizes. 
-\bit
-\item They treat $\sigma_0$ like $\mpeak$
-\item Satellites are smaller than centrals of the same $\sigma_0$, but only for quiescent galaxies. 
-\item no dependence of central-satellite mass difference on $\sigma_0$
-\eit
-\item \citet{somerville_etal17} - spin as the origin of scatter
 \item \citet{cebrian_trujillo14} - NYU-VAGC find that field galaxies are slightly larger than high-density regions (defined by 2Mpc smoothing kernel)
-\item \citet{vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,huang_etal17} - high redshift studies of size evolution with HST
-\item \citet{shankar_etal17,yoon_kim17,huang_leauthaud_etal17} - high mass
-\item \citet{huang_etal13} - multiple component profiles
 \een

### 2017-10-04 paper/galsize_paper.tex
Previous work section is done once somerville discussion is complete

@@
 Our approach is closely aligned with the methods used in \citet{somerville_etal17}, who studied the empirical modeling features that are necessary to recover the tight scatter in the observed $\langle\rhalf\vert\mstar\rangle$ relation.
-
-\ben
-\item \citet{cebrian_trujillo14} - NYU-VAGC find that field galaxies are slightly larger than high-density regions (defined by 2Mpc smoothing kernel)
-\een
+By building models where $\rhalf$ is set by halo spin $\lambda_{\rm halo}$, the authors in \citet{somerville_etal17} found that the level of intrinsic scatter about $\langle\lambda_{\rm halo}\vert\mhalo\rangle$ in dark matter halos is at least as large as the scatter about $\langle\rhalf\vert\mstar\rangle$ seen in observed galaxies.
+Since the latter necessarily receives an additional contribution from measurement error, this implies some tension with the common semi-analytic modeling assumption that $\lambda_{\rm halo}$ scales with $\rhalf.$ As noted in \citet{somerville_etal17}, this evidence cannot be used to directly test the $\lambda_{\rm halo}\propto\rhalf$ assumption because the physical motivation for this correlation is largely limited to disk galaxies \citep{mo_mao_white98}.
 

### 2017-10-04 paper/galsize_paper.tex
Finished discussion of previous work

@@
 By building models where $\rhalf$ is set by halo spin $\lambda_{\rm halo}$, the authors in \citet{somerville_etal17} found that the level of intrinsic scatter about $\langle\lambda_{\rm halo}\vert\mhalo\rangle$ in dark matter halos is at least as large as the scatter about $\langle\rhalf\vert\mstar\rangle$ seen in observed galaxies.
-Since the latter necessarily receives an additional contribution from measurement error, this implies some tension with the common semi-analytic modeling assumption that $\lambda_{\rm halo}$ scales with $\rhalf.$ As noted in \citet{somerville_etal17}, this evidence cannot be used to directly test the $\lambda_{\rm halo}\propto\rhalf$ assumption because the physical motivation for this correlation is largely limited to disk galaxies \citep{mo_mao_white98}.
+Since the latter necessarily receives an additional contribution from measurement error, this implies some tension with the common semi-analytic modeling assumption that $\lambda_{\rm halo}$ scales with $\rhalf.$ As noted in \citet{somerville_etal17}, tension in the level of scatter cannot be used to directly test the $\lambda_{\rm halo}\propto\rhalf$ assumption because the physical motivation for this correlation is largely limited to disk galaxies \citep{mo_mao_white98}.
+This tension is not present in our approach for the reason that the level of scatter is simply a modeling parameter in our approach, and we make no attempt to uncover the physical origin of this scatter.
+However, our fiducial value choice was motivated by \citet{somerville_etal17}, and in the ongoing follow-up work discussed in \S\ref{subsec:future} we will systematically test the large-scale structure implications of the assumption that $\lambda_{\rm halo}\propto\rhalf^{\rm disk}.$
 

### 2017-10-04 paper/galsize_paper.tex
Finshed satellite evolution implications section

@@
 
-Points to address:
-\ben
-\item $\rhalf$ is set at $\zpeak.$ Stripping appears to be statistically unimportant.
-\item The $\rhalf-\rspeak$ correlation implies a very long timeline for co-evolution, since $R_{\rm s}$ is largely frozen in at the time
-\een
+Explanations for differences between the sizes of centrals and satellites fall into two categories, depending on whether or not the processes involved are specific to post-infall physics.
+One obvious possibility that could lead to satellites being smaller than centrals of the same $\mhalo$ is tidal stripping: satellite $\mstar$ could decrease after infall, reducing the size of the galaxy.
+We have quantitatively tested this possibility with the $\mstar-$stripping model described in \S\ref{subsubsec:strippingmodel}.
+Comparing the clustering ratios of the ``$\rvir-$only" and ``$\rvir+$stripping" models in Figure \ref{fig:strippingorphans}, we find that the impact of physically motivated levels of satellite mass loss cannot explain the $\rhalf-$dependent clustering seen in SDSS.
+As an additional test, we reach the same conclusion when implementing an even more extreme $\mstar-$stripping model in which stellar mass loss is linearly proportional to halo mass loss \citep[][Model 1]{watson_etal12}.
+
+Both the $\rvir-$only model and the co-evolution model (see sections \S\ref{subsubsec:rvirmodel} and \S\ref{subsubsec:coevolutionmodel}, respectively) represent explanations falling into the second category, in which centrals and satellites of the same $\mhalo$ have different sizes due to their different evolutionary paths {\em prior} to satellite infall.
+For these models the story is very different: the influence of pre-infall co-evolution has a dramatic impact on $\rhalf-$clustering ratios, with a scale- and $\mstar-$dependence that closely resembles the SDSS signal.
+Quantitative constraints on the true level of this co-evolution effect will be a natural outcome of the program described in \S\ref{subsec:future}, but it is already clear that the long term co-evolution of galaxy and halo profiles should be considered a critical ingredient to models for the distribution of galaxy sizes across the cosmic web.
 

### 2017-10-04 paper/galsize_paper.tex
Finished discussion of future directions

@@
 
-\subsection{Future Directions for Empirical Modeling of Morphology}
+\subsection{Future Directions for Empirical Modeling of Galaxy Size}
 \label{subsec:future}
 
-\ben
-\item joint modeling with the SMHM to get a better handle on satellite fraction
-\item differential buildup like becker model
-\item joint modeling with bulge/disk decomposition
-\een
+\subsubsection{Jointly modeling $\langle\mstar\vert\mhalo\rangle$}
+
+The scope of this work is to serve as a pilot study in which we identify the chief ingredients that can influence the $\rhalf-$dependence of galaxy clustering.
+While our results suggest that our profile co-evolution model is giving the correct qualitative picture, our implementation cannot be correct in quantitative detail: the clustering ratios of this model shown in Figure \ref{fig:clustering_ratio_upshot} are too strong relative to SDSS.
+This likely indicates that the central/satellite size differences depicted in Figure \ref{fig:} are too strong, and that the correlation strength in the real Universe is intermediate, rather than maximal.
+Our publicly available code that reproduces our results already contains the machinery to implement continuously variable levels of $\rhalf-\rspeak$ correlation strength, but for present purposes we have chosen to focus on exploring bracketing cases of qualitative ingredients, rather than fine-tuning the model.
+
+In addition to varying the $\rhalf-\rspeak$ correlation strength, there are other factors that should be included in any proper likelihood analysis of galaxy size models.
+In particular, since the clustering signal is strongly influenced by differences between centrals and satellites, then the satellite fraction $F_{\rm sat}(\mstar)$ plays an important role in $\rhalf-$dependent clustering.
+For fixed scaling relations $\langle\rhalf^{\rm cens}\vert\mhalo\rangle$ and $\langle\rhalf^{\rm sats}\vert\mhalo\rangle,$ models with different satellite fractions will exhibit different $\rhalf-$clustering ratios because $F_{\rm sat}(\mstar)$ controls the relative weighting of the two populations.
+Our results based on the catalog that includes orphan subhalos (Figure \ref{fig:strippingorphans}, dotted curves) give an explicit demonstration of the impact of $F_{\rm sat}(\mstar)$ on the clustering signal.
+
+On the one hand, this degeneracy with the satellite fraction is unfortunate, because it means galaxy sizes does not leave a pure and unique signature on $\rhalf-$clustering ratios.
+However, this can also be viewed as an opportunity to extract tighter constraints on $F_{\rm sat}(\mstar),$ which are sorely needed to discriminate between competing models.
+For this problem, the path forward is clear.
+Traditional galaxy clustering is already being used to validate and/or fit models of the stellar-to-halo-mass relation \citep[e.g.,][]{moster_etal13,behroozi13_smhm,lehmann_etal15}.
+Based on our results, we advocate that empirical models for $\langle\mstar\vert\mhalo\rangle$ be supplemented with additional model ingredients for $\langle\rhalf\vert\mstar\rangle,$ and that the parameters of composite model are jointly constrained by measurements of the stellar mass function, $\mstar-$dependent clustering, and $\rhalf-$dependent clustering.
+Careful attention will need to be paid to the orphan subhalo population, which is well-known to have a significant impact on small-scale clustering \citep{guo_white13,campbell_etal17}.
+
+\subsubsection{Jointly modeling morphology}
+
+Previous studies of large-scale structure measured by SDSS indicate that morphological type has a significant influence on galaxy clustering \citep{skibba_etal08}.
+Because morphology is covariant with star-formation rate (SFR) and $\rhalf,$ accounting for this dependency will require simultaneously modeling each of these variables.
+
+To date, such a task has been beyond the purview of empirical models.
+However, recent progress has substantially improved the richness of the predictions that galaxy-halo models are capable of \citep{becker15,cohn17,moster_etal17}.
+This new class of models has accomplished this by empirically modeling star-formation rate, and then integrating SFR along each halo's history to differentially build up stellar mass.\footnote{This approach towards predicting $\mstar$ is thus mathematically akin to traditional semi-analytic models, although \citet{becker15} have retained the empirical modeling prioritization of simplicity and computational efficiency.} We are currently extending this new class of models to differentially build up the disk and bulge across cosmic time.
+In addition to treating the multi-dimensional nature of the problem, this also allows us to use data at higher redshift in a self-consistent manner.
 

### 2017-10-04 paper/galsize_paper.tex
Starting to sketch intro

@@
 
+%%%%%%%%  cosmology  %%%%%%%%
+\newcommand{\lcdm}{\Lambda{\rm CDM}}
+
 %%%%%%%%  observations  %%%%%%%%
@@
 
-\ben
-\item \citet{vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,huang_etal17} - high redshift studies of size evolution with HST
-\item \citet{shankar_etal17,yoon_kim17,huang_leauthaud_etal17} - high mass
-\item \citet{huang_etal13} - multiple component profiles
-\een
+In the $\lcdm$ framework of cosmological structure formation, galaxies form at the centers of dark matter halos.
+Highly complex and nonlinear baryonic processes regulate galaxy formation, and the quest for a fine-grained understanding of these processes is one of the chief goals of theoretical astrophysics today.
+
+Observationally, many properties of observed galaxies exhibit remarkably tight scaling relations.
+Among the most fundamental of these relations is the strong correlation between galaxy size and stellar mass and luminosity.
+The scaling of galaxy size with galaxy mass is well-measured in the local Universe \citep{shen_etal03,guo_etal09,huang_etal13,zhang_yang17} and at high-redshift \citep{trujillo_etal04,vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,lange_etal15,huang_etal17}.
+
+These well-measured scaling relations are challenging to faithfully recover using ab initio galaxy formation methods such as hydrodynamical simulations and semi-analytic models, and provide useful boundary conditions for the calibration of such modeling efforts \citep{khochfar_silk06,dutton_etal10,hopkins_etal10a,bottrell_etal17b}.
+The precision cosmology program also depends critically on accurate modeling of galaxies, so that cosmological parameter inference can be confidently conducted without undue interference from uncertainty in baryonic physics \citep{LSST_science,LSST_galaxies}.
 

### 2017-10-05 paper/galsize_paper.tex
Updated acknowledgements

@@
 APH thanks John Baker for the {\em Toejam \& Earl} soundtrack.
-Thanks also to Frank van den Bosch, Doug Watson, and Risa Wechsler for thoughtful feedback at various stages of the development of this work.
+Thanks also to Frank van den Bosch, Doug Watson, and Risa Wechsler for thoughtful feedback at various stages of the development of this work, and to Faustin Carter and Sebastian Bocquet for sharing their python expertise.
 

### 2017-10-10 paper/galsize_paper.tex
Modified abstract

@@
 
-\title[Forward Modeling Galaxy Size]
-{Forward Modeling Galaxy Size in a Cosmological Context}
+\title[The Relative Sizes of Centrals and Satellites]
+{Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies}
 
@@
 \begin{abstract}
-We derive empirical modeling constraints on the connection between dark matter halos and the half-light radius of galaxies, $\rhalf.$ Novel to this work, we study galaxy size using new SDSS measurements of the $\rhalf-$dependence of galaxy clustering.
-Smaller galaxies cluster stronger relative to larger galaxies of the same stellar mass, a new result.
-We use {\tt Halotools} to test a collection of forward models of galaxy size to identify the qualitative ingredients needed to reproduce the observed clustering.
-We show that the $\rhalf-$dependence of galaxy clustering is largely driven by centrals being larger than satellite galaxies of the same halo mass.
-Models in which $\rhalf$ is determined by stellar mass $\mstar$ exhibit qualitatively discrepant clustering properties from SDSS galaxies.
-Models where $\rhalf$ is linearly proportional to halo virial radius $\rvir$ at the time of peak halo mass are much more successful, provided that scatter in $\rhalf$ is significantly correlated with the halo scale radius $R_{\rm s}$ at that time.
-Together with the result that stellar mass stripping of satellites has only a mild impact on $\rhalf-$dependent clustering, this suggests that the relative size of centrals and satellites is already in place at the time of satellite infall, and supports the notion that $L_{\ast}$ galaxy and halo profiles co-evolve across many Gyr of cosmic time.
+We place empirical constraints on the connection between dark matter halos and galaxy half-light radii, $\rhalf.$ Using the SDSS, we show that smaller galaxies cluster much more strongly than larger galaxies at fixed stellar mass.
+ Using Halotools to forward-model the observations, we find that the clustering signal generically requires satellite galaxies to be smaller than central galaxies of the same halo mass.
+ We present a simple empirical model consistent with the clustering results, in which galaxy size is proportional to halo virial radius at the time of peak halo mass, and the scatter is strongly correlated with halo scale radius.
+ Models in which galaxy size is related to stellar mass only or that have uncorrelated scatter in galaxy size both fail the clustering test, even considering effects of satellite stripping and orphan galaxies.
+ These results suggest that the relative size of centrals and satellites is predetermined at the time of satellite infall, and supports the notion that $L_\ast$ galaxy and halo profiles co-evolve across many Gyr of cosmic time.
 \end{abstract}

### 2017-10-30 galsize_models/models/load_baseline_catalogs.py
Added orphan subhalo catalog loader, and preliminary sham module

@@ -11,6 +11,8 @@ from astropy.cosmology import Planck15
 from astropy.utils.misc import NumpyRNGContext
 from astropy.table import Table
 from halotools.empirical_models import solve_for_polynomial_coefficients
+from AbundanceMatching import AbundanceFunction, calc_number_densities
+from halotools.empirical_models import enforce_periodicity_of_box
 
 from .random_bt_assignment import value_add_random_bt
 
@@ -18,7 +20,7 @@ from ..measurements import load_umachine_sdss_with_meert15
 
 
 __all__ = ('moster13_based_mock', 'load_umachine_mock', 'load_baseline_halocat',
-        'load_orphan_mock')
+        'load_orphan_mock', 'moustakas_sham_with_orphans', 'load_orphan_subhalos')
 
 default_umachine_galprops = list((
     'sm', 'sfr', 'obs_sm', 'obs_sfr', 'icl', 'halo_id', 'upid',
@@ -31,6 +33,14 @@ moster13_halocat_keys = ('halo_upid', 'halo_mpeak', 'halo_scale_factor_mpeak',
         'halo_scale_factor_firstacc', 'halo_mvir_firstacc', 'halo_halfmass_scale_factor',
         'halo_vx', 'halo_vy', 'halo_vz', 'halo_rvir_zpeak', 'halo_vmax_at_mpeak_percentile',
         'halo_mvir_host_halo', 'halo_spin', 'halo_uran')
+
+smf_dirname = "/Users/aphearin/work/UniverseMachine/code/UniverseMachine/obs"
+smf_basename = "moustakas_z0.01_z0.20.smf"
+smf_fname = os.path.join(smf_dirname, smf_basename)
+smf = np.loadtxt(smf_fname)
+log10_sm_table_h0p7 = 0.5*(smf[:, 0] + smf[:, 1])
+dn_dlog10_sm_h0p7 = smf[:, 2]
+sham_ext_range = (8, 12.75)
 
 
 def load_baseline_halocat(simname='bolplanck', redshift=0, fixed_seed=411):
@@ -141,6 +151,8 @@ def load_umachine_mock(galprops=default_umachine_galprops, Lbox=250):
 
 
 def load_orphan_mock():
+    """ Note that this function calls a Moster+13 model and applies a cut on stellar mass.
+    """
 
     dirname = "/Users/aphearin/work/sims/bolplanck/orphan_catalog_z0"
[…]

### 2017-10-30 galsize_models/measurements/sdss_measurements.py
Added tabulation of penultimate clustering measurements and penultimate_clustering_measurements.ipynb notebook

@@ -37,3 +37,46 @@ wp_sdss_sm11p25_smbell_small = np.load(os.path.join(output_dirname, 'sdss_sm11p2
 wp_sdss_sm11p25_smbell_large = np.load(os.path.join(output_dirname, 'sdss_sm11p25_smbell_large_wp.npy'))
 fracdiff_sm11p25_smbell = (wp_sdss_sm11p25_smbell_large-wp_sdss_sm11p25_smbell_small)/wp_sdss_sm11p25_smbell
 fracdiff_sm11p25_smbell_err = np.maximum(np.sqrt(wperr_sdss_sm11p25_smbell)/wp_sdss_sm11p25_smbell, cutoff_err)
+
+
+wp_sdss_mpajhu_sm9p75 = np.load(os.path.join(output_dirname, 'sdss_mpajhu_sm9p75_wp.npy'))
+wperr_sdss_mpajhu_sm9p75 = np.load(os.path.join(output_dirname, 'sdss_mpajhu_sm9p75_wperr.npy'))
+wp_sdss_mpajhu_sm9p75_small = np.load(os.path.join(output_dirname, 'sdss_mpajhu_sm9p75_small_wp.npy'))
+wp_sdss_mpajhu_sm9p75_large = np.load(os.path.join(output_dirname, 'sdss_mpajhu_sm9p75_large_wp.npy'))
+
+wp_sdss_mpajhu_sm10p0 = np.load(os.path.join(output_dirname, 'sdss_mpajhu_sm10p0_wp.npy'))
+wperr_sdss_mpajhu_sm10p0 = np.load(os.path.join(output_dirname, 'sdss_mpajhu_sm10p0_wperr.npy'))
+wp_sdss_mpajhu_sm10p0_small = np.load(os.path.join(output_dirname, 'sdss_mpajhu_sm10p0_small_wp.npy'))
+wp_sdss_mpajhu_sm10p0_large = np.load(os.path.join(output_dirname, 'sdss_mpajhu_sm10p0_large_wp.npy'))
+
+wp_sdss_mpajhu_sm10p25 = np.load(os.path.join(output_dirname, 'sdss_mpajhu_sm10p25_wp.npy'))
+wperr_sdss_mpajhu_sm10p25 = np.load(os.path.join(output_dirname, 'sdss_mpajhu_sm10p25_wperr.npy'))
[…]

### 2017-10-30 galsize_models/measurements/__init__.py
Added masked_wp convenience function

@@ -5,3 +5,4 @@ from .load_cross_matched_umachine import *
 from .measure_one_points import *
 from .rhalf_rvir_power_law_fit import rvir_rhalf_power_law_fit
 from .wp_ratio_mock import *
+from .wp_absolute_mock import masked_wp

### 2017-10-30 galsize_models/measurements/wp_absolute_mock.py

@@ -1,0 +1,22 @@
+"""
+"""
+import numpy as np
+from halotools.mock_observables import return_xyz_formatted_array, wp
+
+
+__all__ = ('masked_wp', )
+
+
+def masked_wp(subhalos, mask=None):
+    """
+    """
+    if mask is None:
+        mask = np.ones_like(subhalos).astype(bool)
+
+    rp_bins, pi_max = np.logspace(-1, 1.35, 25), 20.
+    rmids = 10**(0.5*(np.log10(rp_bins[:-1]) + np.log10(rp_bins[1:])))
+    pos = return_xyz_formatted_array(
+            subhalos['x'], subhalos['y'], subhalos['z'],
+            mask=mask, period=250,
+            velocity=subhalos['vz'], velocity_distortion_dimension='z')
+    return rmids, wp(pos, rp_bins, pi_max, period=250.)

### 2017-10-31 galsize_models/measurements/sdss_measurements.py
Experimenting with new orphan treatment

@@ -7,7 +7,7 @@ repo_dirname = "/Users/aphearin/work/repositories/python/galsize_models"
 output_subdirname = "galsize_models/measurements/data/two_point_functions"
 output_dirname = os.path.join(repo_dirname, output_subdirname)
 
-cutoff_err = 0.2
+cutoff_err = 0.1
 
 rp = np.load(os.path.join(output_dirname, 'sdss_sm9p75_smbell_rp.npy'))
 wp_sdss_sm9p75_smbell = np.load(os.path.join(output_dirname, 'sdss_sm9p75_smbell_wp.npy'))
@@ -43,36 +43,50 @@ wp_sdss_mpajhu_sm9p75 = np.load(os.path.join(output_dirname, 'sdss_mpajhu_sm9p75
 wperr_sdss_mpajhu_sm9p75 = np.load(os.path.join(output_dirname, 'sdss_mpajhu_sm9p75_wperr.npy'))
 wp_sdss_mpajhu_sm9p75_small = np.load(os.path.join(output_dirname, 'sdss_mpajhu_sm9p75_small_wp.npy'))
 wp_sdss_mpajhu_sm9p75_large = np.load(os.path.join(output_dirname, 'sdss_mpajhu_sm9p75_large_wp.npy'))
+fracdiff_sm9p75_mpajhu = (wp_sdss_mpajhu_sm9p75_large-wp_sdss_mpajhu_sm9p75_small)/wp_sdss_mpajhu_sm9p75
+fracdiff_sm9p75_mpajhu_err = np.maximum(np.sqrt(wperr_sdss_mpajhu_sm9p75)/wp_sdss_mpajhu_sm9p75, cutoff_err)
 
 wp_sdss_mpajhu_sm10p0 = np.load(os.path.join(output_dirname, 'sdss_mpajhu_sm10p0_wp.npy'))
 wperr_sdss_mpajhu_sm10p0 = np.load(os.path.join(output_dirname, 'sdss_mpajhu_sm10p0_wperr.npy'))
 wp_sdss_mpajhu_sm10p0_small = np.load(os.path.join(output_dirname, 'sdss_mpajhu_sm10p0_small_wp.npy'))
[…]

### 2017-10-31 galsize_models/measurements/wp_ratio_mock.py

@@ -4,7 +4,7 @@ import numpy as np
 from halotools.mock_observables import return_xyz_formatted_array, wp
 
 
-__all__ = ('wp_size_ratios_mock', 'single_component_ratios')
+__all__ = ('wp_size_ratios_mock', 'single_component_ratios', 'single_component_clustering')
 
 
 def wp_size_ratios_mock(mock, logsm_min, sample_cut, size_key='r50_magr_kpc_meert15',
@@ -78,5 +78,38 @@ def single_component_ratios(mock, rp_bins=np.logspace(-1, 1.25, 20),
         wp_large = wp(pos_large, rp_bins, pi_max, period=period)
         fracdiff = (wp_large-wp_small)/wp_all
         result_collector.append(fracdiff)
+
+    return result_collector
+
+
+def single_component_clustering(mock, rp_bins=np.logspace(-1, 1.25, 20),
+            pi_max=20., period=250., size_key='r50', num_gals_max=int(1e5)):
+    """
+    """
+    result_collector = []
+    rp_mids = 10**(0.5*(np.log10(rp_bins[:-1]) + np.log10(rp_bins[1:])))
+    result_collector.append(rp_mids)
+
+    for logsm_cut in (9.75, 10.25, 10.75, 11, 11.25):
+        sample = mock[mock['sm'] > logsm_cut]
+        if len(sample) > num_gals_max:
+            downsampling_mask = np.random.choice(np.arange(len(sample)), num_gals_max, replace=False)
+            sample = sample[downsampling_mask]
+
+        pos_all = return_xyz_formatted_array(sample['x'], sample['y'], sample['z'],
+                        velocity=sample['vz'], velocity_distortion_dimension='z', period=period)
+
+        pos_small = return_xyz_formatted_array(sample['x'], sample['y'], sample['z'],
+                        velocity=sample['vz'], velocity_distortion_dimension='z', period=period,
+                        mask=(sample[size_key] < sample[size_key+'_median']))
+        pos_large = return_xyz_formatted_array(sample['x'], sample['y'], sample['z'],
+                        velocity=sample['vz'], velocity_distortion_dimension='z', period=period,
+                        mask=(sample[size_key] >= sample[size_key+'_median']))
+
+        wp_all = wp(pos_all, rp_bins, pi_max, period=period)
+        wp_small = wp(pos_small, rp_bins, pi_max, period=period)
+        wp_large = wp(pos_large, rp_bins, pi_max, period=period)
+
[…]

### 2017-10-31 galsize_models/models/load_baseline_catalogs.py

@@ -13,6 +13,8 @@ from astropy.table import Table
 from halotools.empirical_models import solve_for_polynomial_coefficients
 from AbundanceMatching import AbundanceFunction, calc_number_densities
 from halotools.empirical_models import enforce_periodicity_of_box
+from halotools.utils import crossmatch
+from halotools.empirical_models import noisy_percentile
 
 from .random_bt_assignment import value_add_random_bt
 
@@ -20,7 +22,7 @@ from ..measurements import load_umachine_sdss_with_meert15
 
 
 __all__ = ('moster13_based_mock', 'load_umachine_mock', 'load_baseline_halocat',
-        'load_orphan_mock', 'moustakas_sham_with_orphans', 'load_orphan_subhalos')
+        'load_orphan_mock', 'moustakas_sham', 'load_orphan_subhalos')
 
 default_umachine_galprops = list((
     'sm', 'sfr', 'obs_sm', 'obs_sfr', 'icl', 'halo_id', 'upid',
@@ -41,6 +43,8 @@ smf = np.loadtxt(smf_fname)
 log10_sm_table_h0p7 = 0.5*(smf[:, 0] + smf[:, 1])
 dn_dlog10_sm_h0p7 = smf[:, 2]
 sham_ext_range = (8, 12.75)
+moustakas_af = AbundanceFunction(log10_sm_table_h0p7, dn_dlog10_sm_h0p7,
+        sham_ext_range, faint_end_first=True)
 
 
 def load_baseline_halocat(simname='bolplanck', redshift=0, fixed_seed=411):
@@ -176,13 +180,12 @@ def load_orphan_mock():
 
     from galsize_models.models import moster13_based_mock
 
-    keys_to_keep=list(halocat.halo_table.keys())
+    keys_to_keep = list(halocat.halo_table.keys())
     keys_to_keep.append('halo_rvir_zpeak')
 
     mock = moster13_based_mock(halocat=halocat, mpeak_key='halo_mpeak', zpeak_key='halo_zpeak',
                               keys_to_keep=keys_to_keep)
 
-    from halotools.empirical_models import noisy_percentile
 
     mock['noisy_vmax_at_mpeak_percentile'] = noisy_percentile(
         mock['vmax_at_mpeak_percentile'], 0.5)
@@ -205,29 +208,38 @@ def load_orphan_subhalos():
 
     halo_table['vmax_at_mpeak_percentile'] = np.load(
[…]

### 2017-10-31 paper/galsize_paper.tex
Increased figure size
Updated abstract

@@
 \begin{abstract}
-We place empirical constraints on the connection between dark matter halos and galaxy half-light radii, $\rhalf.$ Using the SDSS, we show that smaller galaxies cluster much more strongly than larger galaxies at fixed stellar mass.
- Using Halotools to forward-model the observations, we find that the clustering signal generically requires satellite galaxies to be smaller than central galaxies of the same halo mass.
- We present a simple empirical model consistent with the clustering results, in which galaxy size is proportional to halo virial radius at the time of peak halo mass, and the scatter is strongly correlated with halo scale radius.
- Models in which galaxy size is related to stellar mass only or that have uncorrelated scatter in galaxy size both fail the clustering test, even considering effects of satellite stripping and orphan galaxies.
- These results suggest that the relative size of centrals and satellites is predetermined at the time of satellite infall, and supports the notion that $L_\ast$ galaxy and halo profiles co-evolve across many Gyr of cosmic time.
+We place empirical constraints on the connection between dark matter halos and galaxy half-light radii, $\rhalf.$ Low-redshift SDSS measurements show that smaller galaxies cluster much more strongly than larger galaxies at fixed stellar mass.
+Using {\tt Halotools} to forward model the observations, we find that the clustering signal generically requires satellite galaxies to be smaller than central galaxies of the same halo mass.
+We present a simple empirical model consistent with the clustering results, in which galaxy size is proportional to halo virial radius at the time of peak halo mass.
+We use this model to predict how galaxy lensing, $\Delta\Sigma,$ should depend on $\rhalf$ for $\mstar-$complete galaxy samples.
+Other simple empirical models fail the clustering test, such as models in which galaxy size is related to stellar mass alone, and models that treat splashback galaxies as ordinary centrals; these failures persist even when accounting for possible effects from satellite stripping and orphan galaxies.
+Our results suggest that the relative size of centrals and satellites is predetermined at the time of satellite infall, and that a remarkably simple scaling relation emerges from the complex physics regulating galaxy size.
+%We make our python code publicly available to support ongoing efforts to generate realistic synthetic galaxy catalogs for large cosmological surveys.  
 \end{abstract}
@@
 %---------------------------------------------------------------------------------------------------
-\begin{figure}
+\begin{figure*}
 \centering
-\includegraphics[width=8cm]{FIGS/penultimate_clustering_ratios_no_orphans.pdf}
+\includegraphics[width=12cm]{FIGS/penultimate_clustering_ratios_no_orphans.pdf}
 \caption{
@@
 \label{fig:clustering_ratio_upshot}
-\end{figure}
+\end{figure*}
 %-----------------------------------------------------------------------------------------------------

### 2017-10-31 paper/galsize_paper.tex
Updated abstract

@@
 We present a simple empirical model consistent with the clustering results, in which galaxy size is proportional to halo virial radius at the time of peak halo mass.
-We use this model to predict how galaxy lensing, $\Delta\Sigma,$ should depend on $\rhalf$ for $\mstar-$complete galaxy samples.
+We use this model to predict how galaxy lensing, $\Delta\Sigma,$ should depend on $\rhalf$ for $\mstar-$complete samples.
 Other simple empirical models fail the clustering test, such as models in which galaxy size is related to stellar mass alone, and models that treat splashback galaxies as ordinary centrals; these failures persist even when accounting for possible effects from satellite stripping and orphan galaxies.
-Our results suggest that the relative size of centrals and satellites is predetermined at the time of satellite infall, and that a remarkably simple scaling relation emerges from the complex physics regulating galaxy size.
+Our results suggest that the relative size of centrals and satellites is predetermined at the time of satellite infall, and that a remarkably simple galaxy--halo scaling relation emerges from the complex physics regulating galaxy size.
 %We make our python code publicly available to support ongoing efforts to generate realistic synthetic galaxy catalogs for large cosmological surveys.  

### 2017-10-31 galsize_models/models/load_baseline_catalogs.py
Finished hand-tuning SHAM orphan treatment. Migrated choice into load_baseline_catalogs

@@ -22,7 +22,7 @@ from ..measurements import load_umachine_sdss_with_meert15
 
 
 __all__ = ('moster13_based_mock', 'load_umachine_mock', 'load_baseline_halocat',
-        'load_orphan_mock', 'moustakas_sham', 'load_orphan_subhalos')
+        'load_orphan_mock', 'moustakas_sham', 'load_orphan_subhalos', 'orphan_selection')
 
 default_umachine_galprops = list((
     'sm', 'sfr', 'obs_sm', 'obs_sfr', 'icl', 'halo_id', 'upid',
@@ -211,6 +211,20 @@ def load_orphan_subhalos():
     halo_table['noisy_vmax_at_mpeak_percentile'] = noisy_percentile(
         halo_table['vmax_at_mpeak_percentile'], 0.5)
 
+    halo_table['orphan_mass_loss_percentile'] = -1.
+    halo_table['orphan_mass_loss_percentile'][halo_table['orphan']] = np.load(
+            os.path.join(dirname, 'orphan_mass_loss_percentile.npy'))
+    halo_table['orphan_vmax_at_mpeak_percentile'] = -1.
+    halo_table['orphan_vmax_at_mpeak_percentile'][halo_table['orphan']] = np.load(
+            os.path.join(dirname, 'orphan_vmax_at_mpeak_percentile.npy'))
+    halo_table['orphan_vmax_loss_percentile'] = -1.
+    halo_table['orphan_vmax_loss_percentile'][halo_table['orphan']] = np.load(
+            os.path.join(dirname, 'orphan_vmax_loss_percentile.npy'))
+
+    halo_table['orphan_fixed_mpeak_mhost_percentile'] = -1.
+    halo_table['orphan_fixed_mpeak_mhost_percentile'][halo_table['orphan']] = np.load(
+            os.path.join(dirname, 'orphan_fixed_mpeak_mhost_percentile.npy'))
+
     halo_table['zpeak'] = 1./halo_table['mpeak_scale']-1.
 
     rvir_peak_physical_unity_h = halo_mass_to_halo_radius(halo_table['mpeak'],
@@ -243,3 +257,15 @@ def moustakas_sham(sham_subhalo_property, scatter):
     return moustakas_af.match(calc_number_densities(sham_subhalo_property, Lbox_h0p7),
                 scatter=scatter, do_add_scatter=True, do_rematch=True)
 
+
[…]

### 2017-10-31 paper/galsize_paper.tex
Updated figures

@@
 We use this model to predict how galaxy lensing, $\Delta\Sigma,$ should depend on $\rhalf$ for $\mstar-$complete samples.
-Other simple empirical models fail the clustering test, such as models in which galaxy size is related to stellar mass alone, and models that treat splashback galaxies as ordinary centrals; these failures persist even when accounting for possible effects from satellite stripping and orphan galaxies.
+Other simple empirical models fail the clustering test, such as models in which galaxy size is related to stellar mass alone; these failures persist even when accounting for possible effects from satellite stripping and orphan galaxies.
 Our results suggest that the relative size of centrals and satellites is predetermined at the time of satellite infall, and that a remarkably simple galaxy--halo scaling relation emerges from the complex physics regulating galaxy size.

### 2017-10-31 galsize_models/models/load_baseline_catalogs.py

@@ -227,10 +227,19 @@ def load_orphan_subhalos():
 
     halo_table['zpeak'] = 1./halo_table['mpeak_scale']-1.
 
+    halo_table['zpeak_no_splashback'] = 0.
+    satmask = halo_table['upid'] != -1
+    halo_table['zpeak_no_splashback'][satmask] = halo_table['zpeak'][satmask]
+
     rvir_peak_physical_unity_h = halo_mass_to_halo_radius(halo_table['mpeak'],
                                 Planck15, halo_table['zpeak'], 'vir')
     rvir_peak_physical = rvir_peak_physical_unity_h/Planck15.h
     halo_table['rvir_zpeak'] = rvir_peak_physical*1000.
+
+    rvir_peak_no_spl_physical_unity_h = halo_mass_to_halo_radius(halo_table['mpeak'],
+                                Planck15, halo_table['zpeak_no_splashback'], 'vir')
+    rvir_peak_no_spl_physical = rvir_peak_no_spl_physical_unity_h/Planck15.h
+    halo_table['rvir_zpeak_no_splashback'] = rvir_peak_no_spl_physical*1000.
 
     halo_table['hostid'] = np.nan
     hostmask = halo_table['upid'] == -1

### 2017-11-01 paper/galsize_paper.tex
Updated paper figures

@@
 
-%---------------------------------------------------------------------------------------------------
-\begin{figure}
-\centering
-\includegraphics[width=8cm]{FIGS/rs_correlation_visual.pdf}
-\caption{
-{\bf Profile co-evolution model.} In this model, the log-normal distribution of galaxy sizes is determined by $\rmpeak,$ the physical size of the halo virial radius at the time the halo reaches its peak mass.
-Thus log-normal the shape of this curve is determined by $\langle\rhalf\vert\rmpeak\rangle=0.0125\rmpeak$ with $0.2$ dex of scatter.
-The profile co-evolution model further supposes that galaxy and halo profiles co-evolve across cosmic time.
-Thus within this log-normal distribution, for two halos with the same $\rmpeak,$ halos with larger scale radius at $\zpeak$ will host galaxies with above-average $\rhalf,$ and conversely for halos with smaller values of $\rspeak.$
-}
-\label{fig:coevolutionmodel}
-\end{figure}
-%-----------------------------------------------------------------------------------------------------
-
 \subsubsection{$\mstar-$stripping model}
@@
 \centering
-\includegraphics[width=8cm]{FIGS/rhalf_vs_mstar_fiducial_model.pdf}
-\caption{The black curve shows the median $\rhalf-\mstar$ relation SDSS galaxies as measured in \citet{meert_etal15}.
+\includegraphics[width=8cm]{FIGS/rvir_only_rhalf_vs_mstar_sham_model.pdf}
+\caption{
+The black curve shows the median $\rhalf-\mstar$ relation SDSS galaxies as measured in \citet{meert_etal15}.
 The two gray bands enveloping the black curve show the $50\%$ and $90\%$ percentile regions.
@@
 %---------------------------------------------------------------------------------------------------
+\begin{figure}
+\centering
+\includegraphics[width=8cm]{FIGS/baseline_sham_orphans.pdf}
+\caption{some caption}
+\label{fig:baseline_sham_clustering}
+\end{figure}
+%-----------------------------------------------------------------------------------------------------
+
+%---------------------------------------------------------------------------------------------------
 \begin{figure*}
 \centering
-\includegraphics[width=12cm]{FIGS/penultimate_clustering_ratios_no_orphans.pdf}
+\includegraphics[width=12cm]{FIGS/rvir_only_wp_large_small_absolute.pdf}
+\caption{some caption}
+\label{fig:rvir_only_clustering_absolute}
+\end{figure*}
+%-----------------------------------------------------------------------------------------------------
+
+%---------------------------------------------------------------------------------------------------
+\begin{figure*}
+\centering
+\includegraphics[width=12cm]{FIGS/rvir_only_wp_ratios.pdf}
 \caption{
 {\bf $\rhalf-$dependence of galaxy clustering.}
-Points with error bars show new SDSS measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj.$ We define a galaxy as ``large" or ``small" according to whether it is above or below the median size for its stellar mass, so that in each panel, the stellar mass functions of the ``large" and ``small" subsamples are identical, as described in the text.
+%Points with error bars show new SDSS measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj.$ We define a galaxy as ``large" or ``small" according to whether it is above or below the median size for its stellar mass, so that in each panel, the stellar mass functions of the ``large" and ``small" subsamples are identical, as described in the text.
 The y-axis shows {\em clustering strength ratios,} so that, for example, a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of comparable stellar mass.
 Each panel shows results separately for different volume-limited $\mstar-$threshold samples; predictions of three different models are shown in each panel.
-See \S\ref{subsec:model} for a description of each model.}
+See \S\ref{subsec:model} for a description of each model.
+}
 \label{fig:clustering_ratio_upshot}
@@
 \centering
-\includegraphics[width=8cm]{FIGS/cen_sat_sizes.pdf}
+\includegraphics[width=8cm]{FIGS/rvir_only_cen_sat_sizes.pdf}
 \caption{
-{\bf Relative sizes of centrals and satellites.} In a narrow bin of halo mass $\mhalo=\mpeak\approx10^{12}\msun,$ we show the distribution of model galaxy sizes for different subpopulations galaxies, as predicted by the $\rvir-$only model.
+{\bf Relative sizes of centrals and satellites.} 
+In a narrow bin of halo mass $\mhalo=\mpeak\approx10^{12}\msun,$ we show the distribution of model galaxy sizes for different subpopulations galaxies, as predicted by the $\rvir-$only model.
 The red histogram shows the sizes of satellites; the blue histogram shows host halos that have never passed inside the virial radius of a larger halo (``true centrals"); the green histogram host halos that were subhalos inside a larger at some point in their past history (``splashback halos").
@@
 \centering
-\includegraphics[width=8cm]{FIGS/penultimate_clustering_ratios_alternate_models.pdf}
+\includegraphics[width=8cm]{FIGS/alt_model_wp_ratios.pdf}
 \caption{
-{\bf Impact of tidal stripping and orphan satellites.} In all panels, the axes and points with error bars are the same as in Figure \ref{fig:clustering_ratio_upshot}.
+{\bf Impact of tidal stripping.} 
+In all panels, the axes and points with error bars are the same as in Figure \ref{fig:clustering_ratio_upshot}.
 The dashed curves (``$\rvir-$only model") and solid curves (``profile co-evolution model") from  Figure \ref{fig:clustering_ratio_upshot} are also shown for convenience.
@@
 \end{figure}
+%-----------------------------------------------------------------------------------------------------
+
+%---------------------------------------------------------------------------------------------------
+%\begin{figure}
+%\centering
+%\includegraphics[width=8cm]{FIGS/sdss_size_dependent_clustering_9p75_to_10p25.pdf}
+%\caption{
+%{\bf Some caption.} 
+%}
+%\label{fig:strippingorphans}
+%\end{figure}
+%-----------------------------------------------------------------------------------------------------
+
+%---------------------------------------------------------------------------------------------------
+\begin{figure*}
+\centering
+\includegraphics[width=8cm]{FIGS/blue_sdss_size_dependent_clustering_9p75_to_10p25.pdf}
+\includegraphics[width=8cm]{FIGS/red_sdss_size_dependent_clustering_9p75_to_10p25.pdf}
+\includegraphics[width=8cm]{FIGS/disk_sdss_size_dependent_clustering_9p75_to_10p25.pdf}
+\includegraphics[width=8cm]{FIGS/bulge_sdss_size_dependent_clustering_9p75_to_10p25.pdf}
+\caption{
+{\bf Some caption.} 
+}
+\label{fig:strippingorphans}
+\end{figure*}
 %-----------------------------------------------------------------------------------------------------

### 2017-11-01 paper/galsize_paper.tex
Minor correction to small/large SDSS sample definitions. Updated all figures and measurements
Minor update to text

@@
 
+\usepackage{lmodern}
+
+\usepackage{amsmath}
+\usepackage{amstext}
 \usepackage{amssymb}
+\usepackage{yfonts}
+
 \usepackage{epsfig}
-\usepackage{amsmath}
+\usepackage{graphicx}
 \usepackage{color}
+
+\usepackage[lowtilde]{url}
+\usepackage{hyperref}
 
@@
 This catalog is based on Data Release 10 of the Sloan Digital Sky Survey \citep[SDSS,][]{ahn_etal14}, with improvements to the photometry pipeline and light profile fitting methods \citep{vikram_etal10,bernardi_etal13,bernardi_etal14,meert_etal13}.
-In the version of this catalog that we use, two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile to determine the half-light radius $\rhalf.$ We apply the \citet{bell_etal03} mass-to-light ratio to the $r-$band flux and $g-r$ colors in this catalog to obtain an estimate for the total stellar mass $\mstar$ of every galaxy.
+In the version of this catalog that we use, two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile to determine the half-light radius $\rhalf.$ We use stellar mass measurements made available through the MPA-JHU catalog \citep{kauffmann_etal03,brinchmann_etal04}, allowing us to define volume-limited samples of galaxies according to the same completeness cuts used in \citet{behroozi_etal15} (see Figure 2).
+
 We calculate two-point clustering $\wproj$ of our SDSS galaxy sample using line-of-sight projection of $\pi_{\rm max}=20\mpc$ using the {\tt correl} program in {\tt UniverseMachine}.
+{\color{red} PSB: Please fill in details about {\tt correl} here}.
 
-As the bedrock of our modeling, we use the catalog of {\tt Rockstar} subhalos identified at $z=0$ in the Bolshoi-Planck simulation \citep{klypin_etal11,behroozi12_rockstar,behroozi12_consistent_trees,riebe_etal13,rodriguez_puebla16_bolplanck}.
-The particular version of the catalog we use is made publicly available through {\tt Halotools} \citep{hearin_etal16}, with {\tt version\_name} = `halotools\_v0p4'.
+As the bedrock of our modeling, we use the publicly available\footnote{\url{http://www.slac.stanford.edu/~behroozi/BPlanck\_Hlists}} catalog of {\tt Rockstar} subhalos identified at $z=0$ in the Bolshoi-Planck simulation \citep{klypin_etal11,behroozi12_rockstar,behroozi12_consistent_trees,riebe_etal13,rodriguez_puebla16_bolplanck}.
 
@@
 The phase space evolution of orphans is approximated by following a point mass evolving in the host halo potential according to the orbital parameters of the subhalo at the time of disruption; the evolution of subhalo mass and circular velocity is approximated using the semi-analytic model presented in \citet{jiang_vdB14}.
+{\color{red} PSB: Make sure you agree with my description of your orphan treatment.}
 
@@
 
+\subsection{Classifying large vs. small galaxies}
+\label{subsec:sizedef}
+
+Because galaxy clustering has well-known dependence upon $\mstar$ that is not the subject of this work, we wish to remove this influence and focus purely on the relationship between $\rhalf$ and $\wproj(\rproj).$ To do so, we determine the value $\langle\rhalf\vert\mstar\rangle$ by computing a sliding median of $\rhalf,$ calculated using a window of width $N_{\rm gal}=1000.$ Each galaxy is categorized as either ``large" or ``small" according to whether it is above or below the median value appropriate for its stellar mass.
+Using this technique, we stress that for any $\mstar-$threshold sample, the SMF of the ``large" and ``small" subsamples are identical, by construction.
+See Figure~\ref{fig:sizedefinition}.
+
+%---------------------------------------------------------------------------------------------------
+\begin{figure}
+\centering
+\includegraphics[width=8cm]{FIGS/sdss_small_large_sample_definitions.pdf}
+\caption{
+{\bf Definition of small and large galaxy samples.} 
+}
+\label{fig:sizedefinition}
+\end{figure}
+%-----------------------------------------------------------------------------------------------------
+
 \section{Galaxy-Halo Model}
@@
 
-We map $\mstar$ onto subhalos with the best-fit stellar-to-halo mass relation from \citet{moster_etal13}:
+We map $\mstar$ onto subhalos using deconvolution abundance matching on the orphan-supplemented Bolshoi-Planck subhalo catalog, as described in detail in the Appendix.
 
-\begin{equation}
-\label{eq:smhm}
-\langle\mstar/\mhalo\rangle = 2N\left[(\mhalo/M_{1})^{-\beta} + (\mhalo/M_1)^{\gamma}\right]^{-1}.
-\end{equation}
-For halo mass $\mhalo$ we use $\mpeak,$ the largest value of $\mvir$ ever attained along the main progenitor branch of the subhalo.
-
-The values of the best-fit parameters in \citet{moster_etal13} were fit to a stellar mass function (SMF) with values $\mstar^{\rm MPA-JHU}$ based on the MPA-JHU catalog \citep{kauffmann_etal03,brinchmann_etal04}, which differs from the SMF in our galaxy sample \citep[see, e.g.,][]{bernardi_etal14}.
-We account for this difference by manually tabulating the median value $\langle\mstar^{\rm Meert+15}\vert\mstar^{\rm MPA-JHU}\rangle$ in logarithmic bins spanning $9 < \log_{10}\mstar^{\rm MPA-JHU}/\msun < 12,$ and applying the median correction to the Monte Carlo realization of the mock galaxy sample.
-This results in a typical boost of $\sim0.25$ dex at $\mstar^{\rm MPA-JHU}\approx10^{9.75}\msun,$ and $\sim0.4$ dex at $\mstar^{\rm MPA-JHU}\approx10^{11.5}\msun.$
+%For halo mass $\mhalo$ we use $\mpeak,$ the largest value of $\mvir$ ever attained along the main progenitor branch of the subhalo.
 
@@
 \label{eq:fiducial_model}
-\rhalf = 0.0125\rvir
+\rhalf = 0.01\rvir
 \eeq
@@
 For the model we refer to as the ``$\rvir-$only model", we add uncorrelated log-normal scatter of $\sigmarhalf=0.2$ dex to generate a Monto Carlo realization of the model population.
-
-\subsubsection{Profile co-evolution model}
-\label{subsubsec:coevolutionmodel}
-
-The ``profile co-evolution" model is identical to the $\rvir-$only model, but the scatter in $\rhalf$ at fixed $\rmpeak$ is no longer purely stochastic, and is instead correlated with $\vmaxmpeak,$ defined as the value of $\vmax$ at $\zpeak.$ In this way, $\rmpeak$ statistically determines the distribution of available sizes, but halos with extended dark matter profiles and large scale radii $R_{\rm s}$ host galaxies with above-average sizes, while halos with small $R_{\rm s}$ host smaller galaxies.
-See Figure \ref{fig:coevolutionmodel} for a visual illustration of this residual correlation.
-We implement scatter correlations using the {\tt halotools.empirical\_models.conditional\_abunmatch} function, which generalizes the Conditional Abundance Matching technique described in \citet{hearin_etal13b}.
 
@@
 
-In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ The black curve enveloped by the gray bands show the scaling relation for our SDSS galaxy sample, while the blue curve shows the median relation $\langle\rhalf\vert\mstar\rangle$ implied by the profile co-evolution model described in \S\ref{sec:model}.
+In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ The black curve enveloped by the gray bands show the scaling relation for our SDSS galaxy sample, while the blue curve shows the median relation $\langle\rhalf\vert\mstar\rangle$ implied by the $\rvir-$only model described in \S\ref{sec:model}.
 This figure shows that models in which $\rhalf\propto\rvir$ can naturally give rise to the characteristic curvature in the $\langle\rhalf\vert\mstar\rangle$ relation, confirming the results in \citet{kravtsov13} in a forward modeling context.
@@
 The two gray bands enveloping the black curve show the $50\%$ and $90\%$ percentile regions.
-The blue curve shows profile co-evolution model in which $\langle\rhalf\vert\rvir\rangle=0.0125\rvir,$ as in \citet{kravtsov13}.
+The blue curve shows $\rvir-$only model in which $\langle\rhalf\vert\rvir\rangle=0.0125\rvir,$ as in \citet{kravtsov13}.
 This figure confirms that a linear relationship between $\rvir$ and $\rhalf,$ convolved against the nonlinear relationships between $\rvir, \mhalo$ and $\mstar,$  predicts the characteristic curvature in the relation $\langle\rhalf\vert\mstar\rangle$ over a wide range in mass.
@@
 
-In Figure \ref{fig:clustering_ratio_upshot} we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj(\rproj).$ Because galaxy clustering has well-known dependence upon $\mstar$ that is not the subject of this work, we wish to remove this influence and focus purely on the relationship between $\rhalf$ and $\wproj(\rproj).$ To do so, we determine the value $\langle\rhalf\vert\mstar\rangle$ by computing a sliding median of $\rhalf,$ calculated using a window of width $N_{\rm gal}=1000.$ Each galaxy is categorized as either ``large" or ``small" according to whether it is above or below the median value appropriate for its stellar mass.
-Using this technique, we stress that for any $\mstar-$threshold sample, the SMF of the ``large" and ``small" subsamples are identical, by construction.
+In Figure \ref{fig:clustering_ratio_upshot} we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj(\rproj).$
 
@@
 
-\subsection{Tidal Stripping and Orphan Satellites}
+\subsection{Satellite Mass Loss}
 \label{subsec:orphan_stripping}
@@
 %---------------------------------------------------------------------------------------------------
-%\begin{figure}
-%\centering
-%\includegraphics[width=8cm]{FIGS/sdss_size_dependent_clustering_9p75_to_10p25.pdf}
-%\caption{
-%{\bf Some caption.} 
-%}
-%\label{fig:strippingorphans}
-%\end{figure}
-%-----------------------------------------------------------------------------------------------------
-
-%---------------------------------------------------------------------------------------------------
 \begin{figure*}
@@
 \end{figure*}
+%-----------------------------------------------------------------------------------------------------
+
+%---------------------------------------------------------------------------------------------------
+\begin{figure}
+\centering
+\includegraphics[width=8cm]{FIGS/rvir_only_lensing_prediction.pdf}
+\caption{
+{\bf Prediction for $\rhalf-$dependence of galaxy lensing.} 
+}
+\label{fig:strippingorphans}
+\end{figure}
 %-----------------------------------------------------------------------------------------------------
@@
 
-Explanations for differences between the sizes of centrals and satellites fall into two categories, depending on whether or not the processes involved are specific to post-infall physics.
+%Explanations for differences between the sizes of centrals and satellites fall into two categories, depending on whether or not the processes involved are specific to post-infall physics.
 One obvious possibility that could lead to satellites being smaller than centrals of the same $\mhalo$ is tidal stripping: satellite $\mstar$ could decrease after infall, reducing the size of the galaxy.
@@
 
-Both the $\rvir-$only model and the co-evolution model (see sections \S\ref{subsubsec:rvirmodel} and \S\ref{subsubsec:coevolutionmodel}, respectively) represent explanations falling into the second category, in which centrals and satellites of the same $\mhalo$ have different sizes due to their different evolutionary paths {\em prior} to satellite infall.
+%Both the $\rvir-$only model and the co-evolution model (see sections \S\ref{subsubsec:rvirmodel} and \S\ref{subsubsec:coevolutionmodel}, respectively) represent explanations falling into the second category, in which centrals and satellites of the same $\mhalo$ have different sizes due to their different evolutionary paths {\em prior} to satellite infall.
 For these models the story is very different: the influence of pre-infall co-evolution has a dramatic impact on $\rhalf-$clustering ratios, with a scale- and $\mstar-$dependence that closely resembles the SDSS signal.
@@
 
-The scope of this work is to serve as a pilot study in which we identify the chief ingredients that can influence the $\rhalf-$dependence of galaxy clustering.
+%The scope of this work is to serve as a pilot study in which we identify the chief ingredients that can influence the $\rhalf-$dependence of galaxy clustering.
 While our results suggest that our profile co-evolution model is giving the correct qualitative picture, our implementation cannot be correct in quantitative detail: the clustering ratios of this model shown in Figure \ref{fig:clustering_ratio_upshot} are too strong relative to SDSS.
@@
 
-In addition to varying the $\rhalf-\rspeak$ correlation strength, there are other factors that should be included in any proper likelihood analysis of galaxy size models.
+%In addition to varying the $\rhalf-\rspeak$ correlation strength, there are other factors that should be included in any proper likelihood analysis of galaxy size models.
 In particular, since the clustering signal is strongly influenced by differences between centrals and satellites, then the satellite fraction $F_{\rm sat}(\mstar)$ plays an important role in $\rhalf-$dependent clustering.
@@
 
-On the one hand, this degeneracy with the satellite fraction is unfortunate, because it means galaxy sizes does not leave a pure and unique signature on $\rhalf-$clustering ratios.
+%On the one hand, this degeneracy with the satellite fraction is unfortunate, because it means galaxy sizes does not leave a pure and unique signature on $\rhalf-$clustering ratios.
 However, this can also be viewed as an opportunity to extract tighter constraints on $F_{\rm sat}(\mstar),$ which are sorely needed to discriminate between competing models.
@@
 
-Previous studies of large-scale structure measured by SDSS indicate that morphological type has a significant influence on galaxy clustering \citep{skibba_etal08}.
+%Previous studies of large-scale structure measured by SDSS indicate that morphological type has a significant influence on galaxy clustering \citep{skibba_etal08}.
 Because morphology is covariant with star-formation rate (SFR) and $\rhalf,$ accounting for this dependency will require simultaneously modeling each of these variables.
 
-To date, such a task has been beyond the purview of empirical models.
+%To date, such a task has been beyond the purview of empirical models.
 However, recent progress has substantially improved the richness of the predictions that galaxy-halo models are capable of \citep{becker15,cohn17,moster_etal17}.
@@
 \item Simple empirical models in which $\rhalf$ is regulated by $\mstar,$ rather than $\mhalo,$ are grossly discrepant with the observed clustering signal.
-\item The ``co-evolution model" shown with solid curves in Figure \ref{fig:clustering_ratio_upshot} exhibits a clustering signal that is strikingly similar to that seen in SDSS.
+%\item The ``co-evolution model" shown with solid curves in Figure \ref{fig:clustering_ratio_upshot} exhibits a clustering signal that is strikingly similar to that seen in SDSS.
 In this model, $\rhalf$ is statistically regulated by $\rmpeak,$ the halo virial radius $\rvir$ at the time of peak halo mass, with strong residual correlation with $\rspeak,$ the halo scale radius at that time.

### 2017-11-01 paper/galsize_paper.tex
Updated a few captions

@@
 \newcommand{\wpall}{w_{\rm p}^{\rm all}}
+
+\newcommand{\median}[2]{\langle{#1}\vert{#2}\rangle_{\rm median}}
 
@@
 \caption{
-{\bf Definition of small and large galaxy samples.} 
+{\bf Definition of ``small" and ``large" galaxies.} For a volume-limited SDSS galaxy sample defined by $M_{\ast}>10^{10.25}M_{\odot},$ we visually demonstrate how we classify galaxies into ``small" and ``large" subsamples.
+As described in detail in \S\ref{subsec:sizedef}, we compute the median value $\median{\rhalf}{\mstar}$ using a sliding window with a width of $1000$ galaxies at each value of $\mstar.$ The {\em left panel} shows a histogram of the stellar masses, confirming that our method yields identical stellar mass functions for the two subsamples.
+The {\em right panel} shows histograms of $\rhalf$ for the two subsamples, which partially overlap due to the finite range of $\mstar$ in the volume-limited sample.
 }
@@
 
-In the first class of models we explore, we suppose that stellar mass $\mstar$ is the statistical regulator of $\rhalf,$ so that galaxy sizes are drawn from a log-normal distribution centered at $\langle\rhalf\vert\mstar\rangle,$ where $\mstar$ derives from the \citet{moster_etal13} relation described above in \S\ref{subsec:smhm}.
-To implement this model, for simplicity we directly tabulate $\langle\rhalf\vert\mstar\rangle$ from the data, rather than pursue a parametric form \citep[see, e.g.,][]{zhang_yang17}.
+In the first class of models we explore, we suppose that stellar mass $\mstar$ is the statistical regulator of $\rhalf,$ so that galaxy sizes are drawn from a log-normal distribution centered at $\median{\rhalf}{\mstar}.$ To implement this model, for simplicity we directly tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form \citep[see, e.g.,][]{zhang_yang17}.
 
@@
 \caption{
-The black curve shows the median $\rhalf-\mstar$ relation SDSS galaxies as measured in \citet{meert_etal15}.
+The black curve shows the median size-mass relation of SDSS galaxies as measured in \citet{meert_etal15}.
 The two gray bands enveloping the black curve show the $50\%$ and $90\%$ percentile regions.
-The blue curve shows $\rvir-$only model in which $\langle\rhalf\vert\rvir\rangle=0.0125\rvir,$ as in \citet{kravtsov13}.
-This figure confirms that a linear relationship between $\rvir$ and $\rhalf,$ convolved against the nonlinear relationships between $\rvir, \mhalo$ and $\mstar,$  predicts the characteristic curvature in the relation $\langle\rhalf\vert\mstar\rangle$ over a wide range in mass.
+The blue curve shows $\rvir-$only model in which $\median{\rhalf}{\rvir}=0.01\rvir.$ This figure confirms that a linear relationship between $\rvir$ and $\rhalf,$ convolved against the nonlinear relationships between $\rvir, \mhalo$ and $\mstar,$  predicts the characteristic curvature in the relation $\median{\rhalf}{\mstar}$ over a wide range in mass.
 }
@@
 \includegraphics[width=8cm]{FIGS/baseline_sham_orphans.pdf}
-\caption{some caption}
+\caption{
+{\bf SHAM + orphan clustering predictions.}
+Using the abundance matching methods described in \S\ref{subsec:smhm}, we compare the projected clustering of mock vs.
+SDSS galaxies.
+Each panel shows the comparison for a volume-limited sample defined by a different $\mstar-$threshold.
+Black points with jackknife-estimated error bars show SDSS measurements; solid red (black) curves show the abundance matching prediction including (excluding) the effect of orphan subhalos (see Appendix A).
+Including orphans mitigates the discrepancy in the clustering predicted by traditional, $\mpeak-$based SHAM based, though mild tension remains for $\mstar\gtrsim10^{10.75}\msun.$
+}
 \label{fig:baseline_sham_clustering}
@@
 
+\section*{Appendix: Treatment of Orphan Subhalos}
+
 \end{document}

### 2017-11-01 paper/galsize_paper.tex
Updated a few more captions

@@
 Each panel shows the comparison for a volume-limited sample defined by a different $\mstar-$threshold.
-Black points with jackknife-estimated error bars show SDSS measurements; solid red (black) curves show the abundance matching prediction including (excluding) the effect of orphan subhalos (see Appendix A).
+Black points with error bars show SDSS measurements; solid red (black) curves show the abundance matching prediction including (excluding) the effect of orphan subhalos (see Appendix A).
 Including orphans mitigates the discrepancy in the clustering predicted by traditional, $\mpeak-$based SHAM based, though mild tension remains for $\mstar\gtrsim10^{10.75}\msun.$
@@
 \includegraphics[width=12cm]{FIGS/rvir_only_wp_large_small_absolute.pdf}
-\caption{some caption}
+\caption{
+{\bf $\rhalf-$dependence of galaxy clustering.}
+Red and blue points with error bars show our SDSS measurements of the clustering of small and large galaxies, respectively.
+For each volume-limited sample of $\mstar-$complete galaxies, the small and large subsamples have identical stellar mass functions, as shown in Figure \ref{fig:sizedefinition}.
+Solid curves show the clustering predictions of the $\rvir-$only model described in \S\ref{subsubsec:rvirmodel}.
+The $\rvir-$only model inherits the shortcoming of ordinary abundance matching at $\mstar\gtrsim10^{10.75}\msun,$ although the model faithfully captures the {\em relative} clustering of small vs.
+large galaxies, as shown in Figure \ref{fig:clustering_ratio_upshot}.
+}
 \label{fig:rvir_only_clustering_absolute}
@@
 \caption{
-{\bf $\rhalf-$dependence of galaxy clustering.}
-%Points with error bars show new SDSS measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj.$ We define a galaxy as ``large" or ``small" according to whether it is above or below the median size for its stellar mass, so that in each panel, the stellar mass functions of the ``large" and ``small" subsamples are identical, as described in the text.
-The y-axis shows {\em clustering strength ratios,} so that, for example, a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of comparable stellar mass.
-Each panel shows results separately for different volume-limited $\mstar-$threshold samples; predictions of three different models are shown in each panel.
-See \S\ref{subsec:model} for a description of each model.
+{\bf $\rhalf-$dependence of galaxy clustering: clustering ratios.}
+Closely related to Figure \ref{fig:rvir_only_clustering_absolute}, the y-axes show {\em clustering strength ratios,} defined as $(w_{\rm p}^{\rm large} - w_{\rm p}^{\rm small})/w_{\rm p}^{\rm all}.$ Thus a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass.
+Solid curves show the clustering ratio predictions of the $\rvir-$only model described in \S\ref{subsubsec:rvirmodel}.
+Normalizing the measurements and predictions by $w_{\rm p}^{\rm all}$ scales away the shortcoming of ordinary abundance matching at high stellar mass (see Figure \ref{fig:baseline_sham_clustering}), highlighting the successful prediction of the $\rvir-$only model for the $\rhalf-$dependence of galaxy clustering.
 }
@@
 {\bf Relative sizes of centrals and satellites.} 
-In a narrow bin of halo mass $\mhalo=\mpeak\approx10^{12}\msun,$ we show the distribution of model galaxy sizes for different subpopulations galaxies, as predicted by the $\rvir-$only model.
-The red histogram shows the sizes of satellites; the blue histogram shows host halos that have never passed inside the virial radius of a larger halo (``true centrals"); the green histogram host halos that were subhalos inside a larger at some point in their past history (``splashback halos").
-In the $\rvir-$only model, galaxy size is set by the {\em physical} size of the virial radius at the time the halo attains its peak mass, naturally resulting in smaller sizes for satellites and backsplash centrals relative to true centrals of the same $\mpeak.$ The central/satellite size differences shown here are not enough to correctly predict the observed clustering ratios (see Figure \ref{fig:clustering_ratio_upshot}), motivating the $\mstar-$stripping and profile co-evolution models.
+In a narrow bin of halo mass $\mhalo\equiv\mpeak\approx10^{12}\msun,$ we show the distribution of model galaxy sizes for different subpopulations galaxies, as predicted by the $\rvir-$only model.
+The red histogram shows the sizes of satellites; the blue histogram shows host halos that have never passed inside the virial radius of a larger halo (``true centrals"); the green histogram host halos that were subhalos inside a larger at some point in their past history (``splashback centrals").
+In the $\rvir-$only model, galaxy size is set by the {\em physical} size of the virial radius at the time the halo attains its peak mass, naturally resulting in smaller sizes for satellites and splashback centrals relative to true centrals of the same $\mhalo.$
 }
@@
 In all panels, the axes and points with error bars are the same as in Figure \ref{fig:clustering_ratio_upshot}.
-The dashed curves (``$\rvir-$only model") and solid curves (``profile co-evolution model") from  Figure \ref{fig:clustering_ratio_upshot} are also shown for convenience.
-The dot-dashed curves show results for a model in which satellites lose mass after infall in a manner similar to what is seen in high-resolution hydrodynamical simulations, as described in \S\ref{subsubsec:strippingmodel}.
-The dotted curve shows results for the same model, but including the effect of ``orphan" galaxies that live in subhalos no longer resolved by {\tt Rockstar}.
+The solid green curves shows the prediction of the $\mstar-$only model, which is in gross tension with the data due to satellites having the same size as centrals of the same mass.
+The solid purple curves show results for a model in which satellites lose mass after infall in a manner similar to what is seen in high-resolution hydrodynamical simulations, as described in \S\ref{subsubsec:strippingmodel}.
+This produces satellites that are smaller than centrals, but the effect is too mild to correctly capture the observed clustering.
+Evidently, satellite-specific mass stripping plays a sub-dominant role in setting the relative size of centrals and satellites.
 }

### 2017-11-01 paper/galsize_paper.tex
Updated all figure captions

@@
 For each volume-limited sample of $\mstar-$complete galaxies, the small and large subsamples have identical stellar mass functions, as shown in Figure \ref{fig:sizedefinition}.
+Small galaxies cluster much more strongly relative to large galaxies of the same stellar mass.
 Solid curves show the clustering predictions of the $\rvir-$only model described in \S\ref{subsubsec:rvirmodel}.
@@
 \caption{
-{\bf Some caption.} 
+{\bf Distinct $\rhalf-$dependence of clustering for color- or morphology-selected galaxy samples.} 
+All panels show the clustering of galaxies in the same bin of stellar mass: $10^{9.75}<\mstar/\msun<10^{10.25}.$ In the {\em upper left} panel, we first select blue galaxies based on $g-r<0.6,$ and subsequently compute $\median{\rhalf}{\mstar}$ {\em of the color-selected sample}.
+This results in identical stellar mass function for large and small blue galaxy samples, in analogy to the left panel of Figure \ref{fig:sizedefinition}.
+The {\em upper right panel} shows results of the same procedure for ``red" galaxies, defined by $g-r>0.6.$ The top two panels show that for color-selected samples, the magnitude of the $\rhalf-$dependence of clustering is dramatically reduced, and changes sign, relative to $\mstar-$complete samples.
+Using the \citet{meert_etal15} measurements of the disk/bulge decomposition of the 2d $r-$band luminosity profile $L_{\rm r},$ the bottom left panel shows analogous results for disk-dominated galaxies defined by $L_{\rm r}^{\rm bulge}<L_{\rm r}^{\rm tot}/4;$ the bottom right panel shows results for bulge-dominated galaxies defined by $L_{\rm r}^{\rm disk}<L_{\rm r}^{\rm tot}/4.$
 }
@@
 \end{figure*}
-%-----------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
 
@@
 {\bf Prediction for $\rhalf-$dependence of galaxy lensing.} 
+Using the $\rvir-$only model described in \S\ref{subsubsec:rvirmodel}, we make predictions for as-yet-unseen measurements of the $\rhalf-$dependence of galaxy lensing of $\mstar-$complete samples.
+To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which the reverse is true: for both blue and red samples, $\Delta\Sigma$ of small galaxies is (weakly) suppressed relative to large galaxies.
+As a generic consequence of satellites being smaller than centrals of the same mass, we predict that the analogous measurement for $\mstar-$complete samples will show $\Delta\Sigma$ of small galaxies to be much stronger relative to large galaxies of the same stellar mass.
 }

### 2017-11-01 paper/galsize_paper.tex
Reworked text in conclusions section

@@
 Our results suggest that the relative size of centrals and satellites is predetermined at the time of satellite infall, and that a remarkably simple galaxy--halo scaling relation emerges from the complex physics regulating galaxy size.
-%We make our python code publicly available to support ongoing efforts to generate realistic synthetic galaxy catalogs for large cosmological surveys.  
 \end{abstract}
@@
 \ben
-\item Small galaxies cluster more strongly than large galaxies of the same stellar mass, a new result.
+\item Small galaxies cluster more strongly than large galaxies of the same stellar mass.
 Differences between the clustering of small and large galaxies increase on small scales $R\lesssim1\mpc,$ and decrease with stellar mass.
@@
 The magnitude, scale-dependence, and $\mstar-$dependence of $\rhalf-$dependent clustering provides strong evidence that satellite galaxies are smaller than central galaxies of the same halo mass.
-\item Simple empirical models in which $\rhalf$ is regulated by $\mstar,$ rather than $\mhalo,$ are grossly discrepant with the observed clustering signal.
-%\item The ``co-evolution model" shown with solid curves in Figure \ref{fig:clustering_ratio_upshot} exhibits a clustering signal that is strikingly similar to that seen in SDSS.
-In this model, $\rhalf$ is statistically regulated by $\rmpeak,$ the halo virial radius $\rvir$ at the time of peak halo mass, with strong residual correlation with $\rspeak,$ the halo scale radius at that time.
-The success of this model supports the notion that galaxy and halo profiles co-evolve across many Gyr of cosmic time.
+\item A simple empirical model in which $\rhalf$ is set by halo $\rvir$ at the time of peak halo mass exhibits a clustering signal that is strikingly similar to that seen in SDSS. 
+\item Models in which $\rhalf$ is regulated by $\mstar,$ rather than $\mhalo,$ are grossly discrepant with the observed clustering signal, even when accounting for satellite mass stripping. 
+\item Taken together, our findings indicate that satellite-specific processes play a sub-dominant role in setting the relative size of centrals and satellites, which instead appears to be largely predetermined at the time of satellite infall.
 \een
@@
 We view the present work as a pilot study that motivates a Bayesian inference program to tightly constrain the galaxy size-halo connection with forward modeling techniques, in direct analogy to the literature on the stellar-to-halo-mass relation.
-Our publicly available code provides a simple means for cosmological surveys to generate synthetic galaxy populations with realistic sizes across the cosmic web.
+Our publicly available python code provides a simple means for cosmological surveys to generate synthetic galaxy populations with realistic sizes across the cosmic web.
 

### 2017-11-01 paper/galsize_paper.tex
Added some text to appendix on orphan treatment

@@
 \newcommand{\mhalo}{M_{\rm halo}}
+\newcommand{\mhost}{M_{\rm host}}
 \newcommand{\rvir}{R_{\rm vir}}
@@
 As the bedrock of our modeling, we use the publicly available\footnote{\url{http://www.slac.stanford.edu/~behroozi/BPlanck\_Hlists}} catalog of {\tt Rockstar} subhalos identified at $z=0$ in the Bolshoi-Planck simulation \citep{klypin_etal11,behroozi12_rockstar,behroozi12_consistent_trees,riebe_etal13,rodriguez_puebla16_bolplanck}.
-
-We additionally explore the potential existence of satellite galaxies that reside in subhalos that are not identified by halo-finder to the present day, so-called ``orphan galaxies" \citep[see, e.g.,][]{campbell_etal17}.
-We use an extension of {\tt Consistent Trees} that models the evolution of subhalos after disruption.
-The phase space evolution of orphans is approximated by following a point mass evolving in the host halo potential according to the orbital parameters of the subhalo at the time of disruption; the evolution of subhalo mass and circular velocity is approximated using the semi-analytic model presented in \citet{jiang_vdB14}.
-{\color{red} PSB: Make sure you agree with my description of your orphan treatment.}
+As described in \S\ref{subsec:sham}, we will use traditional abundance matching to connect stellar mass $\mstar$ with subhalo peak mass $\mpeak.$ To address issues related to subhalo incompleteness \citep{guo_white13}, we supplement the Bolshoi-Planck subhalo catalog with {\em all} subhalos that were ever identified by {\tt Rockstar}, including those that no longer appear in the standard catalog as subhalos that survive to $z=0.$ We describe our treatment of these ``orphan" subhalos in the Appendix.
 
@@
 
-\subsection{Stellar mass model}
-\label{subsec:smhm}
+\subsection{Abundance Matching}
+\label{subsec:sham}
 
 We map $\mstar$ onto subhalos using deconvolution abundance matching on the orphan-supplemented Bolshoi-Planck subhalo catalog, as described in detail in the Appendix.
-
-%For halo mass $\mhalo$ we use $\mpeak,$ the largest value of $\mvir$ ever attained along the main progenitor branch of the subhalo.
+Briefly, our abundance matching prescription is based $\mpeak,$ the largest value of $\mvir$ ever attained along the main progenitor branch of the subhalo.
 
@@
 
-\section*{Appendix: Treatment of Orphan Subhalos}
+\section*{Appendix: Treatment of Disrupted Subhalos}
+
+We use an extension of {\tt Consistent Trees} that models the evolution of subhalos after disruption.
+The phase space evolution of disrupted subhalos is approximated by following a point mass evolving in the host halo potential according to the orbital parameters of the subhalo at the time of disruption; the evolution of subhalo mass and circular velocity is approximated using the semi-analytic model presented in \citet{jiang_vdB14}.
+We then use the {\tt orphans} program in {\tt UniverseMachine} to walk through all the Bolshoi-Planck {\tt hlist} files, yielding the main progenitor information of every subhalo that was ever identified by {\tt Consistent Trees}.
+
+Since it is likely that some portion of these disrupted subhalos should be populated with model galaxies \citep{guo_white13, campbell_etal17}, in our initial application of deconvolution abundance matching we derive the $\mstar--\mpeak$ relation using {\em all} subhalos, including those that may be disrupted.
+We then apply a selection function to the disrupted subhalos, so that a fraction of these objects will host galaxies in our mock universe.
+We refer to this as the {\em orphan selection function}, $\mathcal{F}_{\rm orphan},$ which we consider to be an integral component of our application of abundance matching.
+
+Since a rigorous calibration of $\mathcal{F}_{\rm orphan}$ is beyond the scope of the present work, we instead opt for a simple parameterization that yields reasonably accurate recovery of the galaxy clustering signal observed in SDSS.
+We model $\mathcal{F}_{\rm orphan}=\mathcal{F}_{\rm orphan}(M_{\rm peak},M_{\rm host}),$ where $\mpeak$ is the peak mass of the disrupted subhalo, and $\mhost$ is the present-day virial mass of its $z=0$ host halo.
+For the $\mpeak-$dependence, we select $50\%$ of disrupted subhalos with $\mpeak=10^{11}\msun,$ $0\%$ of subhalos with $\mpeak=10^{13}\msun,$ linearly interpolating in $\log\mpeak$ for intermediate values of $\mpeak.$ At each $\mpeak,$ the selection of disrupted halos is not random; instead, we preferentially select the subhalos with larger $\mhost,$ which we intend to offset the increased difficulty of subhalo-finding algorithms to identify subhalos with especially small values of  $\mu\equiv\mpeak/\mhost.$
 

### 2017-11-02 paper/galsize_paper.tex
Reorganized results subsections

@@
 
+%---------------------------------------------------------------------------------------------------
+\begin{figure}
+\centering
+\includegraphics[width=8cm]{FIGS/baseline_sham_orphans.pdf}
+\caption{
+{\bf SHAM + orphan clustering predictions.}
+Using the abundance matching methods described in \S\ref{subsec:smhm}, we compare the projected clustering of mock vs.
+SDSS galaxies.
+Each panel shows the comparison for a volume-limited sample defined by a different $\mstar-$threshold.
+Black points with error bars show SDSS measurements; solid red (black) curves show the abundance matching prediction including (excluding) the effect of orphan subhalos (see Appendix A).
+Including orphans mitigates the discrepancy in the clustering predicted by traditional, $\mpeak-$based SHAM based, though mild tension remains for $\mstar\gtrsim10^{10.75}\msun.$
+}
+\label{fig:baseline_sham_clustering}
+\end{figure}
+%-----------------------------------------------------------------------------------------------------
+
 \subsection{Galaxy size models}
@@
 
+\subsection{Size-Mass Scaling Relation}
+\label{subsec:one_point_function}
+
 In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ The black curve enveloped by the gray bands show the scaling relation for our SDSS galaxy sample, while the blue curve shows the median relation $\langle\rhalf\vert\mstar\rangle$ implied by the $\rvir-$only model described in \S\ref{sec:model}.
@@
 Points with jackknife-estimated error bars show SDSS measurements, solid curves show the clustering ratios of model galaxies as predicted by the models described in \S\ref{sec:model}.
-
-%---------------------------------------------------------------------------------------------------
-\begin{figure}
-\centering
-\includegraphics[width=8cm]{FIGS/baseline_sham_orphans.pdf}
-\caption{
-{\bf SHAM + orphan clustering predictions.}
-Using the abundance matching methods described in \S\ref{subsec:smhm}, we compare the projected clustering of mock vs.
-SDSS galaxies.
-Each panel shows the comparison for a volume-limited sample defined by a different $\mstar-$threshold.
-Black points with error bars show SDSS measurements; solid red (black) curves show the abundance matching prediction including (excluding) the effect of orphan subhalos (see Appendix A).
-Including orphans mitigates the discrepancy in the clustering predicted by traditional, $\mpeak-$based SHAM based, though mild tension remains for $\mstar\gtrsim10^{10.75}\msun.$
-}
-\label{fig:baseline_sham_clustering}
-\end{figure}
-%-----------------------------------------------------------------------------------------------------
 
@@
 
-In the $\rvir-$only model, satellite and splashback galaxies are smaller than centrals of the same halo mass due to the physical size of their halo being smaller at earlier times $\zpeak.$ There are two distinct reasons why this feature results in small galaxies being more strongly clustered relative to larger galaxies of the same mass.
-First, satellite galaxies statistically occupy higher mass host halos that are more strongly clustered.
-In models where satellites are smaller than centrals, for any given $\mstar-$threshold the ``small" subsample will naturally have a higher satellite fraction, resulting in a negative clustering ratio as seen in SDSS data.
-Second, at fixed mass, halos of $L_\ast$ galaxies that form earlier are more strongly clustered, a phenomenon commonly known as {\em halo assembly bias}.
-Since splashback halos are typically earlier forming than true centrals, then models where splashback halos host smaller-than-average galaxies will naturally predict negative clustering ratios.
-
-In the $\mstar-$only model, in which $\rhalf$ is statistically set by present-day stellar mass with no other dependencies.
-Thus neither of the above features are present: satellites and centrals of the same mass have no differences in size, and there is essentially no $\rhalf-$dependence to galaxy clustering, in gross disagreement with our SDSS observations.
-
-Much more successful is the profile co-evolution model shown with the solid curves in Figure \ref{fig:clustering_ratio_upshot}.
-The strongly negative clustering ratios predicted by the assumption of profile co-evolution can be understood in terms of the same features discussed above.
-Figure \ref{fig:coevolutionmodel} shows that at fixed $\mpeak,$ larger galaxies will occupy halos with larger $\rspeak.$ Since halo concentration $c=\rvir/R_{\rm s},$ this implies that high-concentration galaxies will tend to host smaller galaxies.
-Both satellites and splashback centrals have higher concentration than true centrals, another manifestation of assembly bias, and so the assumption of profile co-evolution naturally results in an enhancement of the clustering ratios beyond the $\rvir-$only model.
-
-\subsection{Satellite Mass Loss}
-\label{subsec:orphan_stripping}
-
-We conclude this section with a discussion of Figure \ref{fig:strippingorphans}, which provides an estimate of how satellite mass stripping and orphan galaxies impact size-dependent clustering ratios.
-In the $\mstar-$stripping model described in \S\ref{subsubsec:strippingmodel}, satellites lose stellar mass in a way that mimics what is seen in high-resolution hydrodynamical simulations.
-This naturally results in an enhancement of size differences between satellites and centrals, and the dot-dashed curves in Figure \ref{fig:strippingorphans} show that produces the expected sign of the effect on the clustering ratios.
-The magnitude of the effect, however is not strong enough to remedy the discrepancy of the clustering predictions of the $\rvir-$only model.
-We discuss the physical implications of this result in \S\ref{subsec:satellite_discussion}.
-
-The dotted curves in Figure \ref{fig:strippingorphans} show results of the $\rvir-$only model applied to a subhalo catalog that includes a orphan halos.
-As described in \S\ref{}, orphan halos are subhalos that are no longer resolved by {\tt Rockstar}, but whose evolution is tracked in a post-processing phase.
-We apply the same mass-stripping model described in \S\ref{subsubsec:strippingmodel} to this subhalo catalog that includes orphan halos, keep all model galaxies that retain more than half of their stellar mass, and show results for the $\rvir-$only model applied to the resulting catalog.
-
-As the orphan catalog has a higher satellite fraction than the standard subhalo catalog, the negative boost shown the dotted curves in Figure \ref{fig:strippingorphans} is expected.
-Orphan halos also typically have earlier-than-average values of $\zpeak$ relative to ordinary subhalos, which also enhances differences between central and satellite sizes.
-See \S\ref{subsec:satellite_discussion} for further discussion.
-
 %---------------------------------------------------------------------------------------------------
@@
 %-----------------------------------------------------------------------------------------------------
+
+In the $\rvir-$only model, satellite and splashback galaxies are smaller than centrals of the same halo mass due to the physical size of their halo being smaller at earlier times $\zpeak.$ There are two distinct reasons why this feature results in small galaxies being more strongly clustered relative to larger galaxies of the same mass.
+First, satellite galaxies statistically occupy higher mass host halos that are more strongly clustered.
+In models where satellites are smaller than centrals, for any given $\mstar-$threshold the ``small" subsample will naturally have a higher satellite fraction, resulting in a negative clustering ratio as seen in SDSS data.
+Second, at fixed mass, halos of $L_\ast$ galaxies that form earlier are more strongly clustered, a phenomenon commonly known as {\em halo assembly bias}.
+Since splashback halos are typically earlier forming than true centrals, then models where splashback halos host smaller-than-average galaxies will naturally predict negative clustering ratios.
+
+In the $\mstar-$only model, in which $\rhalf$ is statistically set by present-day stellar mass with no other dependencies.
+Thus neither of the above features are present: satellites and centrals of the same mass have no differences in size, and there is essentially no $\rhalf-$dependence to galaxy clustering, in gross disagreement with our SDSS observations.
+
+\subsection{Failure of $\mstar-$based Models}
+\label{subsec:orphan_stripping}
+
+We conclude this section with a discussion of Figure \ref{fig:strippingorphans}, which provides an estimate of how satellite mass stripping and orphan galaxies impact size-dependent clustering ratios.
+In the $\mstar+$stripping model described in \S\ref{subsubsec:strippingmodel}, satellites lose stellar mass in a way that mimics what is seen in high-resolution hydrodynamical simulations.
+This naturally results in an enhancement of size differences between satellites and centrals, and the dot-dashed curves in Figure \ref{fig:strippingorphans} show that produces the expected sign of the effect on the clustering ratios.
+The magnitude of the effect, however is not strong enough to remedy the discrepancy of the clustering predictions of the $\mstar-$only model.
+We discuss the physical implications of this result in \S\ref{subsec:satellite_discussion}.
 
@@
 %-----------------------------------------------------------------------------------------------------
+
+The dotted curves in Figure \ref{fig:strippingorphans} show results of the $\rvir-$only model applied to a subhalo catalog that includes a orphan halos.
+As described in \S\ref{}, orphan halos are subhalos that are no longer resolved by {\tt Rockstar}, but whose evolution is tracked in a post-processing phase.
+We apply the same mass-stripping model described in \S\ref{subsubsec:strippingmodel} to this subhalo catalog that includes orphan halos, keep all model galaxies that retain more than half of their stellar mass, and show results for the $\rvir-$only model applied to the resulting catalog.
+
+As the orphan catalog has a higher satellite fraction than the standard subhalo catalog, the negative boost shown the dotted curves in Figure \ref{fig:strippingorphans} is expected.
+Orphan halos also typically have earlier-than-average values of $\zpeak$ relative to ordinary subhalos, which also enhances differences between central and satellite sizes.
+See \S\ref{subsec:satellite_discussion} for further discussion.
+
+\subsection{The Role of Morphology and Color}
+\label{subsec:colormorph}
 

### 2017-11-02 paper/galsize_paper.tex
Switched terminology from  to

@@
 
-\subsubsection{$\mstar-$only model}
+\subsubsection{$\mstar-$based model}
 \label{subsubsec:mstaronlymodel}
@@
 
-\subsubsection{$\rvir-$only model}
+\subsubsection{$\rvir-$based model}
 \label{subsubsec:rvirmodel}
@@
 where for $\Delta_{\rm vir}(\zpeak)$ we use the fitting function to the ``virial" definition used in \citet{bryan_norman98}.
-For the model we refer to as the ``$\rvir-$only model", we add uncorrelated log-normal scatter of $\sigmarhalf=0.2$ dex to generate a Monto Carlo realization of the model population.
+For the model we refer to as the ``$\rvir-$based model", we add uncorrelated log-normal scatter of $\sigmarhalf=0.2$ dex to generate a Monto Carlo realization of the model population.
 
@@
 
-In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ The black curve enveloped by the gray bands show the scaling relation for our SDSS galaxy sample, while the blue curve shows the median relation $\langle\rhalf\vert\mstar\rangle$ implied by the $\rvir-$only model described in \S\ref{sec:model}.
+In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ The black curve enveloped by the gray bands show the scaling relation for SDSS galaxies, while the blue curve shows the median relation  $\median{\rhalf}{\mstar}$ implied by the $\rvir-$based model described in \S\ref{sec:model}.
 This figure shows that models in which $\rhalf\propto\rvir$ can naturally give rise to the characteristic curvature in the $\langle\rhalf\vert\mstar\rangle$ relation, confirming the results in \citet{kravtsov13} in a forward modeling context.
@@
 The two gray bands enveloping the black curve show the $50\%$ and $90\%$ percentile regions.
-The blue curve shows $\rvir-$only model in which $\median{\rhalf}{\rvir}=0.01\rvir.$ This figure confirms that a linear relationship between $\rvir$ and $\rhalf,$ convolved against the nonlinear relationships between $\rvir, \mhalo$ and $\mstar,$  predicts the characteristic curvature in the relation $\median{\rhalf}{\mstar}$ over a wide range in mass.
+The blue curve shows $\rvir-$based model in which $\median{\rhalf}{\rvir}=0.01\rvir.$ This figure confirms that a linear relationship between $\rvir$ and $\rhalf,$ convolved against the nonlinear relationships between $\rvir, \mhalo$ and $\mstar,$  predicts the characteristic curvature in the relation $\median{\rhalf}{\mstar}$ over a wide range in mass.
 }
@@
 
-We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds, $\mstar>10^{9.75}\msun,$ $\mstar>10^{10.25}\msun,$ $\mstar>10^{10.75}\msun,$ and $\mstar>10^{11.25}\msun.$ We make the same measurements for each volume-limited $\mstar-$threshold sample {\em without} splitting on size, giving us measurements $\wpall, \wplarge,$ and $\wpsmall$ for each threshold sample.
+We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds, $\mstar>10^{9.75}\msun,$ $\mstar>10^{10.25}\msun,$ $\mstar>10^{10.75}\msun,$ and $\mstar>10^{11}\msun.$ We make the same measurements for each volume-limited $\mstar-$threshold sample {\em without} splitting on size, giving us measurements $\wpall, \wplarge,$ and $\wpsmall$ for each threshold sample.
 This allow us to compute the ratio $(\wplarge-\wpsmall)/\wpall,$ which we refer to as {\em the $\rhalf$ clustering ratio}.
@@
 Small galaxies cluster much more strongly relative to large galaxies of the same stellar mass.
-Solid curves show the clustering predictions of the $\rvir-$only model described in \S\ref{subsubsec:rvirmodel}.
-The $\rvir-$only model inherits the shortcoming of ordinary abundance matching at $\mstar\gtrsim10^{10.75}\msun,$ although the model faithfully captures the {\em relative} clustering of small vs.
+Solid curves show the clustering predictions of the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}.
+The $\rvir-$based model inherits the shortcoming of ordinary abundance matching at $\mstar\gtrsim10^{10.75}\msun,$ although the model faithfully captures the {\em relative} clustering of small vs.
 large galaxies, as shown in Figure \ref{fig:clustering_ratio_upshot}.
@@
 Closely related to Figure \ref{fig:rvir_only_clustering_absolute}, the y-axes show {\em clustering strength ratios,} defined as $(w_{\rm p}^{\rm large} - w_{\rm p}^{\rm small})/w_{\rm p}^{\rm all}.$ Thus a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass.
-Solid curves show the clustering ratio predictions of the $\rvir-$only model described in \S\ref{subsubsec:rvirmodel}.
-Normalizing the measurements and predictions by $w_{\rm p}^{\rm all}$ scales away the shortcoming of ordinary abundance matching at high stellar mass (see Figure \ref{fig:baseline_sham_clustering}), highlighting the successful prediction of the $\rvir-$only model for the $\rhalf-$dependence of galaxy clustering.
+Solid curves show the clustering ratio predictions of the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}.
+Normalizing the measurements and predictions by $w_{\rm p}^{\rm all}$ scales away the shortcoming of ordinary abundance matching at high stellar mass (see Figure \ref{fig:baseline_sham_clustering}), highlighting the successful prediction of the $\rvir-$based model for the $\rhalf-$dependence of galaxy clustering.
 }
@@
 
-The salient feature of the clustering ratio measurements is that they are negative: small galaxies cluster more strongly than large galaxies of the same stellar mass, a new result.
-This feature also holds true for galaxies predicted by the $\rvir-$only model.
+The salient feature of the clustering ratio measurements is that they are negative: small galaxies cluster more strongly than large galaxies of the same stellar mass.
+This feature also holds true for galaxies predicted by the $\rvir-$based model.
 This result may be surprising, since $\rhalf\propto\rvir,$ halo mass $\rvir\propto\mhalo^{1/3},$ and clustering strength increases with $\mvir.$ Based on this simple argument, one would expect the opposite trend to the measurements shown here.
@@
 {\bf Relative sizes of centrals and satellites.}
-In a narrow bin of halo mass $\mhalo\equiv\mpeak\approx10^{12}\msun,$ we show the distribution of model galaxy sizes for different subpopulations galaxies, as predicted by the $\rvir-$only model.
+In a narrow bin of halo mass $\mhalo\equiv\mpeak\approx10^{12}\msun,$ we show the distribution of model galaxy sizes for different subpopulations galaxies, as predicted by the $\rvir-$based model.
 The red histogram shows the sizes of satellites; the blue histogram shows host halos that have never passed inside the virial radius of a larger halo (``true centrals"); the green histogram host halos that were subhalos inside a larger at some point in their past history (``splashback centrals").
-In the $\rvir-$only model, galaxy size is set by the {\em physical} size of the virial radius at the time the halo attains its peak mass, naturally resulting in smaller sizes for satellites and splashback centrals relative to true centrals of the same $\mhalo.$
+In the $\rvir-$based model, galaxy size is set by the {\em physical} size of the virial radius at the time the halo attains its peak mass, naturally resulting in smaller sizes for satellites and splashback centrals relative to true centrals of the same $\mhalo.$
 }
@@
 
-In the $\rvir-$only model, satellite and splashback galaxies are smaller than centrals of the same halo mass due to the physical size of their halo being smaller at earlier times $\zpeak.$ There are two distinct reasons why this feature results in small galaxies being more strongly clustered relative to larger galaxies of the same mass.
+In the $\rvir-$based model, satellite and splashback galaxies are smaller than centrals of the same halo mass due to the physical size of their halo being smaller at earlier times $\zpeak.$ There are two distinct reasons why this feature results in small galaxies being more strongly clustered relative to larger galaxies of the same mass.
 First, satellite galaxies statistically occupy higher mass host halos that are more strongly clustered.
@@
 
-In the $\mstar-$only model, in which $\rhalf$ is statistically set by present-day stellar mass with no other dependencies.
+In the $\mstar-$based model, in which $\rhalf$ is statistically set by present-day stellar mass with no other dependencies.
 Thus neither of the above features are present: satellites and centrals of the same mass have no differences in size, and there is essentially no $\rhalf-$dependence to galaxy clustering, in gross disagreement with our SDSS observations.
@@
 This naturally results in an enhancement of size differences between satellites and centrals, and the dot-dashed curves in Figure \ref{fig:strippingorphans} show that produces the expected sign of the effect on the clustering ratios.
-The magnitude of the effect, however is not strong enough to remedy the discrepancy of the clustering predictions of the $\mstar-$only model.
+The magnitude of the effect, however is not strong enough to remedy the discrepancy of the clustering predictions of the $\mstar-$based model.
 We discuss the physical implications of this result in \S\ref{subsec:satellite_discussion}.
@@
 In all panels, the axes and points with error bars are the same as in Figure \ref{fig:clustering_ratio_upshot}.
-The solid green curves shows the prediction of the $\mstar-$only model, which is in gross tension with the data due to satellites having the same size as centrals of the same mass.
+The solid green curves shows the prediction of the $\mstar-$based model, which is in gross tension with the data due to satellites having the same size as centrals of the same mass.
 The solid purple curves show results for a model in which satellites lose mass after infall in a manner similar to what is seen in high-resolution hydrodynamical simulations, as described in \S\ref{subsubsec:strippingmodel}.
@@
 
-The dotted curves in Figure \ref{fig:strippingorphans} show results of the $\rvir-$only model applied to a subhalo catalog that includes a orphan halos.
+The dotted curves in Figure \ref{fig:strippingorphans} show results of the $\rvir-$based model applied to a subhalo catalog that includes a orphan halos.
 As described in \S\ref{}, orphan halos are subhalos that are no longer resolved by {\tt Rockstar}, but whose evolution is tracked in a post-processing phase.
-We apply the same mass-stripping model described in \S\ref{subsubsec:strippingmodel} to this subhalo catalog that includes orphan halos, keep all model galaxies that retain more than half of their stellar mass, and show results for the $\rvir-$only model applied to the resulting catalog.
+We apply the same mass-stripping model described in \S\ref{subsubsec:strippingmodel} to this subhalo catalog that includes orphan halos, keep all model galaxies that retain more than half of their stellar mass, and show results for the $\rvir-$based model applied to the resulting catalog.
 
@@
 {\bf Prediction for $\rhalf-$dependence of galaxy lensing.}
-Using the $\rvir-$only model described in \S\ref{subsubsec:rvirmodel}, we make predictions for as-yet-unseen measurements of the $\rhalf-$dependence of galaxy lensing of $\mstar-$complete samples.
+Using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}, we make predictions for as-yet-unseen measurements of the $\rhalf-$dependence of galaxy lensing of $\mstar-$complete samples.
 To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which the reverse is true: for both blue and red samples, $\Delta\Sigma$ of small galaxies is (weakly) suppressed relative to large galaxies.
@@
 We have quantitatively tested this possibility with the $\mstar-$stripping model described in \S\ref{subsubsec:strippingmodel}.
-Comparing the clustering ratios of the ``$\rvir-$only" and ``$\rvir+$stripping" models in Figure \ref{fig:strippingorphans}, we find that the impact of physically motivated levels of satellite mass loss cannot explain the $\rhalf-$dependent clustering seen in SDSS.
+Comparing the clustering ratios of the ``$\rvir-$based" and ``$\rvir+$stripping" models in Figure \ref{fig:strippingorphans}, we find that the impact of physically motivated levels of satellite mass loss cannot explain the $\rhalf-$dependent clustering seen in SDSS.
 As an additional test, we reach the same conclusion when implementing an even more extreme $\mstar-$stripping model in which stellar mass loss is linearly proportional to halo mass loss \citep[][Model 1]{watson_etal12}.
 
-%Both the $\rvir-$only model and the co-evolution model (see sections \S\ref{subsubsec:rvirmodel} and \S\ref{subsubsec:coevolutionmodel}, respectively) represent explanations falling into the second category, in which centrals and satellites of the same $\mhalo$ have different sizes due to their different evolutionary paths {\em prior} to satellite infall.
+%Both the $\rvir-$based model and the co-evolution model (see sections \S\ref{subsubsec:rvirmodel} and \S\ref{subsubsec:coevolutionmodel}, respectively) represent explanations falling into the second category, in which centrals and satellites of the same $\mhalo$ have different sizes due to their different evolutionary paths {\em prior} to satellite infall.
 For these models the story is very different: the influence of pre-infall co-evolution has a dramatic impact on $\rhalf-$clustering ratios, with a scale- and $\mstar-$dependence that closely resembles the SDSS signal.

### 2017-11-02 paper/galsize_paper.tex
Finished revising Section 4.1 and 4.2

@@
 \label{subsec:sizedef}
-
 Because galaxy clustering has well-known dependence upon $\mstar$ that is not the subject of this work, we wish to remove this influence and focus purely on the relationship between $\rhalf$ and $\wproj(\rproj).$ To do so, we determine the value $\langle\rhalf\vert\mstar\rangle$ by computing a sliding median of $\rhalf,$ calculated using a window of width $N_{\rm gal}=1000.$ Each galaxy is categorized as either ``large" or ``small" according to whether it is above or below the median value appropriate for its stellar mass.
@@
 
-In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ The black curve enveloped by the gray bands show the scaling relation for SDSS galaxies, while the blue curve shows the median relation  $\median{\rhalf}{\mstar}$ implied by the $\rvir-$based model described in \S\ref{sec:model}.
-This figure shows that models in which $\rhalf\propto\rvir$ can naturally give rise to the characteristic curvature in the $\langle\rhalf\vert\mstar\rangle$ relation, confirming the results in \citet{kravtsov13} in a forward modeling context.
+In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ The black curve enveloped by the gray bands shows the scaling relation for SDSS galaxies, while the blue curve shows the median relation  $\median{\rhalf}{\mstar}$ implied by the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}.
+This figure shows that models in which $\rhalf\propto\rvir$ can naturally give rise to the characteristic curvature in the $\rhalf-\mstar$ relation, confirming the results in \citet{kravtsov13} in a forward modeling context.
 
@@
 
-In Figure \ref{fig:clustering_ratio_upshot} we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj(\rproj).$
+In Figure~\ref{fig:rvir_only_clustering_absolute}, we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj(\rproj).$ We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds, $\mstar>10^{9.75}\msun,$ $\mstar>10^{10.25}\msun,$ $\mstar>10^{10.75}\msun,$ and $\mstar>10^{11}\msun.$ For each threshold, we split the galaxies into ``large" and ``small" subsamples; as described in \S\ref{subsec:sizedef} and illustrated in Figure \ref{fig:sizedefinition}, our size-based selection is defined so that the subsamples have identical stellar mass functions.
+Red points with jackknife-estimated error bars show SDSS measurements of $\wproj(\rproj)$ for small galaxy samples, blue points show the same for large galaxies.
+Solid curves show $\wproj$ as predicted by the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}.
 
-We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds, $\mstar>10^{9.75}\msun,$ $\mstar>10^{10.25}\msun,$ $\mstar>10^{10.75}\msun,$ and $\mstar>10^{11}\msun.$ We make the same measurements for each volume-limited $\mstar-$threshold sample {\em without} splitting on size, giving us measurements $\wpall, \wplarge,$ and $\wpsmall$ for each threshold sample.
-This allow us to compute the ratio $(\wplarge-\wpsmall)/\wpall,$ which we refer to as {\em the $\rhalf$ clustering ratio}.
+The salient feature of these clustering measurements is that small galaxies cluster more strongly than large galaxies of the same stellar mass.
+This feature also holds true for galaxies predicted by the $\rvir-$based model.
+This result may be surprising, since $\rhalf\propto\rvir,$ halo mass $\rvir\propto\mhalo^{1/3},$ and clustering strength increases with $\mvir.$ Based on this simple argument, one would expect that large galaxies would be the more strongly clustered.
+We provide a resolution to this conundrum in \S\ref{subsec:censat_sizes}; before doing so, we first examine the clustering test of the $\rvir-$based model in more detail.
+
+As shown in Figure \ref{fig:baseline_sham_clustering}, the abundance matching prediction for $\wproj(\rproj)$ exhibits tension with SDSS observations at the $10-20\%$ level, particularly for $\mstar\gtrsim10^{10.75}\msun.$ This tension is inherited by our $\rvir-$based model for size, which is the subject of this work, and so we wish to compare our size models to data in such a way that minimizes the role played by the underlying stellar-to-halo-mass relation.
+We accomplish this using {\em the $\rhalf$ clustering ratios,} described below.
+
+For each volume-limited $\mstar-$threshold sample, we additionally measure $\wproj(\rproj)$ {\em without} splitting on size, giving us measurements $\wpall, \wplarge,$ and $\wpsmall$ for each threshold sample.
+This allows us to compute the ratio $(\wplarge-\wpsmall)/\wpall,$ which we refer to as {\em the $\rhalf$ clustering ratio}, denoted as $\delta_{\rhalf}(\wproj).$ For example, a clustering ratio of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass.
 These ratios are the measurements appearing on the y-axis in each panel of Figure \ref{fig:clustering_ratio_upshot}.
-Points with jackknife-estimated error bars show SDSS measurements, solid curves show the clustering ratios of model galaxies as predicted by the models described in \S\ref{sec:model}.
+
+The points and curves in Figure \ref{fig:clustering_ratio_upshot} are all negative: small galaxies cluster more strongly relative to large.
+This presentation of the measurement makes plain that the underlying signal of $\rhalf-$dependent clustering is strongest for samples with smaller stellar mass; as $\mstar$ increases, the signal weakens and nearly vanishes for $\mstar\gtrsim10^{11}\msun.$ Strikingly, the $\rvir-$based model exhibits this $\mstar-$dependent behavior, as well as the scale-dependence of the observed clustering signal at each $\mstar.$ As described in \S\ref{subsec:censat_sizes} below, we attribute the success of this prediction to the relative sizes of central vs.
+satellite galaxies.
 
@@
 %-----------------------------------------------------------------------------------------------------
-
-The salient feature of the clustering ratio measurements is that they are negative: small galaxies cluster more strongly than large galaxies of the same stellar mass.
-This feature also holds true for galaxies predicted by the $\rvir-$based model.
-This result may be surprising, since $\rhalf\propto\rvir,$ halo mass $\rvir\propto\mhalo^{1/3},$ and clustering strength increases with $\mvir.$ Based on this simple argument, one would expect the opposite trend to the measurements shown here.
 

### 2017-11-02 paper/galsize_paper.tex
Finished revising Section 4.3

@@
 
-A straightforward resolution to the above puzzle is shown in Figure \ref{fig:censatsizehist}, which compares the $\rhalf$ distributions of central, satellite, and splashback galaxies with the same halo mass $\mpeak\approx10^{12}\msun.$ A ``splashback" galaxy is defined as a present-day central that used to be a satellite, i.e., its main progenitor halo passed inside the virial radius of a larger halo at some point in its past history.
+The clustering measurements shown in the previous section present a puzzle.
+The modeling assumption $\rhalf\propto\rvir$ predicts size-dependent galaxy clustering that is in quite good agreement with observations, particularly considering the simplicity of the model.
+Yet, small galaxies cluster more strongly relative to large, which seems at odds with naive expectations based on halo mass, since $\rvir\propto\mvir.$ A straightforward resolution to this puzzle is shown in Figure \ref{fig:censatsizehist}, which compares the $\rhalf$ distributions of central, satellite, and splashback galaxies with the same halo mass $\mhalo\equiv\mpeak\approx10^{12}\msun.$ A ``splashback central"  is defined as a present-day central that used to be a satellite, i.e., its main progenitor halo passed inside the virial radius of a larger halo at some point in its past history.
 On the other hand, we define a ``true central" as a galaxy that has never been a satellite.
@@
 In the $\rvir-$based model, satellite and splashback galaxies are smaller than centrals of the same halo mass due to the physical size of their halo being smaller at earlier times $\zpeak.$ There are two distinct reasons why this feature results in small galaxies being more strongly clustered relative to larger galaxies of the same mass.
-First, satellite galaxies statistically occupy higher mass host halos that are more strongly clustered.
-In models where satellites are smaller than centrals, for any given $\mstar-$threshold the ``small" subsample will naturally have a higher satellite fraction, resulting in a negative clustering ratio as seen in SDSS data.
+First and foremost, satellite galaxies statistically occupy higher mass host halos that are more strongly clustered.
+So in models where satellites are smaller than centrals, at fixed $\mstar$ the ``small" subsample will naturally have a higher satellite fraction, boosting the clustering of small galaxies relative to large of the same stellar mass.
 Second, at fixed mass, halos of $L_\ast$ galaxies that form earlier are more strongly clustered, a phenomenon commonly known as {\em halo assembly bias}.
-Since splashback halos are typically earlier forming than true centrals, then models where splashback halos host smaller-than-average galaxies will naturally predict negative clustering ratios.
-
-In the $\mstar-$based model, in which $\rhalf$ is statistically set by present-day stellar mass with no other dependencies.
-Thus neither of the above features are present: satellites and centrals of the same mass have no differences in size, and there is essentially no $\rhalf-$dependence to galaxy clustering, in gross disagreement with our SDSS observations.
+Splashback halos are typically earlier-forming than true centrals, and so models where splashback halos host smaller-than-average galaxies will naturally predict smaller galaxies being the more strongly clustered.
+We highlight this point in section \ref{subsec:orphan_stripping} below by testing predictions for $\mstar-$based models that do not possess central vs.
+satellite size differences.
 
@@
 \label{subsec:orphan_stripping}
+
+\dots, in which $\rhalf$ is statistically set by present-day stellar mass with no other dependencies.
+Thus neither of the above features are present: satellites and centrals of the same mass have no differences in size, and there is essentially no $\rhalf-$dependence to galaxy clustering, in gross disagreement with our SDSS observations.
 

### 2017-11-02 paper/galsize_paper.tex
Finished draft of section 4.4

@@
 Thus it is natural to consider a class of models in which stellar mass is stripped from satellite galaxies after infall.
+ %satellites lose stellar mass in a way that mimics what is seen in high-resolution hydrodynamical simulations.
 
@@
 
-\dots, in which $\rhalf$ is statistically set by present-day stellar mass with no other dependencies.
-Thus neither of the above features are present: satellites and centrals of the same mass have no differences in size, and there is essentially no $\rhalf-$dependence to galaxy clustering, in gross disagreement with our SDSS observations.
+The green curves in Figure~\ref{fig:mstarmodelclustering} test the clustering predictions of the $\mstar-$based model described in \S\ref{subsubsec:mstaronlymodel}.
+In this model, $\rhalf$ is a log-normal distribution centered at $\median{\rhalf}{\mstar}.$ By construction, this model predicts no dependence at all of galaxy clustering upon $\rhalf$ at fixed $\mstar,$ even though the observed one-point distributions are recovered exactly.
 
-We conclude this section with a discussion of Figure \ref{fig:strippingorphans}, which provides an estimate of how satellite mass stripping and orphan galaxies impact size-dependent clustering ratios.
-In the $\mstar+$stripping model described in \S\ref{subsubsec:strippingmodel}, satellites lose stellar mass in a way that mimics what is seen in high-resolution hydrodynamical simulations.
-This naturally results in an enhancement of size differences between satellites and centrals, and the dot-dashed curves in Figure \ref{fig:strippingorphans} show that produces the expected sign of the effect on the clustering ratios.
-The magnitude of the effect, however is not strong enough to remedy the discrepancy of the clustering predictions of the $\mstar-$based model.
+The reason for the null signal of the purely $\mstar-$based model is simply that the scatter of $\rhalf$ about $\median{\rhalf}{\mstar}$ is uncorrelated with any other property.
+This is in contrast to the $\rvir-$based model, which correlates the scatter with host halo mass and as well as subhalo assembly.
+The purely $\mstar-$based model gives us a useful starting point to test simple alternative hypotheses for how the scatter may be correlated with large-scale structure.
+This is the motivation behind the $\mstar+$stripping model described in \S\ref{subsubsec:strippingmodel}.
+In this alternative model, satellites have smaller sizes than centrals of the same $\mstar$ due to post-infall stripping, where the amount of stripping has been calibrated to the satellite mass loss seen in high-resolution hydrodynamical simulations.
+
+The treatment of stellar mass loss in this model naturally results in an enhancement of size differences between satellites and centrals.
+As shown by the purple curves in Figure \ref{fig:mstarmodelclustering}, these central/satellite differences impact $\rhalf-$dependent clustering in the expected manner: small galaxies cluster more strongly relative to large galaxies of the same stellar mass.
+Since the satellite fraction increases with decreasing stellar mass, the clustering ratios are more negative for samples with smaller $\mstar$ thresholds.
+This confirms the notion that central vs.
+satellite differences drive the $\rhalf-$dependence of clustering, although the magnitude of the effect is evidently is not strong enough to produce clustering predictions that are consistent with SDSS.
+It is difficult to strip enough mass from satellites so that the $\rhalf-$dependent clustering is in agreement with observations.
+Taken together with the results for the $\rvir-$based model presented in \S\ref{subsec:clustering_results} and shown in Figure \ref{fig:clustering_ratio_upshot}, this supports the conclusion that the relative difference between central and satellite size is at least partially in place at the time of satellite infall.
 We discuss the physical implications of this result in \S\ref{subsec:satellite_discussion}.
@@
 }
-\label{fig:strippingorphans}
+\label{fig:mstarmodelclustering}
 \end{figure}
 %-----------------------------------------------------------------------------------------------------
-
-The dotted curves in Figure \ref{fig:strippingorphans} show results of the $\rvir-$based model applied to a subhalo catalog that includes a orphan halos.
-As described in \S\ref{}, orphan halos are subhalos that are no longer resolved by {\tt Rockstar}, but whose evolution is tracked in a post-processing phase.
-We apply the same mass-stripping model described in \S\ref{subsubsec:strippingmodel} to this subhalo catalog that includes orphan halos, keep all model galaxies that retain more than half of their stellar mass, and show results for the $\rvir-$based model applied to the resulting catalog.
-
-As the orphan catalog has a higher satellite fraction than the standard subhalo catalog, the negative boost shown the dotted curves in Figure \ref{fig:strippingorphans} is expected.
-Orphan halos also typically have earlier-than-average values of $\zpeak$ relative to ordinary subhalos, which also enhances differences between central and satellite sizes.
-See \S\ref{subsec:satellite_discussion} for further discussion.
 
@@
 \label{subsec:satellite_discussion}
+
+Our treatment of satellite-specific mass loss with the $\mstar+$stripping model is only approximate, because we have  modified the size of satellites without self-consistently modifiying their total stellar mass.
+In the present work, we have opted not to develop and fine-tune a more complex, semi-analytic model; instead, we have made a simple estimate for the level at which satellite-specific stripping impacts the two-point function.
 
@@
 
+%As the orphan catalog has a higher satellite fraction than the standard subhalo catalog, the negative boost shown the dotted curves in Figure \ref{fig:strippingorphans} is expected.
+Orphan halos also typically have earlier-than-average values of $\zpeak$ relative to ordinary subhalos, which also enhances differences between central and satellite sizes.
+See \S\ref{subsec:satellite_discussion} for further discussion.
+
 \end{document}

### 2017-11-02 paper/galsize_paper.tex
Finished draft of 2.1

@@
 \label{subsec:sizedef}
-Because galaxy clustering has well-known dependence upon $\mstar$ that is not the subject of this work, we wish to remove this influence and focus purely on the relationship between $\rhalf$ and $\wproj(\rproj).$ To do so, we determine the value $\langle\rhalf\vert\mstar\rangle$ by computing a sliding median of $\rhalf,$ calculated using a window of width $N_{\rm gal}=1000.$ Each galaxy is categorized as either ``large" or ``small" according to whether it is above or below the median value appropriate for its stellar mass.
-Using this technique, we stress that for any $\mstar-$threshold sample, the SMF of the ``large" and ``small" subsamples are identical, by construction.
-See Figure~\ref{fig:sizedefinition}.
+
+Because galaxy clustering has well-known dependence upon $\mstar$ that is not the subject of this work, we wish to remove this influence and focus purely on the relationship between $\rhalf$ and $\wproj(\rproj).$ To do so, we determine the value $\median{\rhalf}{\mstar}$ by computing a sliding median of $\rhalf,$ calculated using a window of width $N_{\rm gal}=1000.$ Each galaxy is categorized as either ``large" or ``small" according to whether it is above or below the median value appropriate for its stellar mass.
+We note that this is directly analogous to the common convention for studying the properties of ``red" vs.
+``blue" galaxies, in which the two subsamples are divided by a $\mstar-$ or luminosity-dependent green valley cut \citep[e.g.,][]{vdB_etal08,zehavi_etal11}.
+
+Using this technique, for any $\mstar-$threshold sample, the stellar mass function of the ``large" and ``small" subsamples are identical.
+We illustrate this for the particular case of $\mstar>10^{10.25}\msun$ in left panel of Figure~\ref{fig:sizedefinition}, which shows histograms of stellar mass for the two subsamples.
+The right panel of Figure~\ref{fig:sizedefinition} compares histograms of their size distributions, which partially overlap due to the variation in $\median{\rhalf}{\mstar}$ across the $\mstar-$ range of the threshold sample.
 

### 2017-11-02 paper/galsize_paper.tex
Added discussion of Figure 8

@@
 
+In this section we take a preliminary look at how galaxy clustering exhibits simultaneous dependence upon broadband color, morphology, and size.
+Beginning from the $\mstar>10^{10.25}\msun$ sample used above, we first divide the sample into ``red" and ``blue" subsamples according to a $g-r=0.65$ cut, the rough location of the trough of the green valley for this stellar mass.
+For each color-selected subsample, we separately measure $\median{\rhalf}{\mstar; {\rm red}}$ and $\median{\rhalf}{\mstar; {\rm blue}},$ and use these median size values to split each subsample into two.
+
+In the top left panel of Figure \ref{fig:colorclustering} we show the clustering of large vs.
+small red galaxies; in the top right panel we show the same for blue galaxies.
+For each color-selected sample, large galaxies are slightly more strongly clustered relative to small galaxies.
+Comparing the top panels of Figure \ref{fig:colorclustering} to the the upper right panel of Figure \ref{fig:rvir_only_clustering_absolute} shows the dramatic impact of galaxy color selection upon $\rhalf-$dependent clustering.
+For $\mstar-$complete samples, small galaxies cluster much stronger than large galaxies; for color-selected samples, the reverse is true, and the magnitude of the effect weakens considerably.
+
+The bottom panels of Figure \ref{fig:colorclustering} show results that are analogous to the top panels, but instead using of $g-r$ color, we first divide the $\mstar>10^{10.25}\msun$ sample into ``bulge-dominated" and ``disk-dominated" sequences according to $B/T,$ the fraction of $r-$band flux coming from the bulge component of the 2d light profile measurements in the \citet{meert_etal15} catalog.
+We define a galaxy as bulge-dominated if $B/T<0.25,$ and disk-dominated if $B/T>0.75.$ We separately split the disk-dominated and bulge-dominated subsample into two based on the median size $\median{\rhalf}{\mstar;B/T}$ appropriate for each subsample.
+The bottom left panel of Figure \ref{fig:colorclustering} compares the clustering of small vs.
+large disk-dominated galaxies; the bottom right panel shows the same comparison for bulge-dominated galaxies.
+
+The contrast between the two bottom panels is stark.
+The clustering of large vs.
+small bulge-dominated galaxies has almost no dependence upon $\rhalf.$ On the other hand, for disk-dominated galaxies, small galaxies are much more strongly clustered, and the effect is strong.
+In fact, comparing the bottom left panel of Figure \ref{fig:colorclustering} to the top right panel of Figure \ref{fig:rvir_only_clustering_absolute}, we see that $\rhalf-$dependent clustering is quite similar between disk-dominated galaxies and $\mstar-$threshold samples.
+
+A proper interpretation of these results requires forward-modeling the joint dependence of the galaxy-halo connection upon $\mstar, \rhalf, g-r, $ and $B/T,$ which is beyond the scope of this work (though see \S\ref{subsec:future} for discussion of future work).
+Nonetheless, the broad features of these clustering signals give insight into the characteristics that any model for these properties should exhibit.
+The clustering trends of bulge-dominated galaxies indicates that the size of the bulge is likely to have only a tenuous connection to the properties of its parent dark matter halo.\footnote{Strictly speaking, the size of the bulge could in principle be closely connected to any number of dark matter halo properties, so long as those halo properties do not significantly impact two-point clustering.} On the other hand, for disk-dominated galaxies, the observed $\rhalf-$dependent clustering suggests that the size of disk-dominated galaxies is strongly correlated with whether or not the galaxy is a satellite.
+We elaborate upon this halo model interpretation in \S\ref{subsec:future}.
+
 %---------------------------------------------------------------------------------------------------
@@
 }
-\label{fig:strippingorphans}
+\label{fig:colorclustering}
 \end{figure*}

### 2017-11-02 paper/galsize_paper.tex
Migrated some interpretative discussion to the future work section

@@
 In fact, comparing the bottom left panel of Figure \ref{fig:colorclustering} to the top right panel of Figure \ref{fig:rvir_only_clustering_absolute}, we see that $\rhalf-$dependent clustering is quite similar between disk-dominated galaxies and $\mstar-$threshold samples.
-
-A proper interpretation of these results requires forward-modeling the joint dependence of the galaxy-halo connection upon $\mstar, \rhalf, g-r, $ and $B/T,$ which is beyond the scope of this work (though see \S\ref{subsec:future} for discussion of future work).
-Nonetheless, the broad features of these clustering signals give insight into the characteristics that any model for these properties should exhibit.
-The clustering trends of bulge-dominated galaxies indicates that the size of the bulge is likely to have only a tenuous connection to the properties of its parent dark matter halo.\footnote{Strictly speaking, the size of the bulge could in principle be closely connected to any number of dark matter halo properties, so long as those halo properties do not significantly impact two-point clustering.} On the other hand, for disk-dominated galaxies, the observed $\rhalf-$dependent clustering suggests that the size of disk-dominated galaxies is strongly correlated with whether or not the galaxy is a satellite.
-We elaborate upon this halo model interpretation in \S\ref{subsec:future}.
+We discuss a halo model interpretation of these trends in \S\ref{subsec:future}.
 
@@
 
+A proper interpretation of the results clustering results shown in Figure \ref{fig:colorclustering} requires forward-modeling the joint dependence of the galaxy-halo connection upon $\mstar, \rhalf, g-r, $ and $B/T,$ which is beyond the scope of this work.
+Nonetheless, the broad features of these $\wproj(\rproj)$ measurements give insight into the characteristics that any model for these properties should exhibit.
+
+First, the bottom right panel of Figure \ref{fig:colorclustering} indicates that the size of the bulge has only a tenuous connection to the properties of its parent dark matter halo.\footnote{Strictly speaking, the size of the bulge could in principle be closely connected to any number of dark matter halo properties, so long as those halo properties do not significantly impact two-point clustering.} Second, for disk-dominated galaxies, the observed $\rhalf-$dependent clustering suggests that at fixed $\mstar,$ the size of the disk is strongly correlated with whether or not the galaxy is a satellite.
+
 %Previous studies of large-scale structure measured by SDSS indicate that morphological type has a significant influence on galaxy clustering \citep{skibba_etal08}.

### 2017-11-03 paper/galsize_paper.tex
Finished discussion of lensing prediction in section 4.5

@@
 
+The $\rhalf-$dependence of galaxy lensing has recently been measured using CFHTLenS observations \citep{heymans_etal12,erben_etal13}.
+For both red- and blue-sequence galaxies, it was found in \citet{charlton_etal17} that the lensing signal, $\Delta\Sigma,$ of large galaxies is slightly stronger relative to smaller galaxies.
+This result is in good agreement with the clustering measurements in the top panels of Figure \ref{fig:colorclustering}, which show the same trend.
+To date, the $\rhalf-$dependence of $\Delta\Sigma$ not yet been measured for $\mstar-$complete samples.
+We show  predictions of the $\rvir-$based model for future measurements of this signal in Figure \ref{fig:lensingprediction}.
+The halo model explanation for this trend is the same as for $\wproj:$ satellites occupy higher mass host halos relative to centrals of the same stellar mass, boosting $\Delta\Sigma$ for small relative to large galaxy samples.
+
 %---------------------------------------------------------------------------------------------------
@@
 }
-\label{fig:strippingorphans}
+\label{fig:lensingprediction}
 \end{figure}

### 2017-11-03 paper/galsize_paper.tex
Removed section on forward modeling vs backward modeling

@@
 
-\subsection{Progression from Backwards to Forward Modeling}
-\label{subsec:forwardsmodeling}
-
-Our results give an archetypal demonstration of the natural scientific progression from backwards to forward modeling.
-In backwards modeling, some mapping is applied to observed galaxies to estimate the values of model quantities such as halo mass.
-In \citet{kravtsov13}, the model quantities mapped onto galaxies are $\mhalo$ and $\rvir;$ another classic example of backwards modeling uses a group- or cluster-finding algorithm to assign $\mhalo$ to observed galaxies \citep[e.g.,][]{berlind_etal06,yang_etal05a,rykoff_etal14}.
-Once the observed galaxies have been supplemented with model variables, then the relations of the galaxy-halo connection can be inferred, for example, by calculating quantities such as the mean stellar mass or quiescent fraction as a function of halo mass \citep[e.g.,][]{yang_etal05b,weinmann_etal06}.
-
-In forward modeling, the direction of inference is turned around: a mapping is instead applied to the model quantities such as $\mhalo.$ In the case of {\tt Halotools}, this transforms a cosmological simulation into a synthetic galaxy catalog that can be directly compared with observations.
-This enables a richer quantitative study of modeling hypotheses relative to backwards modeling.
-For example, Figure \ref{fig:clustering_ratio_upshot} shows how forward modeling allows us to exploit galaxy clustering measurements to quantitatively test whether $\mhalo$ or $\mstar$ is the statistical regulator of galaxy size.
-The ability disentangle coupled variables such as $\mstar$ and $\mhalo$ is just one example of this advantage of forward modeling.
-Another example is illustrated in Figure \ref{fig:censatsizehist}, in which we explore the role of splashback halos in setting galaxy size.
-In our forward modeling approach, this is entirely straightforward; in backwards modeling, such an investigation would not even be possible without introducing additional modeling ingredients.
-
-Backwards modeling the galaxy-halo connection is useful for generating hypotheses and motivating functional forms.
-Forward modeling becomes necessary when the problem at hand becomes encumbered by multiple relevant variables, as is the case with galaxy size.
-Forward modeling also makes it possible to conduct rigorous Bayesian inference, which we consider to be the next natural step in the progression described here (see \S\ref{subsec:future} for further discussion).
-
 \subsection{Relation to Previous Work}

### 2017-11-03 paper/galsize_paper.tex
Reworked section 5.2

@@
 
-Our treatment of satellite-specific mass loss with the $\mstar+$stripping model is only approximate, because we have  modified the size of satellites without self-consistently modifiying their total stellar mass.
-In the present work, we have opted not to develop and fine-tune a more complex, semi-analytic model; instead, we have made a simple estimate for the level at which satellite-specific stripping impacts the two-point function.
-
-%Explanations for differences between the sizes of centrals and satellites fall into two categories, depending on whether or not the processes involved are specific to post-infall physics.
-One obvious possibility that could lead to satellites being smaller than centrals of the same $\mhalo$ is tidal stripping: satellite $\mstar$ could decrease after infall, reducing the size of the galaxy.
-We have quantitatively tested this possibility with the $\mstar-$stripping model described in \S\ref{subsubsec:strippingmodel}.
-Comparing the clustering ratios of the ``$\rvir-$based" and ``$\rvir+$stripping" models in Figure \ref{fig:strippingorphans}, we find that the impact of physically motivated levels of satellite mass loss cannot explain the $\rhalf-$dependent clustering seen in SDSS.
+Physical explanations for differences between the sizes of centrals and satellites fall into two categories, depending on whether or not the processes involved are post-infall and satellite-specific.
+The success of the $\rvir-$based model, together with the failure of the $\mstar$+stripping model, suggests that the relative size of central and satellite galaxies is largely driven by the {\rm pre-infall} evolution of the satellite.
+The clustering ratios in Figure \ref{fig:mstarmodelclustering} show that the impact of physically motivated levels of satellite mass loss likely cannot explain the $\rhalf-$dependent clustering seen in SDSS.
 As an additional test, we reach the same conclusion when implementing an even more extreme $\mstar-$stripping model in which stellar mass loss is linearly proportional to halo mass loss \citep[][Model 1]{watson_etal12}.
 
-%Both the $\rvir-$based model and the co-evolution model (see sections \S\ref{subsubsec:rvirmodel} and \S\ref{subsubsec:coevolutionmodel}, respectively) represent explanations falling into the second category, in which centrals and satellites of the same $\mhalo$ have different sizes due to their different evolutionary paths {\em prior} to satellite infall.
-For these models the story is very different: the influence of pre-infall co-evolution has a dramatic impact on $\rhalf-$clustering ratios, with a scale- and $\mstar-$dependence that closely resembles the SDSS signal.
-Quantitative constraints on the true level of this co-evolution effect will be a natural outcome of the program described in \S\ref{subsec:future}, but it is already clear that the long term co-evolution of galaxy and halo profiles should be considered a critical ingredient to models for the distribution of galaxy sizes across the cosmic web.
+While these clustering measurements give supporting evidence that satellite mass stripping plays a sub-dominant role in shaping galaxy size, we point out that our treatment of satellite mass loss is only approximate: we have modified the size of satellites without self-consistently modifying total stellar mass.
+In the present work, we have opted not to develop and fine-tune a complex, semi-analytic model; instead, we have made a simple ``first-order" estimate for the level at which satellite-specific stripping impacts the two-point function.
+Our findings support the idea that the small sizes of satellites arise primarily from the satellite's distinctive evolution within a high density region and a steep tidal field {\em prior} to becoming a present-day satellite.
 

### 2017-11-03 paper/galsize_paper.tex
Revised section 5.3.1

@@
 
+\newcommand{\mean}[2]{\langle{#1}\vert{#2}\rangle}
 \newcommand{\median}[2]{\langle{#1}\vert{#2}\rangle_{\rm median}}
@@
 
-%The scope of this work is to serve as a pilot study in which we identify the chief ingredients that can influence the $\rhalf-$dependence of galaxy clustering.
-While our results suggest that our profile co-evolution model is giving the correct qualitative picture, our implementation cannot be correct in quantitative detail: the clustering ratios of this model shown in Figure \ref{fig:clustering_ratio_upshot} are too strong relative to SDSS.
-This likely indicates that the central/satellite size differences depicted in Figure \ref{fig:} are too strong, and that the correlation strength in the real Universe is intermediate, rather than maximal.
-Our publicly available code that reproduces our results already contains the machinery to implement continuously variable levels of $\rhalf-\rspeak$ correlation strength, but for present purposes we have chosen to focus on exploring bracketing cases of qualitative ingredients, rather than fine-tuning the model.
+The scope of this work is to serve as a pilot study in which we identify the chief ingredients that can influence the $\rhalf-$dependence of galaxy clustering.
+While our results suggest that satellite evolution {\em prior} to infall drives the correct relative size of centrals vs.
+satellites, our implementation cannot be correct in quantitative detail: the clustering ratios of this model shown in Figure \ref{fig:clustering_ratio_upshot} only roughly agree with SDSS.
+For present purposes, we have chosen to focus on exploring bracketing cases of qualitative ingredients, rather than fine-tuning the model.
 
-%In addition to varying the $\rhalf-\rspeak$ correlation strength, there are other factors that should be included in any proper likelihood analysis of galaxy size models.
-In particular, since the clustering signal is strongly influenced by differences between centrals and satellites, then the satellite fraction $F_{\rm sat}(\mstar)$ plays an important role in $\rhalf-$dependent clustering.
-For fixed scaling relations $\langle\rhalf^{\rm cens}\vert\mhalo\rangle$ and $\langle\rhalf^{\rm sats}\vert\mhalo\rangle,$ models with different satellite fractions will exhibit different $\rhalf-$clustering ratios because $F_{\rm sat}(\mstar)$ controls the relative weighting of the two populations.
-Our results based on the catalog that includes orphan subhalos (Figure \ref{fig:strippingorphans}, dotted curves) give an explicit demonstration of the impact of $F_{\rm sat}(\mstar)$ on the clustering signal.
+Since the clustering signal is strongly influenced by differences between centrals and satellites, then the satellite fraction $F_{\rm sat}(\mstar)$ plays an important role in $\rhalf-$dependent clustering.
+For {\em fixed} scaling relations $\median{\rhalf^{\rm cens}}{\mhalo}$ and $\median{\rhalf^{\rm sats}}{\mhalo},$ models with different satellite fractions will exhibit different $\rhalf-$clustering ratios because $F_{\rm sat}(\mstar)$ controls the relative weighting of the two populations.
+An explicit demonstration of this point appears in the Appendix, which repeats the analyses in the main body of the text, but for a subhalo catalog with no orphan correction.
 
-%On the one hand, this degeneracy with the satellite fraction is unfortunate, because it means galaxy sizes does not leave a pure and unique signature on $\rhalf-$clustering ratios.
-However, this can also be viewed as an opportunity to extract tighter constraints on $F_{\rm sat}(\mstar),$ which are sorely needed to discriminate between competing models.
-For this problem, the path forward is clear.
-Traditional galaxy clustering is already being used to validate and/or fit models of the stellar-to-halo-mass relation \citep[e.g.,][]{moster_etal13,behroozi13_smhm,lehmann_etal15}.
-Based on our results, we advocate that empirical models for $\langle\mstar\vert\mhalo\rangle$ be supplemented with additional model ingredients for $\langle\rhalf\vert\mstar\rangle,$ and that the parameters of composite model are jointly constrained by measurements of the stellar mass function, $\mstar-$dependent clustering, and $\rhalf-$dependent clustering.
-Careful attention will need to be paid to the orphan subhalo population, which is well-known to have a significant impact on small-scale clustering \citep{guo_white13,campbell_etal17}.
+On the one hand, this degeneracy with the satellite fraction is unfortunate, because it means galaxy size does not leave a pure and unique signature on $\rhalf-$clustering ratios.
+However, this can also be viewed as an opportunity to extract tighter constraints on $F_{\rm sat}(\mstar),$ which are sorely needed to discriminate between competing models \citep{watson_conroy13}.
+Traditional galaxy clustering is already being used to validate and/or fit models of the stellar-to-halo-mass relation \citep[e.g.,][]{leauthaud_etal11,moster_etal13,behroozi13_smhm,lehmann_etal15}.
+Based on our results, we advocate that empirical models for $\mean{\mstar}{\mhalo}$ be supplemented with additional model ingredients for $\median{\rhalf}{\mstar},$ and that the parameters of the composite model be {\em jointly} constrained by measurements of the stellar mass function, $\mstar-$dependent clustering, and $\rhalf-$dependent clustering.
 
@@
 
+{\color{blue} Include new plot of clustering ratios without orphans.}
 %As the orphan catalog has a higher satellite fraction than the standard subhalo catalog, the negative boost shown the dotted curves in Figure \ref{fig:strippingorphans} is expected.

### 2017-11-03 paper/galsize_paper.tex
Revisions to 5.3.2

@@
 First, the bottom right panel of Figure \ref{fig:colorclustering} indicates that the size of the bulge has only a tenuous connection to the properties of its parent dark matter halo.\footnote{Strictly speaking, the size of the bulge could in principle be closely connected to any number of dark matter halo properties, so long as those halo properties do not significantly impact two-point clustering.} Second, for disk-dominated galaxies, the observed $\rhalf-$dependent clustering suggests that at fixed $\mstar,$ the size of the disk is strongly correlated with whether or not the galaxy is a satellite.
+Our analysis complements \citet{weinmann_etal08}, who reach the same conclusions based on a study of galaxy group catalogs.
+These findings imply that bulge prominence is intimately connected with the quenching of star-formation, but that there is wide variation in star-formation histories amongst disk-dominated galaxies, in agreement with numerous previous findings \citep[see, e.g.,][]{woo_etal15,font_etal17}.
 
-%Previous studies of large-scale structure measured by SDSS indicate that morphological type has a significant influence on galaxy clustering \citep{skibba_etal08}.
+Previous studies of large-scale structure measured by SDSS indicate that morphological type has a significant influence on galaxy clustering \citep{skibba_etal08}.
 Because morphology is covariant with star-formation rate (SFR) and $\rhalf,$ accounting for this dependency will require simultaneously modeling each of these variables.
-
-%To date, such a task has been beyond the purview of empirical models.
+Historically, such a task has been beyond the purview of empirical models.
 However, recent progress has substantially improved the richness of the predictions that galaxy-halo models are capable of \citep{becker15,cohn17,moster_etal17}.
-This new class of models has accomplished this by empirically modeling star-formation rate, and then integrating SFR along each halo's history to differentially build up stellar mass.\footnote{This approach towards predicting $\mstar$ is thus mathematically akin to traditional semi-analytic models, although \citet{becker15} have retained the empirical modeling prioritization of simplicity and computational efficiency.} We are currently extending this new class of models to differentially build up the disk and bulge across cosmic time.
-In addition to treating the multi-dimensional nature of the problem, this also allows us to use data at higher redshift in a self-consistent manner.
+This new class of models has accomplished this by empirically modeling star-formation rate, and then integrating SFR along each halo's history to differentially build up stellar mass.
+We are currently extending this new class of models to differentially build up the disk and bulge across cosmic time using computationally efficient empirical modeling methods.
+In addition to treating the multi-dimensional nature of the problem, this will allow us to use data at higher redshift in a self-consistent manner.
 

### 2017-11-03 paper/galsize_paper.tex
Finished draft of 5.1

@@
 
-The $\rhalf-$dependence of galaxy lensing has recently been measured using CFHTLenS observations \citep{heymans_etal12,erben_etal13}.
-For both red- and blue-sequence galaxies, it was found in \citet{charlton_etal17} that the lensing signal, $\Delta\Sigma,$ of large galaxies is slightly stronger relative to smaller galaxies.
-This result is in good agreement with the clustering measurements in the top panels of Figure \ref{fig:colorclustering}, which show the same trend.
-To date, the $\rhalf-$dependence of $\Delta\Sigma$ not yet been measured for $\mstar-$complete samples.
-We show  predictions of the $\rvir-$based model for future measurements of this signal in Figure \ref{fig:lensingprediction}.
-The halo model explanation for this trend is the same as for $\wproj:$ satellites occupy higher mass host halos relative to centrals of the same stellar mass, boosting $\Delta\Sigma$ for small relative to large galaxy samples.
-
 %---------------------------------------------------------------------------------------------------
@@
 
-Backwards modeling methods have been used extensively in the literature to gain insight into the relationship between galaxy mass, size, and environment.
-Broadly speaking, such studies proceed by using a galaxy group catalog to classify observed galaxies as centrals or satellites, and estimate their halo mass.
-Employing such methods, several analyses of the \citet{yang_etal05b} group catalog have found that the $\mstar-\rhalf$ relation of early-type galaxies exhibits weak, if any, environmental dependence \citep{huertas_company_etal13b,shankar_etal14}.
+Numerous previous analyses have employed the \citet{yang_etal05b} group catalog to ``directly" study the relationship between galaxy mass, size, and environment.
+For example, by treating observed groups as genuine dark matter halos, several analyses have found that the $\mstar-\rhalf$ relation of early-type galaxies exhibits weak, if any, environmental dependence \citep{weinmann_etal08,huertas_company_etal13b,shankar_etal14}.
+Meanwhile, \citet{weinmann_etal08} additionally find that for late-type galaxies, there is a strong correlation between disk size and central/satellite designation.
+Qualitatively, our clustering measurements shown in Figure \ref{fig:colorclustering} are in good agreement with these findings: once galaxies have been morphology-selected, only the clustering of disk shows significant dependence upon $\rhalf.$ Our clustering results are also consistent with the disk model presented in \citet{dutton_etal08,dutton_etal10}, which predicts that at fixed stellar mass, there is weak, positive correlation between disk size and halo mass.
 
-A direct comparison to this finding is not possible because the conclusions drawn here pertain to $\mstar-$limited galaxy samples.
 As discussed in \citet{spindler_wake17}, it is entirely possible that size differences between centrals and satellites of the same mass can be accounted for by mutual covariance with an additional variable such as star formation rate or morphological type \citep[see also][for an explicit demonstration of this scenario]{lilly_carollo16}.
@@
 In such a case, centrals would be larger than satellites of the same mass, even though {\em early-type centrals} would have the same sizes as {\em early-type satellites}.
+This scenario could also explain the sign-change and weakening of $\rhalf-$dependent clustering measurements in the present work.
+
+The $\rhalf-$dependence of galaxy lensing has recently been measured using CFHTLenS observations \citep{heymans_etal12,erben_etal13}.
+For both red- and blue-sequence galaxies, it was found in \citet{charlton_etal17} that the lensing signal, $\Delta\Sigma,$ of large galaxies is slightly stronger relative to smaller galaxies.
+This result is in good agreement with the clustering measurements in the top panels of Figure \ref{fig:colorclustering}, which show the same trend.
+To date, the $\rhalf-$dependence of $\Delta\Sigma$ not yet been measured for $\mstar-$complete samples.
+We show  predictions of the $\rvir-$based model for future measurements of this signal in Figure \ref{fig:lensingprediction}.
+The halo model explanation for this trend is the same as for $\wproj:$ satellites occupy higher mass host halos relative to centrals of the same stellar mass, boosting $\Delta\Sigma$ for small relative to large galaxy samples.
 
 As discussed in \S\ref{subsec:future}, we are currently pursuing follow-up work in which we jointly model morphological type together with galaxy size.
-We consider forward modeling methods to be a requisite for progress on this issue, not only to properly handle the multi-dimensional nature of the problem, but also to rigorously treat systematic errors that plague inference based on galaxy group catalogs \citep[see][for a thorough discussion]{campbell_etal15}.
+We consider forward modeling methods to be a requisite for meaningful progress on this issue, not only to properly handle the multi-dimensional nature of the problem, but also to rigorously treat systematic errors that plague inference based on galaxy group catalogs \citep[see][for a thorough discussion]{campbell_etal15}.
 
-Our approach is closely aligned with the methods used in \citet{somerville_etal17}, who studied the empirical modeling features that are necessary to recover the tight scatter in the observed $\langle\rhalf\vert\mstar\rangle$ relation.
+Our methodology is closely aligned with \citet{somerville_etal17}, who studied the empirical modeling features that are necessary to recover the tight scatter in the observed $\mean{\rhalf}{\mstar}$ relation.
 By building models where $\rhalf$ is set by halo spin $\lambda_{\rm halo}$, the authors in \citet{somerville_etal17} found that the level of intrinsic scatter about $\langle\lambda_{\rm halo}\vert\mhalo\rangle$ in dark matter halos is at least as large as the scatter about $\langle\rhalf\vert\mstar\rangle$ seen in observed galaxies.
-Since the latter necessarily receives an additional contribution from measurement error, this implies some tension with the common semi-analytic modeling assumption that $\lambda_{\rm halo}$ scales with $\rhalf.$ As noted in \citet{somerville_etal17}, tension in the level of scatter cannot be used to directly test the $\lambda_{\rm halo}\propto\rhalf$ assumption because the physical motivation for this correlation is largely limited to disk galaxies \citep{mo_mao_white98}.
-This tension is not present in our approach for the reason that the level of scatter is simply a modeling parameter in our approach, and we make no attempt to uncover the physical origin of this scatter.
-However, our fiducial value choice was motivated by \citet{somerville_etal17}, and in the ongoing follow-up work discussed in \S\ref{subsec:future} we will systematically test the large-scale structure implications of the assumption that $\lambda_{\rm halo}\propto\rhalf^{\rm disk}.$
+In our approach, the level of scatter is simply a modeling parameter whose fiducial value was motivated by \citet{somerville_etal17}.
+In ongoing follow-up work discussed in \S\ref{subsec:future}, we will systematically test the large-scale structure implications of the assumption that $\lambda_{\rm halo}\propto\rhalf^{\rm disk}$ using forward-modeling methods analogous to those advocated for in \citet{somerville_etal17} and employed here.
 
@@
 First, the bottom right panel of Figure \ref{fig:colorclustering} indicates that the size of the bulge has only a tenuous connection to the properties of its parent dark matter halo.\footnote{Strictly speaking, the size of the bulge could in principle be closely connected to any number of dark matter halo properties, so long as those halo properties do not significantly impact two-point clustering.} Second, for disk-dominated galaxies, the observed $\rhalf-$dependent clustering suggests that at fixed $\mstar,$ the size of the disk is strongly correlated with whether or not the galaxy is a satellite.
-Our analysis complements \citet{weinmann_etal08}, who reach the same conclusions based on a study of galaxy group catalogs.
 These findings imply that bulge prominence is intimately connected with the quenching of star-formation, but that there is wide variation in star-formation histories amongst disk-dominated galaxies, in agreement with numerous previous findings \citep[see, e.g.,][]{woo_etal15,font_etal17}.

### 2017-11-03 paper/galsize_paper.tex
Filled out description of abundance matching

@@
 As the bedrock of our modeling, we use the publicly available\footnote{\url{http://www.slac.stanford.edu/~behroozi/BPlanck\_Hlists}} catalog of {\tt Rockstar} subhalos identified at $z=0$ in the Bolshoi-Planck simulation \citep{klypin_etal11,behroozi12_rockstar,behroozi12_consistent_trees,riebe_etal13,rodriguez_puebla16_bolplanck}.
-As described in \S\ref{subsec:sham}, we will use traditional abundance matching to connect stellar mass $\mstar$ with subhalo peak mass $\mpeak.$ To address issues related to subhalo incompleteness \citep{guo_white13}, we supplement the Bolshoi-Planck subhalo catalog with {\em all} subhalos that were ever identified by {\tt Rockstar}, including those that no longer appear in the standard catalog as subhalos that survive to $z=0.$ We describe our treatment of these ``orphan" subhalos in the Appendix.
+As described in \S\ref{subsec:sham}, we will use traditional abundance matching to connect stellar mass $\mstar$ with subhalo peak mass $\mpeak.$ To address issues related to subhalo incompleteness \citep{guo_white13,campbell_etal17}, we supplement the Bolshoi-Planck subhalo catalog with {\em all} subhalos that were ever identified by {\tt Rockstar}, including those that no longer appear in the standard catalog as subhalos that survive to $z=0.$ We describe our treatment of these ``orphan" subhalos in the Appendix.
 
@@
 We compute $\wproj$ using the {\tt mock\_observables.wp} function in {\tt Halotools}, which is a python implementation of the algorithm in the {\tt Corrfunc} C library \citep{sinha_etal17}.
+We compute $\Delta\Sigma$ using the {\tt mock\_observables.delta\_sigma} function.
 
@@
 
-We map $\mstar$ onto subhalos using deconvolution abundance matching on the orphan-supplemented Bolshoi-Planck subhalo catalog, as described in detail in the Appendix.
-Briefly, our abundance matching prescription is based $\mpeak,$ the largest value of $\mvir$ ever attained along the main progenitor branch of the subhalo.
+We map $\mstar$ onto subhalos using deconvolution abundance matching (SHAM).
+See section 3.3 of \citet{behroozi_etal10} or the appendix of \citet{kravtsov_etal14} for an account of the mathematics underlying this technique.
+To perform the abundance matching, we use the publicly available code\footnote{\url{https://bitbucket.org/yymao/abundancematching/overview}} developed by Yao-Yuan Mao \citep{lehmann_etal15} that provides a python wrapper around the C kernel developed by Peter Behroozi \citep{behroozi_etal10}.
+For the subhalo property used in SHAM, we use $\mpeak,$ the largest value of $\mvir$ ever attained by the subhalo throughout the entire history of the main progenitor halo.
+Using the stellar mass function provided in \citet{moustakas_etal13}, we model $\mstar$ as a log-normal distribution with $0.2$dex of scatter about the median relation $\median{\mstar}{\mpeak}$ determined by deconvolution abundance matching.
+As described in the appendix, we include a prescription for supplementing the ordinary {\tt Rockstar} subhalo catalog with disrupted subhalos, so that some of our model galaxies inhabit subhalos that are no longer resolved and do not appear in the standard publicly available catalog.
 
@@
 APH thanks John Baker for the {\em Toejam \& Earl} soundtrack.
-Thanks also to Frank van den Bosch, Doug Watson, and Risa Wechsler for thoughtful feedback at various stages of the development of this work, and to Faustin Carter and Sebastian Bocquet for sharing their python expertise.
+Thanks also to Frank van den Bosch, Andrew Zentner, Doug Watson, and Risa Wechsler for thoughtful feedback at various stages of the development of this work, and to Faustin Carter and Sebastian Bocquet for sharing their matplotlib expertise.
 

### 2017-11-03 paper/galsize_paper.tex
Updated text with new orphan figure

@@
 
-Since it is likely that some portion of these disrupted subhalos should be populated with model galaxies \citep{guo_white13, campbell_etal17}, in our initial application of deconvolution abundance matching we derive the $\mstar--\mpeak$ relation using {\em all} subhalos, including those that may be disrupted.
+Since it is likely that some portion of these disrupted subhalos should be populated with model galaxies \citep{guo_white13, campbell_etal17}, in our initial application of deconvolution abundance matching we derive the $\mstar-\mpeak$ relation using {\em all} subhalos, including those that may be disrupted.
 We then apply a selection function to the disrupted subhalos, so that a fraction of these objects will host galaxies in our mock universe.
@@
 
-{\color{blue} Include new plot of clustering ratios without orphans.}
+The impact of our orphan treatment on $\mstar-$threshold clustering is shown in Figure \ref{fig:baseline_sham_clustering} in the main body of the text.
+We show the impact on $\rhalf-$dependent clustering in Figure \ref{fig:orphan_clustering_ratios}.
+Encouragingly, when tuning $\mathcal{F}_{\rm orphan}$ so that the overall $\mstar-$threshold clustering is roughly correct (as in Figure \ref{fig:baseline_sham_clustering}), the same level of tuning is required for a successful prediction of $\rhalf-$dependent clustering.
+This figure gives quantitative motivation for the program described in \S\ref{subsec:future} to jointly constrain the satellite fraction $F_{\rm sat}(\mstar)$ together with models for galaxy size.
+
+%---------------------------------------------------------------------------------------------------
+\begin{figure}
+\centering
+\includegraphics[width=8cm]{FIGS/clustering_ratios_orphan_impact.pdf}
+\caption{
+Points with error bars as well as the black curves are the same as in Figure \ref{fig:clustering_ratio_upshot}.
+Red curves show predictions for the $\rhalf-$clustering ratios of the $\rvir-$based model, but excluding orphan subhalos.
+}
+\label{fig:orphan_clustering_ratios}
+\end{figure}
+%-----------------------------------------------------------------------------------------------------
 %As the orphan catalog has a higher satellite fraction than the standard subhalo catalog, the negative boost shown the dotted curves in Figure \ref{fig:strippingorphans} is expected.

### 2017-11-03 paper/galsize_paper.tex
Added more thorough discussion of orphan effects in the appendix

@@
 We show the impact on $\rhalf-$dependent clustering in Figure \ref{fig:orphan_clustering_ratios}.
+The character of the effect of orphan subhalos in Figure \ref{fig:orphan_clustering_ratios} is as expected.
+The orphan catalog has a higher satellite fraction than the standard subhalo catalog; since satellites have preferentially smaller sizes and stronger clustering, the black curves are more negative relative to the red.
+Orphan halos also typically have earlier-than-average values of $\zpeak$ relative to ordinary subhalos, which also enhances differences between central and satellite sizes.
+
 Encouragingly, when tuning $\mathcal{F}_{\rm orphan}$ so that the overall $\mstar-$threshold clustering is roughly correct (as in Figure \ref{fig:baseline_sham_clustering}), the same level of tuning is required for a successful prediction of $\rhalf-$dependent clustering.
@@
 %-----------------------------------------------------------------------------------------------------
-%As the orphan catalog has a higher satellite fraction than the standard subhalo catalog, the negative boost shown the dotted curves in Figure \ref{fig:strippingorphans} is expected.
-Orphan halos also typically have earlier-than-average values of $\zpeak$ relative to ordinary subhalos, which also enhances differences between central and satellite sizes.
-See \S\ref{subsec:satellite_discussion} for further discussion.
 

### 2017-11-03 paper/galsize_paper.tex
Minor cleanup to methods section

@@
 
-In the first class of models we explore, we suppose that stellar mass $\mstar$ is the statistical regulator of $\rhalf,$ so that galaxy sizes are drawn from a log-normal distribution centered at $\median{\rhalf}{\mstar}.$ To implement this model, for simplicity we directly tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form \citep[see, e.g.,][]{zhang_yang17}.
+In the first class of models we explore, we suppose that stellar mass $\mstar$ is the statistical regulator of $\rhalf,$ so that galaxy sizes are drawn from a log-normal distribution with $0.2$ dex of scatter centered at $\median{\rhalf}{\mstar}.$ To implement this model, for simplicity we directly tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form \citep[see, e.g.,][]{zhang_yang17}.
 
@@
 Thus it is natural to consider a class of models in which stellar mass is stripped from satellite galaxies after infall.
- %satellites lose stellar mass in a way that mimics what is seen in high-resolution hydrodynamical simulations.
 

### 2017-11-03 paper/galsize_paper.tex
Fixed a few typos

@@
 
-\subsubsection{$\mstar-$stripping model}
+\subsubsection{$\mstar$+stripping model}
 \label{subsubsec:strippingmodel}
@@
 \eeq
-For $f_{\rm DM}$ we use the ratio of present-day subhalo mass divided by the peak mass, $M_{\rm vir}/M_{\rm peak}.$ If we denote the post-stripping stellar mass as $M_{\ast}',$ then we have $M_{\ast}'\equiv f_{\ast}M_{\ast},$ where $M_{\ast}$ is given by Eq.~\ref{eq:smhm}.
+For $f_{\rm DM}$ we use the ratio of present-day subhalo mass divided by the peak mass, $M_{\rm vir}/M_{\rm peak}.$ If we denote the post-stripping stellar mass as $M_{\ast}',$ then we have $M_{\ast}'\equiv f_{\ast}M_{\ast},$ where $M_{\ast}$ is given by the initial application of abundance matching.
 We then calculate the post-stripping radius by interpolating $\langle\rhalf'\vert\mstar'\rangle$ directly from SDSS data.

### 2017-11-04 paper/galsize_paper.tex
Added a few in-draft comments in blue text

@@
 
+{\color{blue} AVK comment: Need to be much clearer and more explicit about which galaxy properties come from which dataset, and probably to reiterate this when discussing the Figure \ref{fig:scatter_plot} plot of the size-mass relation.}
+
 Our galaxy sample comes from the catalog of SDSS galaxy profile decompositions provided by \citet{meert_etal15}.
@@
 The right panel of Figure~\ref{fig:sizedefinition} compares histograms of their size distributions, which partially overlap due to the variation in $\median{\rhalf}{\mstar}$ across the $\mstar-$ range of the threshold sample.
+{\color{blue} AVK comment: left panel should be actual stellar mass function, not just a histogram}
 
@@
 The {\em right panel} shows histograms of $\rhalf$ for the two subsamples, which partially overlap due to the finite range of $\mstar$ in the volume-limited sample.
+{\color{blue} AVK comment: left panel should be actual stellar mass function, not just a histogram}
 }
@@
 \label{subsubsec:rvirmodel}
+
+{\color{blue} AVK comment: The choice of nomenclature of $\rvir-$based model and $\mstar-$based model is not clear at all.
+APH: The big picture being compared/tested here are ``pre-infall" vs.
+``post-infall" processes, respectively.
+Those don't seem like great names either though.}
 

### 2017-11-04 paper/galsize_paper.tex
Reorganized subsections

@@
 {\bf SHAM + orphan clustering predictions.}
-Using the abundance matching methods described in \S\ref{subsec:smhm}, we compare the projected clustering of mock vs.
+Using the abundance matching methods described in \S\ref{subsec:sham}, we compare the projected clustering of mock vs.
 SDSS galaxies.
@@
 
-\subsection{Size-Dependent Clustering}
+\subsection{Size-Dependent Clustering Measurements}
 \label{subsec:clustering_results}
@@
 
-\subsection{Central vs. Satellite Sizes}
-\label{subsec:censat_sizes}
-
-The clustering measurements shown in the previous section present a puzzle.
-The modeling assumption $\rhalf\propto\rvir$ predicts size-dependent galaxy clustering that is in quite good agreement with observations, particularly considering the simplicity of the model.
-Yet, small galaxies cluster more strongly relative to large, which seems at odds with naive expectations based on halo mass, since $\rvir\propto\mvir.$ A straightforward resolution to this puzzle is shown in Figure \ref{fig:censatsizehist}, which compares the $\rhalf$ distributions of central, satellite, and splashback galaxies with the same halo mass $\mhalo\equiv\mpeak\approx10^{12}\msun.$ A ``splashback central"  is defined as a present-day central that used to be a satellite, i.e., its main progenitor halo passed inside the virial radius of a larger halo at some point in its past history.
-On the other hand, we define a ``true central" as a galaxy that has never been a satellite.
-
-%---------------------------------------------------------------------------------------------------
-\begin{figure}
-\centering
-\includegraphics[width=8cm]{FIGS/rvir_only_cen_sat_sizes.pdf}
-\caption{
-{\bf Relative sizes of centrals and satellites.}
-In a narrow bin of halo mass $\mhalo\equiv\mpeak\approx10^{12}\msun,$ we show the distribution of model galaxy sizes for different subpopulations galaxies, as predicted by the $\rvir-$based model.
-The red histogram shows the sizes of satellites; the blue histogram shows host halos that have never passed inside the virial radius of a larger halo (``true centrals"); the green histogram host halos that were subhalos inside a larger at some point in their past history (``splashback centrals").
-In the $\rvir-$based model, galaxy size is set by the {\em physical} size of the virial radius at the time the halo attains its peak mass, naturally resulting in smaller sizes for satellites and splashback centrals relative to true centrals of the same $\mhalo.$
-}
-\label{fig:censatsizehist}
-\end{figure}
-%-----------------------------------------------------------------------------------------------------
-
-In the $\rvir-$based model, satellite and splashback galaxies are smaller than centrals of the same halo mass due to the physical size of their halo being smaller at earlier times $\zpeak.$ There are two distinct reasons why this feature results in small galaxies being more strongly clustered relative to larger galaxies of the same mass.
-First and foremost, satellite galaxies statistically occupy higher mass host halos that are more strongly clustered.
-So in models where satellites are smaller than centrals, at fixed $\mstar$ the ``small" subsample will naturally have a higher satellite fraction, boosting the clustering of small galaxies relative to large of the same stellar mass.
-Second, at fixed mass, halos of $L_\ast$ galaxies that form earlier are more strongly clustered, a phenomenon commonly known as {\em halo assembly bias}.
-Splashback halos are typically earlier-forming than true centrals, and so models where splashback halos host smaller-than-average galaxies will naturally predict smaller galaxies being the more strongly clustered.
-We highlight this point in section \ref{subsec:orphan_stripping} below by testing predictions for $\mstar-$based models that do not possess central vs.
-satellite size differences.
-
 \subsection{Failure of $\mstar-$based Models}
-\label{subsec:orphan_stripping}
+\label{subsec:mstar_stripping}
 
@@
 Taken together with the results for the $\rvir-$based model presented in \S\ref{subsec:clustering_results} and shown in Figure \ref{fig:clustering_ratio_upshot}, this supports the conclusion that the relative difference between central and satellite size is at least partially in place at the time of satellite infall.
-We discuss the physical implications of this result in \S\ref{subsec:satellite_discussion}.
+We discuss the physical implications of this result in \S\ref{sec:interpretation}.
 
@@
 In fact, comparing the bottom left panel of Figure \ref{fig:colorclustering} to the top right panel of Figure \ref{fig:rvir_only_clustering_absolute}, we see that $\rhalf-$dependent clustering is quite similar between disk-dominated galaxies and $\mstar-$threshold samples.
-We discuss a halo model interpretation of these trends in \S\ref{subsec:future}.
+We discuss a halo model interpretation of these trends in \S\ref{sec:future}.
 
@@
 
-\section{Discussion}
-\label{sec:discussion}
+\section{A Unified Interpretation of $\rhalf-$Dependent Clustering}
+\label{sec:interpretation}
 
-\subsection{Relation to Previous Work}
+The clustering measurements shown in the previous section present (at least) two intriguing puzzles.
+First, the modeling assumption $\rhalf\propto\rvir$ predicts size-dependent galaxy clustering that is in quite good agreement with observations, particularly considering the simplicity of the model.
+Yet, small galaxies cluster more strongly relative to large, which seems at odds with naive expectations based on halo mass, since $\rvir\propto\mvir.$ Second, there appears to be a highly non-trivial dependence of $\rhalf-$dependent clustering upon whether or not the galaxy sample has been selected by color or morphology.
+We propose a simple and unified solution to both puzzles in \S\ref{subsec:censat_sizes}, and discuss the broader implications of our interpretation in \S\ref{subsec:broader_implications}.
+
+\subsection{The Relative Size of Centrals vs. Satellites}
+\label{subsec:censat_sizes}
+
+A straightforward resolution to this puzzle is shown in Figure \ref{fig:censatsizehist}, which compares the $\rhalf$ distributions of central, satellite, and splashback galaxies with the same halo mass $\mhalo\equiv\mpeak\approx10^{12}\msun.$ A ``splashback central"  is defined as a present-day central that used to be a satellite, i.e., its main progenitor halo passed inside the virial radius of a larger halo at some point in its past history.
+On the other hand, we define a ``true central" as a galaxy that has never been a satellite.
+
+%---------------------------------------------------------------------------------------------------
+\begin{figure}
+\centering
+\includegraphics[width=8cm]{FIGS/rvir_only_cen_sat_sizes.pdf}
+\caption{
+{\bf Relative sizes of centrals and satellites.}
+In a narrow bin of halo mass $\mhalo\equiv\mpeak\approx10^{12}\msun,$ we show the distribution of model galaxy sizes for different subpopulations galaxies, as predicted by the $\rvir-$based model.
+The red histogram shows the sizes of satellites; the blue histogram shows host halos that have never passed inside the virial radius of a larger halo (``true centrals"); the green histogram host halos that were subhalos inside a larger at some point in their past history (``splashback centrals").
+In the $\rvir-$based model, galaxy size is set by the {\em physical} size of the virial radius at the time the halo attains its peak mass, naturally resulting in smaller sizes for satellites and splashback centrals relative to true centrals of the same $\mhalo.$
+}
+\label{fig:censatsizehist}
+\end{figure}
+%-----------------------------------------------------------------------------------------------------
+
+In the $\rvir-$based model, satellite and splashback galaxies are smaller than centrals of the same halo mass due to the physical size of their halo being smaller at earlier times $\zpeak.$ There are two distinct reasons why this feature results in small galaxies being more strongly clustered relative to larger galaxies of the same mass.
+First and foremost, satellite galaxies statistically occupy higher mass host halos that are more strongly clustered.
+So in models where satellites are smaller than centrals, at fixed $\mstar$ the ``small" subsample will naturally have a higher satellite fraction, boosting the clustering of small galaxies relative to large of the same stellar mass.
+Second, at fixed mass, halos of $L_\ast$ galaxies that form earlier are more strongly clustered, a phenomenon commonly known as {\em halo assembly bias}.
+Splashback halos are typically earlier-forming than true centrals, and so models where splashback halos host smaller-than-average galaxies will naturally predict smaller galaxies being the more strongly clustered.
+We highlight this point in section \ref{subsec:mstar_stripping} below by testing predictions for $\mstar-$based models that do not possess central vs.
+satellite size differences.
+
+\subsection{Broader Implications}
+\label{subsec:broader_implications}
+
+Physical explanations for differences between the sizes of centrals and satellites fall into two categories, depending on whether or not the processes involved are post-infall and satellite-specific.
+The success of the $\rvir-$based model, together with the failure of the $\mstar$+stripping model, suggests that the relative size of central and satellite galaxies is largely driven by the {\rm pre-infall} evolution of the satellite.
+The clustering ratios in Figure \ref{fig:mstarmodelclustering} show that the impact of physically motivated levels of satellite mass loss likely cannot explain the $\rhalf-$dependent clustering seen in SDSS.
+As an additional test, we reach the same conclusion when implementing an even more extreme $\mstar-$stripping model in which stellar mass loss is linearly proportional to halo mass loss \citep[][Model 1]{watson_etal12}.
+
+While these clustering measurements give supporting evidence that satellite mass stripping plays a sub-dominant role in shaping galaxy size, we point out that our treatment of satellite mass loss is only approximate: we have modified the size of satellites without self-consistently modifying total stellar mass.
+In the present work, we have opted not to develop and fine-tune a complex, semi-analytic model; instead, we have made a simple ``first-order" estimate for the level at which satellite-specific stripping impacts the two-point function.
+Our findings support the idea that the small sizes of satellites arise primarily from the satellite's distinctive evolution within a high density region and a steep tidal field {\em prior} to becoming a present-day satellite.
+
+\section{Relation to Previous Work}
 \label{subsec:previous_work}
@@
 
-As discussed in \S\ref{subsec:future}, we are currently pursuing follow-up work in which we jointly model morphological type together with galaxy size.
+As discussed in \S\ref{sec:future}, we are currently pursuing follow-up work in which we jointly model morphological type together with galaxy size.
 We consider forward modeling methods to be a requisite for meaningful progress on this issue, not only to properly handle the multi-dimensional nature of the problem, but also to rigorously treat systematic errors that plague inference based on galaxy group catalogs \citep[see][for a thorough discussion]{campbell_etal15}.
@@
 In our approach, the level of scatter is simply a modeling parameter whose fiducial value was motivated by \citet{somerville_etal17}.
-In ongoing follow-up work discussed in \S\ref{subsec:future}, we will systematically test the large-scale structure implications of the assumption that $\lambda_{\rm halo}\propto\rhalf^{\rm disk}$ using forward-modeling methods analogous to those advocated for in \citet{somerville_etal17} and employed here.
+In ongoing follow-up work discussed in \S\ref{sec:future}, we will systematically test the large-scale structure implications of the assumption that $\lambda_{\rm halo}\propto\rhalf^{\rm disk}$ using forward-modeling methods analogous to those advocated for in \citet{somerville_etal17} and employed here.
 
-\subsection{Implications for Satellite Evolution}
-\label{subsec:satellite_discussion}
+\section{Future Directions for Empirical Modeling of Galaxy Size and Morphology}
+\label{sec:future}
 
-Physical explanations for differences between the sizes of centrals and satellites fall into two categories, depending on whether or not the processes involved are post-infall and satellite-specific.
-The success of the $\rvir-$based model, together with the failure of the $\mstar$+stripping model, suggests that the relative size of central and satellite galaxies is largely driven by the {\rm pre-infall} evolution of the satellite.
-The clustering ratios in Figure \ref{fig:mstarmodelclustering} show that the impact of physically motivated levels of satellite mass loss likely cannot explain the $\rhalf-$dependent clustering seen in SDSS.
-As an additional test, we reach the same conclusion when implementing an even more extreme $\mstar-$stripping model in which stellar mass loss is linearly proportional to halo mass loss \citep[][Model 1]{watson_etal12}.
+{\color{blue} APH comment: Some of this discussion can/should be migrated to \S\ref{subsec:broader_implications}.
+Depending on how that section ends up looking, it may be that this entire Future Directions section can be deleted after cannibalization.}
 
-While these clustering measurements give supporting evidence that satellite mass stripping plays a sub-dominant role in shaping galaxy size, we point out that our treatment of satellite mass loss is only approximate: we have modified the size of satellites without self-consistently modifying total stellar mass.
-In the present work, we have opted not to develop and fine-tune a complex, semi-analytic model; instead, we have made a simple ``first-order" estimate for the level at which satellite-specific stripping impacts the two-point function.
-Our findings support the idea that the small sizes of satellites arise primarily from the satellite's distinctive evolution within a high density region and a steep tidal field {\em prior} to becoming a present-day satellite.
-
-\subsection{Future Directions for Empirical Modeling of Galaxy Size}
-\label{subsec:future}
-
-\subsubsection{Jointly modeling $\langle\mstar\vert\mhalo\rangle$}
+\subsection{Jointly modeling $\langle\mstar\vert\mhalo\rangle$}
+\label{subsec:joint_smhm_modeling}
 
@@
 
-\subsubsection{Jointly modeling morphology}
+\subsection{Jointly modeling morphology}
+\label{subsec:joint_morphology_modeling}
 
@@
 Encouragingly, when tuning $\mathcal{F}_{\rm orphan}$ so that the overall $\mstar-$threshold clustering is roughly correct (as in Figure \ref{fig:baseline_sham_clustering}), the same level of tuning is required for a successful prediction of $\rhalf-$dependent clustering.
-This figure gives quantitative motivation for the program described in \S\ref{subsec:future} to jointly constrain the satellite fraction $F_{\rm sat}(\mstar)$ together with models for galaxy size.
+This figure gives quantitative motivation for the program described in \S\ref{sec:future} to jointly constrain the satellite fraction $F_{\rm sat}(\mstar)$ together with models for galaxy size.
 

### 2017-11-04 paper/galsize_paper.tex
Cleaned up and shortened results sections - now moved most of the interpretation to the following section

@@
 In \S\ref{sec:results}, we calculate predictions for the $\rhalf-$dependence of galaxy clustering for several different kinds of empirical models, described in turn below.
+{\color{blue} AVK comment: The choice of nomenclature of $\rvir-$based model and $\mstar-$based model is not clear at all.
+APH: The big picture being compared/tested here are ``pre-infall" vs.
+``post-infall" processes, respectively.
+Those don't seem like great names either though.}
 
@@
 \label{subsubsec:rvirmodel}
-
-{\color{blue} AVK comment: The choice of nomenclature of $\rvir-$based model and $\mstar-$based model is not clear at all.
-APH: The big picture being compared/tested here are ``pre-infall" vs.
-``post-infall" processes, respectively.
-Those don't seem like great names either though.}
 
@@
 
-\subsection{Failure of $\mstar-$based Models}
+\subsection{Testing the Impact of Satellite Mass Loss}
 \label{subsec:mstar_stripping}
@@
 The green curves in Figure~\ref{fig:mstarmodelclustering} test the clustering predictions of the $\mstar-$based model described in \S\ref{subsubsec:mstaronlymodel}.
-In this model, $\rhalf$ is a log-normal distribution centered at $\median{\rhalf}{\mstar}.$ By construction, this model predicts no dependence at all of galaxy clustering upon $\rhalf$ at fixed $\mstar,$ even though the observed one-point distributions are recovered exactly.
-
-The reason for the null signal of the purely $\mstar-$based model is simply that the scatter of $\rhalf$ about $\median{\rhalf}{\mstar}$ is uncorrelated with any other property.
-This is in contrast to the $\rvir-$based model, which correlates the scatter with host halo mass and as well as subhalo assembly.
-The purely $\mstar-$based model gives us a useful starting point to test simple alternative hypotheses for how the scatter may be correlated with large-scale structure.
-This is the motivation behind the $\mstar+$stripping model described in \S\ref{subsubsec:strippingmodel}.
-In this alternative model, satellites have smaller sizes than centrals of the same $\mstar$ due to post-infall stripping, where the amount of stripping has been calibrated to the satellite mass loss seen in high-resolution hydrodynamical simulations.
+In this model, $\rhalf$ is a log-normal distribution centered at $\median{\rhalf}{\mstar}.$ By construction, this model predicts no dependence at all of galaxy clustering upon $\rhalf$ at fixed $\mstar,$ simply because the scatter of $\rhalf$ about $\median{\rhalf}{\mstar}$ is uncorrelated with any other property.
+This is in contrast to the $\rvir-$based model, which correlates the scatter with host halo mass and as well as halo assembly.
+Likewise, the $\mstar+$stripping model described in \S\ref{subsubsec:strippingmodel} also exhibits correlations between scatter in $\rhalf$ and halo properties: in this alternative model, satellites have smaller sizes than centrals of the same $\mstar$ due to post-infall stripping.
 
 The treatment of stellar mass loss in this model naturally results in an enhancement of size differences between satellites and centrals.
-As shown by the purple curves in Figure \ref{fig:mstarmodelclustering}, these central/satellite differences impact $\rhalf-$dependent clustering in the expected manner: small galaxies cluster more strongly relative to large galaxies of the same stellar mass.
-Since the satellite fraction increases with decreasing stellar mass, the clustering ratios are more negative for samples with smaller $\mstar$ thresholds.
-This confirms the notion that central vs.
-satellite differences drive the $\rhalf-$dependence of clustering, although the magnitude of the effect is evidently is not strong enough to produce clustering predictions that are consistent with SDSS.
-It is difficult to strip enough mass from satellites so that the $\rhalf-$dependent clustering is in agreement with observations.
-Taken together with the results for the $\rvir-$based model presented in \S\ref{subsec:clustering_results} and shown in Figure \ref{fig:clustering_ratio_upshot}, this supports the conclusion that the relative difference between central and satellite size is at least partially in place at the time of satellite infall.
-We discuss the physical implications of this result in \S\ref{sec:interpretation}.
+As shown by the purple curves in Figure \ref{fig:mstarmodelclustering}, this impacts $\rhalf-$dependent clustering in the expected manner.
+The ``small" galaxy population has a higher satellite fraction, and so in this model small galaxies cluster more strongly relative to large galaxies of the same stellar mass.
+However, the magnitude of the effect is evidently is not strong enough to produce clustering predictions that are consistent with SDSS.
+Evidently it is difficult to strip enough mass from satellites so that the $\rhalf-$dependent clustering is in agreement with observations.
+As we argue in \S\ref{sec:interpretation}, this supports the conclusion that the relative difference between central and satellite size is at least partially in place at the time of satellite infall.
 
@@
 satellite size differences.
+
+{\color{blue} Important point/sentence to reincorporate here, after deleting from above:} Since the satellite fraction increases with decreasing stellar mass, the clustering ratios are more negative for samples with smaller $\mstar$ thresholds.
+{\color{blue} The analogous point should be made when discussing the role of color/morphology selection}.
 

### 2017-11-04 paper/galsize_paper.tex
Changed model descriptions so that there are only two models being tested: rvir and satellite mass loss

@@
 
-In \S\ref{sec:results}, we calculate predictions for the $\rhalf-$dependence of galaxy clustering for several different kinds of empirical models, described in turn below.
-{\color{blue} AVK comment: The choice of nomenclature of $\rvir-$based model and $\mstar-$based model is not clear at all.
-APH: The big picture being compared/tested here are ``pre-infall" vs.
-``post-infall" processes, respectively.
-Those don't seem like great names either though.}
+In \S\ref{sec:results}, we calculate predictions for the $\rhalf-$dependence of galaxy clustering for two classes of empirical models, described in turn below.
 
-\subsubsection{$\mstar-$based model}
-\label{subsubsec:mstaronlymodel}
+\subsubsection{Satellite mass loss model}
+\label{subsubsec:strippingmodel}
 
 In the first class of models we explore, we suppose that stellar mass $\mstar$ is the statistical regulator of $\rhalf,$ so that galaxy sizes are drawn from a log-normal distribution with $0.2$ dex of scatter centered at $\median{\rhalf}{\mstar}.$ To implement this model, for simplicity we directly tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form \citep[see, e.g.,][]{zhang_yang17}.
+
+It is natural to consider the possibility that stellar mass is stripped from satellite galaxies after infall.
+The basis for our implementation of this phenomenon is the fitting function presented in \citet{smith_etal16}, which was calibrated by studying stellar mass loss in a suite of high-resolution hydrodynamical simulations.
+In this model, $f_{\ast}$ quantifies the fraction of stellar mass lost as a function of $f_{\rm DM},$ the amount of dark matter that has been stripped since infall:
+
+\beq
+f_{\ast} = 1 - \exp(-14.2f_{\rm DM})
+\eeq
+For $f_{\rm DM}$ we use the ratio of present-day subhalo mass divided by the peak mass, $M_{\rm vir}/M_{\rm peak}.$ If we denote the post-stripping stellar mass as $M_{\ast}',$ then we have $M_{\ast}'\equiv f_{\ast}M_{\ast},$ where $M_{\ast}$ is given by the initial application of abundance matching.
+We then calculate the post-stripping radius by interpolating $\langle\rhalf'\vert\mstar'\rangle$ directly from SDSS data.
+In this way, we model satellite mass loss and subsequent size truncation in a manner that mimics what is seen in hydrodynamical simulations.
 
@@
 
-Motivated by \citet{kravtsov13}, we explore a model in which $\rhalf$ is linearly proportional to halo virial radius:
+Motivated by \citet{kravtsov13}, we additionall explore a model in which $\rhalf$ is linearly proportional to halo virial radius:
 \beq
@@
 For the model we refer to as the ``$\rvir-$based model", we add uncorrelated log-normal scatter of $\sigmarhalf=0.2$ dex to generate a Monto Carlo realization of the model population.
-
-\subsubsection{$\mstar$+stripping model}
-\label{subsubsec:strippingmodel}
-
-As we will show in \S\ref{sec:results}, the chief ingredient needed to recover the observed clustering properties of galaxies is that satellites need to be smaller than centrals of comparable halo mass.
-Thus it is natural to consider a class of models in which stellar mass is stripped from satellite galaxies after infall.
-
-The basis of this class of models is the fitting function presented in \citet{smith_etal16}, which was calibrated by studying stellar mass loss in a suite of high-resolution hydrodynamical simulations.
-In this model, $f_{\ast}$ quantifies the fraction of stellar mass lost as a function of $f_{\rm DM},$ the amount of dark matter that has been stripped since infall:
-
-\beq
-f_{\ast} = 1 - \exp(-14.2f_{\rm DM})
-\eeq
-For $f_{\rm DM}$ we use the ratio of present-day subhalo mass divided by the peak mass, $M_{\rm vir}/M_{\rm peak}.$ If we denote the post-stripping stellar mass as $M_{\ast}',$ then we have $M_{\ast}'\equiv f_{\ast}M_{\ast},$ where $M_{\ast}$ is given by the initial application of abundance matching.
-We then calculate the post-stripping radius by interpolating $\langle\rhalf'\vert\mstar'\rangle$ directly from SDSS data.
 
@@
 
-The green curves in Figure~\ref{fig:mstarmodelclustering} test the clustering predictions of the $\mstar-$based model described in \S\ref{subsubsec:mstaronlymodel}.
-In this model, $\rhalf$ is a log-normal distribution centered at $\median{\rhalf}{\mstar}.$ By construction, this model predicts no dependence at all of galaxy clustering upon $\rhalf$ at fixed $\mstar,$ simply because the scatter of $\rhalf$ about $\median{\rhalf}{\mstar}$ is uncorrelated with any other property.
-This is in contrast to the $\rvir-$based model, which correlates the scatter with host halo mass and as well as halo assembly.
-Likewise, the $\mstar+$stripping model described in \S\ref{subsubsec:strippingmodel} also exhibits correlations between scatter in $\rhalf$ and halo properties: in this alternative model, satellites have smaller sizes than centrals of the same $\mstar$ due to post-infall stripping.
+The green curves in Figure~\ref{fig:mstarmodelclustering} test the clustering predictions of the model described in \S\ref{subsubsec:strippingmodel} {\em before} applying the satellite mass loss prescription.
+Thus the green curves pertain to a model where $\rhalf$ is a purely random log-normal distribution centered at $\median{\rhalf}{\mstar}.$ By construction, this model predicts no dependence at all of galaxy clustering upon $\rhalf$ at fixed $\mstar,$ simply because the scatter of $\rhalf$ about $\median{\rhalf}{\mstar}$ is uncorrelated with any other property.
+The application of satellite mass loss introduces correlations in the scatter: after mass loss, satellites have smaller sizes than centrals of the same $\mstar$ due to post-infall stripping.
 
-The treatment of stellar mass loss in this model naturally results in an enhancement of size differences between satellites and centrals.
-As shown by the purple curves in Figure \ref{fig:mstarmodelclustering}, this impacts $\rhalf-$dependent clustering in the expected manner.
-The ``small" galaxy population has a higher satellite fraction, and so in this model small galaxies cluster more strongly relative to large galaxies of the same stellar mass.
+As shown by the purple curves in Figure \ref{fig:mstarmodelclustering}, satellite mass loss impacts $\rhalf-$dependent clustering in the expected manner.
+The ``small" galaxy population has a higher satellite fraction due to satellites being smaller than centrals of the same $\mstar,$ and so in this model small galaxies cluster more strongly relative to large.
 However, the magnitude of the effect is evidently is not strong enough to produce clustering predictions that are consistent with SDSS.
@@
 In all panels, the axes and points with error bars are the same as in Figure \ref{fig:clustering_ratio_upshot}.
-The solid green curves shows the prediction of the $\mstar-$based model, which is in gross tension with the data due to satellites having the same size as centrals of the same mass.
+The solid green curves shows the prediction of the satellite mass loss model, which is in gross tension with the data due to satellites having the same size as centrals of the same mass.
 The solid purple curves show results for a model in which satellites lose mass after infall in a manner similar to what is seen in high-resolution hydrodynamical simulations, as described in \S\ref{subsubsec:strippingmodel}.
@@
 Splashback halos are typically earlier-forming than true centrals, and so models where splashback halos host smaller-than-average galaxies will naturally predict smaller galaxies being the more strongly clustered.
-We highlight this point in section \ref{subsec:mstar_stripping} below by testing predictions for $\mstar-$based models that do not possess central vs.
+We highlight this point in section \ref{subsec:mstar_stripping} below by testing predictions for satellite mass loss models that do not possess central vs.
 satellite size differences.

### 2017-11-05 paper/galsize_paper.tex
Updated Figure 1

@@
 The right panel of Figure~\ref{fig:sizedefinition} compares histograms of their size distributions, which partially overlap due to the variation in $\median{\rhalf}{\mstar}$ across the $\mstar-$ range of the threshold sample.
-{\color{blue} AVK comment: left panel should be actual stellar mass function, not just a histogram}
 
@@
 {\bf Definition of ``small" and ``large" galaxies.} For a volume-limited SDSS galaxy sample defined by $M_{\ast}>10^{10.25}M_{\odot},$ we visually demonstrate how we classify galaxies into ``small" and ``large" subsamples.
-As described in detail in \S\ref{subsec:sizedef}, we compute the median value $\median{\rhalf}{\mstar}$ using a sliding window with a width of $1000$ galaxies at each value of $\mstar.$ The {\em left panel} shows a histogram of the stellar masses, confirming that our method yields identical stellar mass functions for the two subsamples.
+As described in detail in \S\ref{subsec:sizedef}, we compute the median value $\median{\rhalf}{\mstar}$ using a sliding window with a width of $1000$ galaxies at each value of $\mstar.$ The {\em left panel} compares the stellar mass functions $\phi(\mstar)$ of the two samples, confirming that our method for separating ``small" from ``large" galaxies yields subsamples with statistically indistinguishable $\phi(\mstar)$.
 The {\em right panel} shows histograms of $\rhalf$ for the two subsamples, which partially overlap due to the finite range of $\mstar$ in the volume-limited sample.
-{\color{blue} AVK comment: left panel should be actual stellar mass function, not just a histogram}
 }

### 2017-11-05 paper/galsize_paper.tex
Updated intro

@@
 
-In the $\lcdm$ framework of cosmological structure formation, galaxies form at the centers of dark matter halos.
-Highly complex and nonlinear baryonic processes regulate galaxy formation, and the quest for a fine-grained understanding of these processes is one of the chief goals of theoretical astrophysics today.
-
-Observationally, many properties of observed galaxies exhibit remarkably tight scaling relations.
-Among the most fundamental of these relations is the strong correlation between galaxy size and stellar mass and luminosity.
-The scaling of galaxy size with galaxy mass is well-measured in the local Universe \citep{shen_etal03,guo_etal09,huang_etal13,zhang_yang17} and at high-redshift \citep{trujillo_etal04,vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,lange_etal15,huang_etal17}.
-
-These well-measured scaling relations are challenging to faithfully recover using ab initio galaxy formation methods such as hydrodynamical simulations and semi-analytic models, and provide useful boundary conditions for the calibration of such modeling efforts \citep{khochfar_silk06,dutton_etal10,hopkins_etal10a,bottrell_etal17b}.
-The precision cosmology program also depends critically on accurate modeling of galaxies, so that cosmological parameter inference can be confidently conducted without undue interference from uncertainty in baryonic physics \citep{LSST_science,LSST_galaxies}.
+Many properties of observed galaxies exhibit remarkably tight scaling relations.
+Galaxy size, typically quantified by a half-mass or half-light radius, $\rhalf,$ has well-measured scaling with galaxy mass $\mstar$ in the local Universe \citep{shen_etal03,guo_etal09,huang_etal13,lange_etal15,zhang_yang17}, and at higher redshift \citep{trujillo_etal04,vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,huang_etal17}.
+Observational constraints on models for galaxy $\rhalf$ typically come from one-point function measurements such as $\median{\rhalf}{\mstar}$ and $\sigma(\rhalf\vert\mstar),$ e.g.,  \citet{khochfar_silk06,desmond_etal17,bottrell_etal17b,hou_etal17,somerville_etal17}, or otherwise from catalogs of galaxy groups \citep{weinmann_etal08,huertas_company_etal13b,spindler_wake17}.
+Observations of two-point galaxy clustering, $\wproj(\rproj),$ have historically been used to place tight constraints on many features of the galaxy--halo connection, such as its $\mstar-$dependence \citep{moster_etal10,leauthaud_etal11,reddick_etal13,skibba_etal15}, dependence on luminosity \citep{tinker_etal05,cacciato_etal13}, broadband color \citep{coil_etal08,zehavi_etal11,guo_etal11,hearin_watson13}, and star-formation rate \citep{wang_etal07,tinker_etal13,watson_etal14}.
+In the present work, we exploit the constraining power of $\wproj(\rproj)$ to test empirical models connecting galaxy $\mstar$ and $\rhalf$ to the properties of the galaxy's parent dark matter halo.
 
@@
 
+%The precision cosmology program also depends critically on accurate modeling of galaxies, so that cosmological parameter inference can be confidently conducted without undue interference from uncertainty in baryonic physics \citep{LSST_science,LSST_galaxies}.
+
 \subsection{Jointly modeling $\langle\mstar\vert\mhalo\rangle$}

### 2017-11-05 paper/galsize_paper.tex
Updated Data and Simulations section

@@
 
-{\color{blue} AVK comment: Need to be much clearer and more explicit about which galaxy properties come from which dataset, and probably to reiterate this when discussing the Figure \ref{fig:scatter_plot} plot of the size-mass relation.}
-
-Our galaxy sample comes from the catalog of SDSS galaxy profile decompositions provided by \citet{meert_etal15}.
-This catalog is based on Data Release 10 of the Sloan Digital Sky Survey \citep[SDSS,][]{ahn_etal14}, with improvements to the photometry pipeline and light profile fitting methods \citep{vikram_etal10,bernardi_etal13,bernardi_etal14,meert_etal13}.
-In the version of this catalog that we use, two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile to determine the half-light radius $\rhalf.$ We use stellar mass measurements made available through the MPA-JHU catalog \citep{kauffmann_etal03,brinchmann_etal04}, allowing us to define volume-limited samples of galaxies according to the same completeness cuts used in \citet{behroozi_etal15} (see Figure 2).
-
-We calculate two-point clustering $\wproj$ of our SDSS galaxy sample using line-of-sight projection of $\pi_{\rm max}=20\mpc$ using the {\tt correl} program in {\tt UniverseMachine}.
-{\color{red} PSB: Please fill in details about {\tt correl} here}.
+Using galaxies observed in the Sloan Digital Sky Survey (SDSS) with the stellar mass measurements taken from the MPA-JHU catalog \citep{kauffmann_etal03,brinchmann_etal04}, we define volume-limited samples of galaxies according to the same $\mstar-$completeness cuts used in \citet{behroozi_etal15} (see Figure 2).
+We supplement the MPA-JHU catalog with measurements of half-light radius, $\rhalf,$ derived from galaxy profile decompositions provided by \citet{meert_etal15}.
+The \citet{meert_etal15} catalog is based on Data Release 10 of SDSS \citep{ahn_etal14}, with improvements to the photometry pipeline and light profile fitting methods \citep{vikram_etal10,bernardi_etal13,bernardi_etal14,meert_etal13}.
+In the version of this catalog that we use,\footnote{Our $\mstar$ and $\rhalf$ measurements are derived from different photometry pipelines; this is driven by our desire for consistency with the \citet{behroozi_etal15} completeness cuts used in our clustering measurements.
+We note that we have repeated our analysis for stellar mass measurements based on \citet{meert_etl15}, finding only minor quantitative, and no qualitative changes to our results.} two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile to determine the half-light radius of total $r-$band luminosity, $\rhalf.$
 
@@
 
+For our SDSS galaxy samples, we calculate two-point clustering $\wproj$ using line-of-sight projection of $\pi_{\rm max}=20~\mpc$ using the {\tt correl} program in {\tt UniverseMachine}.
 For mock galaxies, to compute galaxy clustering we employ the distant observer approximation by treating the simulation $z-$axis as the line-of-sight.
-We compute $\wproj$ using the {\tt mock\_observables.wp} function in {\tt Halotools}, which is a python implementation of the algorithm in the {\tt Corrfunc} C library \citep{sinha_etal17}.
-We compute $\Delta\Sigma$ using the {\tt mock\_observables.delta\_sigma} function.
+We compute $\wproj$ using the {\tt mock\_observables.wp} function in {\tt Halotools} \citep{hearin_etal16}, which is a python implementation of the algorithm in the {\tt Corrfunc} C library \citep{sinha_etal17}.
+We also use {\tt Halotools} to compute the galaxy-galaxy lensing signal, $\Delta\Sigma,$ using the {\tt mock\_observables.delta\_sigma} function.
 

### 2017-11-05 paper/galsize_paper.tex
Minor edits to SHAM description

@@
 
-Because galaxy clustering has well-known dependence upon $\mstar$ that is not the subject of this work, we wish to remove this influence and focus purely on the relationship between $\rhalf$ and $\wproj(\rproj).$ To do so, we determine the value $\median{\rhalf}{\mstar}$ by computing a sliding median of $\rhalf,$ calculated using a window of width $N_{\rm gal}=1000.$ Each galaxy is categorized as either ``large" or ``small" according to whether it is above or below the median value appropriate for its stellar mass.
-We note that this is directly analogous to the common convention for studying the properties of ``red" vs.
-``blue" galaxies, in which the two subsamples are divided by a $\mstar-$ or luminosity-dependent green valley cut \citep[e.g.,][]{vdB_etal08,zehavi_etal11}.
+Because galaxy clustering has well-known dependence upon $\mstar$ that is not the subject of this work, we wish to remove this influence and focus purely on the relationship between $\rhalf$ and $\wproj(\rproj).$ To do so, we determine the value $\median{\rhalf}{\mstar}$ by computing a sliding median of $\rhalf$ for galaxies sorted by $\mstar,$ calculated using a window of width $N_{\rm gal}=1000.$ Each galaxy is categorized as either ``large" or ``small" according to whether it is above or below the median value appropriate for its stellar mass.
+We note that this is analogous to the common convention for studying the properties of ``red" vs.
+``blue" galaxies, in which the two subsamples are divided by a $\mstar-$ or luminosity-dependent green valley cut \citep[e.g.,][]{vdB_etal08,zehavi_etal11}, only here the $\rhalf$ distribution is uni-modal, not bi-modal.
 
@@
 We map $\mstar$ onto subhalos using deconvolution abundance matching (SHAM).
-See section 3.3 of \citet{behroozi_etal10} or the appendix of \citet{kravtsov_etal14} for an account of the mathematics underlying this technique.
+See section 3.3 of \citet{behroozi_etal10} or the appendix of \citet{kravtsov_etal14} for an account of the mathematics underlying this technique in the presence of scatter.
 To perform the abundance matching, we use the publicly available code\footnote{\url{https://bitbucket.org/yymao/abundancematching/overview}} developed by Yao-Yuan Mao \citep{lehmann_etal15} that provides a python wrapper around the C kernel developed by Peter Behroozi \citep{behroozi_etal10}.
 For the subhalo property used in SHAM, we use $\mpeak,$ the largest value of $\mvir$ ever attained by the subhalo throughout the entire history of the main progenitor halo.
-Using the stellar mass function provided in \citet{moustakas_etal13}, we model $\mstar$ as a log-normal distribution with $0.2$dex of scatter about the median relation $\median{\mstar}{\mpeak}$ determined by deconvolution abundance matching.
+Using the stellar mass function provided in \citet{moustakas_etal13}, we model $\mstar$ as a log-normal distribution with $0.2$dex of scatter about the median relation $\median{\mstar}{\mpeak}$ determined by SHAM.
 As described in the appendix, we include a prescription for supplementing the ordinary {\tt Rockstar} subhalo catalog with disrupted subhalos, so that some of our model galaxies inhabit subhalos that are no longer resolved and do not appear in the standard publicly available catalog.

### 2017-11-05 paper/galsize_paper.tex
Cleaned up model desriptions

@@
 
-In the first class of models we explore, we suppose that stellar mass $\mstar$ is the statistical regulator of $\rhalf,$ so that galaxy sizes are drawn from a log-normal distribution with $0.2$ dex of scatter centered at $\median{\rhalf}{\mstar}.$ To implement this model, for simplicity we directly tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form \citep[see, e.g.,][]{zhang_yang17}.
+In the first class of models we explore, we suppose that stellar mass $\mstar$ is the statistical regulator of $\rhalf,$ so that galaxy sizes are drawn from a log-normal distribution with $0.2$ dex of scatter centered at $\median{\rhalf}{\mstar}.$ To implement this model, for simplicity we tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form \citep[see, e.g.,][]{zhang_yang17}.
 
@@
 The basis for our implementation of this phenomenon is the fitting function presented in \citet{smith_etal16}, which was calibrated by studying stellar mass loss in a suite of high-resolution hydrodynamical simulations.
-In this model, $f_{\ast}$ quantifies the fraction of stellar mass lost as a function of $f_{\rm DM},$ the amount of dark matter that has been stripped since infall:
-
+In this model, $f_{\ast}$ quantifies the remaining fraction of stellar mass as a function of $f_{\rm DM},$ the fraction of dark matter mass that remains after subhalo infall:
 \beq
-f_{\ast} = 1 - \exp(-14.2f_{\rm DM})
+f_{\ast} = 1 - \exp(-14.2f_{\rm DM}).
 \eeq
@@
 We then calculate the post-stripping radius by interpolating $\langle\rhalf'\vert\mstar'\rangle$ directly from SDSS data.
-In this way, we model satellite mass loss and subsequent size truncation in a manner that mimics what is seen in hydrodynamical simulations.
+In this way, we model satellite mass loss and  size truncation in a manner that mimics what is seen in hydrodynamical simulations.
 
@@
 
-Motivated by \citet{kravtsov13}, we additionall explore a model in which $\rhalf$ is linearly proportional to halo virial radius:
+Motivated by \citet{kravtsov13}, we additionally explore a model in which $\rhalf$ is linearly proportional to halo virial radius:\footnote{We note that the normalization factor in \citet{kravtsov13} is 0.0125, where as our normalization is 0.01.
+The difference derives from the choice of halo radius definition: \citet{bryan_norman98} in the present work, compared to the $200c$ definition used in \citet{kravtsov13}.}
 \beq
 \label{eq:fiducial_model}
-\rhalf = 0.01\rvir
+\rhalf = 0.01\rvir.
 \eeq
-For the virial radius of halos and subhalos, we use $\rmpeak,$ the value of $\rvir$ in physical units of $\kpc$ measured at the time of peak subhalo mass, defined by
+For the virial radius of halos and subhalos, we use $\rmpeak:$ the value of $\rvir$ in physical units of $\kpc$ measured at the time of peak subhalo mass.
+The relationship between $\rmpeak$ and $\mpeak$ is given by
 \beq

### 2017-11-05 paper/galsize_paper.tex
Added flesh to 5.1

@@
 In fact, comparing the bottom left panel of Figure \ref{fig:colorclustering} to the top right panel of Figure \ref{fig:rvir_only_clustering_absolute}, we see that $\rhalf-$dependent clustering is quite similar between disk-dominated galaxies and $\mstar-$threshold samples.
-We discuss a halo model interpretation of these trends in \S\ref{sec:future}.
+We discuss a halo model interpretation of these trends in \S\ref{sec:interpretation}.
 
@@
 Splashback halos are typically earlier-forming than true centrals, and so models where splashback halos host smaller-than-average galaxies will naturally predict smaller galaxies being the more strongly clustered.
-We highlight this point in section \ref{subsec:mstar_stripping} below by testing predictions for satellite mass loss models that do not possess central vs.
-satellite size differences.
 
-{\color{blue} Important point/sentence to reincorporate here, after deleting from above:} Since the satellite fraction increases with decreasing stellar mass, the clustering ratios are more negative for samples with smaller $\mstar$ thresholds.
-{\color{blue} The analogous point should be made when discussing the role of color/morphology selection}.
+We can also understand the $\mstar-$dependence of Figure \ref{fig:clustering_ratio_upshot} in term of the relative sizes of centrals vs.
+satellites.
+The satellite fraction $F_{\rm sat}(\mstar)$ decreases as $\mstar$ increases \citep[e.g.,][]{guo_etal11,reddick_etal13}.
+As $F_{\rm sat}$ decreases, there are fewer satellites available to preferentially weight the subsample of smaller galaxies.
+Thus models where $\rhalf-$dependent clustering is driven by satellite vs.
+central size naturally predict the observed $\mstar-$dependence of the signal, without introducing any explicitly $\mstar-$dependent ingredients in the size model.
+
+Upon first glance, the $\rhalf-$dependence of color- and morphology-selected samples shown in Figure \ref{fig:colorclustering} appear to be driven by different principles, since trends dramatically weaken and change sign.
+However, even very simple models based entirely on central vs.
+satellite size differences can give rise to this behavior.
+
+{\color{blue} APH: finish discussion of color and morphology.}
 

### 2017-11-06 paper/galsize_paper.tex
Moved figures to appear earlier in the pdf
Added new figure of scaling relation for hydro sims and SAMs

@@
 
-Motivated by \citet{kravtsov13}, we additionally explore a model in which $\rhalf$ is linearly proportional to halo virial radius:\footnote{We note that the normalization factor in \citet{kravtsov13} is 0.0125, where as our normalization is 0.01.
-The difference derives from the choice of halo radius definition: \citet{bryan_norman98} in the present work, compared to the $200c$ definition used in \citet{kravtsov13}.}
-\beq
-\label{eq:fiducial_model}
-\rhalf = 0.01\rvir.
-\eeq
-For the virial radius of halos and subhalos, we use $\rmpeak:$ the value of $\rvir$ in physical units of $\kpc$ measured at the time of peak subhalo mass.
-The relationship between $\rmpeak$ and $\mpeak$ is given by
-\beq
-\mpeak\equiv\frac{4\pi}{3}\rmpeak^{3}\Delta_{\rm vir}(\zpeak)\rho_{\rm m}(\zpeak),
-\eeq
-where for $\Delta_{\rm vir}(\zpeak)$ we use the fitting function to the ``virial" definition used in \citet{bryan_norman98}.
-For the model we refer to as the ``$\rvir-$based model", we add uncorrelated log-normal scatter of $\sigmarhalf=0.2$ dex to generate a Monto Carlo realization of the model population.
-
-\section{Results}
-\label{sec:results}
-
-\subsection{Size-Mass Scaling Relation}
-\label{subsec:one_point_function}
-
-In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ The black curve enveloped by the gray bands shows the scaling relation for SDSS galaxies, while the blue curve shows the median relation  $\median{\rhalf}{\mstar}$ implied by the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}.
-This figure shows that models in which $\rhalf\propto\rvir$ can naturally give rise to the characteristic curvature in the $\rhalf-\mstar$ relation, confirming the results in \citet{kravtsov13} in a forward modeling context.
-
 %---------------------------------------------------------------------------------------------------
@@
 %-----------------------------------------------------------------------------------------------------
-
-\subsection{Size-Dependent Clustering Measurements}
-\label{subsec:clustering_results}
-
-In Figure~\ref{fig:rvir_only_clustering_absolute}, we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj(\rproj).$ We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds, $\mstar>10^{9.75}\msun,$ $\mstar>10^{10.25}\msun,$ $\mstar>10^{10.75}\msun,$ and $\mstar>10^{11}\msun.$ For each threshold, we split the galaxies into ``large" and ``small" subsamples; as described in \S\ref{subsec:sizedef} and illustrated in Figure \ref{fig:sizedefinition}, our size-based selection is defined so that the subsamples have identical stellar mass functions.
-Red points with jackknife-estimated error bars show SDSS measurements of $\wproj(\rproj)$ for small galaxy samples, blue points show the same for large galaxies.
-Solid curves show $\wproj$ as predicted by the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}.
-
-The salient feature of these clustering measurements is that small galaxies cluster more strongly than large galaxies of the same stellar mass.
-This feature also holds true for galaxies predicted by the $\rvir-$based model.
-This result may be surprising, since $\rhalf\propto\rvir,$ halo mass $\rvir\propto\mhalo^{1/3},$ and clustering strength increases with $\mvir.$ Based on this simple argument, one would expect that large galaxies would be the more strongly clustered.
-We provide a resolution to this conundrum in \S\ref{subsec:censat_sizes}; before doing so, we first examine the clustering test of the $\rvir-$based model in more detail.
-
-As shown in Figure \ref{fig:baseline_sham_clustering}, the abundance matching prediction for $\wproj(\rproj)$ exhibits tension with SDSS observations at the $10-20\%$ level, particularly for $\mstar\gtrsim10^{10.75}\msun.$ This tension is inherited by our $\rvir-$based model for size, which is the subject of this work, and so we wish to compare our size models to data in such a way that minimizes the role played by the underlying stellar-to-halo-mass relation.
-We accomplish this using {\em the $\rhalf$ clustering ratios,} described below.
-
-For each volume-limited $\mstar-$threshold sample, we additionally measure $\wproj(\rproj)$ {\em without} splitting on size, giving us measurements $\wpall, \wplarge,$ and $\wpsmall$ for each threshold sample.
-This allows us to compute the ratio $(\wplarge-\wpsmall)/\wpall,$ which we refer to as {\em the $\rhalf$ clustering ratio}, denoted as $\delta_{\rhalf}(\wproj).$ For example, a clustering ratio of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass.
-These ratios are the measurements appearing on the y-axis in each panel of Figure \ref{fig:clustering_ratio_upshot}.
-
-The points and curves in Figure \ref{fig:clustering_ratio_upshot} are all negative: small galaxies cluster more strongly relative to large.
-This presentation of the measurement makes plain that the underlying signal of $\rhalf-$dependent clustering is strongest for samples with smaller stellar mass; as $\mstar$ increases, the signal weakens and nearly vanishes for $\mstar\gtrsim10^{11}\msun.$ Strikingly, the $\rvir-$based model exhibits this $\mstar-$dependent behavior, as well as the scale-dependence of the observed clustering signal at each $\mstar.$ As described in \S\ref{subsec:censat_sizes} below, we attribute the success of this prediction to the relative sizes of central vs.
-satellite galaxies.
 
@@
 
+Motivated by \citet{kravtsov13}, we additionally explore a model in which $\rhalf$ is linearly proportional to halo virial radius:\footnote{We note that the normalization factor in \citet{kravtsov13} is 0.0125, where as our normalization is 0.01.
+The difference derives from the choice of halo radius definition: \citet{bryan_norman98} in the present work, compared to the $200c$ definition used in \citet{kravtsov13}.}
+\beq
+\label{eq:fiducial_model}
+\rhalf = 0.01\rvir.
+\eeq
+For the virial radius of halos and subhalos, we use $\rmpeak:$ the value of $\rvir$ in physical units of $\kpc$ measured at the time of peak subhalo mass.
+The relationship between $\rmpeak$ and $\mpeak$ is given by
+\beq
+\mpeak\equiv\frac{4\pi}{3}\rmpeak^{3}\Delta_{\rm vir}(\zpeak)\rho_{\rm m}(\zpeak),
+\eeq
+where for $\Delta_{\rm vir}(\zpeak)$ we use the fitting function to the ``virial" definition used in \citet{bryan_norman98}.
+For the model we refer to as the ``$\rvir-$based model", we add uncorrelated log-normal scatter of $\sigmarhalf=0.2$ dex to generate a Monto Carlo realization of the model population.
+
+\section{Results}
+\label{sec:results}
+
+\subsection{Size-Mass Scaling Relation}
+\label{subsec:one_point_function}
+
+In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ The black curve enveloped by the gray bands shows the scaling relation for SDSS galaxies, while the blue curve shows the median relation  $\median{\rhalf}{\mstar}$ implied by the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}.
+This figure shows that models in which $\rhalf\propto\rvir$ can naturally give rise to the characteristic curvature in the $\rhalf-\mstar$ relation, confirming the results in \citet{kravtsov13} in a forward modeling context.
+
+\subsection{Size-Dependent Clustering Measurements}
+\label{subsec:clustering_results}
+
+In Figure~\ref{fig:rvir_only_clustering_absolute}, we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj(\rproj).$ We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds, $\mstar>10^{9.75}\msun,$ $\mstar>10^{10.25}\msun,$ $\mstar>10^{10.75}\msun,$ and $\mstar>10^{11}\msun.$ For each threshold, we split the galaxies into ``large" and ``small" subsamples; as described in \S\ref{subsec:sizedef} and illustrated in Figure \ref{fig:sizedefinition}, our size-based selection is defined so that the subsamples have identical stellar mass functions.
+Red points with jackknife-estimated error bars show SDSS measurements of $\wproj(\rproj)$ for small galaxy samples, blue points show the same for large galaxies.
+Solid curves show $\wproj$ as predicted by the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}.
+
+The salient feature of these clustering measurements is that small galaxies cluster more strongly than large galaxies of the same stellar mass.
+This feature also holds true for galaxies predicted by the $\rvir-$based model.
+This result may be surprising, since $\rhalf\propto\rvir,$ halo mass $\rvir\propto\mhalo^{1/3},$ and clustering strength increases with $\mvir.$ Based on this simple argument, one would expect that large galaxies would be the more strongly clustered.
+We provide a resolution to this conundrum in \S\ref{subsec:censat_sizes}; before doing so, we first examine the clustering test of the $\rvir-$based model in more detail.
+
+As shown in Figure \ref{fig:baseline_sham_clustering}, the abundance matching prediction for $\wproj(\rproj)$ exhibits tension with SDSS observations at the $10-20\%$ level, particularly for $\mstar\gtrsim10^{10.75}\msun.$ This tension is inherited by our $\rvir-$based model for size, which is the subject of this work, and so we wish to compare our size models to data in such a way that minimizes the role played by the underlying stellar-to-halo-mass relation.
+We accomplish this using {\em the $\rhalf$ clustering ratios,} described below.
+
+For each volume-limited $\mstar-$threshold sample, we additionally measure $\wproj(\rproj)$ {\em without} splitting on size, giving us measurements $\wpall, \wplarge,$ and $\wpsmall$ for each threshold sample.
+This allows us to compute the ratio $(\wplarge-\wpsmall)/\wpall,$ which we refer to as {\em the $\rhalf$ clustering ratio}, denoted as $\delta_{\rhalf}(\wproj).$ For example, a clustering ratio of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass.
+These ratios are the measurements appearing on the y-axis in each panel of Figure \ref{fig:clustering_ratio_upshot}.
+
+The points and curves in Figure \ref{fig:clustering_ratio_upshot} are all negative: small galaxies cluster more strongly relative to large.
+This presentation of the measurement makes plain that the underlying signal of $\rhalf-$dependent clustering is strongest for samples with smaller stellar mass; as $\mstar$ increases, the signal weakens and nearly vanishes for $\mstar\gtrsim10^{11}\msun.$ Strikingly, the $\rvir-$based model exhibits this $\mstar-$dependent behavior, as well as the scale-dependence of the observed clustering signal at each $\mstar.$ As described in \S\ref{subsec:censat_sizes} below, we attribute the success of this prediction to the relative sizes of central vs.
+satellite galaxies.
+
 \subsection{Testing the Impact of Satellite Mass Loss}
 \label{subsec:mstar_stripping}
+%---------------------------------------------------------------------------------------------------
+\begin{figure*}
+\centering
+\includegraphics[width=12cm]{FIGS/alt_model_wp_ratios.pdf}
+\caption{
+{\bf The subdominant role of tidal stripping.}
+In all panels, the axes and points with error bars are the same as in Figure \ref{fig:clustering_ratio_upshot}.
+The solid green curves shows the prediction of the satellite mass loss model, which is in gross tension with the data due to satellites having the same size as centrals of the same mass.
+The solid purple curves show results for a model in which satellites lose mass after infall in a manner similar to what is seen in high-resolution hydrodynamical simulations, as described in \S\ref{subsubsec:strippingmodel}.
+This produces satellites that are smaller than centrals, but the effect is too mild to correctly capture the observed clustering.
+Evidently, satellite-specific mass stripping plays a sub-dominant role in setting the relative size of centrals and satellites.
+}
+\label{fig:mstarmodelclustering}
+\end{figure*}
+%-----------------------------------------------------------------------------------------------------
 
@@
 As we argue in \S\ref{sec:interpretation}, this supports the conclusion that the relative difference between central and satellite size is at least partially in place at the time of satellite infall.
-
-%---------------------------------------------------------------------------------------------------
-\begin{figure}
-\centering
-\includegraphics[width=8cm]{FIGS/alt_model_wp_ratios.pdf}
-\caption{
-{\bf Impact of tidal stripping.}
-In all panels, the axes and points with error bars are the same as in Figure \ref{fig:clustering_ratio_upshot}.
-The solid green curves shows the prediction of the satellite mass loss model, which is in gross tension with the data due to satellites having the same size as centrals of the same mass.
-The solid purple curves show results for a model in which satellites lose mass after infall in a manner similar to what is seen in high-resolution hydrodynamical simulations, as described in \S\ref{subsubsec:strippingmodel}.
-This produces satellites that are smaller than centrals, but the effect is too mild to correctly capture the observed clustering.
-Evidently, satellite-specific mass stripping plays a sub-dominant role in setting the relative size of centrals and satellites.
-}
-\label{fig:mstarmodelclustering}
-\end{figure}
-%-----------------------------------------------------------------------------------------------------
 
@@
 %-----------------------------------------------------------------------------------------------------
+%---------------------------------------------------------------------------------------------------
+\begin{figure}
+\centering
+\includegraphics[width=8cm]{FIGS/rvir_only_cen_sat_sizes.pdf}
+\caption{
+{\bf Relative sizes of centrals and satellites.}
+In a narrow bin of halo mass $\mhalo\equiv\mpeak\approx10^{12}\msun,$ we show the distribution of model galaxy sizes for different subpopulations galaxies, as predicted by the $\rvir-$based model.
+The red histogram shows the sizes of satellites; the blue histogram shows host halos that have never passed inside the virial radius of a larger halo (``true centrals"); the green histogram host halos that were subhalos inside a larger at some point in their past history (``splashback centrals").
+In the $\rvir-$based model, galaxy size is set by the {\em physical} size of the virial radius at the time the halo attains its peak mass, naturally resulting in smaller sizes for satellites and splashback centrals relative to true centrals of the same $\mhalo.$
+}
+\label{fig:censatsizehist}
+\end{figure}
+%-----------------------------------------------------------------------------------------------------
+
+%---------------------------------------------------------------------------------------------------
+\begin{figure}
+\centering
+\includegraphics[width=8cm]{FIGS/cen_sat_size_ratios.pdf}
+\caption{
+{\bf Scaling relation for hydro sims and SAMs.}
+As a function of subhalo mass $\mhalo=\mpeak,$ we show the ratio of mean satellite-to-central size predicted by the $\rvir-$based model.
+This scaling relation should be a useful guideline for more fine-grained physical models of galaxy size that wish to reproduce the observed $\rhalf-$dependence of galaxy clustering.
+}
+\label{fig:censatsizeratios}
+\end{figure}
+%-----------------------------------------------------------------------------------------------------
 
@@
 On the other hand, we define a ``true central" as a galaxy that has never been a satellite.
-
-%---------------------------------------------------------------------------------------------------
-\begin{figure}
-\centering
-\includegraphics[width=8cm]{FIGS/rvir_only_cen_sat_sizes.pdf}
-\caption{
-{\bf Relative sizes of centrals and satellites.}
-In a narrow bin of halo mass $\mhalo\equiv\mpeak\approx10^{12}\msun,$ we show the distribution of model galaxy sizes for different subpopulations galaxies, as predicted by the $\rvir-$based model.
-The red histogram shows the sizes of satellites; the blue histogram shows host halos that have never passed inside the virial radius of a larger halo (``true centrals"); the green histogram host halos that were subhalos inside a larger at some point in their past history (``splashback centrals").
-In the $\rvir-$based model, galaxy size is set by the {\em physical} size of the virial radius at the time the halo attains its peak mass, naturally resulting in smaller sizes for satellites and splashback centrals relative to true centrals of the same $\mhalo.$
-}
-\label{fig:censatsizehist}
-\end{figure}
-%-----------------------------------------------------------------------------------------------------
 

### 2017-11-06 paper/galsize_paper.tex
Finished draft of section 5.1

@@
 
-Upon first glance, the $\rhalf-$dependence of color- and morphology-selected samples shown in Figure \ref{fig:colorclustering} appear to be driven by different principles, since trends dramatically weaken and change sign.
+Upon first glance, the $\rhalf-$dependence of color- and morphology-selected samples shown in Figure \ref{fig:colorclustering} appear to be driven by different principles, since the trends substantially weaken and change sign.
 However, even very simple models based entirely on central vs.
 satellite size differences can give rise to this behavior.
+For example, it is well known that satellites are redder than centrals \citep[e.g.,][]{vdB_etal08}; accordingly, red galaxies cluster much stronger relative to blue \citep{zehavi_etal11}.
+Pre-selecting galaxy samples by color will thus significantly weaken the dynamic range of $F_{\rm sat}$ within each color-selected subsample.
+This reduction in the role of satellites could be sufficient for the $\rhalf\propto\rvir\propto\mhalo$ of {\em central} galaxies to become the dominant effect, which would result in the mild, reversed trend seen in the top panels of Figure \ref{fig:colorclustering}.
+The same mechanism could be at work for the case of morphology pre-selection, except that for disk-dominated systems, there would need to be a larger residual correlation with satellite designation relative to blue-selected samples \citep[This is, in fact, exactly the trend reported in][]{weinmann_etal08}.
 
-{\color{blue} APH: finish discussion of color and morphology.}
+While we consider such an explanation plausible, a conclusive determination of the principles underlying the clustering trends shown in Figure \ref{fig:colorclustering} requires proper forward modeling of morphology and color jointly with galaxy size.
+Such an effort is beyond the scope, but well-motivated, by the present work.
 

### 2017-11-06 paper/galsize_paper.tex
Revisions to section 5.2

@@
 
-A straightforward resolution to this puzzle is shown in Figure \ref{fig:censatsizehist}, which compares the $\rhalf$ distributions of central, satellite, and splashback galaxies with the same halo mass $\mhalo\equiv\mpeak\approx10^{12}\msun.$ A ``splashback central"  is defined as a present-day central that used to be a satellite, i.e., its main progenitor halo passed inside the virial radius of a larger halo at some point in its past history.
+A straightforward resolution to the first puzzle is shown in Figure \ref{fig:censatsizehist}, which compares the $\rhalf$ distributions of central, satellite, and splashback galaxies with the same halo mass $\mhalo\equiv\mpeak\approx10^{12}\msun.$ A ``splashback central"  is defined as a present-day central that used to be a satellite, i.e., its main progenitor halo passed inside the virial radius of a larger halo at some point in its past history.
 On the other hand, we define a ``true central" as a galaxy that has never been a satellite.
@@
 This reduction in the role of satellites could be sufficient for the $\rhalf\propto\rvir\propto\mhalo$ of {\em central} galaxies to become the dominant effect, which would result in the mild, reversed trend seen in the top panels of Figure \ref{fig:colorclustering}.
-The same mechanism could be at work for the case of morphology pre-selection, except that for disk-dominated systems, there would need to be a larger residual correlation with satellite designation relative to blue-selected samples \citep[This is, in fact, exactly the trend reported in][]{weinmann_etal08}.
+The same satellite-driven mechanism could be at work for the case of morphology pre-selection \citep[as in the morphology models developed in][]{skibba_etal08}, except that for disk-dominated systems, there would need to be a larger residual correlation with satellite designation relative to blue-selected samples \citep[which is, in fact, exactly the trend reported in][]{weinmann_etal08}.
 
@@
 Such an effort is beyond the scope, but well-motivated, by the present work.
+See Section \ref{subsec:broader_implications} for further discussion.
 
@@
 Physical explanations for differences between the sizes of centrals and satellites fall into two categories, depending on whether or not the processes involved are post-infall and satellite-specific.
-The success of the $\rvir-$based model, together with the failure of the $\mstar$+stripping model, suggests that the relative size of central and satellite galaxies is largely driven by the {\rm pre-infall} evolution of the satellite.
+In the satellite mass loss model, satellites evolve exactly as centrals prior to the time of infall; this model assumes that {\em all} satellite size truncation occurs after the time of infall.
+The $\rvir-$based model assumes the opposite: namely that the size of {\em all} galaxies is statistically set by the $\rmpeak,$ the physical size of the virial radius at the time at which $\mhalo$ stops growing.
+This assumption is the natural extension of the abundance matching approximation that stellar mass largely stops growing at this time (including in-situ and ex-situ growth).
+The halos of typical satellites reach $\mpeak$ far outside the virial radius of their ultimate host halo \citep{behroozi_etal14}, and so in the $\rvir-$based model the size differences between satellites and centrals is largely in place prior to the time of satellite infall.
+
 The clustering ratios in Figure \ref{fig:mstarmodelclustering} show that the impact of physically motivated levels of satellite mass loss likely cannot explain the $\rhalf-$dependent clustering seen in SDSS.
 As an additional test, we reach the same conclusion when implementing an even more extreme $\mstar-$stripping model in which stellar mass loss is linearly proportional to halo mass loss \citep[][Model 1]{watson_etal12}.
+The success of the $\rvir-$based model, together with the failure of the satellite mass loss model, suggests that the relative size of central and satellite galaxies is largely driven by the {\rm pre-infall} evolution of the satellite.
 
-While these clustering measurements give supporting evidence that satellite mass stripping plays a sub-dominant role in shaping galaxy size, we point out that our treatment of satellite mass loss is only approximate: we have modified the size of satellites without self-consistently modifying total stellar mass.
+The broad features of the $\wproj(\rproj)$ measurements shown in Figure \ref{fig:colorclustering} give insight into the characteristics that should be exhibited by any model for the relationship between $B/T$ and $\rhalf.$ First, the bottom right panel of Figure \ref{fig:colorclustering} indicates that the size of the bulge has only a tenuous connection to the properties of its parent dark matter halo.\footnote{Strictly speaking, the size of the bulge could in principle be closely connected to any number of dark matter halo properties, so long as those halo properties do not significantly impact two-point clustering.} Second, for disk-dominated galaxies, the observed $\rhalf-$dependent clustering suggests that at fixed $\mstar,$ the size of the disk is strongly correlated with whether or not the galaxy is a satellite.
+These findings imply that bulge prominence is intimately connected with the quenching of star-formation, but that there is wide variation in star-formation histories amongst disk-dominated galaxies, in agreement with numerous previous findings \citep[see, e.g.,][]{woo_etal15,font_etal17}.
+
+Recent progress has substantially improved capabilities for the richness of the predictions of empirical galaxy--halo models \citep{becker15,cohn17,moster_etal17}.
+This new class of models has accomplished this by empirically modeling star-formation rate, and then integrating SFR along each halo's history to differentially build up stellar mass.
+In ongoing follow-up work, we are currently extending this new class of models to differentially build up the disk and bulge across cosmic time using computationally efficient empirical modeling methods.
+In addition to treating the multi-dimensional nature of the problem, this will allow us to use data at higher redshift in a self-consistent manner.
+
+% A possibly overkill caveat paragraph:
+%While these clustering measurements give supporting evidence that satellite mass stripping plays a sub-dominant role in shaping galaxy size, we point out that our treatment of satellite mass loss is only approximate: we have modified the size of satellites without self-consistently modifying total stellar mass.
 In the present work, we have opted not to develop and fine-tune a complex, semi-analytic model; instead, we have made a simple ``first-order" estimate for the level at which satellite-specific stripping impacts the two-point function.
@@
 
-As discussed in \S\ref{sec:future}, we are currently pursuing follow-up work in which we jointly model morphological type together with galaxy size.
-We consider forward modeling methods to be a requisite for meaningful progress on this issue, not only to properly handle the multi-dimensional nature of the problem, but also to rigorously treat systematic errors that plague inference based on galaxy group catalogs \citep[see][for a thorough discussion]{campbell_etal15}.
-
 Our methodology is closely aligned with \citet{somerville_etal17}, who studied the empirical modeling features that are necessary to recover the tight scatter in the observed $\mean{\rhalf}{\mstar}$ relation.
@@
 
-{\color{blue} APH comment: Some of this discussion can/should be migrated to \S\ref{subsec:broader_implications}.
-Depending on how that section ends up looking, it may be that this entire Future Directions section can be deleted after cannibalization.}
-
 %The precision cosmology program also depends critically on accurate modeling of galaxies, so that cosmological parameter inference can be confidently conducted without undue interference from uncertainty in baryonic physics \citep{LSST_science,LSST_galaxies}.
-
-\subsection{Jointly modeling $\langle\mstar\vert\mhalo\rangle$}
-\label{subsec:joint_smhm_modeling}
 
@@
 
-\subsection{Jointly modeling morphology}
-\label{subsec:joint_morphology_modeling}
-
-A proper interpretation of the results clustering results shown in Figure \ref{fig:colorclustering} requires forward-modeling the joint dependence of the galaxy-halo connection upon $\mstar, \rhalf, g-r, $ and $B/T,$ which is beyond the scope of this work.
-Nonetheless, the broad features of these $\wproj(\rproj)$ measurements give insight into the characteristics that any model for these properties should exhibit.
-
-First, the bottom right panel of Figure \ref{fig:colorclustering} indicates that the size of the bulge has only a tenuous connection to the properties of its parent dark matter halo.\footnote{Strictly speaking, the size of the bulge could in principle be closely connected to any number of dark matter halo properties, so long as those halo properties do not significantly impact two-point clustering.} Second, for disk-dominated galaxies, the observed $\rhalf-$dependent clustering suggests that at fixed $\mstar,$ the size of the disk is strongly correlated with whether or not the galaxy is a satellite.
-These findings imply that bulge prominence is intimately connected with the quenching of star-formation, but that there is wide variation in star-formation histories amongst disk-dominated galaxies, in agreement with numerous previous findings \citep[see, e.g.,][]{woo_etal15,font_etal17}.
-
-Previous studies of large-scale structure measured by SDSS indicate that morphological type has a significant influence on galaxy clustering \citep{skibba_etal08}.
-Because morphology is covariant with star-formation rate (SFR) and $\rhalf,$ accounting for this dependency will require simultaneously modeling each of these variables.
-Historically, such a task has been beyond the purview of empirical models.
-However, recent progress has substantially improved the richness of the predictions that galaxy-halo models are capable of \citep{becker15,cohn17,moster_etal17}.
-This new class of models has accomplished this by empirically modeling star-formation rate, and then integrating SFR along each halo's history to differentially build up stellar mass.
-We are currently extending this new class of models to differentially build up the disk and bulge across cosmic time using computationally efficient empirical modeling methods.
-In addition to treating the multi-dimensional nature of the problem, this will allow us to use data at higher redshift in a self-consistent manner.
+Figure \ref{fig:censatsizeratios} shows that the satellites in $\mhalo\approx10^{12}\msun$ halos can be as large as $\lesssim40-50\%$ smaller than their central galaxy counterparts.
+Since the satellite fraction varies quite significantly with morphology and/or color, we have demonstrated that it is entirely plausible that most of the observed environmental trends of galaxy size can be understood simply in terms of central vs.
+satellite size differences.
+While it remains to be seen whether this explanation ends up comprising the whole story, one thing is now clear: it is simply not possible to reliably analyze environmental trends of galaxy $\rhalf$ without properly accounting for satellites.
+Because of the large systematics that are common in contemporary group-finding methods \citep{campbell_etal15}, we consider forward modeling methods to be a requisite for meaningful continued progress on this topic.\footnote{We note that group-finders may play an important role in future analyses of galaxy size.
+However, it was shown in \citet{campbell_etal15} that treating observed groups as if they were correctly identified dark matter halos can lead to entirely unreliable conclusions.
+The robust method to extract information from galaxy group catalogs is instead to generate a Monte Carlo realization of a forward model, and then run the same group-finding algorithm on the mock as was run on the data, enabling a proper apples-to-apples comparison.}
 

### 2017-11-06 paper/galsize_paper.tex
Updated figures

@@
 \centering
-\includegraphics[width=8cm]{FIGS/baseline_sham_orphans.pdf}
+\includegraphics[width=8cm]{FIGS/baseline_sham.pdf}
 \caption{
-{\bf SHAM + orphan clustering predictions.}
+{\bf Abundance matching clustering predictions.}
 Using the abundance matching methods described in \S\ref{subsec:sham}, we compare the projected clustering of mock vs.
@@
 Each panel shows the comparison for a volume-limited sample defined by a different $\mstar-$threshold.
-Black points with error bars show SDSS measurements; solid red (black) curves show the abundance matching prediction including (excluding) the effect of orphan subhalos (see Appendix A).
+Black points with error bars show SDSS measurements; solid black curves show the abundance matching prediction of our fiducial model, which includes the effect of orphan subhalos (see Appendix A).
 Including orphans mitigates the discrepancy in the clustering predicted by traditional, $\mpeak-$based SHAM based, though mild tension remains for $\mstar\gtrsim10^{10.75}\msun.$
@@
 Our results can be treated as a boundary condition for more complex and fine-grained models of galaxy size, such as semi-analytic models and hydrodynamical simulations.
+For convenience, Figure \ref{fig:censatsizeratios} provides a simple summary statistic that can be used as a diagnostic for calibrating alternative modeling efforts.
 We view the present work as a pilot study that motivates a Bayesian inference program to tightly constrain the galaxy size-halo connection with forward modeling techniques, in direct analogy to the literature on the stellar-to-halo-mass relation.
@@
 We model $\mathcal{F}_{\rm orphan}=\mathcal{F}_{\rm orphan}(M_{\rm peak},M_{\rm host}),$ where $\mpeak$ is the peak mass of the disrupted subhalo, and $\mhost$ is the present-day virial mass of its $z=0$ host halo.
-For the $\mpeak-$dependence, we select $50\%$ of disrupted subhalos with $\mpeak=10^{11}\msun,$ $0\%$ of subhalos with $\mpeak=10^{13}\msun,$ linearly interpolating in $\log\mpeak$ for intermediate values of $\mpeak.$ At each $\mpeak,$ the selection of disrupted halos is not random; instead, we preferentially select the subhalos with larger $\mhost,$ which we intend to offset the increased difficulty of subhalo-finding algorithms to identify subhalos with especially small values of  $\mu\equiv\mpeak/\mhost.$
+For the $\mpeak-$dependence, we select $50\%$ of disrupted subhalos with $\mpeak=10^{11}\msun,$ $0\%$ of subhalos with $\mpeak=10^{13}\msun,$ linearly interpolating in $\log\mpeak$ for intermediate values of $\mpeak.$ At each $\mpeak,$ the selection of disrupted halos is not random; instead, we preferentially select the subhalos with larger $\mhost,$ which we intend to offset the increased difficulty of subhalo-finding algorithms to identify subhalos with especially small values of  $\mu\equiv\mpeak/\mhost.$ We refer to this model as our ``fiducial orphan model".
+We assess the role of the nontrivial features in $\mathcal{F}_{\rm orphan}$ by randomly selecting the same number of orphan subhalos, referring to this alternate model as the ``random orphan model".
 
-The impact of our orphan treatment on $\mstar-$threshold clustering is shown in Figure \ref{fig:baseline_sham_clustering} in the main body of the text.
-We show the impact on $\rhalf-$dependent clustering in Figure \ref{fig:orphan_clustering_ratios}.
-The character of the effect of orphan subhalos in Figure \ref{fig:orphan_clustering_ratios} is as expected.
-The orphan catalog has a higher satellite fraction than the standard subhalo catalog; since satellites have preferentially smaller sizes and stronger clustering, the black curves are more negative relative to the red.
-Orphan halos also typically have earlier-than-average values of $\zpeak$ relative to ordinary subhalos, which also enhances differences between central and satellite sizes.
-
-Encouragingly, when tuning $\mathcal{F}_{\rm orphan}$ so that the overall $\mstar-$threshold clustering is roughly correct (as in Figure \ref{fig:baseline_sham_clustering}), the same level of tuning is required for a successful prediction of $\rhalf-$dependent clustering.
-This figure gives quantitative motivation for the program described in \S\ref{sec:future} to jointly constrain the satellite fraction $F_{\rm sat}(\mstar)$ together with models for galaxy size.
+Figure \ref{fig:orphan_effects} illustrates the impact of the orphan selection function on $\mstar-$threshold clustering (top panel) and the satellite fraction (bottom panel).
+Comparing the black to the red curves shows that including orphans substantially boosts small-scale clustering due to the increased satellite fraction.
+Comparing the orange to the black curves, we see that randomly selecting orphans results in excessive small-scale clustering for the higher-mass threshold samples due to the inclusion of too many disrupted subhalos with large values of $\mpeak.$
 
@@
 \centering
-\includegraphics[width=8cm]{FIGS/clustering_ratios_orphan_impact.pdf}
+\includegraphics[width=8cm]{FIGS/baseline_sham_orphans.pdf}
+\includegraphics[width=8cm]{FIGS/orphan_satellite_fraction.pdf}
 \caption{
-Points with error bars as well as the black curves are the same as in Figure \ref{fig:clustering_ratio_upshot}.
-Red curves show predictions for the $\rhalf-$clustering ratios of the $\rvir-$based model, but excluding orphan subhalos.
+{\bf Impact of the orphan selection function.} The {\em top panel} is identical to Figure \ref{fig:baseline_sham_clustering}, but includes additional curves for the case of randomly selected orphan halos (orange curves), and no orphans at all (red curves).
+As a function of stellar mass, the {\em bottom panel} shows the satellite fraction, i.e., the fraction of objects that are not central galaxies.
 }
-\label{fig:orphan_clustering_ratios}
+\label{fig:orphan_effects}
 \end{figure}

### 2017-11-06 galsize_models/models/load_baseline_catalogs.py

@@ -22,7 +22,8 @@ from ..measurements import load_umachine_sdss_with_meert15
 
 
 __all__ = ('moster13_based_mock', 'load_umachine_mock', 'load_baseline_halocat',
-        'load_orphan_mock', 'moustakas_sham', 'load_orphan_subhalos', 'orphan_selection')
+        'load_orphan_mock', 'moustakas_sham', 'load_orphan_subhalos', 'orphan_selection',
+        'random_orphan_selection')
 
 default_umachine_galprops = list((
     'sm', 'sfr', 'obs_sm', 'obs_sfr', 'icl', 'halo_id', 'upid',
@@ -278,3 +279,16 @@ def orphan_selection(catalog, mpeak_abscissa=(11, 13), prob_select_ordinates=(0.
     selected_orphan_mask = orphans[selection_key] > 1-prob_select
     selection_indices[eligible_orphan_mask] = selected_orphan_mask
     return selection_indices
+
+
+def random_orphan_selection(catalog, num_to_select):
+    """
+    """
+    num_subhalos = len(catalog)
+    selection_indices = np.arange(num_subhalos).astype(int)
+    surviving_subhalo_indices = selection_indices[~catalog['orphan']]
+    disrupted_subhalo_indices = selection_indices[catalog['orphan']]
+    selected_orphan_indices = np.random.choice(disrupted_subhalo_indices,
+            num_to_select, replace=False)
+    return np.concatenate((surviving_subhalo_indices, selected_orphan_indices))
+

### 2017-11-06 paper/galsize_paper.tex
Added paragraph in Intro describing each section's contents

@@
 In the present work, we exploit the constraining power of $\wproj(\rproj)$ to test empirical models connecting galaxy $\mstar$ and $\rhalf$ to the properties of the galaxy's parent dark matter halo.
+
+The approach we take is is to forward model the $\rhalf-$halo connection: we generate a Monte Carlo realizations of the model, and then make synthetic measurements in a manner that closely mimics the measurements we make on our observed galaxy samples.
+We describe the dataset and simulations we use in \S\ref{sec:data}, and our forward-modeling methods in \S\ref{sec:model}.
+All of our primary results appear in \S\ref{sec:results}, and their theoretical interpretation in \S\ref{sec:interpretation}.
+We contextualize our findings in terms of previous work in \S\ref{sec:previous_work}, and discuss future directions in \S\ref{sec:future}.
+We conclude the paper with a summary of our principal results in \S\ref{sec:conclusion}.
 
@@
 \section{Relation to Previous Work}
-\label{subsec:previous_work}
+\label{sec:previous_work}
 

### 2017-11-07 paper/galsize_paper.tex
Updated draft with alternative version of color-selected clustering results, now neglecting to simultaneously address B/T and g-r, significantly simplifying the discussion with minimal loss of concrete insight

@@
 In the version of this catalog that we use,\footnote{Our $\mstar$ and $\rhalf$ measurements are derived from different photometry pipelines; this is driven by our desire for consistency with the \citet{behroozi_etal15} completeness cuts used in our clustering measurements.
-We note that we have repeated our analysis for stellar mass measurements based on \citet{meert_etl15}, finding only minor quantitative, and no qualitative changes to our results.} two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile to determine the half-light radius of total $r-$band luminosity, $\rhalf.$
+We note that we have repeated our analysis for stellar mass measurements based on \citet{meert_etal15}, finding only minor quantitative, and no qualitative changes to our results.} two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile to determine the half-light radius of total $r-$band luminosity, $\rhalf.$
 
@@
 We illustrate this for the particular case of $\mstar>10^{10.25}\msun$ in left panel of Figure~\ref{fig:sizedefinition}, which shows histograms of stellar mass for the two subsamples.
-The right panel of Figure~\ref{fig:sizedefinition} compares histograms of their size distributions, which partially overlap due to the variation in $\median{\rhalf}{\mstar}$ across the $\mstar-$ range of the threshold sample.
+The right panel of Figure~\ref{fig:sizedefinition} compares histograms of the two size distributions, which partially overlap due to the variation in $\median{\rhalf}{\mstar}$ across the $\mstar-$ range of the threshold sample.
 
@@
 {\bf Definition of ``small" and ``large" galaxies.} For a volume-limited SDSS galaxy sample defined by $M_{\ast}>10^{10.25}M_{\odot},$ we visually demonstrate how we classify galaxies into ``small" and ``large" subsamples.
-As described in detail in \S\ref{subsec:sizedef}, we compute the median value $\median{\rhalf}{\mstar}$ using a sliding window with a width of $1000$ galaxies at each value of $\mstar.$ The {\em left panel} compares the stellar mass functions $\phi(\mstar)$ of the two samples, confirming that our method for separating ``small" from ``large" galaxies yields subsamples with statistically indistinguishable $\phi(\mstar)$.
+As described in detail in \S\ref{subsec:sizedef}, we compute the median value $\median{\rhalf}{\mstar}$ at the stellar mass of each galaxy in the sample, and divide the sample into two based on this $\mstar-$dependent cut.
+The {\em left panel} compares the stellar mass functions $\phi(\mstar)$ of the two samples, confirming that our method for separating ``small" from ``large" galaxies yields subsamples with statistically indistinguishable $\phi(\mstar)$.
 The {\em right panel} shows histograms of $\rhalf$ for the two subsamples, which partially overlap due to the finite range of $\mstar$ in the volume-limited sample.
@@
 As described in the appendix, we include a prescription for supplementing the ordinary {\tt Rockstar} subhalo catalog with disrupted subhalos, so that some of our model galaxies inhabit subhalos that are no longer resolved and do not appear in the standard publicly available catalog.
+
+Figure \ref{fig:baseline_sham_clustering} shows that our implementation of SHAM produces model galaxies whose projected clustering, $\wproj(\rproj)$, is in reasonably good agreement with SDSS galaxies.
+We note, however, that $\wproj(\rproj\gtrsim1{\rm Mpc})$ is $\sim10-20\%$ too weak at stellar mass $\mstar\gtrsim10^{10.75}\msun.$
 
@@
 
-In the first class of models we explore, we suppose that stellar mass $\mstar$ is the statistical regulator of $\rhalf,$ so that galaxy sizes are drawn from a log-normal distribution with $0.2$ dex of scatter centered at $\median{\rhalf}{\mstar}.$ To implement this model, for simplicity we tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form \citep[see, e.g.,][]{zhang_yang17}.
+In one class of models we explore, we suppose that stellar mass $\mstar$ is the statistical regulator of $\rhalf,$ so that galaxy sizes are drawn from a log-normal distribution with $0.2$ dex of scatter centered at $\median{\rhalf}{\mstar}.$ To implement this model, for simplicity we tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form \citep[see, e.g.,][]{zhang_yang17}.
 
@@
 The two gray bands enveloping the black curve show the $50\%$ and $90\%$ percentile regions.
-The blue curve shows $\rvir-$based model in which $\median{\rhalf}{\rvir}=0.01\rvir.$ This figure confirms that a linear relationship between $\rvir$ and $\rhalf,$ convolved against the nonlinear relationships between $\rvir, \mhalo$ and $\mstar,$  predicts the characteristic curvature in the relation $\median{\rhalf}{\mstar}$ over a wide range in mass.
+The blue curve shows $\rvir-$based model in which $\median{\rhalf}{\rvir}=0.01\rvir.$ This figure confirms that a linear relationship between $\rvir$ and $\rhalf$ predicts the characteristic curvature in the relation $\median{\rhalf}{\mstar}$ over a wide range in mass.
 }
@@
 For each volume-limited $\mstar-$threshold sample, we additionally measure $\wproj(\rproj)$ {\em without} splitting on size, giving us measurements $\wpall, \wplarge,$ and $\wpsmall$ for each threshold sample.
-This allows us to compute the ratio $(\wplarge-\wpsmall)/\wpall,$ which we refer to as {\em the $\rhalf$ clustering ratio}, denoted as $\delta_{\rhalf}(\wproj).$ For example, a clustering ratio of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass.
-These ratios are the measurements appearing on the y-axis in each panel of Figure \ref{fig:clustering_ratio_upshot}.
+This allows us to compute the ratio $(\wplarge-\wpsmall)/\wpall,$ which we refer to as {\em the $\rhalf$ clustering ratio}.
+These ratios, denoted as $\delta\wproj/\wproj,$ are the measurements appearing on the y-axis in each panel of Figure \ref{fig:clustering_ratio_upshot}.
+As a specific example, a clustering ratio of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass.
 
@@
 In all panels, the axes and points with error bars are the same as in Figure \ref{fig:clustering_ratio_upshot}.
-The solid green curves shows the prediction of the satellite mass loss model, which is in gross tension with the data due to satellites having the same size as centrals of the same mass.
+The solid green curves shows the prediction of a model where $\rhalf$ is statistically set by $\mstar,$ in the complete absence of satellite mass loss.
+Such a model would predict zero $\rhalf-$dependence to galaxy clustering, in gross tension with observations.
 The solid purple curves show results for a model in which satellites lose mass after infall in a manner similar to what is seen in high-resolution hydrodynamical simulations, as described in \S\ref{subsubsec:strippingmodel}.
@@
 The green curves in Figure~\ref{fig:mstarmodelclustering} test the clustering predictions of the model described in \S\ref{subsubsec:strippingmodel} {\em before} applying the satellite mass loss prescription.
-Thus the green curves pertain to a model where $\rhalf$ is a purely random log-normal distribution centered at $\median{\rhalf}{\mstar}.$ By construction, this model predicts no dependence at all of galaxy clustering upon $\rhalf$ at fixed $\mstar,$ simply because the scatter of $\rhalf$ about $\median{\rhalf}{\mstar}$ is uncorrelated with any other property.
+Thus the green curves pertain to a model where $\rhalf$ follows a purely random log-normal distribution centered at $\median{\rhalf}{\mstar}.$ By construction, this model predicts no dependence at all of galaxy clustering upon $\rhalf$ at fixed $\mstar,$ simply because the scatter of $\rhalf$ about $\median{\rhalf}{\mstar}$ is uncorrelated with any other variable.
 The application of satellite mass loss introduces correlations in the scatter: after mass loss, satellites have smaller sizes than centrals of the same $\mstar$ due to post-infall stripping.
 
-As shown by the purple curves in Figure \ref{fig:mstarmodelclustering}, satellite mass loss impacts $\rhalf-$dependent clustering in the expected manner.
+The purple curves in Figure \ref{fig:mstarmodelclustering} show that satellite mass loss impacts $\rhalf-$dependent clustering in the expected manner.
 The ``small" galaxy population has a higher satellite fraction due to satellites being smaller than centrals of the same $\mstar,$ and so in this model small galaxies cluster more strongly relative to large.
-However, the magnitude of the effect is evidently is not strong enough to produce clustering predictions that are consistent with SDSS.
-Evidently it is difficult to strip enough mass from satellites so that the $\rhalf-$dependent clustering is in agreement with observations.
+However, the magnitude of the effect is not strong enough to produce clustering predictions that are consistent with SDSS.
+Evidently it is difficult to strip enough mass from satellites so that the $\rhalf-$dependent clustering predictions are in agreement with observations.
 As we argue in \S\ref{sec:interpretation}, this supports the conclusion that the relative difference between central and satellite size is at least partially in place at the time of satellite infall.
 
-\subsection{The Role of Morphology and Color}
+\subsection{The Role of Galaxy Color}
 \label{subsec:colormorph}
 
-In this section we take a preliminary look at how galaxy clustering exhibits simultaneous dependence upon broadband color, morphology, and size.
+In this section we take a preliminary look at how galaxy clustering exhibits simultaneous dependence upon broadband color and size.
 Beginning from the $\mstar>10^{10.25}\msun$ sample used above, we first divide the sample into ``red" and ``blue" subsamples according to a $g-r=0.65$ cut, the rough location of the trough of the green valley for this stellar mass.
@@
 
-In the top left panel of Figure \ref{fig:colorclustering} we show the clustering of large vs.
-small red galaxies; in the top right panel we show the same for blue galaxies.
+Figure \ref{fig:colorclustering} shows the clustering of large vs.
+small galaxies, separately for red and blue samples.
 For each color-selected sample, large galaxies are slightly more strongly clustered relative to small galaxies.
-Comparing the top panels of Figure \ref{fig:colorclustering} to the the upper right panel of Figure \ref{fig:rvir_only_clustering_absolute} shows the dramatic impact of galaxy color selection upon $\rhalf-$dependent clustering.
+Comparing Figure \ref{fig:colorclustering} to the the upper right panel of Figure \ref{fig:rvir_only_clustering_absolute} shows the dramatic impact of galaxy color selection upon $\rhalf-$dependent clustering.
 For $\mstar-$complete samples, small galaxies cluster much stronger than large galaxies; for color-selected samples, the reverse is true, and the magnitude of the effect weakens considerably.
-
-The bottom panels of Figure \ref{fig:colorclustering} show results that are analogous to the top panels, but instead using of $g-r$ color, we first divide the $\mstar>10^{10.25}\msun$ sample into ``bulge-dominated" and ``disk-dominated" sequences according to $B/T,$ the fraction of $r-$band flux coming from the bulge component of the 2d light profile measurements in the \citet{meert_etal15} catalog.
-We define a galaxy as bulge-dominated if $B/T<0.25,$ and disk-dominated if $B/T>0.75.$ We separately split the disk-dominated and bulge-dominated subsample into two based on the median size $\median{\rhalf}{\mstar;B/T}$ appropriate for each subsample.
-The bottom left panel of Figure \ref{fig:colorclustering} compares the clustering of small vs.
-large disk-dominated galaxies; the bottom right panel shows the same comparison for bulge-dominated galaxies.
-
-The contrast between the two bottom panels is stark.
-The clustering of large vs.
-small bulge-dominated galaxies has almost no dependence upon $\rhalf.$ On the other hand, for disk-dominated galaxies, small galaxies are much more strongly clustered, and the effect is strong.
-In fact, comparing the bottom left panel of Figure \ref{fig:colorclustering} to the top right panel of Figure \ref{fig:rvir_only_clustering_absolute}, we see that $\rhalf-$dependent clustering is quite similar between disk-dominated galaxies and $\mstar-$threshold samples.
 We discuss a halo model interpretation of these trends in \S\ref{sec:interpretation}.
@@
 \centering
-\includegraphics[width=8cm]{FIGS/blue_sdss_size_dependent_clustering_9p75_to_10p25.pdf}
-\includegraphics[width=8cm]{FIGS/red_sdss_size_dependent_clustering_9p75_to_10p25.pdf}
-\includegraphics[width=8cm]{FIGS/disk_sdss_size_dependent_clustering_9p75_to_10p25.pdf}
-\includegraphics[width=8cm]{FIGS/bulge_sdss_size_dependent_clustering_9p75_to_10p25.pdf}
+\includegraphics[width=8cm]{FIGS/color_selected_size_dependent_clustering.pdf}
 \caption{
-{\bf Distinct $\rhalf-$dependence of clustering for color- or morphology-selected galaxy samples.}
-All panels show the clustering of galaxies in the same bin of stellar mass: $10^{9.75}<\mstar/\msun<10^{10.25}.$ In the {\em upper left} panel, we first select blue galaxies based on $g-r<0.6,$ and subsequently compute $\median{\rhalf}{\mstar}$ {\em of the color-selected sample}.
-This results in identical stellar mass function for large and small blue galaxy samples, in analogy to the left panel of Figure \ref{fig:sizedefinition}.
-The {\em upper right panel} shows results of the same procedure for ``red" galaxies, defined by $g-r>0.6.$ The top two panels show that for color-selected samples, the magnitude of the $\rhalf-$dependence of clustering is dramatically reduced, and changes sign, relative to $\mstar-$complete samples.
-Using the \citet{meert_etal15} measurements of the disk/bulge decomposition of the 2d $r-$band luminosity profile $L_{\rm r},$ the bottom left panel shows analogous results for disk-dominated galaxies defined by $L_{\rm r}^{\rm bulge}<L_{\rm r}^{\rm tot}/4;$ the bottom right panel shows results for bulge-dominated galaxies defined by $L_{\rm r}^{\rm disk}<L_{\rm r}^{\rm tot}/4.$
+{\bf Distinct $\rhalf-$dependence of clustering for color-selected galaxy samples.}
+Projected clustering of SDSS galaxies in the bin of stellar mass: $10^{9.75}<\mstar/\msun<10^{10.25}.$ For both ``blue" and ``red" samples, we first divide SDSS galaxies falling in the $\mstar$ bin based on a color cut at $g-r=0.65.$ We then subsequently compute $\median{\rhalf}{\mstar; {\rm red}}$ and $\median{\rhalf}{\mstar; {\rm blue}}$.
+In analogy to the left panel of Figure \ref{fig:sizedefinition}, this sample definition results in identical stellar mass function for large and small subsamples, separately for both red and blue parent samples.
+We then measure $\wproj$ for each of the four subsamples, plotting the results with color-coding as specified in the legend.
+At this stellar mass, pre-selecting galaxy samples by color results in a dramatic weakening of the $\rhalf-$dependence of $\wproj$ relative to $\mstar-$complete samples, as well as a sign-reversal of the signal.
 }
@@
 {\bf Prediction for $\rhalf-$dependence of galaxy lensing.}
-Using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}, we make predictions for as-yet-unseen measurements of the $\rhalf-$dependence of galaxy lensing of $\mstar-$complete samples.
-To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which the reverse is true: for both blue and red samples, $\Delta\Sigma$ of small galaxies is (weakly) suppressed relative to large galaxies.
-As a generic consequence of satellites being smaller than centrals of the same mass, we predict that the analogous measurement for $\mstar-$complete samples will show $\Delta\Sigma$ of small galaxies to be much stronger relative to large galaxies of the same stellar mass.
+Using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}, we make predictions for as-yet-unseen measurements of the $\rhalf-$dependence of galaxy lensing of $\mstar-$complete samples, where ``small" and ``large" subsamples are defined as in \S\ref{subsec:sizedef}.
+As a generic consequence of satellites being smaller than centrals of the same mass, we predict that future lensing measurements of $\mstar-$complete samples will show $\Delta\Sigma$ of small galaxies to be significantly stronger relative to large galaxies of the same stellar mass.
+To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which the trend is reversed and weakened: for both blue and red samples, $\Delta\Sigma$ of large galaxies is (slightly) stronger relative to small galaxies.
 }
@@
 First, the modeling assumption $\rhalf\propto\rvir$ predicts size-dependent galaxy clustering that is in quite good agreement with observations, particularly considering the simplicity of the model.
-Yet, small galaxies cluster more strongly relative to large, which seems at odds with naive expectations based on halo mass, since $\rvir\propto\mvir.$ Second, there appears to be a highly non-trivial dependence of $\rhalf-$dependent clustering upon whether or not the galaxy sample has been selected by color or morphology.
+Yet, small galaxies cluster more strongly relative to large, which seems at odds with naive expectations based on halo mass, since $\rvir\propto\mvir.$ Second, there appears to be a highly non-trivial dependence of $\rhalf-$dependent clustering upon whether or not the galaxy sample has been selected by color.
 We propose a simple and unified solution to both puzzles in \S\ref{subsec:censat_sizes}, and discuss the broader implications of our interpretation in \S\ref{subsec:broader_implications}.
@@
 
-In the $\rvir-$based model, satellite and splashback galaxies are smaller than centrals of the same halo mass due to the physical size of their halo being smaller at earlier times $\zpeak.$ There are two distinct reasons why this feature results in small galaxies being more strongly clustered relative to larger galaxies of the same mass.
+In the $\rvir-$based model, satellites and splashback galaxies are smaller than centrals of the same halo mass due to the physical size of their halo being smaller at earlier times $\zpeak.$ There are two distinct reasons why this feature results in small galaxies being more strongly clustered relative to larger galaxies of the same mass.
 First and foremost, satellite galaxies statistically occupy higher mass host halos that are more strongly clustered.
-So in models where satellites are smaller than centrals, at fixed $\mstar$ the ``small" subsample will naturally have a higher satellite fraction, boosting the clustering of small galaxies relative to large of the same stellar mass.
-Second, at fixed mass, halos of $L_\ast$ galaxies that form earlier are more strongly clustered, a phenomenon commonly known as {\em halo assembly bias}.
-Splashback halos are typically earlier-forming than true centrals, and so models where splashback halos host smaller-than-average galaxies will naturally predict smaller galaxies being the more strongly clustered.
+So in models where satellites are smaller than centrals of the same mass, smaller galaxies will have a higher satellite fraction, boosting the clustering of small relative to large galaxies of the same stellar mass.
+Second, at fixed mass, halos of $L_\ast$ galaxies that form earlier are more strongly clustered, a phenomenon commonly known as {\em halo assembly bias} \citep{gao_white05,wechsler_etal06}.
+Splashback halos are typically earlier-forming than true centrals \citep{wang_etal09}, and so models where splashback halos host smaller-than-average galaxies will naturally predict smaller galaxies being the more strongly clustered \citep[see][for an example of the splashback-dependence of halo clustering]{sunayama_etal16}.
 
@@
 
-Upon first glance, the $\rhalf-$dependence of color- and morphology-selected samples shown in Figure \ref{fig:colorclustering} appear to be driven by different principles, since the trends substantially weaken and change sign.
+Upon first glance, the $\rhalf-$dependence of color-selected samples shown in Figure \ref{fig:colorclustering} appear to be driven by different principles, since the trends substantially weaken and change sign.
 However, even very simple models based entirely on central vs.
 satellite size differences can give rise to this behavior.
-For example, it is well known that satellites are redder than centrals \citep[e.g.,][]{vdB_etal08}; accordingly, red galaxies cluster much stronger relative to blue \citep{zehavi_etal11}.
+For example, it is well known that satellites are redder than centrals of the same stellar mass \citep[e.g.,][]{vdB_etal08}; accordingly, red galaxies cluster much stronger relative to blue \citep{zehavi_etal11}.
 Pre-selecting galaxy samples by color will thus significantly weaken the dynamic range of $F_{\rm sat}$ within each color-selected subsample.
-This reduction in the role of satellites could be sufficient for the $\rhalf\propto\rvir\propto\mhalo$ of {\em central} galaxies to become the dominant effect, which would result in the mild, reversed trend seen in the top panels of Figure \ref{fig:colorclustering}.
-The same satellite-driven mechanism could be at work for the case of morphology pre-selection \citep[as in the morphology models developed in][]{skibba_etal08}, except that for disk-dominated systems, there would need to be a larger residual correlation with satellite designation relative to blue-selected samples \citep[which is, in fact, exactly the trend reported in][]{weinmann_etal08}.
+This reduction in the role of satellites could be sufficient for {\em central} galaxies to be responsible for the dominant effect.
+When the influence of centrals dominates the signal, models where $\rhalf\propto\rvir$ predict that $\rhalf-$dependent clustering should reverse sign, since $\rvir\propto\mhalo^{1/3},$ and halo bias $b(\mhalo)$ increases with halo mass.
+Models where $\rhalf\propto\rvir$ would also predict this reversed signal should have relatively small magnitude, since $\rvir$ scales only weakly with $\mhalo,$ and because $b(\mhalo)$ is weak function of mass for halos hosting galaxies $\mstar\lesssim10^{11}\msun.$ Therefore, if the segregation of galaxies into red- and blue-sequences is correlated sufficiently strongly with central vs.
+satellite designation, then the $\rhalf-$dependent clustering of color-selected samples shown in the top panels of Figure \ref{fig:colorclustering} are consistent with predictions of models where $\rhalf\propto\rvir.$
 
-While we consider such an explanation plausible, a conclusive determination of the principles underlying the clustering trends shown in Figure \ref{fig:colorclustering} requires proper forward modeling of morphology and color jointly with galaxy size.
+While we consider such an explanation plausible, a conclusive determination of the principles underlying the clustering trends shown in Figure \ref{fig:colorclustering} requires proper forward modeling of size and color jointly.
 Such an effort is beyond the scope, but well-motivated, by the present work.
@@
 These findings imply that bulge prominence is intimately connected with the quenching of star-formation, but that there is wide variation in star-formation histories amongst disk-dominated galaxies, in agreement with numerous previous findings \citep[see, e.g.,][]{woo_etal15,font_etal17}.
-
-Recent progress has substantially improved capabilities for the richness of the predictions of empirical galaxy--halo models \citep{becker15,cohn17,moster_etal17}.
-This new class of models has accomplished this by empirically modeling star-formation rate, and then integrating SFR along each halo's history to differentially build up stellar mass.
-In ongoing follow-up work, we are currently extending this new class of models to differentially build up the disk and bulge across cosmic time using computationally efficient empirical modeling methods.
-In addition to treating the multi-dimensional nature of the problem, this will allow us to use data at higher redshift in a self-consistent manner.
 
@@
 
-\section{Future Directions for Empirical Modeling of Galaxy Size and Morphology}
+\section{Future Directions for Empirical Modeling of Galaxy Size}
 \label{sec:future}
@@
 satellite size differences.
-While it remains to be seen whether this explanation ends up comprising the whole story, one thing is now clear: it is simply not possible to reliably analyze environmental trends of galaxy $\rhalf$ without properly accounting for satellites.
-Because of the large systematics that are common in contemporary group-finding methods \citep{campbell_etal15}, we consider forward modeling methods to be a requisite for meaningful continued progress on this topic.\footnote{We note that group-finders may play an important role in future analyses of galaxy size.
-However, it was shown in \citet{campbell_etal15} that treating observed groups as if they were correctly identified dark matter halos can lead to entirely unreliable conclusions.
-The robust method to extract information from galaxy group catalogs is instead to generate a Monte Carlo realization of a forward model, and then run the same group-finding algorithm on the mock as was run on the data, enabling a proper apples-to-apples comparison.}
+While it remains to be seen whether this explanation ends up comprising the whole story, one thing is now clear: it is not possible to reliably analyze environmental trends of galaxy $\rhalf$ without properly accounting for satellites.
+%Because of the large systematics that are common in contemporary group-finding methods \citep{campbell_etal15}, we consider forward modeling methods to be a requisite for continued progress on this topic.
 

### 2017-11-07 galsize_models/measurements/sdss_measurements.py

@@ -88,7 +88,15 @@ wp_sdss_mpajhu_sm11p25_large = np.load(os.path.join(output_dirname, 'sdss_mpajhu
 fracdiff_sm11p25_mpajhu = (wp_sdss_mpajhu_sm11p25_large-wp_sdss_mpajhu_sm11p25_small)/wp_sdss_mpajhu_sm11p25
 fracdiff_sm11p25_mpajhu_err = np.maximum(np.sqrt(wperr_sdss_mpajhu_sm11p25)/wp_sdss_mpajhu_sm11p25, cutoff_err)
 
+wp_sdss_mpajhu_blue_sm9p75_sm10p25_large = np.load(os.path.join(output_dirname, 'sdss_mpajhu_blue_sm9p75_sm10p25_large_wp.npy'))
+wp_sdss_mpajhu_blue_sm9p75_sm10p25_small = np.load(os.path.join(output_dirname, 'sdss_mpajhu_blue_sm9p75_sm10p25_small_wp.npy'))
+wp_sdss_mpajhu_blue_sm9p75_sm10p25 = np.load(os.path.join(output_dirname, 'sdss_mpajhu_blue_sm9p75_sm10p25_wp.npy'))
+wperr_sdss_mpajhu_blue_sm9p75_sm10p25 = np.load(os.path.join(output_dirname, 'sdss_mpajhu_blue_sm9p75_sm10p25_wperr.npy'))
 
+wp_sdss_mpajhu_red_sm9p75_sm10p25_large = np.load(os.path.join(output_dirname, 'sdss_mpajhu_red_sm9p75_sm10p25_large_wp.npy'))
+wp_sdss_mpajhu_red_sm9p75_sm10p25_small = np.load(os.path.join(output_dirname, 'sdss_mpajhu_red_sm9p75_sm10p25_small_wp.npy'))
+wp_sdss_mpajhu_red_sm9p75_sm10p25 = np.load(os.path.join(output_dirname, 'sdss_mpajhu_red_sm9p75_sm10p25_wp.npy'))
+wperr_sdss_mpajhu_red_sm9p75_sm10p25 = np.load(os.path.join(output_dirname, 'sdss_mpajhu_red_sm9p75_sm10p25_wperr.npy'))
 
 
 

### 2017-11-07 paper/galsize_paper.tex
Commented out now-obselete paragraph in broader implications section

@@
 
-The broad features of the $\wproj(\rproj)$ measurements shown in Figure \ref{fig:colorclustering} give insight into the characteristics that should be exhibited by any model for the relationship between $B/T$ and $\rhalf.$ First, the bottom right panel of Figure \ref{fig:colorclustering} indicates that the size of the bulge has only a tenuous connection to the properties of its parent dark matter halo.\footnote{Strictly speaking, the size of the bulge could in principle be closely connected to any number of dark matter halo properties, so long as those halo properties do not significantly impact two-point clustering.} Second, for disk-dominated galaxies, the observed $\rhalf-$dependent clustering suggests that at fixed $\mstar,$ the size of the disk is strongly correlated with whether or not the galaxy is a satellite.
+%The broad features of the $\wproj(\rproj)$ measurements shown in Figure \ref{fig:colorclustering} give insight into the characteristics that should be exhibited by any model for the relationship between $B/T$ and $\rhalf.$ First, the bottom right panel of Figure \ref{fig:colorclustering} indicates that the size of the bulge has only a tenuous connection to the properties of its parent dark matter halo.\footnote{Strictly speaking, the size of the bulge could in principle be closely connected to any number of dark matter halo properties, so long as those halo properties do not significantly impact two-point clustering.} Second, for disk-dominated galaxies, the observed $\rhalf-$dependent clustering suggests that at fixed $\mstar,$ the size of the disk is strongly correlated with whether or not the galaxy is a satellite.
 These findings imply that bulge prominence is intimately connected with the quenching of star-formation, but that there is wide variation in star-formation histories amongst disk-dominated galaxies, in agreement with numerous previous findings \citep[see, e.g.,][]{woo_etal15,font_etal17}.

### 2017-11-08 paper/galsize_paper.tex
edited intro, added some of the relevant references on size-Rvir connection and on early AM.

@@
 Galaxy size, typically quantified by a half-mass or half-light radius, $\rhalf,$ has well-measured scaling with galaxy mass $\mstar$ in the local Universe \citep{shen_etal03,guo_etal09,huang_etal13,lange_etal15,zhang_yang17}, and at higher redshift \citep{trujillo_etal04,vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,huang_etal17}.
+
 Observational constraints on models for galaxy $\rhalf$ typically come from one-point function measurements such as $\median{\rhalf}{\mstar}$ and $\sigma(\rhalf\vert\mstar),$ e.g.,  \citet{khochfar_silk06,desmond_etal17,bottrell_etal17b,hou_etal17,somerville_etal17}, or otherwise from catalogs of galaxy groups \citep{weinmann_etal08,huertas_company_etal13b,spindler_wake17}.
-Observations of two-point galaxy clustering, $\wproj(\rproj),$ have historically been used to place tight constraints on many features of the galaxy--halo connection, such as its $\mstar-$dependence \citep{moster_etal10,leauthaud_etal11,reddick_etal13,skibba_etal15}, dependence on luminosity \citep{tinker_etal05,cacciato_etal13}, broadband color \citep{coil_etal08,zehavi_etal11,guo_etal11,hearin_watson13}, and star-formation rate \citep{wang_etal07,tinker_etal13,watson_etal14}.
-In the present work, we exploit the constraining power of $\wproj(\rproj)$ to test empirical models connecting galaxy $\mstar$ and $\rhalf$ to the properties of the galaxy's parent dark matter halo.
+More recently, connection of galaxy sizes to virial radius of their parent halos have been
+explored by converting stellar mass to halo mass and virial radius, using abundance matching \citep{kravtsov_etal04,tasitsiomi_etal04,vale_ostriker04,vale_ostriker06,conroy_etal06}.
+Such analysis indicated that sizes of galaxies
+are, on average, proportional to the virial radii of their host halos, both at $z=0$ \citep{kravtsov13}, and higher redshifts \citep{huang_etal17,somerville_etal17}.
+
+Observations of two-point galaxy clustering, $\wproj(\rproj),$ have historically been used to place tight constraints on many features of the galaxy--halo connection, such as its $\mstar-$dependence \citep{moster_etal10,leauthaud_etal11,reddick_etal13,skibba_etal15}, dependence on luminosity \citep{kravtsov_etal04, tasitsiomi_etal04,vale_ostriker04,vale_ostriker06,tinker_etal05,cacciato_etal13}, broadband color \citep{coil_etal08,zehavi_etal11,guo_etal11,hearin_watson13}, and star-formation rate \citep{wang_etal07,tinker_etal13,watson_etal14}.
+In the present work, we exploit the constraining power of $\wproj(\rproj)$ to test empirical models connecting galaxy stellar masses and sizes to the properties of the galaxy's parent dark matter halo.
 

### 2017-11-08 paper/galsize_paper.tex
edited S 3 and 4

@@
 
+%----------------------------
 \section{Introduction}
 \label{sec:intro}
+%----------------------------
 
@@
 
+%---------------------------------------------------------------------------------------------------
+\begin{figure*}
+\centering
+\includegraphics[width=\textwidth]{FIGS/sdss_small_large_sample_definitions.pdf}
+\caption{
+{\bf Definition of ``small" and ``large" galaxies.} For a volume-limited SDSS galaxy sample defined by $M_{\ast}>10^{10.25}M_{\odot},$ we visually demonstrate how we classify galaxies into ``small" and ``large" subsamples.
+As described in detail in \S\ref{subsec:sizedef}, we compute the median value $\median{\rhalf}{\mstar}$ at the stellar mass of each galaxy in the sample, and divide the sample into two based on this $\mstar-$dependent cut.
+The {\em left panel} compares the stellar mass functions $\phi(\mstar)$ of the two samples, confirming that our method for separating ``small" from ``large" galaxies yields subsamples with statistically indistinguishable $\phi(\mstar)$.
+The {\em right panel} shows histograms of $\rhalf$ for the two subsamples, which partially overlap due to the finite range of $\mstar$ in the volume-limited sample.
+\textcolor{blue}{AK: x axis label in the left panel should be just $M_\star\ (M_\odot)$ without $\log_{10}$.
+I think this figure should be either displayed full text width like this, or made into two vertical panels and displayed in a single column.
+Otherwise it is too small.
+I wonder also whether the panel titles at the top are  needed.}
+}
+\label{fig:sizedefinition}
+\end{figure*}
+%-----------------------------------------------------------------------------------------------------
+
+%-----------------------------------------
 \section{Data and Simulations}
 \label{sec:data}
+%-----------------------------------------
 
 Using galaxies observed in the Sloan Digital Sky Survey (SDSS) with the stellar mass measurements taken from the MPA-JHU catalog \citep{kauffmann_etal03,brinchmann_etal04}, we define volume-limited samples of galaxies according to the same $\mstar-$completeness cuts used in \citet{behroozi_etal15} (see Figure 2).
-We supplement the MPA-JHU catalog with measurements of half-light radius, $\rhalf,$ derived from galaxy profile decompositions provided by \citet{meert_etal15}.
-The \citet{meert_etal15} catalog is based on Data Release 10 of SDSS \citep{ahn_etal14}, with improvements to the photometry pipeline and light profile fitting methods \citep{vikram_etal10,bernardi_etal13,bernardi_etal14,meert_etal13}.
+\textcolor{blue}{AK: which DR the catalog is taken from?} We supplement the MPA-JHU catalog with measurements of half-light radius, $\rhalf,$ derived from galaxy profile decompositions provided by \citet{meert_etal15}.
+The \citet{meert_etal15} catalog is based on Data Release 7 of SDSS \citep{abazajian_etal09}, with improvements to the photometry pipeline and light profile fitting method and, especially, in background subtraction \citep{vikram_etal10,bernardi_etal13,bernardi_etal14,meert_etal13}.
 In the version of this catalog that we use,\footnote{Our $\mstar$ and $\rhalf$ measurements are derived from different photometry pipelines; this is driven by our desire for consistency with the \citet{behroozi_etal15} completeness cuts used in our clustering measurements.
@@
 Using this technique, for any $\mstar-$threshold sample, the stellar mass function of the ``large" and ``small" subsamples are identical.
-We illustrate this for the particular case of $\mstar>10^{10.25}\msun$ in left panel of Figure~\ref{fig:sizedefinition}, which shows histograms of stellar mass for the two subsamples.
-The right panel of Figure~\ref{fig:sizedefinition} compares histograms of the two size distributions, which partially overlap due to the variation in $\median{\rhalf}{\mstar}$ across the $\mstar-$ range of the threshold sample.
+We illustrate this for the particular case of $\mstar>10^{10.25}\msun$ in left panel of Figure~\ref{fig:sizedefinition}, which shows stellar mass functions for the two subsamples.
+The right panel of Figure~\ref{fig:sizedefinition} compares histograms of the two size distributions of these subsamples, which partially overlap due to the variation in $\median{\rhalf}{\mstar}$ across the $\mstar-$ range of the threshold sample.
 
-%---------------------------------------------------------------------------------------------------
-\begin{figure}
-\centering
-\includegraphics[width=8cm]{FIGS/sdss_small_large_sample_definitions.pdf}
-\caption{
-{\bf Definition of ``small" and ``large" galaxies.} For a volume-limited SDSS galaxy sample defined by $M_{\ast}>10^{10.25}M_{\odot},$ we visually demonstrate how we classify galaxies into ``small" and ``large" subsamples.
-As described in detail in \S\ref{subsec:sizedef}, we compute the median value $\median{\rhalf}{\mstar}$ at the stellar mass of each galaxy in the sample, and divide the sample into two based on this $\mstar-$dependent cut.
-The {\em left panel} compares the stellar mass functions $\phi(\mstar)$ of the two samples, confirming that our method for separating ``small" from ``large" galaxies yields subsamples with statistically indistinguishable $\phi(\mstar)$.
-The {\em right panel} shows histograms of $\rhalf$ for the two subsamples, which partially overlap due to the finite range of $\mstar$ in the volume-limited sample.
-}
-\label{fig:sizedefinition}
-\end{figure}
-%-----------------------------------------------------------------------------------------------------
+In addition to stellar mass galaxy clustering depends on galaxy color \citep[e.g.,][]{zehavi_etal11}. Thus, we will also consider 
+dependence of clustering on galaxy size while controlling for color. The results for the subsamples split in stellar mass and color are presented in \S\ref{subsec:colormorph}.
 
@@
 
-In one class of models we explore, we suppose that stellar mass $\mstar$ is the statistical regulator of $\rhalf,$ so that galaxy sizes are drawn from a log-normal distribution with $0.2$ dex of scatter centered at $\median{\rhalf}{\mstar}.$ To implement this model, for simplicity we tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form \citep[see, e.g.,][]{zhang_yang17}.
+\textcolor{blue}{AK: I don't think the name of the model is descriptive here, but I could not yet come up with a better one.}
+In the first model we explore, we assume that stellar mass $\mstar$ controls $\rhalf,$ so that galaxy sizes are drawn from a log-normal distribution with $0.2$ dex of scatter centered at $\median{\rhalf}{\mstar}.$ To implement this model, for simplicity we tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form \citep[see, e.g.,][]{zhang_yang17}.
+Note that in this model the theoretical sample of model reproduces the observed $\rhalf-\mstar$ relation by construction.
 
@@
 
-Motivated by \citet{kravtsov13}, we additionally explore a model in which $\rhalf$ is linearly proportional to halo virial radius:\footnote{We note that the normalization factor in \citet{kravtsov13} is 0.0125, where as our normalization is 0.01.
-The difference derives from the choice of halo radius definition: \citet{bryan_norman98} in the present work, compared to the $200c$ definition used in \citet{kravtsov13}.}
+As noted in \S\ref{sec:intro}, \citet{kravtsov13} showed that galaxy sizes are on average proportional to the virial radius of their host halo.
+Motivated by these results, we  explore a model in which $\rhalf$ scales linearly with the halo virial radius:\footnote{We note that the normalization factor in \citet{kravtsov13} is 0.015, where as our normalization is 0.01.
+The difference derives from the choice of halo radius definition: \citet{bryan_norman98} in the present work, compared to the $200c$ definition used in \citet{kravtsov13} and the fact that the latter study used deprojected (larger) sizes for spheroidal galaxies.
+}
 \beq
@@
 \eeq
-For the virial radius of halos and subhalos, we use $\rmpeak:$ the value of $\rvir$ in physical units of $\kpc$ measured at the time of peak subhalo mass.
+For the virial radius of halos and subhalos, we use $\rmpeak:$ the value of $\rvir$ in physical units of $\kpc$ measured at the time when halo mass reached its maximum.
 The relationship between $\rmpeak$ and $\mpeak$ is given by
@@
 
+%-----------------------
 \section{Results}
 \label{sec:results}
+%-----------------------
 
+%--------------------------------------------------------
 \subsection{Size-Mass Scaling Relation}
 \label{subsec:one_point_function}
+%-------------------------------------------------------
 
-In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ The black curve enveloped by the gray bands shows the scaling relation for SDSS galaxies, while the blue curve shows the median relation  $\median{\rhalf}{\mstar}$ implied by the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}.
-This figure shows that models in which $\rhalf\propto\rvir$ can naturally give rise to the characteristic curvature in the $\rhalf-\mstar$ relation, confirming the results in \citet{kravtsov13} in a forward modeling context.
+In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ The black curve enveloped by the gray bands shows the scaling relation for SDSS galaxies, while the blue curve shows the median relation  $\median{\rhalf}{\mstar}$ predicted using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}.
+This figure shows that models in which $\rhalf\propto\rvir$ can naturally match the observed $\rhalf-\mstar$ relation, confirming the results of \citet{kravtsov13} in a forward modeling context.
 
+%---------------------------------------------------------------------------
 \subsection{Size-Dependent Clustering Measurements}
 \label{subsec:clustering_results}
+%---------------------------------------------------------------------------
 
-In Figure~\ref{fig:rvir_only_clustering_absolute}, we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj(\rproj).$ We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds, $\mstar>10^{9.75}\msun,$ $\mstar>10^{10.25}\msun,$ $\mstar>10^{10.75}\msun,$ and $\mstar>10^{11}\msun.$ For each threshold, we split the galaxies into ``large" and ``small" subsamples; as described in \S\ref{subsec:sizedef} and illustrated in Figure \ref{fig:sizedefinition}, our size-based selection is defined so that the subsamples have identical stellar mass functions.
-Red points with jackknife-estimated error bars show SDSS measurements of $\wproj(\rproj)$ for small galaxy samples, blue points show the same for large galaxies.
-Solid curves show $\wproj$ as predicted by the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}.
+In Figure~\ref{fig:rvir_only_clustering_absolute}, we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj(\rproj).$ We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds, $\mstar>10^{9.75}\msun,$ $\mstar>10^{10.25}\msun,$ $\mstar>10^{10.75}\msun,$ and $\mstar>10^{11}\msun.$ For each threshold, we split the galaxies into ``large" and ``small" subsamples, as described in \S\ref{subsec:sizedef}.
+As shown in Figure \ref{fig:sizedefinition}, our size-based samples  have similar stellar mass functions.
+Red points with jackknife-estimated error bars show SDSS measurements of $\wproj(\rproj)$ for samples of small galaxies, while blue points show the measured correlation functions for samples of large galaxies.
+Solid curves show $\wproj$ as predicted for these subsamples by the $\rvir-$based model of galaxy sizes described in \S\ref{subsubsec:rvirmodel}.
 
-The salient feature of these clustering measurements is that small galaxies cluster more strongly than large galaxies of the same stellar mass.
-This feature also holds true for galaxies predicted by the $\rvir-$based model.
-This result may be surprising, since $\rhalf\propto\rvir,$ halo mass $\rvir\propto\mhalo^{1/3},$ and clustering strength increases with $\mvir.$ Based on this simple argument, one would expect that large galaxies would be the more strongly clustered.
-We provide a resolution to this conundrum in \S\ref{subsec:censat_sizes}; before doing so, we first examine the clustering test of the $\rvir-$based model in more detail.
+The salient feature of these clustering measurements is that small galaxies cluster more strongly than large galaxies of the same stellar mass in all but the largest $\mstar$ samples.
+Remarkably, both the trend and the quantitative difference in the shape of the correlation functions of small and large galaxy samples are reproduced by the $\rvir-$based model.
+This may be surprising, since $\rhalf\propto\rvir,$ halo mass $\rvir\propto\mhalo^{1/3},$ and clustering strength of halos increases with $\mvir.$ Based on this simple argument, one would expect that large galaxies would be the more strongly clustered.
+We provide a resolution to this conundrum in \S\ref{subsec:censat_sizes}.
+However,  before doing so, we first examine the clustering test of the $\rvir-$based model in more detail.
 
@@
 The points and curves in Figure \ref{fig:clustering_ratio_upshot} are all negative: small galaxies cluster more strongly relative to large.
-This presentation of the measurement makes plain that the underlying signal of $\rhalf-$dependent clustering is strongest for samples with smaller stellar mass; as $\mstar$ increases, the signal weakens and nearly vanishes for $\mstar\gtrsim10^{11}\msun.$ Strikingly, the $\rvir-$based model exhibits this $\mstar-$dependent behavior, as well as the scale-dependence of the observed clustering signal at each $\mstar.$ As described in \S\ref{subsec:censat_sizes} below, we attribute the success of this prediction to the relative sizes of central vs.
-satellite galaxies.
+This presentation of the measurement makes it clear that the underlying signal of $\rhalf-$dependent clustering is strongest for samples with smaller stellar mass; as $\mstar$ increases, the signal weakens and nearly vanishes for $\mstar\gtrsim10^{11}\msun.$ Strikingly, the $\rvir-$based model reproduces this $\mstar-$dependent behavior, as well as the scale-dependence of the observed clustering signal at each $\mstar.$ As described in \S\ref{subsec:censat_sizes} below, we attribute the success of this prediction to the systematic difference of sizes of central and satellite galaxies.
 
+%--------------------------------------------------------------------------
 \subsection{Testing the Impact of Satellite Mass Loss}
 \label{subsec:mstar_stripping}
-%---------------------------------------------------------------------------------------------------
+%--------------------------------------------------------------------------------------
 \begin{figure*}
@@
 
-The green curves in Figure~\ref{fig:mstarmodelclustering} test the clustering predictions of the model described in \S\ref{subsubsec:strippingmodel} {\em before} applying the satellite mass loss prescription.
-Thus the green curves pertain to a model where $\rhalf$ follows a purely random log-normal distribution centered at $\median{\rhalf}{\mstar}.$ By construction, this model predicts no dependence at all of galaxy clustering upon $\rhalf$ at fixed $\mstar,$ simply because the scatter of $\rhalf$ about $\median{\rhalf}{\mstar}$ is uncorrelated with any other variable.
-The application of satellite mass loss introduces correlations in the scatter: after mass loss, satellites have smaller sizes than centrals of the same $\mstar$ due to post-infall stripping.
+Figure~\ref{fig:mstarmodelclustering} shows a similar comparison of the observed clustering ratios to the model
+in which size is controlled by $\mstar$ with sizes of satellites affected by stellar mass loss due to tides (\S\ref{subsubsec:strippingmodel}).
+Green solid lines show predictions of the model that does not account for stellar
+mass loss of satellites due to tides.
+In this model $\rhalf$ follows a purely random log-normal distribution centered at $\median{\rhalf}{\mstar}$ with the median relation matched to the observed relation by construction.
+This model thus predicts no dependence of galaxy clustering upon $\rhalf$ at fixed $\mstar,$ simply because the scatter of $\rhalf$ about $\median{\rhalf}{\mstar}$ is uncorrelated with any other variable.
+The figure shows that this model clearly is at odds with significant dependence of clustering on size exhibited by SDSS galaxies.
 
+Inclusion of satellite mass loss in the model introduces correlations in the scatter: after mass loss, satellites have smaller sizes than centrals of the same $\mstar$ due to post-infall stripping.
 The purple curves in Figure \ref{fig:mstarmodelclustering} show that satellite mass loss impacts $\rhalf-$dependent clustering in the expected manner.
 The ``small" galaxy population has a higher satellite fraction due to satellites being smaller than centrals of the same $\mstar,$ and so in this model small galaxies cluster more strongly relative to large.
-However, the magnitude of the effect is not strong enough to produce clustering predictions that are consistent with SDSS.
+However, the magnitude of the effect is not sufficiently strong  to produce clustering predictions that are consistent with observations.
 Evidently it is difficult to strip enough mass from satellites so that the $\rhalf-$dependent clustering predictions are in agreement with observations.
-As we argue in \S\ref{sec:interpretation}, this supports the conclusion that the relative difference between central and satellite size is at least partially in place at the time of satellite infall.
+As we argue in \S\ref{sec:interpretation}, this supports the conclusion that the relative difference between central and satellite size is largely in place at the time of satellite infall.
 
+%----------------------------------------------------
 \subsection{The Role of Galaxy Color}
 \label{subsec:colormorph}
+%----------------------------------------------------
 
-In this section we take a preliminary look at how galaxy clustering exhibits simultaneous dependence upon broadband color and size.
-Beginning from the $\mstar>10^{10.25}\msun$ sample used above, we first divide the sample into ``red" and ``blue" subsamples according to a $g-r=0.65$ cut, the rough location of the trough of the green valley for this stellar mass.
+We now examine how galaxy clustering depends on size when we control both for stellar mass and color dependence of galaxy clustering.
+Using the $\mstar>10^{10.25}\msun$ sample used above, we first divide the sample into ``red" and ``blue" subsamples using $g-r=0.65$ as a boundary, which approximately corresponds to the trough of the green valley for this stellar mass.
 For each color-selected subsample, we separately measure $\median{\rhalf}{\mstar; {\rm red}}$ and $\median{\rhalf}{\mstar; {\rm blue}},$ and use these median size values to split each subsample into two.
@@
 For each color-selected sample, large galaxies are slightly more strongly clustered relative to small galaxies.
-Comparing Figure \ref{fig:colorclustering} to the the upper right panel of Figure \ref{fig:rvir_only_clustering_absolute} shows the dramatic impact of galaxy color selection upon $\rhalf-$dependent clustering.
-For $\mstar-$complete samples, small galaxies cluster much stronger than large galaxies; for color-selected samples, the reverse is true, and the magnitude of the effect weakens considerably.
-We discuss a halo model interpretation of these trends in \S\ref{sec:interpretation}.
+Comparing Figure \ref{fig:colorclustering} to the the upper right panel of Figure \ref{fig:rvir_only_clustering_absolute} shows the size dependence for color-selected samples is dramatically weaker.
+For $\mstar-$complete samples, small galaxies cluster much stronger than large galaxies; for color-selected samples, the reverse is true, but the difference is much smaller and is confined to a limited range of scales.
+Although the two results may seem surprising, even contradictory, they can, in fact be
+explained within a unified simple model, as will be discussed in \S\ref{sec:interpretation}.
 

### 2017-11-08 paper/galsize_paper.tex
edited until S 5.2

@@
 Evidently it is difficult to strip enough mass from satellites so that the $\rhalf-$dependent clustering predictions are in agreement with observations.
+We reach the same conclusion when we tested an even more extreme $\mstar-$stripping model, in which stellar mass loss is linearly proportional to halo mass loss \citep[][Model 1]{watson_etal12}.
 As we argue in \S\ref{sec:interpretation}, this supports the conclusion that the relative difference between central and satellite size is largely in place at the time of satellite infall.
@@
 \centering
-\includegraphics[width=8cm]{FIGS/rvir_only_lensing_prediction.pdf}
-\caption{
-{\bf Prediction for $\rhalf-$dependence of galaxy lensing.}
-Using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}, we make predictions for as-yet-unseen measurements of the $\rhalf-$dependence of galaxy lensing of $\mstar-$complete samples, where ``small" and ``large" subsamples are defined as in \S\ref{subsec:sizedef}.
-As a generic consequence of satellites being smaller than centrals of the same mass, we predict that future lensing measurements of $\mstar-$complete samples will show $\Delta\Sigma$ of small galaxies to be significantly stronger relative to large galaxies of the same stellar mass.
-To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which the trend is reversed and weakened: for both blue and red samples, $\Delta\Sigma$ of large galaxies is (slightly) stronger relative to small galaxies.
-}
-\label{fig:lensingprediction}
-\end{figure}
-%-----------------------------------------------------------------------------------------------------
-%---------------------------------------------------------------------------------------------------
-\begin{figure}
-\centering
 \includegraphics[width=8cm]{FIGS/rvir_only_cen_sat_sizes.pdf}
@@
 
-%---------------------------------------------------------------------------------------------------
-\begin{figure}
-\centering
-\includegraphics[width=8cm]{FIGS/cen_sat_size_ratios.pdf}
-\caption{
-{\bf Scaling relation for hydro sims and SAMs.}
-As a function of subhalo mass $\mhalo=\mpeak,$ we show the ratio of mean satellite-to-central size predicted by the $\rvir-$based model.
-This scaling relation should be a useful guideline for more fine-grained physical models of galaxy size that wish to reproduce the observed $\rhalf-$dependence of galaxy clustering.
-}
-\label{fig:censatsizeratios}
-\end{figure}
-%-----------------------------------------------------------------------------------------------------
-
+%-----------------------------------------------------------------------------------------
 \section{A Unified Interpretation of $\rhalf-$Dependent Clustering}
 \label{sec:interpretation}
+%-----------------------------------------------------------------------------------------
 
-The clustering measurements shown in the previous section present (at least) two intriguing puzzles.
-First, the modeling assumption $\rhalf\propto\rvir$ predicts size-dependent galaxy clustering that is in quite good agreement with observations, particularly considering the simplicity of the model.
-Yet, small galaxies cluster more strongly relative to large, which seems at odds with naive expectations based on halo mass, since $\rvir\propto\mvir.$ Second, there appears to be a highly non-trivial dependence of $\rhalf-$dependent clustering upon whether or not the galaxy sample has been selected by color.
-We propose a simple and unified solution to both puzzles in \S\ref{subsec:censat_sizes}, and discuss the broader implications of our interpretation in \S\ref{subsec:broader_implications}.
+Comparison of observed size dependence of galaxy clustering and model predictions in the previous section produced  two intriguing results.
+First,  model that assumes $\rhalf\propto\rvir$ predicts dependence of both the amplitude and shape of  galaxy correlation functions on size remarkably well, especially considering that the model has only one free parameter, normalization of the linear $\rhalf-\rvir$ relation.
+At the same time, small galaxies cluster more strongly relative to large, which seems at odds with naive expectations that within such model larger sizes correspond to larger halo masses, $\rvir\propto\mvir^{1/3}$, which should be clustered more strongly.
+Second, the strong dependence of galaxy clustering on size weakens to almost no dependence for samples of red and blue galaxies selected by color within a given stellar mass range.
+Below we propose a simple and unified explanation of all these results within the $\rvir$-based size model in \S\ref{subsec:censat_sizes}, and discuss the broader implications of our interpretation in \S\ref{subsec:broader_implications}.
 
+%----------------------------------------------------------------------------
 \subsection{The Relative Size of Centrals vs. Satellites}
 \label{subsec:censat_sizes}
+%----------------------------------------------------------------------------
 
-A straightforward resolution to the first puzzle is shown in Figure \ref{fig:censatsizehist}, which compares the $\rhalf$ distributions of central, satellite, and splashback galaxies with the same halo mass $\mhalo\equiv\mpeak\approx10^{12}\msun.$ A ``splashback central"  is defined as a present-day central that used to be a satellite, i.e., its main progenitor halo passed inside the virial radius of a larger halo at some point in its past history.
+Recall that in the $\rvir$-based size model, galaxy size is proportional to the virial radius of host halo at the redshift at which halo had maximum mass.
+Thus, we can expect that in this model satellite galaxies will have sizes smaller than sizes of central galaxies hosted by halos of similar stellar mass.
+Indeed, Figure \ref{fig:censatsizehist} shows the $\rhalf$ distributions of central, satellite, and ``splashback'' central galaxies hosted by halos of the same mass $\mhalo\equiv\mpeak\approx10^{12}\msun.$ A ``splashback central"  is defined as a present-day central galaxy that used to be a satellite, i.e., its main progenitor halo passed inside the virial radius of a larger halo at some point in its past history.
 On the other hand, we define a ``true central" as a galaxy that has never been a satellite.
+The figure shows that there is a clear trend of sizes decreasing from the central to splashback and to satellite galaxies.
 
@@
 
-We can also understand the $\mstar-$dependence of Figure \ref{fig:clustering_ratio_upshot} in term of the relative sizes of centrals vs.
-satellites.
+We can also understand the observed trend of size dependence of clustering with $\mstar$ (Figure \ref{fig:clustering_ratio_upshot}) in terms of the differences of sizes of central and satellites galaxies.
 The satellite fraction $F_{\rm sat}(\mstar)$ decreases as $\mstar$ increases \citep[e.g.,][]{guo_etal11,reddick_etal13}.
 As $F_{\rm sat}$ decreases, there are fewer satellites available to preferentially weight the subsample of smaller galaxies.
-Thus models where $\rhalf-$dependent clustering is driven by satellite vs.
-central size naturally predict the observed $\mstar-$dependence of the signal, without introducing any explicitly $\mstar-$dependent ingredients in the size model.
+Thus,  high $\mstar$ samples consist mostly of central galaxies and the split by size no longer corresponds to the split into satellite- and central-dominated samples.
+The size dependence of clustering correspondingly weakens and nearly disappears for samples with largest $\mstar$.
 
-Upon first glance, the $\rhalf-$dependence of color-selected samples shown in Figure \ref{fig:colorclustering} appear to be driven by different principles, since the trends substantially weaken and change sign.
-However, even very simple models based entirely on central vs.
-satellite size differences can give rise to this behavior.
-For example, it is well known that satellites are redder than centrals of the same stellar mass \citep[e.g.,][]{vdB_etal08}; accordingly, red galaxies cluster much stronger relative to blue \citep{zehavi_etal11}.
-Pre-selecting galaxy samples by color will thus significantly weaken the dynamic range of $F_{\rm sat}$ within each color-selected subsample.
-This reduction in the role of satellites could be sufficient for {\em central} galaxies to be responsible for the dominant effect.
-When the influence of centrals dominates the signal, models where $\rhalf\propto\rvir$ predict that $\rhalf-$dependent clustering should reverse sign, since $\rvir\propto\mhalo^{1/3},$ and halo bias $b(\mhalo)$ increases with halo mass.
-Models where $\rhalf\propto\rvir$ would also predict this reversed signal should have relatively small magnitude, since $\rvir$ scales only weakly with $\mhalo,$ and because $b(\mhalo)$ is weak function of mass for halos hosting galaxies $\mstar\lesssim10^{11}\msun.$ Therefore, if the segregation of galaxies into red- and blue-sequences is correlated sufficiently strongly with central vs.
-satellite designation, then the $\rhalf-$dependent clustering of color-selected samples shown in the top panels of Figure \ref{fig:colorclustering} are consistent with predictions of models where $\rhalf\propto\rvir.$
+Likewise, the the significantly weaker dependence of clustering on size for color-selected samples (Figure \ref{fig:colorclustering}) and its reversed sign can be naturally explained within the same framework.
+For example, it is well known that satellites are redder than centrals of the same stellar mass \citep[e.g.,][]{vdB_etal08}; accordingly, red galaxies cluster much strongly than  blue galaxies \citep[e.g.,][]{zehavi_etal11}.
+Samples of red (blue) galaxies with stellar masses of $\mstar\sim 10^{10}\ M_\odot$ are dominated by satellite (central) galaxies and split in size within such samples no longer corresponds to the split into satellite- and central-dominated samples.
+In this case, $\rvir$-based size model, which reproduces the observed trend, predicts that split by size does correspond to the split by halo mass $\rhalf\propto\rvir\mhalo^{1/3}$ and that that large galaxies should be somewhat more clustered than the small ones.
+That is they predict that size dependence of clustering  is reversed for color-selected samples and the magnitude of the dependence is significantly weaker due to weak dependence of virial radius on halo mass and weak dependence of clustering on halo mass in this regime.
 
-While we consider such an explanation plausible, a conclusive determination of the principles underlying the clustering trends shown in Figure \ref{fig:colorclustering} requires proper forward modeling of size and color jointly.
-Such an effort is beyond the scope, but well-motivated, by the present work.
-See Section \ref{subsec:broader_implications} for further discussion.
+While we consider such an explanation plausible and likely, a conclusive confirmation requires proper forward modeling of size and color jointly.
+Such an effort is beyond the scope of, but is well-motivated by the present work.
 
@@
 The clustering ratios in Figure \ref{fig:mstarmodelclustering} show that the impact of physically motivated levels of satellite mass loss likely cannot explain the $\rhalf-$dependent clustering seen in SDSS.
-As an additional test, we reach the same conclusion when implementing an even more extreme $\mstar-$stripping model in which stellar mass loss is linearly proportional to halo mass loss \citep[][Model 1]{watson_etal12}.
 The success of the $\rvir-$based model, together with the failure of the satellite mass loss model, suggests that the relative size of central and satellite galaxies is largely driven by the {\rm pre-infall} evolution of the satellite.
@@
 Our findings support the idea that the small sizes of satellites arise primarily from the satellite's distinctive evolution within a high density region and a steep tidal field {\em prior} to becoming a present-day satellite.
+
+%---------------------------------------------------------------------------------------------------
+\begin{figure}
+\centering
+\includegraphics[width=8cm]{FIGS/rvir_only_lensing_prediction.pdf}
+\caption{
+{\bf Prediction for $\rhalf-$dependence of galaxy lensing.}
+Using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}, we make predictions for as-yet-unseen measurements of the $\rhalf-$dependence of galaxy lensing of $\mstar-$complete samples, where ``small" and ``large" subsamples are defined as in \S\ref{subsec:sizedef}.
+As a generic consequence of satellites being smaller than centrals of the same mass, we predict that future lensing measurements of $\mstar-$complete samples will show $\Delta\Sigma$ of small galaxies to be significantly stronger relative to large galaxies of the same stellar mass.
+To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which the trend is reversed and weakened: for both blue and red samples, $\Delta\Sigma$ of large galaxies is (slightly) stronger relative to small galaxies.
+}
+\label{fig:lensingprediction}
+\end{figure}
+%-----------------------------------------------------------------------------------------------------
 
@@
 An explicit demonstration of this point appears in the Appendix, which repeats the analyses in the main body of the text, but for a subhalo catalog with no orphan correction.
+
+%---------------------------------------------------------------------------------------------------
+\begin{figure}
+\centering
+\includegraphics[width=8cm]{FIGS/cen_sat_size_ratios.pdf}
+\caption{
+{\bf Scaling relation for hydro sims and SAMs.}
+As a function of subhalo mass $\mhalo=\mpeak,$ we show the ratio of mean satellite-to-central size predicted by the $\rvir-$based model.
+This scaling relation should be a useful guideline for more fine-grained physical models of galaxy size that wish to reproduce the observed $\rhalf-$dependence of galaxy clustering.
+}
+\label{fig:censatsizeratios}
+\end{figure}
+%-----------------------------------------------------------------------------------------------------
 

### 2017-11-08 paper/galsize_paper.tex
Updated figures and simplified orphan treatment

@@
 Black points with error bars show SDSS measurements; solid black curves show the abundance matching prediction of our fiducial model, which includes the effect of orphan subhalos (see Appendix A).
-Including orphans mitigates the discrepancy in the clustering predicted by traditional, $\mpeak-$based SHAM based, though mild tension remains for $\mstar\gtrsim10^{10.75}\msun.$
+Including orphans mitigates the discrepancy in the clustering predicted by traditional, $\mpeak-$based SHAM based, though mild tension remains on small scales for $\mstar\gtrsim10^{10.75}\msun,$ and on all scales for the $\mstar\gtrsim10^{9.75}\msun.$
 }
@@
 Solid curves show the clustering predictions of the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}.
-The $\rvir-$based model inherits the shortcoming of ordinary abundance matching at $\mstar\gtrsim10^{10.75}\msun,$ although the model faithfully captures the {\em relative} clustering of small vs.
+The $\rvir-$based model inherits the shortcoming of ordinary abundance matching shown in Figure \ref{fig:baseline_sham_clustering}, although the model faithfully captures the {\em relative} clustering of small vs.
 large galaxies, as shown in Figure \ref{fig:clustering_ratio_upshot}.
@@
 Solid curves show the clustering ratio predictions of the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}.
-Normalizing the measurements and predictions by $w_{\rm p}^{\rm all}$ scales away the shortcoming of ordinary abundance matching at high stellar mass (see Figure \ref{fig:baseline_sham_clustering}), highlighting the successful prediction of the $\rvir-$based model for the $\rhalf-$dependence of galaxy clustering.
+Normalizing the measurements and predictions by $w_{\rm p}^{\rm all}$ scales away the shortcoming of ordinary abundance matching (see Figure \ref{fig:baseline_sham_clustering}), highlighting the successful prediction of the $\rvir-$based model for the $\rhalf-$dependence of galaxy clustering.
 }
@@
 
+In this appendix, we show two different a priori reasonable choices for the orphan selection function.
 Since a rigorous calibration of $\mathcal{F}_{\rm orphan}$ is beyond the scope of the present work, we instead opt for a simple parameterization that yields reasonably accurate recovery of the galaxy clustering signal observed in SDSS.
+
+In both treatments studied here, we first throw out orphan subhalos with $V_{\rm max}/V_{\rm peak}<0.1,$ so that the most drastically disrupted subhalos remain unused.
+For our fiducial model used throughout the main body of the text, $\mathcal{F}_{\rm orphan}$ is defined by simply randomly select half of the orphan subhalos.
+For the alternative orphan selection function labeled as $M_{\rm host}-$dependent orphans in this appendix, we proceed as follows.
 We model $\mathcal{F}_{\rm orphan}=\mathcal{F}_{\rm orphan}(M_{\rm peak},M_{\rm host}),$ where $\mpeak$ is the peak mass of the disrupted subhalo, and $\mhost$ is the present-day virial mass of its $z=0$ host halo.
-For the $\mpeak-$dependence, we select $50\%$ of disrupted subhalos with $\mpeak=10^{11}\msun,$ $0\%$ of subhalos with $\mpeak=10^{13}\msun,$ linearly interpolating in $\log\mpeak$ for intermediate values of $\mpeak.$ At each $\mpeak,$ the selection of disrupted halos is not random; instead, we preferentially select the subhalos with larger $\mhost,$ which we intend to offset the increased difficulty of subhalo-finding algorithms to identify subhalos with especially small values of  $\mu\equiv\mpeak/\mhost.$ We refer to this model as our ``fiducial orphan model".
-We assess the role of the nontrivial features in $\mathcal{F}_{\rm orphan}$ by randomly selecting the same number of orphan subhalos, referring to this alternate model as the ``random orphan model".
+For the $\mpeak-$dependence, we select $50\%$ of disrupted subhalos with $\mpeak=10^{11}\msun,$ $0\%$ of subhalos with $\mpeak=10^{13}\msun,$ linearly interpolating in $\log\mpeak$ for intermediate values of $\mpeak.$ At each $\mpeak,$ the selection of disrupted halos is not random; instead, we preferentially select the subhalos with larger $\mhost,$ which we intend to offset the increased difficulty of subhalo-finding algorithms to identify subhalos with especially small values of  $\mu\equiv\mpeak/\mhost.$
 
@@
 Comparing the black to the red curves shows that including orphans substantially boosts small-scale clustering due to the increased satellite fraction.
-Comparing the orange to the black curves, we see that randomly selecting orphans results in excessive small-scale clustering for the higher-mass threshold samples due to the inclusion of too many disrupted subhalos with large values of $\mpeak.$
+Comparing the orange to the black curves, we see that random orphan selection, vs.
+the $M_{\rm host}-$dependent selection, results in similar clustering, with slight differences on the smallest scales at the highest masses.
+Because we have not been systematic in the calibration of $\mathcal{F}_{\rm orphan},$ we adopt the simpler, random orphan selection as the fiducial model shown in the main body of the text.
 
@@
 \caption{
-{\bf Impact of the orphan selection function.} The {\em top panel} is identical to Figure \ref{fig:baseline_sham_clustering}, but includes additional curves for the case of randomly selected orphan halos (orange curves), and no orphans at all (red curves).
+{\bf Impact of the orphan selection function.} The {\em top panel} is identical to Figure \ref{fig:baseline_sham_clustering}, but includes additional curves for the case of $M_{\rm host}-$dependent orphan selection (orange curves), and no orphans at all (red curves).
 As a function of stellar mass, the {\em bottom panel} shows the satellite fraction, i.e., the fraction of objects that are not central galaxies.

### 2017-11-08 paper/galsize_paper.tex
Minor grammatical touchups

@@
 The {\em right panel} shows histograms of $\rhalf$ for the two subsamples, which partially overlap due to the finite range of $\mstar$ in the volume-limited sample.
-\textcolor{blue}{AK: x axis label in the left panel should be just $M_\star\ (M_\odot)$ without $\log_{10}$.
-I think this figure should be either displayed full text width like this, or made into two vertical panels and displayed in a single column.
-Otherwise it is too small.
-I wonder also whether the panel titles at the top are  needed.}
 }
@@
 As the bedrock of our modeling, we use the publicly available\footnote{\url{http://www.slac.stanford.edu/~behroozi/BPlanck\_Hlists}} catalog of {\tt Rockstar} subhalos identified at $z=0$ in the Bolshoi-Planck simulation \citep{klypin_etal11,behroozi12_rockstar,behroozi12_consistent_trees,riebe_etal13,rodriguez_puebla16_bolplanck}.
-As described in \S\ref{subsec:sham}, we will use traditional abundance matching to connect stellar mass $\mstar$ with subhalo peak mass $\mpeak.$ To address issues related to subhalo incompleteness \citep{guo_white13,campbell_etal17}, we supplement the Bolshoi-Planck subhalo catalog with {\em all} subhalos that were ever identified by {\tt Rockstar}, including those that no longer appear in the standard catalog as subhalos that survive to $z=0.$ We describe our treatment of these ``orphan" subhalos in the Appendix.
+As described in \S\ref{subsec:sham}, we will use traditional abundance matching to connect stellar mass $\mstar$ with subhalo peak mass $\mpeak.$ To address issues related to subhalo incompleteness \citep{guo_white13,campbell_etal17}, we supplement the Bolshoi-Planck subhalo catalog with subhalos that have been disrupted and no longer appear in the standard catalog as $z=0$ surviving subhalos.
+We describe our treatment of these ``orphan" subhalos in the Appendix.
 
@@
 
-In addition to stellar mass galaxy clustering depends on galaxy color \citep[e.g.,][]{zehavi_etal11}. Thus, we will also consider 
+In addition to stellar mass, $\wproj(\rproj)$ depends on galaxy color \citep[e.g.,][]{zehavi_etal11}. Thus, we will also consider 
 dependence of clustering on galaxy size while controlling for color. The results for the subsamples split in stellar mass and color are presented in \S\ref{subsec:colormorph}.
@@
 In the first model we explore, we assume that stellar mass $\mstar$ controls $\rhalf,$ so that galaxy sizes are drawn from a log-normal distribution with $0.2$ dex of scatter centered at $\median{\rhalf}{\mstar}.$ To implement this model, for simplicity we tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form \citep[see, e.g.,][]{zhang_yang17}.
-Note that in this model the theoretical sample of model reproduces the observed $\rhalf-\mstar$ relation by construction.
+Note that this model reproduces the observed $\rhalf-\mstar$ relation by construction.
 
@@
 Motivated by these results, we  explore a model in which $\rhalf$ scales linearly with the halo virial radius:\footnote{We note that the normalization factor in \citet{kravtsov13} is 0.015, where as our normalization is 0.01.
-The difference derives from the choice of halo radius definition: \citet{bryan_norman98} in the present work, compared to the $200c$ definition used in \citet{kravtsov13} and the fact that the latter study used deprojected (larger) sizes for spheroidal galaxies.
-}
+The difference derives from two factors: {\em i.} the choice of halo radius definition: \citet{bryan_norman98} in the present work, compared to the $200c$ definition used in \citet{kravtsov13}; {\em ii.} the latter study used deprojected (larger) sizes for spheroidal galaxies, whereas we make no such correction here.}
 \beq
@@
 
-Comparison of observed size dependence of galaxy clustering and model predictions in the previous section produced  two intriguing results.
-First,  model that assumes $\rhalf\propto\rvir$ predicts dependence of both the amplitude and shape of  galaxy correlation functions on size remarkably well, especially considering that the model has only one free parameter, normalization of the linear $\rhalf-\rvir$ relation.
-At the same time, small galaxies cluster more strongly relative to large, which seems at odds with naive expectations that within such model larger sizes correspond to larger halo masses, $\rvir\propto\mvir^{1/3}$, which should be clustered more strongly.
+In the previous section, comparing model predictions to the observed size dependence of galaxy clustering produced two intriguing results.
+First, the model that assumes $\rhalf\propto\rvir$ predicts a dependence of both the amplitude and shape of  galaxy correlation functions on size remarkably well, especially considering that the model nominally has only one free parameter: the normalization of the linear $\rhalf-\rvir$ relation.
+At the same time, small galaxies cluster more strongly relative to large, which seems at odds with naive expectations that, within such a model, larger sizes correspond to larger halo masses, $\rvir\propto\mvir^{1/3}$, and so larger sizes should be clustered more strongly.
 Second, the strong dependence of galaxy clustering on size weakens to almost no dependence for samples of red and blue galaxies selected by color within a given stellar mass range.
@@
 
-Recall that in the $\rvir$-based size model, galaxy size is proportional to the virial radius of host halo at the redshift at which halo had maximum mass.
+Recall that in the $\rvir$-based size model, galaxy size is proportional to the virial radius of host halo at the redshift at the time the halo attained its maximum mass.
 Thus, we can expect that in this model satellite galaxies will have sizes smaller than sizes of central galaxies hosted by halos of similar stellar mass.
@@
 
-We can also understand the observed trend of size dependence of clustering with $\mstar$ (Figure \ref{fig:clustering_ratio_upshot}) in terms of the differences of sizes of central and satellites galaxies.
+We can also understand how the observed $\rhalf-$dependent clustering scales with $\mstar$ (shown by comparing different panels in Figure \ref{fig:clustering_ratio_upshot}) in terms of the differences of sizes of central and satellites galaxies.
 The satellite fraction $F_{\rm sat}(\mstar)$ decreases as $\mstar$ increases \citep[e.g.,][]{guo_etal11,reddick_etal13}.
 As $F_{\rm sat}$ decreases, there are fewer satellites available to preferentially weight the subsample of smaller galaxies.
-Thus,  high $\mstar$ samples consist mostly of central galaxies and the split by size no longer corresponds to the split into satellite- and central-dominated samples.
+Thus,  high $\mstar$ samples consist mostly of central galaxies, and the split by size no longer corresponds to the split into satellite- and central-dominated samples.
 The size dependence of clustering correspondingly weakens and nearly disappears for samples with largest $\mstar$.
 
-Likewise, the the significantly weaker dependence of clustering on size for color-selected samples (Figure \ref{fig:colorclustering}) and its reversed sign can be naturally explained within the same framework.
-For example, it is well known that satellites are redder than centrals of the same stellar mass \citep[e.g.,][]{vdB_etal08}; accordingly, red galaxies cluster much strongly than  blue galaxies \citep[e.g.,][]{zehavi_etal11}.
-Samples of red (blue) galaxies with stellar masses of $\mstar\sim 10^{10}\ M_\odot$ are dominated by satellite (central) galaxies and split in size within such samples no longer corresponds to the split into satellite- and central-dominated samples.
-In this case, $\rvir$-based size model, which reproduces the observed trend, predicts that split by size does correspond to the split by halo mass $\rhalf\propto\rvir\mhalo^{1/3}$ and that that large galaxies should be somewhat more clustered than the small ones.
-That is they predict that size dependence of clustering  is reversed for color-selected samples and the magnitude of the dependence is significantly weaker due to weak dependence of virial radius on halo mass and weak dependence of clustering on halo mass in this regime.
+Likewise, the significantly weaker dependence of clustering on size for color-selected samples (Figure \ref{fig:colorclustering}), and its reversed sign, can be naturally explained within the same framework.
+For example, it is well known that satellites are redder than centrals of the same stellar mass \citep[e.g.,][]{vdB_etal08}; accordingly, red galaxies cluster much more strongly than  blue galaxies \citep[e.g.,][]{zehavi_etal11}.
+Samples of red (blue) galaxies with stellar masses of $\mstar\sim 10^{10}\ M_\odot$ are dominated by satellite (central) galaxies, and splitting by size within such samples no longer corresponds to the split into satellite- and central-dominated samples.
+In this case, the $\rvir$-based size model predicts that splitting by size {\em does} correspond to splitting by halo mass $\rhalf\propto\rvir\propto\mhalo^{1/3},$ and therefore that large galaxies should be somewhat more clustered than the small ones.
+That is, the $\rvir-$based model predicts that $\rhalf-$dependent clustering should be reversed for color-selected samples, and that the magnitude of the dependence should be significantly weaker due to weak dependence of virial radius on halo mass, and weak dependence of clustering on halo mass in this regime.
 
-While we consider such an explanation plausible and likely, a conclusive confirmation requires proper forward modeling of size and color jointly.
-Such an effort is beyond the scope of, but is well-motivated by the present work.
+While we consider such an explanation plausible, and even likely, a conclusive confirmation requires proper forward modeling of size and color jointly.
+Such an effort is well-motivated, but beyond the scope of the present work.
 

### 2017-11-09 paper/galsize_paper.tex
edited S 5, including 5.2

@@
 
-Recall that in the $\rvir$-based size model, galaxy size is proportional to the virial radius of host halo at the redshift at the time the halo attained its maximum mass.
+Recall that in the $\rvir$-based size model, galaxy size is proportional to the virial radius of host halo at the redshift  when the halo halo attained its maximum mass.
 Thus, we can expect that in this model satellite galaxies will have sizes smaller than sizes of central galaxies hosted by halos of similar stellar mass.
@@
 While we consider such an explanation plausible, and even likely, a conclusive confirmation requires proper forward modeling of size and color jointly.
-Such an effort is well-motivated, but beyond the scope of the present work.
+Such an effort is strongly motivated by our results, but is beyond the scope of the present work.
 
+%-------------------------------------------------
 \subsection{Broader Implications}
 \label{subsec:broader_implications}
+%-------------------------------------------------
 
-Physical explanations for differences between the sizes of centrals and satellites fall into two categories, depending on whether or not the processes involved are post-infall and satellite-specific.
-In the satellite mass loss model, satellites evolve exactly as centrals prior to the time of infall; this model assumes that {\em all} satellite size truncation occurs after the time of infall.
-The $\rvir-$based model assumes the opposite: namely that the size of {\em all} galaxies is statistically set by the $\rmpeak,$ the physical size of the virial radius at the time at which $\mhalo$ stops growing.
-This assumption is the natural extension of the abundance matching approximation that stellar mass largely stops growing at this time (including in-situ and ex-situ growth).
-The halos of typical satellites reach $\mpeak$ far outside the virial radius of their ultimate host halo \citep{behroozi_etal14}, and so in the $\rvir-$based model the size differences between satellites and centrals is largely in place prior to the time of satellite infall.
+The success of the $\rvir$-based model in explaining the size dependence of galaxy clustering implies that sizes of {\it all} galaxies,  red, blue, spheroid, disks, satellites and central, are, on average, proportional to the $\rmpeak,$ the physical size of the virial radius at the time at which $\mhalo$ stops growing.
+Although correlation is not necessarily causation, such universal and simple dependence poses a useful challenge to galaxy formation models, as it indicates tight connection betw
+een growth of galaxies and their host halos.
 
-The clustering ratios in Figure \ref{fig:mstarmodelclustering} show that the impact of physically motivated levels of satellite mass loss likely cannot explain the $\rhalf-$dependent clustering seen in SDSS.
-The success of the $\rvir-$based model, together with the failure of the satellite mass loss model, suggests that the relative size of central and satellite galaxies is largely driven by the {\rm pre-infall} evolution of the satellite.
+The $\rvir$-based size model also assumes that after halo stops growing the size remains approximately constant and this assumption is consistent with observed size dependence of galaxy clustering in SDSS.
+The halos of typical satellites reach $\mpeak$ far outside the virial radius of their ultimate host halo \citep{behroozi_etal14}, and so in the $\rvir-$based model the size difference between satellites and centrals is largely in place prior to the time of satellite infall.
+Thus, as noted above, halos of central and satellite galaxies of the same $\mstar$  differ in epochs when their halo stopped growing (i.e., $\zpeak$) and this difference explains their different median sizes.
+
+The difference also explains the relative trends of $\rhalf-\mstar$ relations for red and blue, or disk and spheroid galaxies.
+Both types of galaxies exhibit weak dependence of $\rhalf$ on $\mstar$ at $\mstar\lesssim 5\times 10^{10}\ M_\odot$ and 
+at these masses $\rhalf$ of disks is a factor of two larger than those of spheroids.
+At larger masses, the sizes of galaxies of both types show stronger dependence on $\mstar$ and the difference in median size of disk and spheroid galaxies decreases \citep[e.g.,][]{bernardi_etal14}.
+
+In the $\rvir$-based size model, the weak dependence of $\rhalf$ on $\mstar$ for low mass galaxies is due to steep $\mstar-\mvir$ relation.
+For example, if $\mstar\propto\mvir^\alpha\propto\rvir^{3\alpha}$, then $\rhalf\propto \rvir\propto \mstar^{1/(3\alpha)}$.
+Given that $\alpha\sim 1-3$ is inferred for the $\mstar-\mvir$ relation at low masses \citep{kravtsov10,behroozi13_smhm,kravtsov_etal14}, the $\rhalf-\mstar$ relation in this regime is expected to be shallow.
+For galaxies of $\mstar\gtrsim 5\times 10^{10}\ M_\odot$, $\alpha\approx 0.3$ \citep[e.g.,][]{kravtsov_etal14} and thus 
+the slope of the $\rhalf-\mstar$ relation is approximately linear.
+These trends of $\rhalf$ with $\mstar$ have a direct relation to the trends of surface brightness $\mu_\star=\mstar/(\pi\rhalf^2)$ with stellar mass.
+
+The difference in median sizes of disk and spheroidal galaxies at $\mstar\lesssim 10^{11}\ M_\odot$ is explained by the fact that sizes of satellite galaxies are systematically smaller than sizes of central galaxies of the same $\mstar$ and
+the satellite fraction is much higher among spheroidal galaxies compared to the disk galaxies.
+For example, analyses of \citet{rodriguez_puebla_etal15} show that in this regime satellite fraction of blue galaxies is only $\approx 10-20\%$, while
+the satellite fraction of red galaxies is $\gtrsim 30-50\%$ increasing with decreasing stellar mass. 
+As $\mstar$ increases, satellite fractions of both blue and red galaxies drop and at $\mstar\gtrsim 10^{11}\ M_\odot$ vast majority of blue and red galaxies are centrals.
+If these galaxies occupy similar halo masses at the same $\mstar$, $\rvir$-based size model predicts that  the difference in sizes of red and blue galaxies should disappear at these masses, as is indeed observed.
+
+A testable prediction of this picture is that when 3D (de-projected) sizes of only central red and blue galaxies of the same $\mstar$ are compared they should be much closer, than the sizes of the overall red and blue populations.
 
@@
 Meanwhile, \citet{weinmann_etal08} additionally find that for late-type galaxies, there is a strong correlation between disk size and central/satellite designation.
-Qualitatively, our clustering measurements shown in Figure \ref{fig:colorclustering} are in good agreement with these findings: once galaxies have been morphology-selected, only the clustering of disk shows significant dependence upon $\rhalf.$ Our clustering results are also consistent with the disk model presented in \citet{dutton_etal08,dutton_etal10}, which predicts that at fixed stellar mass, there is weak, positive correlation between disk size and halo mass.
+Qualitatively, our clustering measurements shown in Figure \ref{fig:colorclustering} are in good agreement with these findings: once galaxies have been color-selected, only the clustering of blue galaxies shows significant dependence upon $\rhalf.$ Our clustering results are also consistent with the disk model presented in \citet{dutton_etal08,dutton_etal10}, which predicts that at fixed stellar mass, there is weak, positive correlation between disk size and halo mass.
 

### 2017-11-09 paper/galsize_paper.tex
edited S 6 and 7

@@
 To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which the trend is reversed and weakened: for both blue and red samples, $\Delta\Sigma$ of large galaxies is (slightly) stronger relative to small galaxies.
+\textcolor{blue}{AK: is it worth showing a second panel with $\Delta\Sigma$ for color-selected samples to back up the last sentence?}
 }
@@
 
+\textcolor{blue}{AK: when I was reading this paragraph, I had trouble digesting its meaning... Also it definitely broke the flow of the narrative for me.}
 As discussed in \citet{spindler_wake17}, it is entirely possible that size differences between centrals and satellites of the same mass can be accounted for by mutual covariance with an additional variable such as star formation rate or morphological type \citep[see also][for an explicit demonstration of this scenario]{lilly_carollo16}.
@@
 
+%-----------------------------------------------------------------------------------------
 \section{Future Directions for Empirical Modeling of Galaxy Size}
 \label{sec:future}
+%-----------------------------------------------------------------------------------------
 
@@
 The scope of this work is to serve as a pilot study in which we identify the chief ingredients that can influence the $\rhalf-$dependence of galaxy clustering.
-While our results suggest that satellite evolution {\em prior} to infall drives the correct relative size of centrals vs.
-satellites, our implementation cannot be correct in quantitative detail: the clustering ratios of this model shown in Figure \ref{fig:clustering_ratio_upshot} only roughly agree with SDSS.
+While our results suggest that sizes of galaxies are linearly correlated with the
+virial radius of halos at the moment the halo mass reached its peak and that sizes of satellite galaxies were set {\em prior} to infall, our model is probably does not capture galaxy properties and their trends in full quantitative detail.
+For example, the clustering ratios of this model shown in Figure \ref{fig:clustering_ratio_upshot} do capture the overall trends, but also don't match the observed statistics fully. 
  For present purposes, we have chosen to focus on exploring bracketing cases of qualitative ingredients, rather than fine-tuning the model.
@@
 Traditional galaxy clustering is already being used to validate and/or fit models of the stellar-to-halo-mass relation \citep[e.g.,][]{leauthaud_etal11,moster_etal13,behroozi13_smhm,lehmann_etal15}.
-Based on our results, we advocate that empirical models for $\mean{\mstar}{\mhalo}$ be supplemented with additional model ingredients for $\median{\rhalf}{\mstar},$ and that the parameters of the composite model be {\em jointly} constrained by measurements of the stellar mass function, $\mstar-$dependent clustering, and $\rhalf-$dependent clustering.
+Based on our results, we advocate that empirical models for $\mean{\mstar}{\mhalo}$ be supplemented with additional model ingredients for $\median{\rhalf}{\mstar},$ (\textcolor{blue}{AK:} did you mean $\langle\rhalf|\mhalo\rangle$ here?
+Seems more logical in the context of this sentence) and that the parameters of the composite model be {\em jointly} constrained by measurements of the stellar mass function, $\mstar-$dependent clustering, and $\rhalf-$dependent clustering.
 
@@
 satellite size differences.
+The latter reflects not evolution of galaxies inside host halos, but is due to the fact that satellites have reached their peak mass at higher redshifts than the centrals.
 While it remains to be seen whether this explanation ends up comprising the whole story, one thing is now clear: it is not possible to reliably analyze environmental trends of galaxy $\rhalf$ without properly accounting for satellites.
@@
 The magnitude, scale-dependence, and $\mstar-$dependence of $\rhalf-$dependent clustering provides strong evidence that satellite galaxies are smaller than central galaxies of the same halo mass.
-\item A simple empirical model in which $\rhalf$ is set by halo $\rvir$ at the time of peak halo mass exhibits a clustering signal that is strikingly similar to that seen in SDSS.
+\item A simple empirical model in which $\rhalf$ is set by halo $\rvir$ at the time of peak halo mass exhibits a clustering signal that is strikingly similar to that r seen in SDSS.
 \item Models in which $\rhalf$ is regulated by $\mstar,$ rather than $\mhalo,$ are grossly discrepant with the observed clustering signal, even when accounting for satellite mass stripping.
@@
 
-Our results can be treated as a boundary condition for more complex and fine-grained models of galaxy size, such as semi-analytic models and hydrodynamical simulations.
+Our results can be treated as a starting point for more complex and fine-grained models of galaxy size, such as semi-analytic models and hydrodynamical simulations.
 For convenience, Figure \ref{fig:censatsizeratios} provides a simple summary statistic that can be used as a diagnostic for calibrating alternative modeling efforts.
@@
 We thank the {\tt Astropy} developers for the package-template \citep{astropy}, and {\tt NumPy} \citep{numpy_ndarray}, {\tt SciPy} \citep{scipy}, IPython, Matplotlib, and GitHub for their extremely useful free software.
+While writing this paper we made extensive use of the Astrophysics Data Service (ADS) and {\tt arXiv} preprint repository.
 
-This research was supported in part by the National Science Foundation under Grant No. NSF PHY11-25915. Work done at Argonne National Laboratory was supported under the DOE contract DE-AC02-06CH11357.
+This research was supported in part by the National Science Foundation under Grant No.
+NSF PHY11-25915.
+Work done at Argonne National Laboratory was supported under the DOE contract DE-AC02-06CH11357.
+AK was  supported by NSF grant  AST-1412107 and by the Kavli Institute for Cosmological Physics at the University of Chicago through grant PHY-1125897 and an endowment from the Kavli Foundation and its founder Fred Kavli.
 

### 2017-11-09 paper/galsize_paper.tex
fixed my affiliation

@@
 $^{2}$Department of Physics, University of Arizona, 1118 E 4th St, Tucson, AZ 85721 USA\\
-$^{3}$Department of Astronomy \& Astrophysics, The University of Chicago, Chicago, IL 60637 USA\\
+$^{3}$Department of Astronomy \& Astrophysics, and Kavli Institute for Cosmological Physics, University of Chicago, Chicago IL 60637\\
 $^{4}$Universit{\"a}ts-Sternwarte, Ludwig-Maximilians-Universit{\"a}t M{\"u}nchen, Scheinerstr. 1, 81679 M{\"u}nchen, Germany

### 2017-11-09 paper/galsize_paper.tex
Minor revisions; most blue-color text now removed and addressed

--- 2017-11-09 paper/galsize_paper.tex
@@
 
-Using galaxies observed in the Sloan Digital Sky Survey (SDSS) with the stellar mass measurements taken from the MPA-JHU catalog \citep{kauffmann_etal03,brinchmann_etal04}, we define volume-limited samples of galaxies according to the same $\mstar-$completeness cuts used in \citet{behroozi_etal15} (see Figure 2).
-\textcolor{blue}{AK: which DR the catalog is taken from?} We supplement the MPA-JHU catalog with measurements of half-light radius, $\rhalf,$ derived from galaxy profile decompositions provided by \citet{meert_etal15}.
+Using galaxies observed in the Data Release 10 of the Sloan Digital Sky Survey \citep[SDSS,][]{ahn_etal14} with the stellar mass measurements taken from the MPA-JHU catalog \citep{kauffmann_etal03,brinchmann_etal04}, we define volume-limited samples of galaxies according to the same $\mstar-$completeness cuts used in \citet{behroozi_etal15} (see Figure 2).
+We supplement the MPA-JHU catalog with measurements of half-light radius, $\rhalf,$ derived from galaxy profile decompositions provided by \citet{meert_etal15}.
 The \citet{meert_etal15} catalog is based on Data Release 7 of SDSS \citep{abazajian_etal09}, with improvements to the photometry pipeline and light profile fitting method and, especially, in background subtraction \citep{vikram_etal10,bernardi_etal13,bernardi_etal14,meert_etal13}.
@@
 
-The success of the $\rvir$-based model in explaining the size dependence of galaxy clustering implies that sizes of {\it all} galaxies,  red, blue, spheroid, disks, satellites and central, are, on average, proportional to the $\rmpeak,$ the physical size of the virial radius at the time at which $\mhalo$ stops growing.
-Although correlation is not necessarily causation, such universal and simple dependence poses a useful challenge to galaxy formation models, as it indicates tight connection betw
-een growth of galaxies and their host halos.
+The success of the $\rvir$-based model in explaining the size dependence of galaxy clustering implies that the sizes of {\it all} galaxies,  red, blue, spheroid, disks, satellites and central, are, on average, proportional to the $\rmpeak,$ the physical size of the virial radius at the time at which $\mhalo$ stops growing.
+Although correlation is not necessarily causation, such a universal and simple dependence poses a useful challenge to fine-grained galaxy formation models, as it indicates tight connection between the growth of galaxies and their host halos.
 
-The $\rvir$-based size model also assumes that after halo stops growing the size remains approximately constant and this assumption is consistent with observed size dependence of galaxy clustering in SDSS.
+The $\rvir$-based size model assumes as an ansatz that galaxy size remains approximately constant after a halo stops growing; as shown in Figure \ref{fig:clustering_ratio_upshot}, this assumption is consistent with the observed size-dependence of galaxy clustering in SDSS.
 The halos of typical satellites reach $\mpeak$ far outside the virial radius of their ultimate host halo \citep{behroozi_etal14}, and so in the $\rvir-$based model the size difference between satellites and centrals is largely in place prior to the time of satellite infall.
-Thus, as noted above, halos of central and satellite galaxies of the same $\mstar$  differ in epochs when their halo stopped growing (i.e., $\zpeak$) and this difference explains their different median sizes.
+Halos of central and satellite galaxies of the same $\mstar$ differ in the epoch $\zpeak$ at which their halo stopped growing, and this difference gives a natural explanation for their different median sizes.
 
-The difference also explains the relative trends of $\rhalf-\mstar$ relations for red and blue, or disk and spheroid galaxies.
+This difference also explains the relative trends of $\rhalf-\mstar$ relations for red and blue, or disk and spheroid galaxies.
 Both types of galaxies exhibit weak dependence of $\rhalf$ on $\mstar$ at $\mstar\lesssim 5\times 10^{10}\ M_\odot$ and
 at these masses $\rhalf$ of disks is a factor of two larger than those of spheroids.
-At larger masses, the sizes of galaxies of both types show stronger dependence on $\mstar$ and the difference in median size of disk and spheroid galaxies decreases \citep[e.g.,][]{bernardi_etal14}.
+At larger masses, the sizes of galaxies of both types show stronger dependence on $\mstar,$ and the difference in median size of disk and spheroid galaxies decreases \citep[e.g.,][]{bernardi_etal14}.
 
-In the $\rvir$-based size model, the weak dependence of $\rhalf$ on $\mstar$ for low mass galaxies is due to steep $\mstar-\mvir$ relation.
+In the $\rvir$-based size model, the weak dependence of $\rhalf$ on $\mstar$ for low-mass galaxies is due to the steep $\mstar-\mvir$ relation.
 For example, if $\mstar\propto\mvir^\alpha\propto\rvir^{3\alpha}$, then $\rhalf\propto \rvir\propto \mstar^{1/(3\alpha)}$.
-Given that $\alpha\sim 1-3$ is inferred for the $\mstar-\mvir$ relation at low masses \citep{kravtsov10,behroozi13_smhm,kravtsov_etal14}, the $\rhalf-\mstar$ relation in this regime is expected to be shallow.
-For galaxies of $\mstar\gtrsim 5\times 10^{10}\ M_\odot$, $\alpha\approx 0.3$ \citep[e.g.,][]{kravtsov_etal14} and thus 
+Given that $\alpha\sim 1-3$ is inferred for the $\mstar-\mvir$ relation at low masses \citep{kravtsov10,moster_etal13,behroozi13_smhm,kravtsov_etal14}, the $\rhalf-\mstar$ relation in this regime is expected to be shallow.
+For galaxies of $\mstar\gtrsim 5\times 10^{10}\ M_\odot$, $\alpha\approx 0.3$ \citep[e.g.,][]{kravtsov_etal14}, and thus
 the slope of the $\rhalf-\mstar$ relation is approximately linear.
-These trends of $\rhalf$ with $\mstar$ have a direct relation to the trends of surface brightness $\mu_\star=\mstar/(\pi\rhalf^2)$ with stellar mass.
+These trends of $\rhalf$ with $\mstar$ have a direct relation to the trends of surface brightness $\mu_\star=\mstar/(\pi\rhalf^2)$ with stellar mass \citep[see, for example, the $\mu_\star-$dependent clustering measurements in][which are qualitatively similar to the measurements reported here]{li_etal06}.
 
-The difference in median sizes of disk and spheroidal galaxies at $\mstar\lesssim 10^{11}\ M_\odot$ is explained by the fact that sizes of satellite galaxies are systematically smaller than sizes of central galaxies of the same $\mstar$ and
-the satellite fraction is much higher among spheroidal galaxies compared to the disk galaxies.
-For example, analyses of \citet{rodriguez_puebla_etal15} show that in this regime satellite fraction of blue galaxies is only $\approx 10-20\%$, while
-the satellite fraction of red galaxies is $\gtrsim 30-50\%$ increasing with decreasing stellar mass. 
-As $\mstar$ increases, satellite fractions of both blue and red galaxies drop and at $\mstar\gtrsim 10^{11}\ M_\odot$ vast majority of blue and red galaxies are centrals.
-If these galaxies occupy similar halo masses at the same $\mstar$, $\rvir$-based size model predicts that  the difference in sizes of red and blue galaxies should disappear at these masses, as is indeed observed.
-
-A testable prediction of this picture is that when 3D (de-projected) sizes of only central red and blue galaxies of the same $\mstar$ are compared they should be much closer, than the sizes of the overall red and blue populations.
+The difference in median sizes of disk and spheroidal galaxies at $\mstar\lesssim 10^{11}\ M_\odot$ can be explained by the sizes of satellite galaxies being systematically smaller than the sizes of central galaxies of the same $\mstar,$ coupled with the fact that the satellite fraction is much larger among spheroidal galaxies compared to disk galaxies.
+For example, the analysis in \citet{rodriguez_puebla_etal15} shows that in this regime, the satellite fraction of blue galaxies is only $\sim10-20\%$, while
+the satellite fraction of red galaxies is $\gtrsim 30-50\%,$ increasing with decreasing stellar mass.
+As $\mstar$ increases, the satellite fractions of both blue and red galaxies drop, and at $\mstar\gtrsim 10^{11}\ M_\odot,$ the vast majority of blue and red galaxies are centrals.
+If these galaxies occupy similar halo masses at the same $\mstar$, then the $\rvir$-based size model predicts that the difference in sizes of red and blue galaxies should disappear at these masses, as is indeed observed.
+A testable prediction of this picture is that when 3D (de-projected) sizes of only central red and blue galaxies of the same $\mstar$ are compared, the sizes should be much closer than the sizes of the overall red and blue populations.
 
@@
 To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which the trend is reversed and weakened: for both blue and red samples, $\Delta\Sigma$ of large galaxies is (slightly) stronger relative to small galaxies.
-\textcolor{blue}{AK: is it worth showing a second panel with $\Delta\Sigma$ for color-selected samples to back up the last sentence?}
 }
@@
 Traditional galaxy clustering is already being used to validate and/or fit models of the stellar-to-halo-mass relation \citep[e.g.,][]{leauthaud_etal11,moster_etal13,behroozi13_smhm,lehmann_etal15}.
-Based on our results, we advocate that empirical models for $\mean{\mstar}{\mhalo}$ be supplemented with additional model ingredients for $\median{\rhalf}{\mstar},$ (\textcolor{blue}{AK:} did you mean $\langle\rhalf|\mhalo\rangle$ here?
-Seems more logical in the context of this sentence) and that the parameters of the composite model be {\em jointly} constrained by measurements of the stellar mass function, $\mstar-$dependent clustering, and $\rhalf-$dependent clustering.
+Based on our results, we advocate that empirical models for $\mean{\mstar}{\mhalo}$ be supplemented with additional model ingredients for $\median{\rhalf}{\mhalo},$ and that the parameters of the composite model be {\em jointly} constrained by measurements of the stellar mass function, $\mstar-$dependent clustering, and $\rhalf-$dependent clustering.
 

### 2017-11-09 paper/galsize_paper.tex
Updated discussion of relation to previous work

@@
 For example, by treating observed groups as genuine dark matter halos, several analyses have found that the $\mstar-\rhalf$ relation of early-type galaxies exhibits weak, if any, environmental dependence \citep{weinmann_etal08,huertas_company_etal13b,shankar_etal14}.
-Meanwhile, \citet{weinmann_etal08} additionally find that for late-type galaxies, there is a strong correlation between disk size and central/satellite designation.
-Qualitatively, our clustering measurements shown in Figure \ref{fig:colorclustering} are in good agreement with these findings: once galaxies have been color-selected, only the clustering of blue galaxies shows significant dependence upon $\rhalf.$ Our clustering results are also consistent with the disk model presented in \citet{dutton_etal08,dutton_etal10}, which predicts that at fixed stellar mass, there is weak, positive correlation between disk size and halo mass.
 
-\textcolor{blue}{AK: when I was reading this paragraph, I had trouble digesting its meaning... Also it definitely broke the flow of the narrative for me.}
-As discussed in \citet{spindler_wake17}, it is entirely possible that size differences between centrals and satellites of the same mass can be accounted for by mutual covariance with an additional variable such as star formation rate or morphological type \citep[see also][for an explicit demonstration of this scenario]{lilly_carollo16}.
-In particular, suppose that centrals and satellites of the same mass have different early-type fractions as indicated in \citet{weinmann_etal06}, and that early- and late-type galaxies exhibit universal, but distinct, $\mstar-\rhalf$ relations.
-In such a case, centrals would be larger than satellites of the same mass, even though {\em early-type centrals} would have the same sizes as {\em early-type satellites}.
-This scenario could also explain the sign-change and weakening of $\rhalf-$dependent clustering measurements in the present work.
+As shown in \citet{campbell_etal15}, group-finding methods are subject to significant systematics, particularly when analyzing trends based on color: contemporary algorithms {\em generically} wash out differences between centrals and satellites; trends can even be artificially created that are not truly present.
+Our clustering-based, forward modeling methods are immune to such systematics, and so it is encouraging that our findings are commensurable with these results.
+Once galaxies have been color-selected, Figure \ref{fig:colorclustering} shows that the observed clustering trends nearly vanish in magnitude, and reverse sign.
+Insofar as blue galaxies are largely disk-dominated, the clustering results in Figure \ref{fig:colorclustering} are also consistent with the disk model presented in \citet{dutton_etal08,dutton_etal10}, which predicts that at fixed stellar mass, there is weak, positive correlation between disk size and halo mass.
 
@@
 While our results suggest that sizes of galaxies are linearly correlated with the
-virial radius of halos at the moment the halo mass reached its peak and that sizes of satellite galaxies were set {\em prior} to infall, our model is probably does not capture galaxy properties and their trends in full quantitative detail.
-For example, the clustering ratios of this model shown in Figure \ref{fig:clustering_ratio_upshot} do capture the overall trends, but also don't match the observed statistics fully.
- For present purposes, we have chosen to focus on exploring bracketing cases of qualitative ingredients, rather than fine-tuning the model.
+virial radius of halos at the moment the halo mass reached its peak, and also that sizes of satellite galaxies were set {\em prior} to infall, our model does not capture galaxy properties and their trends in full quantitative detail.
+For example, the clustering ratios of this model shown in Figure \ref{fig:clustering_ratio_upshot} do capture the overall trends, and also do not match the observed clustering statistics at the level of $\chi^2.$ For present purposes, we have chosen to focus on exploring bracketing cases of qualitative ingredients, rather than fine-tuning the model.
 
 Since the clustering signal is strongly influenced by differences between centrals and satellites, then the satellite fraction $F_{\rm sat}(\mstar)$ plays an important role in $\rhalf-$dependent clustering.
-For {\em fixed} scaling relations $\median{\rhalf^{\rm cens}}{\mhalo}$ and $\median{\rhalf^{\rm sats}}{\mhalo},$ models with different satellite fractions will exhibit different $\rhalf-$clustering ratios because $F_{\rm sat}(\mstar)$ controls the relative weighting of the two populations.
+For {\em fixed} scaling relations $\median{\rhalf^{\rm cens}}{\mhalo}$ and $\median{\rhalf^{\rm sats}}{\mhalo},$ models with different satellite fractions will exhibit distinct $\rhalf-$clustering ratios because $F_{\rm sat}(\mstar)$ controls the relative weighting of the two populations.
 An explicit demonstration of this point appears in the Appendix, which repeats the analyses in the main body of the text, but for a subhalo catalog with no orphan correction.
@@
 While it remains to be seen whether this explanation ends up comprising the whole story, one thing is now clear: it is not possible to reliably analyze environmental trends of galaxy $\rhalf$ without properly accounting for satellites.
-%Because of the large systematics that are common in contemporary group-finding methods \citep{campbell_etal15}, we consider forward modeling methods to be a requisite for continued progress on this topic.
 

### 2017-11-09 paper/galsize_paper.tex
minor revisions to appendix

@@
 
-In this appendix, we show two different a priori reasonable choices for the orphan selection function.
+In this appendix, we show two different, a priori reasonable choices for the orphan selection function.
 Since a rigorous calibration of $\mathcal{F}_{\rm orphan}$ is beyond the scope of the present work, we instead opt for a simple parameterization that yields reasonably accurate recovery of the galaxy clustering signal observed in SDSS.
 
-In both treatments studied here, we first throw out orphan subhalos with $V_{\rm max}/V_{\rm peak}<0.1,$ so that the most drastically disrupted subhalos remain unused.
-For our fiducial model used throughout the main body of the text, $\mathcal{F}_{\rm orphan}$ is defined by simply randomly select half of the orphan subhalos.
-For the alternative orphan selection function labeled as $M_{\rm host}-$dependent orphans in this appendix, we proceed as follows.
+In both treatments studied here, we first discard orphan subhalos with $V_{\rm max}/V_{\rm peak}<0.1,$ so that the most drastically disrupted subhalos remain unpopulated with galaxies.
+For our fiducial model used throughout the main body of the text, $\mathcal{F}_{\rm orphan}$ is defined by randomly selecting half of the orphan subhalos.
+For the alternative orphan selection function labeled as ``$M_{\rm host}-$dependent orphans" in this appendix, we proceed as follows.
 We model $\mathcal{F}_{\rm orphan}=\mathcal{F}_{\rm orphan}(M_{\rm peak},M_{\rm host}),$ where $\mpeak$ is the peak mass of the disrupted subhalo, and $\mhost$ is the present-day virial mass of its $z=0$ host halo.

### 2017-11-09 paper/galsize_paper.tex
Added comment in conclusions that mocks will be made available upon publication
Finished review of now-complete draft. Paper is ready for co-author review

@@
 Observational constraints on models for galaxy $\rhalf$ typically come from one-point function measurements such as $\median{\rhalf}{\mstar}$ and $\sigma(\rhalf\vert\mstar),$ e.g.,  \citet{khochfar_silk06,desmond_etal17,bottrell_etal17b,hou_etal17,somerville_etal17}, or otherwise from catalogs of galaxy groups \citep{weinmann_etal08,huertas_company_etal13b,spindler_wake17}.
-More recently, connection of galaxy sizes to virial radius of their parent halos have been
+More recently, the connection between a galaxy's size and the virial radius of its parent halo has been
 explored by converting stellar mass to halo mass and virial radius, using abundance matching \citep{kravtsov_etal04,tasitsiomi_etal04,vale_ostriker04,vale_ostriker06,conroy_etal06}.
-Such analysis indicated that sizes of galaxies
-are, on average, proportional to the virial radii of their host halos, both at $z=0$ \citep{kravtsov13}, and higher redshifts \citep{huang_etal17,somerville_etal17}.
+Such analyses have indicated that galaxy size is, on average, proportional to host halo virial radius, both at $z=0$ \citep{kravtsov13}, and higher redshifts \citep{huang_etal17,somerville_etal17}.
 
 Observations of two-point galaxy clustering, $\wproj(\rproj),$ have historically been used to place tight constraints on many features of the galaxy--halo connection, such as its $\mstar-$dependence \citep{moster_etal10,leauthaud_etal11,reddick_etal13,skibba_etal15}, dependence on luminosity \citep{kravtsov_etal04, tasitsiomi_etal04,vale_ostriker04,vale_ostriker06,tinker_etal05,cacciato_etal13}, broadband color \citep{coil_etal08,zehavi_etal11,guo_etal11,hearin_watson13}, and star-formation rate \citep{wang_etal07,tinker_etal13,watson_etal14}.
-In the present work, we exploit the constraining power of $\wproj(\rproj)$ to test empirical models connecting galaxy stellar masses and sizes to the properties of the galaxy's parent dark matter halo.
+In the present work, we exploit the constraining power of $\wproj(\rproj)$ to test empirical models connecting galaxy stellar mass and size to the properties of the galaxy's parent dark matter halo.
 
@@
 
-Using galaxies observed in the Data Release 10 of the Sloan Digital Sky Survey \citep[SDSS,][]{ahn_etal14} with the stellar mass measurements taken from the MPA-JHU catalog \citep{kauffmann_etal03,brinchmann_etal04}, we define volume-limited samples of galaxies according to the same $\mstar-$completeness cuts used in \citet{behroozi_etal15} (see Figure 2).
+Using galaxies from Data Release 10 of the Sloan Digital Sky Survey \citep[SDSS,][]{ahn_etal14} with the stellar mass measurements taken from the MPA-JHU catalog \citep{kauffmann_etal03,brinchmann_etal04}, we define volume-limited samples of galaxies according to the same $\mstar-$completeness cuts used in \citet{behroozi_etal15} (see Figure 2).
 We supplement the MPA-JHU catalog with measurements of half-light radius, $\rhalf,$ derived from galaxy profile decompositions provided by \citet{meert_etal15}.
@@
 
-As the bedrock of our modeling, we use the publicly available\footnote{\url{http://www.slac.stanford.edu/~behroozi/BPlanck\_Hlists}} catalog of {\tt Rockstar} subhalos identified at $z=0$ in the Bolshoi-Planck simulation \citep{klypin_etal11,behroozi12_rockstar,behroozi12_consistent_trees,riebe_etal13,rodriguez_puebla16_bolplanck}.
-As described in \S\ref{subsec:sham}, we will use traditional abundance matching to connect stellar mass $\mstar$ with subhalo peak mass $\mpeak.$ To address issues related to subhalo incompleteness \citep{guo_white13,campbell_etal17}, we supplement the Bolshoi-Planck subhalo catalog with subhalos that have been disrupted and no longer appear in the standard catalog as $z=0$ surviving subhalos.
+As the bedrock of our modeling, we use the publicly available\footnote{\url{http://www.slac.stanford.edu/~behroozi/BPlanck\_Hlists}} catalog of {\tt Rockstar} subhalos identified at $z=0$ in the Bolshoi-Planck simulation \citep{klypin_etal11,behroozi12_rockstar,riebe_etal13,behroozi_etal12b,rodriguez_puebla16_bolplanck}.
+As described in \S\ref{subsec:sham}, we use traditional abundance matching to connect stellar mass $\mstar$ with subhalo mass.
+To address issues related to subhalo incompleteness \citep{guo_white13,campbell_etal17}, we supplement the Bolshoi-Planck subhalo catalog with subhalos that have been disrupted and no longer appear in the standard catalog as $z=0$ surviving subhalos.
 We describe our treatment of these ``orphan" subhalos in the Appendix.
@@
 For our SDSS galaxy samples, we calculate two-point clustering $\wproj$ using line-of-sight projection of $\pi_{\rm max}=20~\mpc$ using the {\tt correl} program in {\tt UniverseMachine}.
-For mock galaxies, to compute galaxy clustering we employ the distant observer approximation by treating the simulation $z-$axis as the line-of-sight.
-We compute $\wproj$ using the {\tt mock\_observables.wp} function in {\tt Halotools} \citep{hearin_etal16}, which is a python implementation of the algorithm in the {\tt Corrfunc} C library \citep{sinha_etal17}.
+For mock galaxies, we compute $\wproj$ using the {\tt mock\_observables.wp} function in {\tt Halotools} \citep{hearin_etal16}, which is a python implementation of the algorithm in the {\tt Corrfunc} C library \citep{sinha_etal17}.
 We also use {\tt Halotools} to compute the galaxy-galaxy lensing signal, $\Delta\Sigma,$ using the {\tt mock\_observables.delta\_sigma} function.
@@
 In addition to stellar mass, $\wproj(\rproj)$ depends on galaxy color \citep[e.g.,][]{zehavi_etal11}. Thus, we will also consider
-dependence of clustering on galaxy size while controlling for color. The results for the subsamples split in stellar mass and color are presented in \S\ref{subsec:colormorph}.
+dependence of clustering on galaxy size while controlling for color. Observations of clustering exhibited by subsamples split in stellar mass and color are presented in \S\ref{subsec:colormorph}.
 
@@
 We map $\mstar$ onto subhalos using deconvolution abundance matching (SHAM).
-See section 3.3 of \citet{behroozi_etal10} or the appendix of \citet{kravtsov_etal14} for an account of the mathematics underlying this technique in the presence of scatter.
+See Section 3.3 of \citet{behroozi_etal10}, or the appendix of \citet{kravtsov_etal14}, for an account of the mathematics underlying this technique in the presence of scatter.
 To perform the abundance matching, we use the publicly available code\footnote{\url{https://bitbucket.org/yymao/abundancematching/overview}} developed by Yao-Yuan Mao \citep{lehmann_etal15} that provides a python wrapper around the C kernel developed by Peter Behroozi \citep{behroozi_etal10}.
@@
 Figure \ref{fig:baseline_sham_clustering} shows that our implementation of SHAM produces model galaxies whose projected clustering, $\wproj(\rproj)$, is in reasonably good agreement with SDSS galaxies.
-We note, however, that $\wproj(\rproj\gtrsim1{\rm Mpc})$ is $\sim10-20\%$ too weak at stellar mass $\mstar\gtrsim10^{10.75}\msun.$
+We note, however, that $\wproj(\rproj\gtrsim1{\rm Mpc})$ is $\sim10-20\%$ too weak at stellar mass $\mstar\gtrsim10^{10.75}\msun,$ and similarly on all scales for the $\mstar\gtrsim10^{9.75}\msun$ sample.
 
@@
 Black points with error bars show SDSS measurements; solid black curves show the abundance matching prediction of our fiducial model, which includes the effect of orphan subhalos (see Appendix A).
-Including orphans mitigates the discrepancy in the clustering predicted by traditional, $\mpeak-$based SHAM based, though mild tension remains on small scales for $\mstar\gtrsim10^{10.75}\msun,$ and on all scales for the $\mstar\gtrsim10^{9.75}\msun.$
+Including orphans mitigates the discrepancy in the clustering predicted by traditional, $\mpeak-$based SHAM, though mild tension remains on small scales for $\mstar\gtrsim10^{10.75}\msun,$ and on all scales for $\mstar\gtrsim10^{9.75}\msun.$
 }
@@
 
-\textcolor{blue}{AK: I don't think the name of the model is descriptive here, but I could not yet come up with a better one.}
+\textcolor{red}{AK: I don't think the name of the model is descriptive here, but I could not yet come up with a better one.}
 In the first model we explore, we assume that stellar mass $\mstar$ controls $\rhalf,$ so that galaxy sizes are drawn from a log-normal distribution with $0.2$ dex of scatter centered at $\median{\rhalf}{\mstar}.$ To implement this model, for simplicity we tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form \citep[see, e.g.,][]{zhang_yang17}.
-Note that this model reproduces the observed $\rhalf-\mstar$ relation by construction.
+Thus this model reproduces the observed $\rhalf-\mstar$ relation by construction.
 
@@
 As noted in \S\ref{sec:intro}, \citet{kravtsov13} showed that galaxy sizes are on average proportional to the virial radius of their host halo.
-Motivated by these results, we  explore a model in which $\rhalf$ scales linearly with the halo virial radius:\footnote{We note that the normalization factor in \citet{kravtsov13} is 0.015, where as our normalization is 0.01.
+Motivated by these results, we  explore a model in which $\rhalf$ scales linearly with halo virial radius:\footnote{We note that the normalization factor in \citet{kravtsov13} is 0.015, where as our normalization is 0.01.
 The difference derives from two factors: {\em i.} the choice of halo radius definition: \citet{bryan_norman98} in the present work, compared to the $200c$ definition used in \citet{kravtsov13}; {\em ii.} the latter study used deprojected (larger) sizes for spheroidal galaxies, whereas we make no such correction here.}
@@
 \eeq
-For the virial radius of halos and subhalos, we use $\rmpeak:$ the value of $\rvir$ in physical units of $\kpc$ measured at the time when halo mass reached its maximum.
-The relationship between $\rmpeak$ and $\mpeak$ is given by
+For the virial radius of halos and subhalos, we use $\rmpeak:$ the value of $\rvir$ in physical units of $\kpc$ measured at the time when halo mass reached its maximum, $\zpeak.$  The relationship between $\rmpeak$ and $\mpeak$ is given by
 \beq
@@
 This model thus predicts no dependence of galaxy clustering upon $\rhalf$ at fixed $\mstar,$ simply because the scatter of $\rhalf$ about $\median{\rhalf}{\mstar}$ is uncorrelated with any other variable.
-The figure shows that this model clearly is at odds with significant dependence of clustering on size exhibited by SDSS galaxies.
+The figure shows that this model clearly is at odds with the significant dependence of clustering on size exhibited by SDSS galaxies.
 
@@
 For $\mstar-$complete samples, small galaxies cluster much stronger than large galaxies; for color-selected samples, the reverse is true, but the difference is much smaller and is confined to a limited range of scales.
-Although the two results may seem surprising, even contradictory, they can, in fact be
-explained within a unified simple model, as will be discussed in \S\ref{sec:interpretation}.
+Although the two results may seem surprising, even contradictory, they can, in fact be explained within a simple, unified model, as will be discussed in \S\ref{sec:interpretation}.
 
@@
 At this stellar mass, pre-selecting galaxy samples by color results in a dramatic weakening of the $\rhalf-$dependence of $\wproj$ relative to $\mstar-$complete samples, as well as a sign-reversal of the signal.
+In \S\ref{sec:interpretation} we give a simple halo model picture unifying the trends shown here with those illustrated in Figure \ref{fig:clustering_ratio_upshot}.
 }
@@
 In a narrow bin of halo mass $\mhalo\equiv\mpeak\approx10^{12}\msun,$ we show the distribution of model galaxy sizes for different subpopulations galaxies, as predicted by the $\rvir-$based model.
-The red histogram shows the sizes of satellites; the blue histogram shows host halos that have never passed inside the virial radius of a larger halo (``true centrals"); the green histogram host halos that were subhalos inside a larger at some point in their past history (``splashback centrals").
+The red histogram shows the sizes of satellites; the blue histogram shows host halos that have never passed inside the virial radius of a larger halo (``true centrals"); the green histogram host halos that were subhalos inside a larger halo at some point in their past history (``splashback centrals").
 In the $\rvir-$based model, galaxy size is set by the {\em physical} size of the virial radius at the time the halo attains its peak mass, naturally resulting in smaller sizes for satellites and splashback centrals relative to true centrals of the same $\mhalo.$
@@
 
-Recall that in the $\rvir$-based size model, galaxy size is proportional to the virial radius of host halo at the redshift  when the halo halo attained its maximum mass.
-Thus, we can expect that in this model satellite galaxies will have sizes smaller than sizes of central galaxies hosted by halos of similar stellar mass.
-Indeed, Figure \ref{fig:censatsizehist} shows the $\rhalf$ distributions of central, satellite, and ``splashback'' central galaxies hosted by halos of the same mass $\mhalo\equiv\mpeak\approx10^{12}\msun.$ A ``splashback central"  is defined as a present-day central galaxy that used to be a satellite, i.e., its main progenitor halo passed inside the virial radius of a larger halo at some point in its past history.
+Recall that in the $\rvir$-based size model, galaxy size is proportional to halo virial radius at $\zpeak,$ the redshift when the halo attained its maximum mass.
+Thus we can expect that in this model, satellite galaxies will have smaller sizes than  central galaxies hosted by halos of similar mass.
+Indeed, Figure \ref{fig:censatsizehist} shows the $\rhalf$ distributions of central, satellite, and ``splashback'' central galaxies hosted by halos of the same mass, $\mhalo\equiv\mpeak\approx10^{12}\msun.$ A ``splashback central"  is defined as a present-day central galaxy that used to be a satellite, i.e., its main progenitor halo passed inside the virial radius of a larger halo at some point in its past history.
 On the other hand, we define a ``true central" as a galaxy that has never been a satellite.
@@
 For example, it is well known that satellites are redder than centrals of the same stellar mass \citep[e.g.,][]{vdB_etal08}; accordingly, red galaxies cluster much more strongly than  blue galaxies \citep[e.g.,][]{zehavi_etal11}.
-Samples of red (blue) galaxies with stellar masses of $\mstar\sim 10^{10}\ M_\odot$ are dominated by satellite (central) galaxies, and splitting by size within such samples no longer corresponds to the split into satellite- and central-dominated samples.
+Samples of red (blue) galaxies with stellar masses of $\mstar\sim 10^{10}\ M_\odot$ are dominated by satellite (central) galaxies, and splitting by size {\em within} such samples no longer corresponds to the split into satellite- and central-dominated samples.
 In this case, the $\rvir$-based size model predicts that splitting by size {\em does} correspond to splitting by halo mass $\rhalf\propto\rvir\propto\mhalo^{1/3},$ and therefore that large galaxies should be somewhat more clustered than the small ones.
@@
 The success of the $\rvir$-based model in explaining the size dependence of galaxy clustering implies that the sizes of {\it all} galaxies,  red, blue, spheroid, disks, satellites and central, are, on average, proportional to the $\rmpeak,$ the physical size of the virial radius at the time at which $\mhalo$ stops growing.
-Although correlation is not necessarily causation, such a universal and simple dependence poses a useful challenge to fine-grained galaxy formation models, as it indicates tight connection between the growth of galaxies and their host halos.
+Although correlation is not necessarily causation, such a universal and simple dependence poses a useful challenge to fine-grained galaxy formation models, as it indicates a tight connection between the growth of galaxies and their host halos.
 
-The $\rvir$-based size model assumes as an ansatz that galaxy size remains approximately constant after a halo stops growing; as shown in Figure \ref{fig:clustering_ratio_upshot}, this assumption is consistent with the observed size-dependence of galaxy clustering in SDSS.
+The $\rvir$-based size model assumes as an ansatz that galaxy size remains approximately constant after its halo stops growing; as shown in Figure \ref{fig:clustering_ratio_upshot}, this assumption is consistent with the observed size-dependence of galaxy clustering in SDSS.
 The halos of typical satellites reach $\mpeak$ far outside the virial radius of their ultimate host halo \citep{behroozi_etal14}, and so in the $\rvir-$based model the size difference between satellites and centrals is largely in place prior to the time of satellite infall.
@@
 
-%The broad features of the $\wproj(\rproj)$ measurements shown in Figure \ref{fig:colorclustering} give insight into the characteristics that should be exhibited by any model for the relationship between $B/T$ and $\rhalf.$ First, the bottom right panel of Figure \ref{fig:colorclustering} indicates that the size of the bulge has only a tenuous connection to the properties of its parent dark matter halo.\footnote{Strictly speaking, the size of the bulge could in principle be closely connected to any number of dark matter halo properties, so long as those halo properties do not significantly impact two-point clustering.} Second, for disk-dominated galaxies, the observed $\rhalf-$dependent clustering suggests that at fixed $\mstar,$ the size of the disk is strongly correlated with whether or not the galaxy is a satellite.
-These findings imply that bulge prominence is intimately connected with the quenching of star-formation, but that there is wide variation in star-formation histories amongst disk-dominated galaxies, in agreement with numerous previous findings \citep[see, e.g.,][]{woo_etal15,font_etal17}.
-
-% A possibly overkill caveat paragraph:
-%While these clustering measurements give supporting evidence that satellite mass stripping plays a sub-dominant role in shaping galaxy size, we point out that our treatment of satellite mass loss is only approximate: we have modified the size of satellites without self-consistently modifying total stellar mass.
-In the present work, we have opted not to develop and fine-tune a complex, semi-analytic model; instead, we have made a simple ``first-order" estimate for the level at which satellite-specific stripping impacts the two-point function.
-Our findings support the idea that the small sizes of satellites arise primarily from the satellite's distinctive evolution within a high density region and a steep tidal field {\em prior} to becoming a present-day satellite.
-
 %---------------------------------------------------------------------------------------------------
@@
 As shown in \citet{campbell_etal15}, group-finding methods are subject to significant systematics, particularly when analyzing trends based on color: contemporary algorithms {\em generically} wash out differences between centrals and satellites; trends can even be artificially created that are not truly present.
-Our clustering-based, forward modeling methods are immune to such systematics, and so it is encouraging that our findings are commensurable with these results.
+Our forward modeling inference technique is not subject to such systematics because our methods are entirely outwith the group-finding framework, and so it is encouraging that our findings are commensurable with these results.
 Once galaxies have been color-selected, Figure \ref{fig:colorclustering} shows that the observed clustering trends nearly vanish in magnitude, and reverse sign.
-Insofar as blue galaxies are largely disk-dominated, the clustering results in Figure \ref{fig:colorclustering} are also consistent with the disk model presented in \citet{dutton_etal08,dutton_etal10}, which predicts that at fixed stellar mass, there is weak, positive correlation between disk size and halo mass.
+Insofar as blue galaxies are largely disk-dominated, our clustering results in Figure \ref{fig:colorclustering} are also consistent with the disk model presented in \citet{dutton_etal08,dutton_etal10}, which predicts that at fixed stellar mass, there is weak, positive correlation between disk size and halo mass.
+Our conclusions are also qualitatively consistent with \citet{spindler_wake17}, who find that centrals in the \citet{yang_etal05a} group catalog are $\sim20-25\%$ larger than satellites of similar halo mass (using stellar velocity dispersion as an observational proxy for halo mass); we find the same trend at a comparable, if slightly larger magnitude.
 
@@
 
-%The precision cosmology program also depends critically on accurate modeling of galaxies, so that cosmological parameter inference can be confidently conducted without undue interference from uncertainty in baryonic physics \citep{LSST_science,LSST_galaxies}.
-
 The scope of this work is to serve as a pilot study in which we identify the chief ingredients that can influence the $\rhalf-$dependence of galaxy clustering.
@@
 virial radius of halos at the moment the halo mass reached its peak, and also that sizes of satellite galaxies were set {\em prior} to infall, our model does not capture galaxy properties and their trends in full quantitative detail.
-For example, the clustering ratios of this model shown in Figure \ref{fig:clustering_ratio_upshot} do capture the overall trends, and also do not match the observed clustering statistics at the level of $\chi^2.$ For present purposes, we have chosen to focus on exploring bracketing cases of qualitative ingredients, rather than fine-tuning the model.
+For example, the clustering ratios of this model shown in Figure \ref{fig:clustering_ratio_upshot} do capture the overall trends, but do not match the observed clustering statistics at the level of $\chi^2.$ For present purposes, we have chosen to focus on exploring bracketing cases of qualitative ingredients, rather than fine-tuning the model.
 
@@
 For {\em fixed} scaling relations $\median{\rhalf^{\rm cens}}{\mhalo}$ and $\median{\rhalf^{\rm sats}}{\mhalo},$ models with different satellite fractions will exhibit distinct $\rhalf-$clustering ratios because $F_{\rm sat}(\mstar)$ controls the relative weighting of the two populations.
-An explicit demonstration of this point appears in the Appendix, which repeats the analyses in the main body of the text, but for a subhalo catalog with no orphan correction.
+An explicit demonstration of this point appears in the Appendix, which repeats the analyses in the main body of the text, but for a subhalo catalog with no orphan correction (and therefore a different satellite fraction).
 
@@
 
-We have presented new measurements of the dependence of galaxy clustering upon galaxy size, and used {\tt Halotools} to identify the basic ingredients that influence the signal.
+We have presented new measurements of the dependence of galaxy clustering upon galaxy size, and used forward-modeling methods based on {\tt Halotools} to identify the basic ingredients that influence the signal.
 We conclude with a brief summary of our primary findings:
@@
 The magnitude, scale-dependence, and $\mstar-$dependence of $\rhalf-$dependent clustering provides strong evidence that satellite galaxies are smaller than central galaxies of the same halo mass.
-\item A simple empirical model in which $\rhalf$ is set by halo $\rvir$ at the time of peak halo mass exhibits a clustering signal that is strikingly similar to that r seen in SDSS.
+\item A simple empirical model in which $\rhalf$ is set by halo $\rvir$ at the time of peak halo mass exhibits a clustering signal that is strikingly similar to that seen in SDSS.
 \item Models in which $\rhalf$ is regulated by $\mstar,$ rather than $\mhalo,$ are grossly discrepant with the observed clustering signal, even when accounting for satellite mass stripping.
-\item Taken together, our findings indicate that satellite-specific processes play a sub-dominant role in setting the relative size of centrals and satellites, which instead appears to be largely predetermined at the time of satellite infall.
+\item Taken together, our findings indicate that satellite-specific processes play a sub-dominant role in setting the different sizes of centrals and satellites; these size differences instead appear to be largely predetermined at the time of satellite infall.
 \een
@@
 We view the present work as a pilot study that motivates a Bayesian inference program to tightly constrain the galaxy size-halo connection with forward modeling techniques, in direct analogy to the literature on the stellar-to-halo-mass relation.
+
 Our publicly available python code provides a simple means for cosmological surveys to generate synthetic galaxy populations with realistic sizes across the cosmic web.
+Mock catalogs of $z=0$ model galaxies with $\mstar$ and $\rhalf$ will be made publicly available upon journal publication; prior to that time, our mocks are available upon request.
 
@@
 APH thanks John Baker for the {\em Toejam \& Earl} soundtrack.
-Thanks also to Frank van den Bosch, Andrew Zentner, Doug Watson, and Risa Wechsler for thoughtful feedback at various stages of the development of this work, and to Faustin Carter and Sebastian Bocquet for sharing their matplotlib expertise.
+Thanks also to Frank van den Bosch, Andrew Zentner, Doug Watson, and Risa Wechsler for thoughtful feedback at various stages of the development of this work, to Faustin Carter and Sebastian Bocquet for sharing their matplotlib expertise, and to Andrew Zentner for Scottish grammar consultation.
 

### 2017-11-10 paper/galsize_paper.tex
Minor grammatical changes

@@
 
-Numerous previous analyses have employed the \citet{yang_etal05b} group catalog to ``directly" study the relationship between galaxy mass, size, and environment.
+Numerous previous analyses have employed the \citet{yang_etal05b} group catalog to study the relationship between galaxy mass, size, and environment.
 For example, by treating observed groups as genuine dark matter halos, several analyses have found that the $\mstar-\rhalf$ relation of early-type galaxies exhibits weak, if any, environmental dependence \citep{weinmann_etal08,huertas_company_etal13b,shankar_etal14}.
@@
 
-The scope of this work is to serve as a pilot study in which we identify the chief ingredients that can influence the $\rhalf-$dependence of galaxy clustering.
+This work is intended to serve as a pilot study in which we identify the chief ingredients that can influence the $\rhalf-$dependence of galaxy clustering.
 While our results suggest that sizes of galaxies are linearly correlated with the

### 2017-11-10 paper/galsize_paper.tex
Improved clarity of discussion in 5.1 of color-dependent results

@@
 
-Likewise, the significantly weaker dependence of clustering on size for color-selected samples (Figure \ref{fig:colorclustering}), and its reversed sign, can be naturally explained within the same framework.
-For example, it is well known that satellites are redder than centrals of the same stellar mass \citep[e.g.,][]{vdB_etal08}; accordingly, red galaxies cluster much more strongly than  blue galaxies \citep[e.g.,][]{zehavi_etal11}.
-Samples of red (blue) galaxies with stellar masses of $\mstar\sim 10^{10}\ M_\odot$ are dominated by satellite (central) galaxies, and splitting by size {\em within} such samples no longer corresponds to the split into satellite- and central-dominated samples.
-In this case, the $\rvir$-based size model predicts that splitting by size {\em does} correspond to splitting by halo mass $\rhalf\propto\rvir\propto\mhalo^{1/3},$ and therefore that large galaxies should be somewhat more clustered than the small ones.
-That is, the $\rvir-$based model predicts that $\rhalf-$dependent clustering should be reversed for color-selected samples, and that the magnitude of the dependence should be significantly weaker due to weak dependence of virial radius on halo mass, and weak dependence of clustering on halo mass in this regime.
+Likewise, the significantly weaker dependence of clustering on size for color-selected samples (Figure \ref{fig:colorclustering}), and its reversed sign, can be naturally explained by the same principles.
+It is well known that satellites are redder than centrals of the same stellar mass \citep[e.g.,][]{vdB_etal08}, and so blue galaxies have a small satellite fraction, while red galaxies have a large fraction of satellites that occupy high-mass halos; accordingly, red galaxies cluster much more strongly than blue galaxies \citep[e.g.,][]{zehavi_etal11}.
+Pre-selecting galaxy samples by color then naturally restricts the impact of satellites on size-dependent clustering.
+For blue galaxies, the reason traces to the small value of $F_{\rm sat};$ for red galaxies, the reason traces to the limited dynamic range of halo masses occupied by the satellites.
+With the impact of satellites reduced, the relative clustering of centrals becomes more important.
+In the limit that size-dependent clustering is dominated by centrals, the $\rvir$-based size model predicts that large galaxy samples should be (weakly) more clustered than small ones, because $\rhalf\propto\rvir\propto\mhalo^{1/3}.$ This is the trend seen in the clustering measurements shown in Figure \ref{fig:colorclustering}.
 
 While we consider such an explanation plausible, and even likely, a conclusive confirmation requires proper forward modeling of size and color jointly.
-Such an effort is strongly motivated by our results, but is beyond the scope of the present work.
+Such an effort is well motivated by our results, but is beyond the scope of the present work.
 

### 2017-11-11 paper/galsize_paper.tex
Updated figures with larger labels
Update text with description of expanded lensing predictions

@@
 %---------------------------------------------------------------------------------------------------
-\begin{figure}
+\begin{figure*}
 \centering
 \includegraphics[width=8cm]{FIGS/rvir_only_lensing_prediction.pdf}
+\includegraphics[width=8cm]{FIGS/host_mass_distributions_sm9p75_sm10p25.pdf}
+\includegraphics[width=8cm]{FIGS/rvir_only_lensing_prediction2.pdf}
+\includegraphics[width=8cm]{FIGS/host_mass_distributions_sm10p25_sm10p75.pdf}
+\includegraphics[width=8cm]{FIGS/rvir_only_lensing_prediction3.pdf}
+\includegraphics[width=8cm]{FIGS/host_mass_distributions_sm10p75_sm11p25.pdf}
 \caption{
 {\bf Prediction for $\rhalf-$dependence of galaxy lensing.}
-Using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}, we make predictions for as-yet-unseen measurements of the $\rhalf-$dependence of galaxy lensing of $\mstar-$complete samples, where ``small" and ``large" subsamples are defined as in \S\ref{subsec:sizedef}.
-As a generic consequence of satellites being smaller than centrals of the same mass, we predict that future lensing measurements of $\mstar-$complete samples will show $\Delta\Sigma$ of small galaxies to be significantly stronger relative to large galaxies of the same stellar mass.
-To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which the trend is reversed and weakened: for both blue and red samples, $\Delta\Sigma$ of large galaxies is (slightly) stronger relative to small galaxies.
+Using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}, in the {\em left panels} we show predictions for as-yet-unseen measurements of the $\rhalf-$dependence of galaxy lensing of $\mstar-$complete samples, where ``small" and ``large" subsamples are defined as in \S\ref{subsec:sizedef}.
+To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which the trends shown here are reversed and weakened: for both blue and red samples, the observed $\Delta\Sigma$ of large galaxies is (slightly) stronger relative to small galaxies.
+As a generic consequence of satellites being smaller than centrals of the same mass, we predict that future lensing measurements of $\mstar-$complete samples will show $\Delta\Sigma$ of small galaxies to be significantly stronger relative to large galaxies of the same stellar mass $\mstar\lesssim10^{11}\msun.$ We additionally predict that at sufficiently large mass $\mstar\gtrsim10^{11}\msun,$ the trend of small-scale $\Delta\Sigma$ with $\rhalf$ should reverse sign.
+The {\em right panels} display the physical explanation for this prediction.
+For $\mstar\lesssim10^{11}\msun,$ satellites preferentially populating the small sample heavily weight high-mass halos, boosting the lensing signal on all scales.
+For $\mstar\gtrsim10^{11}\msun,$ when $F_{\rm sat}\lesssim10\%,$ central galaxies dominate the signal, and the $\rvir-$based model predicts that $\rhalf$ increases with $\mhalo$ for centrals.
+See text for further details.
 }
 \label{fig:lensingprediction}
-\end{figure}
+\end{figure*}
 %-----------------------------------------------------------------------------------------------------
@@
 This result is in good agreement with the clustering measurements in the top panels of Figure \ref{fig:colorclustering}, which show the same trend.
+
 To date, the $\rhalf-$dependence of $\Delta\Sigma$ not yet been measured for $\mstar-$complete samples.
-We show  predictions of the $\rvir-$based model for future measurements of this signal in Figure \ref{fig:lensingprediction}.
-The halo model explanation for this trend is the same as for $\wproj:$ satellites occupy higher mass host halos relative to centrals of the same stellar mass, boosting $\Delta\Sigma$ for small relative to large galaxy samples.
+In the left panels of Figure \ref{fig:lensingprediction}, we show predictions of the $\rvir-$based model for future measurements of $\Delta\Sigma.$ The halo model principles underlying the lensing trends are the same as for $\wproj.$ For $\mstar\lesssim10^{11}\msun,$ the difference in $F_{\rm sat}$ between small and large samples is the dominant factor; satellites occupy higher mass host halos relative to centrals of the same stellar mass, boosting $\Delta\Sigma$ for small relative to large galaxy samples.
+At sufficiently large stellar mass $\mstar\gtrsim10^{11}\msun,$ when $F_{\rm sat}\lesssim10\%,$ the role of centrals becomes dominant; the $\rvir-$based model predicts that $\mhalo$ increases with $\rhalf$ for centrals, which is reflected in the reversal of the small-scale signal in the bottom left panel.
+
+The right panels of Figure \ref{fig:lensingprediction} compare the distributions of host halo mass for small and large samples; for centrals, $\mhost=\mhalo,$ while for satellites, $\mhost$ is the virial mass of the parent halo.
+The peak of each distribution arises from central galaxies, while the long tail at large values of $\mhost$ is due to satellites.
+At all stellar mass, the blue histograms peak at slightly larger $\mhost$ relative the red, because the $\rvir-$based model predicts that $\mhalo$ increases with $\rhalf$ for centrals.
+For $\mstar-$complete samples, this effect only becomes dominant when the satellite fraction drops to sufficiently small values.
+Qualitatively, all of these features are completely generic predictions of the $\rvir-$based model; quantitatively, the precise value of $\mstar$ where the effect of centrals begins to dominate $\Delta\Sigma$ depends sensitively on $F_{\rm sat}(\mstar),$ which we have only roughly calibrated in the present work.
 

### 2017-11-11 paper/galsize_paper.tex
Added paragraph discussing potential importance of halo definition

@@
 
+In any model where galaxy $\rhalf$ co-evolves with halo $\rvir,$ the choice of halo boundary definition necessarily impacts the model prediction.
+Since the clustering of halos has non-trivial dependence upon halo definition \citep{villarreal_etal17}, then measurements of galaxy clustering may be able to observationally distinguish a particular halo boundary that is most closely connected to galaxy size.
+The redshift evolution of the relationship between $\mhalo$ and $\rvir$ also varies with halo definition, and so measurements of $\rhalf-$dependent clustering across redshift may provide a further observational handle on the halo radius definition that best predicts galaxy size.
+
 %---------------------------------------------------------------------------------------------------

### 2017-11-12 paper/galsize_paper.tex
Updated all histograms to be based on Gaussian KDE, and corrected typos in the text

@@
 
-The approach we take is is to forward model the $\rhalf-$halo connection: we generate a Monte Carlo realizations of the model, and then make synthetic measurements in a manner that closely mimics the measurements we make on our observed galaxy samples.
+The approach we take is to forward model the $\rhalf-$halo connection: we generate a Monte Carlo realizations of the model, and then make synthetic measurements in a manner that closely mimics the measurements we make on our observed galaxy samples.
 We describe the dataset and simulations we use in \S\ref{sec:data}, and our forward-modeling methods in \S\ref{sec:model}.
@@
 The solid green curves shows the prediction of a model where $\rhalf$ is statistically set by $\mstar,$ in the complete absence of satellite mass loss.
-Such a model would predict zero $\rhalf-$dependence to galaxy clustering, in gross tension with observations.
+Such a model predicts zero $\rhalf-$dependence to galaxy clustering, in gross tension with observations.
 The solid purple curves show results for a model in which satellites lose mass after infall in a manner similar to what is seen in high-resolution hydrodynamical simulations, as described in \S\ref{subsubsec:strippingmodel}.
@@
 {\bf Relative sizes of centrals and satellites.}
-In a narrow bin of halo mass $\mhalo\equiv\mpeak\approx10^{12}\msun,$ we show the distribution of model galaxy sizes for different subpopulations galaxies, as predicted by the $\rvir-$based model.
+In a narrow bin of subhalo mass $\mhalo\equiv\mpeak\approx10^{12}\msun,$ we show the distribution of galaxy sizes for different subpopulations, as predicted by the $\rvir-$based model.
 The red histogram shows the sizes of satellites; the blue histogram shows host halos that have never passed inside the virial radius of a larger halo (``true centrals"); the green histogram host halos that were subhalos inside a larger halo at some point in their past history (``splashback centrals").
-In the $\rvir-$based model, galaxy size is set by the {\em physical} size of the virial radius at the time the halo attains its peak mass, naturally resulting in smaller sizes for satellites and splashback centrals relative to true centrals of the same $\mhalo.$
+In the $\rvir-$based model, galaxy size is set by the {\em physical} size of the virial radius at the time the halo attains its peak mass, naturally resulting in smaller sizes for satellites and splashback centrals relative to true centrals of the same mass.
 }
@@
 In the left panels of Figure \ref{fig:lensingprediction}, we show predictions of the $\rvir-$based model for future measurements of $\Delta\Sigma.$ The halo model principles underlying the lensing trends are the same as for $\wproj.$ For $\mstar\lesssim10^{11}\msun,$ the difference in $F_{\rm sat}$ between small and large samples is the dominant factor; satellites occupy higher mass host halos relative to centrals of the same stellar mass, boosting $\Delta\Sigma$ for small relative to large galaxy samples.
-At sufficiently large stellar mass $\mstar\gtrsim10^{11}\msun,$ when $F_{\rm sat}\lesssim10\%,$ the role of centrals becomes dominant; the $\rvir-$based model predicts that $\mhalo$ increases with $\rhalf$ for centrals, which is reflected in the reversal of the small-scale signal in the bottom left panel.
+At sufficiently large stellar mass $\mstar\gtrsim10^{11}\msun,$ when $F_{\rm sat}\lesssim10-15\%,$ the role of centrals becomes dominant; the $\rvir-$based model predicts that $\mhalo$ increases with $\rhalf$ for centrals, which is reflected in the reversal of the small-scale signal in the bottom left panel.
 
-The right panels of Figure \ref{fig:lensingprediction} compare the distributions of host halo mass for small and large samples; for centrals, $\mhost=\mhalo,$ while for satellites, $\mhost$ is the virial mass of the parent halo.
+The right panels of Figure \ref{fig:lensingprediction} compare the distributions of host halo mass, $\mhost,$ for small and large samples; for centrals, $\mhost=\mhalo,$ while for satellites, $\mhost$ is the virial mass of the parent halo.
 The peak of each distribution arises from central galaxies, while the long tail at large values of $\mhost$ is due to satellites.
-At all stellar mass, the blue histograms peak at slightly larger $\mhost$ relative the red, because the $\rvir-$based model predicts that $\mhalo$ increases with $\rhalf$ for centrals.
+At all stellar mass, the blue histograms peak at slightly larger $\mhost$ relative to the red, because the $\rvir-$based model predicts that $\mhalo$ increases with $\rhalf$ for centrals.
 For $\mstar-$complete samples, this effect only becomes dominant when the satellite fraction drops to sufficiently small values.
-Qualitatively, all of these features are completely generic predictions of the $\rvir-$based model; quantitatively, the precise value of $\mstar$ where the effect of centrals begins to dominate $\Delta\Sigma$ depends sensitively on $F_{\rm sat}(\mstar),$ which we have only roughly calibrated in the present work.
+Qualitatively, these features are completely generic predictions of the $\rvir-$based model; quantitatively, the precise value of $\mstar$ where the effect of centrals begins to dominate $\Delta\Sigma$ depends sensitively on $F_{\rm sat}(\mstar),$ which we have only roughly calibrated in the present work.
 

### 2017-11-12 paper/galsize_paper.tex
Minor changes to intro and captions

@@
 Many properties of observed galaxies exhibit remarkably tight scaling relations.
-Galaxy size, typically quantified by a half-mass or half-light radius, $\rhalf,$ has well-measured scaling with galaxy mass $\mstar$ in the local Universe \citep{shen_etal03,guo_etal09,huang_etal13,lange_etal15,zhang_yang17}, and at higher redshift \citep{trujillo_etal04,vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,huang_etal17}.
+Galaxy size, typically quantified by a half-mass or half-light radius, $\rhalf,$ has well-measured scaling with galaxy mass $\mstar$ in the local Universe \citep{shen_etal03,huang_etal13,lange_etal15,zhang_yang17}, and at higher redshift \citep{trujillo_etal04,vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,huang_etal17}.
 
-Observational constraints on models for galaxy $\rhalf$ typically come from one-point function measurements such as $\median{\rhalf}{\mstar}$ and $\sigma(\rhalf\vert\mstar),$ e.g.,  \citet{khochfar_silk06,desmond_etal17,bottrell_etal17b,hou_etal17,somerville_etal17}, or otherwise from catalogs of galaxy groups \citep{weinmann_etal08,huertas_company_etal13b,spindler_wake17}.
+Observational constraints on models for galaxy $\rhalf$ typically come from one-point function measurements such as $\median{\rhalf}{\mstar}$ and $\sigma(\rhalf\vert\mstar),$ e.g.,  \citet{khochfar_silk06,desmond_etal17,bottrell_etal17b,hou_etal17,somerville_etal17}, or otherwise from catalogs of galaxy groups \citep{weinmann_etal08,guo_etal09,huertas_company_etal13b,spindler_wake17}.
 More recently, the connection between a galaxy's size and the virial radius of its parent halo has been
@@
 
-The approach we take is to forward model the $\rhalf-$halo connection: we generate a Monte Carlo realizations of the model, and then make synthetic measurements in a manner that closely mimics the measurements we make on our observed galaxy samples.
+The approach we take is to forward model the $\rhalf-$halo connection: we generate Monte Carlo realizations of models using a high-resolution cosmological N-body simulation, and then make synthetic measurements in a manner that closely mimics the measurements we make on our observed galaxy samples.
 We describe the dataset and simulations we use in \S\ref{sec:data}, and our forward-modeling methods in \S\ref{sec:model}.
@@
 The {\em left panel} compares the stellar mass functions $\phi(\mstar)$ of the two samples, confirming that our method for separating ``small" from ``large" galaxies yields subsamples with statistically indistinguishable $\phi(\mstar)$.
-The {\em right panel} shows histograms of $\rhalf$ for the two subsamples, which partially overlap due to the finite range of $\mstar$ in the volume-limited sample.
+The {\em right panel} shows histograms of $\rhalf$ for the two subsamples, which partially overlap due to the stellar mass range spanned by the volume-limited, $\mstar$-threshold sample.
 }
@@
 {\bf Abundance matching clustering predictions.}
-Using the abundance matching methods described in \S\ref{subsec:sham}, we compare the projected clustering of mock vs.
-SDSS galaxies.
+We show the $\mstar-$dependence of projected galaxy clustering, $\wproj(\rproj),$ comparing standard abundance matching to SDSS galaxies (see \S\ref{subsec:sham} for details).
 Each panel shows the comparison for a volume-limited sample defined by a different $\mstar-$threshold.
@@
 
-\subsubsection{Satellite mass loss model}
+\subsubsection{$\mstar$ tidal-stripping model}
 \label{subsubsec:strippingmodel}
 
-\textcolor{red}{AK: I don't think the name of the model is descriptive here, but I could not yet come up with a better one.}
-In the first model we explore, we assume that stellar mass $\mstar$ controls $\rhalf,$ so that galaxy sizes are drawn from a log-normal distribution with $0.2$ dex of scatter centered at $\median{\rhalf}{\mstar}.$ To implement this model, for simplicity we tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form \citep[see, e.g.,][]{zhang_yang17}.
+In the first model we explore, we assume that stellar mass $\mstar$ controls $\rhalf,$ so that galaxy sizes are drawn from a log-normal distribution with $0.2$ dex of scatter centered at $\median{\rhalf}{\mstar}.$ To implement this model, for simplicity we tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form.
 Thus this model reproduces the observed $\rhalf-\mstar$ relation by construction.
@@
 The two gray bands enveloping the black curve show the $50\%$ and $90\%$ percentile regions.
-The blue curve shows $\rvir-$based model in which $\median{\rhalf}{\rvir}=0.01\rvir.$ This figure confirms that a linear relationship between $\rvir$ and $\rhalf$ predicts the characteristic curvature in the relation $\median{\rhalf}{\mstar}$ over a wide range in mass.
+The blue curve shows the $\rvir-$based model in which $\median{\rhalf}{\rvir}=0.01\rvir$ (see Section \ref{subsubsec:rvirmodel} for details).
 }
@@
 \caption{
-{\bf $\rhalf-$dependence of galaxy clustering: clustering ratios.}
-Closely related to Figure \ref{fig:rvir_only_clustering_absolute}, the y-axes show {\em clustering strength ratios,} defined as $(w_{\rm p}^{\rm large} - w_{\rm p}^{\rm small})/w_{\rm p}^{\rm all}.$ Thus a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass.
+{\bf $\rhalf-$dependence of galaxy clustering.}
+Closely related to Figure \ref{fig:rvir_only_clustering_absolute}, the y-axes show {\em clustering strength ratios,} defined as $\delta\wproj/\wproj\equiv(w_{\rm p}^{\rm large} - w_{\rm p}^{\rm small})/w_{\rm p}^{\rm all}.$ Thus a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass.
 Solid curves show the clustering ratio predictions of the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}.

### 2017-11-12 paper/galsize_paper.tex
Minor changes to grammar in conclusions. Added link to GitHub repo.

@@
 
-Our results can be treated as a starting point for more complex and fine-grained models of galaxy size, such as semi-analytic models and hydrodynamical simulations.
+Our results provide an integral constraint for more complex and fine-grained models of galaxy size, such as semi-analytic models and hydrodynamical simulations.
 For convenience, Figure \ref{fig:censatsizeratios} provides a simple summary statistic that can be used as a diagnostic for calibrating alternative modeling efforts.
@@
 
-Our publicly available python code provides a simple means for cosmological surveys to generate synthetic galaxy populations with realistic sizes across the cosmic web.
-Mock catalogs of $z=0$ model galaxies with $\mstar$ and $\rhalf$ will be made publicly available upon journal publication; prior to that time, our mocks are available upon request.
+Our python code is publicly available on GitHub;\footnote{\url{https://github.com/aphearin/galsize_models}} we intend for this to provide a simple means for cosmological surveys to generate synthetic galaxy populations with realistic sizes across the cosmic web.
+Tabulations of our clustering measurements, as well as catalogs of $z=0$ model galaxies with $\mstar$ and $\rhalf,$ will be made publicly available upon publication; prior to that time, our measurements and mock data are available upon request.
 
@@
 
+Work done at Argonne National Laboratory was supported under the DOE contract DE-AC02-06CH11357.
 This research was supported in part by the National Science Foundation under Grant No.
 NSF PHY11-25915.
-Work done at Argonne National Laboratory was supported under the DOE contract DE-AC02-06CH11357.
-AK was  supported by NSF grant  AST-1412107 and by the Kavli Institute for Cosmological Physics at the University of Chicago through grant PHY-1125897 and an endowment from the Kavli Foundation and its founder Fred Kavli.
+AK was  supported by NSF grant  AST-1412107, and by the Kavli Institute for Cosmological Physics at the University of Chicago through grant PHY-1125897, and an endowment from the Kavli Foundation and its founder Fred Kavli.
 

### 2017-11-12 paper/galsize_paper.tex
Improved text in section 7 on Future Directions

@@
 Since the clustering signal is strongly influenced by differences between centrals and satellites, then the satellite fraction $F_{\rm sat}(\mstar)$ plays an important role in $\rhalf-$dependent clustering.
-For {\em fixed} scaling relations $\median{\rhalf^{\rm cens}}{\mhalo}$ and $\median{\rhalf^{\rm sats}}{\mhalo},$ models with different satellite fractions will exhibit distinct $\rhalf-$clustering ratios because $F_{\rm sat}(\mstar)$ controls the relative weighting of the two populations.
+Even for {\em fixed} scaling relations $\median{\rhalf^{\rm cens}}{\mhalo}$ and $\median{\rhalf^{\rm sats}}{\mhalo},$ models with different satellite fractions will exhibit distinct $\rhalf-$clustering ratios because $F_{\rm sat}(\mstar)$ controls the relative weighting of the two populations.
 An explicit demonstration of this point appears in the Appendix, which repeats the analyses in the main body of the text, but for a subhalo catalog with no orphan correction (and therefore a different satellite fraction).
@@
 Based on our results, we advocate that empirical models for $\mean{\mstar}{\mhalo}$ be supplemented with additional model ingredients for $\median{\rhalf}{\mhalo},$ and that the parameters of the composite model be {\em jointly} constrained by measurements of the stellar mass function, $\mstar-$dependent clustering, and $\rhalf-$dependent clustering.
+Because the number of free parameters required to additionally model galaxy size are so few, such analyses will be able to exploit the additional statistical leverage provided by the $\rhalf-$dependence of $\wproj(\rproj)$ to significantly improve constraints on $F_{\rm sat}(\mstar),$ without any appeal to a group-finder.
 
-Figure \ref{fig:censatsizeratios} shows that the satellites in $\mhalo\approx10^{12}\msun$ halos can be as large as $\lesssim40-50\%$ smaller than their central galaxy counterparts.
+Figure \ref{fig:censatsizeratios} shows that satellites in $\mhalo\approx10^{12}\msun$ halos are $\sim25-40\%$ smaller than their central galaxy counterparts.
 Since the satellite fraction varies quite significantly with morphology and/or color, we have demonstrated that it is entirely plausible that most of the observed environmental trends of galaxy size can be understood simply in terms of central vs.
 satellite size differences.
-The latter reflects not evolution of galaxies inside host halos, but is due to the fact that satellites have reached their peak mass at higher redshifts than the centrals.
-While it remains to be seen whether this explanation ends up comprising the whole story, one thing is now clear: it is not possible to reliably analyze environmental trends of galaxy $\rhalf$ without properly accounting for satellites.
+These differences are likely not driven by satellite-specific processes inside host halos, but instead are primarily due to the fact that satellites have reached their peak mass at higher redshifts than centrals.
+While it remains to be seen whether these statistical principles alone are sufficient to capture all the elementary trends that galaxy two-point functions exhibit with galaxy size, morphology and color, one thing is now clear: it is not possible to reliably analyze environmental trends of galaxy $\rhalf$ without properly accounting for satellites.
 

### 2017-11-12 paper/galsize_paper.tex
Improved clarity of discussion of group-finder systematics in Section 6 on Related Work

@@
 Using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}, in the {\em left panels} we show predictions for as-yet-unseen measurements of the $\rhalf-$dependence of galaxy lensing of $\mstar-$complete samples, where ``small" and ``large" subsamples are defined as in \S\ref{subsec:sizedef}.
-To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which the trends shown here are reversed and weakened: for both blue and red samples, the observed $\Delta\Sigma$ of large galaxies is (slightly) stronger relative to small galaxies.
+To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which are reversed and weaker than the trends predicted here: for both blue and red samples, the observed $\Delta\Sigma$ of large galaxies is (slightly) stronger relative to small galaxies.
 As a generic consequence of satellites being smaller than centrals of the same mass, we predict that future lensing measurements of $\mstar-$complete samples will show $\Delta\Sigma$ of small galaxies to be significantly stronger relative to large galaxies of the same stellar mass $\mstar\lesssim10^{11}\msun.$ We additionally predict that at sufficiently large mass $\mstar\gtrsim10^{11}\msun,$ the trend of small-scale $\Delta\Sigma$ with $\rhalf$ should reverse sign.
@@
 
-As shown in \citet{campbell_etal15}, group-finding methods are subject to significant systematics, particularly when analyzing trends based on color: contemporary algorithms {\em generically} wash out differences between centrals and satellites; trends can even be artificially created that are not truly present.
-Our forward modeling inference technique is not subject to such systematics because our methods are entirely outwith the group-finding framework, and so it is encouraging that our findings are commensurable with these results.
+Group-finding methods are subject to significant systematics, the most severe of which are caused by the fracturing of a massive halo's galaxies into multiple small groups, and the fusing of small halos into an apparently large group \citep{duarte_mamon14}.
+As shown in \citet{campbell_etal15}, these effects can significantly bias attempts to infer trends in the galaxy--halo connection directly from group catalogs.
+The chief source of these  biases is that the frequency of fracturing and fusing has significant dependence upon large-scale density, as do galaxy properties such as color and morphology.
+The correlation between group misidentification rate and galaxy properties would be quite challenging to model analytically, but these systematics damage the robustness of the inference: contemporary algorithms {\em generically} wash out differences between centrals and satellites; trends can even be artificially created that are not truly present.
+
+ Our forward modeling inference technique is not subject to such systematics because our methods are entirely outwith the group-finding framework, and so it is encouraging that our conclusions are commensurable with group-based results.
 Once galaxies have been color-selected, Figure \ref{fig:colorclustering} shows that the observed clustering trends nearly vanish in magnitude, and reverse sign.
@@
 
-The right panels of Figure \ref{fig:lensingprediction} compare the distributions of host halo mass, $\mhost,$ for small and large samples; for centrals, $\mhost=\mhalo,$ while for satellites, $\mhost$ is the virial mass of the parent halo.
+The right panels of Figure \ref{fig:lensingprediction} compare the distributions of host halo mass, $\mhost,$ for small and large samples;\footnote{We calculated the PDFs shown in Figure \ref{fig:lensingprediction} using the Scipy implementation of Gaussian kernel density estimation \citep{scipy}.} for centrals, $\mhost=\mhalo,$ while for satellites, $\mhost$ is the virial mass of the parent halo.
 The peak of each distribution arises from central galaxies, while the long tail at large values of $\mhost$ is due to satellites.
-At all stellar mass, the blue histograms peak at slightly larger $\mhost$ relative to the red, because the $\rvir-$based model predicts that $\mhalo$ increases with $\rhalf$ for centrals.
+At all stellar mass, the blue histograms peak at slightly larger $\mhost$ relative to the red; this is because the $\rvir-$based model predicts that $\mhalo$ increases with $\rhalf$ for centrals.
 For $\mstar-$complete samples, this effect only becomes dominant when the satellite fraction drops to sufficiently small values.

### 2017-11-13 paper/galsize_paper.tex
Added paragraph to Future Work making clear the importance of forward-modeling B/T for self-consistent treatment of 2d vs. 3d sizes

@@
 
+In ongoing follow-up work, we are extending the current analysis by jointly modeling stellar mass and sizes together with a bulge/disk decomposition of model galaxies quantified by ${\rm B/T},$ the fraction of the total stellar mass in the bulge.
+Forward modeling methods for ${\rm B/T}$ offer potential to significantly improve upon several aspects of current analysis techniques.
+For example, it is common to ``deproject" two-dimensional sizes of observed galaxies to estimate three-dimensional sizes; such a correction applied to the data requires treating disk-dominated and spheroidal systems separately.
+The forward modeling approach turns the direction of this correction around: three-dimensional sizes of disk and bulge components are modeled separately, and for each model galaxy the projected size can be computed self-consistently with the modeled value of ${\rm B/T}.$ This follow-up analysis will also help robustly quantify the extent to which the ``cause" of satellites having smaller sizes than centrals is due to differences in ${\rm B/T}.$
+
 Figure \ref{fig:censatsizeratios} shows that satellites in $\mhalo\approx10^{12}\msun$ halos are $\sim25-40\%$ smaller than their central galaxy counterparts.

### 2017-11-13 paper/galsize_paper.tex
Incorporated all textual changes suggested by Peter Behroozi

@@
 Other simple empirical models fail the clustering test, such as models in which galaxy size is related to stellar mass alone; these failures persist even when accounting for possible effects from satellite stripping and orphan galaxies.
-Our results suggest that the relative size of centrals and satellites is predetermined at the time of satellite infall, and that a remarkably simple galaxy--halo scaling relation emerges from the complex physics regulating galaxy size.
+Our results suggest that the relative size of centrals and satellites could be predetermined at the time of satellite infall, and that a remarkably simple galaxy--halo scaling relation emerges from the complex physics regulating galaxy size.
 \end{abstract}
@@
 Many properties of observed galaxies exhibit remarkably tight scaling relations.
-Galaxy size, typically quantified by a half-mass or half-light radius, $\rhalf,$ has well-measured scaling with galaxy mass $\mstar$ in the local Universe \citep{shen_etal03,huang_etal13,lange_etal15,zhang_yang17}, and at higher redshift \citep{trujillo_etal04,vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,huang_etal17}.
+Galaxy size, typically quantified by a half-mass or half-light radius, $\rhalf,$ has well-measured scaling with galaxy mass $\mstar$ in the local Universe \citep{shen_etal03,huang_etal13,lange_etal15,zhang_yang17}, and at higher redshift \citep{trujillo_etal04,vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,shibuya_etal15,huang_etal17}.
 
@@
 
-Using galaxies from Data Release 10 of the Sloan Digital Sky Survey \citep[SDSS,][]{ahn_etal14} with the stellar mass measurements taken from the MPA-JHU catalog \citep{kauffmann_etal03,brinchmann_etal04}, we define volume-limited samples of galaxies according to the same $\mstar-$completeness cuts used in \citet{behroozi_etal15} (see Figure 2).
+The starting point for our galaxy samples comes from Data Release 10 of the Sloan Digital Sky Survey \citep[SDSS,][]{ahn_etal14}, with the stellar mass measurements taken from the MPA-JHU catalog \citep{kauffmann_etal03,brinchmann_etal04}.
+Discarding galaxies with redshift $z<0.02,$ we define volume-limited, $\mstar-$threshold samples by applying a maximum-redshift cut $z_{\rm max}$ appropriate for the $\mstar$ threshold; we use the same $z_{\rm max}$ cut shown in Figure 2 of \citet{behroozi_etal15}.
+
 We supplement the MPA-JHU catalog with measurements of half-light radius, $\rhalf,$ derived from galaxy profile decompositions provided by \citet{meert_etal15}.
@@
 
-As the bedrock of our modeling, we use the publicly available\footnote{\url{http://www.slac.stanford.edu/~behroozi/BPlanck\_Hlists}} catalog of {\tt Rockstar} subhalos identified at $z=0$ in the Bolshoi-Planck simulation \citep{klypin_etal11,behroozi12_rockstar,riebe_etal13,behroozi_etal12b,rodriguez_puebla16_bolplanck}.
+As the bedrock of our modeling, we use the publicly available\footnote{\url{http://www.slac.stanford.edu/~behroozi/BPlanck\_Hlists}} catalog of {\tt Rockstar} subhalos identified at $z=0$ in the Bolshoi-Planck simulation \citep{klypin_etal11,klypin_etal16,behroozi12_rockstar,riebe_etal13,behroozi_etal12b,rodriguez_puebla16_bolplanck}.
 As described in \S\ref{subsec:sham}, we use traditional abundance matching to connect stellar mass $\mstar$ with subhalo mass.
 To address issues related to subhalo incompleteness \citep{guo_white13,campbell_etal17}, we supplement the Bolshoi-Planck subhalo catalog with subhalos that have been disrupted and no longer appear in the standard catalog as $z=0$ surviving subhalos.
-We describe our treatment of these ``orphan" subhalos in the Appendix.
+We describe our treatment of these ``orphan" subhalos in the Appendix, where we also show results that exclude all orphan subhalos.
 
 For our SDSS galaxy samples, we calculate two-point clustering $\wproj$ using line-of-sight projection of $\pi_{\rm max}=20~\mpc$ using the {\tt correl} program in {\tt UniverseMachine}.
+The {\tt correl} code uses the \citet{landy_szalay93} estimator ($DD - 2DR + RR$) to compute the redshift-space correlation function $\xi(\rproj, \pi)$, which is then integrated over $\vert\pi\vert < 20$ Mpc to compute the projected correlation function $\wproj(\rproj)$.
+The code uses $10^6$ randoms drawn from the same mask region with uniform volume distribution to compute $DR$, and $RR$ is computed via Monte Carlo integration.
+Errors are estimated by jackknife resampling, giving us an estimate for the lower bound of samples with volumes $V_{\rm eff}\lesssim 0.3{\rm Gpc}^3.$
+
 For mock galaxies, we compute $\wproj$ using the {\tt mock\_observables.wp} function in {\tt Halotools} \citep{hearin_etal16}, which is a python implementation of the algorithm in the {\tt Corrfunc} C library \citep{sinha_etal17}.
@@
 See Section 3.3 of \citet{behroozi_etal10}, or the appendix of \citet{kravtsov_etal14}, for an account of the mathematics underlying this technique in the presence of scatter.
-To perform the abundance matching, we use the publicly available code\footnote{\url{https://bitbucket.org/yymao/abundancematching/overview}} developed by Yao-Yuan Mao \citep{lehmann_etal15} that provides a python wrapper around the C kernel developed by Peter Behroozi \citep{behroozi_etal10}.
+To perform the abundance matching, we use the publicly available code\footnote{\url{https://bitbucket.org/yymao/abundancematching/overview}} developed by Yao-Yuan Mao \citep{lehmann_etal15} that provides a python wrapper around the C kernel developed in \citep{behroozi_etal10}.
 For the subhalo property used in SHAM, we use $\mpeak,$ the largest value of $\mvir$ ever attained by the subhalo throughout the entire history of the main progenitor halo.
-Using the stellar mass function provided in \citet{moustakas_etal13}, we model $\mstar$ as a log-normal distribution with $0.2$dex of scatter about the median relation $\median{\mstar}{\mpeak}$ determined by SHAM.
+Using the stellar mass function provided in \citet{moustakas_etal13}, we model $\mstar$ as a log-normal distribution with $0.2$dex of scatter about the median relation $\median{\mstar}{\mpeak}$ determined by SHAM \citep{reddick_etal13}.
 As described in the appendix, we include a prescription for supplementing the ordinary {\tt Rockstar} subhalo catalog with disrupted subhalos, so that some of our model galaxies inhabit subhalos that are no longer resolved and do not appear in the standard publicly available catalog.
@@
 Figure \ref{fig:baseline_sham_clustering} shows that our implementation of SHAM produces model galaxies whose projected clustering, $\wproj(\rproj)$, is in reasonably good agreement with SDSS galaxies.
-We note, however, that $\wproj(\rproj\gtrsim1{\rm Mpc})$ is $\sim10-20\%$ too weak at stellar mass $\mstar\gtrsim10^{10.75}\msun,$ and similarly on all scales for the $\mstar\gtrsim10^{9.75}\msun$ sample.
+We note, however, that $\wproj(\rproj\gtrsim1{\rm Mpc})$ is $\sim10-20\%$ too weak at stellar mass $\mstar\gtrsim10^{10.75}\msun,$ and similarly on all scales for the $\mstar\gtrsim10^{9.75}\msun$ sample, although the statistical significance of this discrepancy is likely rather mild due to the sample variance of SDSS galaxies with $z\lesssim0.05.$
 
@@
 
-\subsubsection{$\mstar$ tidal-stripping model}
+\subsubsection{Tidal stripping model}
 \label{subsubsec:strippingmodel}
 
-In the first model we explore, we assume that stellar mass $\mstar$ controls $\rhalf,$ so that galaxy sizes are drawn from a log-normal distribution with $0.2$ dex of scatter centered at $\median{\rhalf}{\mstar}.$ To implement this model, for simplicity we tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form.
+In the first model we explore, we assume that stellar mass $\mstar$ controls $\rhalf.$ To implement this model, for simplicity we tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form.
 Thus this model reproduces the observed $\rhalf-\mstar$ relation by construction.
+In order to ensure that the model has a level of scatter in $\rhalf$ at fixed $\mstar$ that is comparable to the level reported in \citet{somerville_etal17}, our model sizes are drawn from a log-normal distribution with $0.2$ dex of scatter centered at $\median{\rhalf}{\mstar}.$
 
@@
 In this way, we model satellite mass loss and  size truncation in a manner that mimics what is seen in hydrodynamical simulations.
+As shown in \citet{smith_etal16}, stellar stripping does not begin until $f_{\rm DM}<0.2,$ and the DM halo needs to be stripped to $5\%$ of its initial mass for $50\%$ of stars to be stripped.
 
@@
 where for $\Delta_{\rm vir}(\zpeak)$ we use the fitting function to the ``virial" definition used in \citet{bryan_norman98}.
-For the model we refer to as the ``$\rvir-$based model", we add uncorrelated log-normal scatter of $\sigmarhalf=0.2$ dex to generate a Monto Carlo realization of the model population.
+This modeling assumption effectively defines $\median{\rhalf}{\mhalo};$ this relation defines the center of the log-normal distribution with $0.2$ dex of scatter that we use to generate a Monto Carlo realization of the model population.
 
@@
 However, the magnitude of the effect is not sufficiently strong  to produce clustering predictions that are consistent with observations.
+
+Due to the shape of ${\rm d}\rhalf/{\rm d}\mstar,$ low-mass satellites have to lose much more halo mass than high-mass satellites in order to get pushed into the small-$\rhalf$ sample.
+Thus even though there are more satellites at lower masses, the shape of ${\rm d}\rhalf/{\rm d}\mstar$ counteracts this trend, making the mass-dependence of the observed signal shown in Figure \ref{fig:mstarmodelclustering} difficult to explain by appealing to tidal stripping.
 Evidently it is difficult to strip enough mass from satellites so that the $\rhalf-$dependent clustering predictions are in agreement with observations.
@@
 
-While we consider such an explanation plausible, and even likely, a conclusive confirmation requires proper forward modeling of size and color jointly.
+While we consider such a hypothesis plausible, and even likely, a conclusive confirmation requires proper forward modeling of size and color jointly.
 Such an effort is well motivated by our results, but is beyond the scope of the present work.
@@
 
-The success of the $\rvir$-based model in explaining the size dependence of galaxy clustering implies that the sizes of {\it all} galaxies,  red, blue, spheroid, disks, satellites and central, are, on average, proportional to the $\rmpeak,$ the physical size of the virial radius at the time at which $\mhalo$ stops growing.
+The success of the $\rvir$-based model in explaining the size dependence of galaxy clustering may be explained if the sizes of {\it all} galaxies, red, blue, spheroid, disks, satellites and central, are, on average, proportional to the $\rmpeak,$ the physical size of the virial radius at the time at which $\mhalo$ stops growing.
 Although correlation is not necessarily causation, such a universal and simple dependence poses a useful challenge to fine-grained galaxy formation models, as it indicates a tight connection between the growth of galaxies and their host halos.
@@
 The phase space evolution of disrupted subhalos is approximated by following a point mass evolving in the host halo potential according to the orbital parameters of the subhalo at the time of disruption; the evolution of subhalo mass and circular velocity is approximated using the semi-analytic model presented in \citet{jiang_vdB14}.
-We then use the {\tt orphans} program in {\tt UniverseMachine} to walk through all the Bolshoi-Planck {\tt hlist} files, yielding the main progenitor information of every subhalo that was ever identified by {\tt Consistent Trees}.
+We then use the {\tt extract\_orphans} program in {\tt UniverseMachine} to walk through all the Bolshoi-Planck {\tt hlist} files, yielding the main progenitor information of every subhalo that was ever identified by {\tt Consistent Trees}.
 

### 2017-11-13 paper/galsize_paper.tex
Updated Figure 1 with a scatter plot

@@
 \centering
+\includegraphics[width=9cm]{FIGS/sdss_size_vs_mstar_scatter.pdf}
 \includegraphics[width=\textwidth]{FIGS/sdss_small_large_sample_definitions.pdf}
 \caption{
-{\bf Definition of ``small" and ``large" galaxies.} For a volume-limited SDSS galaxy sample defined by $M_{\ast}>10^{10.25}M_{\odot},$ we visually demonstrate how we classify galaxies into ``small" and ``large" subsamples.
+{\bf Definition of ``small" and ``large" galaxies.} For a volume-limited SDSS galaxy sample defined by $M_{\ast}>10^{10.25}M_{\odot},$ the {\em top panel} visually demonstrates how we classify galaxies into ``small" and ``large" subsamples.
 As described in detail in \S\ref{subsec:sizedef}, we compute the median value $\median{\rhalf}{\mstar}$ at the stellar mass of each galaxy in the sample, and divide the sample into two based on this $\mstar-$dependent cut.
-The {\em left panel} compares the stellar mass functions $\phi(\mstar)$ of the two samples, confirming that our method for separating ``small" from ``large" galaxies yields subsamples with statistically indistinguishable $\phi(\mstar)$.
-The {\em right panel} shows histograms of $\rhalf$ for the two subsamples, which partially overlap due to the stellar mass range spanned by the volume-limited, $\mstar$-threshold sample.
+The {\em bottom left panel} compares the stellar mass functions $\phi(\mstar)$ of the two samples, confirming that our method for separating ``small" from ``large" galaxies yields subsamples with statistically indistinguishable $\phi(\mstar)$.
+The {\em bottom right panel} shows histograms of $\rhalf$ for the two subsamples, which partially overlap due to the stellar mass range spanned by the volume-limited, $\mstar$-threshold sample.
 }
@@
 Using this technique, for any $\mstar-$threshold sample, the stellar mass function of the ``large" and ``small" subsamples are identical.
-We illustrate this for the particular case of $\mstar>10^{10.25}\msun$ in left panel of Figure~\ref{fig:sizedefinition}, which shows stellar mass functions for the two subsamples.
-The right panel of Figure~\ref{fig:sizedefinition} compares histograms of the two size distributions of these subsamples, which partially overlap due to the variation in $\median{\rhalf}{\mstar}$ across the $\mstar-$ range of the threshold sample.
+We illustrate this for the particular case of $\mstar>10^{10.25}\msun$ in bottom left panel of Figure~\ref{fig:sizedefinition}, which shows stellar mass functions for the two subsamples.
+The bottom right panel of Figure~\ref{fig:sizedefinition} compares histograms of the two size distributions of these subsamples, which partially overlap due to the variation in $\median{\rhalf}{\mstar}$ across the $\mstar-$ range of the threshold sample.
 

### 2017-11-13 paper/galsize_paper.tex
Fixed a few references

@@
 
-Observational constraints on models for galaxy $\rhalf$ typically come from one-point function measurements such as $\median{\rhalf}{\mstar}$ and $\sigma(\rhalf\vert\mstar),$ e.g.,  \citet{khochfar_silk06,desmond_etal17,bottrell_etal17b,hou_etal17,somerville_etal17}, or otherwise from catalogs of galaxy groups \citep{weinmann_etal08,guo_etal09,huertas_company_etal13b,spindler_wake17}.
+Observational constraints on models for galaxy $\rhalf$ typically come from one-point function measurements such as $\median{\rhalf}{\mstar}$ and $\sigma(\rhalf\vert\mstar),$ e.g.,  \citet{khochfar_silk06,lang_etal14,desmond_etal17,bottrell_etal17b,hou_etal17,somerville_etal17}, or otherwise from catalogs of galaxy groups \citep{weinmann_etal08,guo_etal09,huertas_company_etal13b,spindler_wake17}.
 More recently, the connection between a galaxy's size and the virial radius of its parent halo has been

### 2017-11-13 paper/galsize_paper.tex
Minor corrections after re-reading draft

@@
 Many properties of observed galaxies exhibit remarkably tight scaling relations.
-Galaxy size, typically quantified by a half-mass or half-light radius, $\rhalf,$ has well-measured scaling with galaxy mass $\mstar$ in the local Universe \citep{shen_etal03,huang_etal13,lange_etal15,zhang_yang17}, and at higher redshift \citep{trujillo_etal04,vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,shibuya_etal15,huang_etal17}.
+Galaxy size, typically quantified by a half-mass or half-light radius, $\rhalf,$ has well-measured scaling with galaxy mass $\mstar$ in the local Universe \citep{shen_etal03,huang_etal13,lange_etal15,zhang_yang17}, and at higher redshift \citep{trujillo_etal04,vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,huang_etal17}.
 
@@
 
-The starting point for our galaxy samples comes from Data Release 10 of the Sloan Digital Sky Survey \citep[SDSS,][]{ahn_etal14}, with the stellar mass measurements taken from the MPA-JHU catalog \citep{kauffmann_etal03,brinchmann_etal04}.
+The starting point for our galaxy samples comes from Data Release 10 of the Sloan Digital Sky Survey \citep[SDSS,][]{ahn_etal14}, with stellar mass measurements taken from the MPA-JHU catalog \citep{kauffmann_etal03,brinchmann_etal04}.
 Discarding galaxies with redshift $z<0.02,$ we define volume-limited, $\mstar-$threshold samples by applying a maximum-redshift cut $z_{\rm max}$ appropriate for the $\mstar$ threshold; we use the same $z_{\rm max}$ cut shown in Figure 2 of \citet{behroozi_etal15}.
@@
 In the version of this catalog that we use,\footnote{Our $\mstar$ and $\rhalf$ measurements are derived from different photometry pipelines; this is driven by our desire for consistency with the \citet{behroozi_etal15} completeness cuts used in our clustering measurements.
-We note that we have repeated our analysis for stellar mass measurements based on \citet{meert_etal15}, finding only minor quantitative, and no qualitative changes to our results.} two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile to determine the half-light radius of total $r-$band luminosity, $\rhalf.$
+We note that we have repeated our analysis for stellar mass measurements based on \citet{meert_etal15}, finding only minor quantitative, and no qualitative changes to our results.} two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile to determine the projected half-light radius of total $r-$band luminosity, $\rhalf.$
 
@@
 See Section 3.3 of \citet{behroozi_etal10}, or the appendix of \citet{kravtsov_etal14}, for an account of the mathematics underlying this technique in the presence of scatter.
-To perform the abundance matching, we use the publicly available code\footnote{\url{https://bitbucket.org/yymao/abundancematching/overview}} developed by Yao-Yuan Mao \citep{lehmann_etal15} that provides a python wrapper around the C kernel developed in \citep{behroozi_etal10}.
+To perform the abundance matching, we use the publicly available code\footnote{\url{https://bitbucket.org/yymao/abundancematching/overview}} developed by Yao-Yuan Mao \citep{lehmann_etal15} that provides a python wrapper around the C kernel developed in \citet{behroozi_etal10}.
 For the subhalo property used in SHAM, we use $\mpeak,$ the largest value of $\mvir$ ever attained by the subhalo throughout the entire history of the main progenitor halo.
@@
 
-Figure \ref{fig:baseline_sham_clustering} shows that our implementation of SHAM produces model galaxies whose projected clustering, $\wproj(\rproj)$, is in reasonably good agreement with SDSS galaxies.
+Figure \ref{fig:baseline_sham_clustering} shows that our implementation of SHAM produces model galaxies whose projected clustering is in reasonably good agreement with SDSS galaxies.
 We note, however, that $\wproj(\rproj\gtrsim1{\rm Mpc})$ is $\sim10-20\%$ too weak at stellar mass $\mstar\gtrsim10^{10.75}\msun,$ and similarly on all scales for the $\mstar\gtrsim10^{9.75}\msun$ sample, although the statistical significance of this discrepancy is likely rather mild due to the sample variance of SDSS galaxies with $z\lesssim0.05.$
@@
 
-In the first model we explore, we assume that stellar mass $\mstar$ controls $\rhalf.$ To implement this model, for simplicity we tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form.
-Thus this model reproduces the observed $\rhalf-\mstar$ relation by construction.
-In order to ensure that the model has a level of scatter in $\rhalf$ at fixed $\mstar$ that is comparable to the level reported in \citet{somerville_etal17}, our model sizes are drawn from a log-normal distribution with $0.2$ dex of scatter centered at $\median{\rhalf}{\mstar}.$
+In the first model we explore, we assume that stellar mass $\mstar$ controls $\rhalf.$ To implement this model, for simplicity we tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form, so that this model reproduces the observed $\rhalf-\mstar$ relation by construction.
+In order to ensure that the model has a level of scatter in $\rhalf$ at fixed $\mstar$ that is comparable to the level reported in \citet{somerville_etal17}, our model sizes are drawn from a log-normal distribution with $0.2$ dex of scatter centered at the observed $\median{\rhalf}{\mstar}.$
 
@@
 In this way, we model satellite mass loss and  size truncation in a manner that mimics what is seen in hydrodynamical simulations.
-As shown in \citet{smith_etal16}, stellar stripping does not begin until $f_{\rm DM}<0.2,$ and the DM halo needs to be stripped to $5\%$ of its initial mass for $50\%$ of stars to be stripped.
+As shown in \citet{smith_etal16}, stellar stripping in this model does not begin until $f_{\rm DM}\lesssim0.2,$ and the DM halo needs to be stripped to $\sim5\%$ of its initial mass for $\sim50\%$ of stars to be stripped.
 
@@
 \label{eq:fiducial_model}
-\rhalf = 0.01\rvir.
+\rhalf = 0.01\rvir
 \eeq
-For the virial radius of halos and subhalos, we use $\rmpeak:$ the value of $\rvir$ in physical units of $\kpc$ measured at the time when halo mass reached its maximum, $\zpeak.$  The relationship between $\rmpeak$ and $\mpeak$ is given by
+For the virial radius of halos and subhalos, we use $\rmpeak:$ the value of $\rvir$ in physical units of $\kpc$ measured at the time when halo mass reached its maximum, $\zpeak.$  The relationship between $\rmpeak, \mpeak$ and $\zpeak$ is given by
 \beq
@@
 In the previous section, comparing model predictions to the observed size dependence of galaxy clustering produced two intriguing results.
-First, the model that assumes $\rhalf\propto\rvir$ predicts a dependence of both the amplitude and shape of  galaxy correlation functions on size remarkably well, especially considering that the model nominally has only one free parameter: the normalization of the linear $\rhalf-\rvir$ relation.
+First, the model that assumes $\rhalf\propto\rvir$ predicts a dependence of both the amplitude and shape of  size-dependent galaxy correlation functions remarkably well, especially considering that the model nominally has only one free parameter: the normalization of the linear $\rhalf-\rvir$ relation.
 At the same time, small galaxies cluster more strongly relative to large, which seems at odds with naive expectations that, within such a model, larger sizes correspond to larger halo masses, $\rvir\propto\mvir^{1/3}$, and so larger sizes should be clustered more strongly.
@@
 Thus we can expect that in this model, satellite galaxies will have smaller sizes than  central galaxies hosted by halos of similar mass.
-Indeed, Figure \ref{fig:censatsizehist} shows the $\rhalf$ distributions of central, satellite, and ``splashback'' central galaxies hosted by halos of the same mass, $\mhalo\equiv\mpeak\approx10^{12}\msun.$ A ``splashback central"  is defined as a present-day central galaxy that used to be a satellite, i.e., its main progenitor halo passed inside the virial radius of a larger halo at some point in its past history.
+Indeed, Figure \ref{fig:censatsizehist} shows the $\rhalf$ distributions of central, satellite, and ``splashback'' central galaxies living in subhalos of the same mass, $\mhalo\equiv\mpeak\approx10^{12}\msun.$ A ``splashback central"  is defined as a present-day central galaxy that used to be a satellite, i.e., its main progenitor halo passed inside the virial radius of a larger halo at some point in its past history.
 On the other hand, we define a ``true central" as a galaxy that has never been a satellite.
-The figure shows that there is a clear trend of sizes decreasing from the central to splashback and to satellite galaxies.
+The figure shows that there is a clear trend of sizes decreasing from the central to splashback to satellite galaxies.
 
@@
 
-We can also understand how the observed $\rhalf-$dependent clustering scales with $\mstar$ (shown by comparing different panels in Figure \ref{fig:clustering_ratio_upshot}) in terms of the differences of sizes of central and satellites galaxies.
+We can also understand how the observed $\rhalf-$dependent clustering scales with $\mstar$ (shown by comparing different panels in Figure \ref{fig:clustering_ratio_upshot}) in terms of the different of size of centrals and satellites.
 The satellite fraction $F_{\rm sat}(\mstar)$ decreases as $\mstar$ increases \citep[e.g.,][]{guo_etal11,reddick_etal13}.
 As $F_{\rm sat}$ decreases, there are fewer satellites available to preferentially weight the subsample of smaller galaxies.
-Thus,  high $\mstar$ samples consist mostly of central galaxies, and the split by size no longer corresponds to the split into satellite- and central-dominated samples.
-The size dependence of clustering correspondingly weakens and nearly disappears for samples with largest $\mstar$.
+Thus,  high-$\mstar$ samples consist mostly of central galaxies, and the split by size no longer corresponds to the split into satellite- and central-dominated samples.
+The size dependence of clustering correspondingly weakens and nearly disappears for samples with large $\mstar$.
 
@@
 Pre-selecting galaxy samples by color then naturally restricts the impact of satellites on size-dependent clustering.
-For blue galaxies, the reason traces to the small value of $F_{\rm sat};$ for red galaxies, the reason traces to the limited dynamic range of halo masses occupied by the satellites.
+For blue galaxies, the reason traces to the small value of $F_{\rm sat};$ for red galaxies, the reason traces to the limited dynamic range of host halo masses occupied by the satellites.
 With the impact of satellites reduced, the relative clustering of centrals becomes more important.
@@
 
-The success of the $\rvir$-based model in explaining the size dependence of galaxy clustering may be explained if the sizes of {\it all} galaxies, red, blue, spheroid, disks, satellites and central, are, on average, proportional to the $\rmpeak,$ the physical size of the virial radius at the time at which $\mhalo$ stops growing.
+The success of the $\rvir$-based model in predicting the size dependence of galaxy clustering may be explained if the sizes of {\it all} galaxies, red, blue, spheroid, disks, satellites and central, are, on average, proportional to the $\rmpeak,$ the physical size of the virial radius at the time at which $\mhalo$ stops growing.
 Although correlation is not necessarily causation, such a universal and simple dependence poses a useful challenge to fine-grained galaxy formation models, as it indicates a tight connection between the growth of galaxies and their host halos.
@@
 For both red- and blue-sequence galaxies, it was found in \citet{charlton_etal17} that the lensing signal, $\Delta\Sigma,$ of large galaxies is slightly stronger relative to smaller galaxies.
-This result is in good agreement with the clustering measurements in the top panels of Figure \ref{fig:colorclustering}, which show the same trend.
+This result is in good agreement with the clustering measurements in Figure \ref{fig:colorclustering}, which show the same trend.
 
@@
 Our methodology is closely aligned with \citet{somerville_etal17}, who studied the empirical modeling features that are necessary to recover the tight scatter in the observed $\mean{\rhalf}{\mstar}$ relation.
-By building models where $\rhalf$ is set by halo spin $\lambda_{\rm halo}$, the authors in \citet{somerville_etal17} found that the level of intrinsic scatter about $\langle\lambda_{\rm halo}\vert\mhalo\rangle$ in dark matter halos is at least as large as the scatter about $\langle\rhalf\vert\mstar\rangle$ seen in observed galaxies.
+By building models where $\rhalf$ is set by halo spin $\lambda_{\rm halo}$, it was found in \citet{somerville_etal17} that the level of intrinsic scatter about $\langle\lambda_{\rm halo}\vert\mhalo\rangle$ in dark matter halos is at least as large as the scatter about $\langle\rhalf\vert\mstar\rangle$ seen in observed galaxies.
 In our approach, the level of scatter is simply a modeling parameter whose fiducial value was motivated by \citet{somerville_etal17}.
@@
 Since the clustering signal is strongly influenced by differences between centrals and satellites, then the satellite fraction $F_{\rm sat}(\mstar)$ plays an important role in $\rhalf-$dependent clustering.
-Even for {\em fixed} scaling relations $\median{\rhalf^{\rm cens}}{\mhalo}$ and $\median{\rhalf^{\rm sats}}{\mhalo},$ models with different satellite fractions will exhibit distinct $\rhalf-$clustering ratios because $F_{\rm sat}(\mstar)$ controls the relative weighting of the two populations.
+Even for {\em fixed} scaling relations $\median{\rhalf^{\rm cens}}{\mhalo}$ and $\median{\rhalf^{\rm sats}}{\mhalo},$ models with different satellite fractions will exhibit distinct $\rhalf-$clustering ratios, because $F_{\rm sat}(\mstar)$ controls the relative weighting of the two populations.
 An explicit demonstration of this point appears in the Appendix, which repeats the analyses in the main body of the text, but for a subhalo catalog with no orphan correction (and therefore a different satellite fraction).
@@
 
-In ongoing follow-up work, we are extending the current analysis by jointly modeling stellar mass and sizes together with a bulge/disk decomposition of model galaxies quantified by ${\rm B/T},$ the fraction of the total stellar mass in the bulge.
+In ongoing follow-up work, we are extending the current analysis by jointly modeling stellar mass and size together with a bulge/disk decomposition of model galaxies quantified by ${\rm B/T},$ the fraction of the total stellar mass in the bulge.
 Forward modeling methods for ${\rm B/T}$ offer potential to significantly improve upon several aspects of current analysis techniques.
-For example, it is common to ``deproject" two-dimensional sizes of observed galaxies to estimate three-dimensional sizes; such a correction applied to the data requires treating disk-dominated and spheroidal systems separately.
-The forward modeling approach turns the direction of this correction around: three-dimensional sizes of disk and bulge components are modeled separately, and for each model galaxy the projected size can be computed self-consistently with the modeled value of ${\rm B/T}.$ This follow-up analysis will also help robustly quantify the extent to which the ``cause" of satellites having smaller sizes than centrals is due to differences in ${\rm B/T}.$
+For example, it is common to de-project two-dimensional sizes of observed galaxies to estimate three-dimensional sizes; such a correction applied to the data requires treating disk-dominated and spheroidal systems separately.
+The forward modeling approach turns the direction of this correction around: three-dimensional sizes of disk and bulge components are modeled separately; the projected size can then be computed self-consistently with the modeled value of ${\rm B/T},$ permitting a more apples-to-apples comparison to observations of projected size.
+This follow-up analysis will also help robustly quantify the extent to which the ``cause" of satellites being smaller than centrals is due to differences in ${\rm B/T}.$
 
@@
 
-Our python code is publicly available on GitHub;\footnote{\url{https://github.com/aphearin/galsize_models}} we intend for this to provide a simple means for cosmological surveys to generate synthetic galaxy populations with realistic sizes across the cosmic web.
+Our python code has been publicly available on GitHub\footnote{\url{https://github.com/aphearin/galsize_models}} since the inception of the project; we intend for this code to provide a simple means for cosmological surveys to generate synthetic galaxy populations with realistic sizes across the cosmic web.
 Tabulations of our clustering measurements, as well as catalogs of $z=0$ model galaxies with $\mstar$ and $\rhalf,$ will be made publicly available upon publication; prior to that time, our measurements and mock data are available upon request.
@@
 
-We thank the {\tt Astropy} developers for the package-template \citep{astropy}, and {\tt NumPy} \citep{numpy_ndarray}, {\tt SciPy} \citep{scipy}, IPython, Matplotlib, and GitHub for their extremely useful free software.
+We thank the {\tt Astropy} developers for the package-template \citep{astropy}, as well as the developers of {\tt NumPy} \citep{numpy_ndarray}, {\tt SciPy} \citep{scipy}, Jupyter \citep{jupyter}, IPython \citep{ipython}, Matplotlib \citep{matplotlib}, and GitHub for their extremely useful free software.
 While writing this paper we made extensive use of the Astrophysics Data Service (ADS) and {\tt arXiv} preprint repository.
@@
 Since it is likely that some portion of these disrupted subhalos should be populated with model galaxies \citep{guo_white13, campbell_etal17}, in our initial application of deconvolution abundance matching we derive the $\mstar-\mpeak$ relation using {\em all} subhalos, including those that may be disrupted.
-We then apply a selection function to the disrupted subhalos, so that a fraction of these objects will host galaxies in our mock universe.
+We then apply a selection function to the disrupted subhalos, so that a fraction of these objects will host model galaxies.
 We refer to this as the {\em orphan selection function}, $\mathcal{F}_{\rm orphan},$ which we consider to be an integral component of our application of abundance matching.

### 2017-11-13 paper/galsize_paper.tex
Corrected typos in figure captions

@@
 Projected clustering of SDSS galaxies in the bin of stellar mass: $10^{9.75}<\mstar/\msun<10^{10.25}.$ For both ``blue" and ``red" samples, we first divide SDSS galaxies falling in the $\mstar$ bin based on a color cut at $g-r=0.65.$ We then subsequently compute $\median{\rhalf}{\mstar; {\rm red}}$ and $\median{\rhalf}{\mstar; {\rm blue}}$.
-In analogy to the left panel of Figure \ref{fig:sizedefinition}, this sample definition results in identical stellar mass function for large and small subsamples, separately for both red and blue parent samples.
+In analogy to the bottom left panel of Figure \ref{fig:sizedefinition}, for each of the red and blue samples, the small and large subsamples have statistically indistinguishable stellar mass functions.
 We then measure $\wproj$ for each of the four subsamples, plotting the results with color-coding as specified in the legend.
@@
 Using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}, in the {\em left panels} we show predictions for as-yet-unseen measurements of the $\rhalf-$dependence of galaxy lensing of $\mstar-$complete samples, where ``small" and ``large" subsamples are defined as in \S\ref{subsec:sizedef}.
-To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which are reversed and weaker than the trends predicted here: for both blue and red samples, the observed $\Delta\Sigma$ of large galaxies is (slightly) stronger relative to small galaxies.
-As a generic consequence of satellites being smaller than centrals of the same mass, we predict that future lensing measurements of $\mstar-$complete samples will show $\Delta\Sigma$ of small galaxies to be significantly stronger relative to large galaxies of the same stellar mass $\mstar\lesssim10^{11}\msun.$ We additionally predict that at sufficiently large mass $\mstar\gtrsim10^{11}\msun,$ the trend of small-scale $\Delta\Sigma$ with $\rhalf$ should reverse sign.
+To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which the observed trends are reversed and weaker than those predicted here: for both blue and red samples, the observed $\Delta\Sigma$ of large galaxies is (slightly) stronger relative to small galaxies.
+As a generic consequence of satellites being smaller than centrals of the same mass, we predict that future lensing measurements of $\mstar-$complete samples will show that $\Delta\Sigma$ of small galaxies is significantly stronger relative to large galaxies of the same stellar mass $\mstar\lesssim10^{11}\msun.$ We additionally predict that at sufficiently large mass $\mstar\gtrsim10^{11}\msun,$ the trend of small-scale $\Delta\Sigma$ with $\rhalf$ reverses sign.
 The {\em right panels} display the physical explanation for this prediction.

### 2017-11-14 paper/galsize_paper.tex
Cosmetic touchups to figures
Changed color-dependent clustering figure to display in single column format
Changed figure sizes

@@
 
+As noted in \S\ref{sec:intro}, \citet{kravtsov13} showed that galaxy sizes are on average proportional to the virial radius of their host halo.
+Motivated by these results, we  explore a model in which $\rhalf$ scales linearly with halo virial radius:\footnote{We note that the normalization factor in \citet{kravtsov13} is 0.015, where as our normalization is 0.01.
+The difference derives from two factors: {\em i.} the choice of halo radius definition: \citet{bryan_norman98} in the present work, compared to the $200c$ definition used in \citet{kravtsov13}; {\em ii.} the latter study used deprojected (larger) sizes for spheroidal galaxies, whereas we make no such correction here.}
+\beq
+\label{eq:fiducial_model}
+\rhalf = 0.01\rvir
+\eeq
+For the virial radius of halos and subhalos, we use $\rmpeak:$ the value of $\rvir$ in physical units of $\kpc$ measured at the time when halo mass reached its maximum, $\zpeak.$  The relationship between $\rmpeak, \mpeak$ and $\zpeak$ is given by
+\beq
+\mpeak\equiv\frac{4\pi}{3}\rmpeak^{3}\Delta_{\rm vir}(\zpeak)\rho_{\rm m}(\zpeak),
+\eeq
+where for $\Delta_{\rm vir}(\zpeak)$ we use the fitting function to the ``virial" definition used in \citet{bryan_norman98}.
+This modeling assumption effectively defines $\median{\rhalf}{\mhalo};$ this relation defines the center of the log-normal distribution with $0.2$ dex of scatter that we use to generate a Monto Carlo realization of the model population.
+
 %---------------------------------------------------------------------------------------------------
@@
 \centering
-\includegraphics[width=12cm]{FIGS/rvir_only_wp_large_small_absolute.pdf}
+\includegraphics[width=11cm]{FIGS/rvir_only_wp_large_small_absolute.pdf}
 \caption{
@@
 \centering
-\includegraphics[width=12cm]{FIGS/rvir_only_wp_ratios.pdf}
+\includegraphics[width=11cm]{FIGS/rvir_only_wp_ratios.pdf}
 \caption{
@@
 %-----------------------------------------------------------------------------------------------------
-
-As noted in \S\ref{sec:intro}, \citet{kravtsov13} showed that galaxy sizes are on average proportional to the virial radius of their host halo.
-Motivated by these results, we  explore a model in which $\rhalf$ scales linearly with halo virial radius:\footnote{We note that the normalization factor in \citet{kravtsov13} is 0.015, where as our normalization is 0.01.
-The difference derives from two factors: {\em i.} the choice of halo radius definition: \citet{bryan_norman98} in the present work, compared to the $200c$ definition used in \citet{kravtsov13}; {\em ii.} the latter study used deprojected (larger) sizes for spheroidal galaxies, whereas we make no such correction here.}
-\beq
-\label{eq:fiducial_model}
-\rhalf = 0.01\rvir
-\eeq
-For the virial radius of halos and subhalos, we use $\rmpeak:$ the value of $\rvir$ in physical units of $\kpc$ measured at the time when halo mass reached its maximum, $\zpeak.$  The relationship between $\rmpeak, \mpeak$ and $\zpeak$ is given by
-\beq
-\mpeak\equiv\frac{4\pi}{3}\rmpeak^{3}\Delta_{\rm vir}(\zpeak)\rho_{\rm m}(\zpeak),
-\eeq
-where for $\Delta_{\rm vir}(\zpeak)$ we use the fitting function to the ``virial" definition used in \citet{bryan_norman98}.
-This modeling assumption effectively defines $\median{\rhalf}{\mhalo};$ this relation defines the center of the log-normal distribution with $0.2$ dex of scatter that we use to generate a Monto Carlo realization of the model population.
 
@@
 As shown in Figure \ref{fig:baseline_sham_clustering}, the abundance matching prediction for $\wproj(\rproj)$ exhibits tension with SDSS observations at the $10-20\%$ level, particularly for $\mstar\gtrsim10^{10.75}\msun.$ This tension is inherited by our $\rvir-$based model for size, which is the subject of this work, and so we wish to compare our size models to data in such a way that minimizes the role played by the underlying stellar-to-halo-mass relation.
-We accomplish this using {\em the $\rhalf$ clustering ratios,} described below.
+We accomplish this using the {\em $\rhalf$ clustering ratios,} described below.
 
@@
 \centering
-\includegraphics[width=12cm]{FIGS/alt_model_wp_ratios.pdf}
+\includegraphics[width=11cm]{FIGS/alt_model_wp_ratios.pdf}
 \caption{
@@
 \label{fig:colorclustering}
-\end{figure*}
+\end{figure}
 %---------------------------------------------------------------------------------------------------

### 2017-11-16 paper/galsize_paper.tex
Added information with redshift cuts and number of galaxies

@@
 
-In Figure~\ref{fig:rvir_only_clustering_absolute}, we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj(\rproj).$ We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds, $\mstar>10^{9.75}\msun,$ $\mstar>10^{10.25}\msun,$ $\mstar>10^{10.75}\msun,$ and $\mstar>10^{11}\msun.$ For each threshold, we split the galaxies into ``large" and ``small" subsamples, as described in \S\ref{subsec:sizedef}.
+In Figure~\ref{fig:rvir_only_clustering_absolute}, we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj(\rproj).$ We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds: an  $\mstar>10^{9.75}\msun$ sample with $z_{\rm max}=0.0435$ and $N_{\rm gal}=27658;$ an  $\mstar>10^{10.25}\msun$ sample with $z_{\rm max}=0.0663$ and $N_{\rm gal}=48571;$
+an  $\mstar>10^{10.75}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=52350;$ 
+and an  $\mstar>10^{11}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=33578.$ For each threshold, we split the galaxies into ``large" and ``small" subsamples, as described in \S\ref{subsec:sizedef}.
 As shown in Figure \ref{fig:sizedefinition}, our size-based samples  have similar stellar mass functions.

### 2017-11-18 paper/galsize_paper.tex
Minor grammatical corrections throughout. Added references to figures supporting each conclusion

@@
 Many properties of observed galaxies exhibit remarkably tight scaling relations.
-Galaxy size, typically quantified by a half-mass or half-light radius, $\rhalf,$ has well-measured scaling with galaxy mass $\mstar$ in the local Universe \citep{shen_etal03,huang_etal13,lange_etal15,zhang_yang17}, and at higher redshift \citep{trujillo_etal04,vanderwel_etal14,kawamata_etal15,shibuya_etal15,huertas_company_etal13a,huang_etal17}.
+Galaxy size, typically quantified by a half-mass or half-light radius, $\rhalf,$ has well-measured scaling with galaxy mass $\mstar$ in the local Universe \citep{shen_etal03,huang_etal13,lange_etal15,zhang_yang17}, and at higher redshift \citep{trujillo_etal04,huertas_company_etal13a,vanderwel_etal14,kawamata_etal15,shibuya_etal15,huang_etal17}.
 
-Observational constraints on models for galaxy $\rhalf$ typically come from one-point function measurements such as $\median{\rhalf}{\mstar}$ and $\sigma(\rhalf\vert\mstar),$ e.g.,  \citet{khochfar_silk06,lang_etal14,desmond_etal17,bottrell_etal17b,hou_etal17,somerville_etal17}, or otherwise from catalogs of galaxy groups \citep{weinmann_etal08,guo_etal09,huertas_company_etal13b,spindler_wake17}.
+Observational constraints on models for galaxy $\rhalf$ typically come from one-point function measurements such as $\mean{\rhalf}{\mstar}$ and $\sigma(\rhalf\vert\mstar),$ e.g.,  \citet{khochfar_silk06,lang_etal14,desmond_etal17,bottrell_etal17b,hou_etal17,somerville_etal17}, or otherwise from catalogs of galaxy groups \citep{weinmann_etal08,guo_etal09,huertas_company_etal13b,spindler_wake17}.
 More recently, the connection between a galaxy's size and the virial radius of its parent halo has been
@@
 The approach we take is to forward model the $\rhalf-$halo connection: we generate Monte Carlo realizations of models using a high-resolution cosmological N-body simulation, and then make synthetic measurements in a manner that closely mimics the measurements we make on our observed galaxy samples.
-We describe the dataset and simulations we use in \S\ref{sec:data}, and our forward-modeling methods in \S\ref{sec:model}.
+We describe the dataset and simulations we use in \S\ref{sec:data}.
+Our forward-modeling methods are described in \S\ref{sec:model}, with supplementary material in the Appendix.
 All of our primary results appear in \S\ref{sec:results}, and their theoretical interpretation in \S\ref{sec:interpretation}.
@@
 
-In addition to stellar mass, $\wproj(\rproj)$ depends on galaxy color \citep[e.g.,][]{zehavi_etal11}. Thus, we will also consider
+In addition to stellar mass, $\wproj(\rproj)$ depends on galaxy color \citep[e.g.,][]{zehavi_etal11}. Thus, we will also consider the 
 dependence of clustering on galaxy size while controlling for color. Observations of clustering exhibited by subsamples split in stellar mass and color are presented in \S\ref{subsec:colormorph}.
@@
 
-In \S\ref{sec:results}, we calculate predictions for the $\rhalf-$dependence of galaxy clustering for two classes of empirical models, described in turn below.
+Our primary results in \S\ref{sec:results} show predictions for the $\rhalf-$dependence of galaxy clustering for two classes of empirical models, described in turn in the two subsections below.
 
@@
 In this way, we model satellite mass loss and  size truncation in a manner that mimics what is seen in hydrodynamical simulations.
-As shown in \citet{smith_etal16}, stellar stripping in this model does not begin until $f_{\rm DM}\lesssim0.2,$ and the DM halo needs to be stripped to $\sim5\%$ of its initial mass for $\sim50\%$ of stars to be stripped.
+As shown in \citet{smith_etal16}, stellar stripping in this model does not begin until $f_{\rm DM}\lesssim0.2,$ and in order for $\sim50\%$ of stars to be stripped, the DM halo needs to be stripped to $\sim5\%$ of its initial mass.
 
@@
 Motivated by these results, we  explore a model in which $\rhalf$ scales linearly with halo virial radius:\footnote{We note that the normalization factor in \citet{kravtsov13} is 0.015, where as our normalization is 0.01.
-The difference derives from two factors: {\em i.} the choice of halo radius definition: \citet{bryan_norman98} in the present work, compared to the $200c$ definition used in \citet{kravtsov13}; {\em ii.} the latter study used deprojected (larger) sizes for spheroidal galaxies, whereas we make no such correction here.}
+The difference derives from two factors: {\em i.} the choice of halo radius definition: \citet{bryan_norman98} in the present work, compared to the $200c$ definition used in \citet{kravtsov13}; {\em ii.} the latter study used deprojected (larger) sizes for spheroidal galaxies, whereas we make no such correction here.
+See \S\ref{sec:future} for further discussion.}
 \beq
@@
 \item Small galaxies cluster more strongly than large galaxies of the same stellar mass.
-Differences between the clustering of small and large galaxies increase on small scales $R\lesssim1\mpc,$ and decrease with stellar mass.
+Differences between the clustering of small and large galaxies increase on small scales $R\lesssim1\mpc,$ and decrease with stellar mass (see Figure \ref{fig:rvir_only_clustering_absolute}).
 \item The most important ingredient influencing this signal is the relative size of central and satellite galaxies.
 The magnitude, scale-dependence, and $\mstar-$dependence of $\rhalf-$dependent clustering provides strong evidence that satellite galaxies are smaller than central galaxies of the same halo mass.
-\item A simple empirical model in which $\rhalf$ is set by halo $\rvir$ at the time of peak halo mass exhibits a clustering signal that is strikingly similar to that seen in SDSS.
-\item Models in which $\rhalf$ is regulated by $\mstar,$ rather than $\mhalo,$ are grossly discrepant with the observed clustering signal, even when accounting for satellite mass stripping.
+\item A simple empirical model in which $\rhalf$ is set by halo $\rvir$ at the time of peak halo mass exhibits a clustering signal that is strikingly similar to that seen in SDSS (see Figure \ref{fig:clustering_ratio_upshot}).
+\item Models in which $\rhalf$ is regulated by $\mstar,$ rather than $\mhalo,$ are grossly discrepant with the observed clustering signal, even when accounting for satellite mass stripping (see Figure \ref{fig:mstarmodelclustering}).
 \item Taken together, our findings indicate that satellite-specific processes play a sub-dominant role in setting the different sizes of centrals and satellites; these size differences instead appear to be largely predetermined at the time of satellite infall.

### 2017-11-20 paper/galsize_paper.tex
Updated draft with revisions suggested by Ben Moster

@@
 \author[Hearin, Behroozi, Kravtsov \& Moster]{
-Andrew Hearin$^{1}$, Peter Behroozi$^{2}$, Andrey Kravtsov$^{3}$, Benjamin Moster$^{4}$\\
+Andrew Hearin$^{1}$, Peter Behroozi$^{2}$, Andrey Kravtsov$^{3}$, Benjamin Moster$^{4,5}$\\
 $^{1}$Argonne National Laboratory, Argonne, IL, USA 60439, USA\\
@@
 $^{3}$Department of Astronomy \& Astrophysics, and Kavli Institute for Cosmological Physics, University of Chicago, Chicago IL 60637\\
-$^{4}$Universit{\"a}ts-Sternwarte, Ludwig-Maximilians-Universit{\"a}t M{\"u}nchen, Scheinerstr. 1, 81679 M{\"u}nchen, Germany
+$^{4}$Universit{\"a}ts-Sternwarte, Ludwig-Maximilians-Universit{\"a}t M{\"u}nchen, Scheinerstr. 1, 81679 M{\"u}nchen, Germany\\
+$^5$Max-Planck Institut f\"ur Astrophysik, Karl-Schwarzschild Stra\ss e 1, 85748 Garching, Germany
 }
@@
 To address issues related to subhalo incompleteness \citep{guo_white13,campbell_etal17}, we supplement the Bolshoi-Planck subhalo catalog with subhalos that have been disrupted and no longer appear in the standard catalog as $z=0$ surviving subhalos.
-We describe our treatment of these ``orphan" subhalos in the Appendix, where we also show results that exclude all orphan subhalos.
+We describe our treatment of these ``orphan" galaxies in the Appendix, where we also show results that exclude all orphan galaxies.
 
-For our SDSS galaxy samples, we calculate two-point clustering $\wproj$ using line-of-sight projection of $\pi_{\rm max}=20~\mpc$ using the {\tt correl} program in {\tt UniverseMachine}.
+For our SDSS galaxy samples, we calculate two-point clustering $\wproj$ using line-of-sight projection of $\pi_{\rm max}=20~\mpc$ using the {\tt correl} program in {\tt UniverseMachine} (Behroozi et al.
+2017, in prep).
 The {\tt correl} code uses the \citet{landy_szalay93} estimator ($DD - 2DR + RR$) to compute the redshift-space correlation function $\xi(\rproj, \pi)$, which is then integrated over $\vert\pi\vert < 20$ Mpc to compute the projected correlation function $\wproj(\rproj)$.
@@
 Using the stellar mass function provided in \citet{moustakas_etal13}, we model $\mstar$ as a log-normal distribution with $0.2$dex of scatter about the median relation $\median{\mstar}{\mpeak}$ determined by SHAM \citep{reddick_etal13}.
-As described in the appendix, we include a prescription for supplementing the ordinary {\tt Rockstar} subhalo catalog with disrupted subhalos, so that some of our model galaxies inhabit subhalos that are no longer resolved and do not appear in the standard publicly available catalog.
+As described in the appendix, we include a prescription for supplementing the ordinary {\tt Rockstar} subhalo catalog with disrupted subhalos, so that some of our model galaxies inhabit subhalos that are no longer resolved and do not appear in the standard publicly available catalog (``orphan galaxies").
 
 Figure \ref{fig:baseline_sham_clustering} shows that our implementation of SHAM produces model galaxies whose projected clustering is in reasonably good agreement with SDSS galaxies.
-We note, however, that $\wproj(\rproj\gtrsim1{\rm Mpc})$ is $\sim10-20\%$ too weak at stellar mass $\mstar\gtrsim10^{10.75}\msun,$ and similarly on all scales for the $\mstar\gtrsim10^{9.75}\msun$ sample, although the statistical significance of this discrepancy is likely rather mild due to the sample variance of SDSS galaxies with $z\lesssim0.05.$
+We note, however, that small-scale clustering shows mild $\sim10-20\%$ tension at stellar mass $\mstar\gtrsim10^{10.75}\msun,$ and similarly on all scales for the $\mstar\gtrsim10^{9.75}\msun$ sample, although the statistical significance of this discrepancy is likely rather mild due to the sample variance of SDSS galaxies with $z\lesssim0.05.$
 
@@
 In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ The black curve enveloped by the gray bands shows the scaling relation for SDSS galaxies, while the blue curve shows the median relation  $\median{\rhalf}{\mstar}$ predicted using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}.
-This figure shows that models in which $\rhalf\propto\rvir$ can naturally match the observed $\rhalf-\mstar$ relation, confirming the results of \citet{kravtsov13} in a forward modeling context.
+While the curvature of the median relation in the model is slightly weaker than SDSS, this figure shows that models in which $\rhalf\propto\rvir$ can nonetheless match the observed $\rhalf-\mstar$ relation remarkably well given only a single parameter, confirming the results of \citet{kravtsov13} in a forward modeling context.
 
@@
 In our approach, the level of scatter is simply a modeling parameter whose fiducial value was motivated by \citet{somerville_etal17}.
-In ongoing follow-up work discussed in \S\ref{sec:future}, we will systematically test the large-scale structure implications of the assumption that $\lambda_{\rm halo}\propto\rhalf^{\rm disk}$ using forward-modeling methods analogous to those advocated for in \citet{somerville_etal17} and employed here.
+In ongoing follow-up work discussed in \S\ref{sec:future}, we will systematically test the large-scale structure implications of the assumption that $\rhalf^{\rm disk}\propto\lambda_{\rm halo}$ using forward-modeling methods analogous to those advocated for in \citet{somerville_etal17} and employed here.
 
@@
 However, this can also be viewed as an opportunity to extract tighter constraints on $F_{\rm sat}(\mstar),$ which are sorely needed to discriminate between competing models \citep{watson_conroy13}.
-Traditional galaxy clustering is already being used to validate and/or fit models of the stellar-to-halo-mass relation \citep[e.g.,][]{leauthaud_etal11,moster_etal13,behroozi13_smhm,lehmann_etal15}.
+Traditional galaxy clustering is already being used to validate and/or fit models of the stellar-to-halo-mass relation \citep[e.g.,][]{leauthaud_etal11,moster_etal10,behroozi13_smhm,lehmann_etal15}.
 Based on our results, we advocate that empirical models for $\mean{\mstar}{\mhalo}$ be supplemented with additional model ingredients for $\median{\rhalf}{\mhalo},$ and that the parameters of the composite model be {\em jointly} constrained by measurements of the stellar mass function, $\mstar-$dependent clustering, and $\rhalf-$dependent clustering.
@@
 APH thanks John Baker for the {\em Toejam \& Earl} soundtrack.
-Thanks also to Frank van den Bosch, Andrew Zentner, Doug Watson, and Risa Wechsler for thoughtful feedback at various stages of the development of this work, to Faustin Carter and Sebastian Bocquet for sharing their matplotlib expertise, and to Andrew Zentner for Scottish grammar consultation.
+Thanks also to Frank van den Bosch, Andrew Zentner, Doug Watson, Simon White, Thorsten Naab, Risa Wechsler and Chihway Chang for thoughtful feedback at various stages of the development of this work, to Faustin Carter and Sebastian Bocquet for sharing their matplotlib expertise, and to Andrew Zentner for Scottish grammar consultation.
 
@@
 AK was  supported by NSF grant  AST-1412107, and by the Kavli Institute for Cosmological Physics at the University of Chicago through grant PHY-1125897, and an endowment from the Kavli Foundation and its founder Fred Kavli.
+BPM acknowledges an Emmy Noether grant funded by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) -- MO 2979/1-1.
 

### 2017-11-23 paper/galsize_paper.tex
AK's edits

@@
 $^{2}$Department of Physics, University of Arizona, 1118 E 4th St, Tucson, AZ 85721 USA\\
-$^{3}$Department of Astronomy \& Astrophysics, and Kavli Institute for Cosmological Physics, University of Chicago, Chicago IL 60637\\
+$^{3}$Department of Astronomy \& Astrophysics, and Kavli Institute for Cosmological Physics, The University of Chicago, Chicago IL 60637\\
 $^{4}$Universit{\"a}ts-Sternwarte, Ludwig-Maximilians-Universit{\"a}t M{\"u}nchen, Scheinerstr. 1, 81679 M{\"u}nchen, Germany\\
@@
 \begin{abstract}
-We place empirical constraints on the connection between dark matter halos and galaxy half-light radii, $\rhalf.$ Low-redshift SDSS measurements show that smaller galaxies cluster much more strongly than larger galaxies at fixed stellar mass.
-Using {\tt Halotools} to forward model the observations, we find that the clustering signal generically requires satellite galaxies to be smaller than central galaxies of the same halo mass.
-We present a simple empirical model consistent with the clustering results, in which galaxy size is proportional to halo virial radius at the time of peak halo mass.
-We use this model to predict how galaxy lensing, $\Delta\Sigma,$ should depend on $\rhalf$ for $\mstar-$complete samples.
-Other simple empirical models fail the clustering test, such as models in which galaxy size is related to stellar mass alone; these failures persist even when accounting for possible effects from satellite stripping and orphan galaxies.
-Our results suggest that the relative size of centrals and satellites could be predetermined at the time of satellite infall, and that a remarkably simple galaxy--halo scaling relation emerges from the complex physics regulating galaxy size.
+We explore size dependence of galaxy clustering and the implied connection between galaxy half-light radii, $\rhalf$, and their halo virial radii. 
+We show that in the volume-limited SDSS galaxy samples smaller galaxies cluster much more strongly than larger galaxies at fixed stellar mass. 
+The size dependence increases with decreasing scale and decreases with stellar mass of the sample. Using {\tt Halotools} to forward model the observations, 
+we show that a simple empirical model, in which $\rhalf$ is proptortional to the halo $\rvir$ at the time when halo mass reached its maximum,
+reproduces observed size-dependence of galaxy clustering in striking detail.
+The success of the model implies that the size-dependence of galaxy clustering is mainly due to the fact that satellite galaxies have smaller sizes compared 
+to central galaxies of the same stellar mass. Taken together, our findings indicate that  sizes of satellite galaxies are set  prior to satellite infall and that a 
+remarkably simple linear size--virial radius relation emerges from the complex physics regulating galaxy size. The $\rvir$-based size model that reproduces
+ the observed size dependence of clustering makes a prediction that future observations of size dependence of galaxy-galaxy lensing for stellar mass 
+ selected galaxy samples will see stronger signal for smaller galaxies. 
+ %Left over this sentence. Not sure we need to talk about this model in the abstract: 
+ % At the same time, model in which size is based on stellar mass does not reproduce the clustering trend, even after taking into account stellar mass loss by satellites.
+
 \end{abstract}
@@
 
-Observational constraints on models for galaxy $\rhalf$ typically come from one-point function measurements such as $\mean{\rhalf}{\mstar}$ and $\sigma(\rhalf\vert\mstar),$ e.g.,  \citet{khochfar_silk06,lang_etal14,desmond_etal17,bottrell_etal17b,hou_etal17,somerville_etal17}, or otherwise from catalogs of galaxy groups \citep{weinmann_etal08,guo_etal09,huertas_company_etal13b,spindler_wake17}.
+Observational constraints on models for galaxy size typically come from one-point function measurements such as $\mean{\rhalf}{\mstar}$ and $\sigma(\rhalf\vert\mstar),$ e.g.,  \citet{khochfar_silk06,lang_etal14,desmond_etal17,bottrell_etal17b,hou_etal17,somerville_etal17}, or otherwise from catalogs of galaxy groups \citep{weinmann_etal08,guo_etal09,huertas_company_etal13b,spindler_wake17}.
 More recently, the connection between a galaxy's size and the virial radius of its parent halo has been
@@
 
-The approach we take is to forward model the $\rhalf-$halo connection: we generate Monte Carlo realizations of models using a high-resolution cosmological N-body simulation, and then make synthetic measurements in a manner that closely mimics the measurements we make on our observed galaxy samples.
+The approach we take is to forward model the $\rhalf-$halo connection: we generate Monte Carlo realizations of models using a high-resolution cosmological $N$-body simulation, and then make synthetic measurements in a manner that closely mimics the measurements we make on our observed galaxy samples.
 We describe the dataset and simulations we use in \S\ref{sec:data}.
@@
 As the bedrock of our modeling, we use the publicly available\footnote{\url{http://www.slac.stanford.edu/~behroozi/BPlanck\_Hlists}} catalog of {\tt Rockstar} subhalos identified at $z=0$ in the Bolshoi-Planck simulation \citep{klypin_etal11,klypin_etal16,behroozi12_rockstar,riebe_etal13,behroozi_etal12b,rodriguez_puebla16_bolplanck}.
-As described in \S\ref{subsec:sham}, we use traditional abundance matching to connect stellar mass $\mstar$ with subhalo mass.
+As described in \S\ref{subsec:sham}, we use traditional abundance matching to connect stellar mass $\mstar$ with masses of halos and subhalos.
 To address issues related to subhalo incompleteness \citep{guo_white13,campbell_etal17}, we supplement the Bolshoi-Planck subhalo catalog with subhalos that have been disrupted and no longer appear in the standard catalog as $z=0$ surviving subhalos.
@@
 The code uses $10^6$ randoms drawn from the same mask region with uniform volume distribution to compute $DR$, and $RR$ is computed via Monte Carlo integration.
-Errors are estimated by jackknife resampling, giving us an estimate for the lower bound of samples with volumes $V_{\rm eff}\lesssim 0.3{\rm Gpc}^3.$
+Errors are estimated by jackknife resampling, giving us an estimate for the lower bound of samples with volumes $V_{\rm eff}\lesssim 0.3\,{\rm Gpc}^3.$
 
@@
 All numerical values of $\rhalf$ will be quoted in physical $\kpc,$ and all values of $\mstar$ and $\mhalo$ in $\msun,$ assuming $H_0=67.8~\kms\equiv100h~\kms,$ the best-fit value from \citet{planck15}.
-To scale stellar masses to ``$h=1$ units" \citep{croton13}, our numerically quoted values for $\mstar$ should be multiplied by a factor of $h^2,$ while our halo masses and distances should be multiplied by a factor of $h.$
+To scale stellar masses to ``$h=1$ units" \citep{croton13}, our numerically quoted values for $\mstar$ should be multiplied by $h^2,$ while our halo masses and distances should be multiplied by $h.$
 
@@
 
-Because galaxy clustering has well-known dependence upon $\mstar$ that is not the subject of this work, we wish to remove this influence and focus purely on the relationship between $\rhalf$ and $\wproj(\rproj).$ To do so, we determine the value $\median{\rhalf}{\mstar}$ by computing a sliding median of $\rhalf$ for galaxies sorted by $\mstar,$ calculated using a window of width $N_{\rm gal}=1000.$ Each galaxy is categorized as either ``large" or ``small" according to whether it is above or below the median value appropriate for its stellar mass.
+Galaxy clustering has well-known dependence upon $\mstar$, which is not the focus of this work.  We thus wish to remove this dependence to focus solely on the  $\wproj(\rproj)$ dependence
+on $\rhalf.$ To do so, we determine the value $\median{\rhalf}{\mstar}$ by computing a sliding median of $\rhalf$ for galaxies sorted by $\mstar,$ calculated using a window of width $N_{\rm gal}=1000.$ \textcolor{magenta}{AK: is window symmetric?
+What is done for the most massive and least massive galaxies?
+} Each galaxy is categorized as either ``large" or ``small" according to whether it is above or below the median value appropriate for its stellar mass.
 We note that this is analogous to the common convention for studying the properties of ``red" vs.
@@
 For the subhalo property used in SHAM, we use $\mpeak,$ the largest value of $\mvir$ ever attained by the subhalo throughout the entire history of the main progenitor halo.
-Using the stellar mass function provided in \citet{moustakas_etal13}, we model $\mstar$ as a log-normal distribution with $0.2$dex of scatter about the median relation $\median{\mstar}{\mpeak}$ determined by SHAM \citep{reddick_etal13}.
+Using the stellar mass function provided in \citet{moustakas_etal13}, we model $\mstar$ as a log-normal distribution with $0.2$ dex of scatter about the median relation $\median{\mstar}{\mpeak}$ determined by SHAM \citep{reddick_etal13}.
 As described in the appendix, we include a prescription for supplementing the ordinary {\tt Rockstar} subhalo catalog with disrupted subhalos, so that some of our model galaxies inhabit subhalos that are no longer resolved and do not appear in the standard publicly available catalog (``orphan galaxies").
@@
 
-\subsubsection{Tidal stripping model}
+\subsubsection{$\mstar$-based model with satellite mass loss}
 \label{subsubsec:strippingmodel}
 
-In the first model we explore, we assume that stellar mass $\mstar$ controls $\rhalf.$ To implement this model, for simplicity we tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form, so that this model reproduces the observed $\rhalf-\mstar$ relation by construction.
+In the first model we assume that stellar mass $\mstar$ controls $\rhalf.$ To implement this model, for simplicity we tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form, so that this model reproduces the observed $\rhalf-\mstar$ relation by construction.
 In order to ensure that the model has a level of scatter in $\rhalf$ at fixed $\mstar$ that is comparable to the level reported in \citet{somerville_etal17}, our model sizes are drawn from a log-normal distribution with $0.2$ dex of scatter centered at the observed $\median{\rhalf}{\mstar}.$
@@
 As shown in \citet{smith_etal16}, stellar stripping in this model does not begin until $f_{\rm DM}\lesssim0.2,$ and in order for $\sim50\%$ of stars to be stripped, the DM halo needs to be stripped to $\sim5\%$ of its initial mass.
+\textcolor{magenta}{How is mass loss is handled and how stellar mass assigned for orphans? This is not described in the appendix or here.}.
 
@@
 As noted in \S\ref{sec:intro}, \citet{kravtsov13} showed that galaxy sizes are on average proportional to the virial radius of their host halo.
-Motivated by these results, we  explore a model in which $\rhalf$ scales linearly with halo virial radius:\footnote{We note that the normalization factor in \citet{kravtsov13} is 0.015, where as our normalization is 0.01.
+Motivated by these results, we  explore a model in which $\rhalf$ scales linearly with halo virial radius:\footnote{We note that the normalization factor in \citet{kravtsov13} is 0.015, whereas our normalization is 0.01.
 The difference derives from two factors: {\em i.} the choice of halo radius definition: \citet{bryan_norman98} in the present work, compared to the $200c$ definition used in \citet{kravtsov13}; {\em ii.} the latter study used deprojected (larger) sizes for spheroidal galaxies, whereas we make no such correction here.
@@
 
-The points and curves in Figure \ref{fig:clustering_ratio_upshot} are all negative: small galaxies cluster more strongly relative to large.
+The points and curves in Figure \ref{fig:clustering_ratio_upshot} are almost all negative: small galaxies cluster more strongly relative to large.
 This presentation of the measurement makes it clear that the underlying signal of $\rhalf-$dependent clustering is strongest for samples with smaller stellar mass; as $\mstar$ increases, the signal weakens and nearly vanishes for $\mstar\gtrsim10^{11}\msun.$ Strikingly, the $\rvir-$based model reproduces this $\mstar-$dependent behavior, as well as the scale-dependence of the observed clustering signal at each $\mstar.$ As described in \S\ref{subsec:censat_sizes} below, we attribute the success of this prediction to the systematic difference of sizes of central and satellite galaxies.
@@
 We reach the same conclusion when we tested an even more extreme $\mstar-$stripping model, in which stellar mass loss is linearly proportional to halo mass loss \citep[][Model 1]{watson_etal12}.
-As we argue in \S\ref{sec:interpretation}, this supports the conclusion that the relative difference between central and satellite size is largely in place at the time of satellite infall.
+As we argue in \S\ref{sec:interpretation}, this supports the conclusion that the relative difference between median sizes of central and satellite galaxies is largely in place at the time of satellite infall.
 
@@
 \caption{
-{\bf Distinct $\rhalf-$dependence of clustering for color-selected galaxy samples.}
+{\bf \textcolor{magenta}{AK: it may be difficult for people (especially color-blind) to tell the difference between color of points of small and large galaxies.} Distinct $\rhalf-$dependence of clustering for color-selected galaxy samples.}
 Projected clustering of SDSS galaxies in the bin of stellar mass: $10^{9.75}<\mstar/\msun<10^{10.25}.$ For both ``blue" and ``red" samples, we first divide SDSS galaxies falling in the $\mstar$ bin based on a color cut at $g-r=0.65.$ We then subsequently compute $\median{\rhalf}{\mstar; {\rm red}}$ and $\median{\rhalf}{\mstar; {\rm blue}}$.
@@
 It is well known that satellites are redder than centrals of the same stellar mass \citep[e.g.,][]{vdB_etal08}, and so blue galaxies have a small satellite fraction, while red galaxies have a large fraction of satellites that occupy high-mass halos; accordingly, red galaxies cluster much more strongly than blue galaxies \citep[e.g.,][]{zehavi_etal11}.
+
 Pre-selecting galaxy samples by color then naturally restricts the impact of satellites on size-dependent clustering.
 For blue galaxies, the reason traces to the small value of $F_{\rm sat};$ for red galaxies, the reason traces to the limited dynamic range of host halo masses occupied by the satellites.
+\textcolor{magenta}{AK: I did not quite understand the explanation for red galaxies in the last sentence.
+It'd be good to unpack it.
+}.
 With the impact of satellites reduced, the relative clustering of centrals becomes more important.
@@
 the slope of the $\rhalf-\mstar$ relation is approximately linear.
-These trends of $\rhalf$ with $\mstar$ have a direct relation to the trends of surface brightness $\mu_\star=\mstar/(\pi\rhalf^2)$ with stellar mass \citep[see, for example, the $\mu_\star-$dependent clustering measurements in][which are qualitatively similar to the measurements reported here]{li_etal06}.
+These trends of $\rhalf$ with $\mstar$ have a direct relation to the trends of surface brightness $\mu_\star=\mstar/(2\pi\rhalf^2)$ with stellar mass \citep[see, for example, the $\mu_\star-$dependent clustering measurements in][which are qualitatively similar to the measurements reported here]{li_etal06}.
 
@@
 {\bf Prediction for $\rhalf-$dependence of galaxy lensing.}
-Using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}, in the {\em left panels} we show predictions for as-yet-unseen measurements of the $\rhalf-$dependence of galaxy lensing of $\mstar-$complete samples, where ``small" and ``large" subsamples are defined as in \S\ref{subsec:sizedef}.
+Using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}, in the {\em left panels} we show predictions for future measurements of the $\rhalf-$dependence of galaxy lensing of $\mstar-$complete samples, where ``small" and ``large" subsamples are defined as in \S\ref{subsec:sizedef}.
 To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which the observed trends are reversed and weaker than those predicted here: for both blue and red samples, the observed $\Delta\Sigma$ of large galaxies is (slightly) stronger relative to small galaxies.
@@
 The peak of each distribution arises from central galaxies, while the long tail at large values of $\mhost$ is due to satellites.
-At all stellar mass, the blue histograms peak at slightly larger $\mhost$ relative to the red; this is because the $\rvir-$based model predicts that $\mhalo$ increases with $\rhalf$ for centrals.
+At all stellar masses, the blue histograms peak at slightly larger $\mhost$ relative to the red; this is because the $\rvir-$based model predicts that $\mhalo$ increases with $\rhalf$ for centrals.
 For $\mstar-$complete samples, this effect only becomes dominant when the satellite fraction drops to sufficiently small values.
@@
 virial radius of halos at the moment the halo mass reached its peak, and also that sizes of satellite galaxies were set {\em prior} to infall, our model does not capture galaxy properties and their trends in full quantitative detail.
-For example, the clustering ratios of this model shown in Figure \ref{fig:clustering_ratio_upshot} do capture the overall trends, but do not match the observed clustering statistics at the level of $\chi^2.$ For present purposes, we have chosen to focus on exploring bracketing cases of qualitative ingredients, rather than fine-tuning the model.
+For example, the clustering ratios of this model shown in Figure \ref{fig:clustering_ratio_upshot} do capture the overall trends, but do not match the observed clustering statistics at the level of reduced $\chi^2\approx 1.$ For present purposes, we have chosen to focus on exploring bracketing cases of qualitative ingredients, rather than fine-tuning the model.
 
@@
 Forward modeling methods for ${\rm B/T}$ offer potential to significantly improve upon several aspects of current analysis techniques.
-For example, it is common to de-project two-dimensional sizes of observed galaxies to estimate three-dimensional sizes; such a correction applied to the data requires treating disk-dominated and spheroidal systems separately.
+For example,   two-dimensional (projected) sizes of observed galaxies are sometimes de-projected to estimate three-dimensional sizes; such a correction applied to the data requires treating disk-dominated and spheroidal systems separately.
 The forward modeling approach turns the direction of this correction around: three-dimensional sizes of disk and bulge components are modeled separately; the projected size can then be computed self-consistently with the modeled value of ${\rm B/T},$ permitting a more apples-to-apples comparison to observations of projected size.
@@
 Differences between the clustering of small and large galaxies increase on small scales $R\lesssim1\mpc,$ and decrease with stellar mass (see Figure \ref{fig:rvir_only_clustering_absolute}).
-\item The most important ingredient influencing this signal is the relative size of central and satellite galaxies.
+\item The most important factor influencing this signal is the relative size of central and satellite galaxies.
 The magnitude, scale-dependence, and $\mstar-$dependence of $\rhalf-$dependent clustering provides strong evidence that satellite galaxies are smaller than central galaxies of the same halo mass.
-\item A simple empirical model in which $\rhalf$ is set by halo $\rvir$ at the time of peak halo mass exhibits a clustering signal that is strikingly similar to that seen in SDSS (see Figure \ref{fig:clustering_ratio_upshot}).
+\item A simple empirical model in which $\rhalf$ is proptortional to the halo $\rvir$ at the time when halo mass reached its maximum peak halo mass reproduces size-dependence of galaxy clustering of the SDSS galaxies in striking detail (see Figure \ref{fig:clustering_ratio_upshot}).
 \item Models in which $\rhalf$ is regulated by $\mstar,$ rather than $\mhalo,$ are grossly discrepant with the observed clustering signal, even when accounting for satellite mass stripping (see Figure \ref{fig:mstarmodelclustering}).
 \item Taken together, our findings indicate that satellite-specific processes play a sub-dominant role in setting the different sizes of centrals and satellites; these size differences instead appear to be largely predetermined at the time of satellite infall.
+\item The $\rvir$-based size model that reproduces the observed size dependence of clustering makes a prediction that future observations of size dependence of galaxy-galaxy
+lensing for stellar mass selected galaxy samples will see stronger signal for smaller galaxies. 
 \een
@@
 
-In this appendix, we show two different, a priori reasonable choices for the orphan selection function.
+In this appendix, we present two different, a priori reasonable choices for the orphan selection function.
 Since a rigorous calibration of $\mathcal{F}_{\rm orphan}$ is beyond the scope of the present work, we instead opt for a simple parameterization that yields reasonably accurate recovery of the galaxy clustering signal observed in SDSS.
@@
 Figure \ref{fig:orphan_effects} illustrates the impact of the orphan selection function on $\mstar-$threshold clustering (top panel) and the satellite fraction (bottom panel).
-Comparing the black to the red curves shows that including orphans substantially boosts small-scale clustering due to the increased satellite fraction.
+\textcolor{magenta}{AK: given that the focus of the paper is on the size dependence of clustering, some readers could want to see a version of Fig 5 for different orphan models instead of stellar mass dependence of clustering.} Comparing the black to the red curves shows that including orphans substantially boosts small-scale clustering due to the increased satellite fraction.
 Comparing the orange to the black curves, we see that random orphan selection, vs.
@@
 \caption{
-{\bf Impact of the orphan selection function.} The {\em top panel} is identical to Figure \ref{fig:baseline_sham_clustering}, but includes additional curves for the case of $M_{\rm host}-$dependent orphan selection (orange curves), and no orphans at all (red curves).
+{\bf Impact of the orphan selection function.} \textcolor{magenta}{AK: I think the 4-panel plot should be a separate figure.
+Otherwise it's too small.}.
+The {\em top panel} is identical to Figure \ref{fig:baseline_sham_clustering}, but includes additional curves for the case of $M_{\rm host}-$dependent orphan selection (orange curves), and no orphans at all (red curves).
 As a function of stellar mass, the {\em bottom panel} shows the satellite fraction, i.e., the fraction of objects that are not central galaxies.

### 2017-11-25 paper/galsize_paper.tex
APH edits

@@
 \newcommand{\sfr}{{\rm SFR}}
+\newcommand{\fsat}{F_{\rm sat}}
 
@@
 \newcommand{\wpall}{w_{\rm p}^{\rm all}}
-
 \newcommand{\mean}[2]{\langle{#1}\vert{#2}\rangle}
@@
 \begin{abstract}
-We explore size dependence of galaxy clustering and the implied connection between galaxy half-light radii, $\rhalf$, and their halo virial radii. 
-We show that in the volume-limited SDSS galaxy samples smaller galaxies cluster much more strongly than larger galaxies at fixed stellar mass. 
-The size dependence increases with decreasing scale and decreases with stellar mass of the sample. Using {\tt Halotools} to forward model the observations, 
-we show that a simple empirical model, in which $\rhalf$ is proptortional to the halo $\rvir$ at the time when halo mass reached its maximum,
-reproduces observed size-dependence of galaxy clustering in striking detail.
-The success of the model implies that the size-dependence of galaxy clustering is mainly due to the fact that satellite galaxies have smaller sizes compared 
-to central galaxies of the same stellar mass. Taken together, our findings indicate that  sizes of satellite galaxies are set  prior to satellite infall and that a 
-remarkably simple linear size--virial radius relation emerges from the complex physics regulating galaxy size. The $\rvir$-based size model that reproduces
- the observed size dependence of clustering makes a prediction that future observations of size dependence of galaxy-galaxy lensing for stellar mass 
- selected galaxy samples will see stronger signal for smaller galaxies. 
- %Left over this sentence. Not sure we need to talk about this model in the abstract: 
- % At the same time, model in which size is based on stellar mass does not reproduce the clustering trend, even after taking into account stellar mass loss by satellites.
-
+Using new SDSS measurements of projected galaxy clustering, $\wproj(\rproj),$ we place empirical constraints on the connection between galaxy size, $\rhalf,$ and halo virial radius, $\rvir.$  
+We find that small galaxies cluster much more strongly than large galaxies of the same stellar mass. 
+The size-dependence of $\wproj(\rproj)$ increases on smaller scales, and decreases at larger stellar mass.
+Using {\tt Halotools} to forward model the observations, we show that a simple empirical model, in which galaxy $\rhalf$ is proportional to halo $\rvir$ at the time when halo mass reached its maximum,
+reproduces the observed size-dependence of $\wproj(\rproj)$ in striking detail. 
+We show that the success of this model provides strong support for the conclusion that satellite galaxies have smaller sizes relative to central galaxies of the same halo mass. 
+Our findings indicate that the sizes of satellites are set prior to the time of satellite infall, and that a remarkably simple, linear size--virial radius relation emerges from the complex physics regulating galaxy size.
+%We conclude with a prediction that future measurements of galaxy-galaxy lensing will show that small galaxies exhibit a significantly stronger lensing signal relative to large galaxies.of the same stellar mass.
 \end{abstract}
@@
 Galaxy clustering has well-known dependence upon $\mstar$, which is not the focus of this work.  We thus wish to remove this dependence to focus solely on the  $\wproj(\rproj)$ dependence
-on $\rhalf.$ To do so, we determine the value $\median{\rhalf}{\mstar}$ by computing a sliding median of $\rhalf$ for galaxies sorted by $\mstar,$ calculated using a window of width $N_{\rm gal}=1000.$ \textcolor{magenta}{AK: is window symmetric?
-What is done for the most massive and least massive galaxies?
-} Each galaxy is categorized as either ``large" or ``small" according to whether it is above or below the median value appropriate for its stellar mass.
+on $\rhalf.$ To do so, we determine the value $\median{\rhalf}{\mstar}$ by computing a sliding median of $\rhalf$ for galaxies sorted by $\mstar,$ calculated using a symmetric window of width $N_{\rm gal}=1000,$ keeping this window fixed for the first and last $500$ galaxies.
+Each galaxy is categorized as either ``large" or ``small" according to whether it is above or below the median value appropriate for its stellar mass.
 We note that this is analogous to the common convention for studying the properties of ``red" vs.
@@
 See Section 3.3 of \citet{behroozi_etal10}, or the appendix of \citet{kravtsov_etal14}, for an account of the mathematics underlying this technique in the presence of scatter.
-To perform the abundance matching, we use the publicly available code\footnote{\url{https://bitbucket.org/yymao/abundancematching/overview}} developed by Yao-Yuan Mao \citep{lehmann_etal15} that provides a python wrapper around the C kernel developed in \citet{behroozi_etal10}.
+To perform the abundance matching, we use the publicly available code\footnote{\url{https://bitbucket.org/yymao/abundancematching}} developed by Yao-Yuan Mao \citep{lehmann_etal15} that provides a python wrapper around the C kernel developed in \citet{behroozi_etal10}.
 For the subhalo property used in SHAM, we use $\mpeak,$ the largest value of $\mvir$ ever attained by the subhalo throughout the entire history of the main progenitor halo.
@@
 As shown in \citet{smith_etal16}, stellar stripping in this model does not begin until $f_{\rm DM}\lesssim0.2,$ and in order for $\sim50\%$ of stars to be stripped, the DM halo needs to be stripped to $\sim5\%$ of its initial mass.
-\textcolor{magenta}{How is mass loss is handled and how stellar mass assigned for orphans? This is not described in the appendix or here.}.
 
@@
 \caption{
-{\bf \textcolor{magenta}{AK: it may be difficult for people (especially color-blind) to tell the difference between color of points of small and large galaxies.} Distinct $\rhalf-$dependence of clustering for color-selected galaxy samples.}
+{\bf Distinct $\rhalf-$dependence of clustering for color-selected galaxy samples.}
 Projected clustering of SDSS galaxies in the bin of stellar mass: $10^{9.75}<\mstar/\msun<10^{10.25}.$ For both ``blue" and ``red" samples, we first divide SDSS galaxies falling in the $\mstar$ bin based on a color cut at $g-r=0.65.$ We then subsequently compute $\median{\rhalf}{\mstar; {\rm red}}$ and $\median{\rhalf}{\mstar; {\rm blue}}$.
 In analogy to the bottom left panel of Figure \ref{fig:sizedefinition}, for each of the red and blue samples, the small and large subsamples have statistically indistinguishable stellar mass functions.
-We then measure $\wproj$ for each of the four subsamples, plotting the results with color-coding as specified in the legend.
+We then measure $\wproj$ for each of the four subsamples; jackknife-estimated errors are shown alternately using error bars and shaded bands, as specified in the legend.
 At this stellar mass, pre-selecting galaxy samples by color results in a dramatic weakening of the $\rhalf-$dependence of $\wproj$ relative to $\mstar-$complete samples, as well as a sign-reversal of the signal.
@@
 
-Likewise, the significantly weaker dependence of clustering on size for color-selected samples (Figure \ref{fig:colorclustering}), and its reversed sign, can be naturally explained by the same principles.
-It is well known that satellites are redder than centrals of the same stellar mass \citep[e.g.,][]{vdB_etal08}, and so blue galaxies have a small satellite fraction, while red galaxies have a large fraction of satellites that occupy high-mass halos; accordingly, red galaxies cluster much more strongly than blue galaxies \citep[e.g.,][]{zehavi_etal11}.
-
-Pre-selecting galaxy samples by color then naturally restricts the impact of satellites on size-dependent clustering.
-For blue galaxies, the reason traces to the small value of $F_{\rm sat};$ for red galaxies, the reason traces to the limited dynamic range of host halo masses occupied by the satellites.
-\textcolor{magenta}{AK: I did not quite understand the explanation for red galaxies in the last sentence.
-It'd be good to unpack it.
-}.
-With the impact of satellites reduced, the relative clustering of centrals becomes more important.
+Likewise, the significantly weaker dependence of clustering on size for color-selected samples (Figure \ref{fig:colorclustering}), and its reversed sign, may be explained by the same principles.
+It is well known that satellites are redder than centrals of the same stellar mass \citep[e.g.,][]{vdB_etal08}, and that the clustering differences between red and blue galaxies can be understood in terms of red satellites preferentially occupying high-mass halos \citep[e.g.,][]{zehavi_etal11}.
+Pre-selecting galaxies by color then absorbs much of the potential effect that can be reaped by central vs.
+satellite differences, and so the relative clustering of centrals becomes more important.
 In the limit that size-dependent clustering is dominated by centrals, the $\rvir$-based size model predicts that large galaxy samples should be (weakly) more clustered than small ones, because $\rhalf\propto\rvir\propto\mhalo^{1/3}.$ This is the trend seen in the clustering measurements shown in Figure \ref{fig:colorclustering}.
 
-While we consider such a hypothesis plausible, and even likely, a conclusive confirmation requires proper forward modeling of size and color jointly.
+While we consider such a conjecture plausible, a conclusive confirmation requires proper forward modeling of size and color jointly.
 Such an effort is well motivated by our results, but is beyond the scope of the present work.
@@
 
-We have presented new measurements of the dependence of galaxy clustering upon galaxy size, and used forward-modeling methods based on {\tt Halotools} to identify the basic ingredients that influence the signal.
+We have presented new measurements of the dependence of projected galaxy clustering, $\wproj(\rproj),$ upon galaxy size and stellar mass, and used forward-modeling methods based on {\tt Halotools} to identify the basic ingredients that influence the signal.
 We conclude with a brief summary of our primary findings:
@@
 \item Small galaxies cluster more strongly than large galaxies of the same stellar mass.
-Differences between the clustering of small and large galaxies increase on small scales $R\lesssim1\mpc,$ and decrease with stellar mass (see Figure \ref{fig:rvir_only_clustering_absolute}).
-\item The most important factor influencing this signal is the relative size of central and satellite galaxies.
+Differences between the clustering of small and large galaxies increase on small scales $\rproj\lesssim1\mpc,$ and decrease with stellar mass (see Figure \ref{fig:rvir_only_clustering_absolute}).
+\item The most important factor influencing the clustering signal is the relative size of central and satellite galaxies.
 The magnitude, scale-dependence, and $\mstar-$dependence of $\rhalf-$dependent clustering provides strong evidence that satellite galaxies are smaller than central galaxies of the same halo mass.
-\item A simple empirical model in which $\rhalf$ is proptortional to the halo $\rvir$ at the time when halo mass reached its maximum peak halo mass reproduces size-dependence of galaxy clustering of the SDSS galaxies in striking detail (see Figure \ref{fig:clustering_ratio_upshot}).
-\item Models in which $\rhalf$ is regulated by $\mstar,$ rather than $\mhalo,$ are grossly discrepant with the observed clustering signal, even when accounting for satellite mass stripping (see Figure \ref{fig:mstarmodelclustering}).
+\item A simple empirical model in which $\rhalf$ is proportional to halo $\rvir$ at the time when halo mass reached its maximum reproduces the size-dependence of SDSS galaxy clustering in striking detail (see Figure \ref{fig:clustering_ratio_upshot}).
+\item Models in which $\rhalf$ is regulated by $\mstar,$ rather than $\mhalo,$ are grossly discrepant with the observed $\wproj(\rproj),$ even when accounting for satellite mass stripping (see Figure \ref{fig:mstarmodelclustering}).
 \item Taken together, our findings indicate that satellite-specific processes play a sub-dominant role in setting the different sizes of centrals and satellites; these size differences instead appear to be largely predetermined at the time of satellite infall.
-\item The $\rvir$-based size model that reproduces the observed size dependence of clustering makes a prediction that future observations of size dependence of galaxy-galaxy
-lensing for stellar mass selected galaxy samples will see stronger signal for smaller galaxies. 
+\item The $\rvir$-based size model that reproduces the observed $\wproj(\rproj)$ makes an unambiguous  prediction for future observations of galaxy-galaxy lensing: for $\mstar-$selected samples, $\Delta\Sigma$ should be much stronger for small galaxies relative to large (see Figure \ref{fig:lensingprediction}).
+The strength of the predicted difference in $\Delta\Sigma$ makes this test well within reach of numerous present-day imaging surveys.
 \een
@@
 
-We use an extension of {\tt Consistent Trees} that models the evolution of subhalos after disruption.
+Recent results indicate that some portion of subhalos may be artificially disrupted \citep{guo_white13, campbell_etal17}.
+To address this possibility in our modeling, we use an extension of {\tt Consistent Trees} that models the evolution of subhalos after disruption.
 The phase space evolution of disrupted subhalos is approximated by following a point mass evolving in the host halo potential according to the orbital parameters of the subhalo at the time of disruption; the evolution of subhalo mass and circular velocity is approximated using the semi-analytic model presented in \citet{jiang_vdB14}.
@@
 
-Since it is likely that some portion of these disrupted subhalos should be populated with model galaxies \citep{guo_white13, campbell_etal17}, in our initial application of deconvolution abundance matching we derive the $\mstar-\mpeak$ relation using {\em all} subhalos, including those that may be disrupted.
+In our initial application of deconvolution abundance matching we derive the $\mstar-\mpeak$ relation using {\em all} subhalos, including those that were initially considered disrupted.
 We then apply a selection function to the disrupted subhalos, so that a fraction of these objects will host model galaxies.
 We refer to this as the {\em orphan selection function}, $\mathcal{F}_{\rm orphan},$ which we consider to be an integral component of our application of abundance matching.
+Once $\mathcal{F}_{\rm orphan}$ has been applied, the assemblage of calculations described above provides values of $\mpeak,$ $\zpeak,$ and $\mvir$ for disrupted subhalos, which are the only properties needed to apply either the $\rvir-$based or $\mstar-$based size model.
 
-In this appendix, we present two different, a priori reasonable choices for the orphan selection function.
-Since a rigorous calibration of $\mathcal{F}_{\rm orphan}$ is beyond the scope of the present work, we instead opt for a simple parameterization that yields reasonably accurate recovery of the galaxy clustering signal observed in SDSS.
+In this appendix, we present two distinct choices for the orphan selection function, described in detail below.
+For the results in the main body of the text, we have opted for the simplest parameterization we could find that yields reasonably accurate recovery of the galaxy clustering signal observed in SDSS.
+While a rigorous calibration of $\mathcal{F}_{\rm orphan}$ is beyond the scope of the present work, we point out that a systematic study of subhalo disruption is needed to conduct the program discussed in \S\ref{sec:future}.
 
@@
 
-Figure \ref{fig:orphan_effects} illustrates the impact of the orphan selection function on $\mstar-$threshold clustering (top panel) and the satellite fraction (bottom panel).
-\textcolor{magenta}{AK: given that the focus of the paper is on the size dependence of clustering, some readers could want to see a version of Fig 5 for different orphan models instead of stellar mass dependence of clustering.} Comparing the black to the red curves shows that including orphans substantially boosts small-scale clustering due to the increased satellite fraction.
-Comparing the orange to the black curves, we see that random orphan selection, vs.
-the $M_{\rm host}-$dependent selection, results in similar clustering, with slight differences on the smallest scales at the highest masses.
-Because we have not been systematic in the calibration of $\mathcal{F}_{\rm orphan},$ we adopt the simpler, random orphan selection as the fiducial model shown in the main body of the text.
+Figure \ref{fig:orphan_satellite_fractions} illustrates the impact of the orphan selection function on the $\mstar-$dependence of the satellite fraction, $\fsat,$ defined as the fraction of galaxies that are not centrals.
+Both models that include disrupted subhalos receive a significant boost to $\fsat$ due to orphan galaxies.
+The $\mhost-$dependent model suppresses the selection of disrupted subhalos with larger values of $\mpeak,$ resulting in a milder boost to $\fsat$ at large $\mstar.$
+
+Figure \ref{fig:orphan_baseline_clustering} shows how the treatment of orphans impacts $\mstar-$dependent clustering.
+Comparing either the black or orange curves to the red curves shows that including orphans substantially boosts small-scale clustering due to the increased satellite fraction.
+We show the impact of orphans on $\rhalf-$dependent clustering in Figure \ref{fig:orphan_size_clustering}.
+As discussed in \S\ref{subsec:censat_sizes}, the value of $\fsat$ modulates the magnitude of the influence of central/satellite size differences on $\wproj;$ including orphans thus boosts the clustering ratios $\delta\wproj/\wproj.$ Because we have not been systematic in the calibration of $\mathcal{F}_{\rm orphan},$ we adopt the simpler, random orphan selection as the fiducial model shown in the main body of the text.
 
@@
 \centering
-\includegraphics[width=8cm]{FIGS/baseline_sham_orphans.pdf}
 \includegraphics[width=8cm]{FIGS/orphan_satellite_fraction.pdf}
 \caption{
-{\bf Impact of the orphan selection function.} \textcolor{magenta}{AK: I think the 4-panel plot should be a separate figure.
-Otherwise it's too small.}.
-The {\em top panel} is identical to Figure \ref{fig:baseline_sham_clustering}, but includes additional curves for the case of $M_{\rm host}-$dependent orphan selection (orange curves), and no orphans at all (red curves).
-As a function of stellar mass, the {\em bottom panel} shows the satellite fraction, i.e., the fraction of objects that are not central galaxies.
+{\bf Impact of orphans on $\fsat.$} The y-axis shows the fraction of galaxies that are not centrals, plotted as a function of stellar mass $\mstar.$ Different curves show results for three different choices for the treatment of disrupted subhalos, as indicated in the legend and described in the text of the appendix.
 }
-\label{fig:orphan_effects}
+\label{fig:orphan_satellite_fractions}
 \end{figure}
@@
 
+%---------------------------------------------------------------------------------------------------
+\begin{figure*}
+\centering
+\includegraphics[width=12cm]{FIGS/baseline_sham_orphans.pdf}
+\caption{
+{\bf Impact of orphans on $\mstar-$dependent clustering.}  
+Identical to Figure \ref{fig:baseline_sham_clustering}, but including additional curves for the case of $M_{\rm host}-$dependent orphan selection (orange curves), and no orphans at all (red curves). 
+}
+\label{fig:orphan_baseline_clustering}
+\end{figure*}
+%-----------------------------------------------------------------------------------------------------
+
+%---------------------------------------------------------------------------------------------------
+\begin{figure*}
+\centering
+\includegraphics[width=12cm]{FIGS/clustering_ratios_orphan_impact.pdf}
+\caption{
+{\bf Impact of orphans on $\rhalf-$dependent clustering.}  
+Identical to Figure \ref{fig:clustering_ratio_upshot}, but including additional curves for the case of $M_{\rm host}-$dependent orphan selection (orange curves), and no orphans at all (red curves). 
+}
+\label{fig:orphan_size_clustering}
+\end{figure*}
+%-----------------------------------------------------------------------------------------------------
+
 \end{document}

### 2017-11-26 paper/galsize_paper.tex
Resolved mysterious latex compilation bug by commenting out use of latex geometry package - pushing new branch to avoid potential conflicts with possible changes already locally implemented by @a-kravtsov
Further changes to abstract

@@
 \documentclass[usenatbib,usegraphicx,letterpaper]{mn2e}
-\usepackage[totalwidth=480pt,totalheight=680pt]{geometry}
+%\usepackage[totalwidth=480pt,totalheight=680pt]{geometry}
 
@@
 \begin{abstract}
-Using new SDSS measurements of projected galaxy clustering, $\wproj(\rproj),$ we place empirical constraints on the connection between galaxy size, $\rhalf,$ and halo virial radius, $\rvir.$  
+Using new SDSS measurements of projected galaxy clustering, $\wproj(\rproj),$ we place empirical constraints on the connection between galaxy size and halo virial radius.  
 We find that small galaxies cluster much more strongly than large galaxies of the same stellar mass. 
-The size-dependence of $\wproj(\rproj)$ increases on smaller scales, and decreases at larger stellar mass.
-Using {\tt Halotools} to forward model the observations, we show that a simple empirical model, in which galaxy $\rhalf$ is proportional to halo $\rvir$ at the time when halo mass reached its maximum,
-reproduces the observed size-dependence of $\wproj(\rproj)$ in striking detail. 
-We show that the success of this model provides strong support for the conclusion that satellite galaxies have smaller sizes relative to central galaxies of the same halo mass. 
-Our findings indicate that the sizes of satellites are set prior to the time of satellite infall, and that a remarkably simple, linear size--virial radius relation emerges from the complex physics regulating galaxy size.
-%We conclude with a prediction that future measurements of galaxy-galaxy lensing will show that small galaxies exhibit a significantly stronger lensing signal relative to large galaxies.of the same stellar mass.
+The magnitude of this clustering difference increases on small scales, and decreases with stellar mass.
+Using {\tt Halotools} to forward model the observations, we test a simple empirical model in which present-day galaxy size is proportional to the size of the virial radius at the time the halo reached its maximum mass.
+This simple model reproduces the observed size-dependence of $\wproj(\rproj)$ in striking detail.
+The success of this model provides strong support for the conclusion that satellite galaxies have smaller sizes relative to central galaxies of the same halo mass. 
+Our findings indicate that satellite size is set prior to the time of infall, and that a remarkably simple, linear size--virial radius relation emerges from the complex physics regulating galaxy size.
+We make quantitative predictions for future measurements of galaxy-galaxy lensing, including dependence upon size, scale, and stellar mass, and provide a simple scaling relation that can be used to calibrate hydrodynamical simulations and semi-analytic models.
 \end{abstract}

### 2017-11-26 paper/galsize_paper.tex
Grammatical changes to intro

@@
 
-The approach we take is to forward model the $\rhalf-$halo connection: we generate Monte Carlo realizations of models using a high-resolution cosmological $N$-body simulation, and then make synthetic measurements in a manner that closely mimics the measurements we make on our observed galaxy samples.
+The approach we take is to forward model the $\rhalf-$halo connection: we generate Monte Carlo realizations of models using a high-resolution cosmological $N$-body simulation, and then make synthetic measurements in a manner that closely mimics the measurements we make on observed galaxies.
 We describe the dataset and simulations we use in \S\ref{sec:data}.

### 2017-11-26 paper/galsize_paper.tex
Minor grammatical changes to section 3, 4.1 and 4.2

@@
 The {\em bottom left panel} compares the stellar mass functions $\phi(\mstar)$ of the two samples, confirming that our method for separating ``small" from ``large" galaxies yields subsamples with statistically indistinguishable $\phi(\mstar)$.
-The {\em bottom right panel} shows histograms of $\rhalf$ for the two subsamples, which partially overlap due to the stellar mass range spanned by the volume-limited, $\mstar$-threshold sample.
+The {\em bottom right panel} shows histograms of $\rhalf$ for the two subsamples, which partially overlap due to the stellar mass range spanned by the sample.
 }
@@
 
-As noted in \S\ref{sec:intro}, \citet{kravtsov13} showed that galaxy sizes are on average proportional to the virial radius of their host halo.
+As noted in \S\ref{sec:intro}, it was shown in \citet{kravtsov13} that galaxy sizes are on average proportional to the virial radius of their host halo.
 Motivated by these results, we  explore a model in which $\rhalf$ scales linearly with halo virial radius:\footnote{We note that the normalization factor in \citet{kravtsov13} is 0.015, whereas our normalization is 0.01.
@@
 
-As shown in Figure \ref{fig:baseline_sham_clustering}, the abundance matching prediction for $\wproj(\rproj)$ exhibits tension with SDSS observations at the $10-20\%$ level, particularly for $\mstar\gtrsim10^{10.75}\msun.$ This tension is inherited by our $\rvir-$based model for size, which is the subject of this work, and so we wish to compare our size models to data in such a way that minimizes the role played by the underlying stellar-to-halo-mass relation.
+As shown in Figure \ref{fig:baseline_sham_clustering}, the abundance matching prediction for $\wproj(\rproj)$ exhibits tension with SDSS observations at the $10-20\%$ level.
+This tension is inherited by our $\rvir-$based model for size, which is the subject of this work, and so we wish to compare our size models to data in such a way that minimizes the role played by the underlying stellar-to-halo-mass relation.
 We accomplish this using the {\em $\rhalf$ clustering ratios,} described below.

### 2017-11-26 paper/galsize_paper.tex
Minor edits to 4.3

@@
 The points and curves in Figure \ref{fig:clustering_ratio_upshot} are almost all negative: small galaxies cluster more strongly relative to large.
-This presentation of the measurement makes it clear that the underlying signal of $\rhalf-$dependent clustering is strongest for samples with smaller stellar mass; as $\mstar$ increases, the signal weakens and nearly vanishes for $\mstar\gtrsim10^{11}\msun.$ Strikingly, the $\rvir-$based model reproduces this $\mstar-$dependent behavior, as well as the scale-dependence of the observed clustering signal at each $\mstar.$ As described in \S\ref{subsec:censat_sizes} below, we attribute the success of this prediction to the systematic difference of sizes of central and satellite galaxies.
+This presentation of the measurement makes it clear that the underlying signal of $\rhalf-$dependent clustering is strongest for samples with smaller stellar mass; as $\mstar$ increases, the signal weakens and nearly vanishes for $\mstar\gtrsim10^{11}\msun.$ Strikingly, the $\rvir-$based model reproduces this $\mstar-$dependent behavior, as well as the scale-dependence of the observed clustering signal at each $\mstar.$ As described in \S\ref{subsec:censat_sizes} below, we attribute the success of this prediction to the systematic difference between the sizes of central and satellite galaxies.
 
@@
 
-Figure~\ref{fig:mstarmodelclustering} shows a similar comparison of the observed clustering ratios to the model
-in which size is controlled by $\mstar$ with sizes of satellites affected by stellar mass loss due to tides (\S\ref{subsubsec:strippingmodel}).
-Green solid lines show predictions of the model that does not account for stellar
-mass loss of satellites due to tides.
-In this model $\rhalf$ follows a purely random log-normal distribution centered at $\median{\rhalf}{\mstar}$ with the median relation matched to the observed relation by construction.
+Figure~\ref{fig:mstarmodelclustering} is analogous to Figure \ref{fig:clustering_ratio_upshot}, but instead compares observed clustering ratios to those predicted by models
+in which galaxy size is controlled by $\mstar$ (\S\ref{subsubsec:strippingmodel}).
+Green solid lines show predictions of the $\mstar$-based model that does not account for mass loss due to tides.
+In this model, $\rhalf$ follows a purely random log-normal distribution, with the median relation $\median{\rhalf}{\mstar}$ directly matched to the observed relation by construction.
 This model thus predicts no dependence of galaxy clustering upon $\rhalf$ at fixed $\mstar,$ simply because the scatter of $\rhalf$ about $\median{\rhalf}{\mstar}$ is uncorrelated with any other variable.
@@
 
-Inclusion of satellite mass loss in the model introduces correlations in the scatter: after mass loss, satellites have smaller sizes than centrals of the same $\mstar$ due to post-infall stripping.
+Inclusion of satellite mass loss in the model introduces correlations in the scatter: after mass loss, satellites have smaller sizes than centrals of the same $\mstar$ due to post-infall tidal stripping.
 The purple curves in Figure \ref{fig:mstarmodelclustering} show that satellite mass loss impacts $\rhalf-$dependent clustering in the expected manner.

### 2017-11-26 paper/galsize_paper.tex
Minor edits to 4.4

@@
 We now examine how galaxy clustering depends on size when we control both for stellar mass and color dependence of galaxy clustering.
-Using the $\mstar>10^{10.25}\msun$ sample used above, we first divide the sample into ``red" and ``blue" subsamples using $g-r=0.65$ as a boundary, which approximately corresponds to the trough of the green valley for this stellar mass.
-For each color-selected subsample, we separately measure $\median{\rhalf}{\mstar; {\rm red}}$ and $\median{\rhalf}{\mstar; {\rm blue}},$ and use these median size values to split each subsample into two.
+Using a volume-limited galaxy sample with $10^{9.75}\msun < \mstar< 10^{10.25}\msun,$ we first divide the sample into ``red" and ``blue" subsamples using $g-r=0.65$ as a boundary, which approximately corresponds to the trough of the green valley for this stellar mass.
+For each color-selected subsample, we separately measure $\median{\rhalf}{\mstar; {\rm red}}$ and $\median{\rhalf}{\mstar; {\rm blue}},$ and use these median size relations to split each subsample into two.
 

### 2017-11-26 paper/galsize_paper.tex
edited abstract and conclusions

--- 2017-11-26 paper/galsize_paper.tex
@@
 \begin{abstract}
-Using new SDSS measurements of projected galaxy clustering, $\wproj(\rproj),$ we place empirical constraints on the connection between galaxy size and halo virial radius.  
+Using new measurements of projected two-point correlation function, $\wproj(\rproj)$, of  the Sloan Digital Sky Survey galaxies of different sizes and stellar masses,
+ we place empirical constraints on the connection between galaxy size and halo virial radius.  
 We find that small galaxies cluster much more strongly than large galaxies of the same stellar mass. 
-The magnitude of this clustering difference increases on small scales, and decreases with stellar mass.
-Using {\tt Halotools} to forward model the observations, we test a simple empirical model in which present-day galaxy size is proportional to the size of the virial radius at the time the halo reached its maximum mass.
-This simple model reproduces the observed size-dependence of $\wproj(\rproj)$ in striking detail.
-The success of this model provides strong support for the conclusion that satellite galaxies have smaller sizes relative to central galaxies of the same halo mass. 
-Our findings indicate that satellite size is set prior to the time of infall, and that a remarkably simple, linear size--virial radius relation emerges from the complex physics regulating galaxy size.
-We make quantitative predictions for future measurements of galaxy-galaxy lensing, including dependence upon size, scale, and stellar mass, and provide a simple scaling relation that can be used to calibrate hydrodynamical simulations and semi-analytic models.
+The magnitude of this clustering difference increases on small scales, and decreases with increasing stellar mass. 
+Using {\tt Halotools} to forward model the observations, we test a simple empirical model in which present-day galaxy size is 
+proportional to the size of the virial radius at the time the halo reached its maximum mass. This simple model reproduces the 
+observed size-dependence of $\wproj(\rproj)$ in striking detail. 
+The success of this model provides strong support for the conclusion that satellite galaxies have smaller sizes relative to central 
+galaxies of the same halo mass. 
+Our findings indicate that satellite size is set prior to the time of infall, and that a remarkably simple, linear size--virial radius relation 
+emerges from the complex physics regulating galaxy size. 
+We make quantitative predictions for future measurements of galaxy-galaxy lensing, including dependence upon size, scale, 
+and stellar mass, and provide a simple scaling relation of the ratio of mean sizes of satellites and central galaxies as a function of their halo mass 
+that can be used to calibrate hydrodynamical simulations and semi-analytic models. 
 \end{abstract}
@@
 \item Small galaxies cluster more strongly than large galaxies of the same stellar mass.
-Differences between the clustering of small and large galaxies increase on small scales $\rproj\lesssim1\mpc,$ and decrease with stellar mass (see Figure \ref{fig:rvir_only_clustering_absolute}).
+Differences between the clustering of small and large galaxies increase on small scales $\rproj\lesssim1\mpc,$ and decrease with increasing stellar mass (see Figure \ref{fig:rvir_only_clustering_absolute}).
 \item The most important factor influencing the clustering signal is the relative size of central and satellite galaxies.
@@
 \item Models in which $\rhalf$ is regulated by $\mstar,$ rather than $\mhalo,$ are grossly discrepant with the observed $\wproj(\rproj),$ even when accounting for satellite mass stripping (see Figure \ref{fig:mstarmodelclustering}).
-\item Taken together, our findings indicate that satellite-specific processes play a sub-dominant role in setting the different sizes of centrals and satellites; these size differences instead appear to be largely predetermined at the time of satellite infall.
+\item Taken together, our findings indicate that satellite-specific processes play a sub-dominant role in setting the different sizes of centrals and satellites; the sizes of satelitte galaxies instead appear to be largely predetermined at the time of their infall.
 \item The $\rvir$-based size model that reproduces the observed $\wproj(\rproj)$ makes an unambiguous  prediction for future observations of galaxy-galaxy lensing: for $\mstar-$selected samples, $\Delta\Sigma$ should be much stronger for small galaxies relative to large (see Figure \ref{fig:lensingprediction}).
@@
 
+\newpage
 \section*{Appendix: Treatment of Disrupted Subhalos}
+
+%---------------------------------------------------------------------------------------------------
 
@@
 
-Figure \ref{fig:orphan_baseline_clustering} shows how the treatment of orphans impacts $\mstar-$dependent clustering.
-Comparing either the black or orange curves to the red curves shows that including orphans substantially boosts small-scale clustering due to the increased satellite fraction.
-We show the impact of orphans on $\rhalf-$dependent clustering in Figure \ref{fig:orphan_size_clustering}.
-As discussed in \S\ref{subsec:censat_sizes}, the value of $\fsat$ modulates the magnitude of the influence of central/satellite size differences on $\wproj;$ including orphans thus boosts the clustering ratios $\delta\wproj/\wproj.$ Because we have not been systematic in the calibration of $\mathcal{F}_{\rm orphan},$ we adopt the simpler, random orphan selection as the fiducial model shown in the main body of the text.
-
-%---------------------------------------------------------------------------------------------------
 \begin{figure}
@@
 \end{figure}
+
+Figure \ref{fig:orphan_baseline_clustering} shows how the treatment of orphans impacts $\mstar-$dependent clustering.
+Comparing either the black or orange curves to the red curves shows that including orphans substantially boosts small-scale clustering due to the increased satellite fraction.
+We show the impact of orphans on $\rhalf-$dependent clustering in Figure \ref{fig:orphan_size_clustering}.
+As discussed in \S\ref{subsec:censat_sizes}, the value of $\fsat$ modulates the magnitude of the influence of central/satellite size differences on $\wproj;$ including orphans thus boosts the clustering ratios $\delta\wproj/\wproj.$ Because we have not been systematic in the calibration of $\mathcal{F}_{\rm orphan},$ we adopt the simpler, random orphan selection as the fiducial model shown in the main body of the text.
+
 %-----------------------------------------------------------------------------------------------------

### 2017-11-26 paper/galsize_paper.tex
Minor edits to section 5

--- 2017-11-26 paper/galsize_paper.tex
@@
 First, the model that assumes $\rhalf\propto\rvir$ predicts a dependence of both the amplitude and shape of  size-dependent galaxy correlation functions remarkably well, especially considering that the model nominally has only one free parameter: the normalization of the linear $\rhalf-\rvir$ relation.
-At the same time, small galaxies cluster more strongly relative to large, which seems at odds with naive expectations that, within such a model, larger sizes correspond to larger halo masses, $\rvir\propto\mvir^{1/3}$, and so larger sizes should be clustered more strongly.
+At the same time, small galaxies cluster more strongly relative to large, which seems at odds with intuitive expectations that, within such a model, larger sizes correspond to larger halo masses, $\rvir\propto\mvir^{1/3}$; thus  naively, galaxies with larger sizes should be more strongly clustered, not less.
 Second, the strong dependence of galaxy clustering on size weakens to almost no dependence for samples of red and blue galaxies selected by color within a given stellar mass range.

### 2017-11-26 paper/galsize_paper.tex
Minor edits to section 6

@@
 
-To date, the $\rhalf-$dependence of $\Delta\Sigma$ not yet been measured for $\mstar-$complete samples.
+To date, the $\rhalf-$dependence of $\Delta\Sigma$ has not yet been measured for $\mstar-$complete samples.
 In the left panels of Figure \ref{fig:lensingprediction}, we show predictions of the $\rvir-$based model for future measurements of $\Delta\Sigma.$ The halo model principles underlying the lensing trends are the same as for $\wproj.$ For $\mstar\lesssim10^{11}\msun,$ the difference in $F_{\rm sat}$ between small and large samples is the dominant factor; satellites occupy higher mass host halos relative to centrals of the same stellar mass, boosting $\Delta\Sigma$ for small relative to large galaxy samples.
@@
 
-The right panels of Figure \ref{fig:lensingprediction} compare the distributions of host halo mass, $\mhost,$ for small and large samples;\footnote{We calculated the PDFs shown in Figure \ref{fig:lensingprediction} using the Scipy implementation of Gaussian kernel density estimation \citep{scipy}.} for centrals, $\mhost=\mhalo,$ while for satellites, $\mhost$ is the virial mass of the parent halo.
+The right panels of Figure \ref{fig:lensingprediction} compare the distributions of host halo mass, $\mhost,$ for small and large samples; for centrals, $\mhost=\mhalo,$ while for satellites, $\mhost$ is the virial mass of the parent halo.
 The peak of each distribution arises from central galaxies, while the long tail at large values of $\mhost$ is due to satellites.
-At all stellar masses, the blue histograms peak at slightly larger $\mhost$ relative to the red; this is because the $\rvir-$based model predicts that $\mhalo$ increases with $\rhalf$ for centrals.
+At all stellar masses, the distributions in blue peak at slightly larger $\mhost$ relative to the red; this is because the $\rvir-$based model predicts that $\mhalo$ increases with $\rhalf$ for centrals.
 For $\mstar-$complete samples, this effect only becomes dominant when the satellite fraction drops to sufficiently small values.

### 2017-11-26 paper/galsize_paper.tex
Finished editing section 7

@@
 For example,   two-dimensional (projected) sizes of observed galaxies are sometimes de-projected to estimate three-dimensional sizes; such a correction applied to the data requires treating disk-dominated and spheroidal systems separately.
-The forward modeling approach turns the direction of this correction around: three-dimensional sizes of disk and bulge components are modeled separately; the projected size can then be computed self-consistently with the modeled value of ${\rm B/T},$ permitting a more apples-to-apples comparison to observations of projected size.
+The forward modeling approach turns the direction of this correction around: three-dimensional sizes of disk and bulge components are modeled separately; the projected size can then be computed self-consistently with the modeled value of ${\rm B/T},$ permitting a more rigorous, ``apples-to-apples" comparison to observations of projected size.
 This follow-up analysis will also help robustly quantify the extent to which the ``cause" of satellites being smaller than centrals is due to differences in ${\rm B/T}.$

### 2017-11-26 paper/galsize_paper.tex
Minor changes to Section 8
Minor edits to captions

@@
 \caption{
-{\bf Definition of ``small" and ``large" galaxies.} For a volume-limited SDSS galaxy sample defined by $M_{\ast}>10^{10.25}M_{\odot},$ the {\em top panel} visually demonstrates how we classify galaxies into ``small" and ``large" subsamples.
+{\bf Definition of ``small" and ``large" galaxies.} For a volume-limited SDSS galaxy sample defined by $M_{\ast}>10^{10.25}M_{\odot},$ the {\em top panel} visually demonstrates how we classify galaxies into ``small" and ``large" subsamples in an $\mstar$-dependent manner.
 As described in detail in \S\ref{subsec:sizedef}, we compute the median value $\median{\rhalf}{\mstar}$ at the stellar mass of each galaxy in the sample, and divide the sample into two based on this $\mstar-$dependent cut.
@@
 \caption{
-{\bf $\rhalf-$dependence of galaxy clustering.}
+{\bf $\rhalf-$dependence of galaxy clustering: comparison to $\rvir$-based model.}
 Red and blue points with error bars show our SDSS measurements of the clustering of small and large galaxies, respectively.
@@
 \caption{
-{\bf $\rhalf-$dependence of galaxy clustering.}
-Closely related to Figure \ref{fig:rvir_only_clustering_absolute}, the y-axes show {\em clustering strength ratios,} defined as $\delta\wproj/\wproj\equiv(w_{\rm p}^{\rm large} - w_{\rm p}^{\rm small})/w_{\rm p}^{\rm all}.$ Thus a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass.
-Solid curves show the clustering ratio predictions of the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}.
+{\bf $\rhalf-$dependence of galaxy clustering: comparison to $\rvir$-based model.}
+Closely related to Figure \ref{fig:rvir_only_clustering_absolute}, y-axes show {\em clustering strength ratios,} defined as $\delta\wproj/\wproj\equiv(w_{\rm p}^{\rm large} - w_{\rm p}^{\rm small})/w_{\rm p}^{\rm all}.$ Thus a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass.
+Solid curves show predictions of the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}.
 Normalizing the measurements and predictions by $w_{\rm p}^{\rm all}$ scales away the shortcoming of ordinary abundance matching (see Figure \ref{fig:baseline_sham_clustering}), highlighting the successful prediction of the $\rvir-$based model for the $\rhalf-$dependence of galaxy clustering.
@@
 For $\mstar\gtrsim10^{11}\msun,$ when $F_{\rm sat}\lesssim10\%,$ central galaxies dominate the signal, and the $\rvir-$based model predicts that $\rhalf$ increases with $\mhalo$ for centrals.
-See text for further details.
+See \S\ref{sec:previous_work} for further details.
 }
@@
 
+We view the present work as a pilot study that motivates a Bayesian inference program to tightly constrain the galaxy size-halo connection with forward modeling techniques, in direct analogy to the literature on the stellar-to-halo-mass relation.
 Our results provide an integral constraint for more complex and fine-grained models of galaxy size, such as semi-analytic models and hydrodynamical simulations.
 For convenience, Figure \ref{fig:censatsizeratios} provides a simple summary statistic that can be used as a diagnostic for calibrating alternative modeling efforts.
-We view the present work as a pilot study that motivates a Bayesian inference program to tightly constrain the galaxy size-halo connection with forward modeling techniques, in direct analogy to the literature on the stellar-to-halo-mass relation.
 

### 2017-11-26 paper/galsize_paper.tex
Fixed two typos

@@
 \begin{abstract}
-Using new measurements of projected two-point correlation function, $\wproj(\rproj)$, of  the Sloan Digital Sky Survey galaxies of different sizes and stellar masses,
+Using new measurements of the projected two-point correlation function, $\wproj(\rproj)$, of  the Sloan Digital Sky Survey galaxies of different sizes and stellar masses,
  we place empirical constraints on the connection between galaxy size and halo virial radius.  
@@
 \item Models in which $\rhalf$ is regulated by $\mstar,$ rather than $\mhalo,$ are grossly discrepant with the observed $\wproj(\rproj),$ even when accounting for satellite mass stripping (see Figure \ref{fig:mstarmodelclustering}).
-\item Taken together, our findings indicate that satellite-specific processes play a sub-dominant role in setting the different sizes of centrals and satellites; the sizes of satelitte galaxies instead appear to be largely predetermined at the time of their infall.
+\item Taken together, our findings indicate that satellite-specific processes play a sub-dominant role in setting the different sizes of centrals and satellites; the sizes of satellite galaxies instead appear to be largely predetermined at the time of their infall.
 \item The $\rvir$-based size model that reproduces the observed $\wproj(\rproj)$ makes an unambiguous  prediction for future observations of galaxy-galaxy lensing: for $\mstar-$selected samples, $\Delta\Sigma$ should be much stronger for small galaxies relative to large (see Figure \ref{fig:lensingprediction}).

### 2017-11-26 paper/galsize_paper.tex
Reworded first sentence of abstract

@@
 \begin{abstract}
-Using new measurements of the projected two-point correlation function, $\wproj(\rproj)$, of  the Sloan Digital Sky Survey galaxies of different sizes and stellar masses,
- we place empirical constraints on the connection between galaxy size and halo virial radius.  
+Using new measurements of $\wproj(\rproj)$, the projected two-point correlation function of galaxies of different sizes and stellar masses observed in the Sloan Digital Sky Survey, we place empirical constraints on the connection between galaxy size and halo virial radius.
 We find that small galaxies cluster much more strongly than large galaxies of the same stellar mass. 

### 2017-11-26 paper/galsize_paper.tex
Revised opening sentence of abstract

--- 2017-11-26 paper/galsize_paper.tex
@@
 \begin{abstract}
-Using new measurements of the projected two-point correlation function, $\wproj(\rproj)$, of  the Sloan Digital Sky Survey galaxies of different sizes and stellar masses,
- we place empirical constraints on the connection between galaxy size and halo virial radius.  
+We empirically constrain how galaxy size relates to halo virial radius using new measurements of the size- and stellar mass-dependent clustering of galaxies in the Sloan Digital Sky Survey.
 We find that small galaxies cluster much more strongly than large galaxies of the same stellar mass.
@@
 proportional to the size of the virial radius at the time the halo reached its maximum mass. This simple model reproduces the 
-observed size-dependence of $\wproj(\rproj)$ in striking detail. 
+observed size-dependence of galaxy clustering in striking detail. 
 The success of this model provides strong support for the conclusion that satellite galaxies have smaller sizes relative to central 

### 2017-11-27 paper/check_for_irrelevant_files.py
Removed obsolete paper figures

@@ -1,0 +1,30 @@
+import os
+import fnmatch
+import subprocess
+
+
+def fname_generator(root_dirname, basename_filepat):
+    """ Yield the absolute path of all files in the directory tree of ``root_dirname``
+    with a basename matching the input pattern
+    """
+
+    for path, dirlist, filelist in os.walk(root_dirname):
+        for filename in fnmatch.filter(filelist, basename_filepat):
+            yield filename
+
+
+figure_names = list(fname_generator(os.path.dirname(os.path.realpath(__file__)), '*.pdf'))
+
+absent_fignames = []
+used_fignames = []
+command = 'grep "{0}" galsize_paper.tex'
+for figname in figure_names:
+    result = os.system(command.format(figname))
+    if result is 0:
+        used_fignames.append(figname)
+    else:
+        absent_fignames.append(figname)
+
+remove_command = 'git rm FIGS/{0}'
+for figname in absent_fignames:
+    result = os.system(remove_command.format(figname))

### 2017-11-27 paper/galsize_paper.tex
Brought in changes from arXiv_submission1 branch after removing tarball that was uploaded to arXiv and over-writing the merge commit - this is to keep the size of the master branch from becoming too large

@@
 The magnitude of this clustering difference increases on small scales, and decreases with increasing stellar mass. 
-Using {\tt Halotools} to forward model the observations, we test a simple empirical model in which present-day galaxy size is 
+Using {\tt Halotools} to forward model the observations, we test an empirical model in which present-day galaxy size is 
 proportional to the size of the virial radius at the time the halo reached its maximum mass. This simple model reproduces the 
@@
 We make quantitative predictions for future measurements of galaxy-galaxy lensing, including dependence upon size, scale, 
-and stellar mass, and provide a simple scaling relation of the ratio of mean sizes of satellites and central galaxies as a function of their halo mass 
+and stellar mass, and provide a scaling relation of the ratio of mean sizes of satellites and central galaxies as a function of their halo mass 
 that can be used to calibrate hydrodynamical simulations and semi-analytic models. 
@@
 In all panels, the axes and points with error bars are the same as in Figure \ref{fig:clustering_ratio_upshot}.
-The solid green curves shows the prediction of a model where $\rhalf$ is statistically set by $\mstar,$ in the complete absence of satellite mass loss.
+The solid green curves show the prediction of a model where $\rhalf$ is statistically set by $\mstar,$ in the complete absence of satellite mass loss.
 Such a model predicts zero $\rhalf-$dependence to galaxy clustering, in gross tension with observations.
@@
 
-Inclusion of satellite mass loss in the model introduces correlations in the scatter: after mass loss, satellites have smaller sizes than centrals of the same $\mstar$ due to post-infall tidal stripping.
+Including satellite mass loss in the model introduces correlations in the scatter: after mass loss, satellites have smaller sizes than centrals of the same $\mstar$ due to post-infall tidal stripping.
 The purple curves in Figure \ref{fig:mstarmodelclustering} show that satellite mass loss impacts $\rhalf-$dependent clustering in the expected manner.
@@
 Thus even though there are more satellites at lower masses, the shape of ${\rm d}\rhalf/{\rm d}\mstar$ counteracts this trend, making the mass-dependence of the observed signal shown in Figure \ref{fig:mstarmodelclustering} difficult to explain by appealing to tidal stripping.
-Evidently it is difficult to strip enough mass from satellites so that the $\rhalf-$dependent clustering predictions are in agreement with observations.
+Evidently, it is difficult to strip enough mass from satellites so that the $\rhalf-$dependent clustering predictions are in agreement with observations.
 We reach the same conclusion when we tested an even more extreme $\mstar-$stripping model, in which stellar mass loss is linearly proportional to halo mass loss \citep[][Model 1]{watson_etal12}.
@@
 In a narrow bin of subhalo mass $\mhalo\equiv\mpeak\approx10^{12}\msun,$ we show the distribution of galaxy sizes for different subpopulations, as predicted by the $\rvir-$based model.
-The red histogram shows the sizes of satellites; the blue histogram shows host halos that have never passed inside the virial radius of a larger halo (``true centrals"); the green histogram host halos that were subhalos inside a larger halo at some point in their past history (``splashback centrals").
+The red distribution shows the sizes of satellites; the blue distribution shows host halos that have never passed inside the virial radius of a larger halo (``true centrals"); the green distribution host halos that were subhalos inside a larger halo at some point in their past history (``splashback centrals").
 In the $\rvir-$based model, galaxy size is set by the {\em physical} size of the virial radius at the time the halo attains its peak mass, naturally resulting in smaller sizes for satellites and splashback centrals relative to true centrals of the same mass.
@@
 In the previous section, comparing model predictions to the observed size dependence of galaxy clustering produced two intriguing results.
-First, the model that assumes $\rhalf\propto\rvir$ predicts a dependence of both the amplitude and shape of  size-dependent galaxy correlation functions remarkably well, especially considering that the model nominally has only one free parameter: the normalization of the linear $\rhalf-\rvir$ relation.
+First, the model that assumes $\rhalf\propto\rvir$ predicts with remarkable accuracy the dependence of both the amplitude and shape of  size-dependent galaxy correlation functions, especially considering that the model nominally has only one free parameter: the normalization of the linear $\rhalf-\rvir$ relation.
 At the same time, small galaxies cluster more strongly relative to large, which seems at odds with intuitive expectations that, within such a model, larger sizes correspond to larger halo masses, $\rvir\propto\mvir^{1/3}$; thus  naively, galaxies with larger sizes should be more strongly clustered, not less.
 Second, the strong dependence of galaxy clustering on size weakens to almost no dependence for samples of red and blue galaxies selected by color within a given stellar mass range.
-Below we propose a simple and unified explanation of all these results within the $\rvir$-based size model in \S\ref{subsec:censat_sizes}, and discuss the broader implications of our interpretation in \S\ref{subsec:broader_implications}.
+Below, in \S\ref{subsec:censat_sizes}, we propose a simple and unified explanation of all these results within the $\rvir$-based size model; we discuss the broader implications of our interpretation in \S\ref{subsec:broader_implications}.
 
@@
 
-Recall that in the $\rvir$-based size model, galaxy size is proportional to halo virial radius at $\zpeak,$ the redshift when the halo attained its maximum mass.
+Recall that in the $\rvir$-based size model, galaxy size is proportional to the physical size of halo virial radius at $\zpeak,$ the redshift when the halo attained its maximum mass.
 Thus we can expect that in this model, satellite galaxies will have smaller sizes than  central galaxies hosted by halos of similar mass.
@@
 Second, at fixed mass, halos of $L_\ast$ galaxies that form earlier are more strongly clustered, a phenomenon commonly known as {\em halo assembly bias} \citep{gao_white05,wechsler_etal06}.
-Splashback halos are typically earlier-forming than true centrals \citep{wang_etal09}, and so models where splashback halos host smaller-than-average galaxies will naturally predict smaller galaxies being the more strongly clustered \citep[see][for an example of the splashback-dependence of halo clustering]{sunayama_etal16}.
+Splashback halos are typically earlier-forming than true centrals \citep{wang_etal09}, and so models where splashback halos host smaller-than-average galaxies will naturally predict smaller galaxies being the more strongly clustered \citep[see, e.g.,][for a demonstration of the splashback-dependence of halo clustering]{sunayama_etal16}.
 
-We can also understand how the observed $\rhalf-$dependent clustering scales with $\mstar$ (shown by comparing different panels in Figure \ref{fig:clustering_ratio_upshot}) in terms of the different of size of centrals and satellites.
+We can also understand how the observed $\rhalf-$dependent clustering scales with $\mstar$ (shown by comparing different panels in Figure \ref{fig:clustering_ratio_upshot}) in terms of the different sizes of centrals and satellites.
 The satellite fraction $F_{\rm sat}(\mstar)$ decreases as $\mstar$ increases \citep[e.g.,][]{guo_etal11,reddick_etal13}.
@@
 Thus,  high-$\mstar$ samples consist mostly of central galaxies, and the split by size no longer corresponds to the split into satellite- and central-dominated samples.
-The size dependence of clustering correspondingly weakens and nearly disappears for samples with large $\mstar$.
+The size-dependence of clustering correspondingly weakens and nearly disappears for samples with large $\mstar$.
 
@@
 Using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}, in the {\em left panels} we show predictions for future measurements of the $\rhalf-$dependence of galaxy lensing of $\mstar-$complete samples, where ``small" and ``large" subsamples are defined as in \S\ref{subsec:sizedef}.
-To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which the observed trends are reversed and weaker than those predicted here: for both blue and red samples, the observed $\Delta\Sigma$ of large galaxies is (slightly) stronger relative to small galaxies.
+To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which the observed trends are reversed and weaker than those predicted here: for both blue and red samples in CFHTLenS, the observed $\Delta\Sigma$ of large galaxies is (slightly) stronger relative to small galaxies.
 As a generic consequence of satellites being smaller than centrals of the same mass, we predict that future lensing measurements of $\mstar-$complete samples will show that $\Delta\Sigma$ of small galaxies is significantly stronger relative to large galaxies of the same stellar mass $\mstar\lesssim10^{11}\msun.$ We additionally predict that at sufficiently large mass $\mstar\gtrsim10^{11}\msun,$ the trend of small-scale $\Delta\Sigma$ with $\rhalf$ reverses sign.
@@
 
-This work is intended to serve as a pilot study in which we identify the chief ingredients that can influence the $\rhalf-$dependence of galaxy clustering.
+This work is intended to serve as a pilot study in which we identify the chief ingredients that influence the $\rhalf-$dependence of galaxy clustering.
 While our results suggest that sizes of galaxies are linearly correlated with the
@@
 For example, two-dimensional (projected) sizes of observed galaxies are sometimes de-projected to estimate three-dimensional sizes; such a correction applied to the data requires treating disk-dominated and spheroidal systems separately.
-The forward modeling approach turns the direction of this correction around: three-dimensional sizes of disk and bulge components are modeled separately; the projected size can then be computed self-consistently with the modeled value of ${\rm B/T},$ permitting a more rigorous, ``apples-to-apples" comparison to observations of projected size.
+The forward modeling approach transforms this correction into parameterized inference: three-dimensional sizes of disk and bulge components are modeled separately and mapped onto dark matter halos; the projected size of model galaxies can then be computed self-consistently with the modeled value of ${\rm B/T},$ permitting a more rigorous, ``apples-to-apples" comparison to observations of projected size.
 This follow-up analysis will also help robustly quantify the extent to which the ``cause" of satellites being smaller than centrals is due to differences in ${\rm B/T}.$
@@
 We model $\mathcal{F}_{\rm orphan}=\mathcal{F}_{\rm orphan}(M_{\rm peak},M_{\rm host}),$ where $\mpeak$ is the peak mass of the disrupted subhalo, and $\mhost$ is the present-day virial mass of its $z=0$ host halo.
-For the $\mpeak-$dependence, we select $50\%$ of disrupted subhalos with $\mpeak=10^{11}\msun,$ $0\%$ of subhalos with $\mpeak=10^{13}\msun,$ linearly interpolating in $\log\mpeak$ for intermediate values of $\mpeak.$ At each $\mpeak,$ the selection of disrupted halos is not random; instead, we preferentially select the subhalos with larger $\mhost,$ which we intend to offset the increased difficulty of subhalo-finding algorithms to identify subhalos with especially small values of  $\mu\equiv\mpeak/\mhost.$
+For the $\mpeak-$dependence, we select $50\%$ of disrupted subhalos with $\mpeak=10^{11}\msun,$ $0\%$ of subhalos with $\mpeak=10^{13}\msun,$ linearly interpolating in $\log\mpeak$ for intermediate values of $\mpeak.$ At each $\mpeak,$ the selection of disrupted halos is not random; instead, we preferentially select the subhalos with larger $\mhost,$ which we intend to offset the difficulty of subhalo-finding algorithms to identify subhalos with especially small values of  $\mu\equiv\mpeak/\mhost.$
 

### 2017-11-27 paper/submission_notes.tex
Brought in changes from arXiv_submission1 branch after removing tarball that was uploaded to arXiv and over-writing the merge commit - this is to keep the size of the master branch from becoming too large

--- 2017-11-27 paper/galsize_paper.tex
@@
-\documentclass[usenatbib,usegraphicx,letterpaper]{mn2e}
-%\usepackage[totalwidth=480pt,totalheight=680pt]{geometry}
+Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies
 
-\usepackage{lmodern}
+Andrew Hearin, Peter Behroozi, Andrey Kravtsov, Benjamin Moster
 
-\usepackage{amsmath}
-\usepackage{amstext}
-\usepackage{amssymb}
-\usepackage{yfonts}
-
-\usepackage{epsfig}
-\usepackage{graphicx}
-\usepackage{color}
-
-\usepackage[lowtilde]{url}
-\usepackage{hyperref}
-
-\bibliographystyle{mn2e}
-
-%-------- journals
-\newcommand{\araa}{ARAA~}
-\newcommand{\apj}{ApJ~}
-\newcommand{\apjl}{ApJL~}
-\newcommand{\apjs}{ApJS~}
-\newcommand{\mnras}{MNRAS~}
-\newcommand{\nat}{Nature~}
-\newcommand{\physrep}{Phys. Rep.~}
-\newcommand{\aj}{AJ~}
-\newcommand{\pasp}{ASP~}
-
-%%%% Misc %%%
-\newcommand{\beq}{\begin{equation}}
-\newcommand{\eeq}{\end{equation}}
-\newcommand{\beqray}{\begin{eqnarray}}
-\newcommand{\eeqray}{\end{eqnarray}}
-
-\newcommand{\ben}{\begin{enumerate}}
-\newcommand{\een}{\end{enumerate}}
-\newcommand{\bit}{\begin{itemize}}
-\newcommand{\eit}{\end{itemize}}
-
-%%%%%%%%  galaxy properties  %%%%%%%%
-\newcommand{\rhalf}{R_{1/2}}
-\newcommand{\rhalfdisk}{R_{1/2}^{\rm disk}}
-\newcommand{\rhalfbulge}{R_{1/2}^{\rm bulge}}
-\newcommand{\adisk}{A_{\rm disk}}
-\newcommand{\abulge}{A_{\rm bulge}}
-\newcommand{\alphadisk}{\alpha_{\rm disk}}
-\newcommand{\alphabulge}{\alpha_{\rm bulge}}
-\newcommand{\sigmarhalf}{\sigma_{\rm R_{1/2}}}
-\newcommand{\bt}{{\rm B/T}}
-\newcommand{\mstar}{M_{\ast}}
-\newcommand{\ssfr}{{\rm sSFR}}
-\newcommand{\sfr}{{\rm SFR}}
-\newcommand{\fsat}{F_{\rm sat}}
-
-%%%%%%%%  halo properties  %%%%%%%%
-\newcommand{\halospin}{\lambda_{\rm halo}}
-\newcommand{\mvir}{M_{\rm vir}}
-\newcommand{\macc}{M_{\rm acc}}
-\newcommand{\mpeak}{M_{\rm peak}}
-\newcommand{\zpeak}{z_{M_{\rm peak}}}
-\newcommand{\mhalo}{M_{\rm halo}}
-\newcommand{\mhost}{M_{\rm host}}
-\newcommand{\rvir}{R_{\rm vir}}
-\newcommand{\rmpeak}{R_{\rm M_{peak}}}
-\newcommand{\vmaxmpeak}{V_{\rm peak}}
-\newcommand{\vmax}{V_{\rm max}}
-\newcommand{\rspeak}{{R_{\rm s,}}_{\rm M_{peak}}}
-
-%%%%%%%%  cosmology  %%%%%%%%
-\newcommand{\lcdm}{\Lambda{\rm CDM}}
-
-%%%%%%%%  observations  %%%%%%%%
-\newcommand{\rproj}{r_{\rm p}}
-\newcommand{\wproj}{w_{\rm p}}
-\newcommand{\wplarge}{w_{\rm p}^{\rm large}}
-\newcommand{\wpsmall}{w_{\rm p}^{\rm small}}
-\newcommand{\wpall}{w_{\rm p}^{\rm all}}
-\newcommand{\mean}[2]{\langle{#1}\vert{#2}\rangle}
-\newcommand{\median}[2]{\langle{#1}\vert{#2}\rangle_{\rm median}}
-
-%%%%%%%%  units  %%%%%%%%
-\newcommand{\kpc}{{\rm kpc}}
-\newcommand{\mpc}{{\rm Mpc}}
-\newcommand{\msun}{M_\odot}
-\newcommand{\kms}{{\rm km/s}}
-
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-\usepackage{epsfig}  \usepackage{graphicx}   \usepackage{rotating}
-
-\begin{document}
-
-\title[The Relative Sizes of Centrals and Satellites]
-{Clustering Constraints on the Relative Sizes of Central and Satellite Galaxies}
-
-\author[Hearin, Behroozi, Kravtsov \& Moster]{
-Andrew Hearin$^{1}$, Peter Behroozi$^{2}$, Andrey Kravtsov$^{3}$, Benjamin Moster$^{4,5}$\\
-$^{1}$Argonne National Laboratory, Argonne, IL, USA 60439, USA\\
-$^{2}$Department of Physics, University of Arizona, 1118 E 4th St, Tucson, AZ 85721 USA\\
-$^{3}$Department of Astronomy \& Astrophysics, and Kavli Institute for Cosmological Physics, The University of Chicago, Chicago IL 60637\\
-$^{4}$Universit{\"a}ts-Sternwarte, Ludwig-Maximilians-Universit{\"a}t M{\"u}nchen, Scheinerstr. 1, 81679 M{\"u}nchen, Germany\\
-$^5$Max-Planck Institut f\"ur Astrophysik, Karl-Schwarzschild Stra\ss e 1, 85748 Garching, Germany
-}
-
-\maketitle
-
-\begin{abstract}
 We empirically constrain how galaxy size relates to halo virial radius using new measurements of the size- and stellar mass-dependent clustering of galaxies in the Sloan Digital Sky Survey.
@@
 The magnitude of this clustering difference increases on small scales, and decreases with increasing stellar mass.
-Using {\tt Halotools} to forward model the observations, we test an empirical model in which present-day galaxy size is 
-proportional to the size of the virial radius at the time the halo reached its maximum mass. This simple model reproduces the 
-observed size-dependence of galaxy clustering in striking detail. 
-The success of this model provides strong support for the conclusion that satellite galaxies have smaller sizes relative to central 
-galaxies of the same halo mass. 
-Our findings indicate that satellite size is set prior to the time of infall, and that a remarkably simple, linear size--virial radius relation 
-emerges from the complex physics regulating galaxy size. 
-We make quantitative predictions for future measurements of galaxy-galaxy lensing, including dependence upon size, scale, 
-and stellar mass, and provide a scaling relation of the ratio of mean sizes of satellites and central galaxies as a function of their halo mass 
-that can be used to calibrate hydrodynamical simulations and semi-analytic models. 
-\end{abstract}
+Using Halotools to forward model the observations, we test an empirical model in which present-day galaxy size is proportional to the size of the virial radius at the time the halo reached its maximum mass.
+This simple model reproduces the observed size-dependence of galaxy clustering in striking detail.
+The success of this model provides strong support for the conclusion that satellite galaxies have smaller sizes relative to central galaxies of the same halo mass.
+Our findings indicate that satellite size is set prior to the time of infall, and that a remarkably simple, linear size--virial radius relation emerges from the complex physics regulating galaxy size.
+We make quantitative predictions for future measurements of galaxy-galaxy lensing, including dependence upon size, scale, and stellar mass, and provide a scaling relation of the ratio of mean sizes of satellites and central galaxies as a function of their halo mass that can be used to calibrate hydrodynamical simulations and semi-analytic models.
 
-%----------------------------
-\section{Introduction}
-\label{sec:intro}
-%----------------------------
-
-Many properties of observed galaxies exhibit remarkably tight scaling relations.
-Galaxy size, typically quantified by a half-mass or half-light radius, $\rhalf,$ has well-measured scaling with galaxy mass $\mstar$ in the local Universe \citep{shen_etal03,huang_etal13,lange_etal15,zhang_yang17}, and at higher redshift \citep{trujillo_etal04,huertas_company_etal13a,vanderwel_etal14,kawamata_etal15,shibuya_etal15,huang_etal17}.
-
-Observational constraints on models for galaxy size typically come from one-point function measurements such as $\mean{\rhalf}{\mstar}$ and $\sigma(\rhalf\vert\mstar),$ e.g.,  \citet{khochfar_silk06,lang_etal14,desmond_etal17,bottrell_etal17b,hou_etal17,somerville_etal17}, or otherwise from catalogs of galaxy groups \citep{weinmann_etal08,guo_etal09,huertas_company_etal13b,spindler_wake17}.
-More recently, the connection between a galaxy's size and the virial radius of its parent halo has been
-explored by converting stellar mass to halo mass and virial radius, using abundance matching \citep{kravtsov_etal04,tasitsiomi_etal04,vale_ostriker04,vale_ostriker06,conroy_etal06}.
-Such analyses have indicated that galaxy size is, on average, proportional to host halo virial radius, both at $z=0$ \citep{kravtsov13}, and higher redshifts \citep{huang_etal17,somerville_etal17}.
-
-Observations of two-point galaxy clustering, $\wproj(\rproj),$ have historically been used to place tight constraints on many features of the galaxy--halo connection, such as its $\mstar-$dependence \citep{moster_etal10,leauthaud_etal11,reddick_etal13,skibba_etal15}, dependence on luminosity \citep{kravtsov_etal04, tasitsiomi_etal04,vale_ostriker04,vale_ostriker06,tinker_etal05,cacciato_etal13}, broadband color \citep{coil_etal08,zehavi_etal11,guo_etal11,hearin_watson13}, and star-formation rate \citep{wang_etal07,tinker_etal13,watson_etal14}.
-In the present work, we exploit the constraining power of $\wproj(\rproj)$ to test empirical models connecting galaxy stellar mass and size to the properties of the galaxy's parent dark matter halo.
-
-The approach we take is to forward model the $\rhalf-$halo connection: we generate Monte Carlo realizations of models using a high-resolution cosmological $N$-body simulation, and then make synthetic measurements in a manner that closely mimics the measurements we make on observed galaxies.
-We describe the dataset and simulations we use in \S\ref{sec:data}.
-Our forward-modeling methods are described in \S\ref{sec:model}, with supplementary material in the Appendix.
-All of our primary results appear in \S\ref{sec:results}, and their theoretical interpretation in \S\ref{sec:interpretation}.
-We contextualize our findings in terms of previous work in \S\ref{sec:previous_work}, and discuss future directions in \S\ref{sec:future}.
-We conclude the paper with a summary of our principal results in \S\ref{sec:conclusion}.
-
-%---------------------------------------------------------------------------------------------------
-\begin{figure*}
-\centering
-\includegraphics[width=9cm]{FIGS/sdss_size_vs_mstar_scatter.pdf}
-\includegraphics[width=\textwidth]{FIGS/sdss_small_large_sample_definitions.pdf}
-\caption{
-{\bf Definition of ``small" and ``large" galaxies.} For a volume-limited SDSS galaxy sample defined by $M_{\ast}>10^{10.25}M_{\odot},$ the {\em top panel} visually demonstrates how we classify galaxies into ``small" and ``large" subsamples in an $\mstar$-dependent manner.
-As described in detail in \S\ref{subsec:sizedef}, we compute the median value $\median{\rhalf}{\mstar}$ at the stellar mass of each galaxy in the sample, and divide the sample into two based on this $\mstar-$dependent cut.
-The {\em bottom left panel} compares the stellar mass functions $\phi(\mstar)$ of the two samples, confirming that our method for separating ``small" from ``large" galaxies yields subsamples with statistically indistinguishable $\phi(\mstar)$.
-The {\em bottom right panel} shows histograms of $\rhalf$ for the two subsamples, which partially overlap due to the stellar mass range spanned by the sample.
-}
-\label{fig:sizedefinition}
-\end{figure*}
-%-----------------------------------------------------------------------------------------------------
-
-%-----------------------------------------
-\section{Data and Simulations}
-\label{sec:data}
-%-----------------------------------------
-
-The starting point for our galaxy samples comes from Data Release 10 of the Sloan Digital Sky Survey \citep[SDSS,][]{ahn_etal14}, with stellar mass measurements taken from the MPA-JHU catalog \citep{kauffmann_etal03,brinchmann_etal04}.
-Discarding galaxies with redshift $z<0.02,$ we define volume-limited, $\mstar-$threshold samples by applying a maximum-redshift cut $z_{\rm max}$ appropriate for the $\mstar$ threshold; we use the same $z_{\rm max}$ cut shown in Figure 2 of \citet{behroozi_etal15}.
-
-We supplement the MPA-JHU catalog with measurements of half-light radius, $\rhalf,$ derived from galaxy profile decompositions provided by \citet{meert_etal15}.
-The \citet{meert_etal15} catalog is based on Data Release 7 of SDSS \citep{abazajian_etal09}, with improvements to the photometry pipeline and light profile fitting method and, especially, in background subtraction \citep{vikram_etal10,bernardi_etal13,bernardi_etal14,meert_etal13}.
-In the version of this catalog that we use,\footnote{Our $\mstar$ and $\rhalf$ measurements are derived from different photometry pipelines; this is driven by our desire for consistency with the \citet{behroozi_etal15} completeness cuts used in our clustering measurements.
-We note that we have repeated our analysis for stellar mass measurements based on \citet{meert_etal15}, finding only minor quantitative, and no qualitative changes to our results.} two-dimensional $r-$band profiles were fit with a two-component de Vaucouleurs + exponential profile to determine the projected half-light radius of total $r-$band luminosity, $\rhalf.$
-
-As the bedrock of our modeling, we use the publicly available\footnote{\url{http://www.slac.stanford.edu/~behroozi/BPlanck\_Hlists}} catalog of {\tt Rockstar} subhalos identified at $z=0$ in the Bolshoi-Planck simulation \citep{klypin_etal11,klypin_etal16,behroozi12_rockstar,riebe_etal13,behroozi_etal12b,rodriguez_puebla16_bolplanck}.
-As described in \S\ref{subsec:sham}, we use traditional abundance matching to connect stellar mass $\mstar$ with masses of halos and subhalos.
-To address issues related to subhalo incompleteness \citep{guo_white13,campbell_etal17}, we supplement the Bolshoi-Planck subhalo catalog with subhalos that have been disrupted and no longer appear in the standard catalog as $z=0$ surviving subhalos.
-We describe our treatment of these ``orphan" galaxies in the Appendix, where we also show results that exclude all orphan galaxies.
-
-For our SDSS galaxy samples, we calculate two-point clustering $\wproj$ using line-of-sight projection of $\pi_{\rm max}=20~\mpc$ using the {\tt correl} program in {\tt UniverseMachine} (Behroozi et al.
-2017, in prep).
-The {\tt correl} code uses the \citet{landy_szalay93} estimator ($DD - 2DR + RR$) to compute the redshift-space correlation function $\xi(\rproj, \pi)$, which is then integrated over $\vert\pi\vert < 20$ Mpc to compute the projected correlation function $\wproj(\rproj)$.
-The code uses $10^6$ randoms drawn from the same mask region with uniform volume distribution to compute $DR$, and $RR$ is computed via Monte Carlo integration.
-Errors are estimated by jackknife resampling, giving us an estimate for the lower bound of samples with volumes $V_{\rm eff}\lesssim 0.3\,{\rm Gpc}^3.$
-
-For mock galaxies, we compute $\wproj$ using the {\tt mock\_observables.wp} function in {\tt Halotools} \citep{hearin_etal16}, which is a python implementation of the algorithm in the {\tt Corrfunc} C library \citep{sinha_etal17}.
-We also use {\tt Halotools} to compute the galaxy-galaxy lensing signal, $\Delta\Sigma,$ using the {\tt mock\_observables.delta\_sigma} function.
-
-All numerical values of $\rhalf$ will be quoted in physical $\kpc,$ and all values of $\mstar$ and $\mhalo$ in $\msun,$ assuming $H_0=67.8~\kms\equiv100h~\kms,$ the best-fit value from \citet{planck15}.
-To scale stellar masses to ``$h=1$ units" \citep{croton13}, our numerically quoted values for $\mstar$ should be multiplied by $h^2,$ while our halo masses and distances should be multiplied by $h.$
-
-\subsection{Classifying large vs. small galaxies}
-\label{subsec:sizedef}
-
-Galaxy clustering has well-known dependence upon $\mstar$, which is not the focus of this work.  We thus wish to remove this dependence to focus solely on the  $\wproj(\rproj)$ dependence
-on $\rhalf.$ To do so, we determine the value $\median{\rhalf}{\mstar}$ by computing a sliding median of $\rhalf$ for galaxies sorted by $\mstar,$ calculated using a symmetric window of width $N_{\rm gal}=1000,$ keeping this window fixed for the first and last $500$ galaxies.
-Each galaxy is categorized as either ``large" or ``small" according to whether it is above or below the median value appropriate for its stellar mass.
-We note that this is analogous to the common convention for studying the properties of ``red" vs.
-``blue" galaxies, in which the two subsamples are divided by a $\mstar-$ or luminosity-dependent green valley cut \citep[e.g.,][]{vdB_etal08,zehavi_etal11}, only here the $\rhalf$ distribution is uni-modal, not bi-modal.
-
-Using this technique, for any $\mstar-$threshold sample, the stellar mass function of the ``large" and ``small" subsamples are identical.
-We illustrate this for the particular case of $\mstar>10^{10.25}\msun$ in bottom left panel of Figure~\ref{fig:sizedefinition}, which shows stellar mass functions for the two subsamples.
-The bottom right panel of Figure~\ref{fig:sizedefinition} compares histograms of the two size distributions of these subsamples, which partially overlap due to the variation in $\median{\rhalf}{\mstar}$ across the $\mstar-$ range of the threshold sample.
-
-In addition to stellar mass, $\wproj(\rproj)$ depends on galaxy color \citep[e.g.,][]{zehavi_etal11}. Thus, we will also consider the 
-dependence of clustering on galaxy size while controlling for color. Observations of clustering exhibited by subsamples split in stellar mass and color are presented in \S\ref{subsec:colormorph}.
-
-\section{Galaxy-Halo Model}
-\label{sec:model}
-
-\subsection{Abundance Matching}
-\label{subsec:sham}
-
-We map $\mstar$ onto subhalos using deconvolution abundance matching (SHAM).
-See Section 3.3 of \citet{behroozi_etal10}, or the appendix of \citet{kravtsov_etal14}, for an account of the mathematics underlying this technique in the presence of scatter.
-To perform the abundance matching, we use the publicly available code\footnote{\url{https://bitbucket.org/yymao/abundancematching}} developed by Yao-Yuan Mao \citep{lehmann_etal15} that provides a python wrapper around the C kernel developed in \citet{behroozi_etal10}.
-For the subhalo property used in SHAM, we use $\mpeak,$ the largest value of $\mvir$ ever attained by the subhalo throughout the entire history of the main progenitor halo.
-Using the stellar mass function provided in \citet{moustakas_etal13}, we model $\mstar$ as a log-normal distribution with $0.2$ dex of scatter about the median relation $\median{\mstar}{\mpeak}$ determined by SHAM \citep{reddick_etal13}.
-As described in the appendix, we include a prescription for supplementing the ordinary {\tt Rockstar} subhalo catalog with disrupted subhalos, so that some of our model galaxies inhabit subhalos that are no longer resolved and do not appear in the standard publicly available catalog (``orphan galaxies").
-
-Figure \ref{fig:baseline_sham_clustering} shows that our implementation of SHAM produces model galaxies whose projected clustering is in reasonably good agreement with SDSS galaxies.
-We note, however, that small-scale clustering shows mild $\sim10-20\%$ tension at stellar mass $\mstar\gtrsim10^{10.75}\msun,$ and similarly on all scales for the $\mstar\gtrsim10^{9.75}\msun$ sample, although the statistical significance of this discrepancy is likely rather mild due to the sample variance of SDSS galaxies with $z\lesssim0.05.$
-
-%---------------------------------------------------------------------------------------------------
-\begin{figure}
-\centering
-\includegraphics[width=8cm]{FIGS/baseline_sham.pdf}
-\caption{
-{\bf Abundance matching clustering predictions.}
-We show the $\mstar-$dependence of projected galaxy clustering, $\wproj(\rproj),$ comparing standard abundance matching to SDSS galaxies (see \S\ref{subsec:sham} for details).
-Each panel shows the comparison for a volume-limited sample defined by a different $\mstar-$threshold.
-Black points with error bars show SDSS measurements; solid black curves show the abundance matching prediction of our fiducial model, which includes the effect of orphan subhalos (see Appendix A).
-Including orphans mitigates the discrepancy in the clustering predicted by traditional, $\mpeak-$based SHAM, though mild tension remains on small scales for $\mstar\gtrsim10^{10.75}\msun,$ and on all scales for $\mstar\gtrsim10^{9.75}\msun.$
-}
-\label{fig:baseline_sham_clustering}
-\end{figure}
-%-----------------------------------------------------------------------------------------------------
-
-\subsection{Galaxy size models}
-\label{subsec:model}
-
-Our primary results in \S\ref{sec:results} show predictions for the $\rhalf-$dependence of galaxy clustering for two classes of empirical models, described in turn in the two subsections below.
-
-\subsubsection{$\mstar$-based model with satellite mass loss}
-\label{subsubsec:strippingmodel}
-
-In the first model we assume that stellar mass $\mstar$ controls $\rhalf.$ To implement this model, for simplicity we tabulate $\median{\rhalf}{\mstar}$ directly from the data, rather than pursue a parametric form, so that this model reproduces the observed $\rhalf-\mstar$ relation by construction.
-In order to ensure that the model has a level of scatter in $\rhalf$ at fixed $\mstar$ that is comparable to the level reported in \citet{somerville_etal17}, our model sizes are drawn from a log-normal distribution with $0.2$ dex of scatter centered at the observed $\median{\rhalf}{\mstar}.$
-
-It is natural to consider the possibility that stellar mass is stripped from satellite galaxies after infall.
-The basis for our implementation of this phenomenon is the fitting function presented in \citet{smith_etal16}, which was calibrated by studying stellar mass loss in a suite of high-resolution hydrodynamical simulations.
-In this model, $f_{\ast}$ quantifies the remaining fraction of stellar mass as a function of $f_{\rm DM},$ the fraction of dark matter mass that remains after subhalo infall:
-\beq
-f_{\ast} = 1 - \exp(-14.2f_{\rm DM}).
-\eeq
-For $f_{\rm DM}$ we use the ratio of present-day subhalo mass divided by the peak mass, $M_{\rm vir}/M_{\rm peak}.$ If we denote the post-stripping stellar mass as $M_{\ast}',$ then we have $M_{\ast}'\equiv f_{\ast}M_{\ast},$ where $M_{\ast}$ is given by the initial application of abundance matching.
-We then calculate the post-stripping radius by interpolating $\langle\rhalf'\vert\mstar'\rangle$ directly from SDSS data.
-In this way, we model satellite mass loss and  size truncation in a manner that mimics what is seen in hydrodynamical simulations.
-As shown in \citet{smith_etal16}, stellar stripping in this model does not begin until $f_{\rm DM}\lesssim0.2,$ and in order for $\sim50\%$ of stars to be stripped, the DM halo needs to be stripped to $\sim5\%$ of its initial mass.
-
-\subsubsection{$\rvir-$based model}
-\label{subsubsec:rvirmodel}
-
-%---------------------------------------------------------------------------------------------------
-\begin{figure}
-\centering
-\includegraphics[width=8cm]{FIGS/rvir_only_rhalf_vs_mstar_sham_model.pdf}
-\caption{
-The black curve shows the median size-mass relation of SDSS galaxies as measured in \citet{meert_etal15}.
-The two gray bands enveloping the black curve show the $50\%$ and $90\%$ percentile regions.
-The blue curve shows the $\rvir-$based model in which $\median{\rhalf}{\rvir}=0.01\rvir$ (see Section \ref{subsubsec:rvirmodel} for details).
-}
-\label{fig:scatter_plot}
-\end{figure}
-%-----------------------------------------------------------------------------------------------------
-
-As noted in \S\ref{sec:intro}, it was shown in \citet{kravtsov13} that galaxy sizes are on average proportional to the virial radius of their host halo.
-Motivated by these results, we  explore a model in which $\rhalf$ scales linearly with halo virial radius:\footnote{We note that the normalization factor in \citet{kravtsov13} is 0.015, whereas our normalization is 0.01.
-The difference derives from two factors: {\em i.} the choice of halo radius definition: \citet{bryan_norman98} in the present work, compared to the $200c$ definition used in \citet{kravtsov13}; {\em ii.} the latter study used deprojected (larger) sizes for spheroidal galaxies, whereas we make no such correction here.
-See \S\ref{sec:future} for further discussion.}
-\beq
-\label{eq:fiducial_model}
-\rhalf = 0.01\rvir
-\eeq
-For the virial radius of halos and subhalos, we use $\rmpeak:$ the value of $\rvir$ in physical units of $\kpc$ measured at the time when halo mass reached its maximum, $\zpeak.$  The relationship between $\rmpeak, \mpeak$ and $\zpeak$ is given by
-\beq
-\mpeak\equiv\frac{4\pi}{3}\rmpeak^{3}\Delta_{\rm vir}(\zpeak)\rho_{\rm m}(\zpeak),
-\eeq
-where for $\Delta_{\rm vir}(\zpeak)$ we use the fitting function to the ``virial" definition used in \citet{bryan_norman98}.
-This modeling assumption effectively defines $\median{\rhalf}{\mhalo};$ this relation defines the center of the log-normal distribution with $0.2$ dex of scatter that we use to generate a Monto Carlo realization of the model population.
-
-%---------------------------------------------------------------------------------------------------
-\begin{figure*}
-\centering
-\includegraphics[width=11cm]{FIGS/rvir_only_wp_large_small_absolute.pdf}
-\caption{
-{\bf $\rhalf-$dependence of galaxy clustering: comparison to $\rvir$-based model.}
-Red and blue points with error bars show our SDSS measurements of the clustering of small and large galaxies, respectively.
-For each volume-limited sample of $\mstar-$complete galaxies, the small and large subsamples have identical stellar mass functions, as shown in Figure \ref{fig:sizedefinition}.
-Small galaxies cluster much more strongly relative to large galaxies of the same stellar mass.
-Solid curves show the clustering predictions of the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}.
-The $\rvir-$based model inherits the shortcoming of ordinary abundance matching shown in Figure \ref{fig:baseline_sham_clustering}, although the model faithfully captures the {\em relative} clustering of small vs.
-large galaxies, as shown in Figure \ref{fig:clustering_ratio_upshot}.
-}
-\label{fig:rvir_only_clustering_absolute}
-\end{figure*}
-%-----------------------------------------------------------------------------------------------------
-
-%---------------------------------------------------------------------------------------------------
-\begin{figure*}
-\centering
-\includegraphics[width=11cm]{FIGS/rvir_only_wp_ratios.pdf}
-\caption{
-{\bf $\rhalf-$dependence of galaxy clustering: comparison to $\rvir$-based model.}
-Closely related to Figure \ref{fig:rvir_only_clustering_absolute}, y-axes show {\em clustering strength ratios,} defined as $\delta\wproj/\wproj\equiv(w_{\rm p}^{\rm large} - w_{\rm p}^{\rm small})/w_{\rm p}^{\rm all}.$ Thus a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass.
-Solid curves show predictions of the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}.
-Normalizing the measurements and predictions by $w_{\rm p}^{\rm all}$ scales away the shortcoming of ordinary abundance matching (see Figure \ref{fig:baseline_sham_clustering}), highlighting the successful prediction of the $\rvir-$based model for the $\rhalf-$dependence of galaxy clustering.
-}
-\label{fig:clustering_ratio_upshot}
-\end{figure*}
-%-----------------------------------------------------------------------------------------------------
-
-%-----------------------
-\section{Results}
-\label{sec:results}
-%-----------------------
-
-%--------------------------------------------------------
-\subsection{Size-Mass Scaling Relation}
-\label{subsec:one_point_function}
-%-------------------------------------------------------
-
-In Figure \ref{fig:scatter_plot} we show the scaling of galaxy size $\rhalf$ with $\mstar.$ The black curve enveloped by the gray bands shows the scaling relation for SDSS galaxies, while the blue curve shows the median relation  $\median{\rhalf}{\mstar}$ predicted using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}.
-While the curvature of the median relation in the model is slightly weaker than SDSS, this figure shows that models in which $\rhalf\propto\rvir$ can nonetheless match the observed $\rhalf-\mstar$ relation remarkably well given only a single parameter, confirming the results of \citet{kravtsov13} in a forward modeling context.
-
-%---------------------------------------------------------------------------
-\subsection{Size-Dependent Clustering Measurements}
-\label{subsec:clustering_results}
-%---------------------------------------------------------------------------
-
-In Figure~\ref{fig:rvir_only_clustering_absolute}, we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj(\rproj).$ We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds: an  $\mstar>10^{9.75}\msun$ sample with $z_{\rm max}=0.0435$ and $N_{\rm gal}=27658;$ an  $\mstar>10^{10.25}\msun$ sample with $z_{\rm max}=0.0663$ and $N_{\rm gal}=48571;$
-an  $\mstar>10^{10.75}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=52350;$ 
-and an  $\mstar>10^{11}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=33578.$ For each threshold, we split the galaxies into ``large" and ``small" subsamples, as described in \S\ref{subsec:sizedef}.
-As shown in Figure \ref{fig:sizedefinition}, our size-based samples  have similar stellar mass functions.
-Red points with jackknife-estimated error bars show SDSS measurements of $\wproj(\rproj)$ for samples of small galaxies, while blue points show the measured correlation functions for samples of large galaxies.
-Solid curves show $\wproj$ as predicted for these subsamples by the $\rvir-$based model of galaxy sizes described in \S\ref{subsubsec:rvirmodel}.
-
-The salient feature of these clustering measurements is that small galaxies cluster more strongly than large galaxies of the same stellar mass in all but the largest $\mstar$ samples.
-Remarkably, both the trend and the quantitative difference in the shape of the correlation functions of small and large galaxy samples are reproduced by the $\rvir-$based model.
-This may be surprising, since $\rhalf\propto\rvir,$ halo mass $\rvir\propto\mhalo^{1/3},$ and clustering strength of halos increases with $\mvir.$ Based on this simple argument, one would expect that large galaxies would be the more strongly clustered.
-We provide a resolution to this conundrum in \S\ref{subsec:censat_sizes}.
-However,  before doing so, we first examine the clustering test of the $\rvir-$based model in more detail.
-
-As shown in Figure \ref{fig:baseline_sham_clustering}, the abundance matching prediction for $\wproj(\rproj)$ exhibits tension with SDSS observations at the $10-20\%$ level.
-This tension is inherited by our $\rvir-$based model for size, which is the subject of this work, and so we wish to compare our size models to data in such a way that minimizes the role played by the underlying stellar-to-halo-mass relation.
-We accomplish this using the {\em $\rhalf$ clustering ratios,} described below.
-
-For each volume-limited $\mstar-$threshold sample, we additionally measure $\wproj(\rproj)$ {\em without} splitting on size, giving us measurements $\wpall, \wplarge,$ and $\wpsmall$ for each threshold sample.
-This allows us to compute the ratio $(\wplarge-\wpsmall)/\wpall,$ which we refer to as {\em the $\rhalf$ clustering ratio}.
-These ratios, denoted as $\delta\wproj/\wproj,$ are the measurements appearing on the y-axis in each panel of Figure \ref{fig:clustering_ratio_upshot}.
-As a specific example, a clustering ratio of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass.
-
-The points and curves in Figure \ref{fig:clustering_ratio_upshot} are almost all negative: small galaxies cluster more strongly relative to large.
-This presentation of the measurement makes it clear that the underlying signal of $\rhalf-$dependent clustering is strongest for samples with smaller stellar mass; as $\mstar$ increases, the signal weakens and nearly vanishes for $\mstar\gtrsim10^{11}\msun.$ Strikingly, the $\rvir-$based model reproduces this $\mstar-$dependent behavior, as well as the scale-dependence of the observed clustering signal at each $\mstar.$ As described in \S\ref{subsec:censat_sizes} below, we attribute the success of this prediction to the systematic difference between the sizes of central and satellite galaxies.
-
-%--------------------------------------------------------------------------
-\subsection{Testing the Impact of Satellite Mass Loss}
-\label{subsec:mstar_stripping}
-%--------------------------------------------------------------------------------------
-\begin{figure*}
-\centering
-\includegraphics[width=11cm]{FIGS/alt_model_wp_ratios.pdf}
-\caption{
-{\bf The subdominant role of tidal stripping.}
-In all panels, the axes and points with error bars are the same as in Figure \ref{fig:clustering_ratio_upshot}.
-The solid green curves show the prediction of a model where $\rhalf$ is statistically set by $\mstar,$ in the complete absence of satellite mass loss.
-Such a model predicts zero $\rhalf-$dependence to galaxy clustering, in gross tension with observations.
-The solid purple curves show results for a model in which satellites lose mass after infall in a manner similar to what is seen in high-resolution hydrodynamical simulations, as described in \S\ref{subsubsec:strippingmodel}.
-This produces satellites that are smaller than centrals, but the effect is too mild to correctly capture the observed clustering.
-Evidently, satellite-specific mass stripping plays a sub-dominant role in setting the relative size of centrals and satellites.
-}
-\label{fig:mstarmodelclustering}
-\end{figure*}
-%-----------------------------------------------------------------------------------------------------
-
-Figure~\ref{fig:mstarmodelclustering} is analogous to Figure \ref{fig:clustering_ratio_upshot}, but instead compares observed clustering ratios to those predicted by models
-in which galaxy size is controlled by $\mstar$ (\S\ref{subsubsec:strippingmodel}).
-Green solid lines show predictions of the $\mstar$-based model that does not account for mass loss due to tides.
-In this model, $\rhalf$ follows a purely random log-normal distribution, with the median relation $\median{\rhalf}{\mstar}$ directly matched to the observed relation by construction.
-This model thus predicts no dependence of galaxy clustering upon $\rhalf$ at fixed $\mstar,$ simply because the scatter of $\rhalf$ about $\median{\rhalf}{\mstar}$ is uncorrelated with any other variable.
-The figure shows that this model clearly is at odds with the significant dependence of clustering on size exhibited by SDSS galaxies.
-
-Including satellite mass loss in the model introduces correlations in the scatter: after mass loss, satellites have smaller sizes than centrals of the same $\mstar$ due to post-infall tidal stripping.
-The purple curves in Figure \ref{fig:mstarmodelclustering} show that satellite mass loss impacts $\rhalf-$dependent clustering in the expected manner.
-The ``small" galaxy population has a higher satellite fraction due to satellites being smaller than centrals of the same $\mstar,$ and so in this model small galaxies cluster more strongly relative to large.
-However, the magnitude of the effect is not sufficiently strong  to produce clustering predictions that are consistent with observations.
-
-Due to the shape of ${\rm d}\rhalf/{\rm d}\mstar,$ low-mass satellites have to lose much more halo mass than high-mass satellites in order to get pushed into the small-$\rhalf$ sample.
-Thus even though there are more satellites at lower masses, the shape of ${\rm d}\rhalf/{\rm d}\mstar$ counteracts this trend, making the mass-dependence of the observed signal shown in Figure \ref{fig:mstarmodelclustering} difficult to explain by appealing to tidal stripping.
-Evidently, it is difficult to strip enough mass from satellites so that the $\rhalf-$dependent clustering predictions are in agreement with observations.
-We reach the same conclusion when we tested an even more extreme $\mstar-$stripping model, in which stellar mass loss is linearly proportional to halo mass loss \citep[][Model 1]{watson_etal12}.
-As we argue in \S\ref{sec:interpretation}, this supports the conclusion that the relative difference between median sizes of central and satellite galaxies is largely in place at the time of satellite infall.
-
-%----------------------------------------------------
-\subsection{The Role of Galaxy Color}
-\label{subsec:colormorph}
-%----------------------------------------------------
-
-We now examine how galaxy clustering depends on size when we control both for stellar mass and color dependence of galaxy clustering.
-Using a volume-limited galaxy sample with $10^{9.75}\msun < \mstar< 10^{10.25}\msun,$ we first divide the sample into ``red" and ``blue" subsamples using $g-r=0.65$ as a boundary, which approximately corresponds to the trough of the green valley for this stellar mass.
-For each color-selected subsample, we separately measure $\median{\rhalf}{\mstar; {\rm red}}$ and $\median{\rhalf}{\mstar; {\rm blue}},$ and use these median size relations to split each subsample into two.
-
-Figure \ref{fig:colorclustering} shows the clustering of large vs.
-small galaxies, separately for red and blue samples.
-For each color-selected sample, large galaxies are slightly more strongly clustered relative to small galaxies.
-Comparing Figure \ref{fig:colorclustering} to the the upper right panel of Figure \ref{fig:rvir_only_clustering_absolute} shows the size dependence for color-selected samples is dramatically weaker.
-For $\mstar-$complete samples, small galaxies cluster much stronger than large galaxies; for color-selected samples, the reverse is true, but the difference is much smaller and is confined to a limited range of scales.
-Although the two results may seem surprising, even contradictory, they can, in fact be explained within a simple, unified model, as will be discussed in \S\ref{sec:interpretation}.
-
-%---------------------------------------------------------------------------------------------------
-\begin{figure}
-\centering
-\includegraphics[width=8cm]{FIGS/color_selected_size_dependent_clustering.pdf}
-\caption{
-{\bf Distinct $\rhalf-$dependence of clustering for color-selected galaxy samples.}
-Projected clustering of SDSS galaxies in the bin of stellar mass: $10^{9.75}<\mstar/\msun<10^{10.25}.$ For both ``blue" and ``red" samples, we first divide SDSS galaxies falling in the $\mstar$ bin based on a color cut at $g-r=0.65.$ We then subsequently compute $\median{\rhalf}{\mstar; {\rm red}}$ and $\median{\rhalf}{\mstar; {\rm blue}}$.
-In analogy to the bottom left panel of Figure \ref{fig:sizedefinition}, for each of the red and blue samples, the small and large subsamples have statistically indistinguishable stellar mass functions.
-We then measure $\wproj$ for each of the four subsamples; jackknife-estimated errors are shown alternately using error bars and shaded bands, as specified in the legend.
-At this stellar mass, pre-selecting galaxy samples by color results in a dramatic weakening of the $\rhalf-$dependence of $\wproj$ relative to $\mstar-$complete samples, as well as a sign-reversal of the signal.
-In \S\ref{sec:interpretation} we give a simple halo model picture unifying the trends shown here with those illustrated in Figure \ref{fig:clustering_ratio_upshot}.
-}
-\label{fig:colorclustering}
-\end{figure}
-%---------------------------------------------------------------------------------------------------
-
-%---------------------------------------------------------------------------------------------------
-\begin{figure}
-\centering
-\includegraphics[width=8cm]{FIGS/rvir_only_cen_sat_sizes.pdf}
-\caption{
-{\bf Relative sizes of centrals and satellites.}
-In a narrow bin of subhalo mass $\mhalo\equiv\mpeak\approx10^{12}\msun,$ we show the distribution of galaxy sizes for different subpopulations, as predicted by the $\rvir-$based model.
-The red distribution shows the sizes of satellites; the blue distribution shows host halos that have never passed inside the virial radius of a larger halo (``true centrals"); the green distribution host halos that were subhalos inside a larger halo at some point in their past history (``splashback centrals").
-In the $\rvir-$based model, galaxy size is set by the {\em physical} size of the virial radius at the time the halo attains its peak mass, naturally resulting in smaller sizes for satellites and splashback centrals relative to true centrals of the same mass.
-}
-\label{fig:censatsizehist}
-\end{figure}
-%-----------------------------------------------------------------------------------------------------
-
-%-----------------------------------------------------------------------------------------
-\section{A Unified Interpretation of $\rhalf-$Dependent Clustering}
-\label{sec:interpretation}
-%-----------------------------------------------------------------------------------------
-
-In the previous section, comparing model predictions to the observed size dependence of galaxy clustering produced two intriguing results.
-First, the model that assumes $\rhalf\propto\rvir$ predicts with remarkable accuracy the dependence of both the amplitude and shape of  size-dependent galaxy correlation functions, especially considering that the model nominally has only one free parameter: the normalization of the linear $\rhalf-\rvir$ relation.
-At the same time, small galaxies cluster more strongly relative to large, which seems at odds with intuitive expectations that, within such a model, larger sizes correspond to larger halo masses, $\rvir\propto\mvir^{1/3}$; thus  naively, galaxies with larger sizes should be more strongly clustered, not less.
-Second, the strong dependence of galaxy clustering on size weakens to almost no dependence for samples of red and blue galaxies selected by color within a given stellar mass range.
-Below, in \S\ref{subsec:censat_sizes}, we propose a simple and unified explanation of all these results within the $\rvir$-based size model; we discuss the broader implications of our interpretation in \S\ref{subsec:broader_implications}.
-
-%----------------------------------------------------------------------------
-\subsection{The Relative Size of Centrals vs. Satellites}
-\label{subsec:censat_sizes}
-%----------------------------------------------------------------------------
-
-Recall that in the $\rvir$-based size model, galaxy size is proportional to the physical size of halo virial radius at $\zpeak,$ the redshift when the halo attained its maximum mass.
-Thus we can expect that in this model, satellite galaxies will have smaller sizes than  central galaxies hosted by halos of similar mass.
-Indeed, Figure \ref{fig:censatsizehist} shows the $\rhalf$ distributions of central, satellite, and ``splashback'' central galaxies living in subhalos of the same mass, $\mhalo\equiv\mpeak\approx10^{12}\msun.$ A ``splashback central"  is defined as a present-day central galaxy that used to be a satellite, i.e., its main progenitor halo passed inside the virial radius of a larger halo at some point in its past history.
-On the other hand, we define a ``true central" as a galaxy that has never been a satellite.
-The figure shows that there is a clear trend of sizes decreasing from the central to splashback to satellite galaxies.
-
-In the $\rvir-$based model, satellites and splashback galaxies are smaller than centrals of the same halo mass due to the physical size of their halo being smaller at earlier times $\zpeak.$ There are two distinct reasons why this feature results in small galaxies being more strongly clustered relative to larger galaxies of the same mass.
-First and foremost, satellite galaxies statistically occupy higher mass host halos that are more strongly clustered.
-So in models where satellites are smaller than centrals of the same mass, smaller galaxies will have a higher satellite fraction, boosting the clustering of small relative to large galaxies of the same stellar mass.
-Second, at fixed mass, halos of $L_\ast$ galaxies that form earlier are more strongly clustered, a phenomenon commonly known as {\em halo assembly bias} \citep{gao_white05,wechsler_etal06}.
-Splashback halos are typically earlier-forming than true centrals \citep{wang_etal09}, and so models where splashback halos host smaller-than-average galaxies will naturally predict smaller galaxies being the more strongly clustered \citep[see, e.g.,][for a demonstration of the splashback-dependence of halo clustering]{sunayama_etal16}.
-
-We can also understand how the observed $\rhalf-$dependent clustering scales with $\mstar$ (shown by comparing different panels in Figure \ref{fig:clustering_ratio_upshot}) in terms of the different sizes of centrals and satellites.
-The satellite fraction $F_{\rm sat}(\mstar)$ decreases as $\mstar$ increases \citep[e.g.,][]{guo_etal11,reddick_etal13}.
-As $F_{\rm sat}$ decreases, there are fewer satellites available to preferentially weight the subsample of smaller galaxies.
-Thus,  high-$\mstar$ samples consist mostly of central galaxies, and the split by size no longer corresponds to the split into satellite- and central-dominated samples.
-The size-dependence of clustering correspondingly weakens and nearly disappears for samples with large $\mstar$.
-
-Likewise, the significantly weaker dependence of clustering on size for color-selected samples (Figure \ref{fig:colorclustering}), and its reversed sign, may be explained by the same principles.
-It is well known that satellites are redder than centrals of the same stellar mass \citep[e.g.,][]{vdB_etal08}, and that the clustering differences between red and blue galaxies can be understood in terms of red satellites preferentially occupying high-mass halos \citep[e.g.,][]{zehavi_etal11}.
-Pre-selecting galaxies by color then absorbs much of the potential effect that can be reaped by central vs.
-satellite differences, and so the relative clustering of centrals becomes more important.
-In the limit that size-dependent clustering is dominated by centrals, the $\rvir$-based size model predicts that large galaxy samples should be (weakly) more clustered than small ones, because $\rhalf\propto\rvir\propto\mhalo^{1/3}.$ This is the trend seen in the clustering measurements shown in Figure \ref{fig:colorclustering}.
-
-While we consider such a conjecture plausible, a conclusive confirmation requires proper forward modeling of size and color jointly.
-Such an effort is well motivated by our results, but is beyond the scope of the present work.
-
-%-------------------------------------------------
-\subsection{Broader Implications}
-\label{subsec:broader_implications}
-%-------------------------------------------------
-
-The success of the $\rvir$-based model in predicting the size dependence of galaxy clustering may be explained if the sizes of {\it all} galaxies, red, blue, spheroid, disks, satellites and central, are, on average, proportional to the $\rmpeak,$ the physical size of the virial radius at the time at which $\mhalo$ stops growing.
-Although correlation is not necessarily causation, such a universal and simple dependence poses a useful challenge to fine-grained galaxy formation models, as it indicates a tight connection between the growth of galaxies and their host halos.
-
-The $\rvir$-based size model assumes as an ansatz that galaxy size remains approximately constant after its halo stops growing; as shown in Figure \ref{fig:clustering_ratio_upshot}, this assumption is consistent with the observed size-dependence of galaxy clustering in SDSS.
-The halos of typical satellites reach $\mpeak$ far outside the virial radius of their ultimate host halo \citep{behroozi_etal14}, and so in the $\rvir-$based model the size difference between satellites and centrals is largely in place prior to the time of satellite infall.
-Halos of central and satellite galaxies of the same $\mstar$ differ in the epoch $\zpeak$ at which their halo stopped growing, and this difference gives a natural explanation for their different median sizes.
-
-This difference also explains the relative trends of $\rhalf-\mstar$ relations for red and blue, or disk and spheroid galaxies.
-Both types of galaxies exhibit weak dependence of $\rhalf$ on $\mstar$ at $\mstar\lesssim 5\times 10^{10}\ M_\odot$ and
-at these masses $\rhalf$ of disks is a factor of two larger than those of spheroids.
-At larger masses, the sizes of galaxies of both types show stronger dependence on $\mstar,$ and the difference in median size of disk and spheroid galaxies decreases \citep[e.g.,][]{bernardi_etal14}.
-
-In the $\rvir$-based size model, the weak dependence of $\rhalf$ on $\mstar$ for low-mass galaxies is due to the steep $\mstar-\mvir$ relation.
-For example, if $\mstar\propto\mvir^\alpha\propto\rvir^{3\alpha}$, then $\rhalf\propto \rvir\propto \mstar^{1/(3\alpha)}$.
-Given that $\alpha\sim 1-3$ is inferred for the $\mstar-\mvir$ relation at low masses \citep{kravtsov10,moster_etal13,behroozi13_smhm,kravtsov_etal14}, the $\rhalf-\mstar$ relation in this regime is expected to be shallow.
-For galaxies of $\mstar\gtrsim 5\times 10^{10}\ M_\odot$, $\alpha\approx 0.3$ \citep[e.g.,][]{kravtsov_etal14}, and thus
-the slope of the $\rhalf-\mstar$ relation is approximately linear.
-These trends of $\rhalf$ with $\mstar$ have a direct relation to the trends of surface brightness $\mu_\star=\mstar/(2\pi\rhalf^2)$ with stellar mass \citep[see, for example, the $\mu_\star-$dependent clustering measurements in][which are qualitatively similar to the measurements reported here]{li_etal06}.
-
-The difference in median sizes of disk and spheroidal galaxies at $\mstar\lesssim 10^{11}\ M_\odot$ can be explained by the sizes of satellite galaxies being systematically smaller than the sizes of central galaxies of the same $\mstar,$ coupled with the fact that the satellite fraction is much larger among spheroidal galaxies compared to disk galaxies.
-For example, the analysis in \citet{rodriguez_puebla_etal15} shows that in this regime, the satellite fraction of blue galaxies is only $\sim10-20\%$, while
-the satellite fraction of red galaxies is $\gtrsim 30-50\%,$ increasing with decreasing stellar mass.
-As $\mstar$ increases, the satellite fractions of both blue and red galaxies drop, and at $\mstar\gtrsim 10^{11}\ M_\odot,$ the vast majority of blue and red galaxies are centrals.
-If these galaxies occupy similar halo masses at the same $\mstar$, then the $\rvir$-based size model predicts that the difference in sizes of red and blue galaxies should disappear at these masses, as is indeed observed.
-A testable prediction of this picture is that when 3D (de-projected) sizes of only central red and blue galaxies of the same $\mstar$ are compared, the sizes should be much closer than the sizes of the overall red and blue populations.
-
-In any model where galaxy $\rhalf$ co-evolves with halo $\rvir,$ the choice of halo boundary definition necessarily impacts the model prediction.
-Since the clustering of halos has non-trivial dependence upon halo definition \citep{villarreal_etal17}, then measurements of galaxy clustering may be able to observationally distinguish a particular halo boundary that is most closely connected to galaxy size.
-The redshift evolution of the relationship between $\mhalo$ and $\rvir$ also varies with halo definition, and so measurements of $\rhalf-$dependent clustering across redshift may provide a further observational handle on the halo radius definition that best predicts galaxy size.
-
-%---------------------------------------------------------------------------------------------------
-\begin{figure*}
-\centering
-\includegraphics[width=8cm]{FIGS/rvir_only_lensing_prediction.pdf}
-\includegraphics[width=8cm]{FIGS/host_mass_distributions_sm9p75_sm10p25.pdf}
-\includegraphics[width=8cm]{FIGS/rvir_only_lensing_prediction2.pdf}
-\includegraphics[width=8cm]{FIGS/host_mass_distributions_sm10p25_sm10p75.pdf}
-\includegraphics[width=8cm]{FIGS/rvir_only_lensing_prediction3.pdf}
-\includegraphics[width=8cm]{FIGS/host_mass_distributions_sm10p75_sm11p25.pdf}
-\caption{
-{\bf Prediction for $\rhalf-$dependence of galaxy lensing.}
-Using the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}, in the {\em left panels} we show predictions for future measurements of the $\rhalf-$dependence of galaxy lensing of $\mstar-$complete samples, where ``small" and ``large" subsamples are defined as in \S\ref{subsec:sizedef}.
-To date, the $\rhalf-$dependence of $\Delta\Sigma$ has only been measured for color-selected samples \citep{charlton_etal17}, in which the observed trends are reversed and weaker than those predicted here: for both blue and red samples in CFHTLenS, the observed $\Delta\Sigma$ of large galaxies is (slightly) stronger relative to small galaxies.
-As a generic consequence of satellites being smaller than centrals of the same mass, we predict that future lensing measurements of $\mstar-$complete samples will show that $\Delta\Sigma$ of small galaxies is significantly stronger relative to large galaxies of the same stellar mass $\mstar\lesssim10^{11}\msun.$ We additionally predict that at sufficiently large mass $\mstar\gtrsim10^{11}\msun,$ the trend of small-scale $\Delta\Sigma$ with $\rhalf$ reverses sign.
-The {\em right panels} display the physical explanation for this prediction.
-For $\mstar\lesssim10^{11}\msun,$ satellites preferentially populating the small sample heavily weight high-mass halos, boosting the lensing signal on all scales.
-For $\mstar\gtrsim10^{11}\msun,$ when $F_{\rm sat}\lesssim10\%,$ central galaxies dominate the signal, and the $\rvir-$based model predicts that $\rhalf$ increases with $\mhalo$ for centrals.
-See \S\ref{sec:previous_work} for further details.
-}
-\label{fig:lensingprediction}
-\end{figure*}
-%-----------------------------------------------------------------------------------------------------
-
-\section{Relation to Previous Work}
-\label{sec:previous_work}
-
-Numerous previous analyses have employed the \citet{yang_etal05b} group catalog to study the relationship between galaxy mass, size, and environment.
-For example, by treating observed groups as genuine dark matter halos, several analyses have found that the $\mstar-\rhalf$ relation of early-type galaxies exhibits weak, if any, environmental dependence \citep{weinmann_etal08,huertas_company_etal13b,shankar_etal14}.
-
-Group-finding methods are subject to significant systematics, the most severe of which are caused by the fracturing of a massive halo's galaxies into multiple small groups, and the fusing of small halos into an apparently large group \citep{duarte_mamon14}.
-As shown in \citet{campbell_etal15}, these effects can significantly bias attempts to infer trends in the galaxy--halo connection directly from group catalogs.
-The chief source of these  biases is that the frequency of fracturing and fusing has significant dependence upon large-scale density, as do galaxy properties such as color and morphology.
-The correlation between group misidentification rate and galaxy properties would be quite challenging to model analytically, but these systematics damage the robustness of the inference: contemporary algorithms {\em generically} wash out differences between centrals and satellites; trends can even be artificially created that are not truly present.
-
- Our forward modeling inference technique is not subject to such systematics because our methods are entirely outwith the group-finding framework, and so it is encouraging that our conclusions are commensurable with group-based results.
-Once galaxies have been color-selected, Figure \ref{fig:colorclustering} shows that the observed clustering trends nearly vanish in magnitude, and reverse sign.
-Insofar as blue galaxies are largely disk-dominated, our clustering results in Figure \ref{fig:colorclustering} are also consistent with the disk model presented in \citet{dutton_etal08,dutton_etal10}, which predicts that at fixed stellar mass, there is weak, positive correlation between disk size and halo mass.
-Our conclusions are also qualitatively consistent with \citet{spindler_wake17}, who find that centrals in the \citet{yang_etal05a} group catalog are $\sim20-25\%$ larger than satellites of similar halo mass (using stellar velocity dispersion as an observational proxy for halo mass); we find the same trend at a comparable, if slightly larger magnitude.
-
-The $\rhalf-$dependence of galaxy lensing has recently been measured using CFHTLenS observations \citep{heymans_etal12,erben_etal13}.
-For both red- and blue-sequence galaxies, it was found in \citet{charlton_etal17} that the lensing signal, $\Delta\Sigma,$ of large galaxies is slightly stronger relative to smaller galaxies.
-This result is in good agreement with the clustering measurements in Figure \ref{fig:colorclustering}, which show the same trend.
-
-To date, the $\rhalf-$dependence of $\Delta\Sigma$ has not yet been measured for $\mstar-$complete samples.
-In the left panels of Figure \ref{fig:lensingprediction}, we show predictions of the $\rvir-$based model for future measurements of $\Delta\Sigma.$ The halo model principles underlying the lensing trends are the same as for $\wproj.$ For $\mstar\lesssim10^{11}\msun,$ the difference in $F_{\rm sat}$ between small and large samples is the dominant factor; satellites occupy higher mass host halos relative to centrals of the same stellar mass, boosting $\Delta\Sigma$ for small relative to large galaxy samples.
-At sufficiently large stellar mass $\mstar\gtrsim10^{11}\msun,$ when $F_{\rm sat}\lesssim10-15\%,$ the role of centrals becomes dominant; the $\rvir-$based model predicts that $\mhalo$ increases with $\rhalf$ for centrals, which is reflected in the reversal of the small-scale signal in the bottom left panel.
-
-The right panels of Figure \ref{fig:lensingprediction} compare the distributions of host halo mass, $\mhost,$ for small and large samples; for centrals, $\mhost=\mhalo,$ while for satellites, $\mhost$ is the virial mass of the parent halo.
-The peak of each distribution arises from central galaxies, while the long tail at large values of $\mhost$ is due to satellites.
-At all stellar masses, the distributions in blue peak at slightly larger $\mhost$ relative to the red; this is because the $\rvir-$based model predicts that $\mhalo$ increases with $\rhalf$ for centrals.
-For $\mstar-$complete samples, this effect only becomes dominant when the satellite fraction drops to sufficiently small values.
-Qualitatively, these features are completely generic predictions of the $\rvir-$based model; quantitatively, the precise value of $\mstar$ where the effect of centrals begins to dominate $\Delta\Sigma$ depends sensitively on $F_{\rm sat}(\mstar),$ which we have only roughly calibrated in the present work.
-
-Our methodology is closely aligned with \citet{somerville_etal17}, who studied the empirical modeling features that are necessary to recover the tight scatter in the observed $\mean{\rhalf}{\mstar}$ relation.
-By building models where $\rhalf$ is set by halo spin $\lambda_{\rm halo}$, it was found in \citet{somerville_etal17} that the level of intrinsic scatter about $\langle\lambda_{\rm halo}\vert\mhalo\rangle$ in dark matter halos is at least as large as the scatter about $\langle\rhalf\vert\mstar\rangle$ seen in observed galaxies.
-In our approach, the level of scatter is simply a modeling parameter whose fiducial value was motivated by \citet{somerville_etal17}.
-In ongoing follow-up work discussed in \S\ref{sec:future}, we will systematically test the large-scale structure implications of the assumption that $\rhalf^{\rm disk}\propto\lambda_{\rm halo}$ using forward-modeling methods analogous to those advocated for in \citet{somerville_etal17} and employed here.
-
-%-----------------------------------------------------------------------------------------
-\section{Future Directions for Empirical Modeling of Galaxy Size}
-\label{sec:future}
-%-----------------------------------------------------------------------------------------
-
-This work is intended to serve as a pilot study in which we identify the chief ingredients that influence the $\rhalf-$dependence of galaxy clustering.
-While our results suggest that sizes of galaxies are linearly correlated with the
-virial radius of halos at the moment the halo mass reached its peak, and also that sizes of satellite galaxies were set {\em prior} to infall, our model does not capture galaxy properties and their trends in full quantitative detail.
-For example, the clustering ratios of this model shown in Figure \ref{fig:clustering_ratio_upshot} do capture the overall trends, but do not match the observed clustering statistics at the level of reduced $\chi^2\approx 1.$ For present purposes, we have chosen to focus on exploring bracketing cases of qualitative ingredients, rather than fine-tuning the model.
-
-Since the clustering signal is strongly influenced by differences between centrals and satellites, then the satellite fraction $F_{\rm sat}(\mstar)$ plays an important role in $\rhalf-$dependent clustering.
-Even for {\em fixed} scaling relations $\median{\rhalf^{\rm cens}}{\mhalo}$ and $\median{\rhalf^{\rm sats}}{\mhalo},$ models with different satellite fractions will exhibit distinct $\rhalf-$clustering ratios, because $F_{\rm sat}(\mstar)$ controls the relative weighting of the two populations.
-An explicit demonstration of this point appears in the Appendix, which repeats the analyses in the main body of the text, but for a subhalo catalog with no orphan correction (and therefore a different satellite fraction).
-
-%---------------------------------------------------------------------------------------------------
-\begin{figure}
-\centering
-\includegraphics[width=8cm]{FIGS/cen_sat_size_ratios.pdf}
-\caption{
-{\bf Scaling relation for hydro sims and SAMs.}
-As a function of subhalo mass $\mhalo=\mpeak,$ we show the ratio of mean satellite-to-central size predicted by the $\rvir-$based model.
-This scaling relation should be a useful guideline for more fine-grained physical models of galaxy size that wish to reproduce the observed $\rhalf-$dependence of galaxy clustering.
-}
-\label{fig:censatsizeratios}
-\end{figure}
-%-----------------------------------------------------------------------------------------------------
-
-On the one hand, this degeneracy with the satellite fraction is unfortunate, because it means galaxy size does not leave a pure and unique signature on $\rhalf-$clustering ratios.
-However, this can also be viewed as an opportunity to extract tighter constraints on $F_{\rm sat}(\mstar),$ which are sorely needed to discriminate between competing models \citep{watson_conroy13}.
-Traditional galaxy clustering is already being used to validate and/or fit models of the stellar-to-halo-mass relation \citep[e.g.,][]{leauthaud_etal11,moster_etal10,behroozi13_smhm,lehmann_etal15}.
-Based on our results, we advocate that empirical models for $\mean{\mstar}{\mhalo}$ be supplemented with additional model ingredients for $\median{\rhalf}{\mhalo},$ and that the parameters of the composite model be {\em jointly} constrained by measurements of the stellar mass function, $\mstar-$dependent clustering, and $\rhalf-$dependent clustering.
-Because the number of free parameters required to additionally model galaxy size are so few, such analyses will be able to exploit the additional statistical leverage provided by the $\rhalf-$dependence of $\wproj(\rproj)$ to significantly improve constraints on $F_{\rm sat}(\mstar),$ without any appeal to a group-finder.
-
-In ongoing follow-up work, we are extending the current analysis by jointly modeling stellar mass and size together with a bulge/disk decomposition of model galaxies quantified by ${\rm B/T},$ the fraction of the total stellar mass in the bulge.
-Forward modeling methods for ${\rm B/T}$ offer potential to significantly improve upon several aspects of current analysis techniques.
-For example, two-dimensional (projected) sizes of observed galaxies are sometimes de-projected to estimate three-dimensional sizes; such a correction applied to the data requires treating disk-dominated and spheroidal systems separately.
-The forward modeling approach transforms this correction into parameterized inference: three-dimensional sizes of disk and bulge components are modeled separately and mapped onto dark matter halos; the projected size of model galaxies can then be computed self-consistently with the modeled value of ${\rm B/T},$ permitting a more rigorous, ``apples-to-apples" comparison to observations of projected size.
-This follow-up analysis will also help robustly quantify the extent to which the ``cause" of satellites being smaller than centrals is due to differences in ${\rm B/T}.$
-
-Figure \ref{fig:censatsizeratios} shows that satellites in $\mhalo\approx10^{12}\msun$ halos are $\sim25-40\%$ smaller than their central galaxy counterparts.
-Since the satellite fraction varies quite significantly with morphology and/or color, we have demonstrated that it is entirely plausible that most of the observed environmental trends of galaxy size can be understood simply in terms of central vs.
-satellite size differences.
-These differences are likely not driven by satellite-specific processes inside host halos, but instead are primarily due to the fact that satellites have reached their peak mass at higher redshifts than centrals.
-While it remains to be seen whether these statistical principles alone are sufficient to capture all the elementary trends that galaxy two-point functions exhibit with galaxy size, morphology and color, one thing is now clear: it is not possible to reliably analyze environmental trends of galaxy $\rhalf$ without properly accounting for satellites.
-
-\section{Conclusions}
-\label{sec:conclusion}
-
-We have presented new measurements of the dependence of projected galaxy clustering, $\wproj(\rproj),$ upon galaxy size and stellar mass, and used forward-modeling methods based on {\tt Halotools} to identify the basic ingredients that influence the signal.
-We conclude with a brief summary of our primary findings:
-
-\ben
-\item Small galaxies cluster more strongly than large galaxies of the same stellar mass.
-Differences between the clustering of small and large galaxies increase on small scales $\rproj\lesssim1\mpc,$ and decrease with increasing stellar mass (see Figure \ref{fig:rvir_only_clustering_absolute}).
-\item The most important factor influencing the clustering signal is the relative size of central and satellite galaxies.
-The magnitude, scale-dependence, and $\mstar-$dependence of $\rhalf-$dependent clustering provides strong evidence that satellite galaxies are smaller than central galaxies of the same halo mass.
-\item A simple empirical model in which $\rhalf$ is proportional to halo $\rvir$ at the time when halo mass reached its maximum reproduces the size-dependence of SDSS galaxy clustering in striking detail (see Figure \ref{fig:clustering_ratio_upshot}).
-\item Models in which $\rhalf$ is regulated by $\mstar,$ rather than $\mhalo,$ are grossly discrepant with the observed $\wproj(\rproj),$ even when accounting for satellite mass stripping (see Figure \ref{fig:mstarmodelclustering}).
-\item Taken together, our findings indicate that satellite-specific processes play a sub-dominant role in setting the different sizes of centrals and satellites; the sizes of satellite galaxies instead appear to be largely predetermined at the time of their infall.
-\item The $\rvir$-based size model that reproduces the observed $\wproj(\rproj)$ makes an unambiguous  prediction for future observations of galaxy-galaxy lensing: for $\mstar-$selected samples, $\Delta\Sigma$ should be much stronger for small galaxies relative to large (see Figure \ref{fig:lensingprediction}).
-The strength of the predicted difference in $\Delta\Sigma$ makes this test well within reach of numerous present-day imaging surveys.
-\een
-
-We view the present work as a pilot study that motivates a Bayesian inference program to tightly constrain the galaxy size-halo connection with forward modeling techniques, in direct analogy to the literature on the stellar-to-halo-mass relation.
-Our results provide an integral constraint for more complex and fine-grained models of galaxy size, such as semi-analytic models and hydrodynamical simulations.
-For convenience, Figure \ref{fig:censatsizeratios} provides a simple summary statistic that can be used as a diagnostic for calibrating alternative modeling efforts.
-
-Our python code has been publicly available on GitHub\footnote{\url{https://github.com/aphearin/galsize_models}} since the inception of the project; we intend for this code to provide a simple means for cosmological surveys to generate synthetic galaxy populations with realistic sizes across the cosmic web.
-Tabulations of our clustering measurements, as well as catalogs of $z=0$ model galaxies with $\mstar$ and $\rhalf,$ will be made publicly available upon publication; prior to that time, our measurements and mock data are available upon request.
-
-\section*{Acknowledgments}
-
-APH thanks John Baker for the {\em Toejam \& Earl} soundtrack.
-Thanks also to Frank van den Bosch, Andrew Zentner, Doug Watson, Simon White, Thorsten Naab, Risa Wechsler and Chihway Chang for thoughtful feedback at various stages of the development of this work, to Faustin Carter and Sebastian Bocquet for sharing their matplotlib expertise, and to Andrew Zentner for Scottish grammar consultation.
-
-We thank the {\tt Astropy} developers for the package-template \citep{astropy}, as well as the developers of {\tt NumPy} \citep{numpy_ndarray}, {\tt SciPy} \citep{scipy}, Jupyter \citep{jupyter}, IPython \citep{ipython}, Matplotlib \citep{matplotlib}, and GitHub for their extremely useful free software.
-While writing this paper we made extensive use of the Astrophysics Data Service (ADS) and {\tt arXiv} preprint repository.
-
-Work done at Argonne National Laboratory was supported under the DOE contract DE-AC02-06CH11357.
-This research was supported in part by the National Science Foundation under Grant No.
-NSF PHY11-25915.
-AK was  supported by NSF grant  AST-1412107, and by the Kavli Institute for Cosmological Physics at the University of Chicago through grant PHY-1125897, and an endowment from the Kavli Foundation and its founder Fred Kavli.
-BPM acknowledges an Emmy Noether grant funded by the Deutsche Forschungsgemeinschaft (DFG, German Research Foundation) -- MO 2979/1-1.
-
-\bibliography{galsize_paper}
-
-\newpage
-\section*{Appendix: Treatment of Disrupted Subhalos}
-
-%---------------------------------------------------------------------------------------------------
-
-Recent results indicate that some portion of subhalos may be artificially disrupted \citep{guo_white13, campbell_etal17}.
-To address this possibility in our modeling, we use an extension of {\tt Consistent Trees} that models the evolution of subhalos after disruption.
-The phase space evolution of disrupted subhalos is approximated by following a point mass evolving in the host halo potential according to the orbital parameters of the subhalo at the time of disruption; the evolution of subhalo mass and circular velocity is approximated using the semi-analytic model presented in \citet{jiang_vdB14}.
-We then use the {\tt extract\_orphans} program in {\tt UniverseMachine} to walk through all the Bolshoi-Planck {\tt hlist} files, yielding the main progenitor information of every subhalo that was ever identified by {\tt Consistent Trees}.
-
-In our initial application of deconvolution abundance matching we derive the $\mstar-\mpeak$ relation using {\em all} subhalos, including those that were initially considered disrupted.
-We then apply a selection function to the disrupted subhalos, so that a fraction of these objects will host model galaxies.
-We refer to this as the {\em orphan selection function}, $\mathcal{F}_{\rm orphan},$ which we consider to be an integral component of our application of abundance matching.
-Once $\mathcal{F}_{\rm orphan}$ has been applied, the assemblage of calculations described above provides values of $\mpeak,$ $\zpeak,$ and $\mvir$ for disrupted subhalos, which are the only properties needed to apply either the $\rvir-$based or $\mstar-$based size model.
-
-In this appendix, we present two distinct choices for the orphan selection function, described in detail below.
-For the results in the main body of the text, we have opted for the simplest parameterization we could find that yields reasonably accurate recovery of the galaxy clustering signal observed in SDSS.
-While a rigorous calibration of $\mathcal{F}_{\rm orphan}$ is beyond the scope of the present work, we point out that a systematic study of subhalo disruption is needed to conduct the program discussed in \S\ref{sec:future}.
-
-In both treatments studied here, we first discard orphan subhalos with $V_{\rm max}/V_{\rm peak}<0.1,$ so that the most drastically disrupted subhalos remain unpopulated with galaxies.
-For our fiducial model used throughout the main body of the text, $\mathcal{F}_{\rm orphan}$ is defined by randomly selecting half of the orphan subhalos.
-For the alternative orphan selection function labeled as ``$M_{\rm host}-$dependent orphans" in this appendix, we proceed as follows.
-We model $\mathcal{F}_{\rm orphan}=\mathcal{F}_{\rm orphan}(M_{\rm peak},M_{\rm host}),$ where $\mpeak$ is the peak mass of the disrupted subhalo, and $\mhost$ is the present-day virial mass of its $z=0$ host halo.
-For the $\mpeak-$dependence, we select $50\%$ of disrupted subhalos with $\mpeak=10^{11}\msun,$ $0\%$ of subhalos with $\mpeak=10^{13}\msun,$ linearly interpolating in $\log\mpeak$ for intermediate values of $\mpeak.$ At each $\mpeak,$ the selection of disrupted halos is not random; instead, we preferentially select the subhalos with larger $\mhost,$ which we intend to offset the difficulty of subhalo-finding algorithms to identify subhalos with especially small values of  $\mu\equiv\mpeak/\mhost.$
-
-Figure \ref{fig:orphan_satellite_fractions} illustrates the impact of the orphan selection function on the $\mstar-$dependence of the satellite fraction, $\fsat,$ defined as the fraction of galaxies that are not centrals.
-Both models that include disrupted subhalos receive a significant boost to $\fsat$ due to orphan galaxies.
-The $\mhost-$dependent model suppresses the selection of disrupted subhalos with larger values of $\mpeak,$ resulting in a milder boost to $\fsat$ at large $\mstar.$
-
-\begin{figure}
-\centering
-\includegraphics[width=8cm]{FIGS/orphan_satellite_fraction.pdf}
-\caption{
-{\bf Impact of orphans on $\fsat.$} The y-axis shows the fraction of galaxies that are not centrals, plotted as a function of stellar mass $\mstar.$ Different curves show results for three different choices for the treatment of disrupted subhalos, as indicated in the legend and described in the text of the appendix.
-}
-\label{fig:orphan_satellite_fractions}
-\end{figure}
-
-Figure \ref{fig:orphan_baseline_clustering} shows how the treatment of orphans impacts $\mstar-$dependent clustering.
-Comparing either the black or orange curves to the red curves shows that including orphans substantially boosts small-scale clustering due to the increased satellite fraction.
-We show the impact of orphans on $\rhalf-$dependent clustering in Figure \ref{fig:orphan_size_clustering}.
-As discussed in \S\ref{subsec:censat_sizes}, the value of $\fsat$ modulates the magnitude of the influence of central/satellite size differences on $\wproj;$ including orphans thus boosts the clustering ratios $\delta\wproj/\wproj.$ Because we have not been systematic in the calibration of $\mathcal{F}_{\rm orphan},$ we adopt the simpler, random orphan selection as the fiducial model shown in the main body of the text.
-
-%-----------------------------------------------------------------------------------------------------
-
-%---------------------------------------------------------------------------------------------------
-\begin{figure*}
-\centering
-\includegraphics[width=12cm]{FIGS/baseline_sham_orphans.pdf}
-\caption{
-{\bf Impact of orphans on $\mstar-$dependent clustering.}  
-Identical to Figure \ref{fig:baseline_sham_clustering}, but including additional curves for the case of $M_{\rm host}-$dependent orphan selection (orange curves), and no orphans at all (red curves). 
-}
-\label{fig:orphan_baseline_clustering}
-\end{figure*}
-%-----------------------------------------------------------------------------------------------------
-
-%---------------------------------------------------------------------------------------------------
-\begin{figure*}
-\centering
-\includegraphics[width=12cm]{FIGS/clustering_ratios_orphan_impact.pdf}
-\caption{
-{\bf Impact of orphans on $\rhalf-$dependent clustering.}  
-Identical to Figure \ref{fig:clustering_ratio_upshot}, but including additional curves for the case of $M_{\rm host}-$dependent orphan selection (orange curves), and no orphans at all (red curves). 
-}
-\label{fig:orphan_size_clustering}
-\end{figure*}
-%-----------------------------------------------------------------------------------------------------
-
-\end{document}
+12 pages plus an appendix. Submitted to MNRAS. 
+Figure 5 shows that a simple empirical model, with R50 = 0.01Rvir, can accurately reproduce new measurements of size-dependent clustering of SDSS galaxies.
+Figure 9 shows predictions for the size-dependence of future lensing measurements.
+Figure 10 provides a diagnostic for hydro sims and SAMs

### 2018-06-09 paper/referee_reply1.txt
Replied to first comment and implemented revision

Reviewer's Comments:
Reviewer: 1

Comments to the Author
This paper presents size-dependent clustering of SDSS galaxies, and interprets it using a simple model for the dependence of effective radius on halo radius. It is well presented and the results are interesting and useful. I have however a few suggestions/questions that may help to further improve the clarity and strengthen the analysis.

MAJOR:

1) The size-halo connection that the authors advocate, presented in Section 3.2.2, sets each galaxy to be 1% of the size of its halo at the time of Mpeak. The authors state below Eq 3 that this defines a _median_ relation between Reff and Mhalo, around which they assume a log-normal scatter of 0.2 dex. However, it seems that a more direct application of Eq 2 would be to apply it on a halo-by-halo basis, since Rpeak is known for every object in the catalogue. This would specify the full Reff distribution, with scatter deriving from the scatter in Rpeak. Why is this not done? No justification is given for using a log-normal scatter of 0.2 dex.

Reply) The concluding sentence to Section 3.2.2 was indeed confusing; it turns out it was also misleading: in fact, in our analysis we assigned R_1/2 in exactly the fashion the referee described, about each halo's own R_Mpeak. We have changed the language to more accurately reflect the implementation of the model, and thank the referee for pointing out this confusing language.

2) This model is compared to one in which Reff does not correlate with any halo property at fixed stellar mass, but simply depends on M* in a manner that reproduces the M*-Reff relation by construction. Again the authors take 0.2 dex scatter around the median relation, but if one really wanted to reproduce the M*-Reff relation -- including its scatter -- one would take this scatter in bins of M* from the data. Even better would be to drop the assumption of Gaussian scatter altogether and simply assign a size randomly to each model galaxy by sampling the observed Reff distribution at given M*. It appears the authors' choice is motivated by a desire for compatibility with Somerville et al 2017, but it is unclear why this is especially relevant or important here.

3) Why use Rvir at Mpeak and not at any other time (say z=0)? I assume this is simply because Mpeak gives the best match to the observations, but this is not explained and hence comes across as somewhat arbitrary. If the result is sensitive to this (as suggested in the final paragraph of Section 5.2), then clustering provides a means to distinguish different choices for halo size in terms of how well they predict Reff. Do the authors know which choices would or would not work? It would be helpful to compare the clustering predicted by one or more alternatives.

4) There should be an uncertainty on w_p in the mock data, i.e. on the lines in Figs. 4-6. Since the model is probabilistic (both the abundance matching step and size assignment have random scatters), different Monte Carlo realisations of the model should give different results. Further, for a given realisation jackknife resampling would give an uncertainty estimate in a similar manner to the SDSS data. I would like to see these uncertainties as bands on the plots, or at least a general estimate of their magnitude. Looking at the bottom-right panel of Fig. 6, for the green line to be consistent with 0 the uncertainty on it must be fairly large, at least at low r; without this uncertainty it is hard to gauge the significance of the difference between the purple line and the data.

5) When some of the stellar mass is removed due to stripping, does this not cause the final SMF that's actually used in the model to disagree with the observed input SMF? In the discussion just below Eq 1, it seems that the distribution of M* is the one that matches the observations, not M'*. Or is the SMF that's input to AM modified somehow so that only after this stripping does it match Moustakas et al 2013?

6) A complementary method for studying the size-halo connection is to constrain correlations of galaxy size with halo properties *at fixed stellar mass*, which has been done using both weak lensing (e.g. Sonnenfeld et al 2015, Sonnenfeld & Leauthaud 2017) and galaxy dynamics (e.g. Desmond 2016, 2017). These are means of testing disk models such as Dutton et al 2007 & 2011 which the authors mention. It would be helpful to provide more information on how the Rvir-based model presented here relates to this alternative method. For example, since on average M* is positively correlated with Rpeak by AM, and empirically Reff is positively correlated with M*, then the model in which Reff depends only on M* (Sec 3.2.1) will also positively correlate Reff with Rpeak. It is not clear how this correlation differs from Reff=0.01*Rpeak, or in other words how the latter assumption correlates Reff with halo properties at fixed M*. It would be interesting to see 1) The Reff-Rpeak relation implied by the model in Sec 3.2.1, and/or 2) The correlation of Reff with halo mass or concentration at fixed M* implied by Reff=0.01*Rpeak. Understanding these different approaches will be of great help in devising a unified model for the size-halo connection.

7) Final paragraph of Section 6: It has been known for almost 20 years that the scatter in halo spin at fixed mass is larger than the scatter in galaxy size (de Jong & Lacey 2000, Gnedin et al 2007). The forward modelling implications of Reff^{disk} \propto \lambda have already been explored by Desmond & Wechsler 2015, who find it to be problematic for the Tully-Fisher relation as well as the scatter in size. Further, most modern hydrodynamical simulations (including Illustris [Rodriguez-Gomez et al 2017], EAGLE [Sales et al 2009, Desmond et al 2017] and Magneticum [Teklu et al 2015]) correlate Reff little if at all with halo spin. (It would be useful in general to provide a qualitative comparison with hydro sims, which have the potential to test models for the size-halo connection from first principles, and are beginning to do so.) Again it is unclear to me why Somerville et al 2017 should be of any particular importance for the scatter: The scatter in Reff at fixed M* comes straight from the data, and the scatter in lambda at fixed Mhalo (only relevant for angular momentum-based size models, which are barely mentioned here) comes straight from the N-body sim.

MINOR:

1) Please provide more details in the main body of the text on the method used to treat orphan subhalos, and in particular that 50% of these are populated with galaxies in the fiducial model. As shown in the Appendix, this has significant impact on the clustering results, so it is important to be up front about the assumptions required. It should also be mentioned in the main text that the AM was done using all subhalos rather than only the ones that survived, as this may lead to substantial differences with alternative AM models that do not model orphans.

2) I recommend replacing M_{halo} everywhere by the specific definition of halo mass which is being referred to, typically M_{peak}. The reader may naturally interpret M_{halo} to mean something else, for example present-day M_{vir}.

3) DD, DR and RR need to be defined in the calculation of w_p.

4) It may be helpful to normalise the pdfs in Figs 8-9 so that the total area under each curve is 1 (this may already be the case for Fig 8). It is unclear at the moment what scales are used on the y-axes.

5) I suggest that the number of galaxies and stellar mass and redshift range of the datasets used be mentioned in the first paragraph of Section 2, rather than (or in addition to) in Section 4.2. Please justify the z<0.02 cut. Is this done in the simulation as well so that the mock data has the same number of galaxies and redshift distribution as the real data? Also, why does the 10^{11} thresholded sample have the same zmax as the 10^{10.75} sample?

6) Abstract: surely one doesn't "forward model the observations"; this suggests that the observations are an input to the model, which they are precisely not in forward modelling. Perhaps one forward models *to* the observations?

7) I'll let the Scottish grammar pass, but be any misunderstanding on yer ain heids.

### 2018-06-09 paper/galsize_paper.tex
Added reference to Cebrian & Trujillo
Replied to first comment and implemented revision

@@
 where for $\Delta_{\rm vir}(\zpeak)$ we use the fitting function to the ``virial" definition used in \citet{bryan_norman98}.
-This modeling assumption effectively defines $\median{\rhalf}{\mhalo};$ this relation defines the center of the log-normal distribution with $0.2$ dex of scatter that we use to generate a Monto Carlo realization of the model population.
+We implement a forward modeled Monte Carlo realization of this model by drawing $\rhalf$ from a log-normal distribution centered on $0.01\rmpeak$ for every mock galaxy, using $0.2$ dex of scatter for consistency with the constraints obtained in \citet{somerville_etal17} (see \S\ref{sec:previous_work} for further discussion).
 
@@
 Our conclusions are also qualitatively consistent with \citet{spindler_wake17}, who find that centrals in the \citet{yang_etal05a} group catalog are $\sim20-25\%$ larger than satellites of similar halo mass (using stellar velocity dispersion as an observational proxy for halo mass); we find the same trend at a comparable, if slightly larger magnitude.
+Our clustering measurements are in good agreement with \citet{cebrian_trujillo14}, who find that the $\mean{\rhalf}{\mstar}$ relation for field galaxies is larger relative to galaxies in dense environments.
 

### 2018-06-09 paper/referee_reply1.txt
Replied to second comment and implemented revision

@@
 It appears the authors' choice is motivated by a desire for compatibility with Somerville et al 2017, but it is unclear why this is especially relevant or important here.
+
+We agree with the referee that drawing directly from P_SDSS(R_1/2 | M*) would improve the fidelity of our model with respect to the SDSS.
+However, our goal here is actually twofold.
+On the one hand, we want to identify a model that has sufficient flexibility to capture size-dependent clustering with good accuracy, using SDSS as our validation dataset.
+On the other hand, we are attempting to build a class of models that can be applied equally well to other datasets, including those may not have the statistics of the SDSS, as is the case in present-day high-redshift surveys.
+We have added what we hope is a clarifying paragraph on this point towards the end of Section 7, repeated below for convenience:
+
+---
+We have attempted to anticipate such a joint analysis in our choices for the formulation of the model presented here.
+For example, for purposes of the scope of the present work alone, one could more accurately capture the complexity of the true distribution of $\rhalf$ by drawing directly from a numerical tabulation of $P_{\rm SDSS}(\rhalf\vert\mstar).$ Here we choose to approximate this distribution with a log-normal so that the same smooth, analytic model can be applied to datasets sparser than SDSS, e.g., pencil-beam high-redshift surveys.
+While we have kept the level of scatter in our log-normal distribution fixed to the value found in \cite{somerville_etal17}, our model formulation enables self-calibration of the true (possibly mass-dependent) stochasticity in future Bayesian inference analyses.
+---
 

### 2018-06-09 paper/galsize_paper.tex
Replied to second comment and implemented revision

@@
 
+We have attempted to anticipate such a joint analysis in our choices for the formulation of the model presented here.
+For example, for purposes of the scope of the present work alone, one could more accurately capture the complexity of the true distribution of $\rhalf$ by drawing directly from a numerical tabulation of $P_{\rm SDSS}(\rhalf\vert\mstar).$ Here we choose to approximate this distribution with a log-normal so that the same smooth, analytic model can be applied to datasets sparser than SDSS, e.g., pencil-beam high-redshift surveys.
+While we have kept the level of scatter in our log-normal distribution fixed to the value found in \cite{somerville_etal17}, our model formulation enables self-calibration of the true (possibly mass-dependent) stochasticity in future Bayesian inference analyses.
+
 In ongoing follow-up work, we are extending the current analysis by jointly modeling stellar mass and size together with a bulge/disk decomposition of model galaxies quantified by ${\rm B/T},$ the fraction of the total stellar mass in the bulge.

### 2018-06-09 paper/referee_reply1.txt
Replied to third comment

@@
 
-We agree with the referee that drawing directly from P_SDSS(R_1/2 | M*) would improve the fidelity of our model with respect to the SDSS.
+Reply) We agree with the referee that drawing directly from P_SDSS(R_1/2 | M*) would improve the fidelity of our model with respect to the SDSS.
 However, our goal here is actually twofold.
@@
 It would be helpful to compare the clustering predicted by one or more alternatives.
+
+Reply) Our ``tidal stripping" model is an attempt to explore the consequences of using Mvir(z=0) to model galaxy size.
+There are certainly many other possible choices one can make for the halo property used to connect to size, such as the mass at the time of first infall, at the time of last infall, etc.
+We agree with the referee that a more comprehensive study of the hyper-parameter space is warranted by our results.
+In particular, we have found one good-fitting model based on R_Mpeak, several other poor-fitting model based on alternative choices for the galaxy-halo connection.
+This directly implies that observations of galaxy clustering can indeed discriminate between such choices.
+Thus we consider a comprehensive study (analogous to the Reddick+13 SHAM study) well-motivated by our work, but beyond the present scope.
 

### 2018-06-09 paper/referee_reply1.txt
Added reply to comment 5

@@
 
+Reply) The implementation of the stellar mass stripping model is indeed crude and to some extent the self-inconsistency pointed out by the referee is inescapable: we are after all not providing a model for the true evolution of post-infall stellar mass, but instead we are grafting an approximate treatment that is intended to approximate the impact of tidal stripping in a statistical sense.
+The modification to the SMF is rather small; we have added a comment to that effect in the text.
+
 6) A complementary method for studying the size-halo connection is to constrain correlations of galaxy size with halo properties *at fixed stellar mass*, which has been done using both weak lensing (e.g.

### 2018-06-09 paper/referee_reply1.txt
Added reply and revision to comment 7

@@
 
+Reply) We have added a new sentence to this paragraph (copied below for convenience) that clarifies the purpose of the final paragraph of Section 6, which is to call attention to the methodological similarity of our model to that in Somerville+17.
+We are interested in applying our forward-modeling techniques to see what insight can be learned about the R_1/2^{disk} \propto \lambda from galaxy clustering, which would be complementary to the knowledge gained by the Desmond & Wechsler 2015 study.
+
+---
+Their conclusions are consistent with previous findings \citep[e.g.,][]{dejong_lacey00, gnedin_etal07}, but employ modern forward-modeling methods that enable using two-point clustering as constraining data as we have  here.
+---
+
+Studying hydro sims with two-point statistics is the subject of ongoing work.
+We are including, for the referee's interest, a plot showing the results of a recent calculation of the clustering ratios exhibited by Illustris galaxies.
+We consider these and related results more appropriate for a separate follow-up paper.
+
 MINOR:

### 2018-06-09 paper/referee_reply1.txt
Added revision and reply to second minor comment

@@
 
+Reply) We have changed the text discussing Figure 10 at the end of Section 7.
+We replaced "M_{halo}" with "M_{peak}", which we agree improves the clarity of the discussion.
+We are happy to make other analogous changes if there are specific places where the referee finds ambiguity resulting from the use of the term "M_{halo}".
+
 3) DD, DR and RR need to be defined in the calculation of w_p.

### 2018-06-09 paper/galsize_paper.tex
Added reply and revision to comment 7
Added revision and reply to second minor comment

@@
 By building models where $\rhalf$ is set by halo spin $\lambda_{\rm halo}$, it was found in \citet{somerville_etal17} that the level of intrinsic scatter about $\langle\lambda_{\rm halo}\vert\mhalo\rangle$ in dark matter halos is at least as large as the scatter about $\langle\rhalf\vert\mstar\rangle$ seen in observed galaxies.
+Their conclusions are consistent with previous findings \citep[e.g.,][]{dejong_lacey00, gnedin_etal07}, but employ modern forward-modeling methods that enable using two-point clustering as constraining data as we have here.
 In our approach, the level of scatter is simply a modeling parameter whose fiducial value was motivated by \citet{somerville_etal17}.
@@
 
-Figure \ref{fig:censatsizeratios} shows that satellites in $\mhalo\approx10^{12}\msun$ halos are $\sim25-40\%$ smaller than their central galaxy counterparts.
+Figure \ref{fig:censatsizeratios} shows that satellites in $\mpeak\approx10^{12}\msun$ halos are $\sim25-40\%$ smaller than their central galaxy counterparts.
 Since the satellite fraction varies quite significantly with morphology and/or color, we have demonstrated that it is entirely plausible that most of the observed environmental trends of galaxy size can be understood simply in terms of central vs.

### 2018-06-09 paper/galsize_paper.tex
Revised text to address minor comment 1

@@
 Using the stellar mass function provided in \citet{moustakas_etal13}, we model $\mstar$ as a log-normal distribution with $0.2$ dex of scatter about the median relation $\median{\mstar}{\mpeak}$ determined by SHAM \citep{reddick_etal13}.
-As described in the appendix, we include a prescription for supplementing the ordinary {\tt Rockstar} subhalo catalog with disrupted subhalos, so that some of our model galaxies inhabit subhalos that are no longer resolved and do not appear in the standard publicly available catalog (``orphan galaxies").
+
+We include a prescription for supplementing the ordinary {\tt Rockstar} subhalo catalog with disrupted subhalos, so that some of our model galaxies inhabit subhalos that are no longer resolved and do not appear in the standard publicly available catalog (``orphan galaxies").
+Orphans play an important in our model due to the sensitivity of $\rhalf$-dependent clustering upon the satellite fraction.
+In our fiducial model whose results are shown in the main body of the text, half of the disrupted subhalos are selected prior to application of SHAM.
+We explore alternative treatments of orphans in the appendix.
 

### 2018-06-09 paper/galsize_paper.tex
Revised draft to address minor comment 3

@@
 2017, in prep).
-The {\tt correl} code uses the \citet{landy_szalay93} estimator ($DD - 2DR + RR$) to compute the redshift-space correlation function $\xi(\rproj, \pi)$, which is then integrated over $\vert\pi\vert < 20$ Mpc to compute the projected correlation function $\wproj(\rproj)$.
+As a function of projected separation, the {\tt correl} code calculates the number of pairs of galaxies, DD, the number of pairs of galaxy-randoms, DR, and the number of random-random pairs, RR.
+Using the \citet{landy_szalay93} estimator ($DD - 2DR + RR$), we compute the redshift-space correlation function $\xi(\rproj, \pi)$, which is then integrated over $\vert\pi\vert < 20$ Mpc to compute the projected correlation function $\wproj(\rproj)$.
 The code uses $10^6$ randoms drawn from the same mask region with uniform volume distribution to compute $DR$, and $RR$ is computed via Monte Carlo integration.

### 2018-06-09 paper/referee_reply1.txt
Added reply and revisions for major comment 6

@@
 
+Reply)  We have verified the correlation between R_1/2 and Mvir at fixed M* in present day centrals, and added a paragraph to Section 6 with the suggested references.
+The new text is repeated below for convenience.
+
+---
+In closely related work, efforts to constrain correlations of galaxy size with halo properties at fixed stellar mass have been carried out using both weak lensing \citep[e.g.,][]{sonnenfeld_leauthaud18} and galaxy dynamics \citep[e.g.,][]{desmond_wechsler15,desmond_wechsler17}.
+Our results complement these previous studies in that forward-modeling galaxy observables directly into simulations provides a rigorous means by which one can test hypotheses of correlations implemented at fixed halo properties.
+In our fiducial model with $\mean{\rhalf}{\rmpeak}=0.01\rmpeak,$ for Milky Way mass centrals there exists a significant positive correlation between present day mass and galaxy size at fixed stellar mass; these alternative methods are a natural testbed for future tests of the basic conclusions drawn here based on two-point clustering.
+---
+
 7) Final paragraph of Section 6: It has been known for almost 20 years that the scatter in halo spin at fixed mass is larger than the scatter in galaxy size (de Jong & Lacey 2000, Gnedin et al 2007).

### 2018-06-09 paper/galsize_paper.tex
Added reply and revisions for major comment 6

@@
 
+In closely related work, efforts to constrain correlations of galaxy size with halo properties at fixed stellar mass have been carried out using both weak lensing \citep[e.g.,][]{sonnenfeld_leauthaud18} and galaxy dynamics \citep[e.g.,][]{desmond_wechsler15,desmond_wechsler17}.
+Our results complement these previous studies in that forward-modeling galaxy observables directly into simulations provides a rigorous means by which one can test hypotheses of correlations implemented at fixed halo properties.
+In our fiducial model with $\mean{\rhalf}{\rmpeak}=0.01\rmpeak,$ for Milky Way mass centrals there exists a significant positive correlation between present day mass and galaxy size at fixed stellar mass; these alternative methods are a natural testbed for future tests of the basic conclusions drawn here based on two-point clustering.
+
 To date, the $\rhalf-$dependence of $\Delta\Sigma$ has not yet been measured for $\mstar-$complete samples.

### 2018-06-10 paper/referee_reply1.txt
Modified reply to comment 5 and implemented revision in draft

@@
 Reply) The implementation of the stellar mass stripping model is indeed crude and to some extent the self-inconsistency pointed out by the referee is inescapable: we are after all not providing a model for the true evolution of post-infall stellar mass, but instead we are grafting an approximate treatment that is intended to approximate the impact of tidal stripping in a statistical sense.
-The modification to the SMF is rather small; we have added a comment to that effect in the text.
+That being said, the modification to the SMF is rather small, at or below 10% for the mass ranges relevant to our clustering measurements, and so comparing these two models directly should not be too misleading.
+We have added a sentence at the end of 3.2.1 calling attention to this detail.
 

### 2018-06-10 paper/referee_reply1.txt
Revised text and reply again to comment 6

--- 2018-06-09 paper/referee_reply1.txt
@@
 On the other hand, we are attempting to build a class of models that can be applied equally well to other datasets, including those may not have the statistics of the SDSS, as is the case in present-day high-redshift surveys.
-We have added what we hope is a clarifying paragraph on this point towards the end of Section 7, repeated below for convenience:
-
----
-We have attempted to anticipate such a joint analysis in our choices for the formulation of the model presented here.
-For example, for purposes of the scope of the present work alone, one could more accurately capture the complexity of the true distribution of $\rhalf$ by drawing directly from a numerical tabulation of $P_{\rm SDSS}(\rhalf\vert\mstar).$ Here we choose to approximate this distribution with a log-normal so that the same smooth, analytic model can be applied to datasets sparser than SDSS, e.g., pencil-beam high-redshift surveys.
-While we have kept the level of scatter in our log-normal distribution fixed to the value found in \cite{somerville_etal17}, our model formulation enables self-calibration of the true (possibly mass-dependent) stochasticity in future Bayesian inference analyses.
----
+We have added what we hope is a clarifying paragraph on this point towards the end of Section 7.
 
@@
 
+Reply)  We have verified the correlation between R_1/2 and Mvir at fixed M* in present day centrals, and added a paragraph to Section 6 with the suggested references.
+
 7) Final paragraph of Section 6: It has been known for almost 20 years that the scatter in halo spin at fixed mass is larger than the scatter in galaxy size (de Jong & Lacey 2000, Gnedin et al 2007).
@@
 
-Reply) We have added a new sentence to this paragraph (copied below for convenience) that clarifies the purpose of the final paragraph of Section 6, which is to call attention to the methodological similarity of our model to that in Somerville+17.
+Reply) We have added a new sentence that clarifies the purpose of the final paragraph of Section 6, which is to call attention to the methodological similarity of our model to that in Somerville+17.
 We are interested in applying our forward-modeling techniques to see what insight can be learned about the R_1/2^{disk} \propto \lambda from galaxy clustering, which would be complementary to the knowledge gained by the Desmond & Wechsler 2015 study.
-
----
-Their conclusions are consistent with previous findings \citep[e.g.,][]{dejong_lacey00, gnedin_etal07}, but employ modern forward-modeling methods that enable using two-point clustering as constraining data as we have  here.
----
 

### 2018-06-10 paper/galsize_paper.tex
Modified reply to comment 5 and implemented revision in draft
Revised text and reply again to comment 6

--- 2018-06-09 paper/galsize_paper.tex
@@
 As shown in \citet{smith_etal16}, stellar stripping in this model does not begin until $f_{\rm DM}\lesssim0.2,$ and in order for $\sim50\%$ of stars to be stripped, the DM halo needs to be stripped to $\sim5\%$ of its initial mass.
+We note that mass loss slightly depletes the stellar mass function of this model relative to the \citet{moustakas_etal13}, but the differences are less than $10\%$ for stellar masses $\mstar\gtrsim10^{9.5}\msun.$
 
@@
 
-To date, the $\rhalf-$dependence of $\Delta\Sigma$ has not yet been measured for $\mstar-$complete samples.
+In other closely related work, efforts to constrain correlations between galaxy size and various halo properties at fixed {\em stellar mass} have been carried out using both weak lensing \citep[e.g.,][]{sonnenfeld_leauthaud18} and galaxy dynamics \citep[e.g.,][]{desmond_wechsler15,desmond_wechsler17}.
+Our results complement these previous studies: forward-modeling galaxies directly into simulations allows us to test hypotheses of correlations at fixed {\em halo mass.} Calculating fixed-$\mstar$ correlations from a Monte Carlo realization of the model is straightforward, and in our fiducial model, in which $\mean{\rhalf}{\rmpeak}=0.01\rmpeak,$ for Milky Way mass centrals of the same $\mstar$ there exists a significant positive correlation between present day halo mass $\mvir$ and galaxy size $\rhalf.$ Alternative observational methods based on lensing and dynamics such as those mentioned above are a natural testbed for the conclusions drawn here based on two-point clustering.
+We now give an example of how such a future measurement could be made to directly and independently test these conclusions.
+
+The $\rhalf-$dependence of $\Delta\Sigma$ has not yet been measured for $\mstar-$complete samples.
 In the left panels of Figure \ref{fig:lensingprediction}, we show predictions of the $\rvir-$based model for future measurements of $\Delta\Sigma.$ The halo model principles underlying the lensing trends are the same as for $\wproj.$ For $\mstar\lesssim10^{11}\msun,$ the difference in $F_{\rm sat}$ between small and large samples is the dominant factor; satellites occupy higher mass host halos relative to centrals of the same stellar mass, boosting $\Delta\Sigma$ for small relative to large galaxy samples.

### 2018-06-10 paper/galsize_paper.tex
Updated notebook and plots to include jackknife error estimation for clustering ratios

@@
 Closely related to Figure \ref{fig:rvir_only_clustering_absolute}, y-axes show {\em clustering strength ratios,} defined as $\delta\wproj/\wproj\equiv(w_{\rm p}^{\rm large} - w_{\rm p}^{\rm small})/w_{\rm p}^{\rm all}.$ Thus a y-axis value of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass.
-Solid curves show predictions of the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}.
+Solid curves show predictions of the $\rvir-$based model described in \S\ref{subsubsec:rvirmodel}, with gray bands showing our jackknife error estimation.
 Normalizing the measurements and predictions by $w_{\rm p}^{\rm all}$ scales away the shortcoming of ordinary abundance matching (see Figure \ref{fig:baseline_sham_clustering}), highlighting the successful prediction of the $\rvir-$based model for the $\rhalf-$dependence of galaxy clustering.
@@
 As a specific example, a clustering ratio of $-0.5$ corresponds to small galaxies being $50\%$ more strongly clustered than large galaxies of the same stellar mass.
+The gray bands enveloping each curve show our $1\sigma$ error bars, estimated by jackknifing 125 subvolumes.
 
@@
 The figure shows that this model clearly is at odds with the significant dependence of clustering on size exhibited by SDSS galaxies.
+Error bars are not shown for this model but they are comparable to the errors shown on the purple curves calculated through same jackknife estimation method used in Figure~\ref{fig:clustering_ratio_upshot}.
 

### 2018-06-10 paper/galsize_paper.tex
Modified text to address minor comment 5

@@
 
+We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds: an  $\mstar>10^{9.75}\msun$ sample with $z_{\rm max}=0.0435$ and $N_{\rm gal}=27658;$ an  $\mstar>10^{10.25}\msun$ sample with $z_{\rm max}=0.0663$ and $N_{\rm gal}=48571;$
+an  $\mstar>10^{10.75}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=52350;$ 
+and an  $\mstar>10^{11}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=33578.$ We follow standard practice \citep[e.g.,][]{zehavi_etal11} and throw out all galaxies with $z<z_{\rm min}=0.02;$ we also throw out galaxies with redshift $z \geq z_{\rm max}=0.1$ even in cases where a volume-limited sample would be attainable out to higher redshift.
+
 For mock galaxies, we compute $\wproj$ using the {\tt mock\_observables.wp} function in {\tt Halotools} \citep{hearin_etal16}, which is a python implementation of the algorithm in the {\tt Corrfunc} C library \citep{sinha_etal17}.
@@
 
-In Figure~\ref{fig:rvir_only_clustering_absolute}, we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj(\rproj).$ We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds: an  $\mstar>10^{9.75}\msun$ sample with $z_{\rm max}=0.0435$ and $N_{\rm gal}=27658;$ an  $\mstar>10^{10.25}\msun$ sample with $z_{\rm max}=0.0663$ and $N_{\rm gal}=48571;$
-an  $\mstar>10^{10.75}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=52350;$ 
-and an  $\mstar>10^{11}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=33578.$ For each threshold, we split the galaxies into ``large" and ``small" subsamples, as described in \S\ref{subsec:sizedef}.
+In Figure~\ref{fig:rvir_only_clustering_absolute}, we present new measurements of the $\rhalf-$dependence of projected galaxy clustering, $\wproj(\rproj).$ As described in \S\ref{sec:data}, we measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds: $\log\mstar/\msun\geq 9.75, 10.25, 10.75, 11.$
+%$\mstar\geq10^{9.75}\msun; \mstar\geq10^{10.25}\msun; \mstar\geq10^{10.75}\msun; \mstar\geq10^{11}\msun.$ 
+For each threshold, we split the galaxies into ``large" and ``small" subsamples, as described in \S\ref{subsec:sizedef}.
 As shown in Figure \ref{fig:sizedefinition}, our size-based samples  have similar stellar mass functions.

### 2018-06-10 paper/galsize_paper.tex
Changed language in abstract to accommodate referee objection to grammatical construction related to forward modeling

@@
 The magnitude of this clustering difference increases on small scales, and decreases with increasing stellar mass. 
-Using {\tt Halotools} to forward model the observations, we test an empirical model in which present-day galaxy size is 
+Using forward model techniques implemented in {\tt Halotools}, we test an empirical model in which present-day galaxy size is 
 proportional to the size of the virial radius at the time the halo reached its maximum mass. This simple model reproduces the 

### 2018-06-10 paper/galsize_paper.tex
Expanded discussion of correl program

@@
 2017, in prep).
-As a function of projected separation, the {\tt correl} code calculates the number of pairs of galaxies, DD, the number of pairs of galaxy-randoms, DR, and the number of random-random pairs, RR.
+For two samples of points distributed in redshift space, $\vec{x}_1$ and $\vec{x}_2,$ with $\vec{s}\equiv\vec{x}_2-\vec{x}_1$ and $\vec{l}\equiv0.5(\vec{x}_2+\vec{x}_1),$ the {\tt correl} code program counts the number of pairs of points within a line-of-sight distance $\pi\equiv(\vec{s}\cdot\vec{l})/\vert\vec{l}\vert$ and transverse separation $r_{\rm p}\equiv\sqrt{s^{2} - \pi^{2}}.$ When both sets of points are galaxy data, the resulting pair-counts are denoted by DD; when both sets are random points, RR; cross-counts between data and randoms are denoted by DR.
 Using the \citet{landy_szalay93} estimator ($DD - 2DR + RR$), we compute the redshift-space correlation function $\xi(\rproj, \pi)$, which is then integrated over $\vert\pi\vert < 20$ Mpc to compute the projected correlation function $\wproj(\rproj)$.
@@
 an  $\mstar>10^{10.75}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=52350;$ 
-and an  $\mstar>10^{11}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=33578.$ We follow standard practice \citep[e.g.,][]{zehavi_etal11} and throw out all galaxies with $z<z_{\rm min}=0.02;$ we also throw out galaxies with redshift $z \geq z_{\rm max}=0.1$ even in cases where a volume-limited sample would be attainable out to higher redshift.
+and an  $\mstar>10^{11}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=33578.$ We follow standard practice \citep[e.g.,][]{zehavi_etal11} and throw out all galaxies with $z<z_{\rm min}=0.02$ to minimize lightcone effects; to minimize the effect of redshift evolution we also throw out galaxies with redshift $z \geq z_{\rm max}=0.1,$ including cases where a volume-limited sample would be attainable out to higher redshift.
 

### 2018-06-10 paper/referee_reply1.txt
Thanked referee in reply
Added sentence in reply addressing no justification given for the scatter

@@
-Reviewer's Comments:
-Reviewer: 1
+We thank the referee for a thoughtful, expert critique of our paper. We respond to each major and minor comment below, omitting a direct reply when the changes were straightforward to implement.
 
@@
 We have changed the language to more accurately reflect the implementation of the model, and thank the referee for pointing out this confusing language.
+We have also expanded the discussion for our choice of the fiducial level of scatter, as described further in our reply to the next comment.
 

### 2018-06-14 paper/referee_reply1.txt
Completed revisions after implementing changes suggested by co-authors

@@
-We thank the referee for a thoughtful, expert critique of our paper. We respond to each major and minor comment below, omitting a direct reply when the changes were straightforward to implement.
+We thank the referee for a thoughtful, expert critique of our paper.
+We respond to each major and minor comment below, omitting a direct reply to the minor comments when the changes were straightforward to implement.
 
@@
 We agree with the referee that a more comprehensive study of the hyper-parameter space is warranted by our results.
-In particular, we have found one good-fitting model based on R_Mpeak, several other poor-fitting model based on alternative choices for the galaxy-halo connection.
+In particular, we have found one good-fitting model based on R_Mpeak, and several other poor-fitting models based on alternative choices for the galaxy-halo connection.
 This directly implies that observations of galaxy clustering can indeed discriminate between such choices.
@@
 6, for the green line to be consistent with 0 the uncertainty on it must be fairly large, at least at low r; without this uncertainty it is hard to gauge the significance of the difference between the purple line and the data.
+
+Reply) We have added jackknife error bars in the form of shaded bands surrounding wp in the figures comparing models to data.
 
@@
 
+We note that although the correlation of size or baryon specific angular momentum with current specific halo angular momentum is found to be weak in current simulations, some simulations show a nearly linear size-virial radius correlation consistent with observations (J.
+Schaye, private comm.).
+Also, the observed distribution of galaxy sizes is comparable to that expected in simple spin-based models from the halo spin distribution, when galaxies of *all* types are considered.
+Thus, the smaller scatter of sizes exhibited by disk galaxies may indicate either that sizes are affected by other factors and not only by spin, or, alternatively, that disk galaxies do not sample the entire spin distribution of halos.
+Both possibilities are very interesting and motivate future studies, which we believe are outside the scope of this paper.
+
 MINOR:

### 2018-06-14 paper/galsize_paper.tex
Completed revisions after implementing changes suggested by co-authors

@@
 \newcommand{\bt}{{\rm B/T}}
-\newcommand{\mstar}{M_{\ast}}
+\newcommand{\mstar}{M_{\star}}
 \newcommand{\ssfr}{{\rm sSFR}}
@@
 \caption{
-{\bf Definition of ``small" and ``large" galaxies.} For a volume-limited SDSS galaxy sample defined by $M_{\ast}>10^{10.25}M_{\odot},$ the {\em top panel} visually demonstrates how we classify galaxies into ``small" and ``large" subsamples in an $\mstar$-dependent manner.
+{\bf Definition of ``small" and ``large" galaxies.} For a volume-limited SDSS galaxy sample defined by $M_{\star}>10^{10.25}M_{\odot},$ the {\em top panel} visually demonstrates how we classify galaxies into ``small" and ``large" subsamples in an $\mstar$-dependent manner.
 As described in detail in \S\ref{subsec:sizedef}, we compute the median value $\median{\rhalf}{\mstar}$ at the stellar mass of each galaxy in the sample, and divide the sample into two based on this $\mstar-$dependent cut.
@@
 The basis for our implementation of this phenomenon is the fitting function presented in \citet{smith_etal16}, which was calibrated by studying stellar mass loss in a suite of high-resolution hydrodynamical simulations.
-In this model, $f_{\ast}$ quantifies the remaining fraction of stellar mass as a function of $f_{\rm DM},$ the fraction of dark matter mass that remains after subhalo infall:
+In this model, $f_{\star}$ quantifies the remaining fraction of stellar mass as a function of $f_{\rm DM},$ the fraction of dark matter mass that remains after subhalo infall:
 \beq
-f_{\ast} = 1 - \exp(-14.2f_{\rm DM}).
+f_{\star} = 1 - \exp(-14.2f_{\rm DM}).
 \eeq
-For $f_{\rm DM}$ we use the ratio of present-day subhalo mass divided by the peak mass, $M_{\rm vir}/M_{\rm peak}.$ If we denote the post-stripping stellar mass as $M_{\ast}',$ then we have $M_{\ast}'\equiv f_{\ast}M_{\ast},$ where $M_{\ast}$ is given by the initial application of abundance matching.
+For $f_{\rm DM}$ we use the ratio of present-day subhalo mass divided by the peak mass, $M_{\rm vir}/M_{\rm peak}.$ If we denote the post-stripping stellar mass as $M_{\star}',$ then we have $M_{\star}'\equiv f_{\star}M_{\star},$ where $M_{\star}$ is given by the initial application of abundance matching.
 We then calculate the post-stripping radius by interpolating $\langle\rhalf'\vert\mstar'\rangle$ directly from SDSS data.
@@
 So in models where satellites are smaller than centrals of the same mass, smaller galaxies will have a higher satellite fraction, boosting the clustering of small relative to large galaxies of the same stellar mass.
-Second, at fixed mass, halos of $L_\ast$ galaxies that form earlier are more strongly clustered, a phenomenon commonly known as {\em halo assembly bias} \citep{gao_white05,wechsler_etal06}.
+Second, at fixed mass, halos of $L_\star$ galaxies that form earlier are more strongly clustered, a phenomenon commonly known as {\em halo assembly bias} \citep{gao_white05,wechsler_etal06}.
 Splashback halos are typically earlier-forming than true centrals \citep{wang_etal09}, and so models where splashback halos host smaller-than-average galaxies will naturally predict smaller galaxies being the more strongly clustered \citep[see, e.g.,][for a demonstration of the splashback-dependence of halo clustering]{sunayama_etal16}.
@@
 
-Recent results indicate that some portion of subhalos may be artificially disrupted \citep{guo_white13, campbell_etal17}.
+Recent results indicate that some portion of subhalos may be artificially disrupted \citep{guo_white13, campbell_etal17, vdBosch_etal17, vdbosch_ogiya18}.
 To address this possibility in our modeling, we use an extension of {\tt Consistent Trees} that models the evolution of subhalos after disruption.

### 2018-06-14 paper/galsize_paper.tex
Fixed abstract and updated ascii version

@@
 The magnitude of this clustering difference increases on small scales, and decreases with increasing stellar mass.
-Using forward model techniques implemented in {\tt Halotools}, we test an empirical model in which present-day galaxy size is
+Using forward modeling techniques implemented in {\tt Halotools}, we test an empirical model in which present-day galaxy size is
 proportional to the size of the virial radius at the time the halo reached its maximum mass. This simple model reproduces the

### 2018-06-14 paper/submission_notes.tex
Fixed abstract and updated ascii version

@@
 The magnitude of this clustering difference increases on small scales, and decreases with increasing stellar mass.
-Using Halotools to forward model the observations, we test an empirical model in which present-day galaxy size is proportional to the size of the virial radius at the time the halo reached its maximum mass.
+Using forward modeling techniques implemented in Halotools, we test an empirical model in which present-day galaxy size is proportional to the size of the virial radius at the time the halo reached its maximum mass.
 This simple model reproduces the observed size-dependence of galaxy clustering in striking detail.

### 2018-07-11 paper/galsize_paper.tex
Added KITP grant acknowledgement

@@
 Work done at Argonne National Laboratory was supported under the DOE contract DE-AC02-06CH11357.
-This research was supported in part by the National Science Foundation under Grant No.
+This research was supported in part by the National Science Foundation under Grants No.
 NSF PHY11-25915.
+Research for this paper was initiated at the Kavli Institute of Theoretical Physics workshop on the Galaxy-Halo Connection, which is supported by NSF PHY17-48958.
 AK was supported by NSF grant  AST-1412107, and by the Kavli Institute for Cosmological Physics at the University of Chicago through grant PHY-1125897, and an endowment from the Kavli Foundation and its founder Fred Kavli.

### 2019-07-17 paper/referee_reply2.txt
Revised text and added reply to referee comment 1

We thank the referee...

1. Re: Discussion in Section 3.2.2

Referee: "So to be clear, you have two sources of scatter in R_1/2 at fixed M* that sum in quadrature: 1) The scatter between M* and R_Mpeak, and 2) An additional 0.2 scatter that you impose by hand. Does this not increase the scatter in the M*-Reff relation to more than the level of Somerville et al 2017? I'm not sure what the scatter in R_Mpeak is at fixed M*, but the M*-Reff relation does not have more than 0.2 dex scatter."

Reply:

We have added a clarifying sentence to Section 6 to address this potential source of confusion.

2. Section 4.3

"If you have found models for the galaxy-halo connection other than the tidal stripping model which provide a poor fit to the observations, please mention them in the paper. Otherwise other people will waste their time investigating them."

3. Jackknife error bars

"Jackknife was one of the error estimation methods that I mentioned, but what about the scatter between different Monte Carlo realisations of the model. Presumably each realisation, with different M* and R_1/2 values for each subhalo, gives a single line on Figs 4-6, so that the entire model effectively produces a band even before jackknifing. How big is this scatter relative to that between different subregions for the same realisation? Or am I missing something and the line can only be calculated over many realisations? I don't think the role of the Monte Carlo realisations is explained completely clearly. Also, why not add the band to the green lines in Fig 6? It would be good to see explicitly that these are consistent with 0."

4. Section 6

"The Desmond 2016, 2017 papers I was referring to were MNRAS 464 (4) 4160 and MNRAS 472 (1) L35. These papers use galaxies' M-R-V scalings to constrain the R_1/2--Mvir,c relation at fixed M*, after applying AM. They find that at fixed M*, R_1/2 is weakly anticorrelated with Mvir or c. Thus I would suggest that the positive R_1/2--Mvir correlation at fixed M* implied by your model is in conflict with galaxies' internal dynamics, for example by leading to a positive correlation between the residuals of the Tully-Fisher and mass-size relations, which is not observed. Perhaps you could add this caveat."

5. The final comment in the referee's second review partains to a qualitative comment we made in our response to the initial report. This issue is germane to ongoing follow-up work on the relation between galaxy size and halo spin, but is mostly tangential to the scope of the present work.

### 2019-07-17 paper/galsize_paper.tex
Revised text and added reply to referee comment 1

@@
 Their conclusions are consistent with previous findings \citep[e.g.,][]{dejong_lacey00, gnedin_etal07}, but employ modern forward-modeling methods that enable using two-point clustering as constraining data as we have here.
-In our approach, the level of scatter is simply a modeling parameter whose fiducial value was motivated by \citet{somerville_etal17}.
-In ongoing follow-up work discussed in \S\ref{sec:future}, we will systematically test the large-scale structure implications of the assumption that $\rhalf^{\rm disk}\propto\lambda_{\rm halo}$ using forward-modeling methods analogous to those advocated for in \citet{somerville_etal17} and employed here.
+In our approach, the level of scatter about the $\langle\rhalf\vert\mstar\rangle$ relation receives a contribution both from the scatter in the stellar-to-halo mass relation, $\langle\mstar\vert\mhalo\rangle,$ as well as from scatter about the $\langle\rhalf\vert\mhalo\rangle$ relation; the fiducial value chosen for the former level of scatter was motivated by the results in \citet{reddick_etal13} to ensure our fiducial model has reasonable satellite fractions; the fiducial value for the second contribution to the model's stochasticity was motivated by \citet{somerville_etal17}.
+Both modeling choices are germane to ongoing follow-up work discussed in \S\ref{sec:future}, in which we will systematically test the large-scale structure implications of the assumption that $\rhalf^{\rm disk}\propto\lambda_{\rm halo}$ using forward-modeling methods analogous to those advocated for in \citet{somerville_etal17} and employed here.
 

### 2019-07-17 paper/referee_reply2.txt
Updated reply to referee report with additional citations to Desmond 2016 and Desmond 2017

@@
 
-Reply:
-
-We have added a clarifying sentence to Section 6 to address this potential source of confusion.
+Reply: We have added a clarifying sentence to Section 6 to address this potential source of confusion.
 
@@
 
-"If you have found models for the galaxy-halo connection other than the tidal stripping model which provide a poor fit to the observations, please mention them in the paper.
+Referee: "If you have found models for the galaxy-halo connection other than the tidal stripping model which provide a poor fit to the observations, please mention them in the paper.
 Otherwise other people will waste their time investigating them."
+
+Reply: We have included discussion of all additional models we developed for purposes of the present paper.
 
@@
 
-"Jackknife was one of the error estimation methods that I mentioned, but what about the scatter between different Monte Carlo realisations of the model.
+Referee: "Jackknife was one of the error estimation methods that I mentioned, but what about the scatter between different Monte Carlo realisations of the model.
 Presumably each realisation, with different M* and R_1/2 values for each subhalo, gives a single line on Figs 4-6, so that the entire model effectively produces a band even before jackknifing.
@@
 
+Reply:
+
 4. Section 6
 
-"The Desmond 2016, 2017 papers I was referring to were MNRAS 464 (4) 4160 and MNRAS 472 (1) L35.
+Referee: "The Desmond 2016, 2017 papers I was referring to were MNRAS 464 (4) 4160 and MNRAS 472 (1) L35.
 These papers use galaxies' M-R-V scalings to constrain the R_1/2--Mvir,c relation at fixed M*, after applying AM.
@@
 
+Reply: We have added two additional citations, Desmond (2016) and Desmond (2017), and called attention to possible tension between our findings and those deriving from internal dynamics.
+
 5.

### 2019-07-17 paper/galsize_paper.tex
Updated reply to referee report with additional citations to Desmond 2016 and Desmond 2017

@@
 In other closely related work, efforts to constrain correlations between galaxy size and various halo properties at fixed {\em stellar mass} have been carried out using both weak lensing \citep[e.g.,][]{sonnenfeld_leauthaud18} and galaxy dynamics \citep[e.g.,][]{desmond_wechsler15,desmond_wechsler17}.
-Our results complement these previous studies: forward-modeling galaxies directly into simulations allows us to test hypotheses of correlations at fixed {\em halo mass.} Calculating fixed-$\mstar$ correlations from a Monte Carlo realization of the model is straightforward, and in our fiducial model, in which $\mean{\rhalf}{\rmpeak}=0.01\rmpeak,$ for Milky Way mass centrals of the same $\mstar$ there exists a significant positive correlation between present day halo mass $\mvir$ and galaxy size $\rhalf.$ Alternative observational methods based on lensing and dynamics such as those mentioned above are a natural testbed for the conclusions drawn here based on two-point clustering.
+Our results complement these previous studies: forward-modeling galaxies directly into simulations allows us to test hypotheses of correlations at fixed {\em halo mass.} Calculating fixed-$\mstar$ correlations from a Monte Carlo realization of the model is straightforward, and in our fiducial model, in which $\mean{\rhalf}{\rmpeak}=0.01\rmpeak,$ for Milky Way mass centrals of the same $\mstar$ there exists a significant positive correlation between present day halo mass $\mvir$ and galaxy size $\rhalf,$ in some tension with the finding based on internal dynamics that at fixed $\mstar,$ there is a weak anti-correlation between $\rhalf$ and halo mass \citep{desmond17a,desmond17b}.
+Alternative observational methods based on lensing and dynamics such as those mentioned above are a natural testbed for the conclusions drawn here based on two-point clustering.
 We now give an example of how such a future measurement could be made to directly and independently test these conclusions.

### 2019-07-17 galsize_models/measurements/load_cross_matched_umachine.py
Modified paths in the loader modules to identify the updated location to the data files after some laptop reorganization. Cannot find /Users/aphearin/work/SIMS/bolplanck/cross_matched_orphan_catalog.hdf5, so will need to go digging for this on my backup disks.

@@ -7,7 +7,7 @@ from astropy.table import Table
 
 __all__ = ('load_umachine_sdss_with_meert15', 'mendel13_bulge_to_total')
 
-default_datadir = "/Users/aphearin/work/sdss/cross_matched_catalogs/meert15"
+default_datadir = "/Users/aphearin/work/DATA/SDSS/cross_matched_catalogs/meert15"
 
 
 def load_umachine_sdss_with_meert15(datadir=default_datadir):

### 2019-07-17 galsize_models/models/load_baseline_catalogs.py

@@ -37,7 +37,7 @@ moster13_halocat_keys = ('halo_upid', 'halo_mpeak', 'halo_scale_factor_mpeak',
         'halo_vx', 'halo_vy', 'halo_vz', 'halo_rvir_zpeak', 'halo_vmax_at_mpeak_percentile',
         'halo_mvir_host_halo', 'halo_spin', 'halo_uran')
 
-smf_dirname = "/Users/aphearin/work/UniverseMachine/code/UniverseMachine/obs"
+smf_dirname = "/Users/aphearin/work/repositories/c/universemachine/obs"
 smf_basename = "moustakas_z0.01_z0.20.smf"
 smf_fname = os.path.join(smf_dirname, smf_basename)
 smf = np.loadtxt(smf_fname)

### 2019-07-18 galsize_models/models/load_baseline_catalogs.py
Updated notebook

@@ -159,7 +159,7 @@ def load_orphan_mock():
     """ Note that this function calls a Moster+13 model and applies a cut on stellar mass.
     """
 
-    dirname = "/Users/aphearin/work/sims/bolplanck/orphan_catalog_z0"
+    dirname = "/Users/aphearin/work/DATA/SIMS/BPl/orphan_catalog_z0"
     basename = "cross_matched_orphan_catalog.hdf5"
 
     halo_table = Table.read(os.path.join(dirname, basename), path='data')
@@ -197,7 +197,7 @@ def load_orphan_mock():
 def load_orphan_subhalos():
     """
     """
-    dirname = "/Users/aphearin/work/sims/bolplanck/orphan_catalog_z0"
+    dirname = "/Users/aphearin/work/DATA/SIMS/BPl/orphan_catalog_z0"
     basename = "cross_matched_orphan_catalog.hdf5"
 
     halo_table = Table.read(os.path.join(dirname, basename), path='data')

### 2019-07-18 paper/galsize_paper.tex
Updated figure 6 to include jackknife errors around the purple curves

--- 2018-07-11 paper/galsize_paper.tex
@@
 In all panels, the axes and points with error bars are the same as in Figure \ref{fig:clustering_ratio_upshot}.
-The solid green curves show the prediction of a model where $\rhalf$ is statistically set by $\mstar,$ in the complete absence of satellite mass loss.
+The green curves show the prediction of a model where $\rhalf$ is statistically set by $\mstar,$ in the complete absence of satellite mass loss.
 Such a model predicts zero $\rhalf-$dependence to galaxy clustering, in gross tension with observations.
-The solid purple curves show results for a model in which satellites lose mass after infall in a manner similar to what is seen in high-resolution hydrodynamical simulations, as described in \S\ref{subsubsec:strippingmodel}.
+The purple curves show results for a model in which satellites lose mass after infall in a manner similar to what is seen in high-resolution hydrodynamical simulations, as described in \S\ref{subsubsec:strippingmodel}.
 This produces satellites that are smaller than centrals, but the effect is too mild to correctly capture the observed clustering.
@@
 in which galaxy size is controlled by $\mstar$ (\S\ref{subsubsec:strippingmodel}).
-Green solid lines show predictions of the $\mstar$-based model that does not account for mass loss due to tides.
+Green curves show predictions of the $\mstar$-based model that does not account for mass loss due to tides.
 In this model, $\rhalf$ follows a purely random log-normal distribution, with the median relation $\median{\rhalf}{\mstar}$ directly matched to the observed relation by construction.
@@
 The figure shows that this model clearly is at odds with the significant dependence of clustering on size exhibited by SDSS galaxies.
-Error bars are not shown for this model but they are comparable to the errors shown on the purple curves calculated through same jackknife estimation method used in Figure~\ref{fig:clustering_ratio_upshot}.
 

### 2019-07-19 paper/galsize_paper.tex
Added sentence describing error bands
Updated text describing Figure 6

--- 2019-07-17 paper/galsize_paper.tex
@@
 in which galaxy size is controlled by $\mstar$ (\S\ref{subsubsec:strippingmodel}).
-Green solid lines show predictions of the $\mstar$-based model that does not account for mass loss due to tides.
+Shaded bands around all model predictions show $1\sigma$ jackknife errors, as in Fig.~\ref{fig:clustering_ratio_upshot}.
+Green curves show predictions of the $\mstar$-based model that does not account for mass loss due to tides.
 In this model, $\rhalf$ follows a purely random log-normal distribution, with the median relation $\median{\rhalf}{\mstar}$ directly matched to the observed relation by construction.

### 2019-07-19 paper/referee_reply2.txt
Updated referee reply

@@
 
-Reply:
+Reply: We have included jackknife error estimation the errors on the green curve in Figure 6.
+We have furthermore verified that for these clustering ratios, statistical errors associated with Monte Carlo realizations are approximately captured by the jackknife: when we repeat the error estimation by repopulating each of the 125 jackknife subsamples with a new realization, the error bars on the ratio plots are comparable to the more standard treatment in which mock population is done once.
+We consider this sufficient for the purpose of these error estimations, which is merely to guide the reader's eye, rather than to compute chi^2 in an MCMC analysis.
 
-4. Section 6
+4. Section 6 discussion
 

### 2019-07-19 paper/referee_reply2.txt
Finished reply to referee

@@
-We thank the referee...
+We thank the referee for careful consideration of our revised manuscript. The second round of requested changes were rather minor, and so we apologize for our protracted reply.
+
+In the intervening time we have pursued two closely related directions of research that we had originally thought might be included in our revisions: 1.
+Studying the IllustrisTNG predictions for size-dependent lensing, and 2.
+new SDSS measurements of size-dependentlensing.
+In the end, both extensions turned out to be more involved than we anticipated, and so we have decided to pursue these directions in separate papers.
+
+We respond to each of the referee's second round of comments in the text below.
 

### 2019-08-06 paper/galsize_paper.tex
Implemented all of Andrey's comments on new submission except for the data table

@@
 For two samples of points distributed in redshift space, $\vec{x}_1$ and $\vec{x}_2,$ with $\vec{s}\equiv\vec{x}_2-\vec{x}_1$ and $\vec{l}\equiv0.5(\vec{x}_2+\vec{x}_1),$ the {\tt correl} code program counts the number of pairs of points within a line-of-sight distance $\pi\equiv(\vec{s}\cdot\vec{l})/\vert\vec{l}\vert$ and transverse separation $r_{\rm p}\equiv\sqrt{s^{2} - \pi^{2}}.$ When both sets of points are galaxy data, the resulting pair-counts are denoted by DD; when both sets are random points, RR; cross-counts between data and randoms are denoted by DR.
-Using the \citet{landy_szalay93} estimator ($DD - 2DR + RR$), we compute the redshift-space correlation function $\xi(\rproj, \pi)$, which is then integrated over $\vert\pi\vert < 20$ Mpc to compute the projected correlation function $\wproj(\rproj)$.
+Using the \citet{landy_szalay93} estimator ($DD - 2DR + RR$), we compute the redshift-space correlation function $\xi(\rproj, \pi)$.
+The function is then integrated over $\vert\pi\vert < 20$ Mpc to compute the projected correlation function $\wproj(\rproj)$.
 The code uses $10^6$ randoms drawn from the same mask region with uniform volume distribution to compute $DR$, and $RR$ is computed via Monte Carlo integration.
@@
 Given that $\alpha\sim 1-3$ is inferred for the $\mstar-\mvir$ relation at low masses \citep{kravtsov10,moster_etal13,behroozi13_smhm,kravtsov_etal14}, the $\rhalf-\mstar$ relation in this regime is expected to be shallow.
-For galaxies of $\mstar\gtrsim 5\times 10^{10}\ M_\odot$, $\alpha\approx 0.3$ \citep[e.g.,][]{kravtsov_etal14}, and thus
+For galaxies of $\mstar\gtrsim 5\times 10^{10}\ M_\odot$, $\alpha\approx 0.3$ \citep[e.g.,][]{kravtsov_etal18}, and thus
 the slope of the $\rhalf-\mstar$ relation is approximately linear.
@@
 In other closely related work, efforts to constrain correlations between galaxy size and various halo properties at fixed {\em stellar mass} have been carried out using both weak lensing \citep[e.g.,][]{sonnenfeld_leauthaud18} and galaxy dynamics \citep[e.g.,][]{desmond_wechsler15,desmond_wechsler17}.
-Our results complement these previous studies: forward-modeling galaxies directly into simulations allows us to test hypotheses of correlations at fixed {\em halo mass.} Calculating fixed-$\mstar$ correlations from a Monte Carlo realization of the model is straightforward, and in our fiducial model, in which $\mean{\rhalf}{\rmpeak}=0.01\rmpeak,$ for Milky Way mass centrals of the same $\mstar$ there exists a significant positive correlation between present day halo mass $\mvir$ and galaxy size $\rhalf,$ in some tension with the finding based on internal dynamics that at fixed $\mstar,$ there is a weak anti-correlation between $\rhalf$ and halo mass \citep{desmond17a,desmond17b}.
+Our results complement these previous studies: forward-modeling galaxies directly in simulations allows us to test hypotheses of correlations at fixed {\em halo mass.} Calculating fixed-$\mstar$ correlations from a Monte Carlo realization of the model is straightforward, and in our fiducial model, in which $\mean{\rhalf}{\rmpeak}=0.01\rmpeak,$ for Milky Way mass centrals of the same $\mstar$ there exists a significant positive correlation between present day halo mass $\mvir$ and galaxy size $\rhalf,$ in some tension with the finding based on internal dynamics that at fixed $\mstar,$ there is a weak anti-correlation between $\rhalf$ and halo mass \citep{desmond17a,desmond17b}.
 Alternative observational methods based on lensing and dynamics such as those mentioned above are a natural testbed for the conclusions drawn here based on two-point clustering.

### 2019-08-06 paper/galsize_paper.tex
Added Andrey's final suggestion for a data table of galaxy sample information.

@@
 
-We measure $\wproj(\rproj)$ separately for large and small subsamples for four different $\mstar$ thresholds: an  $\mstar>10^{9.75}\msun$ sample with $z_{\rm max}=0.0435$ and $N_{\rm gal}=27658;$ an  $\mstar>10^{10.25}\msun$ sample with $z_{\rm max}=0.0663$ and $N_{\rm gal}=48571;$
-an  $\mstar>10^{10.75}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=52350;$
-and an  $\mstar>10^{11}\msun$ sample with $z_{\rm max}=0.1$ and $N_{\rm gal}=33578.$ We follow standard practice \citep[e.g.,][]{zehavi_etal11} and throw out all galaxies with $z<z_{\rm min}=0.02$ to minimize lightcone effects; to minimize the effect of redshift evolution we also throw out galaxies with redshift $z \geq z_{\rm max}=0.1,$ including cases where a volume-limited sample would be attainable out to higher redshift.
+We measure $\wproj(\rproj)$ separately for large and small subsamples for four different thresholds in $\log_{10}\mstar/\msun:$ 9.75, 10.25, 10.75, and 11.
+We follow standard practice \citep[e.g.,][]{zehavi_etal11} and throw out all galaxies with $z<z_{\rm min}=0.02$ to minimize lightcone effects; to minimize the effect of redshift evolution we also throw out galaxies with redshift $z \geq z_{\rm max}=0.1,$ including cases where a volume-limited sample would be attainable out to higher redshift.
+We refer to Table \ref{table:data} for a summary of our volume-limited galaxy samples.
+
+\begin{table}
+\caption{Summary of SDSS galaxy samples used as constraining data.
+The stellar mass threshold defining the mass-limited sample appears in the leftmost column.
+The remaining columns show the redshift range and the total number of galaxies in each sample.
+} % title of Table
+\centering % used for centering table
+\begin{tabular}{c c c c} % centered columns (4 columns)
+\hline\hline %inserts double horizontal lines
+$\log_{10}\mstar^{\rm min}/M_{\odot}$ & $z_{\rm min}$ & $z_{\rm max}$ & $N_{\rm gal}$ \\ [0.5ex] % inserts table
+%heading
+\hline % inserts single horizontal line
+9.75 & 0.02 & 0.0435 & 27658 \\ % inserting body of the table
+10.25 & 0.02 & 0.0663 & 48571\\
+10.75 & 0.02 & 0.1 & 52350 \\
+11 & 0.02 & 0.1 & 33578 \\ [1ex] % [1ex] adds vertical space
+\hline %inserts single line
+\end{tabular}
+\label{table:data} % is used to refer this table in the text
+\end{table}
 

### 2019-08-12 paper/referee_reply2.txt
Updated reply to referee. Version submitted for reconsideration

@@
+The submitted draft is a very minor revision from a previously submitted manuscript that had reached the "minor revisions" stage of the MNRAS referee process.
+However, we missed the deadline for resubmitting the second revision, and in accord with an email exchange with Joop Schaye, we are submitting this paper as a new manuscript.
+
+In the intervening time since the last round of minor revisions, we have pursued two closely related directions of research that we had originally thought might be included in our revisions: 1.
+Studying the IllustrisTNG predictions for size-dependent lensing, and 2.
+new SDSS measurements of size-dependent lensing.
+In the end, both extensions turned out to be more involved than we anticipated, and so we have decided to pursue these directions in separate papers.
+We apologize for the inconvenient timing and hope that our tardiness will not adversely influence the review of our manuscript.
+
+As the original referee was clearly an expert in the relevant domain who has already provided a thorough review of the paper, we request that the same referee review the current manuscript, if possible.
+To facilitate review of our resubmission, we have included below our response to the second referee report, and as supplementary material we have uploaded a redline PDF showing the changes made in the second round of revisions.
+
+-----
+
 We thank the referee for careful consideration of our revised manuscript. The second round of requested changes were rather minor, and so we apologize for our protracted reply.
-
-In the intervening time we have pursued two closely related directions of research that we had originally thought might be included in our revisions: 1.
-Studying the IllustrisTNG predictions for size-dependent lensing, and 2.
-new SDSS measurements of size-dependentlensing.
-In the end, both extensions turned out to be more involved than we anticipated, and so we have decided to pursue these directions in separate papers.
 

### 2019-08-12 paper/submitted_tarball/galsize_paper.tex
Tarballed up source files for final submission

--- 2019-08-06 paper/galsize_paper.tex
@@
 
+\begin{keywords}
+galaxies: statistics -- galaxies: fundamental parameters -- galaxies: haloes -- galaxies: evolution --  cosmology: large-scale structure of Universe
+\end{keywords}
+
 %----------------------------
@@
 
-Observations of two-point galaxy clustering, $\wproj(\rproj),$ have historically been used to place tight constraints on many features of the galaxy--halo connection, such as its $\mstar-$dependence \citep{moster_etal10,leauthaud_etal11,reddick_etal13,skibba_etal15}, dependence on luminosity \citep{kravtsov_etal04, tasitsiomi_etal04,vale_ostriker04,vale_ostriker06,tinker_etal05,cacciato_etal13}, broadband color \citep{coil_etal08,zehavi_etal11,guo_etal11,hearin_watson13}, and star-formation rate \citep{wang_etal07,tinker_etal13,watson_etal14}.
+Observations of two-point galaxy clustering, $\wproj(\rproj),$ have historically been used to place tight constraints on many features of the galaxy--halo connection, such as its $\mstar-$dependence \citep{moster_etal10,behroozi_etal10,leauthaud_etal11,reddick_etal13,skibba_etal15}, dependence on luminosity \citep{kravtsov_etal04, tasitsiomi_etal04,vale_ostriker04,vale_ostriker06,tinker_etal05,cacciato_etal13}, broadband color \citep{coil_etal08,zehavi_etal11,guo_etal11,hearin_watson13}, and star-formation rate \citep{wang_etal07,tinker_etal13,watson_etal14}.
 In the present work, we exploit the constraining power of $\wproj(\rproj)$ to test empirical models connecting galaxy stellar mass and size to the properties of the galaxy's parent dark matter halo.
@@
 We measure $\wproj(\rproj)$ separately for large and small subsamples for four different thresholds in $\log_{10}\mstar/\msun:$ 9.75, 10.25, 10.75, and 11.
-We follow standard practice \citep[e.g.,][]{zehavi_etal11} and throw out all galaxies with $z<z_{\rm min}=0.02$ to minimize lightcone effects; to minimize the effect of redshift evolution we also throw out galaxies with redshift $z \geq z_{\rm max}=0.1,$ including cases where a volume-limited sample would be attainable out to higher redshift.
+We follow standard practice \citep[e.g.,][]{zehavi_etal11} and throw out all galaxies with $z<z_{\rm min}=0.02$ to ensure the applicability of our use of the small-angle approximation in calculating two-point clustering; to minimize the effect of redshift evolution we also throw out galaxies with redshift $z \geq z_{\rm max}=0.1,$ including cases where a volume-limited sample would be attainable out to higher redshift.
 We refer to Table \ref{table:data} for a summary of our volume-limited galaxy samples.
@@
 We include a prescription for supplementing the ordinary {\tt Rockstar} subhalo catalog with disrupted subhalos, so that some of our model galaxies inhabit subhalos that are no longer resolved and do not appear in the standard publicly available catalog (``orphan galaxies").
-Orphans play an important in our model due to the sensitivity of $\rhalf$-dependent clustering upon the satellite fraction.
+Orphans play an important role in our model due to the sensitivity of $\rhalf$-dependent clustering upon the satellite fraction.
 In our fiducial model whose results are shown in the main body of the text, half of the disrupted subhalos are selected prior to application of SHAM.
@@
 Their conclusions are consistent with previous findings \citep[e.g.,][]{dejong_lacey00, gnedin_etal07}, but employ modern forward-modeling methods that enable using two-point clustering as constraining data as we have here.
-In our approach, the level of scatter about the $\langle\rhalf\vert\mstar\rangle$ relation receives a contribution both from the scatter in the stellar-to-halo mass relation, $\langle\mstar\vert\mhalo\rangle,$ as well as from scatter about the $\langle\rhalf\vert\mhalo\rangle$ relation; the fiducial value chosen for the former level of scatter was motivated by the results in \citet{reddick_etal13} to ensure our fiducial model has reasonable satellite fractions; the fiducial value for the second contribution to the model's stochasticity was motivated by \citet{somerville_etal17}.
+In our approach, the level of scatter about the $\langle\rhalf\vert\mhalo\rangle$ relation receives a contribution both from the scatter in the stellar-to-halo mass relation, $\langle\mstar\vert\mhalo\rangle,$ as well as from scatter about the $\langle\rhalf\vert\mstar\rangle$ relation; the fiducial value chosen for the former level of scatter was motivated by the results in \citet{reddick_etal13} to ensure our fiducial model has reasonable satellite fractions; the fiducial value for the second contribution to the model's stochasticity was motivated by \citet{somerville_etal17}.
 Both modeling choices are germane to ongoing follow-up work discussed in \S\ref{sec:future}, in which we will systematically test the large-scale structure implications of the assumption that $\rhalf^{\rm disk}\propto\lambda_{\rm halo}$ using forward-modeling methods analogous to those advocated for in \citet{somerville_etal17} and employed here.
